### 2008-07-23 papers/web_of_ideas/web_of_ideas.tex/web_of_ideas.tex.tex
moved repo from svn to git

%% Based on a TeXnicCenter-Template by Gyorgy SZEIDL.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------
%
\documentclass{article}%
%Options -- Point size:  10pt (default), 11pt, 12pt
%        -- Paper size:  letterpaper (default), a4paper, a5paper, b5paper
%                        legalpaper, executivepaper
%        -- Orientation  (portrait is the default)
%                        landscape
%        -- Print size:  oneside (default), twoside
%        -- Quality      final(default), draft
%        -- Title page   notitlepage, titlepage(default)
%        -- Columns      onecolumn(default), twocolumn
%        -- Equation numbering (equation numbers on the right is the default)
%                        leqno
%        -- Displayed equations (centered is the default)
%                        fleqn (equations start at the same distance from the right side)
%        -- Open bibliography style (closed is the default)
%                        openbib
% For instance the command
%           \documentclass[a4paper,12pt,leqno]{article}
% ensures that the paper size is a4, the fonts are typeset at the size 12p
% and the equation numbers are on the left side
%
\usepackage{amsmath}%
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{graphicx}
%-------------------------------------------
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\title{This is the Title of a Standard \LaTeX\ Article}
\author{J. A. Smith\thanks{This is for making an acknowledgement.}
\\The University of Miskolc, Hungary}
\date{February 24, 2002}
\maketitle

\begin{abstract}
This is a sample document which shows the most important features of the Standard
\LaTeX\ Journal Article class.
\end{abstract}

\section{Introduction}

\noindent The front matter has various entries such as\\
\hspace*{\fill}\verb" \title", \verb"\author", \verb"\date", and
\verb"\thanks"\hspace*{\fill}\\
You should replace their arguments with your own.

This text is the body of your article. You may delete everything between the commands\\
\hspace*{\fill} \verb"\begin{document}" \ldots \verb"\end{documant}"
\hspace*{\fill}\\in this file to start with a blank document.

\section{The Most Important Features}

\noindent Sectioning commands. The first one is the\\
\hspace*{\fill} \verb"\section{The Most Important Features}" \hspace*{\fill}\\
command. Below you shall find examples for further sectioning commands:

\subsection{Subsection}
Subsection text.

\subsubsection{Subsubsection}
Subsubsection text.

\paragraph{Paragraph}
Paragraph text.

\subparagraph{Subparagraph}Subparagraph text.\vspace{2mm}

Select a part of the text then click on the button Emphasize (H!), or Bold (Fs), or
Italic (Kt), or Slanted (Kt) to typeset \emph{Emphasize}, \textbf{Bold},
\textit{Italics}, \textsl{Slanted} texts.

You can also typeset \textrm{Roman}, \textsf{Sans Serif}, \textsc{Small Caps}, and
\texttt{Typewriter} texts.

You can also apply the special, mathematics only commands $\mathbb{BLACKBOARD}$
$\mathbb{BOLD}$, $\mathcal{CALLIGRAPHIC}$, and $\mathfrak{fraktur}$. Note that
blackboard bold and calligraphic are correct only when applied to uppercase letters A
through Z.

You can apply the size tags -- Format menu, Font size submenu -- {\tiny tiny},
{\scriptsize scriptsize}, {\footnotesize footnotesize}, {\small small}, {\normalsize
normalsize}, {\large large}, {\Large Large}, {\LARGE LARGE}, {\huge huge} and {\Huge
Huge}.

You can use the \verb"\begin{quote} etc. \end{quote}" environment for typesetting
short quotations. Select the text then click on Insert, Quotations, Short Quotations:

\begin{quote}
The buck stops here. \emph{Harry Truman}

Ask not what your country can do for you; ask what you can do for your
country. \emph{John F Kennedy}

I am not a crook. \emph{Richard Nixon}

I did not have sexual relations with that woman, Miss Lewinsky. \emph{Bill Clinton}
\end{quote}

The Quotation environment is used for quotations of more than one paragraph. Following
is the beginning of \emph{The Jungle Books} by Rudyard Kipling. (You should select
the text first then click on Insert, Quotations, Quotation):

\begin{quotation}
It was seven o'clock of a very warm evening in the Seeonee Hills when Father Wolf woke
up from his day's rest, scratched himself, yawned  and spread out his paws one after
the other to get rid of sleepy feeling in their tips. Mother Wolf lay with her big gray
nose dropped across her four tumbling, squealing cubs, and the moon shone into the
mouth of the cave where they all lived. ``\emph{Augrh}'' said Father Wolf, ``it is time
to hunt again.'' And he was going to spring down hill when a little shadow with a bushy
tail crossed the threshold and whined: ``Good luck go with you, O Chief of the Wolves;
and good luck and strong white teeth go with the noble children, that they may never
forget the hungry in this world.''

It was the jackal---Tabaqui the Dish-licker---and the wolves of India despise Tabaqui
because he runs about making mischief, and telling tales, and eating rags and pieces of
leather from the village rubbish-heaps. But they are afraid of him too, because
Tabaqui, more than any one else in the jungle, is apt to go mad, and then he forgets
that he was afraid of anyone, and runs through the forest biting everything in his way.
\end{quotation}

Use the Verbatim environment if you want \LaTeX\ to preserve spacing, perhaps when
including a fragment from a program such as:
\begin{verbatim}
#include <iostream>         // < > is used for standard libraries.
void main(void)             // ''main'' method always called first.
{
 cout << ''This is a message.'';
                            // Send to output stream.
}
\end{verbatim}
(After selecting the text click on Insert, Code Environments, Code.)

\subsection{Mathematics and Text}

It holds \cite{KarelRektorys} the following
\begin{theorem}
(The Currant minimax principle.) Let $T$ be completely continuous selfadjoint operator
in a Hilbert space $H$. Let $n$ be an arbitrary integer and let $u_1,\ldots,u_{n-1}$ be
an arbitrary system of $n-1$ linearly independent elements of $H$. Denote
\begin{equation}
\max_{\substack{v\in H, v\neq
0\\(v,u_1)=0,\ldots,(v,u_n)=0}}\frac{(Tv,v)}{(v,v)}=m(u_1,\ldots, u_{n-1})
\label{eqn10}
\end{equation}
Then the $n$-th eigenvalue of $T$ is equal to the minimum of these maxima, when
minimizing over all linearly independent systems $u_1,\ldots u_{n-1}$ in $H$,
\begin{equation}
\mu_n = \min_{\substack{u_1,\ldots, u_{n-1}\in H}} m(u_1,\ldots, u_{n-1}) \label{eqn20}
\end{equation}
\end{theorem}
The above equations are automatically numbered as equation (\ref{eqn10}) and
(\ref{eqn20}).

\subsection{List Environments}

You can create numbered, bulleted, and description lists using the tag popup
at the bottom left of the screen.

\begin{enumerate}
\item List item 1

\item List item 2

\begin{enumerate}
\item A list item under a list item.

The typeset style for this level is different than the screen style. \ The
screen shows a lower case alphabetic character followed by a period while the
typeset style uses a lower case alphabetic character surrounded by parentheses.

\item Just another list item under a list item.

\begin{enumerate}
\item Third level list item under a list item.

\begin{enumerate}
\item Fourth and final level of list items allowed.
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}

\begin{itemize}
\item Bullet item 1

\item Bullet item 2

\begin{itemize}
\item Second level bullet item.

\begin{itemize}
\item Third level bullet item.

\begin{itemize}
\item Fourth (and final) level bullet item.
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}

\begin{description}
\item[Description List] Each description list item has a term followed by the
description of that term. Double click the term box to enter the term, or to
change it.

\item[Bunyip] Mythical beast of Australian Aboriginal legends.
\end{description}

\subsection{Theorem-like Environments}

The following theorem-like environments (in alphabetical order) are available
in this style.

\begin{acknowledgement}
This is an acknowledgement
\end{acknowledgement}

\begin{algorithm}
This is an algorithm
\end{algorithm}

\begin{axiom}
This is an axiom
\end{axiom}

\begin{case}
This is a case
\end{case}

\begin{claim}
This is a claim
\end{claim}

\begin{conclusion}
This is a conclusion
\end{conclusion}

\begin{condition}
This is a condition
\end{condition}

\begin{conjecture}
This is a conjecture
\end{conjecture}

\begin{corollary}
This is a corollary
\end{corollary}

\begin{criterion}
This is a criterion
\end{criterion}

\begin{definition}
This is a definition
\end{definition}

\begin{example}
This is an example
\end{example}

\begin{exercise}
This is an exercise
\end{exercise}

\begin{lemma}
This is a lemma
\end{lemma}

\begin{proof}
This is the proof of the lemma.
\end{proof}

\begin{notation}
This is notation
\end{notation}

\begin{problem}
This is a problem
\end{problem}

\begin{proposition}
This is a proposition
\end{proposition}

\begin{remark}
This is a remark
\end{remark}

\begin{solution}
This is a solution
\end{solution}

\begin{summary}
This is a summary
\end{summary}

\begin{theorem}
This is a theorem
\end{theorem}

\begin{proof}
[Proof of the Main Theorem]This is the proof.
\end{proof}
\medskip

This text is a sample for a short bibliography. You can cite a book by making use of
the command \verb"\cite{KarelRektorys}": \cite{KarelRektorys}. Papers can be cited
similarly: \cite{Bertoti97}. If you want multiple citations to appear in a single set
of square brackets you must type all of the citation keys inside a single citation,
separating each with a comma. Here is an example: \cite{Bertoti97, Szeidl2001,
Carlson67}.

\begin{thebibliography}{9}                                                                                                %
\bibitem {KarelRektorys}Rektorys, K., \textit{Variational methods in Mathematics,
Science and Engineering}, D. Reidel Publishing Company,
Dordrecht-Hollanf/Boston-U.S.A., 2th edition, 1975

\bibitem {Bertoti97} \textsc{Bert\'{o}ti, E.}:\ \textit{On mixed variational formulation
of linear elasticity using nonsymmetric stresses and displacements}, International
Journal for Numerical Methods in Engineering., \textbf{42}, (1997), 561-578.

\bibitem {Szeidl2001} \textsc{Szeidl, G.}:\ \textit{Boundary integral equations for
plane problems in terms of stress functions of order one}, Journal of Computational and
Applied Mechanics, \textbf{2}(2), (2001), 237-261.

\bibitem {Carlson67}  \textsc{Carlson D. E.}:\ \textit{On G\"{u}nther's stress functions
for couple stresses}, Quart. Appl. Math., \textbf{25}, (1967), 139-146.
\end{thebibliography}

\appendix

\section{The First Appendix}

The appendix fragment is used only once. Subsequent appendices can be created
using the Section Section/Body Tag.
\end{document}

### 2008-07-23 client_js/tl_helpers.js

@@ -1,0 +1,440 @@
+
+function tl_log(msg){		
+	if(typeof console !== "undefined"){
+		console.log(msg);
+	}
+}
+
+function doAJAX(scriptID,url,callback) {
+	//if (typeof thinklink_callback !== "undefined") { tl_log("callback: "+thinklink_callback); }
+	var url = thinklink_urlbase + url;
+	var doc = document;
+	var scripttag = doc.createElement("script");
+    thinklink_callback = callback;
+    scripttag.src = url+"&cb=thinklink_callback";
+    scripttag.type = "text/javascript";
+	scripttag.id = scriptID;
+    doc.getElementsByTagName("head")[0].appendChild(scripttag);
+}
+
+function mark_snippet(snippet) {
+	var text = document.body.textContent.replace(/\s+/g," ");
+	var offset = text.indexOf(snippet);
+	if(offset == -1) return null;
+
+	var snipspans = [];
+	
+	addspans(document.body,offset,snippet.length,snippet,snipspans,false);
+	return snipspans;
+}
+
+function addspans(node,start,length,snipText,snipspans,sawSpace) {
+	var nodeText = node.textContent.replace(/\s+/g," ");
+	
+	if (start+length < nodeText.length) {
+		start = nodeText.indexOf(snipText);
+	}
+	
+	if (node.nodeName == "#text") {
+		// before snippet
+		if (start != 0) {
+			var beforeNode = document.createTextNode(nodeText.substring(0,start));
+			node.parentNode.insertBefore(beforeNode,node);
+		}
+		// during snippet
+		var newSpan = document.createElement("span");
+		newSpan.className = "highlight";
+		var middleNode = document.createTextNode(nodeText.substring(start,start+length));
+		node.parentNode.insertBefore(newSpan,node);
+		newSpan.appendChild(middleNode);
+		snipspans.push(newSpan);
+		
+		
+		// after snippet
+		if (start+length < nodeText.length) {
+			var afterNode = document.createTextNode(nodeText.substring(start+length));
+			node.parentNode.insertBefore(afterNode,node);
+		}
+		node.parentNode.removeChild(node);
+	}
+	else {
+		var nodeList = [];
+		var alltext = "";
+		var done = 0;
+		for (var k=0; k<node.childNodes.length; k++) {
+			if(node.childNodes[k].nodeName != "#comment" ){//&& node.childNodes[k].nodeName != "SCRIPT"){
+				nodeList.push(node.childNodes[k]);
[…]

### 2008-07-23 client_js/tl_snippet.js

@@ -1,0 +1,243 @@
+function tl_snippet(id,author,sourceText,pointText,pointID,date) {
+	this.author = author;
+	this.sourceText = sourceText;
+	this.displayText = pointText;
+	this.pointText = pointText;
+	this.pointID = pointID;
+	this.timestamp = date;
+	this.id = id;
+	this.position;
+	this.height;
+	this.spanList; // array of span nodes surrounding snippet text on page
+	
+	this.setPosition = function(pos){
+		this.position = pos;
+	}
+	
+	this.setGroupPosition = function(pos){
+		this.groupPosition = pos;
+	}
+	
+	this.setHeight = function(h) {
+		this.height = h;
+	}
+}
+
+function tl_snippet_dialog(margin) {
+	// make any necessary <div>s
+	this.divID = "tl_snippet_dialog";
+	// set the associated margin
+	this.margin = margin;
+	// set the snippet source text looking at
+	this.sourceText;
+	// set the snippet permalink for the source text
+	this.permaLink;
+	this.gotPermaLink = false;
+	// where to post new snippet link
+	this.postURL = "new_snippet_link.php";
+	// where to post new point
+	this.newPointURL = "new_point.php";
+	
+	this.init = function() {
+		$("<div></div>").attr("id",this.divID).addClass("tl_dialog").appendTo($("body")); // add dialog element to DOM
+		//$("#"+this.divID).draggable();
+		$("#"+this.divID).hide();		// hide the dialog
+	}
+	
+	this.showMe = function(){
+		$("#"+this.divID).animate({ width: 'show', opacity: 'show' }, 'fast');
+	}
+
+	this.hideMe = function(){
+		$("#"+this.divID).animate({ height: 'hide', opacity: 'hide' }, 'slow');
+	}
+	
+	this.new = function(sourceText){
+		if (sourceText=="" || sourceText == null) { return; }
+		this.sourceText = sourceText;
+		
+		// determine last dom node to aid in finding associated permalink
+		var sourceSpans = mark_snippet(this.sourceText);
+		if(!sourceSpans) return;
+		
+		var pivotSpan = sourceSpans[sourceSpans.length-1];
+		var that = this;
+		this.permaLink = this.margin.normTool.findPermalinkForNode(pivotSpan,this.sourceText,function(url){
+			tl_log("permalink is :"+url);
+			that.permaLink = url;
+			that.gotPermaLink = true;
+		});
+		that.makeNewSnippetDialog(sourceSpans);
+	};
+	
[…]

### 2008-07-23 client_js/tl_url.js

@@ -1,0 +1,169 @@
+
+function tl_normurl(){	
+	this.essentialArg = function(str){
+		var str = str.toLowerCase();
+		if(str.match("id") || str.match("article") || str.match("post") || str.match("story")){
+			return true;
+		}else{
+			return false;
+		}	
+	};
+	
+	this.normalizeUrl = function(url){
+		var urlinfo = this.getFormArgs(url);
+		var request = "";
+		for(var i in urlinfo.args){
+			if(this.essentialArg(i)){						
+				if(request != ""){
+					request += "&";
+				}else{
+					request += "?";
+				}
+				request += i + "=" + urlinfo.args[i];
+			}
+		}
+		return urlinfo.base + request;
+	};
+	
+	this.getFormArgs = function(url){
+    if(!url) return {};
+    var formmatch = url.match(/\?([^\#]*)/);
+    if(!formmatch || !formmatch[1]){
+    	 return {base:url};
+    };
+    var formstr = formmatch[1];
+    
+    var basematch = url.match(/([^?#]*)/);
+    if(!basematch) return {};
+    var baseurl = basematch[1];
+    
+    var argstrs = formstr.match(/[^=\&]+=[^=\&]*/g);
+    var formargs = {};
+    for(var i = 0; i < argstrs.length; i++){
+        var parts = argstrs[i].match(/(.*)=(.*)/);
+        formargs[parts[1]] = parts[2];
+    }
+        
+    return {base:baseurl,args:formargs};
+	};
+	
+	this.permstr = function(str){
+		if(!str){
+			return false;
+		}
+		str = str.toLowerCase();
+		return str.match("permalink") || str.match("permanent link");
+	};
+
+	// returned in document order	
+	this.findPermalinks = function(){
+		var links = document.getElementsByTagName("a");
+		
+		var permalinks = [];				
+		for(var i = 0; i < links.length; i++){
+			var link = links[i];
+			if(this.permstr(link.className) ||
+				this.permstr(link.textContent) ||
+				link.getAttribute("rel") == "bookmark" ||
+				this.permstr(link.getAttribute("title"))){					
+					permalinks.push(link);
+			}
+		}
+		return permalinks;
+	};
+		
+	this.getPos = function(node){
+    var left = 0;
+    var top = 0;
+    while(node){
+        left += node.offsetLeft;
+        top += node.offsetTop;
+        node = node.offsetParent;
+    }
+    return {left:left,top:top};
+  };
+	
[…]

### 2008-07-23 firefox_plugin/chrome/content/thinklink.js

@@ -1,0 +1,223 @@
+
+// this is the script that we inject into every page we load
+
+var thinklink_base_rob = 
+"http://mashmaker.intel-research.net/rob/scripts/";
+
+var thinklink_base = 
+"http://mashmaker.intel-research.net/beth/scripts/";
+
+
+var thinklink_scriptUrls;
+
+function thinklink_setScriptUrls(username){
+	if(username == "rob@ennals.org"){
+	 	thinklink_base = thinklink_base_rob;
+	}
+	
+	thinklink_scriptUrls = 
+		[thinklink_base+"jquery-1.2.3.js",
+		thinklink_base+"ui.core.js",
+		thinklink_base+"ui.draggable.js",
+		thinklink_base+"ui.resizable.js",
+		thinklink_base+"tl_margin.js",
+		thinklink_base+"tl_snippet.js",
+		thinklink_base+"tl_point.js",
+		thinklink_base+"tl_helpers.js",
+		thinklink_base+"tl_suggest.js",
+		thinklink_base+"tl_url.js"];
+		
+	if(username == "rob@ennals.org"){
+		thinklink_scriptUrls.push(thinklink_base+"tl_robconfig.js");	
+	}else{
+		thinklink_scriptUrls.push(thinklink_base+"tl_bethconfig.js");
+	}
+	
+	thinklink_scriptUrls.push(thinklink_base+"thinklink.js");
+}
+
+// var thinklink_scriptUrl = "http://berkeley.intel-research.net/rennals/thinklink.js";
+var thinklink_styleUrl = "http://mashmaker.intel-research.net/beth/css/style.css";
+
+var thinklink_name = "ThinkLink";
+
+
+function thinklink_error(msg,e){
+	thinklink_msg(msg);
+	Components.utils.reportError(e);
+}
+
+function thinklink_msg(msg){
+	var cs = Components.classes["@mozilla.org/consoleservice;1"].getService(Components.interfaces.nsIConsoleService);
+	cs.logStringMessage(thinklink_name + ": " + msg);
+}
+
+function thinklink_show(button){
+	var doc = thinklink_winlistener.getDoc();
+	if(button.checked){
+		doc.location.href = "javascript:myMargin.hideMargin()";
+	}else{
+		doc.location.href = "javascript:myMargin.showMargin()";
+	}
+	button.checked = !button.checked;
+	doc.thinklink_checked = button.checked;
+}
+
+function thinklink_setIcon(image,doc){
[…]

### 2008-07-23 junk/point.rb

@@ -1,0 +1,5 @@
+class Point < ActiveRecord::Base
+	has_many :snippets
+	
+	validates_presence_of :title
+end

### 2008-07-23 junk/snippet.rb

@@ -1,0 +1,4 @@
+class Snippet < ActiveRecord::Base
+	belongs_to :point
+	belongs_to :user	
+end

### 2008-07-23 package/makepackage.sh

@@ -1,0 +1,9 @@
+#!/usr/bin/bash
+
+pushd ../firefox_plugin/chrome
+zip -r thinklink.jar content skin
+popd
+mv ../firefox_plugin/chrome/thinklink.jar chrome/
+rm thinklink.xpi
+zip -r thinklink.xpi chrome chrome.manifest defaults install.rdf
+

### 2008-07-23 rails_server/thinklink/app/controllers/application.rb

@@ -1,0 +1,18 @@
+# Filters added to this controller apply to all controllers in the application.
+# Likewise, all the methods added will be available for all controllers.
+
+class ApplicationController < ActionController::Base
+  helper :all # include all helpers, all the time
+	include ApplicationHelper
+	
+	before_filter :setup_auth
+
+  # See ActionController::RequestForgeryProtection for details
+  # Uncomment the :secret if you're not using the cookie session store
+  protect_from_forgery # :secret => '6a2bfcac8927de12b6b0511cb48db6ea'
+  
+  # See ActionController::Base for details 
+  # Uncomment this to filter the contents of submitted sensitive data parameters
+  # from your application log (in this case, all fields with names like "password"). 
+  # filter_parameter_logging :password
+end

### 2008-07-23 rails_server/thinklink/app/controllers/main_controller.rb

@@ -1,0 +1,36 @@
+class MainController < ApplicationController
+	include MainHelper
+
+	def feed
+		@points = Point.find(:all)
+		emit(@points)
+	end
+
+  def register
+    if request.post?
+      @user = User.new params[:user]
+      if @user.save
+        flash[:info] = 'You are registered now'
+      end
+    end
+  end
+    
+  def login
+  	if request.post?
+  	  if auth_correct?(params[:email],params[:password])
+			   cookies[:email] = params[:email]
+			   cookies[:password] = params[:password]					   
+	       redirect_to :controller => 'news', :action => 'index'
+			else 
+			   @auth_error = 'Wrong username or password'
+			end
+  	end
+	end
+	
+	def showuser
+		check_auth
+		@email = cookies[:email]
+		@password = cookies[:password]
+	end
+
+end

### 2008-07-23 rails_server/thinklink/app/controllers/snippets_controller.rb

@@ -1,0 +1,59 @@
+class SnippetsController < ApplicationController
+	layout 'standard';
+	auto_complete_for :snippet, :url
+
+
+	def index		
+		@title = "Recent Snippets"
+		@snippets = Snippet.all(:order => "created_at DESC")
+		@options = {}
+	end
+	def list 
+		@title = "Recent Snippets"
+		@snippets = Snippet.all(:order => "created_at DESC")
+		@options = {}
+		render :action => :index
+	end
+	def mine	
+		@title = "My Snippets"	
+		@snippets = @user.snippets
+		@options = {:noauthor => true}
+		render :action => :index
+	end
+	def show
+		@snippet = Snippet.find(params[:id])
+	end
+	def new
+		@snippet = Snippet.new
+		@points = Point.find(:all)
+	end
+	def create
+		@snippet = Snippet.new(params[:snippet])
+		if @snippet.save
+			redirect_to :action => 'list'
+		else
+			@points = Point.find(:all)
+			render :action => 'new'
+		end
+	end
+	def edit
+		@snippet = Snippet.find(params[:id])
+		@points = Point.find(:all)
+	end
+	def update
+		@snippet = Snippet.find(params[:id])
+		if @snippet.update_attributes(params[:snippet])
+			redirect_to :action => 'show', :id => @snippet
+		else
+			@points = Point.find(:all)
+			render :action => 'edit'
+		end
+	end
+	def delete
+		Snippet.find(params[:id]).destroy
+		redirect_to :action => 'list'
+	end
+	def show_points
+		@point = Points.find(params[:id])
+	end
+end

### 2008-07-23 rails_server/thinklink/app/controllers/sources_controller.rb

@@ -1,0 +1,85 @@
+class SourcesController < ApplicationController
+  # GET /sources
+  # GET /sources.xml
+  def index
+    @sources = Source.find(:all)
+
+    respond_to do |format|
+      format.html # index.html.erb
+      format.xml  { render :xml => @sources }
+    end
+  end
+
+  # GET /sources/1
+  # GET /sources/1.xml
+  def show
+    @source = Source.find(params[:id])
+
+    respond_to do |format|
+      format.html # show.html.erb
+      format.xml  { render :xml => @source }
+    end
+  end
+
+  # GET /sources/new
+  # GET /sources/new.xml
+  def new
+    @source = Source.new
+
+    respond_to do |format|
+      format.html # new.html.erb
+      format.xml  { render :xml => @source }
+    end
+  end
+
+  # GET /sources/1/edit
+  def edit
+    @source = Source.find(params[:id])
+  end
+
+  # POST /sources
+  # POST /sources.xml
+  def create
+    @source = Source.new(params[:source])
+
+    respond_to do |format|
+      if @source.save
+        flash[:notice] = 'Source was successfully created.'
+        format.html { redirect_to(@source) }
+        format.xml  { render :xml => @source, :status => :created, :location => @source }
+      else
+        format.html { render :action => "new" }
+        format.xml  { render :xml => @source.errors, :status => :unprocessable_entity }
+      end
+    end
+  end
+
+  # PUT /sources/1
+  # PUT /sources/1.xml
+  def update
+    @source = Source.find(params[:id])
+
+    respond_to do |format|
+      if @source.update_attributes(params[:source])
+        flash[:notice] = 'Source was successfully updated.'
+        format.html { redirect_to(@source) }
+        format.xml  { head :ok }
+      else
+        format.html { render :action => "edit" }
+        format.xml  { render :xml => @source.errors, :status => :unprocessable_entity }
+      end
+    end
+  end
+
+  # DELETE /sources/1
+  # DELETE /sources/1.xml
+  def destroy
+    @source = Source.find(params[:id])
+    @source.destroy
+
+    respond_to do |format|
+      format.html { redirect_to(sources_url) }
+      format.xml  { head :ok }
+    end
+  end
+end

### 2008-07-23 rails_server/thinklink/app/helpers/application_helper.rb

@@ -1,0 +1,64 @@
+# Methods added to this helper will be available to all templates in the application.
+module ApplicationHelper
+	def auth_correct?(email = cookies[:email], password = cookies[:password])
+  	@user = User.find_by_email(email)
+		if @user and @user.password == password
+			return true
+		else
+			return false
+		end
+	end
+	
+	def check_auth(email = cookies[:email], password = cookies[:password])
+		unless auth_correct?(email,password)
+			flash[:error] = 'You need to be logged in to do this'
+			redirect_to :controller => 'main', :action => 'login'
+		end
+	end
+	
+	def setup_auth
+		auth_correct? #will set up @user param
+	end
+	
+	def emit(obj,opts = {})
+		respond_to do |format|
+			format.html {}
+			format.xml { render :xml => obj.to_xml(opts)}
+			format.json { render :text => obj.to_json(opts)}
+			format.js {render :text => "tl_callback(" + obj.to_json(opts) + ")"}
+		end
+	end
+	
+	def trim_string (string,length=400)
+		if(string.length < length)
+			return string
+		else
+			return string[0,length] + "..."
+		end
+	end
+	
+	def trim_url url
+		matches = url.match(%r{http://([^/]*)});
+		if matches && matches[1]
+			return matches[1];
+		else
+			return url
+		end
+	end
+	
+	def render_points points
+		render :partial => 'main/itemlist', 
+					 :locals => {:itemlist => points, 
+					 		:options => {:noauthor => true}, 
+					 		:renderer => 'points/pointref'}, 
+					 	:layout => 'standard'
+	end
+	def render_snippets snippets
+		render :partial => 'main/itemlist', 
+					 :locals => {:itemlist => snippets, 
+					 		:options => {:noauthor => true}, 
+					 		:renderer => 'snippets/snippet'}, 
+				 	:layout => 'standard'
+	end
+
+end

### 2008-07-23 rails_server/thinklink/app/models/point.rb

@@ -1,0 +1,17 @@
+class Point < ActiveRecord::Base
+	has_many :snippets
+	belongs_to :creator, :class_name => :user
+	has_many :users, :through => :snippets, :uniq => true
+#	has_many :point_links_a, :class_name => 'PointLink', :source => 'point_a'
+#	has_many :point_links_b, :class_name => 'PointLink', :source => :point_b
+	
+	def point_links_a
+		return PointLink.find :all, :conditions => "point_a_id = #{self.id}"
+	end
+	def point_links_b
+		return PointLink.find :all, :conditions => "point_b_id = #{self.id}"
+	end
+
+	
+	validates_presence_of :txt
+end

### 2008-07-23 rails_server/thinklink/app/models/point_link.rb

@@ -1,0 +1,12 @@
+class PointLink < ActiveRecord::Base
+	belongs_to :point_a, :class_name => 'Point'
+	belongs_to :point_b, :class_name => 'Point'
+	
+#	def point_a 
+#		Point.find self.point_a_id
+#	end
+	
+#	def point_b
+#		Point.find self.point_b_id
+#	end
+end

### 2008-07-23 rails_server/thinklink/app/models/rating.rb

@@ -1,0 +1,4 @@
+class Rating < ActiveRecord::Base
+	belongs_to :point
+	belongs_to :snippet
+end

### 2008-07-23 rails_server/thinklink/app/models/source.rb

@@ -1,0 +1,6 @@
+class Source < ActiveRecord::Base
+	has_many :snippets
+
+	validates_length_of :name, :within => 1..30
+	validates_uniqueness_of :domain, :message => "already exists"
+end

### 2008-07-23 rails_server/thinklink/config/routes.rb

@@ -1,0 +1,51 @@
+ActionController::Routing::Routes.draw do |map|
+  map.resources :sources
+  map.resources :snippets, :collection => {:mine => :get, :list => :get}
+  map.resources :ratings
+  map.resources :users, :member => {:snippets => :get, :points => :get}
+  map.resources :points, :collection => {:list => :get, :search => :get, :mine => :get}, :member => {:snippets => :get}
+
+  # The priority is based upon order of creation: first created -> highest priority.
+
+  # Sample of regular route:
+  #   map.connect 'products/:id', :controller => 'catalog', :action => 'view'
+  # Keep in mind you can assign values other than :controller and :action
+
+  # Sample of named route:
+  #   map.purchase 'products/:id/purchase', :controller => 'catalog', :action => 'purchase'
+  # This route can be invoked with purchase_url(:id => product.id)
+
+  # Sample resource route (maps HTTP verbs to controller actions automatically):
+  #   map.resources :products
+
+  # Sample resource route with options:
+  #   map.resources :products, :member => { :short => :get, :toggle => :post }, :collection => { :sold => :get }
+
+  # Sample resource route with sub-resources:
+  #   map.resources :products, :has_many => [ :comments, :sales ], :has_one => :seller
+  
+  # Sample resource route with more complex sub-resources
+  #   map.resources :products do |products|
+  #     products.resources :comments
+  #     products.resources :sales, :collection => { :recent => :get }
+  #   end
+
+  # Sample resource route within a namespace:
+  #   map.namespace :admin do |admin|
+  #     # Directs /admin/products/* to Admin::ProductsController (app/controllers/admin/products_controller.rb)
+  #     admin.resources :products
+  #   end
+
+  # You can have the root of your site routed with map.root -- just remember to delete public/index.html.
+  map.root :controller => "news"
+
+  # See how all your routes lay out with "rake routes"
+
+  # Install the default routes as the lowest priority.
+  map.connect ':controller/:action/page/:page'
+  map.connect ':controller/:id/:action/page/:page'
+  map.connect ':controller/:action/:id'
+  map.connect ':controller/:action/:id.:format'
+  map.connect ':controller/:action.:format'
+  map.connect ':controller.:format'
+end

### 2008-07-23 rails_server/thinklink/db/migrate/20080716233037_create_users.rb

@@ -1,0 +1,15 @@
+class CreateUsers < ActiveRecord::Migration
+  def self.up
+    create_table :users do |t|
+			t.column :email, :string, :limit =>32, :null => false
+			t.column :password, :string, :limit =>32, :null => false
+			t.column :secret, :string, :limit => 32, :null => false
+			t.column :status, :string, :limit => 4, :null => false
+      t.timestamps
+    end
+  end
+
+  def self.down
+    drop_table :users
+  end
+end

### 2008-07-23 rails_server/thinklink/db/migrate/20080719024533_create_ratings.rb

@@ -1,0 +1,15 @@
+class CreateRatings < ActiveRecord::Migration
+  def self.up
+    create_table :ratings do |t|
+    	t.column :snippet_id, :integer
+    	t.column :point_id, :integer
+    	t.column :user_id, :integer
+    	t.column :rating, :integer
+      t.timestamps
+    end
+  end
+
+  def self.down
+    drop_table :ratings
+  end
+end

### 2008-07-23 rails_server/thinklink/test/functional/snippet_controller_test.rb

@@ -1,0 +1,8 @@
+require 'test_helper'
+
+class SnippetControllerTest < ActionController::TestCase
+  # Replace this with your real tests.
+  def test_truth
+    assert true
+  end
+end

### 2008-07-23 rails_server_fucked/thinklink/app/controllers/news_controller.rb

@@ -1,0 +1,17 @@
+class NewsController < ApplicationController
+
+	layout 'standard'
+
+	# TODO don't show points you have already seen
+	# Allow ordering by time, etc
+	# Bias according to friends
+	def index
+		emit(Snippet.all(:limit => 10))
+	end
+	
+	
+	
+	private
+	
+	
+end

### 2008-07-23 rails_server_fucked/thinklink/app/helpers/point_helper.rb

@@ -1,0 +1,2 @@
+module PointHelper
+end

### 2008-07-23 rails_server_fucked/thinklink/app/models/point.rb

@@ -1,0 +1,7 @@
+class Point < ActiveRecord::Base
+	has_many :snippets
+	belongs_to :creator, :class_name => :user
+	has_many :users, :through => :snippets, :uniq => true
+	
+	validates_presence_of :txt
+end

### 2008-07-23 rails_server_fucked/thinklink/config/environment.rb

@@ -1,0 +1,70 @@
+# Be sure to restart your server when you modify this file
+
+# Uncomment below to force Rails into production mode when
+# you don't control web/app server and can't set it the proper way
+# ENV['RAILS_ENV'] ||= 'production'
+
+# Specifies gem version of Rails to use when vendor/rails is not present
+RAILS_GEM_VERSION = '2.1.0' unless defined? RAILS_GEM_VERSION
+
+# Store source info for ruby-debug
+SCRIPT_LINES__ = {} if ENV['RAILS_ENV'] == 'development'
+
+# Bootstrap the Rails environment, frameworks, and default configuration
+require File.join(File.dirname(__FILE__), 'boot')
+
+Rails::Initializer.run do |config|
+  # Settings in config/environments/* take precedence over those specified here.
+  # Application configuration should go into files in config/initializers
+  # -- all .rb files in that directory are automatically loaded.
+  # See Rails::Configuration for more options.
+
+  # Skip frameworks you're not going to use. To use Rails without a database
+  # you must remove the Active Record framework.
+  # config.frameworks -= [ :active_record, :active_resource, :action_mailer ]
+
+  # Specify gems that this application depends on. 
+  # They can then be installed with "rake gems:install" on new installations.
+  # config.gem "bj"
+  # config.gem "hpricot", :version => '0.6', :source => "http://code.whytheluckystiff.net"
+  # config.gem "aws-s3", :lib => "aws/s3"
+
+  # Only load the plugins named here, in the order given. By default, all plugins 
+  # in vendor/plugins are loaded in alphabetical order.
+  # :all can be used as a placeholder for all plugins not explicitly named
+  # config.plugins = [ :exception_notification, :ssl_requirement, :all ]
+
+  # Add additional load paths for your own custom dirs
+  # config.load_paths += %W( #{RAILS_ROOT}/extras )
+
+  # Force all environments to use the same logger level
+  # (by default production uses :info, the others :debug)
+  # config.log_level = :debug
+
+  # Make Time.zone default to the specified zone, and make Active Record store time values
+  # in the database in UTC, and return them converted to the specified local zone.
+  # Run "rake -D time" for a list of tasks for finding time zone names. Uncomment to use default local time.
+  config.time_zone = 'UTC'
+
+  # Your secret key for verifying cookie session data integrity.
+  # If you change this key, all old sessions will become invalid!
+  # Make sure the secret is at least 30 characters and all random, 
[…]

### 2008-07-23 rails_server_fucked/thinklink/config/routes.rb

@@ -1,0 +1,50 @@
+ActionController::Routing::Routes.draw do |map|
+  map.resources :sources
+  map.resources :snippets, :collection => {:mine => :get, :list => :get}
+  map.resources :ratings
+  map.resources :users, :member => {:snippets => :get}
+  map.resources :points, :collection => {:list => :get}, :member => {:snippets => :get}
+
+  # The priority is based upon order of creation: first created -> highest priority.
+
+  # Sample of regular route:
+  #   map.connect 'products/:id', :controller => 'catalog', :action => 'view'
+  # Keep in mind you can assign values other than :controller and :action
+
+  # Sample of named route:
+  #   map.purchase 'products/:id/purchase', :controller => 'catalog', :action => 'purchase'
+  # This route can be invoked with purchase_url(:id => product.id)
+
+  # Sample resource route (maps HTTP verbs to controller actions automatically):
+  #   map.resources :products
+
+  # Sample resource route with options:
+  #   map.resources :products, :member => { :short => :get, :toggle => :post }, :collection => { :sold => :get }
+
+  # Sample resource route with sub-resources:
+  #   map.resources :products, :has_many => [ :comments, :sales ], :has_one => :seller
+  
+  # Sample resource route with more complex sub-resources
+  #   map.resources :products do |products|
+  #     products.resources :comments
+  #     products.resources :sales, :collection => { :recent => :get }
+  #   end
+
+  # Sample resource route within a namespace:
+  #   map.namespace :admin do |admin|
+  #     # Directs /admin/products/* to Admin::ProductsController (app/controllers/admin/products_controller.rb)
+  #     admin.resources :products
+  #   end
+
+  # You can have the root of your site routed with map.root -- just remember to delete public/index.html.
+  map.root :controller => "news"
+
+  # See how all your routes lay out with "rake routes"
+
+  # Install the default routes as the lowest priority.
+  map.connect ':controller/:action/page/:page'
+  map.connect ':controller/:action/:id'
+  map.connect ':controller/:action/:id.:format'
+  map.connect ':controller/:action.:format'
+  map.connect ':controller.:format'
+end

### 2008-07-23 rails_server_fucked/thinklink/db/migrate/20080716232724_create_snippets.rb

@@ -1,0 +1,17 @@
+class CreateSnippets < ActiveRecord::Migration
+  def self.up
+    create_table :snippets do |t|
+			t.column :txt, :string, :limit => 1024, :null => false
+			t.column :user_id, :integer
+			t.column :point_id, :integer
+			t.column :source_id, :integer
+			t.column :pagetitle, :string, :limit => 128, :null => false
+			t.column :url, :string, :limit => 2048, :null => false
+      t.timestamps
+    end
+  end
+
+  def self.down
+    drop_table :snippets
+  end
+end

### 2008-07-23 rails_server_fucked/thinklink/db/schema.rb

@@ -1,0 +1,58 @@
+# This file is auto-generated from the current state of the database. Instead of editing this file, 
+# please use the migrations feature of Active Record to incrementally modify your database, and
+# then regenerate this schema definition.
+#
+# Note that this schema.rb definition is the authoritative source for your database schema. If you need
+# to create the application database on another system, you should be using db:schema:load, not running
+# all the migrations from scratch. The latter is a flawed and unsustainable approach (the more migrations
+# you'll amass, the slower it'll run and the greater likelihood for issues).
+#
+# It's strongly recommended to check this file into your version control system.
+
+ActiveRecord::Schema.define(:version => 20080719024533) do
+
+  create_table "points", :force => true do |t|
+    t.integer  "user_id",    :limit => 11
+    t.string   "txt",        :limit => 128, :default => "", :null => false
+    t.datetime "created_at"
+    t.datetime "updated_at"
+  end
+
+  create_table "ratings", :force => true do |t|
+    t.integer  "snippet_id", :limit => 11
+    t.integer  "point_id",   :limit => 11
+    t.integer  "user_id",    :limit => 11
+    t.integer  "rating",     :limit => 11
+    t.datetime "created_at"
+    t.datetime "updated_at"
+  end
+
+  create_table "snippets", :force => true do |t|
+    t.string   "txt",        :limit => 1024, :default => "", :null => false
+    t.integer  "user_id",    :limit => 11
+    t.integer  "point_id",   :limit => 11
+    t.integer  "source_id",  :limit => 11
+    t.string   "pagetitle",  :limit => 128,  :default => "", :null => false
+    t.string   "url",        :limit => 2048, :default => "", :null => false
+    t.datetime "created_at"
+    t.datetime "updated_at"
+  end
+
+  create_table "sources", :force => true do |t|
+    t.string   "name"
+    t.string   "domain"
+    t.string   "titleexp"
+    t.datetime "created_at"
+    t.datetime "updated_at"
+  end
+
+  create_table "users", :force => true do |t|
+    t.string   "email",      :limit => 32, :default => "", :null => false
+    t.string   "password",   :limit => 32, :default => "", :null => false
+    t.string   "secret",     :limit => 32, :default => "", :null => false
+    t.string   "status",     :limit => 4,  :default => "", :null => false
+    t.datetime "created_at"
+    t.datetime "updated_at"
+  end
+
+end

### 2008-07-23 rails_server_fucked/thinklink/test/functional/sources_controller_test.rb

@@ -1,0 +1,45 @@
+require 'test_helper'
+
+class SourcesControllerTest < ActionController::TestCase
+  def test_should_get_index
+    get :index
+    assert_response :success
+    assert_not_nil assigns(:sources)
+  end
+
+  def test_should_get_new
+    get :new
+    assert_response :success
+  end
+
+  def test_should_create_source
+    assert_difference('Source.count') do
+      post :create, :source => { }
+    end
+
+    assert_redirected_to source_path(assigns(:source))
+  end
+
+  def test_should_show_source
+    get :show, :id => sources(:one).id
+    assert_response :success
+  end
+
+  def test_should_get_edit
+    get :edit, :id => sources(:one).id
+    assert_response :success
+  end
+
+  def test_should_update_source
+    put :update, :id => sources(:one).id, :source => { }
+    assert_redirected_to source_path(assigns(:source))
+  end
+
+  def test_should_destroy_source
+    assert_difference('Source.count', -1) do
+      delete :destroy, :id => sources(:one).id
+    end
+
+    assert_redirected_to sources_path
+  end
+end

### 2008-07-23 scads_server/app/controllers/example_controller.rb

@@ -1,0 +1,27 @@
+class ExampleController < ApplicationController
+  def index
+    @things = Thing.find_by_name(Storage::Key.new(Storage::WildcardCondition.new))
+  end
+  
+  def new
+    @thing = Thing.new
+    render :action => 'edit'
+  end
+  
+  def edit
+    @thing = Thing.find(params[:id])
+  end
+  
+  def update
+    if params[:id].nil?
+      @thing = Thing.new
+    else
+      @thing = Thing.find(params[:id])
+    end
+    
+    @thing[:name] = params[:thing_name]
+    @thing.save
+    
+    redirect_to :action => 'index'
+  end
+end

### 2008-07-23 scads_server/example/app/models/sub_thing.rb

@@ -1,0 +1,2 @@
+class SubThing < Scads::Entity::Base
+end

### 2008-07-23 scads_server/example/app/models/thing.rb

@@ -1,0 +1,4 @@
+class Thing < Scads::Entity::Base
+  searchable_by :name
+  has_many :sub_things
+end

### 2008-07-23 scads_server/example/config/environment.rb

@@ -1,0 +1,59 @@
+# Be sure to restart your server when you modify this file
+
+# Uncomment below to force Rails into production mode when
+# you don't control web/app server and can't set it the proper way
+# ENV['RAILS_ENV'] ||= 'production'
+
+# Specifies gem version of Rails to use when vendor/rails is not present
+RAILS_GEM_VERSION = '2.0.2' unless defined? RAILS_GEM_VERSION
+
+# Bootstrap the Rails environment, frameworks, and default configuration
+require File.join(File.dirname(__FILE__), 'boot')
+
+Rails::Initializer.run do |config|
+  # Settings in config/environments/* take precedence over those specified here.
+  # Application configuration should go into files in config/initializers
+  # -- all .rb files in that directory are automatically loaded.
+  # See Rails::Configuration for more options.
+
+  # Skip frameworks you're not going to use (only works if using vendor/rails).
+  # To use Rails without a database, you must remove the Active Record framework
+  # config.frameworks -= [ :active_record, :active_resource, :action_mailer ]
+
+  # Only load the plugins named here, in the order given. By default, all plugins 
+  # in vendor/plugins are loaded in alphabetical order.
+  # :all can be used as a placeholder for all plugins not explicitly named
+  # config.plugins = [ :exception_notification, :ssl_requirement, :all ]
+
+  # Add additional load paths for your own custom dirs
+  # config.load_paths += %W( #{RAILS_ROOT}/extras )
+
+  # Force all environments to use the same logger level
+  # (by default production uses :info, the others :debug)
+  # config.log_level = :debug
+
+  # Your secret key for verifying cookie session data integrity.
+  # If you change this key, all old sessions will become invalid!
+  # Make sure the secret is at least 30 characters and all random, 
+  # no regular words or you'll be exposed to dictionary attacks.
+  config.action_controller.session = {
+    :session_key => '_example_session',
+    :secret      => 'fcbe76ff6a6b70aa02dcd81300ebcc746d0262d111f6f813360de400a7805e92f1a66939fc74d47a93806b45760639486b67292210a955306b19206a710c432d'
+  }
+
+  # Use the database for sessions instead of the cookie-based default,
+  # which shouldn't be used to store highly confidential information
+  # (create the session table with 'rake db:sessions:create')
+  # config.action_controller.session_store = :active_record_store
+
+  # Use SQL instead of Active Record's schema dumper when creating the test database.
+  # This is necessary if your schema can't be completely dumped by the schema dumper,
[…]

### 2008-07-23 scads_server/example/config/initializers/scads.rb

@@ -1,0 +1,18 @@
+[Thing, SubThing]
+
+SCADS_SERVER.registerType(:Thing)
+SCADS_SERVER.registerType(:SubThing)
+
+t = Thing.new
+t[:name] = "thing1"
+t.save
+
+s1 = SubThing.new
+s1[:name] = "sub thing 1"
+s1[:thing] = t
+s1.save
+
+s2 = SubThing.new
+s2[:name] = "sub thing 2"
+s2[:thing] = t
+s2.save

### 2008-07-23 scads_server/example/db/schema.rb

@@ -1,0 +1,23 @@
+# This file is auto-generated from the current state of the database. Instead of editing this file, 
+# please use the migrations feature of ActiveRecord to incrementally modify your database, and
+# then regenerate this schema definition.
+#
+# Note that this schema.rb definition is the authoritative source for your database schema. If you need
+# to create the application database on another system, you should be using db:schema:load, not running
+# all the migrations from scratch. The latter is a flawed and unsustainable approach (the more migrations
+# you'll amass, the slower it'll run and the greater likelihood for issues).
+#
+# It's strongly recommended to check this file into your version control system.
+
+ActiveRecord::Schema.define(:version => 2) do
+
+  create_table "sub_things", :force => true do |t|
+    t.string  "name"
+    t.integer "thing_id"
+  end
+
+  create_table "things", :force => true do |t|
+    t.string "name"
+  end
+
+end

### 2008-07-29 papers/web_of_ideas/web_of_ideas.tex
Started adding ideas to the paper. Fixed another tl_url bug.

\documentclass{sig-alt-release2}
\usepackage{graphicx}
\usepackage{url}
\usepackage{textcomp}
\usepackage{times}
\usepackage{color}

\newcommand{\todo}[1]{}
% \newcommand{\todo}[1]{\footnote{{\bf TODO:} #1}}
\newcommand{\Intel}{Intel\textsuperscript{\textregistered}}

\newcommand{\idea}[1]{{\color{blue} IDEA: #1}\\}
\newcommand{\studyresult}[1]{{\color{red} STUDY RESULT?: #1}\\}

\begin{document}
%
\title{Connecting Documents to Ideas}

\numberofauthors{3}

\author{
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \email{trush@berkeley.edu}
\alignauthor Rob Ennals\\
       \affaddr{Intel Research}\\
       \affaddr{2150 Shattuck Avenue}\\
       \affaddr{Penthouse Suite}\\
       \affaddr{Berkeley, CA 94704, USA}\\
       \email{robert.ennals@intel.com}
}

\sloppy

\maketitle

\begin{abstract}

Much of the information contained on the web consists of opinions, arguments, blogs, articles, and other such unstructured natural language text. Each such document contains one or more statements or ideas that might be of interest to readers.

We propose a new approach to finding, organizing, and sharing ideas contained in web pages. In this approach, a user marks points of interest

\end{abstract}

\section{Introduction}

\idea{Much interesting data on the web is unstructured text}

\idea{These documents consist of ideas}

\idea{Think Link connects documents to the ideas they express}

\idea{This paper is itself marked up in think link - with URL}

\idea{If the ideas in a document are known then this allows interesting queries}

\section{Why People Annotate}

\idea{People already annotate documents, in the form of blogs, comments etc}

\idea{People already organize data, using text files, Google Notepad, OneNote, etc}

\idea{People already share information, by mailing links, posting stories on facebook, sending messages on twitter, etc}

\idea{People already want to see what each other are interested in - using Facebook, Twitter, Friendfeed, etc}

\studyresult{Our users used these tools}

\studyresult{Users want to put forward their opinions}

\studyresult{People want to be seen as a source of useful information}

\studyresult{People want to organize the information they find}

\studyresult{Our users said they would use our tool}

\studyresult{The best way to find answers is social - by learning from friends who understand the topic}

\section{Organizing Knowledge}

\idea{Like Wikipedia without the articles}

\idea{Organize ideas with Points, snippets, and topics}

\idea{A point can support or oppose another point}

\idea{A point can be exactly the same or exactly opposite}

\idea{Important to have wiki features to keep things in check}

\studyresult{People found it useful to organize ideas}

\studyresult{People found the topic approach worked well}

\studyresult{People were able to easily find and reuse existing points and topics}

\section{Using this Knowledge}

\idea{Show me the points that other people disagree with}

\idea{Show me the points that other people found interesting}

\idea{Show me the points that my friends found interesting}

\idea{Show me the articles that make interesting points I haven't heard before}

\idea{Show me when new snippets appear on points I'm interested in}

\idea{Show me when new points appear on topics I'm interested in}

\studyresult{People liked to be able to monitor interesting new ideas on topics they were interested in}

\studyresult{People liked the other features too}

\section{Creating Knowledge}

\section{Sharing Knowledge}

Why do users g

\section{Using Knowledge}

\section{Querying Data}

\section{Related Work}

\subsection{Web Annotation Systems}

\subsection{Semantic Linking}

\subsection{User Contributed Links}

Memex allowed users to describe their own paths between pages, rather than requiring the page authors to modify them.

Everything2 creates soft-links between documents based on the browsing patterns of users.

ENQUIRE contains bi-directional links that show who links to a document. TrackBack does the same.

\subsection{Automated Reasoning}

\subsection{Argumentation Graphs}

\section{Evaluation}

\section{Conclusions}

\end{document}

### 2008-08-25 papers/web_of_ideas/web_of_ideas.tex
screenshots and user study work in paper

@@
 \section{Introduction}
+1p:  
+overview, 
+motivation,
+list of contributions,
+(briefly) describe application,
+(briefly) describe user studies,
+describe results,
 
-\idea{Much interesting data on the web is unstructured text}
+% \idea{Much interesting data on the web is unstructured text}
+% 
+% \idea{These documents consist of ideas}
+% 
+% \idea{Think Link connects documents to the ideas they express}
+% 
+% %\idea{This paper is itself marked up in think link - with URL}
+% 
+% \idea{If the ideas in a document are known then this allows interesting queries}
 
-\idea{These documents consist of ideas}
+% Motivation for tool
 
-\idea{Think Link connects documents to the ideas they express}
+% What thinklink allows people to do
 
-\idea{This paper is itself marked up in think link - with URL}
+% Why thinklink is needed
+\section{Motivation?}
+1-2pp: 
+how do people currently organize, interact, share with web content; 
+Thinklink data structures; 
+what can people now do with Thinklink
 
-\idea{If the ideas in a document are known then this allows interesting queries}
-
-\section{Why People Annotate}
+\subsection{Why People Annotate}
 
@@
 
-\studyresult{The best way to find answers is social - by learning from friends who understand the topic}
+%\studyresult{The best way to find answers is social - by learning from friends who understand the topic}
 
-\section{Organizing Knowledge}
+\subsection{Organizing Knowledge}
 
@@
 
-\studyresult{People found the topic approach worked well}
+%\studyresult{People found the topic approach worked well}
 
-\studyresult{People were able to easily find and reuse existing points and topics}
+%\studyresult{People were able to easily find and reuse existing points and topics}
 
-\section{Using this Knowledge}
+\subsection{Using this Knowledge}
 
@@
 
+% future queries want to support
+
 \idea{Show me the articles that make interesting points I haven't heard before}
@@
 
-\studyresult{People liked to be able to monitor interesting new ideas on topics they were interested in}
+%\studyresult{People liked to be able to monitor interesting new ideas on topics they were interested in}
 
@@
 
-\section{Creating Knowledge}
+\section{Design}
+2pp: describe how the application works and show some screenshots; discuss some implementation decisions
+\subsection{Features}
+descriptions and screenshots: margin, snippet creation, relationship creation, web UI, point browser
+\begin{figure}[ht]
+	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
+	\caption{Snippet creation dialog}
+	\label{snippetdialog}
+\end{figure}
 
-\section{Sharing Knowledge}
+\begin{figure}[ht]
+	\includegraphics[scale=0.3]{../screenshots/topicpage_sm.jpg}
+	\caption{Example topic page}
+	\label{topicpage}
+\end{figure}
 
-Why do users g
+\subsection{Implementation Decisions}
 
-\section{Using Knowledge}
+\idea{Wiki model not appropriate for points since want to manipulate several points at once}
+\idea{Need to visualize relationships in web of ideas}
 
-\section{Querying Data}
+% \section{Creating Knowledge}
+% 
+% \section{Sharing Knowledge}
+% 
+% Why do users g
+% 
+% \section{Using Knowledge}
+% 
+% \section{Querying Data}
+
+\section{User Studies}
+1.5pp: recruitment, environment, tasks, observations, smaller study
+
+\subsection{Recruitment}
+Our user study participants were selected from a pool of respondents to a Craigslist posting for people who use the internet as one of their primary sources of information, regularly gather and share this information, and are interested in a new application to facilitate that process.
+We chose participants based on their responses to the following questions:
+\begin{enumerate}
+	\item What topics or types of information do you usually look for on the internet?
+	\item How do usually go about finding information? (e.g. google, digg, friends, etc)
+	\item How do you organize the information you find? (e.g. text file, paper, wiki, etc)
+	\item How do you share information with others? (e.g. blog posts, comments, email, facebook, etc)
+\end{enumerate}
+We preferred individuals who search the internet for research and reading news rather than online shopping, as well as those interested in social and collaborative web activities like social networking web sites.
+We were also interested in those who seemed to express a need for our application: people who copy-and-paste text from web pages into word processing documents, or who regularly email web page addresses to friends.
+Twelve people were selected to participate in this study.
+
+\subsection{Study Environment}
+Each study session lasted between thirty to forty-five minutes, with the participant sitting at a desktop computer with the Firefox browser running the application plugin.
+The session was a Think-Aloud study in which the participant verbally describes his/her thoughts throughout the duration of the study.
+A video camera captured the audio/video and was focused on the monitor screen.
+Before the session began, we briefly demonstrated the features of the application: how to (1) select snippets, (2) write a snippet topic and point, (3) relate points, (4) show/hide the margin, and (5) browse recent activity.
+
+\subsection{Study Tasks}
+The study consisted of two tasks to collect snippets, each lasting ten to fifteen minutes.
+During both tasks, we asked participants to browse the web as they normally would.
+In the first task, the participant browses the web about a topic or issue of their choice from the domain of politics.
+The collection of snippets should help the participant either argue or form an opinion/perspective about the topic, and should be thought of being used to help him/her explain or discuss the topic with a friend.
+We constrained the first task to politics to increase the likelihood that the study participants would encounter similar issues and news stories.
+
+For the second task, the participant was allowed to browse for any topic of their choosing.
+While the likelihood of topic overlap across participants was much lower, we were able to observe their behavior when searching for information in which each person had genuine interest.
+
+At the conclusion of the session, we asked the participant if the application is something that would be likely to use, and for what purposes they would find it most useful.
+Any confusing features or experiences were also noted.
+
+\subsection{Observations and Discussion}
+% observed good and bad things
+% good things validate the application's usefulness and applicability
+% snippet selection super easy
+% organization part a little lacking
+% bad things we have ideas how to fix: UI redesign and smaller second study
+% not as much social stuff going on, but limited stuff in DB for overlap to happen (more social stuff towards end of study)
+
+{\it Note:} The first four study participants used a version of the web interface in which point relationships were constructed by navigating to one point page, searching for or typing the text of another point, and then expressing a directional relationship via a drop-down menu.
+We saw that participants found this process cumbersome and were less inclined to do it.
+Three of the four noted their confusion by the directional terms {\it supports} versus {\it is supported by}, and expressed a need for a more visual technique for constructing relationships.
+We modified the interface to allow users to drag and drop points on top of one another, with just the choice of {\it supports} and {\it opposes}.
+Half of the four participants were also confused by the Gmail-like labels alongside listed points that specified the topics each point belongs to.
+The interface was modified to show topics listed with their related points beneath them.
+The remainder of the study used the modified interface.
+
+%hopefully more social uses when have more stuff in database
+
+\subsubsection{Validating Observations?}
+In general, the user study demonstrated that our application successfully allows people to associate portions of web content with ideas, and to organize and share those ideas.
+All the study participants were able to create new snippets, and only a couple ($2/12$) had initial difficulty in correctly summarizing snippet text into a point.
+Most participants ($10/12$) were interested in viewing the margin as they were creating new snippets.
+These observations demonstrate that snippet creation is easy for most users.
+
+Many ($7/12$) participants also expressed the desire to organize snippets and points during their session.
+Of these seven, we noticed that four were alternating between creating snippets from new articles and organizing points in their {\it Recent Activity}: with each new snippet, users were creating relationships between points.
+When browsing web content about a particular topic or issue, most participants ($10/12$) either reused a topic that they created during their session or that someone else had created previously.
+Half of those ten used a topic that they {\it hadn't} created, demonstrating the ease of collaboration in our application.
+Both these organizational activities support connections inside the web of ideas.
+While the level of social activity was undoubtedly limited by the relatively small number of points (about $400$), three of the six people who browsed points in the main web interface looked at points created by other users.
+Two of the later study participants viewed someone else's point and either read the snippet text or viewed the originating document.
+As the number of points and topics increases, we expect to see more social behavior like this.
+
+% easy to create snippets and view margin
+% participants expressed desire to organize
+% saw social activity and browsing
+% (see more in usage types)
+% not as much social stuff going on, but limited stuff in DB for overlap to happen (more social stuff towards end of study)
+
+\subsubsection{Suggested Usage}
+Many of the study participants who said they would our application suggested uses that match those described in our motivation, validating our prescribed use cases.
+We identified the following use types, based on participant responses.
+Note that these many people suggested multiple use types.
+
+\textbf{Blogging and writing:} Snippet collections are useful when gathering evidence and supporting material for a blog entry, report, or any kind of written composition.
+This use case necessitates the ability to organize, order, and rearrange snippets to best tell a story, generate a persuasive argument, or facilitate forming an opinion.
+
+\textbf{Self-Bookmarking:} Creating snippets can be a means of bookmarking web page content that a user will return to for his/her own needs.
+These bookmarks are more specific than the web address of the page itself, and was suggested by users who currently find themselves cutting and pasting web content into a word processing file.
+This use case is more for retaining factual information than constructing an argument, although the information could also be used for the writing usage type.
+
+\textbf{Social:} Sharing snippets with friends or targeted interest groups allows users to see what web content is interesting to people they follow.
+This use case is applicable both to those who wish to collaboratively generate a collection of information and to those who like sharing and browsing information from friends.
+
+% Not for everyone! 3/12 people used it "incorrectly"
+Several of the study participants suggested specific use cases that mirror our initial motivation for the application.
+One example was a user who would use snippets to as supporting evidence for asserting the incorrectness of someone else's claim on a web forum, as simple comments are not as effective.
+Our application, however, is not for everyone.
+Three of the twelve user study participants used (or wanted to use) our application ``incorrectly,'' e.g.
+to compare airline flight prices.
+
+\subsubsection{User Interface Redesign}
+The first user study demonstrated a few flaws in the application's user interface. These problems can be generalized as:
+\begin{itemize}
+	\item \textbf{People need to easily visualize the the hierarchy of points, topics, and relationships.} A significant portion of the participants ($5/12$) explicitly expressed confusion about not being able to view the entire hierarchy of topics and points, and felt lost when looking at the individual point or topic pages.
+In this view, each point and topic is visually separated from its related points and topics, and thus users did not understand the significance of these individual pages.
+Viewing related points as lists of {\it child} and {\it parent} points was confusing to three of the eight people who used the second version of the UI.
+This ``flattened'' perspective also makes it difficult to relate several points to another.
+Most of the users who linked points together ($5/7$) did not recognize the need to first create an intermediate point and then relate other points to that new point.
+An easier model for grouping and associating objects together is necessary.
+	\item \textbf{People need better organization capabilities at snippet creation time.}
+\end{itemize}
+
+% motivation for file save-as in snippet dialog
+\idea{people want to do most of their organization during the snippet creation process}
+\idea{people want to be able to create subtopics right away}
+\idea{specific topics used by different users are more likely not to be recreated}
+
+Our solution to these problems was to redesign the user interface to resemble the traditional file browser.
+The left-hand side shows the expandable/collapsable hierarchy and shortcut paths, while the right-hand side shows a content preview of the selected item from the left.
+For example, when a point is selected, the preview shows its snippets and related points.
+Snippet creation will resemble a \texttt{save as...} dialog where users can easily traverse the topic/point hierarchy, and create new topics inside existing ones as deemed necessary.
+This solution was implemented and used in a smaller user study. See section \ref{secondstudy}.
+
+\subsubsection{Second User Study}
+\label{secondstudy}
+There were six study participants who used the redesigned web interface.
+\studyresult{we solved organization difficulties with this redesign}
 
 \section{Related Work}
+1p
 
@@
 
-\section{Evaluation}
+%\section{Evaluation}
+
+\section{Future Work}
+1p: social queries, NLP stuff
 
 \section{Conclusions}
+$1/2$p
 

### 2008-08-27 papers/web_of_ideas/web_of_ideas.tex

@@
 An easier model for grouping and associating objects together is necessary.
-	\item \textbf{People need better organization capabilities at snippet creation time.}
+	\item \textbf{People need better organization capabilities at snippet creation time.} Only a few ($3/12$) users went back to their {\it Recent Activity} to create additional topics when organizing, which suggests that a majority of users prefer to place snippets within topics when they are first created.
+However, if users are only allowed to assign a snippet to one topic without context of a topic hierarchy, they may create a very specific topic that is unlikely to be used by another person.
+We observed this behavior with two participants who both created snippets regarding a politician's controversial affair, but whose snippets did not belong to related topics.
+Several participants ($4/12$) remarked that they were unsure how broad a topic should be.
+By allowing users to create and traverse the topic hierarchy, they would be able to more easily organize and specify new topics when creating a snippet.
 \end{itemize}
-
-% motivation for file save-as in snippet dialog
-\idea{people want to do most of their organization during the snippet creation process}
-\idea{people want to be able to create subtopics right away}
-\idea{specific topics used by different users are more likely not to be recreated}
 

### 2008-09-13 papers/web_of_ideas/web_of_ideas.tex
Minor paper changes. Largely screenshots

@@
-\documentclass{sig-alt-release2}
-\usepackage{graphicx}
+\documentclass{chi2009}
+\usepackage{times}
 \usepackage{url}
-\usepackage{textcomp}
-\usepackage{times}
+\usepackage{graphics}
 \usepackage{color}
+\usepackage[pdftex]{hyperref}
+\hypersetup{%
+pdftitle={Browsing the Web of Factual Claims},
+pdfauthor={Beth Trushkowski and Rob Ennals},
+pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
+bookmarksnumbered,
+pdfstartview={FitH},
+colorlinks,
+citecolor=black,
+filecolor=black,
+linkcolor=black,
+urlcolor=black,
+breaklinks=true,
+}
 
@@
 
+\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy
+
 \begin{document}
+% to make various LaTeX processors do the right thing with page size
+\special{papersize=8.5in,11in}
+\setlength{\paperheight}{11in}
+\setlength{\paperwidth}{8.5in}
+\setlength{\pdfpageheight}{\paperheight}
+\setlength{\pdfpagewidth}{\paperwidth}
 %
-\title{Connecting Documents to Ideas}
+\toappear{Submitted for review to CHI 2009.}
 
-\numberofauthors{3}
+\title{Browsing the Web of Factual Claims}
+
+\numberofauthors{2}
 
@@
 
-Much of the information contained on the web consists of opinions, arguments, blogs, articles, and other such unstructured natural language text.
-Each such document contains one or more statements or ideas that might be of interest to readers.
-
-We propose a new approach to finding, organizing, and sharing ideas contained in web pages. In this approach, a user marks points of interest
+Traditional web browsing consists of looking at pages and following links between pages; however when a user browses the web it is often not the pages themselves that they are looking for but the factual claims contained within those documents.
+A page may contain claims that are contradicted by other pages, or contain one interesting new claim, hidden in a sea of claims that the user has already read.
+A user must thus invest significant effort extracting the claims that are accurate and interesting from the pages that they look at.
+We present Think Link, a tool that links pages to the factual claims that they make, and allows users to browse the web of factual claims, rather than the web of pages.
 
 \end{abstract}
+
+\keywords{CSCW, sensemaking, web, browsers, collaboration, mind mapping}
+
+\category{H.5.2}{Information Interfaces and Presentation}{User Interfaces}[Graphical User Interfaces]
+
+\begin{figure}[ht]
+	\includegraphics[width=8.5cm]{../screenshots/redhighlight.png}
+	\caption{Browsing interface, with a contentious claim highlighted}
+	\label{redhighlight}
+\end{figure}
+
+\begin{figure}[ht]
+	\includegraphics[width=8.5cm]{../screenshots/sidebar.png}
+	\caption{Browsing interface, with the sidebar opened}
+	\label{sidebar}
+\end{figure}
+
+\begin{figure}[ht]
+	\includegraphics[width=8.5cm]{../screenshots/claim_popup.png}
+	\caption{The ``Investigate Claim'' window pops up when one clicks on a claim}
+	\label{redhighlight}
+\end{figure}
 
@@
 % Why thinklink is needed
-\section{Motivation?}
-1-2pp: 
-how do people currently organize, interact, share with web content; 
-Thinklink data structures; 
-what can people now do with Thinklink
-
-\subsection{Why People Annotate}
 
@@
 %\studyresult{The best way to find answers is social - by learning from friends who understand the topic}
+
+\section{Motivation?}
+1-2pp: 
+how do people currently organize, interact, share with web content; 
+Thinklink data structures; 
+what can people now do with Thinklink
+
+\subsection{Why People Annotate}
 
@@
 
-\section{Design}
-2pp: describe how the application works and show some screenshots; discuss some implementation decisions
-\subsection{Features}
-descriptions and screenshots: margin, snippet creation, relationship creation, web UI, point browser
-\begin{figure}[ht]
-	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
-	\caption{Snippet creation dialog}
-	\label{snippetdialog}
-\end{figure}
+\section{Related Work}
 
-\begin{figure}[ht]
-	\includegraphics[scale=0.3]{../screenshots/topicpage_sm.jpg}
-	\caption{Example topic page}
-	\label{topicpage}
-\end{figure}
+\subsection{Web Annotation Systems}
 
-\subsection{Implementation Decisions}
+Diigo lets you save, import, tag, highlight, mark up and share Web pages
+	select content on webpage
+	share bookmarked content; bookmark url and see what people have tagged on that page
+	search over collection of selected content
+	tag selected content; social tagging
+	see friends activity; more social behavior than necessary (eg. msging)
+	meet people ``like'' me?
+Stickis
+Fleck
+Shiftspace
+SharedCopy
+JKN
+MyStickies
+DrawHere
 
-\idea{Wiki model not appropriate for points since want to manipulate several points at once}
-\idea{Need to visualize relationships in web of ideas}
+- UIs for highlighting
+- wikipedia highlighting not trustworthy stuff
 
-% \section{Creating Knowledge}
-% 
-% \section{Sharing Knowledge}
-% 
-% Why do users g
-% 
-% \section{Using Knowledge}
-% 
-% \section{Querying Data}
+\subsection{Web Clippings}
 
-\section{User Studies}
-1.5pp: recruitment, environment, tasks, observations, smaller study
+Google Notebook
+Trailfire
+
+\subsection{Semantic Linking}
+
+\subsection{Social Bookmarking}
+
+Shadows
+
+\subsection{User Contributed Links}
+
+Memex allowed users to describe their own paths between pages, rather than requiring the page authors to modify them.
+
+Everything2 creates soft-links between documents based on the browsing patterns of users.
+
+ENQUIRE contains bi-directional links that show who links to a document. TrackBack does the same.
+
+\subsection{Automated Reasoning}
+
+Case-Based reasoning
+Sensemaking
+
+\subsection{Argumentation Graphs}
+Argumentation graphs express positions and arguments in a formal graph model as nodes and edges, respectively, and are typically used to make a decision or draw a conclusion about some issue.
+One example implementation is the {\it Zeno} argumentation framework [\idea{cite}], designed for collaborative use in mediation systems to debate the quality of alternative solutions for a problem.
+In their object model of argumentation elements, based on Rittel's IBIS model [\idea{cite}], example nodes include pro/con arguments, positions, preferences, comments, and decisions.
+Importantly, arguments are connected via {\it consequent} and {\it antecedent} edges, which are used to inform {\it choices}.
+The decision-making power of the argumentation graph follows from the traversal of argument relationships to enhance the depth and breadth of understanding about an issue.
+Our application similarly links claims as {\it supporting} and {\it opposing} other claims to allow users to develop a cohesive understanding of arguments.
+
+Traditional argumentation graphs are designed to solve a specific, isolated issue.
+Our application supports an ever-expanding set of topics, and arguments can form links between multiple topics.
+Users can consult the web of ideas directly to form an opinion about a particular issue, but they can also browse for new issues to explore.
+Opinions or decisions in our model don't have to be static: as the topic is expanded with more supporting and opposing evidence, users may alter previous viewpoints.
+Another advantage of our model is that the ability to explore claims' source-document evidence is built right into the navigation.
+Looking at an argument shows both its related argument as well as its supporting {\it snippets}, allowing the user to explore the evidence for himself.
+
+\section{Observations Informing Design}
 
@@
 
+\section{Interaction Techniques}
+
+\subsection{Features}
+descriptions and screenshots: margin, snippet creation, relationship creation, web UI, point browser
+\begin{figure}[ht]
+	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
+	\caption{Snippet creation dialog}
+	\label{snippetdialog}
+\end{figure}
+
+\begin{figure}[ht]
+	\includegraphics[scale=0.3]{../screenshots/topicpage_sm.jpg}
+	\caption{Example topic page}
+	\label{topicpage}
+\end{figure}
+
+\subsection{Implementation Decisions}
+
+\idea{Wiki model not appropriate for points since want to manipulate several points at once}
+\idea{Need to visualize relationships in web of ideas}
+
+% \section{Creating Knowledge}
+% 
+% \section{Sharing Knowledge}
+% 
+% Why do users g
+% 
+% \section{Using Knowledge}
+% 
+% \section{Querying Data}
+
+\section{Preliminary User Feedback}
+
+1.5pp: recruitment, environment, tasks, observations, smaller study
+
 \subsubsection{User Interface Redesign}
@@
 
+\idea{remove confusion about ``where i am'' with fisheye view of current claim}
+
 \subsubsection{Second User Study}
@@
 \studyresult{we solved organization difficulties with this redesign}
-
-\section{Related Work}
-1p
-
-\subsection{Web Annotation Systems}
-
-\subsection{Semantic Linking}
-
-\subsection{User Contributed Links}
-
-Memex allowed users to describe their own paths between pages, rather than requiring the page authors to modify them.
-
-Everything2 creates soft-links between documents based on the browsing patterns of users.
-
-ENQUIRE contains bi-directional links that show who links to a document. TrackBack does the same.
-
-\subsection{Automated Reasoning}
-
-\subsection{Argumentation Graphs}
 
@@
 
+\bibliographystyle{abbrv}
+\bibliography{biblio.bib}
+
 \end{document}

### 2008-09-15 papers/web_of_ideas/web_of_ideas.tex
Fleshing out the paper

@@
 A user must thus invest significant effort extracting the claims that are accurate and interesting from the pages that they look at.
+
 We present Think Link, a tool that links pages to the factual claims that they make, and allows users to browse the web of factual claims, rather than the web of pages.
@@
 	\includegraphics[width=8.5cm]{../screenshots/redhighlight.png}
-	\caption{Browsing interface, with a contentious claim highlighted}
-	\label{redhighlight}
+	\caption{Think Link highlights the key claims made by a page. Red means the claim is contentious.}
+	\label{highlight}
 \end{figure}
@@
 \begin{figure}[ht]
-	\includegraphics[width=8.5cm]{../screenshots/sidebar.png}
-	\caption{Browsing interface, with the sidebar opened}
-	\label{sidebar}
+	\includegraphics[width=8.5cm]{../screenshots/sidebar3.png}
+	\caption{The margin shows a summary of the key claims made by the page}
+	\label{margin}
 \end{figure}
@@
 	\includegraphics[width=8.5cm]{../screenshots/claim_popup.png}
-	\caption{The ``Investigate Claim'' window pops up when one clicks on a claim}
-	\label{redhighlight}
+	\caption{Click on a claim to see supporting or opposing evidence on other web pages}
+	\label{claimview}
 \end{figure}
@@
 \section{Introduction}
+
+The web provides users with a huge number of pages they can read, but extracting useful factual information from these pages can be hard work.
+Not everything on the web is true.
+A web site may make claims that are contradicted by other web sites.
+If a user is to avoid incorrect claims then they will need to either stick to sources they can trust, or spend time looking for evidence on other web sites that supports or opposes what they have read.
+Similarly, not everything on the web is interesting.
+If a user wants to find interesting factual claims about a topic then they may have to waste time reading claims that they have either read elsewhere or do not find interesting in order to find the claims that interest them.
+
+Several commentators have observed that there is a Media Echo Chamber effect~\cite{echochamber,echochamber2} in which news sources report claims that they have heard from other news sources, despite the fact that these claims may be misleading or untrue.
+If a user only reads news sources from a particular group then they may only be exposed to the views of that group and may not be aware that opposing views exist unless they actively seek them.
+
+Part of the problem is that traditional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them.
+While a web page will typically contain links to other pages, as chosen by the page author, it does not provide an easy way for a user to validate whether the claims made by a page are supported by evidence that may be available on other pages.
+Moreover the best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web.
+The web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages).
+While this makes it easier for add knowledge to the web, it makes it harder for users to extract factual claims from it.
+
+\subsection{Browse the Web of Factual Claims}
+
+We have created a tool called Think Link that connects pages on the web to the factual claims being made on those pages, and allows a user to quickly find snippets of text on other web pages that make supporting or opposing claims.
+We hope that this tool will make it easier for users to identify incorrect claims in documents they read, and to quickly identify the best arguments for and against claims that they may be interested in.
+
+As a user browses a web page Think Link will highlight snippets of text that make factual claims (Figure~\ref{highlight}).
+If a factual claim is contentious (meaning that other pages make opposing claims) then the highlight will be red.
+More information about highlighted claims can be found by either mousing over one of them, or opening the Think Link margin (Figure~\ref{margin}).
+
+These highlighted claims serve as entry points to a browsable graph of factual claims.
+Clicking on a claim will pop up a window that allows one to easily view the other claims that support or oppose the selected claim, and the snippets of text on the web that make these claims (Figure~\ref{claimview}).
+
+For example, if a user browsed a web page that claimed ``Global Warming does not exist'', then the text snippet that made this claim would be highlighted in red, indicating the fact that there are web pages elsewhere that make opposing claims.
+If the user were to click on the highlighted snippet then an ``investigate claim'' window would appear.
+This window would show that the claim ``Global Warming does not exist'' is opposed by the claim ``There is strong evidence for global warming''.
+If the user navigated to this new claim then they could quickly see the best claims that support the existence of global warming, and would be able to see summaries of the best sources that supported these claims.
+
+\subsection{Collaborating to connect claims}
+
+Think Link shares a lot in common with Wikis like Wikipedia~\cite{wikipedia}.
+The claim graph is shared between all users and editable by anyone.
+Any user can identify a claim made on a web page by selecting the web snippet that makes this claim and clicking the ``new snippet'' button on the browser toolbar.
+Similarly, any user can establish new supporting and opposing relationships between claims by using drag and drop within the claim browser.
+One can think of Think Link as being rather like a Wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.
+
+Think Link uses collaborative filtering~\cite{collaborativefilter} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim.
+If a user finds a snippet or claim interesting then they can mark it as such.
+When Think Link lists claims or snippets, it will show first those that the user marked as interesting, and order the rest according to the number of other users who marked them interesting.
+
+\subsection{The Mental Model}
+
+Think Link presents users with three kinds of object, each associated with a different family of icons:
+
+\begin{itemize}
+\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false.
+For example ``Global warming exists''.
+A claim may support or oppose other claims.
+Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and are not understood logically by Think Link.
+\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a particular web site that asserts or assumes the truth of a particular claim.
+Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
+\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about.
+For example ``Global Warming'', or ``Computer Science''.
+A claim can have one or more topics that it is about, and a topic can have one or more more general topics.
+Topics are used both to organize, and to disambiguate claims.
+For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''.
+Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
+\end{itemize}
+
+The three icons are used consistently when refering to these three object types. 
+Yellow versions of these icons (\includegraphics[width=0.3cm]{../images/lightbulb.png},\includegraphics[width=0.3cm]{../images/folder.png},\includegraphics[width=0.3cm]{../images/comment_yellow.png}) are used to identify claims, folders, or snippets that the user has marked as interesting.
+
+\subsection{Why People Annotate}
+
+Tools like Think Link rely on user contributions in order to be useful.
+If no users are identifying factual claims on pages then other people who browse such pages will not see any claims identified.
+Similarly, if no other users are connecting claims together, then users will not see any supporting or opposing claims when they click on a highlighted snippet.
+
+Moreover, in order to become popular, a tool like Think Link needs to be useful even when very few people are using it.
+If a tool is only useful when it has a large community using it then it is unlikely that early adopters will stick with it enough for it to ever acquire a large community.
+
+Our user study participants identified several reasons why they would want to mark up factual claims in documents they found.
+The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found.
+One user (who was an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
+The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
+
+\studyresult{Quotes of users saying why they would use it}
+
+\subsection{Contributions}
+
+We believe that this work makes the following key contributions:
+
+\begin{itemize}
+\item We propose a new approach to browsing web pages that focusses on the factual claims made by these articles
+\item We develop interaction techniques that make it easy for a user to browse the web through factual claims
+\end{itemize}
+
+\section{Interaction Techniques}
+
+Users interact with Think Link in four key ways.
+Think Link will draw attention to interesting claims on pages that the user browses; it allows the user to identify new factual claims on pages they browse; it allows them to browse the graph of related claims and identify the strongest evidence supporting or opposing the claims they are looking at; and it allows them to organize the claim graph by making new connections between existing claims and topics.
+
+\subsection{Identifying factual claims on a page}
+
+When a user browses a web page, we want to make them aware of claims being made on the page that they might find interesting, or that other sources disagree with.
+Think Link draws attention to the factual claims that other users have identified on a web page by highlighting them (Figure~\ref{highlight}).
+Snippets are highlighted in red if they are contenious (other sources disagree with the claim), or yellow otherwise.
+The highlight colors are chosen such as to be pale enough to not impede reading, but dark enough to be noticeable.
+The colors are chosen to fit with people's normal associations with colors, where red is commonly associated with danger (e.g.
+a traffic light) and yellow is the standard color used for highlighter pens.
+
+While a highlight lets the user know that a the snippet is making an interesting or contentious claim, the user may still wonder what claim the snippet has been identified as making.
+A snippet could be interpreted as asserting the truth of several claims.
+For example the phrase ``Alice and Bob live in Canada'' asserts both that Alice lives in Canada and that Bob lives in Canada.
+Similarly, a user may have eroneously marked a snippet as asserting a claim that it does not directly assert to be true.
+For example ``Alice and Bob live together''.
+
+There are two ways that a user can identify the claims being made by the highlighted snippet; they can either hover their mose over a particular snippet to show information about that snippet (Figure~\ref{highlight}, or they can use the Think Link margin to show information about all snippets on the page (Figure~\ref{margin}).
+
+The Think Link Margin is designed to mimick the traditional margin notes that readers often write on physical documents they are reading~\cite{marginalia}.
+A margin space is added to the left of the page containing a margin note for each snippet.
+Each margin note is aligned vertically with the claim it is about and contains the text of the claim.
+To emphasise the connection between a margin note and its associated snippet, a snippet is highlighted more strongly when the user mouses over the associated margin note (Figure~\ref{margin}).
+
+We found that when a participant sees a highlighted snippet, they will typically want to do one of four things: ignore it, remember it, delete it, or investigate it.
+If the user finds the snippet interesting and wants to use it later then they can bookmark it by clicking the bookmark icon that pops up when they mouse over the margin note.
+This will cause it to be displayed prominently in the claim browser (Section~\ref{browseclaims}).
+If the user believes the snippet to not be making the claim that it says it does or otherwise badly marked up then they can delete the snippet by clicking on the trash can icon on the margin note.
+If the user thinks the claim is interesting and wants to see how it relates to claims made by other snippets on the web then they can click on either the highlighted text or the margin note to open the claim browser (Section~\ref{browseclaims}).
+
+A user can also use the margin to provide a quick overview of a document.
+They can scroll quickly through the document and look to see what key claims other users have marked in the margins.
+Several users remarked on how useful it was when reading a long document to be able to quickly scan through it and see what other users have thought were the most interesting points.
+\studyresult{put in some quotes}
+
+\todo{sort out more consistent colors and icons between this view and the web view}
+\todo{give the margin consistent colors with the highlight sections}
+\todo{more nice zoomed-in screenshots showing the different interaction techniques}
+
+\subsection{Identifying new factual claims}
+
+If a user finds a snippet of text on a page that makes an interesting claim then they may want to enter it into Think Link.
+There are several reasons they may wish to do this.
+It may be that they find the snippet useful and may want to refer to it again in the future.
+It may be that they disagree with the claim, and want to alert other readers to the fact that there are opposing arguments, or it may be that they agree with the claim and want to provide easy access to evidence that backs it up.
+
+\todo{Make new snippet icon throb when something is selected}
+
+\subsection{Browsing factual claims}
+\label{browseclaim}
+
+\subsection{Organizing factual claims}
+
+\section{Discussion}
+
+\subsection{Context of a Claim}
+
+\subsection{How many claims to show}
+
+\subsection{Beyond Claims}
+
+\section{Implementation}
+
+Think Link is implemented as three largely independent components:
+
+\begin{itemize}
+\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains a graph of claims, topics, and snippets and provides an API that allows this data to be queried and modified
+\item {\bf A web UI}, written using Ruby on Rails~\cite{rails} that provides a visual interface to the claim graph
+\item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page.
+This script also provides the ability to create new snippets or display the rails interface to investigate a particular claim.
+\item {\bf A browser extension}, implemented for Firefox~\cite{firefoxextension}, that inserts the page enhancement script into all pages the user browses to, and provides toolbar and context-menu shortcuts to the ``new snippet'' feature of the page enhancement script.
+\end{itemize}
+
+These components are largely independent.
+One could use the javascript script on a web page without using the firefox extension, by either manually including it on the page (e.g.
+to enhance your own blog) or by adding it using a proxy.
+Since the server API is public, one could write alternative tools that mark up web pages in different ways, or use the claim graph for different purposes.
+
+The source code to Think Link is publicly available under the Apache license at the following URL:
+
+{\b url removed for blind submission}
+
+We expect to have a public deployment available by the time of publication.
+
+We use icons from the free FamFamFam Silk~\cite{silkicons} collection.
+
+\section{Iterative Evaluation}
+
+Think link was developed using an iterative design process.
+During each iteration, we would talk to participants about the way they found and organized information on the web, and then perform a think aloud study where the participants would use the tool and tell us what they were thinking.
+After each iteration, we would study what we had learned from the participants and update our prototype accordingly.
+We went through a total of four iterations, with varying degrees of formality.
+
+\subsection{Investigatory Study}
+
+\subsection{Evaluation Study}
+
+We performed two user studies.
+In the first study, we asked participants about how they found and organized information on the web, and performed a think aloud study where they used the tool and told us what they were thinking.
+The learnings from the first study.
+
+In the first user study, we perf
+
+showed the participants an early version of the Think Link interface
+
+Think Link was developed using an iterative design process.
+
+We performed two user studies. The aim of the first study was to determine
+
+In the first of these studies, we recruited 12 paid subjects, aske
+
+\subsection{Interaction Techniques}
+
+The web has provided users with many pages that they can read.
+
 1p:  
@@
 
-% \idea{Much interesting data on the web is unstructured text}
-% 
-% \idea{These documents consist of ideas}
-% 
-% \idea{Think Link connects documents to the ideas they express}
-% 
-% %\idea{This paper is itself marked up in think link - with URL}
-% 
-% \idea{If the ideas in a document are known then this allows interesting queries}
-
-% Motivation for tool
-
-% What thinklink allows people to do
-
-% Why thinklink is needed
-
-\idea{People already annotate documents, in the form of blogs, comments etc}
-
-\idea{People already organize data, using text files, Google Notepad, OneNote, etc}
-
-\idea{People already share information, by mailing links, posting stories on facebook, sending messages on twitter, etc}
-
-\idea{People already want to see what each other are interested in - using Facebook, Twitter, Friendfeed, etc}
-
-\studyresult{Our users used these tools}
-
-\studyresult{Users want to put forward their opinions}
-
-\studyresult{People want to be seen as a source of useful information}
-
-\studyresult{People want to organize the information they find}
-
-\studyresult{Our users said they would use our tool}
-
-%\studyresult{The best way to find answers is social - by learning from friends who understand the topic}
-
-\section{Motivation?}
-1-2pp: 
-how do people currently organize, interact, share with web content; 
-Thinklink data structures; 
-what can people now do with Thinklink
-
-\subsection{Why People Annotate}
-
-\subsection{Organizing Knowledge}
-
-\idea{Like Wikipedia without the articles}
-
-\idea{Organize ideas with Points, snippets, and topics}
-
-\idea{A point can support or oppose another point}
-
-\idea{A point can be exactly the same or exactly opposite}
-
-\idea{Important to have wiki features to keep things in check}
-
-\studyresult{People found it useful to organize ideas}
-
-%\studyresult{People found the topic approach worked well}
-
-%\studyresult{People were able to easily find and reuse existing points and topics}
-
-\subsection{Using this Knowledge}
-
-\idea{Show me the points that other people disagree with}
-
-\idea{Show me the points that other people found interesting}
-
-\idea{Show me the points that my friends found interesting}
-
-% future queries want to support
-
-\idea{Show me the articles that make interesting points I haven't heard before}
-
-\idea{Show me when new snippets appear on points I'm interested in}
-
-\idea{Show me when new points appear on topics I'm interested in}
-
-%\studyresult{People liked to be able to monitor interesting new ideas on topics they were interested in}
-
-\studyresult{People liked the other features too}
+%\studyresult{The best way to find answcuters is social - by learning from friends who understand the topic}
 
 \section{Related Work}
+
+\subsection{Wikis}
+
+\subsection{Web Annotation}
+
+\subsection{Sensemaking}
+
+\subsection{Argumentation Theory}
+
+The 
+\cite{Korb97acognitive}
+\cite{toulmin}
+\cite{carneades}
+\cite{conceptmap}
+\cite{argmas}
+
+Memex
+Vannevar 
+Bush’s vision of Memex. Bush popularized the idea that 
+people can collaboratively organize and share knowledge: 
+“Wholly new forms of encyclopedias will appear, ready-made 
+with a mesh of associative trails running through them...” 
+[5]. In many ways the vision has come to pass with large 
+amounts of hyper-linked information in the World Wide 
+Web, digital libraries, and online encyclopedias. However, 
+researchers continue to point out that people, especially 
+those lacking domain expertise, struggle to navigate infor- 
+mation spaces.
+
+\subsection{Identifying Ideas on the Web}
+
+\cite{quotations}, \cite{quotationdl} Overall aim is to identify and connect ideas. Do quotation matching as a partial solution.
+
+\cite{ideanavigation}, \cite{citesense}
 
@@
 Argumentation graphs express positions and arguments in a formal graph model as nodes and edges, respectively, and are typically used to make a decision or draw a conclusion about some issue.
-One example implementation is the {\it Zeno} argumentation framework [\idea{cite}], designed for collaborative use in mediation systems to debate the quality of alternative solutions for a problem.
-In their object model of argumentation elements, based on Rittel's IBIS model [\idea{cite}], example nodes include pro/con arguments, positions, preferences, comments, and decisions.
+One example implementation is the {\it Zeno} argumentation framework~\cite{zeno}, designed for collaborative use in mediation systems to debate the quality of alternative solutions for a problem.
+In their object model of argumentation elements, based on Rittel's IBIS model~\cite{ibis}, example nodes include pro/con arguments, positions, preferences, comments, and decisions.
 Importantly, arguments are connected via {\it consequent} and {\it antecedent} edges, which are used to inform {\it choices}.
@@
 \bibliographystyle{abbrv}
-\bibliography{biblio.bib}
+\bibliography{biblio}
 

### 2008-09-15 client_js/tl_margin.js

@@ -335,17 +335,17 @@ function tl_margin()
 			// then if necessary change pos to be underneath, and check again
 			if (vertPos >= itemPos && vertPos <= itemPosRange) {
 				var itemAbove = document.getElementById("margin"+this.items[index].id);
-				if(!itemAbove.tl_squeezed){
-					itemAbove.textContent = itemAbove.textContent.substr(0,20) + "...";
-					this.items[index].displayText= itemAbove.textContent;				
-					itemAbove.tl_squeezed = true;
-					itemPosRange = itemPos + itemAbove.offsetHeight;
-					if (vertPos >= itemPos && vertPos <= itemPosRange) {
-						vertPos = itemPosRange + 1;
-					}					
-				}else{
+//				if(!itemAbove.tl_squeezed){
+//					itemAbove.textContent = itemAbove.textContent.substr(0,20) + "...";
+//					this.items[index].displayText= itemAbove.textContent;				
+//					itemAbove.tl_squeezed = true;
+//					itemPosRange = itemPos + itemAbove.offsetHeight;
+//					if (vertPos >= itemPos && vertPos <= itemPosRange) {
+//						vertPos = itemPosRange + 1;
+//					}					
+//				}else{
 					vertPos = itemPosRange+1;
-				}
+//				}
 			}
 		}
 		return vertPos;
@@ -393,10 +393,10 @@ function tl_margin()
 				function(){ 					
 					if (snippet.opposed){
 						var div = $("<div><span class='tl_claim_warn'>contentious claim: </span><span class='tl_claim_text'>"
-								+snippet.pointText+"</span><span class='tl_claim_click'> (click for more info)</span></div>").get(0);
+								+snippet.pointText+"</span><span class='tl_claim_click'> (click snippet for more info)</span></div>").get(0);
 					}else{
 						var div = $("<div><span class='tl_claim_prefix'>this claims: </span><span class='tl_claim_text'>"
-							+snippet.pointText+"</span><span class='tl_claim_click'> (click for more info)</span></div>").get(0);
+							+snippet.pointText+"</span><span class='tl_claim_click'> (click snippet for more info)</span></div>").get(0);
 					}
 					tool=
 					tl_delayedShowTooltip(div,mouseX+10,mouseY-30); },
@@ -449,12 +449,20 @@ function tl_margin()
[…]

### 2008-09-16 papers/web_of_ideas/web_of_ideas.tex
More work on the paper. Fleshing out more

@@
 \author{
-\alignauthor Beth Trushkowsky\\
-       \affaddr{Computer Science Division}\\
-       \affaddr{University of California at Berkeley}\\
-       \email{trush@berkeley.edu}
-\alignauthor Rob Ennals\\
-       \affaddr{Intel Research}\\
-       \affaddr{2150 Shattuck Avenue}\\
-       \affaddr{Penthouse Suite}\\
-       \affaddr{Berkeley, CA 94704, USA}\\
-       \email{robert.ennals@intel.com}
+	\alignauthor Authors anonymized for submission
 }
+
+%\author{
+%\alignauthor Beth Trushkowsky\\
+%       \affaddr{Computer Science Division}\\
+%       \affaddr{University of California at Berkeley}\\
+%       \email{trush@berkeley.edu}
+%\alignauthor Rob Ennals\\
+%       \affaddr{Intel Research}\\
+%       \affaddr{2150 Shattuck Avenue}\\
+%       \affaddr{Penthouse Suite}\\
+%       \affaddr{Berkeley, CA 94704, USA}\\
+%       \email{robert.ennals@intel.com}
+%}
 
@@
 If a user only reads news sources from a particular group then they may only be exposed to the views of that group and may not be aware that opposing views exist unless they actively seek them.
+Tim Berners Lee has expressed concern about the difficulty that people face discerning whether information on the web is true~\cite{bbcwebwarning}.
 
@@
 
+\begin{figure}[t]
+	\includegraphics[width=8.5cm]{../screenshots/snipsave_full.png}
+	\caption{The claim selection window allows one to identify the claim a snippet is making}
+	\label{snipsavefull}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.5cm]{../screenshots/snipsave_crop.png}
+	\caption{Close up view of the claim selection window}
+	\label{snipsavecrop}
+\end{figure}
+
 If a user finds a snippet of text on a page that makes an interesting claim then they may want to enter it into Think Link.
@@
 
+To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button.
+This is a similar approach to that taken clipping tools such as Google Notebook~\cite{googlenotebook}.
+
+Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making.
+To do this, Think Link presents the user with a ``claim selection'' window.
+This window contains a small version of the claim browser (Section~\ref{browseclaim}) that the user can use to select the claim that the snippet is making.
+At the bottom of the window, we show the phrase ``the snippet text {\it snippet} claims that {\it claim}''.
+We found that this helps users understand the nature of a claim and its relationship to a snippet (Section~\ref{study-claimmeaning}).
+
+Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics.
+Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one.
+Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim.
+To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to.
+For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim.
+
+This is an intentionally different model to that used by ad-hoc tag-based~\cite{tags} systems such as Delicious~\cite{delicious} and Flickr~\cite{flickr}.
+This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected.
+
+In earlier revisions of the interface it was very easy for users to quickly create new claim texts and awkward to find and reuse existing ones.
+This led users to create many claims that were essentially equivalent and reduced the utility of Think Link as a tool for connection snippets together (Section~\ref{study-reuse}).
+
 \todo{Make new snippet icon throb when something is selected}
@@
 \label{browseclaim}
+
+\begin{figure}[ht]
+	\includegraphics[width=8.5cm]{../screenshots/claimbrowse.png}
+	\caption{The Claim Browser}
+	\label{fig:claimbrowser}
+\end{figure}
+
+Our users expressed an interest in using snippets to help them construct arguments that support a claim they agree with, to show them the arguments for and against a claim that they are unsure about, to collect evidence about a topic they are interested in, to share information with friends, and to see arguments against claims that they encountered on the web.
+We constructed the ``claim browser'' interface to help users do these things (Figure~\ref{fig:claimbrowser}).
+
+Claims and topics form a directed graph structure. A claim can have any number of claims that support or oppose it, and any number of claims that it supports or opposes.
+A topic can have any number of more specific topics (e.g.
+``US Election 2008'' is more specific than ``US Elections'') and any number of more general topics.
+A topic can also have any number of claims about that topic.
+
+When designing an interface to this structure, we were faced with two opposing constraints.
+We needed to be able to clearly view a large number of claims and topics in a small screen space, and we needed an interface that made it clear that the data was a graph rather than a tree.
+Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims.
+Tree-based outliners such as OmniOutliner~\cite{outliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
+
+After several iterations, we settled on an interface that is a dynamically reorganizing graph layed out like an outliner.
+Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it.
+Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line.
+Our users commented that they found it quite intuitive to navigate through a graph of claims and topics in this way.
+\studyresult{quote}.
+
+The placement of objects above and below is intended to emphasize the conventional structuring of an argument graph (Section~\ref{argumentgraph}), with topics going upwards and arguments for and against a claim going downwards.
+A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
+
+\todo{Have I seen an interface like this elsewhere? Did PARC have something like this?}
+
+\todo{Is this interface a contribution in itself? Has an interface like this been presented before?}
+
+Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states.
+When a new item is selected, it grows in size and moves to the center.
+Other items that were already on the screen move from their current locations to their new locations.
+Other objects appear and disapper by smoothly sliding into or out of view.
+We found that this animation helps users retain a sense of where they are with respect to what they were looking at previously and helps users avoid getting lost (Section~\ref{gettinglost}).
 
@@
 Vannevar 
-Bush’s vision of Memex. Bush popularized the idea that 
+Bush's vision of Memex. Bush popularized the idea that 
 people can collaboratively organize and share knowledge: 
-“Wholly new forms of encyclopedias will appear, ready-made 
-with a mesh of associative trails running through them...” 
+``Wholly new forms of encyclopedias will appear, ready-made 
+with a mesh of associative trails running through them...'' 
 [5]. In many ways the vision has come to pass with large 
@@
 \cite{quotations}, \cite{quotationdl} Overall aim is to identify and connect ideas. Do quotation matching as a partial solution.
+
+\cite{scenthighlights}
 
@@
 Trailfire
+Zotero~\cite{zotero} is a citation mangament tool. Find and organise sources, while recording author, date etc by understanding pages. Can add notes to sources.
 

### 2008-09-16 papers/web_of_ideas/web_of_ideas.tex
More minor tidy ups - removing the frame from the popup point browser
More fleshed out. Starting to write about the user studies

@@
 
+\todo{This interface is actually closer to TheBrain than the text suggests}
+
 After several iterations, we settled on an interface that is a dynamically reorganizing graph layed out like an outliner.
@@
 
+Users see a claim browser in three different places:
+\begin{itemize}
+\item {\bf The Main Organizer} shows two claim browsers, and allows users to use drag and drop to make new connections between claims in the two organizers. (Figure~\ref{fig:claimbrowser})
+\item {\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page. (Figure~\ref{claimview})
+\item {\bf The Claim Selection Window} shows one claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making. (Figure~\ref{snipsavefull}) 
+\end{itemize}
+
 \subsection{Organizing factual claims}
+
+Much of the value of Think Link comes from the connections between claims. It is thus important that it be easy to establish new connections between claims and topics.
+
+Think Link uses the familiar drag and drop interface for establishing new connections.
+To establish a connection between two claims, one need simply drag one claim onto the other.
+In the full interface, one can open two browsers and drag points from one browser onto points on the other.
+
+In our initial study, we found that many users did not realize that they could use drag and drop to create connections to existing claims.
+We rectify this, we added a notice at the top of the main organizer window (Figure~\ref{fig:claimbrowser}) telling users that they can use drag and drop.
+
+We found that creating new connections between existing claims was one of the things that users found most difficult.
+
+\todo{say more here}
 
@@
 \section{Iterative Evaluation}
+
+We performed two user studies to guide and evaluate the development of Think Link.
+The aim of the first study was to talk to users about the way in which they gather knowledge on the web and see how they might try to use an initial prototype of Think Link.
+After the first study, we revised out implementation, guided by our observations from the first study.
+The aim of the second study was to validate that our new design was indeed useful and to look for areas for future improvement.
+
+\subsection{Protocol for the First Study}
+
+For the first study, we recruited 13 paid participants. Five were female, eight were male. Their ages ranged from high school age to retired.
+
+Our user study participants were selected from a pool of respondents to a Craigslist posting in which we asked for people who use the internet as one of their primary sources of information, regularly gather and share this information, and are interested in a new application to facilitate that process.
+We chose participants based on their responses to the following questions:
+\begin{enumerate}
+	\item What topics or types of information do you usually look for on the internet?
+	\item How do usually go about finding information? (e.g. google, digg, friends, etc)
+	\item How do you organize the information you find? (e.g. text file, paper, wiki, etc)
+	\item How do you share information with others? (e.g. blog posts, comments, email, facebook, etc)
+\end{enumerate}
+We preferred individuals who search the internet for research and reading news rather than online shopping, as well as those interested in social and collaborative web activities like social networking web sites.
+We were also interested in those who seemed to express a need for our application: people who copy-and-paste text from web pages into word processing documents, or who regularly email web page addresses to friends.
+
+Each study session lasted between thirty to forty-five minutes, with the participant sitting at a desktop computer with the Firefox browser running the application plugin.
+The session was a Think-Aloud study in which the participant verbally describes his/her thoughts throughout the duration of the study.
+A video camera captured the audio/video and was focused on the monitor screen.
+Before the session began, we briefly demonstrated the features of the application: how to (1) select snippets, (2) write a snippet topic and point, (3) relate points, (4) show/hide the margin, and (5) browse recent activity.
+
+The study consisted of two tasks to collect snippets, each lasting ten to fifteen minutes.
+During both tasks, we asked participants to browse the web as they normally would.
+In the first task, the participant browses the web about a topic or issue of their choice from the domain of politics.
+The collection of snippets should help the participant either argue or form an opinion/perspective about the topic, and should be thought of being used to help him/her explain or discuss the topic with a friend.
+We constrained the first task to politics to increase the likelihood that the study participants would encounter similar issues and news stories.
+
+For the second task, the participant was allowed to browse for any topic of their choosing.
+While the likelihood of topic overlap across participants was much lower, we were able to observe their behavior when searching for information in which each person had genuine interest.
+
+At the conclusion of the session, we asked the participant if the application is something that would be likely to use, and for what purposes they would find it most useful.
+Any confusing features or experiences were also noted.
+
+\subsection{Protocol for the Second Study}
 
@@
 
+\cite{scenthighlights}\cite{scenttrails}
+
 \subsection{Argumentation Theory}
@@
 
+\cite{personalweb}
+
 Diigo lets you save, import, tag, highlight, mark up and share Web pages
@@
 Zotero~\cite{zotero} is a citation mangament tool. Find and organise sources, while recording author, date etc by understanding pages. Can add notes to sources.
+Scrapbook~\cite{scrapbook}
 
@@
 \section{Observations Informing Design}
-
-\subsection{Recruitment}
-Our user study participants were selected from a pool of respondents to a Craigslist posting for people who use the internet as one of their primary sources of information, regularly gather and share this information, and are interested in a new application to facilitate that process.
-We chose participants based on their responses to the following questions:
-\begin{enumerate}
-	\item What topics or types of information do you usually look for on the internet?
-	\item How do usually go about finding information? (e.g. google, digg, friends, etc)
-	\item How do you organize the information you find? (e.g. text file, paper, wiki, etc)
-	\item How do you share information with others? (e.g. blog posts, comments, email, facebook, etc)
-\end{enumerate}
-We preferred individuals who search the internet for research and reading news rather than online shopping, as well as those interested in social and collaborative web activities like social networking web sites.
-We were also interested in those who seemed to express a need for our application: people who copy-and-paste text from web pages into word processing documents, or who regularly email web page addresses to friends.
-Twelve people were selected to participate in this study.
-
-\subsection{Study Environment}
-Each study session lasted between thirty to forty-five minutes, with the participant sitting at a desktop computer with the Firefox browser running the application plugin.
-The session was a Think-Aloud study in which the participant verbally describes his/her thoughts throughout the duration of the study.
-A video camera captured the audio/video and was focused on the monitor screen.
-Before the session began, we briefly demonstrated the features of the application: how to (1) select snippets, (2) write a snippet topic and point, (3) relate points, (4) show/hide the margin, and (5) browse recent activity.
-
-\subsection{Study Tasks}
-The study consisted of two tasks to collect snippets, each lasting ten to fifteen minutes.
-During both tasks, we asked participants to browse the web as they normally would.
-In the first task, the participant browses the web about a topic or issue of their choice from the domain of politics.
-The collection of snippets should help the participant either argue or form an opinion/perspective about the topic, and should be thought of being used to help him/her explain or discuss the topic with a friend.
-We constrained the first task to politics to increase the likelihood that the study participants would encounter similar issues and news stories.
-
-For the second task, the participant was allowed to browse for any topic of their choosing.
-While the likelihood of topic overlap across participants was much lower, we were able to observe their behavior when searching for information in which each person had genuine interest.
-
-At the conclusion of the session, we asked the participant if the application is something that would be likely to use, and for what purposes they would find it most useful.
-Any confusing features or experiences were also noted.
 

### 2008-09-16 papers/web_of_ideas/web_of_ideas.tex
Part way through writing up user study stuff

--- 2008-09-16 papers/web_of_ideas/web_of_ideas.tex
@@
 
-\section{Iterative Evaluation}
+\section{Investigative Study}
 
-Think link was developed using an iterative design process.
-During each iteration, we would talk to participants about the way they found and organized information on the web, and then perform a think aloud study where the participants would use the tool and tell us what they were thinking.
-After each iteration, we would study what we had learned from the participants and update our prototype accordingly.
-We went through a total of four iterations, with varying degrees of formality.
+We performed two ``think aloud'' studies to guide and evaluate the development of Think Link.
+The aim of the first study was to see how users normally browse the web and to see how they might try to use an initial prototype of Think Link to help them.
 
-\subsection{Investigatory Study}
+\subsection{Protocol for the First Study}
 
-\subsection{Evaluation Study}
+We recruited 12 paid participants.
+Five were female, seven were male.
+Their ages ranged from high school age to retired.
+Our intention was to recruit users who were not experts, but who regularly used the internet to find information.
+We recruited participants using a posting to the Craigslist~\cite{craigslist} classified adverts site.
+In our advert, we expressed an interest in people who use the internet to gather knowledge, rather than just for tasks such as email or shopping.
+We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.
 
-We performed two user studies.
-In the first study, we asked participants about how they found and organized information on the web, and performed a think aloud study where they used the tool and told us what they were thinking.
-The learnings from the first study.
+\subsection{Study Protocol}
 
-In the first user study, we perf
+Study sessions took approximately 45 minutes.
+Participants were seated at a single-screen workstation with the Firefox browser, augmented with the Think Link plugin.
+We first demonstrated Think Link's interface, and then asked them to perform two tasks.
+In the first task, we asked them to use Think Link to gather information about a political topic that was of interest to them and currently in the news.
+For the second task, we asked them to browse the web in a way that would typically do so at home or at work, and see if they could use Think Link to help them do so.
 
-showed the participants an early version of the Think Link interface
+In the second task, we wanted to leave users relatively unconstrained so that we could see how users might try to use a tool like this during their normal browsing, rather than how well they could accomplish a pre-set task that they might never attempt in normal life.
+For the first task, we constrained the task to an a topic for which we had already marked up a number of claims, to increase the likelyhood that users would encounter existing claims.
 
-Think Link was developed using an iterative design process.
+\subsection{Findings}
 
-We performed two user studies. The aim of the first study was to determine
+All the participants were able to create new snippets.
+Participants had little difficulty identifying interesting claims being made by web pages, selecting appropriate sections of text, and either picking existing claims that were appropriate, or writing appropriate new claims.
+Most ($9/12$) stated that they found it easy to create new snippets and associate them with claims.
 
-In the first of these studies, we recruited 12 paid subjects, aske
+In the initial interface, snippets were only highlighted when the margin was open.
+This confused some participants ($5/12$) who were surprised to not see their snippets highlighted when they created them.
+This led us to change the interface so that snippets were always highlighted.
 
-\subsection{Interaction Techniques}
+In the initial interface, the button to open the margin was on the toolbar, next to the ``new snippet'' button, rather than
 
-The web has provided users with many pages that they can read.
+Two participants initially had dificulty summarising text with a claim that the text was actually making, rather than an claim it was associated with.
 
-1p:  
-overview, 
-motivation,
-list of contributions,
-(briefly) describe application,
-(briefly) describe user studies,
-describe results,
+Many ($7/12$) participants also expressed a desire to organize snippets and claims during their session.
+Of these seven, we noticed that four would alternate between creating new snippets and organizing their claims in the claim browser (Section~\ref{claimbrowser}).
+With each new claim, users would create relationships between existing claims.
 
-%\studyresult{The best way to find answcuters is social - by learning from friends who understand the topic}
+\subsection{The Prototype Interface}
+
+Participants were shown an earlier interface than that described in Section~\ref{interface}.
+
+\begin{figure}[ht]
+	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
+	\caption{First Prototype Snippet Creation Dialog}
+	\label{oldsnippetbox}
+\end{figure}
+
+\subsection{Successes}
+
+All the participants were able to create new snippets, succeeding in identifying appropriate sections of text that should be marked, and picking out either an appropriate existing claim, or creating a new claims that accurately summarized the snippet.
+Two participants initially had difficulty in correctly summarizing text with a claim that the text was actually making, but they eventually got used to it.
+
+Many ($7/12$) participants also expressed a desire to organize snippets and claims during their session.
+Of these seven, we noticed that four would alternate between creating new snippets and organizing their claims in the claim browser (Section~\ref{claimbrowser}).
+With each new claim, users would create relationships between existing claims.
+
+Most ($10/12$) either reused a topic that they had created themselves or that we had previously created.
+While the level of social activity was undoubtedly limited by the relatively small number of claims available in our database and the wide range of topics participants read about, three of the six people who browsed points in the
+
+\subsection{Observations Motivating Design Changes}
+
+Many ($7/12$) participants also expressed the desire to organize snippets and points during their session.
+Of these seven, we noticed that four were alternating between creating snippets from new articles and organizing points in their {\it Recent Activity}: with each new snippet, users were creating relationships between points.
+When browsing web content about a particular topic or issue, most participants ($10/12$) either reused a topic that they created during their session or that someone else had created previously.
+Half of those ten used a topic that they {\it hadn't} created, demonstrating the ease of collaboration in our application.
+Both these organizational activities support connections inside the web of ideas.
+While the level of social activity was undoubtedly limited by the relatively small number of points (about $400$), three of the six people who browsed points in the main web interface looked at points created by other users.
+Two of the later study participants viewed someone else's point and either read the snippet text or viewed the originating document.
+As the number of points and topics increases, we expect to see more social behavior like this.
+
+\subsection{Browsing Claims}
+
+\subsection{Creating Snippets}
+
+\section{Evaluation Study}
+
+The purpose of the second study was to evaluate whether the interface changes we had made in reaction to the first study had made the tool usable.
+
+\subsection{Recruitment}
+
+We recruited 6 paid participants.
+Four were female and two were male.
+Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students.
+Since the second group was different demographically to the first group, it is not possible to make a direct comparison between their behaviours.
+However we were still able to make interesting observations about how users used the new interface.
+
+\subsection{Study Protocol}
+
+For the second study, we changed the task to focus on how easy users found it to use the interface, rather than on how they might apply it to their normal browsing.
+We told users nothing about how to use the tool.
+Instead, we just gave them a brief introduction to what our tool was for, and then asked them to attempt two tasks.
+The first task was to look at a selection of web pages that already had highlights and tell them to explore the interface.
+The second task was to identify claims on a page that had not been marked up and connect them appropriately to existing claims.
 
@@
 \subsection{Sensemaking}
+
+\cite{scenthighlights}\cite{scenttrails}
 

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
More work on the paper - primarily related work

@@
 \newcommand{\studyresult}[1]{{\color{red} STUDY RESULT?: #1}\\}
+\newcommand{\howmany}{{\color{red} (HOW MANY?)}}
 
@@
 \subsection{Identifying new factual claims}
+\label{newsnippet}
 
@@
 
-\subsection{Protocol for the First Study}
-
 We recruited 12 paid participants.
@@
 
-\subsection{Study Protocol}
+\subsection{Protocol for the First Study}
 
@@
 
+The focus of this study was on whether people would be able to gather snippets on the web and structure them into a coherent argument graph, rather than on how they would react when they browsed to a page where an argument had already been identified - which was one of the focusses of our second study.
+
+In this initial study, users were exposed to the prototype interface shown in Figures~\ref{oldsnippetbox} and \ref{oldbrowser}, rather than the final interface described in Section~\ref{interface}.
+
 \subsection{Findings}
@@
 Most ($9/12$) stated that they found it easy to create new snippets and associate them with claims.
+In the initial interface snippets were only highlighted when the margin was open.
+This confused some participants ($5/12$) who were surprised to not see their snippets highlighted when they created them.
+In the final interface, we addressed this problem by always highlighting snippets.
 
-In the initial interface, snippets were only highlighted when the margin was open.
-This confused some participants ($5/12$) who were surprised to not see their snippets highlighted when they created them.
-This led us to change the interface so that snippets were always highlighted.
-
-In the initial interface, the button to open the margin was on the toolbar, next to the ``new snippet'' button, rather than
-
-Two participants initially had dificulty summarising text with a claim that the text was actually making, rather than an claim it was associated with.
-
-Many ($7/12$) participants also expressed a desire to organize snippets and claims during their session.
-Of these seven, we noticed that four would alternate between creating new snippets and organizing their claims in the claim browser (Section~\ref{claimbrowser}).
-With each new claim, users would create relationships between existing claims.
-
-\subsection{The Prototype Interface}
-
-Participants were shown an earlier interface than that described in Section~\ref{interface}.
+In the initial interface the button to open the margin was on the toolbar, next to the ``new snippet'' button.
+This led some participants ($4/12$) to get confused about which they should use in each case.
+In the final interface, we addressed this problem by putting the margin button on the side of the page, with a chevron to indicate that it will pull out a margin (Figure~\ref{marginpull}).
 
 \begin{figure}[ht]
-	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
+	\includegraphics[width=8.5cm]{../screenshots/snippetdialog_sm.jpg}
 	\caption{First Prototype Snippet Creation Dialog}
@@
 
-\subsection{Successes}
+In the initial interface we used a simplified snippet creation window (Figure~\ref{oldsnippetbox}) that was intended to make the process of snippet creation very lightweight.
+This window contained two text boxes.
+The first of these boxes was for the topic (e.g.
+``Global Warming'') and the second of the boxes was for the claim (e.g.
+``Global Warming is Man Made'').
+Both of these boxes used an auto-complete drop-down list to suggest appropriate existing topics or snippets as the user typed,
+biasing towards topics that were recent or hot.
 
-All the participants were able to create new snippets, succeeding in identifying appropriate sections of text that should be marked, and picking out either an appropriate existing claim, or creating a new claims that accurately summarized the snippet.
-Two participants initially had difficulty in correctly summarizing text with a claim that the text was actually making, but they eventually got used to it.
+Most ($7/12$) users got confused between topics and claims at some point, either entering a topic as a claim, or entering a claim as a topic.
+We felt that this was partly because the snippet creation interface (Figure~\ref{oldsnippetbox}) gave the user little impression of how their snippet would appear in the claim browser.
+In the final interface we addressed this problem by giving the snippet creation interface the same core UI as the claim browser interface (Section~\ref{newsnippet}).
+We also decided to change our name for a factual claim from ``point'' to ``claim''.
 
-Many ($7/12$) participants also expressed a desire to organize snippets and claims during their session.
+While most ($10/12$) reused a topic that they had created or someone else had created, many ($6/12$) had a tendency to ignore the suggestion box and type new claims rather than looking for existing claims that might be a good match for their snippet.
+For the final interface, we tried to encourage users to reuse existing claims rather than writing new ones by making it easier to browse existing claims from the snippet creation window, and requiring users to click a \includegraphics[width=0.3cm]{../images/add.png} button in order to create a new claim (Section~\ref{newsnippet}).
+
+Our initial interface for claim browsing (Figure~\ref{oldbrowser}) caused several ($5/12$) to remark that they felt they were confused about where they were in the claim graph.
+This interface had a separate page for each claim or topic, rather than animating between them, making it easy to lose track of ones position in the graph of points.
+Several ($2/12$) remarked that part of the problem was that it wasn't obvious that the various boxes on the page were information about the claim in large text.
+For the final interface we addressed this problem by using animation to maintain a sense of where things were when the focus changed, and by placing information about a point around that point rather than in separate boxes (Section~\ref{claimbrowser}).
+
+All users had some difficulty connecting existing claims together.
+The first four participants were a different interface in which new connections were made by clicking on an ``add'' button, and then typing the name of the claim into an auto-complete box.
+Users found this approach difficult as it required them to remember the text of claims that they had seen recently.
+In light of this, after the first four participants we switched to a drag and drop interface (Figure~\ref{oldbrowser}).
+
+The drag and drop interface worked better.
+Most ($7/8$) users were eventually able to use the new interface proficiently.
+However all users initially found the drag and drop interface confusing, and no users guessed that they could connect existing points using drag and drop.
+We identified this as an area needing improvement in the next interface revision.
+
+\begin{figure}[ht]
+	\includegraphics[width=8.5cm]{../screenshots/oldpoint_search.png}
+	\caption{Initial Prototype Claim Browser}
+	\label{oldbrowser}
+\end{figure}
+
+Many ($7/12$) participants also expressed a desire to organize claims into connected arguments during their session.
 Of these seven, we noticed that four would alternate between creating new snippets and organizing their claims in the claim browser (Section~\ref{claimbrowser}).
@@
 
-Most ($10/12$) either reused a topic that they had created themselves or that we had previously created.
-While the level of social activity was undoubtedly limited by the relatively small number of claims available in our database and the wide range of topics participants read about, three of the six people who browsed points in the
+Many ($6/12$) participants marked one claim as supporting another claim when in fact they should have both been marked as supporting a shared claim that needed to be created.
+For the final interface we tried to address this problem by making the graph structure of claims easier to visualize and making it easier to create new claims (Section~\ref{claimbrowser}).
 
-\subsection{Observations Motivating Design Changes}
+Two participants wanted to mark up a table as being a snippet and were unsure what claim they should say it made.
+In both cases, the table was a table of gold medals from the Beijing Olympics.
+We identified this as an area that we should investigate adding support for, since a table can provide evidence for the truth of many interesting claims.
 
-Many ($7/12$) participants also expressed the desire to organize snippets and points during their session.
-Of these seven, we noticed that four were alternating between creating snippets from new articles and organizing points in their {\it Recent Activity}: with each new snippet, users were creating relationships between points.
-When browsing web content about a particular topic or issue, most participants ($10/12$) either reused a topic that they created during their session or that someone else had created previously.
-Half of those ten used a topic that they {\it hadn't} created, demonstrating the ease of collaboration in our application.
-Both these organizational activities support connections inside the web of ideas.
-While the level of social activity was undoubtedly limited by the relatively small number of points (about $400$), three of the six people who browsed points in the main web interface looked at points created by other users.
-Two of the later study participants viewed someone else's point and either read the snippet text or viewed the originating document.
-As the number of points and topics increases, we expect to see more social behavior like this.
+One participant falsely connected claims that were actually referring to similar events that took place at different times rather than really being the same event.
+We identified the need for Think Link to provide more support for identifying the point in time that a claim or snippet is discussing.
 
-\subsection{Browsing Claims}
+Most ($9/12$) stated that they found the tool easy to use, and many ($5/12$) expressed an interest in using it during their normal browsing in its current state.
+When asked what they would want to use Think Link for, the most popular uses were helping them write a document ($5/12$), helping them form a personal opinion ($5/12$), or helping them argue a point to others ($5/12$).
+Many ($5/12$) were interested in seeing claims and snippets identified by their friends.
+Two said they were not interested in seeing what other people thought was interesting.
+Three users expressed an interest in using Think Link in ways that do not fit well with the current design, including gathering information about products they might buy, or finding cheap flights.
 
-\subsection{Creating Snippets}
+Due to the nature of the task, few ($3/12$) participants browsed pages that contained claims highlighted by other people, and so we were not able to evaluate how people reacted to seeing such highlights.
+This was made a priority of the second study.
+
+\todo{mention people not being sure how broad a topic should be}
+\todo{mention people creating claim in one topic and not being found in other related topics}
 
@@
 The purpose of the second study was to evaluate whether the interface changes we had made in reaction to the first study had made the tool usable.
-
-\subsection{Recruitment}
 
@@
 
-For the second study, we changed the task to focus on how easy users found it to use the interface, rather than on how they might apply it to their normal browsing.
-We told users nothing about how to use the tool.
-Instead, we just gave them a brief introduction to what our tool was for, and then asked them to attempt two tasks.
+In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it.
+We gave each user a brief introduction to the aims of the tool, and then asked them to perform two tasks with it.
 The first task was to look at a selection of web pages that already had highlights and tell them to explore the interface.
@@
 
+Unlike the first study, we specified the pages that our users should look at.
+This was because we wanted to see how users would react to seeing pages in which core claims had been marked up as snippets, and wanted to be sure that new snippets people identified had related claims in our database.
+
+Participants were shown an interface that is largely identical to that described in Section~\ref{interface}. All changes are described in the text below.
+
+\subsection{Findings}
+
+All the participants were very enthusiastic about the new interface.
+Most \howmany participants expressed a strong interest in being able to use the tool now.
+One user commented ``I can see myself getting quite addicted to this''.
+
+When shown a page with highlighted text, all users noticed that text had been highlighted and all users were able to infer that red highlight meant that the point was contentious.
+All users worked out that they could get more information about a claim by clicking on it.
+Most \howmany users did not immediately notice the presence of the margin button or the fact that Think Link had a margin feature, suggesting that the icon may need to be animated or perhaps made bigger.
+
+Several \howmany users were very enthusiastic about the ability to see when other users thought a claim on a page was contentious, and the ability to quickly navigate to contradictory arguments.
+One user commented ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
+
+The problems we had identified with the prototype interface seemed to have been fixed --- though, given the different demographics, we cannot state this conclusively.
+Everybody found it easy to tell what the ``open margin'' and ``new snippet'' buttons did.
+Nobody got confused between topics and claims.
+
+Users seemed to enjoy the process of browsing through the graph of claims, seeing what supporting and opposing arguments had been identified, and what snippets had been found about topics.
+
+Many ($4/6$) wanted to have a ``back'' button to help them navigate through the claim graph, but all users were comfortable navigating backwards once they noticed that the place they had come from was shown as a link at the top of the display.
+
+Most users \howmany still seemed to find the process of creating connections between existing claims confusing, at least at first.
+Several \howmany users tried to create a connection to an existing point by clicking on the \includegraphics[width=0.3cm]{../images/add.png} button, rather than by dragging the existing point over.
+This prompted us to display a message in this case (Figure~\ref{newdragmessage}).
+Most \howmany users did not not immediately realize that they could use drag and drop.
+This prompted us to add a prominent message at the top of the claim browser encouraging users to use drag and drop to organize claims and points.
+All users were able to successfully organize points and claims with drag and drop once they had realized that this is what they were supposed to do.
+
+Many users \howmany uncovered a bug in our new snippet window.
+They would navigate to an existing claim and then click the \includegraphics[width=0.3cm]{../images/add.png} button to create a new supporting or opposing claim.
+However they would then click ``Save'' before they had pressed return to create the new claim, with the result that their new snippet was attached to the selected claim rather than the new claim.
+This bug was easily fixed...
+
+One user said they wanted to be able to mark a claim on a web page as being wrong without having to find other snippets that argued against it.
+In future work we plan to offer such a feature by allowing users to say whether they believe a claim is true.
+
+\todo{quote collection}
+
 \section{Related Work}
+
+Think Link is influenced by previous work in a number of fields.
+Most notably, the idea of a collectively edited space in which people can create shared descriptions of topics is influenced by Wikis, the dynamic graph interface is influenced by mind mapping tools, the structuring of arguments as a graph is influenced by argumentation graphs, and the approach to gathering snippets from web pages is influenced by existing web clipping tools.
 
@@
 
-\subsection{Web Annotation}
+Wikis like Wikipedia~\cite{wikipedia} allow many authors to collaborate together to build a single shared document about a topic.
+Wikis thus achieve Think Links's goal of putting all information about a particular factual claim in one place, rather than scattering knowledge across a number of pages, each authored by a different writer.
+Indeed one can Think of Think Link as being a bit like a wiki in which all content is transcluded~\cite{transclusion} from existing sources and implicit links are added back from those sources to the wiki page to allow readers of other pages to easily see how they relate to arguments elsewhere.
 
-\subsection{Sensemaking}
+\subsection{Web Clipping and Annotation Systems}
+
+Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages.
+Several of Several of these tools also allow one to share one's collection of snippets with other people that one may be collaborating with.
+
+Many web clipping systems are also web annotation systems.
+Web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, DrawHere~\cite{drawhere}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add annotations to existing web pages and view annotations written by other people.
+Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents.
+More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
+
+Think Link takes a different approach to other web clipping and annotation tools by allowing a user to identify the factual claim that a snippet is making within a shared graph of related claims, and using this information to connect snippets based on what they are claiming to be true.
+While this extra level of structure makes the process of collecting snippets more cumbersome, the extra structure potentially makes snippets more useful.
+
+\subsection{User Contributed Links}
+
+In our existing web, links are created primarily by the authors of a document, rather than the readers.
+In Vannevir Bush's seminar MEMEX article~\cite{memex} he proposed a different architecture, in which links between documents were established by readers, according to the associations between them.
+As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''.
+Similar approaches have been taken by other hypertext systems including EQUIRE~\cite{enquire} and Everything2~\cite{everything2}.
+
+\subsection{Sensemaking Tools}
 
 \cite{scenthighlights}\cite{scenttrails}
+\cite{quotations}, \cite{quotationdl} Overall aim is to identify and connect ideas. Do quotation matching as a partial solution.
+
+\cite{scenthighlights}
+
+\cite{ideanavigation}, \cite{citesense}
 
@@
 
-\subsection{Identifying Ideas on the Web}
-
-\cite{quotations}, \cite{quotationdl} Overall aim is to identify and connect ideas. Do quotation matching as a partial solution.
-
-\cite{scenthighlights}
-
-\cite{ideanavigation}, \cite{citesense}
-
-\subsection{Web Annotation Systems}
-
-\cite{personalweb}
-
-Diigo lets you save, import, tag, highlight, mark up and share Web pages
-	select content on webpage
-	share bookmarked content; bookmark url and see what people have tagged on that page
-	search over collection of selected content
-	tag selected content; social tagging
-	see friends activity; more social behavior than necessary (eg. msging)
-	meet people ``like'' me?
-Stickis
-Fleck
-Shiftspace
-SharedCopy
-JKN
-MyStickies
-DrawHere
-
-- UIs for highlighting
-- wikipedia highlighting not trustworthy stuff
-
-\subsection{Web Clippings}
-
-Google Notebook
-Trailfire
-Zotero~\cite{zotero} is a citation mangament tool. Find and organise sources, while recording author, date etc by understanding pages. Can add notes to sources.
-Scrapbook~\cite{scrapbook}
-
 \subsection{Semantic Linking}
@@
 Shadows
-
-\subsection{User Contributed Links}
-
-Memex allowed users to describe their own paths between pages, rather than requiring the page authors to modify them.
-
-Everything2 creates soft-links between documents based on the browsing patterns of users.
-
-ENQUIRE contains bi-directional links that show who links to a document. TrackBack does the same.
 
@@
 
-\section{Observations Informing Design}
-
-\subsection{Recruitment}
-Our user study participants were selected from a pool of respondents to a Craigslist posting for people who use the internet as one of their primary sources of information, regularly gather and share this information, and are interested in a new application to facilitate that process.
-We chose participants based on their responses to the following questions:
-\begin{enumerate}
-	\item What topics or types of information do you usually look for on the internet?
-	\item How do usually go about finding information? (e.g. google, digg, friends, etc)
-	\item How do you organize the information you find? (e.g. text file, paper, wiki, etc)
-	\item How do you share information with others? (e.g. blog posts, comments, email, facebook, etc)
-\end{enumerate}
-We preferred individuals who search the internet for research and reading news rather than online shopping, as well as those interested in social and collaborative web activities like social networking web sites.
-We were also interested in those who seemed to express a need for our application: people who copy-and-paste text from web pages into word processing documents, or who regularly email web page addresses to friends.
-Twelve people were selected to participate in this study.
-
-\subsection{Study Environment}
-Each study session lasted between thirty to forty-five minutes, with the participant sitting at a desktop computer with the Firefox browser running the application plugin.
-The session was a Think-Aloud study in which the participant verbally describes his/her thoughts throughout the duration of the study.
-A video camera captured the audio/video and was focused on the monitor screen.
-Before the session began, we briefly demonstrated the features of the application: how to (1) select snippets, (2) write a snippet topic and point, (3) relate points, (4) show/hide the margin, and (5) browse recent activity.
-
-\subsection{Study Tasks}
-The study consisted of two tasks to collect snippets, each lasting ten to fifteen minutes.
-During both tasks, we asked participants to browse the web as they normally would.
-In the first task, the participant browses the web about a topic or issue of their choice from the domain of politics.
-The collection of snippets should help the participant either argue or form an opinion/perspective about the topic, and should be thought of being used to help him/her explain or discuss the topic with a friend.
-We constrained the first task to politics to increase the likelihood that the study participants would encounter similar issues and news stories.
-
-For the second task, the participant was allowed to browse for any topic of their choosing.
-While the likelihood of topic overlap across participants was much lower, we were able to observe their behavior when searching for information in which each person had genuine interest.
-
-At the conclusion of the session, we asked the participant if the application is something that would be likely to use, and for what purposes they would find it most useful.
-Any confusing features or experiences were also noted.
-
-\subsection{Observations and Discussion}
-% observed good and bad things
-% good things validate the application's usefulness and applicability
-% snippet selection super easy
-% organization part a little lacking
-% bad things we have ideas how to fix: UI redesign and smaller second study
-% not as much social stuff going on, but limited stuff in DB for overlap to happen (more social stuff towards end of study)
-
-{\it Note:} The first four study participants used a version of the web interface in which point relationships were constructed by navigating to one point page, searching for or typing the text of another point, and then expressing a directional relationship via a drop-down menu.
-We saw that participants found this process cumbersome and were less inclined to do it.
-Three of the four noted their confusion by the directional terms {\it supports} versus {\it is supported by}, and expressed a need for a more visual technique for constructing relationships.
-We modified the interface to allow users to drag and drop points on top of one another, with just the choice of {\it supports} and {\it opposes}.
-Half of the four participants were also confused by the Gmail-like labels alongside listed points that specified the topics each point belongs to.
-The interface was modified to show topics listed with their related points beneath them.
-The remainder of the study used the modified interface.
-
-%hopefully more social uses when have more stuff in database
-
-\subsubsection{Validating Observations?}
-In general, the user study demonstrated that our application successfully allows people to associate portions of web content with ideas, and to organize and share those ideas.
-All the study participants were able to create new snippets, and only a couple ($2/12$) had initial difficulty in correctly summarizing snippet text into a point.
-Most participants ($10/12$) were interested in viewing the margin as they were creating new snippets.
-These observations demonstrate that snippet creation is easy for most users.
-
-Many ($7/12$) participants also expressed the desire to organize snippets and points during their session.
-Of these seven, we noticed that four were alternating between creating snippets from new articles and organizing points in their {\it Recent Activity}: with each new snippet, users were creating relationships between points.
-When browsing web content about a particular topic or issue, most participants ($10/12$) either reused a topic that they created during their session or that someone else had created previously.
-Half of those ten used a topic that they {\it hadn't} created, demonstrating the ease of collaboration in our application.
-Both these organizational activities support connections inside the web of ideas.
-While the level of social activity was undoubtedly limited by the relatively small number of points (about $400$), three of the six people who browsed points in the main web interface looked at points created by other users.
-Two of the later study participants viewed someone else's point and either read the snippet text or viewed the originating document.
-As the number of points and topics increases, we expect to see more social behavior like this.
-
-% easy to create snippets and view margin
-% participants expressed desire to organize
-% saw social activity and browsing
-% (see more in usage types)
-% not as much social stuff going on, but limited stuff in DB for overlap to happen (more social stuff towards end of study)
-
-\subsubsection{Suggested Usage}
-Many of the study participants who said they would our application suggested uses that match those described in our motivation, validating our prescribed use cases.
-We identified the following use types, based on participant responses.
-Note that these many people suggested multiple use types.
-
-\textbf{Blogging and writing:} Snippet collections are useful when gathering evidence and supporting material for a blog entry, report, or any kind of written composition.
-This use case necessitates the ability to organize, order, and rearrange snippets to best tell a story, generate a persuasive argument, or facilitate forming an opinion.
-
-\textbf{Self-Bookmarking:} Creating snippets can be a means of bookmarking web page content that a user will return to for his/her own needs.
-These bookmarks are more specific than the web address of the page itself, and was suggested by users who currently find themselves cutting and pasting web content into a word processing file.
-This use case is more for retaining factual information than constructing an argument, although the information could also be used for the writing usage type.
-
-\textbf{Social:} Sharing snippets with friends or targeted interest groups allows users to see what web content is interesting to people they follow.
-This use case is applicable both to those who wish to collaboratively generate a collection of information and to those who like sharing and browsing information from friends.
-
-% Not for everyone! 3/12 people used it "incorrectly"
-Several of the study participants suggested specific use cases that mirror our initial motivation for the application.
-One example was a user who would use snippets to as supporting evidence for asserting the incorrectness of someone else's claim on a web forum, as simple comments are not as effective.
-Our application, however, is not for everyone.
-Three of the twelve user study participants used (or wanted to use) our application ``incorrectly,'' e.g.
-to compare airline flight prices.
-
-\section{Interaction Techniques}
-
-\subsection{Features}
-descriptions and screenshots: margin, snippet creation, relationship creation, web UI, point browser
-\begin{figure}[ht]
-	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
-	\caption{Snippet creation dialog}
-	\label{snippetdialog}
-\end{figure}
-
-\begin{figure}[ht]
-	\includegraphics[scale=0.3]{../screenshots/topicpage_sm.jpg}
-	\caption{Example topic page}
-	\label{topicpage}
-\end{figure}
-
-\subsection{Implementation Decisions}
-
-\idea{Wiki model not appropriate for points since want to manipulate several points at once}
-\idea{Need to visualize relationships in web of ideas}
-
-% \section{Creating Knowledge}
-% 
-% \section{Sharing Knowledge}
-% 
-% Why do users g
-% 
-% \section{Using Knowledge}
-% 
-% \section{Querying Data}
-
-\section{Preliminary User Feedback}
-
-1.5pp: recruitment, environment, tasks, observations, smaller study
-
-\subsubsection{User Interface Redesign}
-The first user study demonstrated a few flaws in the application's user interface. These problems can be generalized as:
-\begin{itemize}
-	\item \textbf{People need to easily visualize the the hierarchy of points, topics, and relationships.} A significant portion of the participants ($5/12$) explicitly expressed confusion about not being able to view the entire hierarchy of topics and points, and felt lost when looking at the individual point or topic pages.
-In this view, each point and topic is visually separated from its related points and topics, and thus users did not understand the significance of these individual pages.
-Viewing related points as lists of {\it child} and {\it parent} points was confusing to three of the eight people who used the second version of the UI.
-This ``flattened'' perspective also makes it difficult to relate several points to another.
-Most of the users who linked points together ($5/7$) did not recognize the need to first create an intermediate point and then relate other points to that new point.
-An easier model for grouping and associating objects together is necessary.
-	\item \textbf{People need better organization capabilities at snippet creation time.} Only a few ($3/12$) users went back to their {\it Recent Activity} to create additional topics when organizing, which suggests that a majority of users prefer to place snippets within topics when they are first created.
-However, if users are only allowed to assign a snippet to one topic without context of a topic hierarchy, they may create a very specific topic that is unlikely to be used by another person.
-We observed this behavior with two participants who both created snippets regarding a politician's controversial affair, but whose snippets did not belong to related topics.
-Several participants ($4/12$) remarked that they were unsure how broad a topic should be.
-By allowing users to create and traverse the topic hierarchy, they would be able to more easily organize and specify new topics when creating a snippet.
-\end{itemize}
-
-Our solution to these problems was to redesign the user interface to resemble the traditional file browser.
-The left-hand side shows the expandable/collapsable hierarchy and shortcut paths, while the right-hand side shows a content preview of the selected item from the left.
-For example, when a point is selected, the preview shows its snippets and related points.
-Snippet creation will resemble a \texttt{save as...} dialog where users can easily traverse the topic/point hierarchy, and create new topics inside existing ones as deemed necessary.
-This solution was implemented and used in a smaller user study. See section \ref{secondstudy}.
-
-\idea{remove confusion about ``where i am'' with fisheye view of current claim}
-
-\subsubsection{Second User Study}
-\label{secondstudy}
-There were six study participants who used the redesigned web interface.
-\studyresult{we solved organization difficulties with this redesign}
-
-%\section{Evaluation}
-
 \section{Future Work}

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
First draft of related work now completed

@@
 More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
+Perhaps the tool most similar to Think Link is SpinSpotter~\cite{spinspotter}, a tool that allows users to mark up newspaper articles to identify spin and factual inaccuracies.
 
@@
 
-In our existing web, links are created primarily by the authors of a document, rather than the readers.
-In Vannevir Bush's seminar MEMEX article~\cite{memex} he proposed a different architecture, in which links between documents were established by readers, according to the associations between them.
+In Vannevir Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them.
 As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''.
 Similar approaches have been taken by other hypertext systems including EQUIRE~\cite{enquire} and Everything2~\cite{everything2}.
+Think Link very much follows in this philosophy, the key difference being that Think Link structures its connections between documents using a graph of factual claims.
 
-\subsection{Sensemaking Tools}
+\subsection{Browsing Ideas}
 
-\cite{scenthighlights}\cite{scenttrails}
-\cite{quotations}, \cite{quotationdl} Overall aim is to identify and connect ideas. Do quotation matching as a partial solution.
+One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed.
+This is a goal that is shared with several other projects.
+Kolak and Schilit~\cite{quotations,quotationsdl} finds places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted.
+Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus.
+ScentHighlights~\cite{scenthighlights} identifies sections of text that you might find interesting and highlights them for you.
+ScentTrails~\cite{scenttrails} identifies links to documents that you might find interesting and makes them bigger.
+Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.
 
-\cite{scenthighlights}
-
-\cite{ideanavigation}, \cite{citesense}
+%\cite{citesense}
 
@@
 
-The 
-\cite{Korb97acognitive}
-\cite{toulmin}
-\cite{carneades}
-\cite{conceptmap}
-\cite{argmas}
+Argumentation Theory is a whole field in itself~\cite{argumentation,argmas} and much has been written about ways that one can represent arguments using a graph of connected claims.
+Popular argument representations include the Toulmin Model~\cite{toulmin}, and the Carneades Model~\cite{carneades}.
+Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model as they typically want to represent more of the logic of the argument, and perhaps even be able to do reasoning.
+Early versions of Think Link used a more complex model and we cut things down in order to make it easier for users to assemble claim graphs.
 
-Memex
-Vannevar 
-Bush's vision of Memex. Bush popularized the idea that 
-people can collaboratively organize and share knowledge: 
-``Wholly new forms of encyclopedias will appear, ready-made 
-with a mesh of associative trails running through them...'' 
-[5]. In many ways the vision has come to pass with large 
-amounts of hyper-linked information in the World Wide 
-Web, digital libraries, and online encyclopedias. However, 
-researchers continue to point out that people, especially 
-those lacking domain expertise, struggle to navigate infor- 
-mation spaces.
+One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numberical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.
 
-\subsection{Semantic Linking}
-
-\subsection{Social Bookmarking}
-
-Shadows
-
-\subsection{Automated Reasoning}
-
-Case-Based reasoning
-Sensemaking
+%\subsection{Automated Reasoning}
+%
+%Case-Based reasoning
+%Sensemaking
 

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
Added future work and conclusions

@@
 
-\section{Future Work}
-1p: social queries, NLP stuff
+\section{Limitations and Future Work}
+
+There are a number of issues that a widely released tool would need to address.
+Firstly, our current implementation has privacy issues.
+Every time one navigates to a web page, the plugin contacts our server and gives it the current URL so that it can check if there are snippets on that page.
+This information is anonymous, cacheable, and not logged, but it is still likely that some people would object to this information being given to an external server.
+
+At present, all claims have to be marked up by users who must not only identify the correct section of text to highlight, but also use a browsing interface to find the interesting claim that is being made.
+It would be interesting to see if natural language processing techniques could be used to either simplify the process of marking snippets, or even to detect snippets that make known claims without human intervention.
+
+While Think Link is influenced by Wikis, it does not currently have support for reverting bad edits made by previous users, or managing history in general.
+It will be interesting to see what interfaces work well for managing history, given that our data is a graph rather than a series of pages.
+
+Similarly, Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics.
+Since our graph and user base are currently small we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.
+
+We think it could be useful to use Think Link as a tool to suggest reading material.
+Just as tools like Digg suggest pages that you might like, Think Link could potentially suggest pages that contain claims that the user had not read and would be likely to find interesting.
 
 \section{Conclusions}
-$1/2$p
+
+We have introduced the concept of browsing the web of factual claims using Think Link.
+Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors.
+It allows users to identify contentious claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.
+
+On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or contraversial, and then using a wiki model to allow users to collaborate together to structure claims into an argument graph.
+
+We hope that Think Link will make it easier for people to be informed about the world and be exposed to factual claims that they might not otherwise be exposed to.
+
+\section{Acknowledgements}
+
+We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link.
 

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
More paper fleshing. Lots of nice figures and diagrams

@@
 \usepackage{color}
+\usepackage{wrapfig}
 \usepackage[pdftex]{hyperref}
@@
 
-Traditional web browsing consists of looking at pages and following links between pages; however when a user browses the web it is often not the pages themselves that they are looking for but the factual claims contained within those documents.
+Traditional web browsing consists of looking at pages and following links between pages; however when a user browses the web it is often not the pages themselves that they are looking for but the factual claims contained on those pages.
 A page may contain claims that are contradicted by other pages, or contain one interesting new claim, hidden in a sea of claims that the user has already read.
@@
 
-\begin{figure}[ht]
-	\includegraphics[width=8.5cm]{../screenshots/redhighlight.png}
-	\caption{Think Link highlights the key claims made by a page. Red means the claim is contentious.}
-	\label{highlight}
-\end{figure}
-
-\begin{figure}[ht]
-	\includegraphics[width=8.5cm]{../screenshots/sidebar3.png}
-	\caption{The margin shows a summary of the key claims made by the page}
-	\label{margin}
-\end{figure}
-
-\begin{figure}[ht]
-	\includegraphics[width=8.5cm]{../screenshots/claim_popup.png}
-	\caption{Click on a claim to see supporting or opposing evidence on other web pages}
-	\label{claimview}
-\end{figure}
-
 \section{Introduction}
@@
 If a user wants to find interesting factual claims about a topic then they may have to waste time reading claims that they have either read elsewhere or do not find interesting in order to find the claims that interest them.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
+	\caption{Key factual claims are highlighted}
+	\label{highlight}
+	\end{center}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/claim_popup_crop2.png}
+	\caption{Click on a claim to investigate evidence for and against}
+	\label{claimview}
+	\end{center}
+\end{figure}
 
@@
 While this makes it easier for add knowledge to the web, it makes it harder for users to extract factual claims from it.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/sidebar_crop.png}
+	\caption{The margin summarizes the key claims on the page}
+	\label{margin}
+	\end{center}
+\end{figure}
 
@@
 
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/bookmark_icons.png}
+	\caption{Icons used for Claims, Snippets, and Topics}
+	\label{bookmark_icons}
+	\end{center}
+\end{figure}
+
+%\begin{wrapfigure}{r}{4cm}
+%	\begin{center}
+%	\includegraphics[width=4cm]{../screenshots/bookmark_icons.png}
+%	\end{center}
+%\end{wrapfigure}
 \begin{itemize}
@@
 
-\subsection{Identifying factual claims on a page}
+\subsection{Exploring factual claims on a page}
 
@@
 
-\subsection{Identifying new factual claims}
-\label{newsnippet}
-
-\begin{figure}[t]
-	\includegraphics[width=8.5cm]{../screenshots/snipsave_full.png}
-	\caption{The claim selection window allows one to identify the claim a snippet is making}
-	\label{snipsavefull}
-\end{figure}
-
-\begin{figure}[t]
-	\includegraphics[width=8.5cm]{../screenshots/snipsave_crop.png}
-	\caption{Close up view of the claim selection window}
-	\label{snipsavecrop}
-\end{figure}
-
-If a user finds a snippet of text on a page that makes an interesting claim then they may want to enter it into Think Link.
-There are several reasons they may wish to do this.
-It may be that they find the snippet useful and may want to refer to it again in the future.
-It may be that they disagree with the claim, and want to alert other readers to the fact that there are opposing arguments, or it may be that they agree with the claim and want to provide easy access to evidence that backs it up.
-
-To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button.
-This is a similar approach to that taken clipping tools such as Google Notebook~\cite{googlenotebook}.
-
-Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making.
-To do this, Think Link presents the user with a ``claim selection'' window.
-This window contains a small version of the claim browser (Section~\ref{browseclaim}) that the user can use to select the claim that the snippet is making.
-At the bottom of the window, we show the phrase ``the snippet text {\it snippet} claims that {\it claim}''.
-We found that this helps users understand the nature of a claim and its relationship to a snippet (Section~\ref{study-claimmeaning}).
-
-Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics.
-Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one.
-Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim.
-To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to.
-For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim.
-
-This is an intentionally different model to that used by ad-hoc tag-based~\cite{tags} systems such as Delicious~\cite{delicious} and Flickr~\cite{flickr}.
-This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected.
-
-In earlier revisions of the interface it was very easy for users to quickly create new claim texts and awkward to find and reuse existing ones.
-This led users to create many claims that were essentially equivalent and reduced the utility of Think Link as a tool for connection snippets together (Section~\ref{study-reuse}).
-
-\todo{Make new snippet icon throb when something is selected}
-
 \subsection{Browsing factual claims}
@@
 
-\begin{figure}[ht]
+\begin{figure}[tb]
 	\includegraphics[width=8.5cm]{../screenshots/claimbrowse.png}
-	\caption{The Claim Browser}
+	\caption{The Claim Organizer contains two claim browsers}
 	\label{fig:claimbrowser}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
+	\caption{The Claim Browser Allows one to browse the argument graph}
+	\label{claimbrowse_diagram}
+	\end{center}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/claimbrowse_zoom.png}
+	\caption{Close up of a list of supporting claims}
+	\label{claimbrowse_zoom}
+	\end{center}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/fullbrowser.png}
+	\caption{The Enhanced claim browser adds additional controls}
+	\label{enhancedbrowser}
+	\end{center}
 \end{figure}
@@
 \end{itemize}
+
+\subsection{Identifying new factual claims}
+\label{newsnippet}
+
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=16cm]{../screenshots/newsnip_all.png}
+	\caption{Process for creating a new snippet}
+	\label{snipsavecrop}
+	\end{center}
+\end{figure*}
+
+%\begin{figure}[tb]
+%	\includegraphics[width=8.5cm]{../screenshots/snipsave_full.png}
+%	\caption{The claim selection window allows one to identify the claim a snippet is making}
+%	\label{snipsavefull}
+%\end{figure}
+
+\begin{figure}[tb]
+	\includegraphics[width=8.5cm]{../screenshots/snipsave_crop.png}
+	\caption{Close up view of the claim selection window}
+	\label{snipsavecrop}
+\end{figure}
+
+If a user finds a snippet of text on a page that makes an interesting claim then they may want to enter it into Think Link.
+There are several reasons they may wish to do this.
+It may be that they find the snippet useful and may want to refer to it again in the future.
+It may be that they disagree with the claim, and want to alert other readers to the fact that there are opposing arguments, or it may be that they agree with the claim and want to provide easy access to evidence that backs it up.
+
+To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button.
+This is a similar approach to that taken clipping tools such as Google Notebook~\cite{googlenotebook}.
+
+Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making.
+To do this, Think Link presents the user with a ``claim selection'' window.
+This window contains a small version of the claim browser (Section~\ref{browseclaim}) that the user can use to select the claim that the snippet is making.
+At the bottom of the window, we show the phrase ``the snippet text {\it snippet} claims that {\it claim}''.
+We found that this helps users understand the nature of a claim and its relationship to a snippet (Section~\ref{study-claimmeaning}).
+
+Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics.
+Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one.
+Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim.
+To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to.
+For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim.
+
+This is an intentionally different model to that used by ad-hoc tag-based~\cite{tags} systems such as Delicious~\cite{delicious} and Flickr~\cite{flickr}.
+This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected.
+
+In earlier revisions of the interface it was very easy for users to quickly create new claim texts and awkward to find and reuse existing ones.
+This led users to create many claims that were essentially equivalent and reduced the utility of Think Link as a tool for connection snippets together (Section~\ref{study-reuse}).
+
+\todo{Make new snippet icon throb when something is selected}
 
@@
 \begin{figure}[ht]
-	\includegraphics[width=8.5cm]{../screenshots/oldpoint_search.png}
+	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
 	\caption{Initial Prototype Claim Browser}

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
Status before Allison feedback. Minor changes to diagrams, intro, and related work

@@
 
-Traditional web browsing consists of looking at pages and following links between pages; however when a user browses the web it is often not the pages themselves that they are looking for but the factual claims contained on those pages.
-A page may contain claims that are contradicted by other pages, or contain one interesting new claim, hidden in a sea of claims that the user has already read.
+Conventional web browsing allows a user to look at pages and follow links between them; however when a user browses the web it is often not the pages themselves that they are looking for but  factual claims contained on those pages.
+A page may contain claims that are contradicted by other pages, or contain one interesting new claim hidden in a sea of claims that the user has already read.
 A user must thus invest significant effort extracting the claims that are accurate and interesting from the pages that they look at.
 
-We present Think Link, a tool that links pages to the factual claims that they make, and allows users to browse the web of factual claims, rather than the web of pages.
+We present Think Link, a tool that overlays a web of factual claims on top of the web of pages.
+If a snippet of text on a web page makes a factual claim then a user can use Think Link to connect that snippet to other places on the web that make related claims.
+We argue that this makes it easier for users to determine the truth of claims made on the web.
 
@@
 
-The web provides users with a huge number of pages they can read, but extracting useful factual information from these pages can be hard work.
-Not everything on the web is true.
-A web site may make claims that are contradicted by other web sites.
-If a user is to avoid incorrect claims then they will need to either stick to sources they can trust, or spend time looking for evidence on other web sites that supports or opposes what they have read.
-Similarly, not everything on the web is interesting.
-If a user wants to find interesting factual claims about a topic then they may have to waste time reading claims that they have either read elsewhere or do not find interesting in order to find the claims that interest them.
+The web provides users with a huge number of pages that they can read, but extracting useful and correct information from these pages can be difficult.
+Not everything on the web is true~\cite{bbcwebwarning}.
+If a user is to avoid incorrect factual claims then they will need to either stick to sources they can trust, or spend time looking for evidence on other web sites that supports or opposes what they have read.
+Similarly, a user will not find every claim on the web interesting.
+If a user is to locate claims that help them answer the questions they are interested in then they may have to spend considerable time reading claims that do not interest them in order to pick out those that do.
+Throughout this paper we will use the motivating example of a user who is worried about global warming and wants to find out what is going on and what they can do to help.
+Many web pages contain claims about global warming that are false, and many web pages repeat the same claims, making it difficult for a user to find interesting new facts that they were not previously aware of.
 
@@
 
+The difficulty of finding correct information on the web has been discussed a lot recently.
+Tim Berners Lee has expressed concern about the difficulty that people face discerning whether information on the web is true~\cite{bbcwebwarning}.
+Many people have also voiced concerns about how easily people can subvert Wikipedia to give peolpe false information~\cite{wikifalse}.
 Several commentators have observed that there is a Media Echo Chamber effect~\cite{echochamber,echochamber2} in which news sources report claims that they have heard from other news sources, despite the fact that these claims may be misleading or untrue.
 If a user only reads news sources from a particular group then they may only be exposed to the views of that group and may not be aware that opposing views exist unless they actively seek them.
-Tim Berners Lee has expressed concern about the difficulty that people face discerning whether information on the web is true~\cite{bbcwebwarning}.
 
-Part of the problem is that traditional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them.
-While a web page will typically contain links to other pages, as chosen by the page author, it does not provide an easy way for a user to validate whether the claims made by a page are supported by evidence that may be available on other pages.
+Part of the problem is that conventional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them.
+While a web page will typically contain links provided by the author of the page, these typically only reference a small proportion of the other pages that discuss the topic and are unlikely to include sources that disagree with the author.
+If the user wants to find all the
+
  Moreover the best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web.
@@
 
-Think Link uses collaborative filtering~\cite{collaborativefilter} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim.
+Think Link uses collaborative filtering~\cite{collective} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim.
 If a user finds a snippet or claim interesting then they can mark it as such.
@@
 
-Think Link presents users with three kinds of object, each associated with a different family of icons:
+Think Link presents users with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}):
 
@@
 If the user finds the snippet interesting and wants to use it later then they can bookmark it by clicking the bookmark icon that pops up when they mouse over the margin note.
-This will cause it to be displayed prominently in the claim browser (Section~\ref{browseclaims}).
+This will cause it to be displayed prominently in the claim browser (Section~\ref{claimbrowser}).
 If the user believes the snippet to not be making the claim that it says it does or otherwise badly marked up then they can delete the snippet by clicking on the trash can icon on the margin note.
-If the user thinks the claim is interesting and wants to see how it relates to claims made by other snippets on the web then they can click on either the highlighted text or the margin note to open the claim browser (Section~\ref{browseclaims}).
+If the user thinks the claim is interesting and wants to see how it relates to claims made by other snippets on the web then they can click on either the highlighted text or the margin note to open the claim browser (Section~\ref{claimbrowser}).
 
@@
 \subsection{Browsing factual claims}
-\label{browseclaim}
+\label{browseclaim}\label{claimbrowser}
 
@@
 \item {\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page. (Figure~\ref{claimview})
-\item {\bf The Claim Selection Window} shows one claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making. (Figure~\ref{snipsavefull}) 
+\item {\bf The Claim Selection Window} shows one claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making. (Figure~\ref{snipsavecrop}) 
 \end{itemize}
@@
 	\caption{Process for creating a new snippet}
-	\label{snipsavecrop}
+	\label{createprocess}
 	\end{center}
@@
 \begin{figure}[tb]
-	\includegraphics[width=8.5cm]{../screenshots/snipsave_crop.png}
-	\caption{Close up view of the claim selection window}
+	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram.png}
+	\caption{Selecting the claim made by a new snippet}
 	\label{snipsavecrop}
@@
 
+Wikipedia's greatest strength is also its greatest weakness.
+Since anyone can edit Wikipedia, there is always the danger that the information one reads could be incorrect~\cite{wikifalse}.
+Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect}, but it is difficult to remove the problem entirely.
+While Think Link also allows anyone to edit its argument graph, all snippets come from known sources, making it easier to see where claims have come from and whether trustworthy sources agree with them.
+
 \subsection{Web Clipping and Annotation Systems}

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
Beginnings of reactions to Allison Feedback

@@
 	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
-	\caption{Key factual claims are highlighted}
-	\label{highlight}
-	\end{center}
-\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/claim_popup_crop2.png}
+	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
 	\caption{Click on a claim to investigate evidence for and against}
@@
 Part of the problem is that conventional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them.
-While a web page will typically contain links provided by the author of the page, these typically only reference a small proportion of the other pages that discuss the topic and are unlikely to include sources that disagree with the author.
-If the user wants to find all the
+While a web page will typically contain links to other articles, these typically only reference a small proportial of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author.
+The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web.
+The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages).
+While this makes it easier for add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.
 
- Moreover the best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web.
-The web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages).
-While this makes it easier for add knowledge to the web, it makes it harder for users to extract factual claims from it.
+In this paper we present Think Link (Figure~\ref{claimview}), a tool that overlays a new set of links over the existing web that connects passages of text that make related factual claims.
+As a user browses the web they will see factual claims highlighted, in yellow or red, with red meaning that there is evidence that the claim being made is false.
+A user can click on a highlighted claim and easily navigate to other pages on the web that make related factual claims.
+
+\section{Related Work}
+
+Think Link is influenced by previous work in a number of fields.
+Most notably, the idea of a collectively edited space in which people can create shared descriptions of topics is influenced by Wikis, the dynamic graph interface is influenced by mind mapping tools, the structuring of arguments as a graph is influenced by argumentation graphs, and the approach to gathering snippets from web pages is influenced by existing web clipping tools.
+
+\subsection{Wikis}
+
+Wikis like Wikipedia~\cite{wikipedia} allow many authors to collaborate together to build a single shared document about a topic.
+Wikis thus achieve Think Links's goal of putting all information about a particular factual claim in one place, rather than scattering knowledge across a number of pages, each authored by a different writer.
+Indeed one can Think of Think Link as being a bit like a wiki in which all content is transcluded~\cite{transclusion} from existing sources and implicit links are added back from those sources to the wiki page to allow readers of other pages to easily see how they relate to arguments elsewhere.
+
+Wikipedia's greatest strength is also its greatest weakness.
+Since anyone can edit Wikipedia, there is always the danger that the information one reads could be incorrect~\cite{wikifalse}.
+Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect}, but it is difficult to remove the problem entirely.
+While Think Link also allows anyone to edit its argument graph, all snippets come from known sources, making it easier to see where claims have come from and whether trustworthy sources agree with them.
+
+\subsection{Web Clipping and Annotation Systems}
+
+Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages.
+Several of Several of these tools also allow one to share one's collection of snippets with other people that one may be collaborating with.
+
+Many web clipping systems are also web annotation systems.
+Web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, DrawHere~\cite{drawhere}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add annotations to existing web pages and view annotations written by other people.
+Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents.
+More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
+Perhaps the tool most similar to Think Link is SpinSpotter~\cite{spinspotter}, a tool that allows users to mark up newspaper articles to identify spin and factual inaccuracies.
+
+Think Link takes a different approach to other web clipping and annotation tools by allowing a user to identify the factual claim that a snippet is making within a shared graph of related claims, and using this information to connect snippets based on what they are claiming to be true.
+While this extra level of structure makes the process of collecting snippets more cumbersome, the extra structure potentially makes snippets more useful.
+
+\subsection{User Contributed Links}
+
+In Vannevir Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them.
+As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''.
+Similar approaches have been taken by other hypertext systems including EQUIRE~\cite{enquire} and Everything2~\cite{everything2}.
+Think Link very much follows in this philosophy, the key difference being that Think Link structures its connections between documents using a graph of factual claims.
+
+\subsection{Browsing Ideas}
+
+One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed.
+This is a goal that is shared with several other projects.
+Kolak and Schilit~\cite{quotations,quotationsdl} finds places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted.
+Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus.
+ScentHighlights~\cite{scenthighlights} identifies sections of text that you might find interesting and highlights them for you.
+ScentTrails~\cite{scenttrails} identifies links to documents that you might find interesting and makes them bigger.
+Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.
+
+%\cite{citesense}
+
+\subsection{Argumentation Theory}
+
+Argumentation Theory is a whole field in itself~\cite{argumentation,argmas} and much has been written about ways that one can represent arguments using a graph of connected claims.
+Popular argument representations include the Toulmin Model~\cite{toulmin}, and the Carneades Model~\cite{carneades}.
+Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model as they typically want to represent more of the logic of the argument, and perhaps even be able to do reasoning.
+Early versions of Think Link used a more complex model and we cut things down in order to make it easier for users to assemble claim graphs.
+
+One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numberical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.
+
+%\subsection{Automated Reasoning}
+%
+%Case-Based reasoning
+%Sensemaking
+
+%\subsection{Argumentation Graphs}
+%Argumentation graphs express positions and arguments in a formal graph model as nodes and edges, respectively, and are typically used to make a decision or draw a conclusion about some issue.
+One example implementation is the {\it Zeno} argumentation framework~\cite{zeno}, designed for collaborative use in mediation systems to debate the quality of alternative solutions for a problem.
+In their object model of argumentation elements, based on Rittel's IBIS model~\cite{ibis}, example nodes include pro/con arguments, positions, preferences, comments, and decisions.
+Importantly, arguments are connected via {\it consequent} and {\it antecedent} edges, which are used to inform {\it choices}.
+The decision-making power of the argumentation graph follows from the traversal of argument relationships to enhance the depth and breadth of understanding about an issue.
+Our application similarly links claims as {\it supporting} and {\it opposing} other claims to allow users to develop a cohesive understanding of arguments.
+%
+%Traditional argumentation graphs are designed to solve a specific, isolated issue.
+Our application supports an ever-expanding set of topics, and arguments can form links between multiple topics.
+Users can consult the web of ideas directly to form an opinion about a particular issue, but they can also browse for new issues to explore.
+Opinions or decisions in our model don't have to be static: as the topic is expanded with more supporting and opposing evidence, users may alter previous viewpoints.
+Another advantage of our model is that the ability to explore claims' source-document evidence is built right into the navigation.
+Looking at an argument shows both its related argument as well as its supporting {\it snippets}, allowing the user to explore the evidence for himself.
+
+\section{The Think Link System}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
+	\caption{Key factual claims are highlighted}
+	\label{highlight}
+	\end{center}
+\end{figure}
 
@@
 
-\subsection{Browse the Web of Factual Claims}
-
-We have created a tool called Think Link that connects pages on the web to the factual claims being made on those pages, and allows a user to quickly find snippets of text on other web pages that make supporting or opposing claims.
+Think Link that connects pages on the web to the factual claims being made on those pages, and allows a user to quickly find snippets of text on other web pages that make supporting or opposing claims.
 We hope that this tool will make it easier for users to identify incorrect claims in documents they read, and to quickly identify the best arguments for and against claims that they may be interested in.
@@
 
-\section{Investigative Study}
+\section{User Studies}
 
-We performed two ``think aloud'' studies to guide and evaluate the development of Think Link.
-The aim of the first study was to see how users normally browse the web and to see how they might try to use an initial prototype of Think Link to help them.
+We performed two qualitative ``think aloud'' user studies to guide the development of Think Link.
 
-We recruited 12 paid participants.
+The aim of the first study was to see how users normally browse the web and how they might go about using Think Link to identify snippets in the pages they browse.
+The aim of the second study was to evaluate changes made to the interface as a result of the first study and see how people react to browsing pages that have interesting claims highlighted.
+
+\subsection{Procedure for the First Study}
+
+For the first study we recruited 12 paid participants.
 Five were female, seven were male.
@@
 
-\subsection{Protocol for the First Study}
-
 Study sessions took approximately 45 minutes.
-Participants were seated at a single-screen workstation with the Firefox browser, augmented with the Think Link plugin.
-We first demonstrated Think Link's interface, and then asked them to perform two tasks.
-In the first task, we asked them to use Think Link to gather information about a political topic that was of interest to them and currently in the news.
-For the second task, we asked them to browse the web in a way that would typically do so at home or at work, and see if they could use Think Link to help them do so.
-
-In the second task, we wanted to leave users relatively unconstrained so that we could see how users might try to use a tool like this during their normal browsing, rather than how well they could accomplish a pre-set task that they might never attempt in normal life.
-For the first task, we constrained the task to an a topic for which we had already marked up a number of claims, to increase the likelyhood that users would encounter existing claims.
-
-The focus of this study was on whether people would be able to gather snippets on the web and structure them into a coherent argument graph, rather than on how they would react when they browsed to a page where an argument had already been identified - which was one of the focusses of our second study.
+Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link plugin.
+We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they found interesting and connect those claims to the existing claim graph.
+For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelyhood that there would be existing claims about the topic they were browsing.
 
 In this initial study, users were exposed to the prototype interface shown in Figures~\ref{oldsnippetbox} and \ref{oldbrowser}, rather than the final interface described in Section~\ref{interface}.
+We discuss some of the key differences in the findings section.
+
+\subsection{Procedure for the Second Study}
+
+For the second study, we recruited 6 paid participants.
+Four were female and two were male.
+Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students.
+Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviours.
+
+In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it.
+We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
+The first task was to look at a selection of web pages that already had highlights and explore the interface while thinking aloud about what they saw.
+The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated our database with.
+Participants were shown an interface that is largely identical to that described in Section~\ref{interface}.
 
 \subsection{Findings}
+
+In this section we present the findings from our two users studies. Findings from the two studies are presented together and clustered by topic.
+
+\subsubsection{High-Level Impressions}
+
+Response was generally positive, with some participants being very keen to use the tool soon.
+One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it becomes publically available.
+Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
+
+Participants liked the ability to see when other pages disagreed with the claim they were looking at.
+One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
+
+\subsubsection{Usability}
+
+Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version. None of these problems re-occured during the second study.
+
+Most participants in the first study, and all participants in the second study were able to get competent with the tool.
+Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
+
+\idea{first study confused between claims and topic}
+\idea{felt disoreintated by the fact that the interface used for saving snippets was different from the interface used for browsing them}
+
+ere able to get competent with the tool.
+
+\subsubsection{Snippet Creation Strategies}
+
+\idea{selecting the first paragraph}
+
+\idea{selecting a table}
+
+\idea{wanted to have the same snippet make several claims}
+
+\subsubsection{Claim Creation Strategies}
+
+\idea{not sure how specific a claim should be}
+
+\idea{several wanted to be able to use the text they had selected as the claim, particularly when no relevant claims existed}
+
+\idea{Need for topics - Ronnie Wood}
+
+\subsubsection{Claim Connection Strategies}
+
+\idea{confused when needed to make an intermediate claim}
+\idea{wanted to say ``related'' and didn't realize this was what topics were for. When told them they agreed that this was what they wanted}
+\idea{connecting same event at different times}
 
@@
 
-\section{Related Work}
-
-Think Link is influenced by previous work in a number of fields.
-Most notably, the idea of a collectively edited space in which people can create shared descriptions of topics is influenced by Wikis, the dynamic graph interface is influenced by mind mapping tools, the structuring of arguments as a graph is influenced by argumentation graphs, and the approach to gathering snippets from web pages is influenced by existing web clipping tools.
-
-\subsection{Wikis}
-
-Wikis like Wikipedia~\cite{wikipedia} allow many authors to collaborate together to build a single shared document about a topic.
-Wikis thus achieve Think Links's goal of putting all information about a particular factual claim in one place, rather than scattering knowledge across a number of pages, each authored by a different writer.
-Indeed one can Think of Think Link as being a bit like a wiki in which all content is transcluded~\cite{transclusion} from existing sources and implicit links are added back from those sources to the wiki page to allow readers of other pages to easily see how they relate to arguments elsewhere.
-
-Wikipedia's greatest strength is also its greatest weakness.
-Since anyone can edit Wikipedia, there is always the danger that the information one reads could be incorrect~\cite{wikifalse}.
-Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect}, but it is difficult to remove the problem entirely.
-While Think Link also allows anyone to edit its argument graph, all snippets come from known sources, making it easier to see where claims have come from and whether trustworthy sources agree with them.
-
-\subsection{Web Clipping and Annotation Systems}
-
-Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages.
-Several of Several of these tools also allow one to share one's collection of snippets with other people that one may be collaborating with.
-
-Many web clipping systems are also web annotation systems.
-Web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, DrawHere~\cite{drawhere}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add annotations to existing web pages and view annotations written by other people.
-Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents.
-More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
-Perhaps the tool most similar to Think Link is SpinSpotter~\cite{spinspotter}, a tool that allows users to mark up newspaper articles to identify spin and factual inaccuracies.
-
-Think Link takes a different approach to other web clipping and annotation tools by allowing a user to identify the factual claim that a snippet is making within a shared graph of related claims, and using this information to connect snippets based on what they are claiming to be true.
-While this extra level of structure makes the process of collecting snippets more cumbersome, the extra structure potentially makes snippets more useful.
-
-\subsection{User Contributed Links}
-
-In Vannevir Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them.
-As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''.
-Similar approaches have been taken by other hypertext systems including EQUIRE~\cite{enquire} and Everything2~\cite{everything2}.
-Think Link very much follows in this philosophy, the key difference being that Think Link structures its connections between documents using a graph of factual claims.
-
-\subsection{Browsing Ideas}
-
-One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed.
-This is a goal that is shared with several other projects.
-Kolak and Schilit~\cite{quotations,quotationsdl} finds places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted.
-Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus.
-ScentHighlights~\cite{scenthighlights} identifies sections of text that you might find interesting and highlights them for you.
-ScentTrails~\cite{scenttrails} identifies links to documents that you might find interesting and makes them bigger.
-Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.
-
-%\cite{citesense}
-
-\subsection{Argumentation Theory}
-
-Argumentation Theory is a whole field in itself~\cite{argumentation,argmas} and much has been written about ways that one can represent arguments using a graph of connected claims.
-Popular argument representations include the Toulmin Model~\cite{toulmin}, and the Carneades Model~\cite{carneades}.
-Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model as they typically want to represent more of the logic of the argument, and perhaps even be able to do reasoning.
-Early versions of Think Link used a more complex model and we cut things down in order to make it easier for users to assemble claim graphs.
-
-One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numberical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.
-
-%\subsection{Automated Reasoning}
-%
-%Case-Based reasoning
-%Sensemaking
-
-\subsection{Argumentation Graphs}
-Argumentation graphs express positions and arguments in a formal graph model as nodes and edges, respectively, and are typically used to make a decision or draw a conclusion about some issue.
-One example implementation is the {\it Zeno} argumentation framework~\cite{zeno}, designed for collaborative use in mediation systems to debate the quality of alternative solutions for a problem.
-In their object model of argumentation elements, based on Rittel's IBIS model~\cite{ibis}, example nodes include pro/con arguments, positions, preferences, comments, and decisions.
-Importantly, arguments are connected via {\it consequent} and {\it antecedent} edges, which are used to inform {\it choices}.
-The decision-making power of the argumentation graph follows from the traversal of argument relationships to enhance the depth and breadth of understanding about an issue.
-Our application similarly links claims as {\it supporting} and {\it opposing} other claims to allow users to develop a cohesive understanding of arguments.
-
-Traditional argumentation graphs are designed to solve a specific, isolated issue.
-Our application supports an ever-expanding set of topics, and arguments can form links between multiple topics.
-Users can consult the web of ideas directly to form an opinion about a particular issue, but they can also browse for new issues to explore.
-Opinions or decisions in our model don't have to be static: as the topic is expanded with more supporting and opposing evidence, users may alter previous viewpoints.
-Another advantage of our model is that the ability to explore claims' source-document evidence is built right into the navigation.
-Looking at an argument shows both its related argument as well as its supporting {\it snippets}, allowing the user to explore the evidence for himself.
-
 \section{Limitations and Future Work}

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
Re-did the user study findings. Improved some figures.

@@
 \section{Interaction Techniques}
+\label{interface}
 
@@
 \begin{figure}[tb]
-	\includegraphics[width=8.5cm]{../screenshots/claimbrowse.png}
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/claimbrowse.png}
 	\caption{The Claim Organizer contains two claim browsers}
 	\label{fig:claimbrowser}
+	\end{center}
 \end{figure}
@@
 \end{figure}
-
 \begin{figure}[tb]
@@
 
-Response was generally positive, with some participants being very keen to use the tool soon.
+Response was generally positive, with many participants being very keen to use the tool soon.
 One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it becomes publically available.
@@
 
-Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version. None of these problems re-occured during the second study.
+Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version.
+None of these problems re-occured during the second study.
+We discuss some of these changes in the sections below.
 
-Most participants in the first study, and all participants in the second study were able to get competent with the tool.
+Most participants in the first study, and all participants in the second study were able to use the tool competently.
 Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
+Particpants in the second study said they found the tool ``very intuitive''.
 
-\idea{first study confused between claims and topic}
-\idea{felt disoreintated by the fact that the interface used for saving snippets was different from the interface used for browsing them}
+\subsubsection{Browsing the Argument Graph}
 
-ere able to get competent with the tool.
+%In the first study, several participants reported that they felt ``disorientated'' when browsing through the idea graph.
+%
+%Several participants in the second study seemed to enjoy the action of browsing through ideas.
 
-\subsubsection{Snippet Creation Strategies}
+\subsubsection{Creating a Snippet}
 
-\idea{selecting the first paragraph}
+Users would often encounter a snippet that could be interpreted as making several interesting claims, and were unsure about what to do in such circumstances.
+Sometimes users would deal with this by writing a compound claim like ``Global Warming will cause X and Y''.
+While users could mark up the same snippet as making multiple claims, users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.
 
-\idea{selecting a table}
+One special case of this was that several users wanted to mark up a table as a snippet.
+A table can usually be considered to be making several interesting claims and users were often confused about what they should say the table cliams.
+Our current guidance is that one should mark up a table as making the most interesting claims that that table makes.
+In other cases, a user wanted to mark up an image as a snippet.
+While Think Link does not currently support this, it might make sense to allow this if an interesting claim can be inferred from the image.
 
-\idea{wanted to have the same snippet make several claims}
+Some users expressed an interest in marking up a snippet as a primary source rather than a claim.
+For example they might find the text of an important speech or an Olympic results table.
+Several expressed a desire to have a new class of object that was neither a topic nor a claim, but instead just ``an interesting object relavent to this topic''.
 
-\subsubsection{Claim Creation Strategies}
+Many users would consistently mark the first paragraph of an article as a snippet.
+This paragraph would frequently summarise the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.
 
-\idea{not sure how specific a claim should be}
+\subsubsection{Chosing a Claim for a Snippet}
 
-\idea{several wanted to be able to use the text they had selected as the claim, particularly when no relevant claims existed}
-
-\idea{Need for topics - Ronnie Wood}
-
-\subsubsection{Claim Connection Strategies}
-
-\idea{confused when needed to make an intermediate claim}
-\idea{wanted to say ``related'' and didn't realize this was what topics were for. When told them they agreed that this was what they wanted}
-\idea{connecting same event at different times}
-
-All the participants were able to create new snippets.
-Participants had little difficulty identifying interesting claims being made by web pages, selecting appropriate sections of text, and either picking existing claims that were appropriate, or writing appropriate new claims.
-Most ($9/12$) stated that they found it easy to create new snippets and associate them with claims.
-In the initial interface snippets were only highlighted when the margin was open.
-This confused some participants ($5/12$) who were surprised to not see their snippets highlighted when they created them.
-In the final interface, we addressed this problem by always highlighting snippets.
-
-In the initial interface the button to open the margin was on the toolbar, next to the ``new snippet'' button.
-This led some participants ($4/12$) to get confused about which they should use in each case.
-In the final interface, we addressed this problem by putting the margin button on the side of the page, with a chevron to indicate that it will pull out a margin (Figure~\ref{marginpull}).
-
-\begin{figure}[ht]
-	\includegraphics[width=8.5cm]{../screenshots/snippetdialog_sm.jpg}
-	\caption{First Prototype Snippet Creation Dialog}
+\begin{figure}[t]
+	\includegraphics[width=8.5cm]{../screenshots/oldsnipcreate_diagram.png}
+	\caption{Initial Prototype Snippet Creation Dialog}
 	\label{oldsnippetbox}
@@
 
-Most ($7/12$) users got confused between topics and claims at some point, either entering a topic as a claim, or entering a claim as a topic.
-We felt that this was partly because the snippet creation interface (Figure~\ref{oldsnippetbox}) gave the user little impression of how their snippet would appear in the claim browser.
-In the final interface we addressed this problem by giving the snippet creation interface the same core UI as the claim browser interface (Section~\ref{newsnippet}).
-We also decided to change our name for a factual claim from ``point'' to ``claim''.
+We found that participants using this initial interface felt disorientated by the fact that the interface for creating snippets was different to the interface used for visualizing them.
+Participants would often confuse claims and topics, either entering a claim in the topic box, or a topic in the claim box.
+Several participants expressed confusion about the difference between the two.
+Participants would also often create new points and topics when appropriate points and topics already existed in the claim graph, even when the suggestion list was drawing their attention to a topic or claim that would have been appropriate.
 
-While most ($10/12$) reused a topic that they had created or someone else had created, many ($6/12$) had a tendency to ignore the suggestion box and type new claims rather than looking for existing claims that might be a good match for their snippet.
-For the final interface, we tried to encourage users to reuse existing claims rather than writing new ones by making it easier to browse existing claims from the snippet creation window, and requiring users to click a \includegraphics[width=0.3cm]{../images/add.png} button in order to create a new claim (Section~\ref{newsnippet}).
+For the second study, we used the interface described in Section~\ref{newsnippet}, which uses the same claim browser interface used for exploring the claim graph.
+We found that users of this interface had no difficulty distinguishing between claims and topics and were much more likely to reuse existing claims and topics.
+We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.
 
-Our initial interface for claim browsing (Figure~\ref{oldbrowser}) caused several ($5/12$) to remark that they felt they were confused about where they were in the claim graph.
-This interface had a separate page for each claim or topic, rather than animating between them, making it easy to lose track of ones position in the graph of points.
-Several ($2/12$) remarked that part of the problem was that it wasn't obvious that the various boxes on the page were information about the claim in large text.
-For the final interface we addressed this problem by using animation to maintain a sense of where things were when the focus changed, and by placing information about a point around that point rather than in separate boxes (Section~\ref{claimbrowser}).
+Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one.
+For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information?
 
-All users had some difficulty connecting existing claims together.
-The first four participants were a different interface in which new connections were made by clicking on an ``add'' button, and then typing the name of the claim into an auto-complete box.
-Users found this approach difficult as it required them to remember the text of claims that they had seen recently.
-In light of this, after the first four participants we switched to a drag and drop interface (Figure~\ref{oldbrowser}).
+Several users also expressed an interest in being able to use the text of the snippet they selected as the text of its claim, particularly for short snippets.
+We intentionally made this a little difficult to do in an attempt to encourage users to find existing claims that are appropriate, however this may have been a mistake as it also increases the amount of effort required to create a snippet.
 
-The drag and drop interface worked better.
-Most ($7/8$) users were eventually able to use the new interface proficiently.
-However all users initially found the drag and drop interface confusing, and no users guessed that they could connect existing points using drag and drop.
-We identified this as an area needing improvement in the next interface revision.
+\subsubsection{Connecting Claims}
+
+Many participants expressed a desire to organize claims into connected arguments during their session.
+
+Some users incorrectly marked one claim as supporting another when in fact they should have both been marked as supporting a third claim that needed to be created, or where an intermediate claim was needed.
+For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing environmental problems''.
+Users realized that the claims were related, but did not immediately recognize that they needed to create new claims in order to structure the relationship correctly.
+It is possible that creating correct logical claim structures may just be too difficult for some people.
+We hope that, if Think Link was deployed more widely many of the intermediate claims that were needed would already have been created and this problem would be reduced.
+
+Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship.
+For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''.
+Similarly, many users expressed a desire to mark claims as being ``related'' without supporting or opposing each other.
+For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''.
+Our current advice in such circumstances is to use topics to group claims that are related.
+For example these claims could all be in a topic called ``America and the Kyoto Protocol''.
+Participants seemed comfortable with the idea of relating claims in this way when we pointed it out to them, but most participants needed to be told that this was a strategy they could use.
+
+Several users got confused by claims that referred to similar events at different points in time.
+For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written.
+This is a particular problem when talking about breaking news events, where what claims are true can change fast.
+If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the {\it time} at which a claim was asserted to be true.
 
@@
 \end{figure}
-
-Many ($7/12$) participants also expressed a desire to organize claims into connected arguments during their session.
-Of these seven, we noticed that four would alternate between creating new snippets and organizing their claims in the claim browser (Section~\ref{claimbrowser}).
-With each new claim, users would create relationships between existing claims.
-
-Many ($6/12$) participants marked one claim as supporting another claim when in fact they should have both been marked as supporting a shared claim that needed to be created.
-For the final interface we tried to address this problem by making the graph structure of claims easier to visualize and making it easier to create new claims (Section~\ref{claimbrowser}).
-
-Two participants wanted to mark up a table as being a snippet and were unsure what claim they should say it made.
-In both cases, the table was a table of gold medals from the Beijing Olympics.
-We identified this as an area that we should investigate adding support for, since a table can provide evidence for the truth of many interesting claims.
-
-One participant falsely connected claims that were actually referring to similar events that took place at different times rather than really being the same event.
-We identified the need for Think Link to provide more support for identifying the point in time that a claim or snippet is discussing.
-
-Most ($9/12$) stated that they found the tool easy to use, and many ($5/12$) expressed an interest in using it during their normal browsing in its current state.
-When asked what they would want to use Think Link for, the most popular uses were helping them write a document ($5/12$), helping them form a personal opinion ($5/12$), or helping them argue a point to others ($5/12$).
-Many ($5/12$) were interested in seeing claims and snippets identified by their friends.
-Two said they were not interested in seeing what other people thought was interesting.
-Three users expressed an interest in using Think Link in ways that do not fit well with the current design, including gathering information about products they might buy, or finding cheap flights.
-
-Due to the nature of the task, few ($3/12$) participants browsed pages that contained claims highlighted by other people, and so we were not able to evaluate how people reacted to seeing such highlights.
-This was made a priority of the second study.
-
-\todo{mention people not being sure how broad a topic should be}
-\todo{mention people creating claim in one topic and not being found in other related topics}
-
-\section{Evaluation Study}
-
-The purpose of the second study was to evaluate whether the interface changes we had made in reaction to the first study had made the tool usable.
-
-We recruited 6 paid participants.
-Four were female and two were male.
-Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students.
-Since the second group was different demographically to the first group, it is not possible to make a direct comparison between their behaviours.
-However we were still able to make interesting observations about how users used the new interface.
-
-\subsection{Study Protocol}
-
-In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it.
-We gave each user a brief introduction to the aims of the tool, and then asked them to perform two tasks with it.
-The first task was to look at a selection of web pages that already had highlights and tell them to explore the interface.
-The second task was to identify claims on a page that had not been marked up and connect them appropriately to existing claims.
-
-Unlike the first study, we specified the pages that our users should look at.
-This was because we wanted to see how users would react to seeing pages in which core claims had been marked up as snippets, and wanted to be sure that new snippets people identified had related claims in our database.
-
-Participants were shown an interface that is largely identical to that described in Section~\ref{interface}. All changes are described in the text below.
-
-\subsection{Findings}
-
-All the participants were very enthusiastic about the new interface.
-Most \howmany participants expressed a strong interest in being able to use the tool now.
-One user commented ``I can see myself getting quite addicted to this''.
-
-When shown a page with highlighted text, all users noticed that text had been highlighted and all users were able to infer that red highlight meant that the point was contentious.
-All users worked out that they could get more information about a claim by clicking on it.
-Most \howmany users did not immediately notice the presence of the margin button or the fact that Think Link had a margin feature, suggesting that the icon may need to be animated or perhaps made bigger.
-
-Several \howmany users were very enthusiastic about the ability to see when other users thought a claim on a page was contentious, and the ability to quickly navigate to contradictory arguments.
-One user commented ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
-
-The problems we had identified with the prototype interface seemed to have been fixed --- though, given the different demographics, we cannot state this conclusively.
-Everybody found it easy to tell what the ``open margin'' and ``new snippet'' buttons did.
-Nobody got confused between topics and claims.
-
-Users seemed to enjoy the process of browsing through the graph of claims, seeing what supporting and opposing arguments had been identified, and what snippets had been found about topics.
-
-Many ($4/6$) wanted to have a ``back'' button to help them navigate through the claim graph, but all users were comfortable navigating backwards once they noticed that the place they had come from was shown as a link at the top of the display.
-
-Most users \howmany still seemed to find the process of creating connections between existing claims confusing, at least at first.
-Several \howmany users tried to create a connection to an existing point by clicking on the \includegraphics[width=0.3cm]{../images/add.png} button, rather than by dragging the existing point over.
-This prompted us to display a message in this case (Figure~\ref{newdragmessage}).
-Most \howmany users did not not immediately realize that they could use drag and drop.
-This prompted us to add a prominent message at the top of the claim browser encouraging users to use drag and drop to organize claims and points.
-All users were able to successfully organize points and claims with drag and drop once they had realized that this is what they were supposed to do.
-
-Many users \howmany uncovered a bug in our new snippet window.
-They would navigate to an existing claim and then click the \includegraphics[width=0.3cm]{../images/add.png} button to create a new supporting or opposing claim.
-However they would then click ``Save'' before they had pressed return to create the new claim, with the result that their new snippet was attached to the selected claim rather than the new claim.
-This bug was easily fixed...
-
-One user said they wanted to be able to mark a claim on a web page as being wrong without having to find other snippets that argued against it.
-In future work we plan to offer such a feature by allowing users to say whether they believe a claim is true.
-
-\todo{quote collection}
 

### 2008-09-19 papers/web_of_ideas/web_of_ideas.tex
Started making Tye changes

@@
 \usepackage{wrapfig}
+% \usepackage{picins}
+% \usepackage{floatflt}
 \usepackage[pdftex]{hyperref}
@@
 
-Conventional web browsing allows a user to look at pages and follow links between them; however when a user browses the web it is often not the pages themselves that they are looking for but  factual claims contained on those pages.
+Conventional web browsers allow a user to look at pages and follow links between them; however when a user browses the web it is often not the pages themselves that they are looking for but claims about the world that are contained on those pages.
 A page may contain claims that are contradicted by other pages, or contain one interesting new claim hidden in a sea of claims that the user has already read.
-A user must thus invest significant effort extracting the claims that are accurate and interesting from the pages that they look at.
+If a user is to form an accurate opinion about a topic then they may have to spend considerable time gathering information from many disconnected pages scattered across the web.
 
-We present Think Link, a tool that overlays a web of factual claims on top of the web of pages.
+We present Think Link, a tool that overlays a network of factual claims on top of the existing web.
 If a snippet of text on a web page makes a factual claim then a user can use Think Link to connect that snippet to other places on the web that make related claims.
-We argue that this makes it easier for users to determine the truth of claims made on the web.
+We argue that this allows users to more easily find information that will help them understand a topic, evaluate whether a claim is true, and see the range of opinions expressed on the web.
 
@@
 
-The web provides users with a huge number of pages that they can read, but extracting useful and correct information from these pages can be difficult.
-Not everything on the web is true~\cite{bbcwebwarning}.
-If a user is to avoid incorrect factual claims then they will need to either stick to sources they can trust, or spend time looking for evidence on other web sites that supports or opposes what they have read.
+The web provides users with a huge number of pages that they can read, but extracting useful and reliable information from these pages can be difficult.
+Not everything on the web is accurate~\cite{bbcwebwarning}.
+If a user is to avoid being mislead by false claims then they will need to either stick to sources they can trust, or spend time looking for evidence on other web sites that supports or opposes what they have read.
 Similarly, a user will not find every claim on the web interesting.
@@
 	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
-	\caption{Click on a claim to investigate evidence for and against}
+	\caption{Click on a claim to investigate evidence for and against it}
 	\label{claimview}
@@
 
-In this paper we present Think Link (Figure~\ref{claimview}), a tool that overlays a new set of links over the existing web that connects passages of text that make related factual claims.
-As a user browses the web they will see factual claims highlighted, in yellow or red, with red meaning that there is evidence that the claim being made is false.
-A user can click on a highlighted claim and easily navigate to other pages on the web that make related factual claims.
+In this paper we present Think Link, a tool that overlays a new network of links over the existing web, connecting snippets of text to snippets elsewhere on the web that make related claims.
+Think Link maintains a central shared ``claim graph'' (Figure~\ref{summarygraph}) containing claims made on the web, their supporting and opposing relationships to each other, and the snippets that make these claims.
+When a user views a web page, Think Link highlights snippets that have been identified as making factual claims, with the highlight color indicating whether other sources have been found that disagree with the claim.
+If a user clicks on such a snippet then they will see a ``claim browser'' (Figure~\ref{claimview}) that allows them to see other claims made on the web that support or oppose the claim the snippet makes, and snippets elsewhere on the web that make these other claims.
+
+The Think Link claim graph is editable by all users, in a manner similar to a wiki.
+Any user can add new claims, connect existing claims together, and identify snippets on web pages that make specific claims.
+Collaborative filtering is used to filter out junk or abusive information, while minimizing the danger of politification.
+
+Not everyone will necessarily want a tool like Think Link.
+Some people may be looking for confirmation of their own points of view rather than information that challenges their beliefs.
+We hope however that Think Link may be able to make some contribution to helping peolpe find out about other points of view, and help people more easily find the most interest claims about topics they are interested in.
+
+The contributions of this paper are the presentation of a new approach for connecting information on the web, the design of a user interface that makes it easy for users to find claims that support and oppose claims that they read on the web, and a qualitative user study of how participants use such an interface.
 
@@
 
-Think Link is influenced by previous work in a number of fields.
-Most notably, the idea of a collectively edited space in which people can create shared descriptions of topics is influenced by Wikis, the dynamic graph interface is influenced by mind mapping tools, the structuring of arguments as a graph is influenced by argumentation graphs, and the approach to gathering snippets from web pages is influenced by existing web clipping tools.
+Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}.
+Like Think Link, wikis allow users to find information organised by topic rather than author and allow users to collaborate together to bring together all the best information about a topic.
+Wikipedia's greatest strength is arguable also it's greatest weakness.
+Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}.
+Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2}, but it is difficult to remove the problem entirely.
+While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious.
+Think Link tries to avoid this problem by linking claims back to the original sources that made these claims.
+Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim.
+Another key difference is that Think Link pulls allows users to provide links from the external web into its graph of claims, thus allowing readers to evaluate the truth of claims they read on arbitrary web pages rather than having to restrict their browsing to a single wiki site.
 
-\subsection{Wikis}
+SpinSpotter~\cite{spinspotter} shares Think Link's goal of allowing users to identify misleading and innaccurate information on web pages that they read.
+If a user sees a section of text that they think is misleading then they can mark it up, causing it to be highlighted when other users view the same page.
+While Think Link and SpinSpotter both share the goal of letting users mark up snippets that may be inaccurate, they differ in what they let users find out about such snippets.
+SpinSpotter allows users to give a textual description of why the snippet is spin and a suggested edit that would make it more accurate.
+ThinkLink instead connects the snippet to its global claim graph, allowing users to quickly access evidence for and against the truth of the claim.
+There is alos a difference in the nature of what SpinSpotter and Think Link expect users to mark up.
+Think Link is interested in evaluating the truth of factual claims, while SpinSpotter also interested in identifying biased phrases (e.g.
+``tree hugger'').
 
-Wikis like Wikipedia~\cite{wikipedia} allow many authors to collaborate together to build a single shared document about a topic.
-Wikis thus achieve Think Links's goal of putting all information about a particular factual claim in one place, rather than scattering knowledge across a number of pages, each authored by a different writer.
-Indeed one can Think of Think Link as being a bit like a wiki in which all content is transcluded~\cite{transclusion} from existing sources and implicit links are added back from those sources to the wiki page to allow readers of other pages to easily see how they relate to arguments elsewhere.
+Other web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add their own annotations to existing web pages and view annotations written by other people.
+Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents.
+More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
+We are not aware of any such system that links web pages to a graph of factual claims.
 
-Wikipedia's greatest strength is also its greatest weakness.
-Since anyone can edit Wikipedia, there is always the danger that the information one reads could be incorrect~\cite{wikifalse}.
-Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect}, but it is difficult to remove the problem entirely.
-While Think Link also allows anyone to edit its argument graph, all snippets come from known sources, making it easier to see where claims have come from and whether trustworthy sources agree with them.
-
-\subsection{Web Clipping and Annotation Systems}
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/summary_graph.png}
+	\caption{Think link connects claims to each other and to web snippets}
+	\label{summarygraph}
+	\end{center}
+\end{figure}
 
 Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages.
-Several of Several of these tools also allow one to share one's collection of snippets with other people that one may be collaborating with.
-
-Many web clipping systems are also web annotation systems.
-Web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, DrawHere~\cite{drawhere}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add annotations to existing web pages and view annotations written by other people.
-Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents.
-More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
-Perhaps the tool most similar to Think Link is SpinSpotter~\cite{spinspotter}, a tool that allows users to mark up newspaper articles to identify spin and factual inaccuracies.
-
-Think Link takes a different approach to other web clipping and annotation tools by allowing a user to identify the factual claim that a snippet is making within a shared graph of related claims, and using this information to connect snippets based on what they are claiming to be true.
-While this extra level of structure makes the process of collecting snippets more cumbersome, the extra structure potentially makes snippets more useful.
-
-\subsection{User Contributed Links}
+Many web clipping tools are also web annotation systems.
 
@@
 As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''.
-Similar approaches have been taken by other hypertext systems including EQUIRE~\cite{enquire} and Everything2~\cite{everything2}.
-Think Link very much follows in this philosophy, the key difference being that Think Link structures its connections between documents using a graph of factual claims.
-
-\subsection{Browsing Ideas}
+Several more recent systems have allowed user to add links to existing pages.
+ENQUIRE~\cite{enquire} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it.
+Everything2~\cite{everything2} links each page to the most popular pages that users viewed at the same time.
+Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making.
 
@@
 
-%\cite{citesense}
-
-\subsection{Argumentation Theory}
-
-Argumentation Theory is a whole field in itself~\cite{argumentation,argmas} and much has been written about ways that one can represent arguments using a graph of connected claims.
-Popular argument representations include the Toulmin Model~\cite{toulmin}, and the Carneades Model~\cite{carneades}.
-Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model as they typically want to represent more of the logic of the argument, and perhaps even be able to do reasoning.
-Early versions of Think Link used a more complex model and we cut things down in order to make it easier for users to assemble claim graphs.
-
+Much work has been done on the idea of using a graph to represent an argument~\cite{argumentatino,argmas}.
+Popular argument models include the Toulmin Model~\cite{toulmin}, the Carneades Model~\cite{carneades}, and the IBIS model~\cite{ibis}.
+Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model, with the result that they provide a more accurate model of the logical argument, at the cost of requiring more skill to assemble.
 One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numberical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.
@@
 	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
-	\caption{Key factual claims are highlighted}
+	\caption{Hovering over a highlighted snippet shows a summary}
 	\label{highlight}
@@
 
+Think Link is a tool that overlays a web of factual claims on the existing web (Figure~\ref{summarygraph}).
+As a user browses the web, Think Link highlightes snippets of text that have been identified as making factual claims.
+If a user clicks on a highlighted snippet then Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}).
+Our intention is that Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.
+
+Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}).
+This graph is managed like a Wiki, allowing any user to add new claims or snippets.
+As a user browses the web, they can identify snippets that make claims that are interesting or contraversion and link them into the global claim graph.
+Think Link is implemented as a FireFox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.
+
+\subsection{Exploring factual claims on a page}
+
+When a user browses a web page, we want to make them aware of claims being made on the page that they might find interesting, or that other sources disagree with.
+Think Link draws attention to the factual claims that other users have identified on a web page by highlighting them (Figure~\ref{highlight}).
+Snippets are highlighted in red if they are contentious (other sources disagree with the claim).
+The highlight colors are chosen such as to be pale enough to not impede reading, but dark enough to be noticeable.
+A user can see what claim a snippet is making by hovering their mouse over the snippet (Figure~\ref{highlight}).
+
 \begin{figure}[tb]
 	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/sidebar_crop.png}
+	\includegraphics[width=6cm]{../screenshots/sidebar_diagram.png}
 	\caption{The margin summarizes the key claims on the page}
@@
 
-Think Link that connects pages on the web to the factual claims being made on those pages, and allows a user to quickly find snippets of text on other web pages that make supporting or opposing claims.
-We hope that this tool will make it easier for users to identify incorrect claims in documents they read, and to quickly identify the best arguments for and against claims that they may be interested in.
-
-As a user browses a web page Think Link will highlight snippets of text that make factual claims (Figure~\ref{highlight}).
-If a factual claim is contentious (meaning that other pages make opposing claims) then the highlight will be red.
-More information about highlighted claims can be found by either mousing over one of them, or opening the Think Link margin (Figure~\ref{margin}).
-
-These highlighted claims serve as entry points to a browsable graph of factual claims.
-Clicking on a claim will pop up a window that allows one to easily view the other claims that support or oppose the selected claim, and the snippets of text on the web that make these claims (Figure~\ref{claimview}).
-
-For example, if a user browsed a web page that claimed ``Global Warming does not exist'', then the text snippet that made this claim would be highlighted in red, indicating the fact that there are web pages elsewhere that make opposing claims.
+If a user thinks a claim is interesting and wants to know what other sources say about it then they can open up a ``claim browser'' window (Figures~\ref{claimview} and \ref{claimbrowse_diagram}) by clicking on the highlighted snippet.
+The claim browser allows the user to easily view claims that support or oppose the selected claim, and the snippets of text on the web that make these claims (Figure~\ref{claimview}).
+For example, if a user browsed a web page that claimed ``Global Warming does not exist'', then the snippet that made this claim would be highlighted in red, indicating that there are web pages elsewhere that make opposing claims.
 If the user were to click on the highlighted snippet then an ``investigate claim'' window would appear.
@@
 If the user navigated to this new claim then they could quickly see the best claims that support the existence of global warming, and would be able to see summaries of the best sources that supported these claims.
+
+%\begin{floatingfigure}{2cm}
+%\includegraphics[width=2cm]{../screenshots/marginpull_out.png}
+%\end{floatingfigure}
+
+\begin{wrapfigure}{r}[0.5cm]{2cm}
+\includegraphics[width=2cm]{../screenshots/marginpull_out.png}
+\end{wrapfigure}
+If the current page contains snippets then a tab appears in the top left corner of the window.
+The tab contains a lightbulb whose color changes according to the nature of the snippets on the page - red if a snippet contains a contentious claim.
+This allows a user to quickly tell if a page contains something of interest without having to scroll down.
+Clicking on the tab opens the margin.
+The margin provides a summary of all the intersting claims that users have identified on the current page and is designed to mimick the traditional margin notes that readers often write on physical documents~\cite{marginalia}.
+To emphasise the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.
+
+We found that when a participant sees a highlighted snippet, they will typically want to do one of four things: ignore it, remember it, delete it, or investigate it.
+If the user finds the snippet interesting and wants to use it later then they can bookmark it by clicking the bookmark icon that pops up when they mouse over the margin note.
+This will cause it to be displayed prominently in the claim browser.
+If the user believes the snippet to not be making the claim that it says it does or otherwise badly marked up then they can delete the snippet by clicking on the trash can icon on the margin note.
+If the user thinks the claim is interesting and wants to see how it relates to claims made by other snippets on the web then they can click on the highlighted text or the margin note to open the claim browser.
+
+\subsection{The Mental Model}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=7cm]{../screenshots/bookmark_icons.png}
+	\caption{Icons used for Claims, Snippets, and Topics}
+	\label{bookmark_icons}
+	\end{center}
+\end{figure}
+
+Think Link users interact with three kinds of object, each of which is associated with a different family of icons (Figure~\ref{bookmark_icons}):
+
+\begin{itemize}
+\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false.
+For example ``Global warming is man made''.
+A claim may support or oppose other claims.
+Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
+\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim.
+Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
+\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about.
+For example ``Global Warming'', or ``Computer Science''.
+A claim can have one or more topics that it is about, and a topic can have one or more more general topics.
+Topics are used both to organize, and to disambiguate claims.
+For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''.
+Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
+\end{itemize}
+
+Varients of these three icons are used consistently when refering to these three object types. 
+Yellow versions of these icons are used to identify claims, folders, or snippets that the user has marked as interesting (by clicking on their icon).
+
+Colors are also used to indicate the extent to which a claim is supported or opposed by other claims.
+Red means that a claim is opposed by other claims, and green means that a claim is supported by other claims and not opposed by any.
+The colors are chosen to fit with people's normal associations with colors, where red is commonly associated with danger (e.g.
+a traffic light) and yellow is the standard color used for highlighter pens.
 
@@
 
-\subsection{The Mental Model}
-
-Think Link presents users with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}):
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/bookmark_icons.png}
-	\caption{Icons used for Claims, Snippets, and Topics}
-	\label{bookmark_icons}
-	\end{center}
-\end{figure}
-
-%\begin{wrapfigure}{r}{4cm}
-%	\begin{center}
-%	\includegraphics[width=4cm]{../screenshots/bookmark_icons.png}
-%	\end{center}
-%\end{wrapfigure}
-\begin{itemize}
-\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false.
-For example ``Global warming exists''.
-A claim may support or oppose other claims.
-Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and are not understood logically by Think Link.
-\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a particular web site that asserts or assumes the truth of a particular claim.
-Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
-\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about.
-For example ``Global Warming'', or ``Computer Science''.
-A claim can have one or more topics that it is about, and a topic can have one or more more general topics.
-Topics are used both to organize, and to disambiguate claims.
-For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''.
-Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
-\end{itemize}
-
-The three icons are used consistently when refering to these three object types. 
-Yellow versions of these icons (\includegraphics[width=0.3cm]{../images/lightbulb.png},\includegraphics[width=0.3cm]{../images/folder.png},\includegraphics[width=0.3cm]{../images/comment_yellow.png}) are used to identify claims, folders, or snippets that the user has marked as interesting.
+It is important to avoid political fights, where two competing sides delete claims, snippets, or connections that they disagree with.
+Similarly, it is important to avoid vandalism, where people abuse people with competing beliefs by adding abuse claims or snippets.
+While we do not have a perfect solution to this problem, our current approach is to treat deletion as a special case of collaborative filtering.
+A claim or snippet will only be deleted if many people vote to delete it and very few people bookmark it.
 
@@
 
-\studyresult{Quotes of users saying why they would use it}
-
-\subsection{Contributions}
-
-We believe that this work makes the following key contributions:
-
-\begin{itemize}
-\item We propose a new approach to browsing web pages that focusses on the factual claims made by these articles
-\item We develop interaction techniques that make it easy for a user to browse the web through factual claims
-\end{itemize}
-
 \section{Interaction Techniques}
@@
 Think Link will draw attention to interesting claims on pages that the user browses; it allows the user to identify new factual claims on pages they browse; it allows them to browse the graph of related claims and identify the strongest evidence supporting or opposing the claims they are looking at; and it allows them to organize the claim graph by making new connections between existing claims and topics.
-
-\subsection{Exploring factual claims on a page}
-
-When a user browses a web page, we want to make them aware of claims being made on the page that they might find interesting, or that other sources disagree with.
-Think Link draws attention to the factual claims that other users have identified on a web page by highlighting them (Figure~\ref{highlight}).
-Snippets are highlighted in red if they are contenious (other sources disagree with the claim), or yellow otherwise.
-The highlight colors are chosen such as to be pale enough to not impede reading, but dark enough to be noticeable.
-The colors are chosen to fit with people's normal associations with colors, where red is commonly associated with danger (e.g.
-a traffic light) and yellow is the standard color used for highlighter pens.
-
-While a highlight lets the user know that a the snippet is making an interesting or contentious claim, the user may still wonder what claim the snippet has been identified as making.
-A snippet could be interpreted as asserting the truth of several claims.
-For example the phrase ``Alice and Bob live in Canada'' asserts both that Alice lives in Canada and that Bob lives in Canada.
-Similarly, a user may have eroneously marked a snippet as asserting a claim that it does not directly assert to be true.
-For example ``Alice and Bob live together''.
-
-There are two ways that a user can identify the claims being made by the highlighted snippet; they can either hover their mose over a particular snippet to show information about that snippet (Figure~\ref{highlight}, or they can use the Think Link margin to show information about all snippets on the page (Figure~\ref{margin}).
-
-The Think Link Margin is designed to mimick the traditional margin notes that readers often write on physical documents they are reading~\cite{marginalia}.
-A margin space is added to the left of the page containing a margin note for each snippet.
-Each margin note is aligned vertically with the claim it is about and contains the text of the claim.
-To emphasise the connection between a margin note and its associated snippet, a snippet is highlighted more strongly when the user mouses over the associated margin note (Figure~\ref{margin}).
-
-We found that when a participant sees a highlighted snippet, they will typically want to do one of four things: ignore it, remember it, delete it, or investigate it.
-If the user finds the snippet interesting and wants to use it later then they can bookmark it by clicking the bookmark icon that pops up when they mouse over the margin note.
-This will cause it to be displayed prominently in the claim browser (Section~\ref{claimbrowser}).
-If the user believes the snippet to not be making the claim that it says it does or otherwise badly marked up then they can delete the snippet by clicking on the trash can icon on the margin note.
-If the user thinks the claim is interesting and wants to see how it relates to claims made by other snippets on the web then they can click on either the highlighted text or the margin note to open the claim browser (Section~\ref{claimbrowser}).
-
-A user can also use the margin to provide a quick overview of a document.
-They can scroll quickly through the document and look to see what key claims other users have marked in the margins.
-Several users remarked on how useful it was when reading a long document to be able to quickly scan through it and see what other users have thought were the most interesting points.
-\studyresult{put in some quotes}
-
-\todo{sort out more consistent colors and icons between this view and the web view}
-\todo{give the margin consistent colors with the highlight sections}
-\todo{more nice zoomed-in screenshots showing the different interaction techniques}
 
@@
 
-The placement of objects above and below is intended to emphasize the conventional structuring of an argument graph (Section~\ref{argumentgraph}), with topics going upwards and arguments for and against a claim going downwards.
+The placement of objects above and below is intended to emphasize the conventional structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
 A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
@@
 Other objects appear and disapper by smoothly sliding into or out of view.
-We found that this animation helps users retain a sense of where they are with respect to what they were looking at previously and helps users avoid getting lost (Section~\ref{gettinglost}).
+We found that this animation helps users retain a sense of where they are with respect to what they were looking at previously and helps users avoid getting lost.
 
@@
 To do this, Think Link presents the user with a ``claim selection'' window.
-This window contains a small version of the claim browser (Section~\ref{browseclaim}) that the user can use to select the claim that the snippet is making.
+This window contains a small version of the claim browser that the user can use to select the claim that the snippet is making.
 At the bottom of the window, we show the phrase ``the snippet text {\it snippet} claims that {\it claim}''.
-We found that this helps users understand the nature of a claim and its relationship to a snippet (Section~\ref{study-claimmeaning}).
+We found that this helps users understand the nature of a claim and its relationship to a snippet.
 
@@
 In earlier revisions of the interface it was very easy for users to quickly create new claim texts and awkward to find and reuse existing ones.
-This led users to create many claims that were essentially equivalent and reduced the utility of Think Link as a tool for connection snippets together (Section~\ref{study-reuse}).
+This led users to create many claims that were essentially equivalent and reduced the utility of Think Link as a tool for connection snippets together.
 
@@
 
-In this initial study, users were exposed to the prototype interface shown in Figures~\ref{oldsnippetbox} and \ref{oldbrowser}, rather than the final interface described in Section~\ref{interface}.
+In this initial study, users were exposed to the prototype interface shown in Figures~\ref{oldsnippetbox} and \ref{oldbrowser}, rather than the final interface described earlier in this paper.
 We discuss some of the key differences in the findings section.
@@
 The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated our database with.
-Participants were shown an interface that is largely identical to that described in Section~\ref{interface}.
+Participants were shown an interface that is largely identical to that described earlier in this paper.
 
@@
 
+Several users expressed an interest in being able to mark a claim as contraversial without having to create an opposing claim.
+One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
+In the future we are planning to implement a social voting system to allow users to say what claims they believe are false and see what claims their friends agreed or disagreed with.
+
 \begin{figure}[ht]

### 2008-09-19 papers/web_of_ideas/web_of_ideas.tex
Made changes suggested by Tye

@@
 
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/summary_graph.png}
+	\caption{Think link connects claims to each other and to web snippets}
+	\label{summarygraph}
+	\end{center}
+\end{figure}
+
 In this paper we present Think Link, a tool that overlays a new network of links over the existing web, connecting snippets of text to snippets elsewhere on the web that make related claims.
@@
 Like Think Link, wikis allow users to find information organised by topic rather than author and allow users to collaborate together to bring together all the best information about a topic.
-Wikipedia's greatest strength is arguable also it's greatest weakness.
+Wikipedia's greatest strength is arguably also its greatest weakness.
 Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}.
-Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2}, but it is difficult to remove the problem entirely.
+Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2,wikicorrect3}, but it is difficult to remove the problem entirely.
 While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious.
@@
 Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim.
-Another key difference is that Think Link pulls allows users to provide links from the external web into its graph of claims, thus allowing readers to evaluate the truth of claims they read on arbitrary web pages rather than having to restrict their browsing to a single wiki site.
+
+When a topic is heavily politicized, Wikipedia can be subject to edit wars in which people who hold one opinion delete opinions held by the other side~\cite{wikicorrect3}, making it difficult for the community to collaborate together to produce a document that is both comprehensive and unbiased.
+Think Link attempts to avoid this problem by taking an ``append-only, collaborative filtering'' approach.
+A user cannot remove claims that they disagree with\footnote{With special exceptions for dealing with spam and abuse}.
+Instead all they can do is vote against them, and connect them to claims that provide opposing evidence.
+
+Another key difference between Think Link and a Wiki is that Think Link pulls the whole web into its graph of connected claims.
+A user can use Think Link to investigate claims they read on arbitrary web sites, without having to restrict their browsing to a single wiki site.
 
@@
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/summary_graph.png}
-	\caption{Think link connects claims to each other and to web snippets}
-	\label{summarygraph}
-	\end{center}
-\end{figure}
-
 Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages.
 Many web clipping tools are also web annotation systems.
+These tools are designed for gathering and sharing interesting information, rather than for identifying the claims being made, or allowing users to navigate to related claims being made on other sites.
 
@@
 Everything2~\cite{everything2} links each page to the most popular pages that users viewed at the same time.
-Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making.
+Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making and allowing users to browse this graph, rather than just allowing users to specify links between pages.
 
@@
 This is a goal that is shared with several other projects.
-Kolak and Schilit~\cite{quotations,quotationsdl} finds places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted.
+Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted.
 Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus.
@@
 Think Link is a tool that overlays a web of factual claims on the existing web (Figure~\ref{summarygraph}).
-As a user browses the web, Think Link highlightes snippets of text that have been identified as making factual claims.
+As a user browses the web, Think Link highlights snippets of text that have been identified as making factual claims.
 If a user clicks on a highlighted snippet then Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}).
@@
 As a user browses the web, they can identify snippets that make claims that are interesting or contraversion and link them into the global claim graph.
+
 Think Link is implemented as a FireFox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.
@@
 Snippets are highlighted in red if they are contentious (other sources disagree with the claim).
-The highlight colors are chosen such as to be pale enough to not impede reading, but dark enough to be noticeable.
+The highlight colors are chosen to be pale enough to not impede reading, dark enough to be noticeable\footnote{Unless the background is close to a highlight color.
+Think Link does not yet adapt to different page background colors}, and different enough to be distinguishable by colorblind people.
 A user can see what claim a snippet is making by hovering their mouse over the snippet (Figure~\ref{highlight}).
@@
 If a user thinks a claim is interesting and wants to know what other sources say about it then they can open up a ``claim browser'' window (Figures~\ref{claimview} and \ref{claimbrowse_diagram}) by clicking on the highlighted snippet.
-The claim browser allows the user to easily view claims that support or oppose the selected claim, and the snippets of text on the web that make these claims (Figure~\ref{claimview}).
+The claim browser allows the user to easily view claims that support or oppose the selected claim, and find snippets of text on the web that make these claims (Figure~\ref{claimview}).
 For example, if a user browsed a web page that claimed ``Global Warming does not exist'', then the snippet that made this claim would be highlighted in red, indicating that there are web pages elsewhere that make opposing claims.
-If the user were to click on the highlighted snippet then an ``investigate claim'' window would appear.
-This window would show that the claim ``Global Warming does not exist'' is opposed by the claim ``There is strong evidence for global warming''.
+If the user were to click on the highlighted snippet then an ``investigate claim'' window would appear (Figure~\ref{claimview}).
+This window would show the user that the claim ``Global Warming does not exist'' is opposed by the claim ``There is strong evidence for global warming''.
 If the user navigated to this new claim then they could quickly see the best claims that support the existence of global warming, and would be able to see summaries of the best sources that supported these claims.
@@
 
-\begin{wrapfigure}{r}[0.5cm]{2cm}
+\begin{wrapfigure}{r}[0.3cm]{2cm}
 \includegraphics[width=2cm]{../screenshots/marginpull_out.png}
@@
 If the current page contains snippets then a tab appears in the top left corner of the window.
-The tab contains a lightbulb whose color changes according to the nature of the snippets on the page - red if a snippet contains a contentious claim.
-This allows a user to quickly tell if a page contains something of interest without having to scroll down.
+The tab contains a lightbulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim.
+This allows a user to quickly tell if a page contains something of interest without having to scroll through the whole page.
 Clicking on the tab opens the margin.
-The margin provides a summary of all the intersting claims that users have identified on the current page and is designed to mimick the traditional margin notes that readers often write on physical documents~\cite{marginalia}.
+The margin provides a summary of all the interesting claims that users have identified on the current page and is designed to mimick the traditional margin notes that readers often write on physical documents~\cite{marginalia}.
 To emphasise the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.
-
-We found that when a participant sees a highlighted snippet, they will typically want to do one of four things: ignore it, remember it, delete it, or investigate it.
-If the user finds the snippet interesting and wants to use it later then they can bookmark it by clicking the bookmark icon that pops up when they mouse over the margin note.
-This will cause it to be displayed prominently in the claim browser.
-If the user believes the snippet to not be making the claim that it says it does or otherwise badly marked up then they can delete the snippet by clicking on the trash can icon on the margin note.
-If the user thinks the claim is interesting and wants to see how it relates to claims made by other snippets on the web then they can click on the highlighted text or the margin note to open the claim browser.
 
@@
 	\begin{center}
-	\includegraphics[width=7cm]{../screenshots/bookmark_icons.png}
+	\includegraphics[width=7cm]{../screenshots/bookmark_icons2.png}
 	\caption{Icons used for Claims, Snippets, and Topics}
@@
 
-Think Link users interact with three kinds of object, each of which is associated with a different family of icons (Figure~\ref{bookmark_icons}):
+Think Link users interact with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}):
 
@@
 Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
+A topic can itself by disambiguated by having a super-topic.
 \end{itemize}
-
-Varients of these three icons are used consistently when refering to these three object types. 
-Yellow versions of these icons are used to identify claims, folders, or snippets that the user has marked as interesting (by clicking on their icon).
-
-Colors are also used to indicate the extent to which a claim is supported or opposed by other claims.
-Red means that a claim is opposed by other claims, and green means that a claim is supported by other claims and not opposed by any.
-The colors are chosen to fit with people's normal associations with colors, where red is commonly associated with danger (e.g.
-a traffic light) and yellow is the standard color used for highlighter pens.
-
-\subsection{Collaborating to connect claims}
-
-Think Link shares a lot in common with Wikis like Wikipedia~\cite{wikipedia}.
-The claim graph is shared between all users and editable by anyone.
-Any user can identify a claim made on a web page by selecting the web snippet that makes this claim and clicking the ``new snippet'' button on the browser toolbar.
-Similarly, any user can establish new supporting and opposing relationships between claims by using drag and drop within the claim browser.
-One can think of Think Link as being rather like a Wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.
-
-Think Link uses collaborative filtering~\cite{collective} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim.
-If a user finds a snippet or claim interesting then they can mark it as such.
-When Think Link lists claims or snippets, it will show first those that the user marked as interesting, and order the rest according to the number of other users who marked them interesting.
-
-It is important to avoid political fights, where two competing sides delete claims, snippets, or connections that they disagree with.
-Similarly, it is important to avoid vandalism, where people abuse people with competing beliefs by adding abuse claims or snippets.
-While we do not have a perfect solution to this problem, our current approach is to treat deletion as a special case of collaborative filtering.
-A claim or snippet will only be deleted if many people vote to delete it and very few people bookmark it.
-
-\subsection{Why People Annotate}
-
-Tools like Think Link rely on user contributions in order to be useful.
-If no users are identifying factual claims on pages then other people who browse such pages will not see any claims identified.
-Similarly, if no other users are connecting claims together, then users will not see any supporting or opposing claims when they click on a highlighted snippet.
-
-Moreover, in order to become popular, a tool like Think Link needs to be useful even when very few people are using it.
-If a tool is only useful when it has a large community using it then it is unlikely that early adopters will stick with it enough for it to ever acquire a large community.
-
-Our user study participants identified several reasons why they would want to mark up factual claims in documents they found.
-The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found.
-One user (who was an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
-The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
-
-\section{Interaction Techniques}
-\label{interface}
-
-Users interact with Think Link in four key ways.
-Think Link will draw attention to interesting claims on pages that the user browses; it allows the user to identify new factual claims on pages they browse; it allows them to browse the graph of related claims and identify the strongest evidence supporting or opposing the claims they are looking at; and it allows them to organize the claim graph by making new connections between existing claims and topics.
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/claimbrowse.png}
-	\caption{The Claim Organizer contains two claim browsers}
-	\label{fig:claimbrowser}
-	\end{center}
-\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
 	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
-	\caption{The Claim Browser Allows one to browse the argument graph}
+	\caption{The claim browser visualizes the claim graph}
 	\label{claimbrowse_diagram}
@@
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/fullbrowser.png}
-	\caption{The Enhanced claim browser adds additional controls}
-	\label{enhancedbrowser}
-	\end{center}
-\end{figure}
-
-Our users expressed an interest in using snippets to help them construct arguments that support a claim they agree with, to show them the arguments for and against a claim that they are unsure about, to collect evidence about a topic they are interested in, to share information with friends, and to see arguments against claims that they encountered on the web.
-We constructed the ``claim browser'' interface to help users do these things (Figure~\ref{fig:claimbrowser}).
-
 Claims and topics form a directed graph structure. A claim can have any number of claims that support or oppose it, and any number of claims that it supports or opposes.
@@
 When designing an interface to this structure, we were faced with two opposing constraints.
-We needed to be able to clearly view a large number of claims and topics in a small screen space, and we needed an interface that made it clear that the data was a graph rather than a tree.
-Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims.
+We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree.
+Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place.
 Tree-based outliners such as OmniOutliner~\cite{outliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
 
-\todo{This interface is actually closer to TheBrain than the text suggests}
+After several iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner.
+Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it.
+Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.
 
-After several iterations, we settled on an interface that is a dynamically reorganizing graph layed out like an outliner.
-Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it.
-Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line.
-Our users commented that they found it quite intuitive to navigate through a graph of claims and topics in this way.
-\studyresult{quote}.
-
-The placement of objects above and below is intended to emphasize the conventional structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
+The placement of objects above and below is intended to emphasize the conventional hierachial structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
 A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
-
-\todo{Have I seen an interface like this elsewhere? Did PARC have something like this?}
-
-\todo{Is this interface a contribution in itself? Has an interface like this been presented before?}
 
@@
 Other objects appear and disapper by smoothly sliding into or out of view.
-We found that this animation helps users retain a sense of where they are with respect to what they were looking at previously and helps users avoid getting lost.
 
-Users see a claim browser in three different places:
-\begin{itemize}
-\item {\bf The Main Organizer} shows two claim browsers, and allows users to use drag and drop to make new connections between claims in the two organizers. (Figure~\ref{fig:claimbrowser})
-\item {\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page. (Figure~\ref{claimview})
-\item {\bf The Claim Selection Window} shows one claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making. (Figure~\ref{snipsavecrop}) 
-\end{itemize}
+Users see a claim browser in three different places.
+The {\bf organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}).
+{\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}).
+The {\bf Claim Selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).
 
-\subsection{Identifying new factual claims}
+\subsection{Creating new Snippets}
 \label{newsnippet}
@@
 \begin{figure}[tb]
-	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram.png}
+	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram_full.png}
 	\caption{Selecting the claim made by a new snippet}
@@
 
-If a user finds a snippet of text on a page that makes an interesting claim then they may want to enter it into Think Link.
-There are several reasons they may wish to do this.
+There are several reasons a user may wish to add a snippet to Think Link.
 It may be that they find the snippet useful and may want to refer to it again in the future.
-It may be that they disagree with the claim, and want to alert other readers to the fact that there are opposing arguments, or it may be that they agree with the claim and want to provide easy access to evidence that backs it up.
+It may be that they disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments, it may be that they think the claim argues a point well and want to be able to use it to make an argument, or it may be that they agree with the claim and want to provide easy access to evidence elsewhere that backs it up.
 
-To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button.
+To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}).
 This is a similar approach to that taken clipping tools such as Google Notebook~\cite{googlenotebook}.
@@
 Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making.
-To do this, Think Link presents the user with a ``claim selection'' window.
+To do this, Think Link presents the user with a ``claim selector'' window.
 This window contains a small version of the claim browser that the user can use to select the claim that the snippet is making.
-At the bottom of the window, we show the phrase ``the snippet text {\it snippet} claims that {\it claim}''.
-We found that this helps users understand the nature of a claim and its relationship to a snippet.
 
@@
 For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim.
-
 This is an intentionally different model to that used by ad-hoc tag-based~\cite{tags} systems such as Delicious~\cite{delicious} and Flickr~\cite{flickr}.
 This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected.
+In practice, it is inevitable that duplicates claims and topics will sometimes be created.
+When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.
 
-In earlier revisions of the interface it was very easy for users to quickly create new claim texts and awkward to find and reuse existing ones.
-This led users to create many claims that were essentially equivalent and reduced the utility of Think Link as a tool for connection snippets together.
+\subsection{Organizing the Claim Graph}
 
-\todo{Make new snippet icon throb when something is selected}
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/claimbrowse.png}
+	\caption{The Claim Organizer contains two claim browsers}
+	\label{fig:claimbrowser}
+	\end{center}
+\end{figure}
 
-\subsection{Organizing factual claims}
+Like Wikipedia~\cite{wikipedia}, Think Link allows any user to improve the information in the claim graph.
+The claim graph is shared between all users and editable by anyone.
+Any user can add new snippets, create new claims, create new topics, or establish new relationships between these objects.
+One can think of Think Link as being rather like a Wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.
 
-Much of the value of Think Link comes from the connections between claims. It is thus important that it be easy to establish new connections between claims and topics.
+Think Link uses collaborative filtering~\cite{collective} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim.
+If a user finds a snippet or claim interesting then they can vote in favor of it by clicking on its icon, causing it to light up (Figure~\ref{bookmark_icons}).
+When Think Link lists claims or snippets, it will show first those that the user marked as interesting, and order the rest according to the number of other users who marked them as interesting.
+
+It is important to avoid political fights, where two competing sides delete claims, snippets, or connections that they disagree with.
+Similarly, it is important to avoid vandalism, where people abuse people with competing beliefs by adding abuse claims or snippets.
+While we do not have a perfect solution to this problem, our current approach is to treat deletion as a special case of collaborative filtering.
+If a user believes a claim, topic, snippet, or connection is junk then they can request that it be deleted by clicking on the ``delete'' button.
+This will hide the object for the user who request deletion and reduce the score of the object for other users.
+If enough people vote to delete the object then its score will eventually be low enough that it is not displayed to users unless they request to see junk objects.
+
+Unlike a Wiki, in which users can edit and delete information produced by others, and history is used to revert abusive changes, Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects.
+The hope is that over time ratings should converge to a steady state and edit wars should be avoided.
+It would not be practical for a wiki to take this approach as their data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.
 
@@
 To establish a connection between two claims, one need simply drag one claim onto the other.
-In the full interface, one can open two browsers and drag points from one browser onto points on the other.
+The claim organizer window has two claim browsers, allowing a user to points from one browser onto points on the other (Figure~\ref{fig:claimbrowser}).
 
-In our initial study, we found that many users did not realize that they could use drag and drop to create connections to existing claims.
-We rectify this, we added a notice at the top of the main organizer window (Figure~\ref{fig:claimbrowser}) telling users that they can use drag and drop.
+\subsection{Why People Annotate}
 
-We found that creating new connections between existing claims was one of the things that users found most difficult.
+Tools like Think Link rely on user contributions in order to be useful.
+If no users are identifying factual claims on pages then other people who browse such pages will not see any claims identified.
+Similarly, if no other users are connecting claims together, then users will not see any supporting or opposing claims when they click on a highlighted snippet.
 
-\todo{say more here}
+Moreover, in order to become popular, a tool like Think Link needs to be useful even when very few people are using it.
+If a tool is only useful when it has a large community using it then it is unlikely that early adopters will stick with it enough for it to ever acquire a large community.
 
-\section{Discussion}
+Our user study participants identified several reasons why they would want to mark up factual claims in documents they found.
+The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found.
+One user (who was an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
+The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
 
-\subsection{Context of a Claim}
-
-\subsection{How many claims to show}
-
-\subsection{Beyond Claims}
-
-\section{Implementation}
+\subsection{Implementation}
 
@@
 \begin{itemize}
-\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains a graph of claims, topics, and snippets and provides an API that allows this data to be queried and modified
-\item {\bf A web UI}, written using Ruby on Rails~\cite{rails} that provides a visual interface to the claim graph
+\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains the claim graph and provides an API that allows this data to be queried and modified
+\item {\bf A web UI}, written using Javascript that implements the claim browser
 \item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page.
-This script also provides the ability to create new snippets or display the rails interface to investigate a particular claim.
-\item {\bf A browser extension}, implemented for Firefox~\cite{firefoxextension}, that inserts the page enhancement script into all pages the user browses to, and provides toolbar and context-menu shortcuts to the ``new snippet'' feature of the page enhancement script.
+This script displays the web UI in an iframe to pick or investigate a claim.
+\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides toolbar and context-menu shortcuts.
 \end{itemize}
@@
 These components are largely independent.
-One could use the javascript script on a web page without using the firefox extension, by either manually including it on the page (e.g.
+One could use the page enhancement script on a web page without using the Firefox extension, by either manually including it on the page (e.g.
 to enhance your own blog) or by adding it using a proxy.
@@
 
-The source code to Think Link is publicly available under the Apache license at the following URL:
-
-{\b url removed for blind submission}
-
-We expect to have a public deployment available by the time of publication.
-
-We use icons from the free FamFamFam Silk~\cite{silkicons} collection.
+The source code to Think Link is publicaly available under the Apache license.
 
@@
 Our intention was to recruit users who were not experts, but who regularly used the internet to find information.
-We recruited participants using a posting to the Craigslist~\cite{craigslist} classified adverts site.
+We recruited participants using a posting to the Craigslist~\cite{craigslist} classified advert site.
 In our advert, we expressed an interest in people who use the internet to gather knowledge, rather than just for tasks such as email or shopping.
@@
 The first task was to look at a selection of web pages that already had highlights and explore the interface while thinking aloud about what they saw.
-The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated our database with.
+The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with.
 Participants were shown an interface that is largely identical to that described earlier in this paper.
@@
 
-In this section we present the findings from our two users studies. Findings from the two studies are presented together and clustered by topic.
+In this section we present the findings from our two user studies. Findings from the two studies are presented together and clustered by topic.
 
@@
 Response was generally positive, with many participants being very keen to use the tool soon.
-One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it becomes publically available.
+One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed.
 Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
@@
 Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
-Particpants in the second study said they found the tool ``very intuitive''.
-
-\subsubsection{Browsing the Argument Graph}
-
-%In the first study, several participants reported that they felt ``disorientated'' when browsing through the idea graph.
-%
-%Several participants in the second study seemed to enjoy the action of browsing through ideas.
+Participants said they found the tool ``very intuitive''.
 
@@
 Sometimes users would deal with this by writing a compound claim like ``Global Warming will cause X and Y''.
-While users could mark up the same snippet as making multiple claims, users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.
+While users could mark up the same snippet as making multiple claims.
+Users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.
 
-One special case of this was that several users wanted to mark up a table as a snippet.
-A table can usually be considered to be making several interesting claims and users were often confused about what they should say the table cliams.
-Our current guidance is that one should mark up a table as making the most interesting claims that that table makes.
+One special case of this problem was that several users wanted to mark up a table as a snippet.
+A table can usually be considered to be making several interesting claims and users were often confused about what they should say the table claimed.
+Our current guidance is that one should mark up a table as making the most interesting claims that that table makes --- those that support or oppose claims made elsewhere.
 In other cases, a user wanted to mark up an image as a snippet.
@@
 For example they might find the text of an important speech or an Olympic results table.
-Several expressed a desire to have a new class of object that was neither a topic nor a claim, but instead just ``an interesting object relavent to this topic''.
+Several expressed a desire to have a new class of object that was neither a topic nor a claim, but instead just ``interesting information relevant to this topic''.
 
@@
 biasing towards topics that were recent or hot.
+The auto-complete list would show either when the user started typing, or when the user clicked the drop down button.
+Selecting a claim would auto-populate the topic.
+Selecting a topic would constrain the claims that were suggested to be within that topic.
 
@@
 Participants would often confuse claims and topics, either entering a claim in the topic box, or a topic in the claim box.
-Several participants expressed confusion about the difference between the two.
-Participants would also often create new points and topics when appropriate points and topics already existed in the claim graph, even when the suggestion list was drawing their attention to a topic or claim that would have been appropriate.
+Participants would also frequently create new points and topics when appropriate points and topics already existed in the claim graph, even when the suggestion list was drawing their attention to a topic or claim that would have been appropriate.
 
 For the second study, we used the interface described in Section~\ref{newsnippet}, which uses the same claim browser interface used for exploring the claim graph.
-We found that users of this interface had no difficulty distinguishing between claims and topics and were much more likely to reuse existing claims and topics.
+We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics.
 We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.
@@
 
-Some users incorrectly marked one claim as supporting another when in fact they should have both been marked as supporting a third claim that needed to be created, or where an intermediate claim was needed.
+Some users incorrectly marked one claim as supporting another when in fact they should have both been marked as supporting a third claim that needed to be created.
 For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing environmental problems''.
 Users realized that the claims were related, but did not immediately recognize that they needed to create new claims in order to structure the relationship correctly.
-It is possible that creating correct logical claim structures may just be too difficult for some people.
-We hope that, if Think Link was deployed more widely many of the intermediate claims that were needed would already have been created and this problem would be reduced.
+It is possible that creating correct logical claim structures may just be too difficult for some people, or it may be that users would get used to the idea with more practice.
+We hope that if Think Link was deployed more widely many of the intermediate claims that were needed would already have been created and this problem would thus be reduced.
 
@@
 This is a particular problem when talking about breaking news events, where what claims are true can change fast.
-If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the {\it time} at which a claim was asserted to be true.
+If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the time at which a claim was asserted to be true.
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[tb]
 	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
@@
 Firstly, our current implementation has privacy issues.
-Every time one navigates to a web page, the plugin contacts our server and gives it the current URL so that it can check if there are snippets on that page.
-This information is anonymous, cacheable, and not logged, but it is still likely that some people would object to this information being given to an external server.
+Every time one navigates to a web page, the plugin contacts our server and gives it the current URL so that the server can check if there are snippets on that page.
+These requests are anonymous, cacheable, and not logged, but it is still likely that some people would object to this information being given to an external server.
 
@@
 
-While Think Link is influenced by Wikis, it does not currently have support for reverting bad edits made by previous users, or managing history in general.
-It will be interesting to see what interfaces work well for managing history, given that our data is a graph rather than a series of pages.
-
-Similarly, Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics.
+Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics.
 Since our graph and user base are currently small we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.
@@
 
-On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or contraversial, and then using a wiki model to allow users to collaborate together to structure claims into an argument graph.
+On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or contraversial, and then using an ``append only, collaborative filtering'' model to allow users to collaborate together to structure claims into an argument graph.
 
@@
 We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link.
+Think Link uses icons from the free FamFamFam Silk~\cite{silkicons} collection.
 

### 2008-09-19 papers/web_of_ideas/web_of_ideas.tex
State before Beth changes. Largely just reference fixing.

@@
 pdftitle={Browsing the Web of Factual Claims},
-pdfauthor={Beth Trushkowski and Rob Ennals},
+pdfauthor={Beth Trushkowsky and Rob Ennals},
 pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
@@
 Tim Berners Lee has expressed concern about the difficulty that people face discerning whether information on the web is true~\cite{bbcwebwarning}.
-Many people have also voiced concerns about how easily people can subvert Wikipedia to give peolpe false information~\cite{wikifalse}.
+Many people have also voiced concerns about how easily people can subvert Wikipedia to give people false information~\cite{wikifalse}.
 Several commentators have observed that there is a Media Echo Chamber effect~\cite{echochamber,echochamber2} in which news sources report claims that they have heard from other news sources, despite the fact that these claims may be misleading or untrue.
@@
 Part of the problem is that conventional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them.
-While a web page will typically contain links to other articles, these typically only reference a small proportial of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author.
+While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author.
 The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web.
@@
 Any user can add new claims, connect existing claims together, and identify snippets on web pages that make specific claims.
-Collaborative filtering is used to filter out junk or abusive information, while minimizing the danger of politification.
+Collaborative filtering is used to filter out junk or abusive information, while minimizing the danger of political edit wars.
 
@@
 Some people may be looking for confirmation of their own points of view rather than information that challenges their beliefs.
-We hope however that Think Link may be able to make some contribution to helping peolpe find out about other points of view, and help people more easily find the most interest claims about topics they are interested in.
+We hope however that Think Link may be able to make some contribution to helping people find out about other points of view, and help people more easily find the most interest claims about topics they are interested in.
 
@@
 Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}.
-Like Think Link, wikis allow users to find information organised by topic rather than author and allow users to collaborate together to bring together all the best information about a topic.
+Like Think Link, wikis allow users to find information organized by topic rather than author and allow users to collaborate together to bring together all the best information about a topic.
 Wikipedia's greatest strength is arguably also its greatest weakness.
@@
 
-SpinSpotter~\cite{spinspotter} shares Think Link's goal of allowing users to identify misleading and innaccurate information on web pages that they read.
+SpinSpotter~\cite{spinspotter} shares Think Link's goal of allowing users to identify misleading and inaccurate information on web pages that they read.
 If a user sees a section of text that they think is misleading then they can mark it up, causing it to be highlighted when other users view the same page.
@@
 SpinSpotter allows users to give a textual description of why the snippet is spin and a suggested edit that would make it more accurate.
-ThinkLink instead connects the snippet to its global claim graph, allowing users to quickly access evidence for and against the truth of the claim.
-There is alos a difference in the nature of what SpinSpotter and Think Link expect users to mark up.
+Think Link instead connects the snippet to its global claim graph, allowing users to quickly access evidence for and against the truth of the claim.
+There is also a difference in the nature of what SpinSpotter and Think Link expect users to mark up.
 Think Link is interested in evaluating the truth of factual claims, while SpinSpotter also interested in identifying biased phrases (e.g.
@@
 
-Other web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add their own annotations to existing web pages and view annotations written by other people.
-Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents.
+Other web annotation systems such as ShiftSpace.org, Stickis.com, SharedCopy.com, and Diigo.com allow people to add their own annotations to existing web pages and view annotations written by other people.
+Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relevant documents.
 More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
@@
 
-Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages.
+Web clipping tools such as Google Notebook, Scrapbook~\cite{scrapbook}, and Zotero.org allow one to gather and organize interesting from web pages.
 Many web clipping tools are also web annotation systems.
@@
 
-In Vannevir Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them.
+In Vannevar Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them.
 As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''.
 Several more recent systems have allowed user to add links to existing pages.
-ENQUIRE~\cite{enquire} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it.
-Everything2~\cite{everything2} links each page to the most popular pages that users viewed at the same time.
+ENQUIRE~\cite{weavingtheweb} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it.
+Everything2.com links each page to the most popular pages that users viewed at the same time.
 Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making and allowing users to browse this graph, rather than just allowing users to specify links between pages.
@@
 
-Much work has been done on the idea of using a graph to represent an argument~\cite{argumentatino,argmas}.
+Much work has been done on the idea of using a graph to represent an argument~\cite{argumentation,argmas}.
 Popular argument models include the Toulmin Model~\cite{toulmin}, the Carneades Model~\cite{carneades}, and the IBIS model~\cite{ibis}.
 Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model, with the result that they provide a more accurate model of the logical argument, at the cost of requiring more skill to assemble.
-One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numberical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.
+One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numerical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.
 
@@
 This graph is managed like a Wiki, allowing any user to add new claims or snippets.
-As a user browses the web, they can identify snippets that make claims that are interesting or contraversion and link them into the global claim graph.
+As a user browses the web, they can identify snippets that make claims that are interesting or controversial and link them into the global claim graph.
 
-Think Link is implemented as a FireFox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.
+Think Link is implemented as a Firefox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.
 
@@
 If the current page contains snippets then a tab appears in the top left corner of the window.
-The tab contains a lightbulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim.
+The tab contains a light bulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim.
 This allows a user to quickly tell if a page contains something of interest without having to scroll through the whole page.
 Clicking on the tab opens the margin.
-The margin provides a summary of all the interesting claims that users have identified on the current page and is designed to mimick the traditional margin notes that readers often write on physical documents~\cite{marginalia}.
-To emphasise the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.
+The margin provides a summary of all the interesting claims that users have identified on the current page and is designed to mimic the traditional margin notes that readers often write on physical documents~\cite{marginalia}.
+To emphasize the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.
 
@@
 Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place.
-Tree-based outliners such as OmniOutliner~\cite{outliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
+Tree-based outliners such as OmniOutliner~\cite{omnioutliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
 
@@
 
-The placement of objects above and below is intended to emphasize the conventional hierachial structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
+The placement of objects above and below is intended to emphasize the conventional hierarchical structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
 A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
@@
 Other items that were already on the screen move from their current locations to their new locations.
-Other objects appear and disapper by smoothly sliding into or out of view.
+Other objects appear and disappear by smoothly sliding into or out of view.
 
@@
 
-To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}).
-This is a similar approach to that taken clipping tools such as Google Notebook~\cite{googlenotebook}.
+To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser tool bar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}).
+This is a similar approach to that taken clipping tools such as Google Notebook.
 
@@
 For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim.
-This is an intentionally different model to that used by ad-hoc tag-based~\cite{tags} systems such as Delicious~\cite{delicious} and Flickr~\cite{flickr}.
+This is an intentionally different model to that used by ad-hoc tag-based systems such as Del.icio.us and Flickr.com.
 This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected.
@@
 This script displays the web UI in an iframe to pick or investigate a claim.
-\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides toolbar and context-menu shortcuts.
+\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides tool bar and context-menu shortcuts.
 \end{itemize}
@@
 
-The source code to Think Link is publicaly available under the Apache license.
+The source code to Think Link is publicly available under the Apache license.
 
@@
 Their ages ranged from high school age to retired.
-Our intention was to recruit users who were not experts, but who regularly used the internet to find information.
-We recruited participants using a posting to the Craigslist~\cite{craigslist} classified advert site.
-In our advert, we expressed an interest in people who use the internet to gather knowledge, rather than just for tasks such as email or shopping.
+Our intention was to recruit users who were not experts, but who regularly used the Internet to find information.
+We recruited participants using a posting to the Craigslist.org classified advert site.
+In our advert, we expressed an interest in people who use the Internet to gather knowledge, rather than just for tasks such as email or shopping.
 We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.
@@
 We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they found interesting and connect those claims to the existing claim graph.
-For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelyhood that there would be existing claims about the topic they were browsing.
+For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.
 
@@
 Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students.
-Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviours.
+Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.
 
@@
 Response was generally positive, with many participants being very keen to use the tool soon.
-One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed.
+One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed.
 Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
@@
 Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version.
-None of these problems re-occured during the second study.
+None of these problems re-occurred during the second study.
 We discuss some of these changes in the sections below.
@@
 Most participants in the first study, and all participants in the second study were able to use the tool competently.
-Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
+Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
 Participants said they found the tool ``very intuitive''.
@@
 Many users would consistently mark the first paragraph of an article as a snippet.
-This paragraph would frequently summarise the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.
+This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.
 
-\subsubsection{Chosing a Claim for a Snippet}
+\subsubsection{Choosing a Claim for a Snippet}
 
@@
 
-For the second study, we used the interface described in Section~\ref{newsnippet}, which uses the same claim browser interface used for exploring the claim graph.
+For the second study, we used the interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph.
 We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics.
@@
 
-Several users expressed an interest in being able to mark a claim as contraversial without having to create an opposing claim.
+Several users expressed an interest in being able to mark a claim as controversial without having to create an opposing claim.
 One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
@@
 
-On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or contraversial, and then using an ``append only, collaborative filtering'' model to allow users to collaborate together to structure claims into an argument graph.
+On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using an ``append only, collaborative filtering'' model to allow users to collaborate together to structure claims into an argument graph.
 
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 

### 2008-09-20 papers/web_of_ideas/web_of_ideas.tex
Submitted version. Minor changes

@@
 
-Conventional web browsers allow a user to look at pages and follow links between them; however when a user browses the web it is often not the pages themselves that they are looking for but claims about the world that are contained on those pages.
-A page may contain claims that are contradicted by other pages, or contain one interesting new claim hidden in a sea of claims that the user has already read.
+Conventional web browsers allow a user to look at pages and follow links between them; however when a user browses the web it is often not the pages themselves that they are looking for, but claims about the world that are contained on those pages.
+A page may contain claims that are contradicted by pages elsewhere on the web, or for which better arguments can be found in other places.
 If a user is to form an accurate opinion about a topic then they may have to spend considerable time gathering information from many disconnected pages scattered across the web.
@@
 
-Part of the problem is that conventional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them.
+Part of the problem is that conventional web browsers present the web as a network of connected pages, when it is often the case that what the user is really interested in is the factual claims made by those pages, and the connections between those claims.
 While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author.
@@
 The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages).
-While this makes it easier for add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.
+While this makes it easier for users to add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.
 
@@
 	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/summary_graph.png}
+	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
 	\caption{Think link connects claims to each other and to web snippets}
@@
 When a user views a web page, Think Link highlights snippets that have been identified as making factual claims, with the highlight color indicating whether other sources have been found that disagree with the claim.
-If a user clicks on such a snippet then they will see a ``claim browser'' (Figure~\ref{claimview}) that allows them to see other claims made on the web that support or oppose the claim the snippet makes, and snippets elsewhere on the web that make these other claims.
+If a user clicks on a snippet then they will see a ``claim browser'' (Figure~\ref{claimview}) that allows them to see other claims made on the web that support or oppose the claim the snippet makes, and snippets elsewhere on the web that make these other claims.
 
@@
 
-Another key difference between Think Link and a Wiki is that Think Link pulls the whole web into its graph of connected claims.
+Another key difference between Think Link and a wiki is that Think Link pulls the whole web into its graph of connected claims.
 A user can use Think Link to investigate claims they read on arbitrary web sites, without having to restrict their browsing to a single wiki site.
@@
 This is a goal that is shared with several other projects.
-Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted.
+Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allow users to navigate from such a passage to all other documents where that passage is quoted.
 Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus.
@@
 As a user browses the web, Think Link highlights snippets of text that have been identified as making factual claims.
-If a user clicks on a highlighted snippet then Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}).
-Our intention is that Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.
+If a user clicks on a highlighted snippet, Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}).
+Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.
 
 Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}).
-This graph is managed like a Wiki, allowing any user to add new claims or snippets.
+This graph is managed like a wiki, allowing any user to add new claims or snippets.
 As a user browses the web, they can identify snippets that make claims that are interesting or controversial and link them into the global claim graph.
@@
 For example ``Global Warming'', or ``Computer Science''.
-A claim can have one or more topics that it is about, and a topic can have one or more more general topics.
-Topics are used both to organize, and to disambiguate claims.
+A claim can be about one or more topics, and a topic can have one or more more general topics.
+Topics are used to organize and disambiguate claims.
 For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''.
@@
 \end{figure}
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/claimbrowse_zoom.png}
-	\caption{Close up of a list of supporting claims}
-	\label{claimbrowse_zoom}
-	\end{center}
-\end{figure}
 
@@
 
-After several iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner.
+After several design iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner.
 Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it.
@@
 A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/claimbrowse_zoom.png}
+	\caption{Close up of a list of supporting claims}
+	\label{claimbrowse_zoom}
+	\end{center}
+\end{figure}
 
@@
 Users see a claim browser in three different places.
-The {\bf organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}).
-{\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}).
-The {\bf Claim Selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).
+The {\it organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}).
+The {\it popup browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}).
+The {\it claim selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).
 
@@
 There are several reasons a user may wish to add a snippet to Think Link.
-It may be that they find the snippet useful and may want to refer to it again in the future.
-It may be that they disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments, it may be that they think the claim argues a point well and want to be able to use it to make an argument, or it may be that they agree with the claim and want to provide easy access to evidence elsewhere that backs it up.
+They may find the snippet useful and may want to refer to it again in the future; they may disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments; they may think the claim argues a point well and want to be able to use it to make an argument, or they may agree with the claim and want to provide easy access to evidence elsewhere that backs it up.
 
@@
 
-Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics.
-Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one.
+Since much of Think Link's utility comes from linking snippets together, it is important to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics.
+We designed the claim selection window to make it easier to pick out an existing claim than to create a new one.
 Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim.
@@
 Any user can add new snippets, create new claims, create new topics, or establish new relationships between these objects.
-One can think of Think Link as being rather like a Wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.
+One can think of Think Link as being rather like a wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.
 
@@
 
-Unlike a Wiki, in which users can edit and delete information produced by others, and history is used to revert abusive changes, Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects.
+In a wiki, users edit and delete information produced by others, and history is used to revert abusive changes.
+Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects.
 The hope is that over time ratings should converge to a steady state and edit wars should be avoided.
-It would not be practical for a wiki to take this approach as their data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.
+It would not be practical for a wiki to take this approach as wiki data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.
 
@@
 The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found.
-One user (who was an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
+One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
 The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
@@
 Four were female and two were male.
-Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students.
+Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the college semester meant that five of the participants were students.
 Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.
@@
 We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
-The first task was to look at a selection of web pages that already had highlights and explore the interface while thinking aloud about what they saw.
+The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw.
 The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with.
@@
 Users would often encounter a snippet that could be interpreted as making several interesting claims, and were unsure about what to do in such circumstances.
-Sometimes users would deal with this by writing a compound claim like ``Global Warming will cause X and Y''.
-While users could mark up the same snippet as making multiple claims.
+Some users would deal with this by writing a compound claim like ``Global Warming will cause X and Y'' while other users would create several snippets for the same text, making different claims.
 Users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.
@@
 
-For the second study, we used the interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph.
+For the second study, we used the snippet creation interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph.
 We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics.
@@
 Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics.
-Since our graph and user base are currently small we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.
+Since our graph and user base are currently small, we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.
 

### 2008-09-20 papers/cscw_mash/cscw_mash.tex
New paper for CSCW workshop

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage{wrapfig}
% \usepackage{picins}
% \usepackage{floatflt}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Mashing the Ideas Expressed on the Web},
pdfauthor={Beth Trushkowsky and Rob Ennals},
pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

\newcommand{\todo}[1]{}
% \newcommand{\todo}[1]{\footnote{{\bf TODO:} #1}}
\newcommand{\Intel}{Intel\textsuperscript{\textregistered}}

\newcommand{\idea}[1]{{\color{blue} IDEA: #1}\\}
\newcommand{\studyresult}[1]{{\color{red} STUDY RESULT?: #1}\\}
\newcommand{\howmany}{{\color{red} (HOW MANY?)}}

\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy

\begin{document}
% to make various LaTeX processors do the right thing with page size
\special{papersize=8.5in,11in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}
%
\toappear{Submitted to the Tinkering, Tailoring, and Mashing workshop at CSCW 2008}

\title{Participatory Mashups: Using Users to make Data Mashable}

\numberofauthors{2}

%\author{
%	\alignauthor Authors anonymized for submission
%}

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Research}\\
       \affaddr{2150 Shattuck Avenue}\\
       \affaddr{Penthouse Suite}\\
       \affaddr{Berkeley, CA 94704, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \email{trush@berkeley.edu}
}
\sloppy

\maketitle

\begin{abstract}
Most mashups concern themselves with data that is fairly easy for a machine to understand: addresses, phone numbers, information available through APIs, or information that can be scraped from a small set of popular web sites.

However much of the most interesting information on the web is not in a form that a computer can easily understand. It may be in natural language text, or it may be in the long tail of web sites that developers have not found it worthwhile to write scrapers for.

In this paper, we promote the approach of ``participatory mashups'' in which the users of the mashup also teach the mashup ways that it can understand new data. As examples, we present our work on Think Link, which connects factual statements on the web to related statements elsewhere, and Mash Maker, which attempts to understand the meaning of structured data on arbitrary web pages.
\end{abstract}

\section{Introduction}

If we understand what the information on a page means then we can do useful things with it. We can connect the information to information elsewhere that might be relevant, we can compute new information from the information we have, and we can present users with new interfaces that are more useful than that provided by any individual site.

Some kinds of information are easier to understand than others, and mashups have so far understandably focussed on the low-hanging fruit. Addresses follow an easily recognized pattern, and have led to a large number of useful mashups which plot various things on maps or work out what things are near to other things. Similarly, many mashups have made use of data that is available from APIs, or that can be easily scraped from popular web pages that the mashup has been hard-coded to understand.

But what about everything else?

Much of the most interesting information on the web is available as unstructured natural language text: arguments, ideas, opinions, factual claims, jokes. Much of this is information that could benefit a lot from being mashed up. For example ``which of these claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this claim?'', or ``what ideas on this site would I be likely to find most interesting?''.

Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be very interesting. For example, tables of data that have been entered by hand, or one of the many tiny web services that display data from a database backend using their own custom template that nobody has ever written a scraper for.

In this approach we argue for ``participatory mashups'' as a way to open up access to this data. In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and connecting information in new ways. By teaching a participatory mashup the meaning of some data, the user helps themselves, since they can now include this data in their mashup, but they also help the wider community of users, since all other users can now benefit from the system understanding this data.

We motivate this approach using two mashup tools that we have built. Think Link allows users to identify factual claims that they read on web pages and connect them to related factual claims on other sites, including claims that may oppose the original claim. Mash Maker allows users to teach it the meaning of structured data on arbitrary web sites, and then enhances these web sites to make them more useful, guided by example improvements provided by users.

More generally, we consider a tool to be a ``participatory mashup'' if it relies on users to teach it what information on the web means, and how that information is connected together. We argue that this is an approach that other applications could also use to help them understand the web.

\section{Think Link}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
	\caption{Hovering over a highlighted snippet shows a summary}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
	\caption{Click on a claim to investigate evidence for and against it}
	\label{claimview}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
	\caption{Think link connects claims to each other and to web snippets}
	\label{summarygraph}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
	\caption{The claim browser visualizes the claim graph}
	\label{claimbrowse_diagram}
	\end{center}
\end{figure}

Much concern has been expressed recently about biased or inaccurate information on web sites~\cite{bbcwebwarning,wikifalse}, and the media echo chamber problem in which people read web sites that feed their own views back to them, rather than exposing them to the opposing opinions held by other groups~\cite{echochamber,echochamber2}.

Think Link~\cite{thinklink} is a Firefox extension that helps users evaluate the truth of statements they read, helps users be more easily exposed to a range of ideas and opinions that they might not otherwise encounter.

As a user browses the web, Think Link highlights snippets of text that other users have identified as making claims that are interesting or contraversial (Figure~\ref{highlight}). Interesting claims are highlighted in yellow, and contraversial claims are highlighted in red. If a user clicks on a highlighted snippet, Think Link will display an interface that allows a user to easily find snippets on other web pages that make related claims, including snippets that argue against the opinion put forward by the highlighted snippet (Figures~\ref{claimview} and \ref{claimbrowse_diagram}). Think Link allows a user to easily access the best arguments for and against a claim, including arguments they might not otherwise have come across because they would not have been voiced by the web sites that the reader normally reads.

Think Link maintains a graph of known factual claims, their relationship to each other, and the snippets that hold these claims (Figure~\ref{summarygraph}). This graph is built entirely by users of the tool. Users create claims, users connect claims, and users identify snippets making claims. Similarly, users vote for snippets, claims, or connections that they believe are particularly important.

This graph allows one to ask interesting questions such as ``Which snippets on this page make claims that are opposed by snippets elsewhere on them web?'', ``What is the most trustworthy news source that makes this claim?'', ``What do my friends think about this idea?'', ``What are the most interesting claims about this topic that I haven't read before'', or ``What is the best argument against this claim, and what would be the best counter-argument to that?''.

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=14cm]{../screenshots/newsnip_all.png}
	\caption{Process for creating a new snippet}
	\label{createprocess}
	\end{center}
\end{figure*}

Identifying factual claims and the connections between them automatically would be very difficult using the current generation of natural language processing and automated reasoning tools; however this is quite an easy task for humans.  To create a new snippet, a user selects the text that is making an interesting factual claim, and then uses a claim browser interface to identify the claim being made (Figure~\ref{createprocess}). Users can connect claims together using a simple drag and drop interface.

Our user study participants identified several reasons why they would want to mark up factual claims in documents they found. The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found. One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments. The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.

Like the work of Luis von Ahn~\cite{vonahn,recaptcha} or the ``invisible hand'' or Adam Smith the intention is that people should be motivated by self interest to do something that benefits the wider community.

\section{Mash Maker}

Mash Maker~\cite{mashmaker} is a browser extension that understands the meaning of the pages that users browse and suggests ways that it can improve the current page so as to be more useful to the user. Mash Maker relies on users to teach it both how to understand web pages, and also how particular kinds of web page might be improved in interesting ways.

As views a web page, Mash Maker will suggest ways that it can make the page more useful, and suggest these improvements on its toolbar. If the user clicks on the button for such an improvement then Mash Maker will apply it to the current page, potentially using other web sites and remote APIs, and potentially applying widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}). Mash Maker suggests improvements based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behaviour of other users.

Our intention is that users should be able to use Mash Maker to enhance arbitrary web sites in arbitrary ways. Unlike ``mashup creation tools'' like Yahoo Pipes~\cite{pipes} or Microsoft Popfli~\cite{popfly}, we see Mash Maker not a tool for creating special-case mashup sites, but as a generalized tool that understands what you are doing and infers new mashups that can enhance your current experience, based on what others have tried in the past.

Users can contribute to Mash Maker in several different ways. They can teach Mash Maker how to understand new kinds of web site, they can write new widgets, and they can show Mash Maker new ways that it can improve web pages that contain particular kinds of data. A user teaches Mash Maker how to extract information from a particular kind of web page by opening the Mash Maker extractor editor (Figure~\ref{extractedit}) and picking out examples of things on the page that the user thinks is interesting. As more users give Mash Maker more examples, Mash Maker gets better at understanding what pages mean. Unlike tools like Dapper~\cite{dapper} extractors are not owned by particular users. Instead an extractor is built up from examples given by all users on the web.

Given the huge number of differently formatted web sites on the web, it would not be practical for Mash Maker to be able to understand such a large range of web sites without users participating to teach in what different sites mean. For the users, the benefit of teaching Mash Maker how to understand a web site is that they get to use an enhanced version of the web site that Mash Maker has improved for them.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../mmpics/mapinsert.png}
	\caption{Using Mash Maker to add a map to a page}
	\label{mapinsert}
	\end{center}
\end{figure}

%\begin{figure}[tb]
%	\begin{center}
%	\includegraphics[width=6cm]{../mmpics/layers.png}
%	\caption{The layers of Mash Maker}
%	\label{layers}
%	\end{center}
%\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../mmpics/extractor_summary.png}
	\caption{Any user can teach Mash Maker how to understand new pages}
	\label{extractedit}
	\end{center}
\end{figure}

\section{Patterns vs Instances}

Users teach Mash Maker ``patterns'' that Mash Maker can use to understand a large number of similarly formatted web pages (e.g. how to understand a flight listing on expedia). This differs from Think Link, in which users pick out individual instances of factual claims which are not generalized to automatically find more snippets.

In the future, we plan to extend Think Link with natural language processing technology so that Think Link can automatically find new snippets, based on the examples it has been given. For example, if many users have shown Think Link example snippets that make the claim ``global warming is man made'', then Think Link could use these examples to find other snippets that may also be making this claim. At the simplest level, this could be done using simple textual similarity, similar to that done by Google Book Quotations~\cite{quotations}.

\section{Related Work}

The notion of a ``participatory mashup'' is somewhat fuzzy, and indeed some previous work can be considered to fit this description to some extent. To be a ``true'' participatory mashup, we believe a tool should not just allow users to contribute content, but allow users to teach it how to understand the meaning of content that already exists on the web, and use this knowledge to help other users of the tool.

reCAPTCHA~\cite{recaptcha} gives users the task of correctly transcribing scanned books as a test to see if they are human. Users thus unintentionally help machines better understand this information. Luis von Ahn has also shown how users can be persueded to teach a system what data means by making it fun~\cite{vonahn}. Our approach to persueding users to teach us what data means is to make this data immediately useful to them.

Online mashup creation tools such as Yahoo Pipes~\cite{pipes} or Microsoft Popfly~\cite{popfly} allow users to contribute new mashups. These tools treat each mashup as a separate entity and do not enable users to contribute knowledge about the web that can be used by other mashups.

Dapper~\cite{dapper} allows users to create new web scrapers, effectively creating APIs from web sites. This is similar to the extractor editor in Think Link. The key difference is that each scraper users create is treated as a separate entity, owned by a particular user, rather than as a pool of knowledge about the web that can be shared and edited by all users.

Like Think Link, SpinSpotter~\cite{spinspotter} also uses a browser plugin to help users identify and share instanes of media bias and misrepresentation. SpinSpotter allows users to annotate web pages with comments about the spin they think is present and suggest textual edits. This differs from Think Link, which attempts to understand what claims are being made and relate them to claims made elsewhere on the web.

FreeBase~\cite{freebase} is an open database of knowledge that anyone can contribute to. While FreeBase does not understand the meaning of existing web sites, it does allow users to contribute knowledge that mashups can use.

\section{Acknowledgments}

We would like to think Allison Woodruff, Tye Rattenbury, Prashant Gandhi, Eric Brewer, and all our user study participants for all their help during the design of Think Link and Mash Maker. Think Link and Mash Maker both use icons from the free FamFamFam Silk~\cite{silkicons} collection.

\bibliographystyle{abbrv}
\bibliography{biblio}

\end{document}

### 2008-09-20 papers/cscw_thinklink/cscw_thinklink.tex
New paper for CSCW workshop

--- 2008-09-20 papers/cscw_mash/cscw_mash.tex
@@
 %
-\toappear{Submitted to the Tinkering, Tailoring, and Mashing workshop at CSCW 2008}
+\toappear{Submitted for review to CHI 2009.}
 
@@
 \begin{abstract}
-Most mashups concern themselves with data that is fairly easy for a machine to understand: addresses, phone numbers, information available through APIs, or information that can be scraped from a small set of popular web sites.
+Most mashups produced so far have concerned themselves with structured machine readable, generated from databases, or written in very standard formats.
+Addresses, phone numbers, products, personal profiles, information available through APIs, and information that can be scraped from well-understood web site templates.
 
-However much of the most interesting information on the web is not in a form that a computer can easily understand.
-It may be in natural language text, or it may be in the long tail of web sites that developers have not found it worthwhile to write scrapers for.
+However much of the most interesting information on the web is not in forms that a computer can easily understand.
+It may be in natural language text, or it may be in web site templates that our tool does not yet understand.
 
-In this paper, we promote the approach of ``participatory mashups'' in which the users of the mashup also teach the mashup ways that it can understand new data.
+In this paper, we discuss the alternative approach of ``participatory mashups'' in which the users of the mashup also teach the mashup ways that it can understand new data.
 As examples, we present our work on Think Link, which connects factual statements on the web to related statements elsewhere, and Mash Maker, which attempts to understand the meaning of structured data on arbitrary web pages.
@@
 
-If we understand what the information on a page means then we can do useful things with it.
-We can connect the information to information elsewhere that might be relevant, we can compute new information from the information we have, and we can present users with new interfaces that are more useful than that provided by any individual site.
+If we understand what the information on a page means, then we can do useful things with it.
+We can connect the information to information elsewhere that might be relevant, we can compute new information from the information we have, and we can present users with new interfaces that are more powerful than that provided by any individual site.
 
@@
 Addresses follow an easily recognized pattern, and have led to a large number of useful mashups which plot various things on maps or work out what things are near to other things.
-Similarly, many mashups have made use of data that is available from APIs, or that can be easily scraped from popular web pages that the mashup has been hard-coded to understand.
+Similarly, many mashups have made use of data that is available from APIs, or that can be easily scraped from web pages that have been generated from databases.
 
-But what about everything else?
+However much of the most interesting information on the web does not have a form that can be easily mashed up.
 
-Much of the most interesting information on the web is available as unstructured natural language text: arguments, ideas, opinions, factual claims, jokes.
-Much of this is information that could benefit a lot from being mashed up.
-For example ``which of these claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this claim?'', or ``what ideas on this site would I be likely to find most interesting?''.
+Most mashups produced so far have concerned themselves with structured machine readable, generated from databases, or written in very standard formats.
+Addresses, phone numbers, products, personal profiles, and information laid out from standard templates.
 
-Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be very interesting.
-For example, tables of data that have been entered by hand, or one of the many tiny web services that display data from a database backend using their own custom template that nobody has ever written a scraper for.
+But a lot of the most interesting information on the web isn't like this.
+Much of the web consists of information written as unstructured natural language text.
+Arguments, ideas, opinions, factual claims, jokes.
+Information that cannot be easily be accessed using an API or a screen scraper.
 
-In this approach we argue for ``participatory mashups'' as a way to open up access to this data.
-In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and connecting information in new ways.
-By teaching a participatory mashup the meaning of some data, the user helps themselves, since they can now include this data in their mashup, but they also help the wider community of users, since all other users can now benefit from the system understanding this data.
+We believe that people have the potential to benefit a lot by applying mashups to such data, understanding, connecting, and visualizing it in new ways.
+What other web sites oppose this opinion?
+What ideas would I need to understand in order to understand this idea?
+Do by friends agree with this?
+Is there a more respectable source that also voices this idea?
 
-We motivate this approach using two mashup tools that we have built.
-Think Link allows users to identify factual claims that they read on web pages and connect them to related factual claims on other sites, including claims that may oppose the original claim.
-Mash Maker allows users to teach it the meaning of structured data on arbitrary web sites, and then enhances these web sites to make them more useful, guided by example improvements provided by users.
+In this paper we discuss our work with Think Link, a tool that allows user to identify factual claims made in documents, and uses this to connect web pages to other web pages that make related claims.
 
-More generally, we consider a tool to be a ``participatory mashup'' if it relies on users to teach it what information on the web means, and how that information is connected together.
-We argue that this is an approach that other applications could also use to help them understand the web.
+People have created
 
-\section{Think Link}
+ The information on one web page can be connected to information on other web pages, structural proper
 
@@
 	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/sidebar_diagram.png}
+	\caption{The margin summarizes the key claims on the page}
+	\label{margin}
+	\end{center}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
 	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
@@
 
-Much concern has been expressed recently about biased or inaccurate information on web sites~\cite{bbcwebwarning,wikifalse}, and the media echo chamber problem in which people read web sites that feed their own views back to them, rather than exposing them to the opposing opinions held by other groups~\cite{echochamber,echochamber2}.
-
-Think Link~\cite{thinklink} is a Firefox extension that helps users evaluate the truth of statements they read, helps users be more easily exposed to a range of ideas and opinions that they might not otherwise encounter.
-
-As a user browses the web, Think Link highlights snippets of text that other users have identified as making claims that are interesting or contraversial (Figure~\ref{highlight}).
-Interesting claims are highlighted in yellow, and contraversial claims are highlighted in red.
-If a user clicks on a highlighted snippet, Think Link will display an interface that allows a user to easily find snippets on other web pages that make related claims, including snippets that argue against the opinion put forward by the highlighted snippet (Figures~\ref{claimview} and \ref{claimbrowse_diagram}).
-Think Link allows a user to easily access the best arguments for and against a claim, including arguments they might not otherwise have come across because they would not have been voiced by the web sites that the reader normally reads.
-
-Think Link maintains a graph of known factual claims, their relationship to each other, and the snippets that hold these claims (Figure~\ref{summarygraph}).
-This graph is built entirely by users of the tool.
-Users create claims, users connect claims, and users identify snippets making claims.
-Similarly, users vote for snippets, claims, or connections that they believe are particularly important.
-
-This graph allows one to ask interesting questions such as ``Which snippets on this page make claims that are opposed by snippets elsewhere on them web?'', ``What is the most trustworthy news source that makes this claim?'', ``What do my friends think about this idea?'', ``What are the most interesting claims about this topic that I haven't read before'', or ``What is the best argument against this claim, and what would be the best counter-argument to that?''.
-
 \begin{figure*}[tb]
 	\begin{center}
-	\includegraphics[width=14cm]{../screenshots/newsnip_all.png}
+	\includegraphics[width=16cm]{../screenshots/newsnip_all.png}
 	\caption{Process for creating a new snippet}
@@
 
-Identifying factual claims and the connections between them automatically would be very difficult using the current generation of natural language processing and automated reasoning tools; however this is quite an easy task for humans.
-To create a new snippet, a user selects the text that is making an interesting factual claim, and then uses a claim browser interface to identify the claim being made (Figure~\ref{createprocess}).
-Users can connect claims together using a simple drag and drop interface.
-
-Our user study participants identified several reasons why they would want to mark up factual claims in documents they found.
-The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found.
-One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
-The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
-
-Like the work of Luis von Ahn~\cite{vonahn,recaptcha} or the ``invisible hand'' or Adam Smith the intention is that people should be motivated by self interest to do something that benefits the wider community.
-
-\section{Mash Maker}
-
-Mash Maker~\cite{mashmaker} is a browser extension that understands the meaning of the pages that users browse and suggests ways that it can improve the current page so as to be more useful to the user.
-Mash Maker relies on users to teach it both how to understand web pages, and also how particular kinds of web page might be improved in interesting ways.
-
-As views a web page, Mash Maker will suggest ways that it can make the page more useful, and suggest these improvements on its toolbar.
-If the user clicks on the button for such an improvement then Mash Maker will apply it to the current page, potentially using other web sites and remote APIs, and potentially applying widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}).
-Mash Maker suggests improvements based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behaviour of other users.
-
-Our intention is that users should be able to use Mash Maker to enhance arbitrary web sites in arbitrary ways.
-Unlike ``mashup creation tools'' like Yahoo Pipes~\cite{pipes} or Microsoft Popfli~\cite{popfly}, we see Mash Maker not a tool for creating special-case mashup sites, but as a generalized tool that understands what you are doing and infers new mashups that can enhance your current experience, based on what others have tried in the past.
-
-Users can contribute to Mash Maker in several different ways.
-They can teach Mash Maker how to understand new kinds of web site, they can write new widgets, and they can show Mash Maker new ways that it can improve web pages that contain particular kinds of data.
-A user teaches Mash Maker how to extract information from a particular kind of web page by opening the Mash Maker extractor editor (Figure~\ref{extractedit}) and picking out examples of things on the page that the user thinks is interesting.
-As more users give Mash Maker more examples, Mash Maker gets better at understanding what pages mean.
-Unlike tools like Dapper~\cite{dapper} extractors are not owned by particular users.
-Instead an extractor is built up from examples given by all users on the web.
-
-Given the huge number of differently formatted web sites on the web, it would not be practical for Mash Maker to be able to understand such a large range of web sites without users participating to teach in what different sites mean.
-For the users, the benefit of teaching Mash Maker how to understand a web site is that they get to use an enhanced version of the web site that Mash Maker has improved for them.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../mmpics/mapinsert.png}
-	\caption{Using Mash Maker to add a map to a page}
-	\label{mapinsert}
-	\end{center}
-\end{figure}
-
-%\begin{figure}[tb]
-%	\begin{center}
-%	\includegraphics[width=6cm]{../mmpics/layers.png}
-%	\caption{The layers of Mash Maker}
-%	\label{layers}
-%	\end{center}
-%\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{../mmpics/extractor_summary.png}
-	\caption{Any user can teach Mash Maker how to understand new pages}
-	\label{extractedit}
-	\end{center}
-\end{figure}
-
-\section{Patterns vs Instances}
-
-Users teach Mash Maker ``patterns'' that Mash Maker can use to understand a large number of similarly formatted web pages (e.g.
-how to understand a flight listing on expedia).
-This differs from Think Link, in which users pick out individual instances of factual claims which are not generalized to automatically find more snippets.
-
-In the future, we plan to extend Think Link with natural language processing technology so that Think Link can automatically find new snippets, based on the examples it has been given.
-For example, if many users have shown Think Link example snippets that make the claim ``global warming is man made'', then Think Link could use these examples to find other snippets that may also be making this claim.
-At the simplest level, this could be done using simple textual similarity, similar to that done by Google Book Quotations~\cite{quotations}.
-
-\section{Related Work}
-
-The notion of a ``participatory mashup'' is somewhat fuzzy, and indeed some previous work can be considered to fit this description to some extent.
-To be a ``true'' participatory mashup, we believe a tool should not just allow users to contribute content, but allow users to teach it how to understand the meaning of content that already exists on the web, and use this knowledge to help other users of the tool.
-
-reCAPTCHA~\cite{recaptcha} gives users the task of correctly transcribing scanned books as a test to see if they are human.
-Users thus unintentionally help machines better understand this information.
-Luis von Ahn has also shown how users can be persueded to teach a system what data means by making it fun~\cite{vonahn}.
-Our approach to persueding users to teach us what data means is to make this data immediately useful to them.
-
-Online mashup creation tools such as Yahoo Pipes~\cite{pipes} or Microsoft Popfly~\cite{popfly} allow users to contribute new mashups.
-These tools treat each mashup as a separate entity and do not enable users to contribute knowledge about the web that can be used by other mashups.
-
-Dapper~\cite{dapper} allows users to create new web scrapers, effectively creating APIs from web sites.
-This is similar to the extractor editor in Think Link.
-The key difference is that each scraper users create is treated as a separate entity, owned by a particular user, rather than as a pool of knowledge about the web that can be shared and edited by all users.
-
-Like Think Link, SpinSpotter~\cite{spinspotter} also uses a browser plugin to help users identify and share instanes of media bias and misrepresentation.
-SpinSpotter allows users to annotate web pages with comments about the spin they think is present and suggest textual edits.
-This differs from Think Link, which attempts to understand what claims are being made and relate them to claims made elsewhere on the web.
-
-FreeBase~\cite{freebase} is an open database of knowledge that anyone can contribute to.
-While FreeBase does not understand the meaning of existing web sites, it does allow users to contribute knowledge that mashups can use.
-
 \section{Acknowledgments}
 
-We would like to think Allison Woodruff, Tye Rattenbury, Prashant Gandhi, Eric Brewer, and all our user study participants for all their help during the design of Think Link and Mash Maker.
-Think Link and Mash Maker both use icons from the free FamFamFam Silk~\cite{silkicons} collection.
+We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link.
+Think Link uses icons from the free FamFamFam Silk~\cite{silkicons} collection.
 

### 2008-09-20 papers/cscw_mash/cscw_mash.tex
Spell check. This is the submitted version.

@@
 
-Some kinds of information are easier to understand than others, and mashups have so far understandably focussed on the low-hanging fruit.
+Some kinds of information are easier to understand than others, and mashups have so far understandably focused on the low-hanging fruit.
 Addresses follow an easily recognized pattern, and have led to a large number of useful mashups which plot various things on maps or work out what things are near to other things.
@@
 
-As a user browses the web, Think Link highlights snippets of text that other users have identified as making claims that are interesting or contraversial (Figure~\ref{highlight}).
-Interesting claims are highlighted in yellow, and contraversial claims are highlighted in red.
+As a user browses the web, Think Link highlights snippets of text that other users have identified as making claims that are interesting or controversial (Figure~\ref{highlight}).
+Interesting claims are highlighted in yellow, and controversial claims are highlighted in red.
 If a user clicks on a highlighted snippet, Think Link will display an interface that allows a user to easily find snippets on other web pages that make related claims, including snippets that argue against the opinion put forward by the highlighted snippet (Figures~\ref{claimview} and \ref{claimbrowse_diagram}).
@@
 
-As views a web page, Mash Maker will suggest ways that it can make the page more useful, and suggest these improvements on its toolbar.
+As views a web page, Mash Maker will suggest ways that it can make the page more useful, and suggest these improvements on its tool bar.
 If the user clicks on the button for such an improvement then Mash Maker will apply it to the current page, potentially using other web sites and remote APIs, and potentially applying widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}).
-Mash Maker suggests improvements based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behaviour of other users.
+Mash Maker suggests improvements based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behavior of other users.
 
 Our intention is that users should be able to use Mash Maker to enhance arbitrary web sites in arbitrary ways.
-Unlike ``mashup creation tools'' like Yahoo Pipes~\cite{pipes} or Microsoft Popfli~\cite{popfly}, we see Mash Maker not a tool for creating special-case mashup sites, but as a generalized tool that understands what you are doing and infers new mashups that can enhance your current experience, based on what others have tried in the past.
+Unlike ``mashup creation tools'' like Yahoo Pipes~\cite{pipes} or Microsoft Popfly~\cite{popfly}, we see Mash Maker not a tool for creating special-case mashup sites, but as a generalized tool that understands what you are doing and infers new mashups that can enhance your current experience, based on what others have tried in the past.
 
@@
 Users teach Mash Maker ``patterns'' that Mash Maker can use to understand a large number of similarly formatted web pages (e.g.
-how to understand a flight listing on expedia).
+how to understand a flight listing on Expedia).
 This differs from Think Link, in which users pick out individual instances of factual claims which are not generalized to automatically find more snippets.
@@
 Users thus unintentionally help machines better understand this information.
-Luis von Ahn has also shown how users can be persueded to teach a system what data means by making it fun~\cite{vonahn}.
-Our approach to persueding users to teach us what data means is to make this data immediately useful to them.
+Luis von Ahn has also shown how users can be persuaded to teach a system what data means by making it fun~\cite{vonahn}.
+Our approach to persuading users to teach us what data means is to make this data immediately useful to them.
 
@@
 
-Like Think Link, SpinSpotter~\cite{spinspotter} also uses a browser plugin to help users identify and share instanes of media bias and misrepresentation.
+Like Think Link, SpinSpotter~\cite{spinspotter} also uses a browser plugin to help users identify and share instances of media bias and misrepresentation.
 SpinSpotter allows users to annotate web pages with comments about the spin they think is present and suggest textual edits.

### 2008-09-26 papers/cscw_mash/cscw_mash.tex
Minor paper changes, and working on the data store

@@
 For example ``which of these claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this claim?'', or ``what ideas on this site would I be likely to find most interesting?''.
+While natural language processing techniques have achieved a lot, understanding such information in a fully automated way is hard.
 
 Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be very interesting.
-For example, tables of data that have been entered by hand, or one of the many tiny web services that display data from a database backend using their own custom template that nobody has ever written a scraper for.
+For example, tables of data that have been entered by hand, or one of the many tiny web sites that display data from a database backend using their own custom template that nobody has ever written a scraper for.
 
-In this approach we argue for ``participatory mashups'' as a way to open up access to this data.
-In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and connecting information in new ways.
-By teaching a participatory mashup the meaning of some data, the user helps themselves, since they can now include this data in their mashup, but they also help the wider community of users, since all other users can now benefit from the system understanding this data.
+In this paper we argue for ``participatory mashups'' as a way to open up access to this data.
+In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and how to connect information in new ways.
+By teaching a participatory mashup the meaning of some data, the user helps themselves, since the new information becomes part of the mashup they are interacting with, but they also help the wider community of users, since all other users can now benefit from the system understanding this data.
 
 We motivate this approach using two mashup tools that we have built.
-Think Link allows users to identify factual claims that they read on web pages and connect them to related factual claims on other sites, including claims that may oppose the original claim.
+Think Link allows a user to identify factual claims on web pages, and uses this information to expose users to opposing points of view.
 Mash Maker allows users to teach it the meaning of structured data on arbitrary web sites, and then enhances these web sites to make them more useful, guided by example improvements provided by users.

### 2008-09-29 papers/cscw_mash/cscw_mash.tex
Paper updates, largely guided by Beth suggestions

@@
        \affaddr{University of California at Berkeley}\\
-       \email{trush@berkeley.edu}
+       \email{trush@cs.berkeley.edu}
 }
@@
 If we understand what the information on a page means then we can do useful things with it.
-We can connect the information to information elsewhere that might be relevant, we can compute new information from the information we have, and we can present users with new interfaces that are more useful than that provided by any individual site.
+We can connect the information to information elsewhere that might be relevant, compute new information from the information we have, and present users with new interfaces that are more useful than that provided by any individual site.
 
@@
 
-Much of the most interesting information on the web is available as unstructured natural language text: arguments, ideas, opinions, factual claims, jokes.
+Much of the most interesting information on the web is in the form of unstructured natural language text: arguments, ideas, opinions, factual claims, jokes.
 Much of this is information that could benefit a lot from being mashed up.
-For example ``which of these claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this claim?'', or ``what ideas on this site would I be likely to find most interesting?''.
+For example ``which of these factual claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this assertion?'', or ``what ideas on this site would I be likely to find most interesting?''.
 While natural language processing techniques have achieved a lot, understanding such information in a fully automated way is hard.
 
-Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be very interesting.
+Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be interesting.
 For example, tables of data that have been entered by hand, or one of the many tiny web sites that display data from a database backend using their own custom template that nobody has ever written a scraper for.
@@
 In this paper we argue for ``participatory mashups'' as a way to open up access to this data.
-In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and how to connect information in new ways.
-By teaching a participatory mashup the meaning of some data, the user helps themselves, since the new information becomes part of the mashup they are interacting with, but they also help the wider community of users, since all other users can now benefit from the system understanding this data.
+In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and new connections between things.
+By teaching a participatory mashup the meaning of the data on a particular web page, the user helps themselves, since the mashup can now enhance that information for them, but they also help the wider community of users, since other users looking at the same page will be able to see an enhanced view, and the information on that page can now be used to enhance other pages on the web.
 
@@
 
-More generally, we consider a tool to be a ``participatory mashup'' if it relies on users to teach it what information on the web means, and how that information is connected together.
+More generally, we consider a tool to be a ``participatory mashup'' if it relies on users to teach it how to interpret and connect information on the web.
 We argue that this is an approach that other applications could also use to help them understand the web.
@@
 
-Much concern has been expressed recently about biased or inaccurate information on web sites~\cite{bbcwebwarning,wikifalse}, and the media echo chamber problem in which people read web sites that feed their own views back to them, rather than exposing them to the opposing opinions held by other groups~\cite{echochamber,echochamber2}.
+Much concern has been expressed recently about biased or inaccurate information on web sites~\cite{bbcwebwarning,wikifalse}, and the media echo chamber problem in which people read web sites that feed their own views back to them, rather than exposing people to the opposing opinions held by other groups~\cite{echochamber,echochamber2}.
 
-Think Link~\cite{thinklink} is a Firefox extension that helps users evaluate the truth of statements they read, helps users be more easily exposed to a range of ideas and opinions that they might not otherwise encounter.
+Think Link~\cite{thinklink} is a Firefox extension that helps users evaluate the truth of statements they read exposes users to a range of ideas and opinions that they might not otherwise encounter.
 
@@
 This graph is built entirely by users of the tool.
-Users create claims, users connect claims, and users identify snippets making claims.
+Users create claims, connect claims, and identify snippets making claims.
 Similarly, users vote for snippets, claims, or connections that they believe are particularly important.
@@
 
-Our user study participants identified several reasons why they would want to mark up factual claims in documents they found.
-The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found.
-One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
-The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
-
-Like the work of Luis von Ahn~\cite{vonahn,recaptcha} or the ``invisible hand'' or Adam Smith the intention is that people should be motivated by self interest to do something that benefits the wider community.
+Our user study participants identified several reasons why they would want to identify and connect factual claims in documents they found.
+The most common reason was to organize information they had found while researching a topic or writing a document.
+One user (who is an active blogger) also expressed an interest in finding and marking up statements that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
+The same user also expressed an interest in marking up claims made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
 
@@
 
-Mash Maker~\cite{mashmaker} is a browser extension that understands the meaning of the pages that users browse and suggests ways that it can improve the current page so as to be more useful to the user.
-Mash Maker relies on users to teach it both how to understand web pages, and also how particular kinds of web page might be improved in interesting ways.
+Mash Maker~\cite{mashmaker} is a browser extension that understands the meaning of the web pages that users browse and suggests ways that it can enhance the current page so as to be more useful to the user.
+Mash Maker relies on users to teach it both how to understand web pages, and also how particular kinds of web pages might be enhanced in interesting ways.
 
-As views a web page, Mash Maker will suggest ways that it can make the page more useful, and suggest these improvements on its tool bar.
-If the user clicks on the button for such an improvement then Mash Maker will apply it to the current page, potentially using other web sites and remote APIs, and potentially applying widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}).
-Mash Maker suggests improvements based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behavior of other users.
+When a user views a web page, Mash Maker will suggest on its toolbar ways that it can enhance the web site to make it more useful.
+If the user clicks on the button for such an enhancement then Mash Maker will apply the enhancement to the current page, potentially using other web sites and remote APIs.
+An improvement can also use third-party widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}).
+Mash Maker suggests enhancement based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behavior of other users.
 
@@
 They can teach Mash Maker how to understand new kinds of web site, they can write new widgets, and they can show Mash Maker new ways that it can improve web pages that contain particular kinds of data.
-A user teaches Mash Maker how to extract information from a particular kind of web page by opening the Mash Maker extractor editor (Figure~\ref{extractedit}) and picking out examples of things on the page that the user thinks is interesting.
-As more users give Mash Maker more examples, Mash Maker gets better at understanding what pages mean.
+A user teaches Mash Maker how to extract information from a particular kind of web page by opening the Mash Maker extractor editor (Figure~\ref{extractedit}) and picking out examples of things on the page that the user thinks are interesting.
+As users give Mash Maker more examples, Mash Maker gets better at understanding what pages mean.
 Unlike tools like Dapper~\cite{dapper} extractors are not owned by particular users.
@@
 
-Given the huge number of differently formatted web sites on the web, it would not be practical for Mash Maker to be able to understand such a large range of web sites without users participating to teach in what different sites mean.
+Given the huge number of differently formatted web sites on the web, it would not be practical for Mash Maker to be able to understand such a large range of web sites without users providing some form of guidance.
 For the users, the benefit of teaching Mash Maker how to understand a web site is that they get to use an enhanced version of the web site that Mash Maker has improved for them.
@@
 
-Users teach Mash Maker ``patterns'' that Mash Maker can use to understand a large number of similarly formatted web pages (e.g.
+Users teach Mash Maker ``patterns'' that it can use to understand a large number of similarly formatted web pages (e.g.
 how to understand a flight listing on Expedia).
@@
 For example, if many users have shown Think Link example snippets that make the claim ``global warming is man made'', then Think Link could use these examples to find other snippets that may also be making this claim.
-At the simplest level, this could be done using simple textual similarity, similar to that done by Google Book Quotations~\cite{quotations}.
+At the simplest level, this could be done using textual similarity, similar to that done by Google Book Quotations~\cite{quotations}.
 
@@
 
-The notion of a ``participatory mashup'' is somewhat fuzzy, and indeed some previous work can be considered to fit this description to some extent.
+The notion of a ``participatory mashup'' is somewhat fuzzy, and some existing systems fit this description to some extent.
 To be a ``true'' participatory mashup, we believe a tool should not just allow users to contribute content, but allow users to teach it how to understand the meaning of content that already exists on the web, and use this knowledge to help other users of the tool.
 
-reCAPTCHA~\cite{recaptcha} gives users the task of correctly transcribing scanned books as a test to see if they are human.
-Users thus unintentionally help machines better understand this information.
-Luis von Ahn has also shown how users can be persuaded to teach a system what data means by making it fun~\cite{vonahn}.
-Our approach to persuading users to teach us what data means is to make this data immediately useful to them.
+reCAPTCHA~\cite{recaptcha} gives a user the task of correctly transcribing text from a scanned book as a test to see if the user is human.
+Users thus unintentionally help machines better understand the books.
+Luis von Ahn has also shown how users can be persuaded to help a machine understand things by making the process fun~\cite{vonahn}.
+We persuade users to show us how to understand things by using the information to help the user themselves.
 

### 2008-09-29 papers/cscw_mash/cscw_mash.tex
Final submitted version - after deadline extension

@@
 \begin{abstract}
-Most mashups concern themselves with data that is fairly easy for a machine to understand: addresses, phone numbers, information available through APIs, or information that can be scraped from a small set of popular web sites.
+Most mashups concern themselves with data that machines can understand fairly easily: addresses, phone numbers, information available through APIs, or information that can be scraped from a small set of popular web sites.
 
@@
 In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and new connections between things.
-By teaching a participatory mashup the meaning of the data on a particular web page, the user helps themselves, since the mashup can now enhance that information for them, but they also help the wider community of users, since other users looking at the same page will be able to see an enhanced view, and the information on that page can now be used to enhance other pages on the web.
+By teaching a participatory mashup the meaning of the data on a particular web page, the user helps themselves, since the mashup can now enhance that page for them, but they also help the wider community, since that information can now be used to produce mashups for others.
 
@@
 Think Link allows a user to identify factual claims on web pages, and uses this information to expose users to opposing points of view.
-Mash Maker allows users to teach it the meaning of structured data on arbitrary web sites, and then enhances these web sites to make them more useful, guided by example improvements provided by users.
+Mash Maker allows users to teach it the meaning of structured data on arbitrary web sites, and then enhances these web sites to make them more useful, guided by example enhancements provided by users.
 
 More generally, we consider a tool to be a ``participatory mashup'' if it relies on users to teach it how to interpret and connect information on the web.
-We argue that this is an approach that other applications could also use to help them understand the web.
+We argue that this is a useful technique for understanding the web.
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
+	\includegraphics[width=6.5cm]{../screenshots/claim_popup_crop2.png}
 	\caption{Click on a claim to investigate evidence for and against it}
@@
 	\begin{center}
-	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
+	\includegraphics[width=8.2cm]{../screenshots/summary_graph.png}
 	\caption{Think link connects claims to each other and to web snippets}
@@
 	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
+	\includegraphics[width=8.4cm]{../screenshots/claimbrowse_diagram.png}
 	\caption{The claim browser visualizes the claim graph}
@@
 
-Much concern has been expressed recently about biased or inaccurate information on web sites~\cite{bbcwebwarning,wikifalse}, and the media echo chamber problem in which people read web sites that feed their own views back to them, rather than exposing people to the opposing opinions held by other groups~\cite{echochamber,echochamber2}.
+Much concern has been expressed recently about biased or inaccurate information on web sites~\cite{bbcwebwarning,wikifalse}, and the tendency for people to get information from sources that feed their own views back to them, rather than exposing them to opposing opinions held by other groups~\cite{echochamber,echochamber2}.
 
-Think Link~\cite{thinklink} is a Firefox extension that helps users evaluate the truth of statements they read exposes users to a range of ideas and opinions that they might not otherwise encounter.
+Think Link~\cite{thinklink} is a Firefox extension that helps users evaluate the truth of statements they read and exposes users to a range of ideas and opinions that they might not otherwise encounter.
 
 As a user browses the web, Think Link highlights snippets of text that other users have identified as making claims that are interesting or controversial (Figure~\ref{highlight}).
-Interesting claims are highlighted in yellow, and controversial claims are highlighted in red.
+Interesting claims are highlighted in yellow and controversial claims are highlighted in red.
 If a user clicks on a highlighted snippet, Think Link will display an interface that allows a user to easily find snippets on other web pages that make related claims, including snippets that argue against the opinion put forward by the highlighted snippet (Figures~\ref{claimview} and \ref{claimbrowse_diagram}).
-Think Link allows a user to easily access the best arguments for and against a claim, including arguments they might not otherwise have come across because they would not have been voiced by the web sites that the reader normally reads.
+Think Link allows a user to easily access the best arguments for and against a claim, including arguments they might not otherwise have come across because they would not have been voiced by the web sites that the user normally reads.
 
-Think Link maintains a graph of known factual claims, their relationship to each other, and the snippets that hold these claims (Figure~\ref{summarygraph}).
+Think Link maintains a graph of known factual claims, their relationship to each other, and the snippets (Figure~\ref{summarygraph}).
 This graph is built entirely by users of the tool.
@@
 
-Mash Maker~\cite{mashmaker} is a browser extension that understands the meaning of the web pages that users browse and suggests ways that it can enhance the current page so as to be more useful to the user.
+Mash Maker~\cite{mashmaker} is a browser extension that understands the meaning of the web pages that users browse and suggests ways that it can enhance the current page to be more useful to the user.
 Mash Maker relies on users to teach it both how to understand web pages, and also how particular kinds of web pages might be enhanced in interesting ways.
 
-When a user views a web page, Mash Maker will suggest on its toolbar ways that it can enhance the web site to make it more useful.
-If the user clicks on the button for such an enhancement then Mash Maker will apply the enhancement to the current page, potentially using other web sites and remote APIs.
-An improvement can also use third-party widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}).
-Mash Maker suggests enhancement based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behavior of other users.
+When a user views a web page, Mash Maker will suggest on its toolbar ways that it can enhance the web page to make it more useful.
+If the user clicks on the button for such an enhancement then Mash Maker will apply the enhancement to the current page, potentially using information from other web sites and remote APIs.
+An enhancement can also use third-party widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}).
+When suggesting enhancements, Mash Maker considers the meaning of the current page, the meaning of the pages that the user has recently browsed, the enhancements the user liked in the past, and the enhancements chosen by other users in similar circumstances.
 

### 2008-11-16 papers/web_of_ideas/rebuttal.txt
Work on rebuttal

We would like to thank the reviewers for their comments. We believe that we should have little difficulty making the suggested changes.

The reviewers focussed on two related concerns: the relation of Think Link to prior work on argumentation in hypermedia systems, and the simple nature of our claim graph.

-- simple structure of the claim graph --

The AC is correct that the simple "supports/opposes" model that we use does not thoroughly model the semantic relation between claims; indeed it is not intended to. There is a trade-off between making a system rich enough to model complex relations between claims, and making it simple enough that it does not overwhelm users.

The intention of our claim graph is not to provide a rigorous graph of a logical argument, but to provide a user with a list of things that they might want to look at in order to assemble such an argument in their head. For example, if we look at Toulmin's standard example of asserting British Citizenship, Toulmin would say:

  claim: Harry is a British Citizen
  grounds: Harry was born in Bermuda 
  warrant: A man born in Bermuda will be a British Citizen

but Think Link would consider both the "grounds" and "warrant" to be "supporting" claims and leave it to the user to understand how to form a logical argument from these claims.

It is also useful to compare to ClaimMaker, which expands Think Link's "supports" into proves, isEvidenceFor, agreesWith, and isConsistentWith.

Our claim graph is also a simplification of that of IBIS. We merge "arguments" and "positions" into "claims", and merge "issues" into our "topics". Thus, while it is possible to map any IBIS graph into a Think Link graph, some type information will be lost. Like SynView, we extend IBIS by allowing users to rate the links they believe to be important.

We do not claim that our graph structure is optimal, or even necessarily better than the standard IBIS structure. Indeed we have informally experimented with a number of other graph structures, including having a separate "question" type (like IBIS), and introducing a "related" link type between claims.

The focus of the paper is the idea of allowing users to overlay such a structure over the existing web. It is quite likely that the details of the graph structure will evolve as we observe how Think Link is used.

TODO: talk about "refines" and "because" for claims.

-- relation to past work in hypermedia --

We agree with the AC that the paper should include a discussion of ZENO; indeed an earlier draft of the paper included a paragraph on ZENO which was accidentally cut.

As the reviewers note, that has been a lot of past work on using hypermedia systems to model arguments, and our paper would benefit from a more through commentary on its relation to this work.

Many of the early hypermedia systems (e.g. NoteCards, Xanadu, Intermedia, gIBIS, TextNet, and Augment) included typed links that could be used to model arguments. TextNet in particular provided a rich vocabulary of link types for such things as "refutes" and "supports".

Several hypermedia systems were explicitly designed to allow users to create structured arguments. For example gIBIS presented a graphical view of arguments created in the IBIS model,  *** TODO: read more about how these differ ***

Unlike the web, many of these hypermedia systems assumed that a linkable object would be a small snippet of text (around 100 words for NoteCards) rather than a large scrollable page. Indeed one can see Think Link's snippets as being an attempt to move the web back to this model.

Many early hypermedia systems also allowed a user to visually browse the graph of connected nodes (e.g. NoteCards, Intermedia, PlaneText, gIBIS, Belvedere, and Aquanet). Again, this is a concept that Think Link reintroduces to the web. When one clicks on a Think Link snippet one is shown a claim graph that bears some similarity to the graph browsers from these early hypertext systems.

The main differences between Think Link and this prior work result from it's application to the existing web, and the design implications that this has.

Most of the early hypertext argumentation systems.

One can see Think Link's snippets as being an attempt to move back to this model.

Other notable examples include EUCLID, TRELLIS, JANUS, AQUANET, BELVEDER, InterNote, and gIBIS.

TODO: in-depth description of this work...

### 2008-11-16 papers/web_of_ideas/rebuttal.txt
Tightening the argument

@@
 
-The reviewers focussed on two related concerns: the relation of Think Link to prior work on argumentation in hypermedia systems, and the simple nature of our claim graph.
+The reviewers focussed on two related concerns: the simple nature of our claim graph, and the relationship of Think Link to prior work on argumentation in hypermedia systems.
 
--- simple structure of the claim graph --
+-- simple claim graph --
 
 The AC is correct that the simple "supports/opposes" model that we use does not thoroughly model the semantic relation between claims; indeed it is not intended to.
-There is a trade-off between making a system rich enough to model complex relations between claims, and making it simple enough that it does not overwhelm users.
+There is a trade-off between making a system rich enough to model complex relations, and making it simple enough that it does not confuse users.
 
-The intention of our claim graph is not to provide a rigorous graph of a logical argument, but to provide a user with a list of things that they might want to look at in order to assemble such an argument in their head.
+The intention of our claim graph is not to provide a rigorous graph of a logical argument, but give a user a list of things that they can use to assemble such an argument in their head.
 For example, if we look at Toulmin's standard example of asserting British Citizenship, Toulmin would say:
@@
 
-but Think Link would consider both the "grounds" and "warrant" to be "supporting" claims and leave it to the user to understand how to form a logical argument from these claims.
+We consider the grounds and warrant to be supporting claims and leave it to the user to understand how to form a logical argument from them.
 
-It is also useful to compare to ClaimMaker, which expands Think Link's "supports" into proves, isEvidenceFor, agreesWith, and isConsistentWith.
-
-Our claim graph is also a simplification of that of IBIS.
-We merge "arguments" and "positions" into "claims", and merge "issues" into our "topics".
+Our claim graph is a simplification of that of IBIS.
+IBIS arguments and positions turn into claims, IBIS issues turn into topics, and all links from issues to positions or arguments become "about".
 Thus, while it is possible to map any IBIS graph into a Think Link graph, some type information will be lost.
 Like SynView, we extend IBIS by allowing users to rate the links they believe to be important.
-
-We do not claim that our graph structure is optimal, or even necessarily better than the standard IBIS structure.
-Indeed we have informally experimented with a number of other graph structures, including having a separate "question" type (like IBIS), and introducing a "related" link type between claims.
+We also extend IBIS by linking to evidence in the form of snippets.
+Note that the "because" weakness we raised in our paper also applies to IBIS.
 
 The focus of the paper is the idea of allowing users to overlay such a structure over the existing web.
-It is quite likely that the details of the graph structure will evolve as we observe how Think Link is used.
-
-TODO: talk about "refines" and "because" for claims.
+We do not claim that our graph structure is optimal, or even necessarily better than IBIS.
+We have informally experimented with a number of other graph structures and it is likely that our graph structure will evolve as we learn from use in the field.
 
@@
 
-We agree with the AC that the paper should include a discussion of ZENO; indeed an earlier draft of the paper included a paragraph on ZENO which was accidentally cut.
+We agree with the AC that the paper should include a discussion of ZENO; indeed an earlier draft of the paper included a paragraph on ZENO and IBIS which was mistakenly cut during a late compression pass.
 
-As the reviewers note, that has been a lot of past work on using hypermedia systems to model arguments, and our paper would benefit from a more through commentary on its relation to this work.
+As the reviewers note, that has been a lot of past work on using hypermedia systems to model arguments, and we agree that our paper would benefit from a more through commentary on its relation to this work.
+We are more than happy to add such a discussion.
 
@@
 
-The main differences between Think Link and this prior work result from it's application to the existing web, and the design implications that this has.
-
-Most of the early hypertext argumentation systems.
-
-One can see Think Link's snippets as being an attempt to move back to this model.
-
-Other notable examples include EUCLID, TRELLIS, JANUS, AQUANET, BELVEDER, InterNote, and gIBIS.
-
-TODO: in-depth description of this work...
+The key contribution that Think Link has over this past work is that we are retrofitting a collaborative argument tool on top of the existing web, rather than creating a clean-slate system.
+This involves retrofitting a number of ideas from these early hypermedia systems onto the existing web, such as small snippets of text that can be linked into a graph, typed links, and browsable graphs of linked nodes.
+Think Link thus has one hypermedia system layered on top of another.
+At the bottom, we have the existing web, in which pages are linked together according to the desires of the author, and above that we have a second graph in which snippets from these pages are linked in a graph with claims and topics.

### 2008-11-18 papers/web_of_ideas/rebuttal.txt
Final submitted version of the rebuttal

@@
-We would like to thank the reviewers for their comments. We believe that we should have little difficulty making the suggested changes.
+We would like to thank the reviewers for their comments. We believe that we should have little difficulty making the requested changes.
 
-The reviewers focussed on two related concerns: the simple nature of our claim graph, and the relationship of Think Link to prior work on argumentation in hypermedia systems.
+The reviewers focused on two related concerns: the simple nature of our claim graph, and the relationship of Think Link to prior work on argumentation in hypermedia systems.
 
@@
 
-The AC is correct that the simple "supports/opposes" model that we use does not thoroughly model the semantic relation between claims; indeed it is not intended to.
-There is a trade-off between making a system rich enough to model complex relations, and making it simple enough that it does not confuse users.
-
-The intention of our claim graph is not to provide a rigorous graph of a logical argument, but give a user a list of things that they can use to assemble such an argument in their head.
-For example, if we look at Toulmin's standard example of asserting British Citizenship, Toulmin would say:
+There is a trade-off between making the claim graph rich enough to be useful, while making it simple enough that users are able to easy construct it.
+As the AC observes, our "supports/opposes" model ignores some of the details of argument structure.
+For example, if we look at Toulmin's standard example of asserting British citizenship, Toulmin would say:
 
@@
 
-We consider the grounds and warrant to be supporting claims and leave it to the user to understand how to form a logical argument from them.
+Think Link considers the grounds and warrant to both be supporting claims.
+Toulmin puts more information in his graph, at the cost of requiring users to understand how to put arguments into this form.
+Think Link makes it easier to create the graph, but the graph contains less information and a user reading the graph needs to infer the logical connections between claims themselves.
+
+Our intention is that Think Link allow users to identify things that are relevant to an argument for or against a claim, without requiring users to structure arguments an a rigorous logical way.
 
 Our claim graph is a simplification of that of IBIS.
-IBIS arguments and positions turn into claims, IBIS issues turn into topics, and all links from issues to positions or arguments become "about".
-Thus, while it is possible to map any IBIS graph into a Think Link graph, some type information will be lost.
+IBIS distinguishes between "issues" (e.g.
+"what should we buy?"), "positions" (e.g.
+"we should buy a porsche") and arguments (e.g.
+"a porsche is fast").
+We model both positions and arguments as claims.
+An IBIS issue can be either open (e.g.
+"what should we buy?"), or closed (e.g.
+"we should buy a porsche?").
+We model an open issue as a topic, and a closed issue as a claim.
+Similarly all IBIS link types can be meaningfully mapped onto Think Link link types.
+Thus, while one can map any IBIS graph into a Think Link graph, some type information will be lost.
 Like SynView, we extend IBIS by allowing users to rate the links they believe to be important.
 We also extend IBIS by linking to evidence in the form of snippets.
-Note that the "because" weakness we raised in our paper also applies to IBIS.
+Note that the "because" weakness raised in our paper also applies to IBIS.
 
-The focus of the paper is the idea of allowing users to overlay such a structure over the existing web.
+The focus of the paper is the idea of allowing users to overlay an argument structure over the existing web.
 We do not claim that our graph structure is optimal, or even necessarily better than IBIS.
@@
 
-As the reviewers note, that has been a lot of past work on using hypermedia systems to model arguments, and we agree that our paper would benefit from a more through commentary on its relation to this work.
-We are more than happy to add such a discussion.
+As the reviewers note, there has been a lot of work on using hypermedia systems to model arguments, and we agree that our paper would benefit from a more through discussion of the relation of Think Link to this work - which we are happy to add.
 
@@
 TextNet in particular provided a rich vocabulary of link types for such things as "refutes" and "supports".
+Several hypermedia systems were explicitly designed for argumentation (e.g.
+gIBIS, Belvedere, Aquanet, and TRELLIS).
 
-Several hypermedia systems were explicitly designed to allow users to create structured arguments.
-For example gIBIS presented a graphical view of arguments created in the IBIS model,  *** TODO: read more about how these differ ***
+Think Link's browsable claim graph and small snippets of text both hark back to earlier hypermedia systems.
+In many early hypermedia systems (e.g NoteCards) a linkable object is a small piece of text, rather than a large scrollable page.
+Similarly, many early hypermedia systems allow a user to visually browse the graph of connected nodes (e.g.
+NoteCards, Intermedia, PlaneText, gIBIS, Belvedere).
 
-Unlike the web, many of these hypermedia systems assumed that a linkable object would be a small snippet of text (around 100 words for NoteCards) rather than a large scrollable page.
-Indeed one can see Think Link's snippets as being an attempt to move the web back to this model.
+The key contribution that Think Link has over this past work is that we are layering a collaborative argument tool on top of the existing web, rather than creating a clean-slate argumentation tool.
+Think Link layers a new hypermedia system on top of an existing one.
+At the bottom, we have the existing web, in which scrollable pages are linked together according to the desires of the author.
+Above that we have a second hypermedia system in which snippets from the web pages are linked into a graph with claims and topics.
+Think Link thus provides users with a new, argument-focussed way to browse the web.
 
-Many early hypermedia systems also allowed a user to visually browse the graph of connected nodes (e.g.
-NoteCards, Intermedia, PlaneText, gIBIS, Belvedere, and Aquanet).
-Again, this is a concept that Think Link reintroduces to the web.
-When one clicks on a Think Link snippet one is shown a claim graph that bears some similarity to the graph browsers from these early hypertext systems.
-
-The key contribution that Think Link has over this past work is that we are retrofitting a collaborative argument tool on top of the existing web, rather than creating a clean-slate system.
-This involves retrofitting a number of ideas from these early hypermedia systems onto the existing web, such as small snippets of text that can be linked into a graph, typed links, and browsable graphs of linked nodes.
-Think Link thus has one hypermedia system layered on top of another.
-At the bottom, we have the existing web, in which pages are linked together according to the desires of the author, and above that we have a second graph in which snippets from these pages are linked in a graph with claims and topics.
+We would like to thank the AC and reviewers again for their help.

### 2009-03-10 papers/uist_thinklink/thinklink.tex
Started work on UIST paper + various other changes

%\documentclass{article}
\documentclass{chi2009}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}

\begin{document}

% --- Copyright notice ---
\conferenceinfo{UIST'09}{October 4-7, 2008, Victoria, BC, Canada}
\CopyrightYear{2009}
\crdata{x-xxxxx-xxx-x/xx/xxxx}

% Uncomment the following line to hide the copyright notice
\toappear{}
% ------------------------

\bibliographystyle{plain}

\title{Exposing Disputed Statements on the Web}

%%
%% Note on formatting authors at different institutions, as shown below:
%% Change width arg (currently 7cm) to parbox commands as needed to
%% accommodate widest lines, taking care not to overflow the 17.8cm line width.
%% Add or delete parboxes for additional authors at different institutions. 
%% If additional authors won't fit in one row, you can add a "\\"  at the
%% end of a parbox's closing "}" to have the next parbox start a new row.
%% Be sure NOT to put any blank lines between parbox commands!
%%

\author{
\parbox[t]{9cm}{\centering
	     {\em Author Name removed for blind review}\\
}
\parbox[t]{9cm}{\centering
	     {\em Author Name removed for blind review}}
}

\maketitle

%RULE: Don't cite media reports unless I have to

\abstract
We present DisagreeWeb, a browser extension that aims to let users see when the information they are reading presents only one side of a disputed issue. As the user browses the web, DisagreeWeb highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on such a disputed claim then DisagreeWeb will show tem an argument graph showing the best evidence for and against the claim being true, as determined by other users of DisagreeWeb.

\keywords{CSCW, sensemaking, web, browsers, collaboration, mind mapping}

\classification{H5.2 [Information interfaces and presentation]:
User Interfaces. - Graphical user interfaces.}

\terms{Design, Human Factors}

\keywords{Sense-making, Annotation, Argumentation, Web}

\tolerance=400 
  % makes some lines with lots of white space, but 	
  % tends to prevent words from sticking out in the margin

\section{INTRODUCTION}

The web provides users with a huge number of pages that they can read, but extracting accurate and balanced information from these pages can be difficult. Not everything on the web is accurate~\cite{Mintz2002,Neumann2003,Resnik98,Zhou2004} and many web sites have a strong political bias~\cite{Herman2002,Genzkow2007}. If a user is to form a rounded opinion about a topic then they will need to either stick to sources that they trust or spend time looking for evidence on other web sites that supports or opposes what they read. Even if a user tries hard to research every topic they read, they can still get caught out by beliefs that they had not realised were disputed.

In this paper we present DisagreeWeb, a tool helps users discover when information they read is disputed or presents only one side of a contentious issue. We hope that DisagreeWeb will make it easier for users to be be aware of points of view that contradict with those that they usually encounter.

When DisagreeWeb is used as a browser plugin it will highlight text on web pages that expresses or implies a disputed claim. If a user clicks on such a highlighted snippet then DisagreeWeb presents the user with a visualization of an argu

visualization that shows the user the best evidence for and against the claim, as judged by other users of DisagreeWeb.

that shows users when the information that they read conflicts with information available on other sources.

D

 DisagreeWeb is implemented as a browser extension

aims to let users see when the information they are reading conflicts with information from other sources.

DisagreeWeb is implemented as a browser extension.

The web suffers from filter failure~\cite{Shirky2008}.

Part of the problem is that conventional web browsers present the web as a network of connected pages, when it is often the case that what the user is really interested in is the factual claims made by those pages, and the connections between those claims. While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author. The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web. The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages). While this makes it easier for users to add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
	\caption{Click on a claim to investigate evidence for and against it}
	\label{claimview}
	\end{center}
\end{figure}

% \begin{figure}[tb]
% %	\begin{center}
%  	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
%  	\caption{Click on a claim to investigate evidence for and against it}
%  	\label{claimview}
% 	\end{center}
% \end{figure}

\section{HIGHLIGHTING CONTROVERSIAL CLAIMS}

\section{CONNECTING UP THE ARGUMENT}

\section{THE THINK LINK SYSTEM}

\section{USER STUDIES}

\section{CONCLUSIONS}

\bibliographystyle{abbrv}
\bibliography{refs}

\end{document}

### 2009-03-10 papers/uist_thinklink/uistSample.tex
Started work on UIST paper + various other changes

\documentclass{article}

\usepackage{times}
\usepackage{uist}

\begin{document}

% --- Copyright notice ---
\conferenceinfo{UIST'09}{October 4-7, 2008, Victoria, BC, Canada}
\CopyrightYear{2009}
\crdata{x-xxxxx-xxx-x/xx/xxxx}

% Uncomment the following line to hide the copyright notice
% \toappear{}
% ------------------------

\bibliographystyle{plain}

\title{Standard UIST Conference Format:\\
       Preparing Camera-Ready Submissions}

%%
%% Note on formatting authors at different institutions, as shown below:
%% Change width arg (currently 7cm) to parbox commands as needed to
%% accommodate widest lines, taking care not to overflow the 17.8cm line width.
%% Add or delete parboxes for additional authors at different institutions. 
%% If additional authors won't fit in one row, you can add a "\\"  at the
%% end of a parbox's closing "}" to have the next parbox start a new row.
%% Be sure NOT to put any blank lines between parbox commands!
%%

\author{
\parbox[t]{9cm}{\centering
	     {\em Author Name removed for blind review}\\
	     Affiliation removed for blind review\\
             Address removed for blind review\\
	     Address removed for blind review\\
	     Email removed for blind review\\
	     Optional Phone Number removed for blind review}
\parbox[t]{9cm}{\centering
	     {\em Author Name removed for blind review}\\
	     Affiliation removed for blind review\\
	     Address removed for blind review\\
	     Address removed for blind review\\
	     Email removed for blind review}
}

\maketitle

\abstract
Each paper should begin with an abstract, followed by a set of keywords, both
placed in the left column of the first page under the left half of the title.
All body text, such as this paragraph, should be set in 10 point Times Roman
type, with 11 points between successive baselines.  (We will repeat that later
in this document to make sure that you do not forget.)

\classification{H5.2 [Information interfaces and presentation]:
User Interfaces. - Graphical user interfaces.}

\terms{Design, Human Factors (Your general terms must be any of the
  following 16 designated terms: Algorithms, Management, Measurement,
  Documentation, Performance, Design, Economics, Reliability,
  Experimentation, Security, Human Factors, Standardization,
  Languages, Theory, Legal Aspects, Verification. See ~\cite{ACMTerms} for more details.)}

\keywords{Guides, instructions, formatting.}

\tolerance=400 
  % makes some lines with lots of white space, but 	
  % tends to prevent words from sticking out in the margin

\section{INTRODUCTION}
The {\em UIST} proceedings represent the final archival records of
the conference.  We would like the proceedings to have a
uniform, high quality appearance.  To accomplish this, authors must follow
the format specified here.

In essence, we ask that whatever text formatting program you use,
you format your paper exactly like this document.  Please
match the type style, type size, line spacing, indentation, and layout
format as closely as you can.  In fact, if you received this document online
as a LaTeX file, along with its accompanying uist.sty style file, you can
use it as a template.

Use an A4 or 8.5"$\times$11" sheet of paper. Center the image on the page.
The whole image of your text must {\em completely} fit in a 17.8 cm$\times$23.5 cm box. 
If you are not using LaTeX with the uist.sty style
file, then the recommendations we have included here should help you match this
sample with the facilities you do have, such as Microsoft Word.

\section{TITLE AND AUTHORS}
\textbf{The authors list should be removed for blind review.}

The title, author's names and affiliations run across the full width of the
page.  We also recommend phone number and e-mail address, if available.  (See
the top of this page for an example of two names with different addresses.
If only one address is needed, center all text on the page.)

Here are the typographic details:
\begin{itemize}
\item Title area: 1 column, 5.9 cm (2 1/3") length, 17.8 cm (7") width.
\item Title: 18 point Helvetica Bold---mixed cases
\item Names: 12 point Times Italic
\item Addresses, Telephone, E-mail:  12 point Times Roman
\end{itemize}

\section{FIRST PAGE COPYRIGHT NOTICE}
Remember to leave 2.54 cm of blank space at the bottom of the left
column of the first  page,  as on this page. You must leave this space for
the copyright notice on {\em all} submissions intended for publication in the
proceedings.

Please note that the first author of all accepted submissions
will have to sign a copyright release form.  Those forms will be sent with the
acceptance letters and need to be returned rapidly.  We encourage the contact 
persons of each submission to keep track of their co-authors' locations because 
they will be responsible for rapidly collecting the signatures.

\section{NUMBER OF PAGES}
Submissions have the following page limits:
\begin{itemize}
\item Papers: 10 pages maximum
\item TechNotes: 4 pages maximum
\end{itemize}

\section{TWO COLUMNS}
All body text should be in 10 point Times Roman, with 11 points between
successive baselines.

After the title use a double-column format as shown here. Column width is 8.5
cm, with 0.8 cm between columns (for a total image width still equal to 17.8
cm).  Total text length should remain between 23.2 and 24 cm (9 1/4") .
Right margins should be justified, not ragged.   Separate each paragraph by a
blank line (and do not indent them)  Hyphenation is at your own discretion.
If at all possible, the two columns of the last page should be of equal length.
(The  LaTeX uist.sty file does not do this automatically, so
you will need to insert the commands \verb+\linebreak+ and \verb+\newpage+
at an appropriate point on the last page to justify the current line and
force a new column.)

\section{SECTIONS}
The title of a section should be in 9 point Helvetica Bold font in all
capitals. Notice that the sections, subsections, and subsubsections are not
numbered in this document, but you may number them if you want.

\subsection{Subsections}
The title of a subsection should be in 9 point Helvetica Bold with only the
initial letters of each word capitalized. (Note: Words like ``the'' and ``a''
are not capitalized unless they start a title.)

\subsubsection{Subsubsections.} The heading for a subsubsection should be in
9 point Helvetica Oblique (italic) with initial letters
capitalized. (Note: Words like ``the'' and ``a'' are not capitalized
unless they start a title.)  The subsubsection heading should {\em not}
appear on its own separate line.

\section{TYPESETTING}
Please use the fonts specified in this description
so that we can produce a conference proceedings that looks like a unified
document, rather than a collection of unrelated papers thrown
together.  The body of your paper should use 10 point Times Roman type,
set with an 11 point vertical spacing between baselines (also known as
1 point of leading).
Do not use a sans-serif font (e.g., Helvetica),  except for emphasis, headings
and the title, as described above.
Computer Modern Roman or another font with serifs should be used {\em only} 
as a last resort if Times Roman is not available. 
Macintosh users should use the font named Times.

\section{FIGURES}
Figures should be inserted at the appropriate point in your text, or
optionally floated to the top or bottom of the page, as was done with
Figure \ref{fig-example}.  If necessary, figures can extend up to the
width of the full two columns: 17.8 cm (7") if necessary.

The quality of your images and figures is critical. Your paper, if accepted, will
be printed in the high quality print proceedings, and will also be available 
for download on the ACM Digital Library where readers may read it online
and zoom in to see the details.

Screen dumps should be captured at the screen resolution and
use a lossless format such as TIFF.
Photos should have a resolution of at least 150dpi, and preferably
300dpi or 600dpi. They may be slightly compressed, e.g. in JPEG,
if this does not degrade quality (use the "Better" or "8/10" setting).
Diagrams, data plots and schemas should use a vector format
rather than a raster format where possible.

\begin{figure}[tb]
\vspace{1.9in}
\caption{A figure caption.  It is set in 9 point Helvetica type, with a
0.5 cm wider margin on both left and right sides.} 
\label{fig-example}
\end{figure}

Remember also that some readers may never see anything other than a 
oor photocopy of your paper, so make sure that the figure will still be 
readable (try to see how it looks after recopying it a couple of times).

\section{PRODUCING PDF FILES}
Submissions as well as final versions of your paper must be submitted in PDF format.
Most typesetting systems can produce PDF either directly or by using
a virtual printer. If you cannot produce PDF directly, you can produce
a PostScript file and then use a PostScript to PDF converter. Either way,
make sure that your PDF file is correct by viewing it with a standard
PDF reader such as Adobe's Acrobat.

\section{REFERENCES AND CITATIONS}
Your references should appear in the standard CACM format: a numbered list at
the end of the paper, ordered alphabetically by first author, and referenced by
number in brackets as shown here~\cite{badenov91,henry-etal92,zaranka81}.
(See the examples of citations at the end of this document, and the other
examples on p. 12 of the April 94 issue of the {\em Communications of the
ACM.}) 
References should be materials accessible to the public:
books, articles in standard journals, and papers in open conference
proceedings. 
Internal technical reports should be avoided unless easily accessible (i.e. you
can give the address to obtain it).  Personal communications should be
acknowledged, not referenced. Be sure to remove all dangling references and citations.

\section{LANGUAGE, STYLE AND CONTENT}
The written and spoken language of UIST is English. Spelling and punctuation may use
 any dialect of English (e.g., British, Canadian, US, etc.) provided this is done 
consistently. Hyphenation is optional. To ensure suitability for an international audience, 
please pay attention to the following:
\begin{itemize}
\item Try to avoid long or complex sentence structures. 
\item Briefly define or explain all technical terms that may be unfamiliar to readers.
\item Explain all acronyms the first time they are used in your text – e.g., 
“Digital Signal Processing (DSP)”.
\item Explain local references (e.g., not everyone knows all city names in a particular country).
\item Explain “insider” comments. Ensure that your whole audience understands any
reference whose meaning you do not describe (e.g., do not assume that everyone has 
used a Macintosh or a particular application).
\item Explain colloquial language and puns. Understanding phrases like “red herring” 
may require a local knowledge of English.  Humor and irony are difficult to translate.
\item Use unambiguous forms for culturally localized con-cepts, such as times, dates, 
currencies and numbers (e.g., “1-5- 97” or “5/1/97” may mean 5 January or 1 May, 
and “seven o’clock” may mean 7:00 am or 19:00).  For cur-rencies, indicate 
equivalences – e.g., “Participants were paid 10,000 lire, or roughly \$5.”
\item Be careful with the use of gender-specific pronouns ({\em he, she}) and other gendered 
words ({\em chairman, manpower, man-months}). Use inclusive language that is gender-
neutral (e.g., {\em she or he, they, s/he, chair, staff, staff-hours, person-years}). 
See~\cite{GenderNeutral} for further advice and ex-amples regarding gender and 
other personal attributes.
\item If possible, use the full (extended) alphabetic character set for names of persons, 
institutions, and places (e.g., Gr{\o}nb{\ae}k, Lafreni\'{e}re, S\^{a}nchez, Universit\"{a}t, 
Wei{\ss}enbach, Z\"{u}llighoven, {\AA}rhus, etc.).  These characters are already included in 
most versions of Times, Helvetica, and Arial fonts.
\end{itemize}

\section{HEADERS, FOOTERS AND PAGE NUMBERING}
Do not use headers, footers or footnotes. Page numbers, footers and headers will
be added when the Conference Proceedings are assembled. Papers submitted
to the paper chairs for review should have page numbers (to help the review process).

\section{OTHER CONSIDERATIONS}
\subsection{No Private Material}
Presentations should not contain any proprietary or confidential
material. Please clear all materials before submitting or presenting them.
Submission of pictures of identifiable people should be done only with the
understanding that responsibility for obtaining appropriate permissions rests
with the paper's authors.

\subsection{Equations}
Displayed equations should be centered, with optional equation numbers 
right-justified to the right margin of the column.

% use \newpage to break the columns on the last page so they have equal length
% if the break occurs in the middle of a paragraph, insert \linebreak before \newpage

\section{BLIND REVIEW}
For archival submissions, UIST requires a “blind review.” To prepare your 
submission for blind review, remove author and institutional identities in 
the title and header areas of the paper. You may also need to remove all 
of the Acknowledgments text. Authors should \textbf{not} use anonymous citations 
(by blanking their name or using Anonymous as an author) for references 
to their previous work. Instead, authors should 
refer  to previous work in 
the third person (i.e. as if they were not the authors). This will ensure that 
reviewers can take into 
\linebreak
\newpage
account previous research by the authors. 
Further suppression of identity in the body of the paper is left to the authors' discretion.
 For more details, 
see the submission guidelines and checklist for your submission category.

\section{CONCLUSION}
It is important that you write for the UIST audience.  Please read previous years’
{\em Proceedings} to understand the writing style and conventions that successful 
authors have used.  It is particularly important that you state clearly what you 
have done, not merely what you plan to do, and explain how your work is
different from previously published work, i.e., what is the unique contribution
that your work makes to the field?  Please consider what the reader will learn
from your submission, and how they will find your work useful.  If you write with
these questions in mind, your work is more likely to be successful, both in being
accepted into the Conference, and in influencing the work of our field.

\section{ACKNOWLEDGMENTS}
\begin{center}
\textbf{This section should be left blank for blind review}
\end{center}

The authors would like to acknowledge the contributions of many previous
editors in the writing and formatting of this document.  This document is based on
the {\em CHI '94} format-ting guidelines.

%%%	You can use bibtex if you like, but I've hardwired in these 
%%%	references to avoid sending you a separate .bib file.
\begin{thebibliography}{9}

\bibitem{ACMTerms} How to Classify Works Using ACM’s Computing
Classification System. {http://www.acm.org/class/how\_to\_use.html}.

\bibitem{badenov91}  Badenov, B. Effects of prolonged use of WIMP user
interfaces on Alces americana and Glaucomys volans.
In {\em Proceedings of UIST '87}
(February 30--April 1, Graceland, TN), ACM, NY, 1987, pp. 231--240.

\bibitem{henry-etal92} Henry, T.R., Yeatts, A.K., Hudson, S.E., Myers, B.A.,
and Feiner, S.K.  A nose gesture interface device: Extending virtual realities.
{\em Presence 1}, 2 (Spring 1992), 258--261.

\bibitem{GenderNeutral} Schwartz, M. Guidelines for Bias-Free Writing.
Indiana University Press, Bloomington, IN, USA, 1995.

\bibitem{zaranka81} Zaranka, W., Ed. {\em The Brand-X Anthology of Poetry:  A
Parody Anthology.}  Apple-wood Books, Cambridge, MA, 1981.
\end{thebibliography}

\end{document}

### 2009-03-10 ruby/scrapesnopes.rb

@@ -1,0 +1,38 @@
+
+require 'rubygems'
+require 'hpricot'
+require 'find'
+
+#Find.find("/home/rob/Reference/Crawls/www.snopes.com") do |path|
+	#next if FileTest.directory? path
+	#doc = Hpricot(open(path))
+	#bullets = doc.search("//img[@title='Red bullet']")
+	#bullets.each do |bullet|
+		#next if bullet.parent.name == "font"
+		#claim = bullet.next.to_s + 
+				#bullet.next.next.search("text()").to_s + 
+				#bullet.next.next.next.to_s
+		#href = bullet.next.next[:href]
+		#puts "#{claim}\t#{href}\n"		
+	#end
+#end
+
+
+outfile = File.new("snopesclaims.csv","w")
+
+Find.find("/home/rob/Reference/Crawls/www.snopes.com") do |path|
+	next if FileTest.directory? path
+	doc = Hpricot(open(path))
+	claim = doc.search("//font[@color='#2D8F26']/b[text()*='Claim']")
+	status = doc.search("//font[@color='#2D8F26']/b[text()*='Status']")
+	next if claim.length != 1 
+	next if status.length != 1
+	
+	claimtext = claim[0].parent.next.to_s.gsub(/^\s*\?\s*/,"").gsub(/[\n\r]/,"")
+	statustext = status[0].parent.next.next.search("text()").to_s.gsub(/\./,"")
+	
+	puts "#{claimtext}\t#{path}\t#{statustext}"
+	outfile.puts "#{path}\t#{statustext}\t#{claimtext}"
+end
+
+outfile.close

### 2009-03-10 ruby/striprefnotes.rb

@@ -1,0 +1,15 @@
+
+innote = false
+
+ARGF.each do |line|
+ 	if line =~ /note =/
+ 	 	innote = true
+	end
+	if !innote 
+		puts line
+	end
+	if line =~ /\},/
+		innote = false
+	end
+end
+

### 2009-03-11 papers/uist_thinklink/thinklink.tex
Tidied up database schema. Added data from snopes. Javascript Ui tweaks

@@
 \usepackage{color}
+
+\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
 
@@
 The web provides users with a huge number of pages that they can read, but extracting accurate and balanced information from these pages can be difficult.
-Not everything on the web is accurate~\cite{Mintz2002,Neumann2003,Resnik98,Zhou2004} and many web sites have a strong political bias~\cite{Herman2002,Genzkow2007}.
+Not everything on the web is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and many web sites have a strong political bias~\cite{Herman2002,Gentzkow2007}.
 If a user is to form a rounded opinion about a topic then they will need to either stick to sources that they trust or spend time looking for evidence on other web sites that supports or opposes what they read.
@@
 In this paper we present DisagreeWeb, a tool helps users discover when information they read is disputed or presents only one side of a contentious issue.
-We hope that DisagreeWeb will make it easier for users to be be aware of points of view that contradict with those that they usually encounter.
+When DisagreeWeb is used as a browser plugin it will highlight text that makes a disputed claim.
+If a user clicks on such a highlighted snippet then DisagreeWeb presents the user with an argument graph that shows the best evidence for and against the claim, as judged by other users of DisagreeWeb (Figure~\ref{claimview}).
+The argument graph contains links to snippets of text on other web sites that express conflicting or supporting points of view.
 
-When DisagreeWeb is used as a browser plugin it will highlight text on web pages that expresses or implies a disputed claim.
-If a user clicks on such a highlighted snippet then DisagreeWeb presents the user with a visualization of an argu
+DisagreeWeb relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.
 
-visualization that shows the user the best evidence for and against the claim, as judged by other users of DisagreeWeb.
+\want{Seeded with all claims from Snopes}.
+\want{Seeded with all contentious claims identified in the three months on FactCheck.org}
+\want{Tested with hundreds of users}.
+\want{Tested with real users and found took N seconds on average to identify and categorize snippets}
 
-that shows users when the information that they read conflicts with information available on other sources.
-
-D
-
- DisagreeWeb is implemented as a browser extension
-
-aims to let users see when the information they are reading conflicts with information from other sources.
-
-DisagreeWeb is implemented as a browser extension.
-
-The web suffers from filter failure~\cite{Shirky2008}.
-
-Part of the problem is that conventional web browsers present the web as a network of connected pages, when it is often the case that what the user is really interested in is the factual claims made by those pages, and the connections between those claims.
-While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author.
-The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web.
-The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages).
-While this makes it easier for users to add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.
+DisagreeWeb layers an argumentation graph over the existing web.
 
@@
 
-% \begin{figure}[tb]
-% %	\begin{center}
-%  	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
-%  	\caption{Click on a claim to investigate evidence for and against it}
-%  	\label{claimview}
-% 	\end{center}
-% \end{figure}
+\section{RELATED WORK}
 

### 2009-03-11 java/com/intel/thinklink/DataBase.java

@@ -1,16 +1,13 @@
 package com.intel.thinklink;
 
 import java.net.URLEncoder;
-import java.sql.Array;
 import java.sql.Connection;
 import java.sql.DriverManager;
 import java.sql.PreparedStatement;
 import java.sql.ResultSet;
-import java.sql.ResultSetMetaData;
 import java.sql.SQLException;
 import java.sql.Statement;
 import java.util.HashMap;
-import java.util.Set;
 import java.util.Vector;
 
 class JSONString{
@@ -20,123 +17,6 @@ class JSONString{
 	}
 }
 
-/**
- * Dyn is not efficient. Replace with static stuff when it matters.
- * @author rob
- *
- */
-class Dyn{
-	HashMap<String,Object> map = new HashMap<String,Object>(); 	
-
-	Dyn(HashMap v){
-		map = v;
-	}
-	Dyn(){
-	}
-	
-	void put(String key,Object o){
-		map.put(key, o);
-	}
-	void putJSON(String key, String s){
-		map.put(key, new JSONString(s));
-	}
-	void setJSON(String key){
-		putJSON(key,getString(key));
-	}
-	String get(String key){
-		return (String)map.get(key);
-	}
-	Dyn getDyn(String key){
-		return (Dyn)map.get(key);
-	}
-	Vector<Dyn> getVec(String key){
-		return (Vector<Dyn>)map.get(key);
-	}
-	String getString(String key){
-		return (String)map.get(key);
-	}
-	int getInt(String key){
-		return (Integer)map.get(key);
-	}
-	void remove(String key){
-		map.remove(key);
-	}
-	
-	static Dyn one(ResultSet res) throws SQLException{
-		res.next();
-		Dyn d = dyn(res);
-		res.close();
-		return d;
-	}
-	
-	static Dyn dyn(ResultSet res) throws SQLException{
-		Dyn dyn = new Dyn();
-		ResultSetMetaData meta = res.getMetaData();
-		int numcolumns = meta.getColumnCount();
-		for(int i = 1; i <= numcolumns; i++){
-			dyn.put(meta.getColumnLabel(i), res.getObject(i));
-		}
-		return dyn;
-	}
-	
-	static Vector<Dyn> list(ResultSet res) throws SQLException{
-		Vector<Dyn> vec = new Vector<Dyn>();
-		while(res.next()){
-			Dyn d = Dyn.dyn(res);
-			vec.add(d);
-		}
-		res.close();
-		return vec;
-	}
-	
-	static String toJSON(Object o){
[…]

### 2009-03-11 java/com/intel/thinklink/MainServlet.java

@@ -26,7 +26,8 @@ public class MainServlet extends HttpServlet {
 			DataBase base = ConnectionPool.get();
 			try{
 				Dyn snippet = base.getSnippet(id);
-				String text = snippet.get("text") + " " + snippet.get("text") + " "+ snippet.get("page_text");
+				String sniptext = snippet.get("text");
+				String text = sniptext + " " + sniptext + " " + sniptext + " " + sniptext+ " " + sniptext + " " + snippet.get("page_text");
 				Vector<WikiMatch> matches = WikiMatcher.getMatches(text); 
 				matches = WikiMatcher.sumMatches(matches);
 				

### 2009-03-11 java/com/intel/thinklink/WikiApplyRedirects.java

@@ -14,7 +14,7 @@ public class WikiApplyRedirects {
 
 	public static HashMap<String,String> loadRedirects() throws Exception{
 		HashMap<String,String> h = new HashMap<String,String>();
-		BufferedReader reader = WikiKeywordiness.openInFile(redirectfile);
+		BufferedReader reader = Util.openInFile(redirectfile);
 		String line;
 		while((line = reader.readLine()) != null){
 			int colonidx = line.indexOf("->");
@@ -31,7 +31,7 @@ public class WikiApplyRedirects {
 	
 	public static HashMap<String,Integer> loadAndMergeLinks(HashMap<String,String> redirects) throws Exception{
 		HashMap<String,Integer> linkmap = new HashMap<String,Integer>();
-		BufferedReader reader = WikiKeywordiness.openInFile(linkfile);
+		BufferedReader reader = Util.openInFile(linkfile);
 		String line;
 		while((line = reader.readLine()) != null){
 			int colonidx = line.indexOf(":");
@@ -82,7 +82,7 @@ public class WikiApplyRedirects {
 			HashMap<String,Integer> links = loadAndMergeLinks(redirects);
 			out("saving");
 			Set<String> keys = links.keySet();
-			Writer writer = WikiKeywordiness.openOutFile(outfile);
+			Writer writer = Util.openOutFile(outfile);
 			for(String key : keys){
 				writer.append(key+":"+links.get(key)+"\n");
 			}

### 2009-03-11 webapps/node/javascript/webui.js

@@ -274,17 +274,21 @@ function makeDragItem(obj,label){
 
 	var tdvote = $("<td/>").appendTo(tr);
 
+	var votebox = $("<nobr/>").attr("class","votebox").appendTo(tditem);
+
 	var up = $("<img/>").attr("src",urlbase+"/images/vote_up_e.png")
 		.attr("title","Promote")
+		.attr("class","votebutton")
 		.mouseover(function(){up.attr("src",urlbase+"/images/vote_up_on.png")})
 		.mouseout(function(){up.attr("src",urlbase+"/images/vote_up_e.png")})
-		.appendTo(tdvote);
+		.appendTo(votebox);
 		
 	var down = $("<img/>").attr("src",urlbase+"/images/vote_down_e.png")
 		.attr("title","Remove")
+		.attr("class","votebutton")
 		.mouseover(function(){down.attr("src",urlbase+"/images/vote_down_on.png")})
 		.mouseout(function(){down.attr("src",urlbase+"/images/vote_down_e.png")})
-		.appendTo(tdvote);
+		.appendTo(votebox);
 
 
 	if(thinklink_user_id == obj.user){
@@ -403,7 +407,7 @@ function makeSnippet(snippet,bossmode){
 		"<table class='dragtable'>"
 			+"<tr><td><img/></td><td><div class='snipbody'/></td></tr>"
 		+"</table>").appendTo(holder);	
-	var img = $("<img/>").attr("src",urlbase+"/images/application_go.png");
+//	var img = $("<img/>").attr("src",urlbase+"/images/application_go.png");
 	table.find("img").attr("src",urlbase+"/images/comment.png");
 	var snipbody = table.find(".snipbody");
 	var sniptext = $("<div class='sniptext'/>")
@@ -413,7 +417,7 @@ function makeSnippet(snippet,bossmode){
 		
 	$("<a class='snippet_url'/>").text(trim_string(snippet.info.title,40) + " - "+trim_url(url))
 		.attr("href",realurl).attr("target","_blank")
-		.append(img)
+	//	.append(img)
 		.appendTo(table.find(".snipbody"));
 
 	
@@ -538,12 +542,13 @@ function makeSubItems(div,obj){
 	}
 	
 	for(var i = 0; i < verbs.length; i++){
-		var verb = verbs[i];		
+		var verb = verbs[i];	
+		var reltitle = null;	
[…]

### 2009-03-16 papers/uist_thinklink/thinklink.tex
Updated paper plan and tweaks to uist paper and notes

@@
 \usepackage{color}
+% \usepackage[pdftex]{hyperref}
+% \hypersetup{%
+% pdftitle={Browsing the Web of Factual Claims},
+% pdfauthor={Beth Trushkowsky and Rob Ennals},
+% pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
+% bookmarksnumbered,
+% pdfstartview={FitH},
+% colorlinks,
+% citecolor=black,
+% filecolor=black,
+% linkcolor=black,
+% urlcolor=black,
+% breaklinks=true,
+% }
 
@@
 \abstract
-We present DisagreeWeb, a browser extension that aims to let users see when the information they are reading presents only one side of a disputed issue.
-As the user browses the web, DisagreeWeb highlights snippets of text that make claims that conflict with information on other web sites.
-If a user clicks on such a disputed claim then DisagreeWeb will show tem an argument graph showing the best evidence for and against the claim being true, as determined by other users of DisagreeWeb.
+We present Think Link, a browser extension that aims to let users see when the information they are reading presents only one side of a disputed issue.
+As the user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites.
+If a user clicks on such a disputed claim then Think Link will show tem an argument graph showing the best evidence for and against the claim being true, as determined by other users of Think Link.
 
@@
 
-In this paper we present DisagreeWeb, a tool helps users discover when information they read is disputed or presents only one side of a contentious issue.
-When DisagreeWeb is used as a browser plugin it will highlight text that makes a disputed claim.
-If a user clicks on such a highlighted snippet then DisagreeWeb presents the user with an argument graph that shows the best evidence for and against the claim, as judged by other users of DisagreeWeb (Figure~\ref{claimview}).
+In this paper we present Think Link, a tool helps users discover when information they read is disputed or presents only one side of a contentious issue.
+When Think Link is used as a browser plugin it will highlight text that makes a disputed claim.
+If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by other users of Think Link (Figure~\ref{claimview}).
 The argument graph contains links to snippets of text on other web sites that express conflicting or supporting points of view.
 
-DisagreeWeb relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.
+Think Link relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.
 
@@
 
-DisagreeWeb layers an argumentation graph over the existing web.
+Think Link layers an argumentation graph over the existing web.
 

### 2009-03-16 papers/uist_thinklink/thinklink.tex
Included text from the old paper - must of which will be rewritten

@@
 
-\section{RELATED WORK}
+\section{Introduction}
 
-\section{HIGHLIGHTING CONTROVERSIAL CLAIMS}
+The web provides users with a huge number of pages that they can read, but extracting useful and reliable information from these pages can be difficult.
+Not everything on the web is accurate~\cite{bbcwebwarning}.
+If a user is to avoid being mislead by false claims then they will need to either stick to sources they can trust, or spend time looking for evidence on other web sites that supports or opposes what they have read.
+Similarly, a user will not find every claim on the web interesting.
+If a user is to locate claims that help them answer the questions they are interested in then they may have to spend considerable time reading claims that do not interest them in order to pick out those that do.
+Throughout this paper we will use the motivating example of a user who is worried about global warming and wants to find out what is going on and what they can do to help.
+Many web pages contain claims about global warming that are false, and many web pages repeat the same claims, making it difficult for a user to find interesting new facts that they were not previously aware of.
 
-\section{CONNECTING UP THE ARGUMENT}
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
+	\caption{Click on a claim to investigate evidence for and against it}
+	\label{claimview}
+	\end{center}
+\end{figure}
 
-\section{THE THINK LINK SYSTEM}
+The difficulty of finding correct information on the web has been discussed a lot recently.
+Tim Berners Lee has expressed concern about the difficulty that people face discerning whether information on the web is true~\cite{bbcwebwarning}.
+Many people have also voiced concerns about how easily people can subvert Wikipedia to give people false information~\cite{wikifalse}.
+Several commentators have observed that there is a Media Echo Chamber effect~\cite{echochamber,echochamber2} in which news sources report claims that they have heard from other news sources, despite the fact that these claims may be misleading or untrue.
+If a user only reads news sources from a particular group then they may only be exposed to the views of that group and may not be aware that opposing views exist unless they actively seek them.
 
-\section{USER STUDIES}
+Part of the problem is that conventional web browsers present the web as a network of connected pages, when it is often the case that what the user is really interested in is the factual claims made by those pages, and the connections between those claims.
+While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author.
+The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web.
+The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages).
+While this makes it easier for users to add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.
 
-\section{CONCLUSIONS}
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
+	\caption{Think link connects claims to each other and to web snippets}
+	\label{summarygraph}
+	\end{center}
+\end{figure}
 
-\bibliographystyle{abbrv}
+In this paper we present Think Link, a tool that overlays a new network of links over the existing web, connecting snippets of text to snippets elsewhere on the web that make related claims.
+Think Link maintains a central shared ``claim graph'' (Figure~\ref{summarygraph}) containing claims made on the web, their supporting and opposing relationships to each other, and the snippets that make these claims.
+When a user views a web page, Think Link highlights snippets that have been identified as making factual claims, with the highlight color indicating whether other sources have been found that disagree with the claim.
+If a user clicks on a snippet then they will see a ``claim browser'' (Figure~\ref{claimview}) that allows them to see other claims made on the web that support or oppose the claim the snippet makes, and snippets elsewhere on the web that make these other claims.
+
+The Think Link claim graph is editable by all users, in a manner similar to a wiki.
+Any user can add new claims, connect existing claims together, and identify snippets on web pages that make specific claims.
+Collaborative filtering is used to filter out junk or abusive information, while minimizing the danger of political edit wars.
+
+Not everyone will necessarily want a tool like Think Link.
+Some people may be looking for confirmation of their own points of view rather than information that challenges their beliefs.
+We hope however that Think Link may be able to make some contribution to helping people find out about other points of view, and help people more easily find the most interest claims about topics they are interested in.
+
+The contributions of this paper are the presentation of a new approach for connecting information on the web, the design of a user interface that makes it easy for users to find claims that support and oppose claims that they read on the web, and a qualitative user study of how participants use such an interface.
+
+\section{Related Work}
+
+Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}.
+Like Think Link, wikis allow users to find information organized by topic rather than author and allow users to collaborate together to bring together all the best information about a topic.
+Wikipedia's greatest strength is arguably also its greatest weakness.
+Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}.
+Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2,wikicorrect3}, but it is difficult to remove the problem entirely.
+While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious.
+Think Link tries to avoid this problem by linking claims back to the original sources that made these claims.
+Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim.
+
+When a topic is heavily politicized, Wikipedia can be subject to edit wars in which people who hold one opinion delete opinions held by the other side~\cite{wikicorrect3}, making it difficult for the community to collaborate together to produce a document that is both comprehensive and unbiased.
+Think Link attempts to avoid this problem by taking an ``append-only, collaborative filtering'' approach.
+A user cannot remove claims that they disagree with\footnote{With special exceptions for dealing with spam and abuse}.
+Instead all they can do is vote against them, and connect them to claims that provide opposing evidence.
+
+Another key difference between Think Link and a wiki is that Think Link pulls the whole web into its graph of connected claims.
+A user can use Think Link to investigate claims they read on arbitrary web sites, without having to restrict their browsing to a single wiki site.
+
+SpinSpotter~\cite{spinspotter} shares Think Link's goal of allowing users to identify misleading and inaccurate information on web pages that they read.
+If a user sees a section of text that they think is misleading then they can mark it up, causing it to be highlighted when other users view the same page.
+While Think Link and SpinSpotter both share the goal of letting users mark up snippets that may be inaccurate, they differ in what they let users find out about such snippets.
+SpinSpotter allows users to give a textual description of why the snippet is spin and a suggested edit that would make it more accurate.
+Think Link instead connects the snippet to its global claim graph, allowing users to quickly access evidence for and against the truth of the claim.
+There is also a difference in the nature of what SpinSpotter and Think Link expect users to mark up.
+Think Link is interested in evaluating the truth of factual claims, while SpinSpotter also interested in identifying biased phrases (e.g.
+``tree hugger'').
+
+Other web annotation systems such as ShiftSpace.org, Stickis.com, SharedCopy.com, and Diigo.com allow people to add their own annotations to existing web pages and view annotations written by other people.
+Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relevant documents.
+More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
+We are not aware of any such system that links web pages to a graph of factual claims.
+
+Web clipping tools such as Google Notebook, Scrapbook~\cite{scrapbook}, and Zotero.org allow one to gather and organize interesting from web pages.
+Many web clipping tools are also web annotation systems.
+These tools are designed for gathering and sharing interesting information, rather than for identifying the claims being made, or allowing users to navigate to related claims being made on other sites.
+
+In Vannevar Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them.
+As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''.
+Several more recent systems have allowed user to add links to existing pages.
+ENQUIRE~\cite{weavingtheweb} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it.
+Everything2.com links each page to the most popular pages that users viewed at the same time.
+Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making and allowing users to browse this graph, rather than just allowing users to specify links between pages.
+
+One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed.
+This is a goal that is shared with several other projects.
+Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allow users to navigate from such a passage to all other documents where that passage is quoted.
+Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus.
+ScentHighlights~\cite{Chi2005} identifies sections of text that you might find interesting and highlights them for you.
+ScentTrails~\cite{Center2003} identifies links to documents that you might find interesting and makes them bigger.
+Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.
+
+Much work has been done on the idea of using a graph to represent an argument~\cite{argumentation,argmas}.
+Popular argument models include the Toulmin Model~\cite{toulmin}, the Carneades Model~\cite{carneades}, and the IBIS model~\cite{ibis}.
+Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model, with the result that they provide a more accurate model of the logical argument, at the cost of requiring more skill to assemble.
+One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numerical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.
+
+%\subsection{Automated Reasoning}
+%
+%Case-Based reasoning
+%Sensemaking
+
+%\subsection{Argumentation Graphs}
+%Argumentation graphs express positions and arguments in a formal graph model as nodes and edges, respectively, and are typically used to make a decision or draw a conclusion about some issue.
+One example implementation is the {\it Zeno} argumentation framework~\cite{zeno}, designed for collaborative use in mediation systems to debate the quality of alternative solutions for a problem.
+In their object model of argumentation elements, based on Rittel's IBIS model~\cite{ibis}, example nodes include pro/con arguments, positions, preferences, comments, and decisions.
+Importantly, arguments are connected via {\it consequent} and {\it antecedent} edges, which are used to inform {\it choices}.
+The decision-making power of the argumentation graph follows from the traversal of argument relationships to enhance the depth and breadth of understanding about an issue.
+Our application similarly links claims as {\it supporting} and {\it opposing} other claims to allow users to develop a cohesive understanding of arguments.
+%
+%Traditional argumentation graphs are designed to solve a specific, isolated issue.
+Our application supports an ever-expanding set of topics, and arguments can form links between multiple topics.
+Users can consult the web of ideas directly to form an opinion about a particular issue, but they can also browse for new issues to explore.
+Opinions or decisions in our model don't have to be static: as the topic is expanded with more supporting and opposing evidence, users may alter previous viewpoints.
+Another advantage of our model is that the ability to explore claims' source-document evidence is built right into the navigation.
+Looking at an argument shows both its related argument as well as its supporting {\it snippets}, allowing the user to explore the evidence for himself.
+
+\section{The Think Link System}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
+	\caption{Hovering over a highlighted snippet shows a summary}
+	\label{highlight}
+	\end{center}
+\end{figure}
+
+Think Link is a tool that overlays a web of factual claims on the existing web (Figure~\ref{summarygraph}).
+As a user browses the web, Think Link highlights snippets of text that have been identified as making factual claims.
+If a user clicks on a highlighted snippet, Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}).
+Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.
+
+Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}).
+This graph is managed like a wiki, allowing any user to add new claims or snippets.
+As a user browses the web, they can identify snippets that make claims that are interesting or controversial and link them into the global claim graph.
+
+Think Link is implemented as a Firefox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.
+
+\subsection{Exploring factual claims on a page}
+
+When a user browses a web page, we want to make them aware of claims being made on the page that they might find interesting, or that other sources disagree with.
+Think Link draws attention to the factual claims that other users have identified on a web page by highlighting them (Figure~\ref{highlight}).
+Snippets are highlighted in red if they are contentious (other sources disagree with the claim).
+The highlight colors are chosen to be pale enough to not impede reading, dark enough to be noticeable\footnote{Unless the background is close to a highlight color.
+Think Link does not yet adapt to different page background colors}, and different enough to be distinguishable by colorblind people.
+A user can see what claim a snippet is making by hovering their mouse over the snippet (Figure~\ref{highlight}).
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/sidebar_diagram.png}
+	\caption{The margin summarizes the key claims on the page}
+	\label{margin}
+	\end{center}
+\end{figure}
+
+If a user thinks a claim is interesting and wants to know what other sources say about it then they can open up a ``claim browser'' window (Figures~\ref{claimview} and \ref{claimbrowse_diagram}) by clicking on the highlighted snippet.
+The claim browser allows the user to easily view claims that support or oppose the selected claim, and find snippets of text on the web that make these claims (Figure~\ref{claimview}).
+For example, if a user browsed a web page that claimed ``Global Warming does not exist'', then the snippet that made this claim would be highlighted in red, indicating that there are web pages elsewhere that make opposing claims.
+If the user were to click on the highlighted snippet then an ``investigate claim'' window would appear (Figure~\ref{claimview}).
+This window would show the user that the claim ``Global Warming does not exist'' is opposed by the claim ``There is strong evidence for global warming''.
+If the user navigated to this new claim then they could quickly see the best claims that support the existence of global warming, and would be able to see summaries of the best sources that supported these claims.
+
+%\begin{floatingfigure}{2cm}
+%\includegraphics[width=2cm]{../screenshots/marginpull_out.png}
+%\end{floatingfigure}
+
+If the current page contains snippets then a tab appears in the top left corner of the window.
+The tab contains a light bulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim.
+This allows a user to quickly tell if a page contains something of interest without having to scroll through the whole page.
+Clicking on the tab opens the margin.
+The margin provides a summary of all the interesting claims that users have identified on the current page and is designed to mimic the traditional margin notes that readers often write on physical documents~\cite{marginalia}.
+To emphasize the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.
+
+\subsection{The Mental Model}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=7cm]{../screenshots/bookmark_icons2.png}
+	\caption{Icons used for Claims, Snippets, and Topics}
+	\label{bookmark_icons}
+	\end{center}
+\end{figure}
+
+Think Link users interact with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}):
+
+\begin{itemize}
+\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false.
+For example ``Global warming is man made''.
+A claim may support or oppose other claims.
+Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
+\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim.
+Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
+\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about.
+For example ``Global Warming'', or ``Computer Science''.
+A claim can be about one or more topics, and a topic can have one or more more general topics.
+Topics are used to organize and disambiguate claims.
+For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''.
+Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
+A topic can itself by disambiguated by having a super-topic.
+\end{itemize}
+
+\subsection{Browsing factual claims}
+\label{browseclaim}\label{claimbrowser}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
+	\caption{The claim browser visualizes the claim graph}
+	\label{claimbrowse_diagram}
+	\end{center}
+\end{figure}
+
+Claims and topics form a directed graph structure. A claim can have any number of claims that support or oppose it, and any number of claims that it supports or opposes.
+A topic can have any number of more specific topics (e.g.
+``US Election 2008'' is more specific than ``US Elections'') and any number of more general topics.
+A topic can also have any number of claims about that topic.
+
+When designing an interface to this structure, we were faced with two opposing constraints.
+We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree.
+Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place.
+Tree-based outliners such as OmniOutliner~\cite{omnioutliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
+
+After several design iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner.
+Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it.
+Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.
+
+The placement of objects above and below is intended to emphasize the conventional hierarchical structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
+A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/claimbrowse_zoom.png}
+	\caption{Close up of a list of supporting claims}
+	\label{claimbrowse_zoom}
+	\end{center}
+\end{figure}
+
+Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states.
+When a new item is selected, it grows in size and moves to the center.
+Other items that were already on the screen move from their current locations to their new locations.
+Other objects appear and disappear by smoothly sliding into or out of view.
+
+Users see a claim browser in three different places.
+The {\it organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}).
+The {\it popup browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}).
+The {\it claim selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).
+
+\subsection{Creating new Snippets}
+\label{newsnippet}
+
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=16cm]{../screenshots/newsnip_all.png}
+	\caption{Process for creating a new snippet}
+	\label{createprocess}
+	\end{center}
+\end{figure*}
+
+%\begin{figure}[tb]
+%	\includegraphics[width=8.5cm]{../screenshots/snipsave_full.png}
+%	\caption{The claim selection window allows one to identify the claim a snippet is making}
+%	\label{snipsavefull}
+%\end{figure}
+
+\begin{figure}[tb]
+	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram_full.png}
+	\caption{Selecting the claim made by a new snippet}
+	\label{snipsavecrop}
+\end{figure}
+
+There are several reasons a user may wish to add a snippet to Think Link.
+They may find the snippet useful and may want to refer to it again in the future; they may disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments; they may think the claim argues a point well and want to be able to use it to make an argument, or they may agree with the claim and want to provide easy access to evidence elsewhere that backs it up.
+
+To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser tool bar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}).
+This is a similar approach to that taken clipping tools such as Google Notebook.
+
+Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making.
+To do this, Think Link presents the user with a ``claim selector'' window.
+This window contains a small version of the claim browser that the user can use to select the claim that the snippet is making.
+
+Since much of Think Link's utility comes from linking snippets together, it is important to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics.
+We designed the claim selection window to make it easier to pick out an existing claim than to create a new one.
+Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim.
+To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to.
+For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim.
+This is an intentionally different model to that used by ad-hoc tag-based systems such as Del.icio.us and Flickr.com.
+This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected.
+In practice, it is inevitable that duplicates claims and topics will sometimes be created.
+When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.
+
+\subsection{Organizing the Claim Graph}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/claimbrowse.png}
+	\caption{The Claim Organizer contains two claim browsers}
+	\label{fig:claimbrowser}
+	\end{center}
+\end{figure}
+
+Like Wikipedia~\cite{wikipedia}, Think Link allows any user to improve the information in the claim graph.
+The claim graph is shared between all users and editable by anyone.
+Any user can add new snippets, create new claims, create new topics, or establish new relationships between these objects.
+One can think of Think Link as being rather like a wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.
+
+Think Link uses collaborative filtering~\cite{collective} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim.
+If a user finds a snippet or claim interesting then they can vote in favor of it by clicking on its icon, causing it to light up (Figure~\ref{bookmark_icons}).
+When Think Link lists claims or snippets, it will show first those that the user marked as interesting, and order the rest according to the number of other users who marked them as interesting.
+
+It is important to avoid political fights, where two competing sides delete claims, snippets, or connections that they disagree with.
+Similarly, it is important to avoid vandalism, where people abuse people with competing beliefs by adding abuse claims or snippets.
+While we do not have a perfect solution to this problem, our current approach is to treat deletion as a special case of collaborative filtering.
+If a user believes a claim, topic, snippet, or connection is junk then they can request that it be deleted by clicking on the ``delete'' button.
+This will hide the object for the user who request deletion and reduce the score of the object for other users.
+If enough people vote to delete the object then its score will eventually be low enough that it is not displayed to users unless they request to see junk objects.
+
+In a wiki, users edit and delete information produced by others, and history is used to revert abusive changes.
+Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects.
+The hope is that over time ratings should converge to a steady state and edit wars should be avoided.
+It would not be practical for a wiki to take this approach as wiki data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.
+
+Think Link uses the familiar drag and drop interface for establishing new connections.
+To establish a connection between two claims, one need simply drag one claim onto the other.
+The claim organizer window has two claim browsers, allowing a user to points from one browser onto points on the other (Figure~\ref{fig:claimbrowser}).
+
+\subsection{Why People Annotate}
+
+Tools like Think Link rely on user contributions in order to be useful.
+If no users are identifying factual claims on pages then other people who browse such pages will not see any claims identified.
+Similarly, if no other users are connecting claims together, then users will not see any supporting or opposing claims when they click on a highlighted snippet.
+
+Moreover, in order to become popular, a tool like Think Link needs to be useful even when very few people are using it.
+If a tool is only useful when it has a large community using it then it is unlikely that early adopters will stick with it enough for it to ever acquire a large community.
+
+Our user study participants identified several reasons why they would want to mark up factual claims in documents they found.
+The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found.
+One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
+The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
+
+\subsection{Implementation}
+
+Think Link is implemented as three largely independent components:
+
+\begin{itemize}
+\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains the claim graph and provides an API that allows this data to be queried and modified
+\item {\bf A web UI}, written using Javascript that implements the claim browser
+\item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page.
+This script displays the web UI in an iframe to pick or investigate a claim.
+\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides tool bar and context-menu shortcuts.
+\end{itemize}
+
+These components are largely independent.
+One could use the page enhancement script on a web page without using the Firefox extension, by either manually including it on the page (e.g.
+to enhance your own blog) or by adding it using a proxy.
+Since the server API is public, one could write alternative tools that mark up web pages in different ways, or use the claim graph for different purposes.
+
+The source code to Think Link is publicly available under the Apache license.
+
+\section{User Studies}
+
+We performed two qualitative ``think aloud'' user studies to guide the development of Think Link.
+
+The aim of the first study was to see how users normally browse the web and how they might go about using Think Link to identify snippets in the pages they browse.
+The aim of the second study was to evaluate changes made to the interface as a result of the first study and see how people react to browsing pages that have interesting claims highlighted.
+
+\subsection{Procedure for the First Study}
+
+For the first study we recruited 12 paid participants.
+Five were female, seven were male.
+Their ages ranged from high school age to retired.
+Our intention was to recruit users who were not experts, but who regularly used the Internet to find information.
+We recruited participants using a posting to the Craigslist.org classified advert site.
+In our advert, we expressed an interest in people who use the Internet to gather knowledge, rather than just for tasks such as email or shopping.
+We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.
+
+Study sessions took approximately 45 minutes.
+Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link plugin.
+We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they found interesting and connect those claims to the existing claim graph.
+For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.
+
+In this initial study, users were exposed to the prototype interface shown in Figures~\ref{oldsnippetbox} and \ref{oldbrowser}, rather than the final interface described earlier in this paper.
+We discuss some of the key differences in the findings section.
+
+\subsection{Procedure for the Second Study}
+
+For the second study, we recruited 6 paid participants.
+Four were female and two were male.
+Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the college semester meant that five of the participants were students.
+Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.
+
+In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it.
+We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
+The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw.
+The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with.
+Participants were shown an interface that is largely identical to that described earlier in this paper.
+
+\subsection{Findings}
+
+In this section we present the findings from our two user studies. Findings from the two studies are presented together and clustered by topic.
+
+\subsubsection{High-Level Impressions}
+
+Response was generally positive, with many participants being very keen to use the tool soon.
+One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed.
+Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
+
+Participants liked the ability to see when other pages disagreed with the claim they were looking at.
+One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
+
+\subsubsection{Usability}
+
+Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version.
+None of these problems re-occurred during the second study.
+We discuss some of these changes in the sections below.
+
+Most participants in the first study, and all participants in the second study were able to use the tool competently.
+Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
+Participants said they found the tool ``very intuitive''.
+
+\subsubsection{Creating a Snippet}
+
+Users would often encounter a snippet that could be interpreted as making several interesting claims, and were unsure about what to do in such circumstances.
+Some users would deal with this by writing a compound claim like ``Global Warming will cause X and Y'' while other users would create several snippets for the same text, making different claims.
+Users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.
+
+One special case of this problem was that several users wanted to mark up a table as a snippet.
+A table can usually be considered to be making several interesting claims and users were often confused about what they should say the table claimed.
+Our current guidance is that one should mark up a table as making the most interesting claims that that table makes --- those that support or oppose claims made elsewhere.
+In other cases, a user wanted to mark up an image as a snippet.
+While Think Link does not currently support this, it might make sense to allow this if an interesting claim can be inferred from the image.
+
+Some users expressed an interest in marking up a snippet as a primary source rather than a claim.
+For example they might find the text of an important speech or an Olympic results table.
+Several expressed a desire to have a new class of object that was neither a topic nor a claim, but instead just ``interesting information relevant to this topic''.
+
+Many users would consistently mark the first paragraph of an article as a snippet.
+This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.
+
+\subsubsection{Choosing a Claim for a Snippet}
+
+\begin{figure}[t]
+	\includegraphics[width=8.5cm]{../screenshots/oldsnipcreate_diagram.png}
+	\caption{Initial Prototype Snippet Creation Dialog}
+	\label{oldsnippetbox}
+\end{figure}
+
+In the initial interface we used a simplified snippet creation window (Figure~\ref{oldsnippetbox}) that was intended to make the process of snippet creation very lightweight.
+This window contained two text boxes.
+The first of these boxes was for the topic (e.g.
+``Global Warming'') and the second of the boxes was for the claim (e.g.
+``Global Warming is Man Made'').
+Both of these boxes used an auto-complete drop-down list to suggest appropriate existing topics or snippets as the user typed,
+biasing towards topics that were recent or hot.
+The auto-complete list would show either when the user started typing, or when the user clicked the drop down button.
+Selecting a claim would auto-populate the topic.
+Selecting a topic would constrain the claims that were suggested to be within that topic.
+
+We found that participants using this initial interface felt disorientated by the fact that the interface for creating snippets was different to the interface used for visualizing them.
+Participants would often confuse claims and topics, either entering a claim in the topic box, or a topic in the claim box.
+Participants would also frequently create new points and topics when appropriate points and topics already existed in the claim graph, even when the suggestion list was drawing their attention to a topic or claim that would have been appropriate.
+
+For the second study, we used the snippet creation interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph.
+We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics.
+We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.
+
+Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one.
+For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information?
+
+Several users also expressed an interest in being able to use the text of the snippet they selected as the text of its claim, particularly for short snippets.
+We intentionally made this a little difficult to do in an attempt to encourage users to find existing claims that are appropriate, however this may have been a mistake as it also increases the amount of effort required to create a snippet.
+
+\subsubsection{Connecting Claims}
+
+Many participants expressed a desire to organize claims into connected arguments during their session.
+
+Some users incorrectly marked one claim as supporting another when in fact they should have both been marked as supporting a third claim that needed to be created.
+For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing environmental problems''.
+Users realized that the claims were related, but did not immediately recognize that they needed to create new claims in order to structure the relationship correctly.
+It is possible that creating correct logical claim structures may just be too difficult for some people, or it may be that users would get used to the idea with more practice.
+We hope that if Think Link was deployed more widely many of the intermediate claims that were needed would already have been created and this problem would thus be reduced.
+
+Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship.
+For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''.
+Similarly, many users expressed a desire to mark claims as being ``related'' without supporting or opposing each other.
+For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''.
+Our current advice in such circumstances is to use topics to group claims that are related.
+For example these claims could all be in a topic called ``America and the Kyoto Protocol''.
+Participants seemed comfortable with the idea of relating claims in this way when we pointed it out to them, but most participants needed to be told that this was a strategy they could use.
+
+Several users got confused by claims that referred to similar events at different points in time.
+For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written.
+This is a particular problem when talking about breaking news events, where what claims are true can change fast.
+If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the time at which a claim was asserted to be true.
+
+Several users expressed an interest in being able to mark a claim as controversial without having to create an opposing claim.
+One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
+In the future we are planning to implement a social voting system to allow users to say what claims they believe are false and see what claims their friends agreed or disagreed with.
+
+\begin{figure}[tb]
+	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
+	\caption{Initial Prototype Claim Browser}
+	\label{oldbrowser}
+\end{figure}
+
+\section{Limitations and Future Work}
+
+There are a number of issues that a widely released tool would need to address.
+Firstly, our current implementation has privacy issues.
+Every time one navigates to a web page, the plugin contacts our server and gives it the current URL so that the server can check if there are snippets on that page.
+These requests are anonymous, cacheable, and not logged, but it is still likely that some people would object to this information being given to an external server.
+
+At present, all claims have to be marked up by users who must not only identify the correct section of text to highlight, but also use a browsing interface to find the interesting claim that is being made.
+It would be interesting to see if natural language processing techniques could be used to either simplify the process of marking snippets, or even to detect snippets that make known claims without human intervention.
+
+Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics.
+Since our graph and user base are currently small, we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.
+
+We think it could be useful to use Think Link as a tool to suggest reading material.
+Just as tools like Digg suggest pages that you might like, Think Link could potentially suggest pages that contain claims that the user had not read and would be likely to find interesting.
+
+\section{Conclusions}
+
+We have introduced the concept of browsing the web of factual claims using Think Link.
+Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors.
+It allows users to identify contentious claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.
+
+On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using an ``append only, collaborative filtering'' model to allow users to collaborate together to structure claims into an argument graph.
+
+We hope that Think Link will make it easier for people to be informed about the world and be exposed to factual claims that they might not otherwise be exposed to.
+
+\section{Acknowledgments}
+
+We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link.
+Think Link uses icons from the free FamFamFam Silk~\cite{silkicons} collection.
+
 \bibliography{refs}

### 2009-03-18 papers/uist_thinklink/thinklink.tex
Added a shed load of related work references

@@
 \newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
+\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
 
@@
 The web provides users with a huge number of pages that they can read, but extracting accurate and balanced information from these pages can be difficult.
-Not everything on the web is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and many web sites have a strong political bias~\cite{Herman2002,Gentzkow2007}.
+Not everything on the web is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and many web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
 If a user is to form a rounded opinion about a topic then they will need to either stick to sources that they trust or spend time looking for evidence on other web sites that supports or opposes what they read.
@@
 
-In this paper we present Think Link, a tool helps users discover when information they read is disputed or presents only one side of a contentious issue.
+In this paper we present Think Link, a tool helps users discover when information they read conflicts with information on other web sites, and shows users the best sources that provide alternative points of view.
 When Think Link is used as a browser plugin it will highlight text that makes a disputed claim.
@@
 Think Link relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.
+If a user is viewing a web page, they can identify disputed claims and useful evidence.
+Think Link will guide a user in finding existing claims that a snippet may be making and in connecting existing claims.
 
-\want{Seeded with all claims from Snopes}.
-\want{Seeded with all contentious claims identified in the three months on FactCheck.org}
-\want{Tested with hundreds of users}.
-\want{Tested with real users and found took N seconds on average to identify and categorize snippets}
+Think Link is designed to cator to two distinct groups of people.
+Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them.
+Sceptical readers install Think Link as a browser plugin so that they can see when things they read and disputed and find other links that present other points of view.
+A reader may of course be an activist for one issue and a sceptical reader for others.
 
-Think Link layers an argumentation graph over the existing web.
+The design of Think Link was guided by two user studies, in which we observed the behaviour of users who fitted the roles of Activist or Sceptical Reader.
 
@@
 
-\section{Introduction}
-
-The web provides users with a huge number of pages that they can read, but extracting useful and reliable information from these pages can be difficult.
-Not everything on the web is accurate~\cite{bbcwebwarning}.
-If a user is to avoid being mislead by false claims then they will need to either stick to sources they can trust, or spend time looking for evidence on other web sites that supports or opposes what they have read.
-Similarly, a user will not find every claim on the web interesting.
-If a user is to locate claims that help them answer the questions they are interested in then they may have to spend considerable time reading claims that do not interest them in order to pick out those that do.
-Throughout this paper we will use the motivating example of a user who is worried about global warming and wants to find out what is going on and what they can do to help.
-Many web pages contain claims about global warming that are false, and many web pages repeat the same claims, making it difficult for a user to find interesting new facts that they were not previously aware of.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
-	\caption{Click on a claim to investigate evidence for and against it}
-	\label{claimview}
-	\end{center}
-\end{figure}
-
-The difficulty of finding correct information on the web has been discussed a lot recently.
-Tim Berners Lee has expressed concern about the difficulty that people face discerning whether information on the web is true~\cite{bbcwebwarning}.
-Many people have also voiced concerns about how easily people can subvert Wikipedia to give people false information~\cite{wikifalse}.
-Several commentators have observed that there is a Media Echo Chamber effect~\cite{echochamber,echochamber2} in which news sources report claims that they have heard from other news sources, despite the fact that these claims may be misleading or untrue.
-If a user only reads news sources from a particular group then they may only be exposed to the views of that group and may not be aware that opposing views exist unless they actively seek them.
-
-Part of the problem is that conventional web browsers present the web as a network of connected pages, when it is often the case that what the user is really interested in is the factual claims made by those pages, and the connections between those claims.
-While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author.
-The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web.
-The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages).
-While this makes it easier for users to add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
-	\caption{Think link connects claims to each other and to web snippets}
-	\label{summarygraph}
-	\end{center}
-\end{figure}
-
-In this paper we present Think Link, a tool that overlays a new network of links over the existing web, connecting snippets of text to snippets elsewhere on the web that make related claims.
-Think Link maintains a central shared ``claim graph'' (Figure~\ref{summarygraph}) containing claims made on the web, their supporting and opposing relationships to each other, and the snippets that make these claims.
-When a user views a web page, Think Link highlights snippets that have been identified as making factual claims, with the highlight color indicating whether other sources have been found that disagree with the claim.
-If a user clicks on a snippet then they will see a ``claim browser'' (Figure~\ref{claimview}) that allows them to see other claims made on the web that support or oppose the claim the snippet makes, and snippets elsewhere on the web that make these other claims.
-
-The Think Link claim graph is editable by all users, in a manner similar to a wiki.
-Any user can add new claims, connect existing claims together, and identify snippets on web pages that make specific claims.
-Collaborative filtering is used to filter out junk or abusive information, while minimizing the danger of political edit wars.
-
-Not everyone will necessarily want a tool like Think Link.
-Some people may be looking for confirmation of their own points of view rather than information that challenges their beliefs.
-We hope however that Think Link may be able to make some contribution to helping people find out about other points of view, and help people more easily find the most interest claims about topics they are interested in.
-
-The contributions of this paper are the presentation of a new approach for connecting information on the web, the design of a user interface that makes it easy for users to find claims that support and oppose claims that they read on the web, and a qualitative user study of how participants use such an interface.
+% \begin{figure}[tb]
+% 	\begin{center}
+% 	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
+% 	\caption{Think link connects claims to each other and to web snippets}
+% 	\label{summarygraph}
+% 	\end{center}
+% \end{figure}
 
 \section{Related Work}
+
+\subsection{Argumentation}
+
+Cohere~\cite{Shum2008}.
+Compendium~\cite{Selvin2001}.
+Cope it~\cite{Karacapilidis2001}.
+AIF~\cite{McGinnis2007} and ArgDF~\cite{Rahwan2007}.
+IBIS~\cite{Rittel1973}.
+gIBIS~\cite{Conklin1987}.
+IBIS problems~\cite{Isenmann1997}.
+ClaimSpotter~\cite{Sereno2005,Sereno2004}.
+ClaiMaker~\cite{Uren2003}.
+Video Annotation~\cite{Diakopoulos2008}.
+Collabatorium~\cite{Klein2007}, for Global Warming~\cite{Malone2007}.
+Lawyer argument model~\cite{Verheij1999}.
+Toulmin model~\cite{Toulmin1958}.
+Zeno~\cite{Gordon1997}.
+Discoursium~\cite{Yetim2007}.
+Entity Workspace~\cite{Billman2007}. 
+Mess Maps and Resolution Mapping~\cite{Horn2007}.
+TRELLIS~\cite{Chklovski2005}.  
+People should define own link types~\cite{Wang1998}.
+
+\subsection{Checking Accuracy on the Web}
+
+NewsCube~\cite{Park2009}.
+Wikipedia fixes Vandalism~\cite{Viegas2004}.
+Trustworthiness~\cite{Gil2006}.
+WikiTrust~\cite{Adler2008}. Wiki Dashboard~\cite{Kittur2008}.
+Wiki Scanner\footnote{http://wikiscanner.virgil.gr}.
+SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.
+
+\subsection{Tagging and Annotating}
+
+Tagging~\cite{Marlow2006}. Tagomizer~\cite{Park2007}. Reasons for choices of tags~\cite{Sen2006}. Tagging Roles~\cite{Muller2008}.
+
+SpinSpotter\footnote{http://spinspotter.com}. ClipMarks\footnote{http://clipmarks.com}, Diigo~\footnote{http://diigo.com}, Stickis\footnote{http://stickis.com}.
+
+How to Personalize the Web~\cite{Barrett1997}.
+
+\subsection{Clipping}
+
+ScratchPad~\cite{Gotz2007}. Internet Scrapbook~\cite{Sugiura1998}. Reverse Linking~\cite{Yesilada2007}. Hunter Gatherer~\cite{2002}. Dontcheva~\cite{Dontcheva2007a}.
+
+\subsection{To discuss in the body}
+
+Paraphrases~\cite{Chklovski2005}. Suggested formal paraphrases~\cite{Blythe2004}.
+Importance of Lurkers~\cite{Takahashi2003}
+Wikify~\cite{Mihalcea2007}.
 
@@
 ScentHighlights~\cite{Chi2005} identifies sections of text that you might find interesting and highlights them for you.
-ScentTrails~\cite{Center2003} identifies links to documents that you might find interesting and makes them bigger.
+ScentTrails~\cite{Olston2003} identifies links to documents that you might find interesting and makes them bigger.
 Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.

### 2009-03-19 papers/uist_thinklink/thinklink.tex
Related work changes

@@
 
+Think Link builds on work in several different areas.
+The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987}; the idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by Wiki-Trust~\cite{Adler2008}; the model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}; and the idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
+
+What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of leading users towards information that conflicts with that which they read.
+
 \subsection{Argumentation}
@@
 
+Hypertext systems such as Notecards~\cite{Halasz1988}.
+
 \subsection{Checking Accuracy on the Web}
@@
 ScratchPad~\cite{Gotz2007}. Internet Scrapbook~\cite{Sugiura1998}. Reverse Linking~\cite{Yesilada2007}. Hunter Gatherer~\cite{2002}. Dontcheva~\cite{Dontcheva2007a}.
+
+\subsection{Semantic Web}
+
+Nobody is going to mark up their own web page as being wrong.
 

### 2009-03-19 papers/uist_thinklink/thinklink.tex
Did related work on argumentation and accuracy checking

@@
 
-Cohere~\cite{Shum2008}.
+Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}.
+IBIS tools such as gIBIS~\cite{Conklin1987}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1996}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas.
+While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue.
+Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.
+
+Cohere is perhaps the tool most similar to Think Link.
+Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from pages that one browses.
+While Cohere and Think Link both connect an argument graph to the web, they do so in very different ways.
+In Cohere, a user attaches a web snippet to their idea in order to use it as evidence.
+By contrast, in Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument.
+
+ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly document with logical triples (subject, verb, object) describing interesting claims that are being made in the document.
+This semantic information can be used to connect claims in different documents and see when a logical claim in one document contradicts another.
+Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.
+
+Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklink1987}, allowing a claim to support, oppose, or be related to another claim.
+Cohere~\cite{Shum2008} extends this by allowing one to new link types marked with pro,con,or neutral polarity Toulmin~\cite{toulmin1958} proposes a more complex graph structure, implemented that expresses warrants, data, qualifiers, and reservations.
+Verheij~\cite{Verheij1999} uses the Toulmin model to create an argumentation tool for lawyers.
+
+Think Link's argument visualization is influenced by the left-to-right layout of Cohere~\cite{Shum2008}.
+Compendium~\cite{Selvin2001} contains a number of other visualizations of argument graphs.
+Mess Maps~\cite{Horn2007} present an alternative view in which an argument is divided into different sectors, each of which presents the argument from a different frame of discourse (e.g.
+policy maker vs industrialist vs environmentalist).
+
+Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use.
+We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
+We do not expect users to use Think Link to create a detailed model of an argument and use this to reach consensus.
+Instead, our aim is that a user should use Think Link to discover when things they read are disputed, and easily find evidence for the other side.
+\todo{Say more about this}.
+
+When chosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use.
+For Think Link, we have tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model.
+The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.
+
+% TRELLIS
+% 
+%  gIBIS~\cite{Conklin1987} and other IBIS~\cite{Rittel1973} such as ZEN
+% 
+% Cohere~\cite{Shum2008} is probably the tool most similar
+% 
+% 
+% 
+% Cohere~\cite{Shum2008}.
 Compendium~\cite{Selvin2001}.
@@
 Discoursium~\cite{Yetim2007}.
-Entity Workspace~\cite{Billman2007}. 
-Mess Maps and Resolution Mapping~\cite{Horn2007}.
-TRELLIS~\cite{Chklovski2005}.  
-People should define own link types~\cite{Wang1998}.
+% Entity Workspace~\cite{Billman2007}. 
+% Mess Maps and Resolution Mapping~\cite{Horn2007}.
+% TRELLIS~\cite{Chklovski2005}.  
+% People should define own link types~\cite{Wang1998}.
+% 
+% Hypertext systems such as Notecards~\cite{Halasz1988}.
 
-Hypertext systems such as Notecards~\cite{Halasz1988}.
+\subsection{Checking Accuracy and Bias on the Web}
 
-\subsection{Checking Accuracy on the Web}
+If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}.
+Snopes is a database of urban legends that the site owners have investigated to determine whether they are true or not.
+FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.
 
-NewsCube~\cite{Park2009}.
-Wikipedia fixes Vandalism~\cite{Viegas2004}.
-Trustworthiness~\cite{Gil2006}.
-WikiTrust~\cite{Adler2008}. Wiki Dashboard~\cite{Kittur2008}.
-Wiki Scanner\footnote{http://wikiscanner.virgil.gr}.
-SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.
+NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias.
+NewsCube presents a user with articles on the same topic that have different biases.
+MediaCloud applies various statistical analyses to news sources so that a reader can see when different news sources associate different words with the same topic.
+
+Several authors have investigated ways to make Wikipedia\footnote{http://wikipedia.org} more trustworthy.
+WikiTrust~\cite{Adler2008} highlights passages on wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors.
+Wiki Dashboard~\cite{Kittur2008} presents the reader of a Wikipedia article with a visualization that shows them how it has been edited in the past and lets them see graphically how contentious the topic is.
+Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds Wikipedia edits that have been made by people with an interest in spreading misinformation (e.g.
+people from a company editing pages about that company).
+
+% 
+% 
+% NewsCube~\cite{Park2009}.
+% Wikipedia fixes Vandalism~\cite{Viegas2004}.
+% Trustworthiness~\cite{Gil2006}.
+% WikiTrust~\cite{Adler2008}. Wiki Dashboard~\cite{Kittur2008}.
+% Wiki Scanner\footnote{http://wikiscanner.virgil.gr}.
+% SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.
 
 \subsection{Tagging and Annotating}
+
+Video Annotation~\cite{Diakopoulos2008}
 

### 2009-03-19 papers/uist_thinklink/thinklink.tex
More work on related work

@@
 
+In attempt to unify the different argumentation tools being developed, several interchange formats have been proposed~\cite{Rahwan2007a,McGinnis2007} to allow different web argumentation tools to share descriptions of contentious issues.
+
 Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use.
@@
 
-\subsection{Tagging and Annotating}
+\subsection{Tagging, Clipping, and Annotating}
 
-Video Annotation~\cite{Diakopoulos2008}
+Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags.
+Notable tagging systems include del.icio.us\footnote{http:\\del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.
 
-Tagging~\cite{Marlow2006}. Tagomizer~\cite{Park2007}. Reasons for choices of tags~\cite{Sen2006}. Tagging Roles~\cite{Muller2008}.
+Some tagging tools also do clipping.
+Clipping tools such as Internet Scrapbook~\cite{Sugiura19998}, Hunter Gatherer~\cite{2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends.
+In many cases, a tagging or clipping system will also allow users who are looking at a tagged or clipped object to see the tags that other users have associated with it, or highlight the parts of a document that have been clipped.
 
-SpinSpotter\footnote{http://spinspotter.com}. ClipMarks\footnote{http://clipmarks.com}, Diigo~\footnote{http://diigo.com}, Stickis\footnote{http://stickis.com}.
+Several tools allow users to mark up content that is considered to controversial.
+Videolyzer~\cite{Diakopoulos2008} allows users to annotate and comment on political videos with accompanying textual transcriptions.
+A user can mark up a section of video for bias, accuracy, or rhetorical technique.
+Comments can include references to external sources that back up the argument being made.
 
-How to Personalize the Web~\cite{Barrett1997}.
+SpinSpotter\footnote{http://spinspotter.com} allows a user to highlight snippets of text that contain spin or bias and either describe why the text is biased, or rewrite the text in an unbiased way.
+While SpinSpotter and Think Link share a goal of drawing user attention to biased or inaccurate information, they do so in a different way.
+SpinSpotter annotates a snippet with an annotation specific to that particular snippet of text, while Think Link treats a snippet as being an instance of a shared contentious claim, and links all snippets identified as making that claim to a shared graph node linking to other information about that claim.
 
-\subsection{Clipping}
+\subsection{Augmented Web Navigation}
 
-ScratchPad~\cite{Gotz2007}. Internet Scrapbook~\cite{Sugiura1998}. Reverse Linking~\cite{Yesilada2007}. Hunter Gatherer~\cite{2002}. Dontcheva~\cite{Dontcheva2007a}.
+Several tools layer an alternative navigation graph over information on the web.
+TextRunner~\cite{Etzioni2008} looks for instances of subject-verb-object triples on web pages and connects these together as a graph in which objects are linked by statements made about them on different web pages.
 
-\subsection{Semantic Web}
+Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
+This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.
 
-Nobody is going to mark up their own web page as being wrong.
+% Tagging~\cite{Marlow2006}. Tagomizer~\cite{Park2007}. Reasons for choices of tags~\cite{Sen2006}. Tagging Roles~\cite{Muller2008}. 
+% 
+% SpinSpotter\footnote{http://spinspotter.com}. ClipMarks\footnote{http://clipmarks.com}, Diigo~\footnote{http://diigo.com}, Stickis\footnote{http://stickis.com}.
+% 
+% How to Personalize the Web~\cite{Barrett1997}.
+
+% \subsection{Clipping}
+% 
+% ScratchPad~\cite{Gotz2007}. Internet Scrapbook~\cite{Sugiura1998}. Reverse Linking~\cite{Yesilada2007}. Hunter Gatherer~\cite{2002}. Dontcheva~\cite{Dontcheva2007a}.
+
+% \subsection{Semantic Web}
+% 
+% Nobody is going to mark up their own web page as being wrong.
 
@@
 Wikify~\cite{Mihalcea2007}.
-
-Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}.
-Like Think Link, wikis allow users to find information organized by topic rather than author and allow users to collaborate together to bring together all the best information about a topic.
-Wikipedia's greatest strength is arguably also its greatest weakness.
-Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}.
-Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2,wikicorrect3}, but it is difficult to remove the problem entirely.
-While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious.
-Think Link tries to avoid this problem by linking claims back to the original sources that made these claims.
-Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim.
-
-When a topic is heavily politicized, Wikipedia can be subject to edit wars in which people who hold one opinion delete opinions held by the other side~\cite{wikicorrect3}, making it difficult for the community to collaborate together to produce a document that is both comprehensive and unbiased.
-Think Link attempts to avoid this problem by taking an ``append-only, collaborative filtering'' approach.
-A user cannot remove claims that they disagree with\footnote{With special exceptions for dealing with spam and abuse}.
-Instead all they can do is vote against them, and connect them to claims that provide opposing evidence.
-
-Another key difference between Think Link and a wiki is that Think Link pulls the whole web into its graph of connected claims.
-A user can use Think Link to investigate claims they read on arbitrary web sites, without having to restrict their browsing to a single wiki site.
-
-SpinSpotter~\cite{spinspotter} shares Think Link's goal of allowing users to identify misleading and inaccurate information on web pages that they read.
-If a user sees a section of text that they think is misleading then they can mark it up, causing it to be highlighted when other users view the same page.
-While Think Link and SpinSpotter both share the goal of letting users mark up snippets that may be inaccurate, they differ in what they let users find out about such snippets.
-SpinSpotter allows users to give a textual description of why the snippet is spin and a suggested edit that would make it more accurate.
-Think Link instead connects the snippet to its global claim graph, allowing users to quickly access evidence for and against the truth of the claim.
-There is also a difference in the nature of what SpinSpotter and Think Link expect users to mark up.
-Think Link is interested in evaluating the truth of factual claims, while SpinSpotter also interested in identifying biased phrases (e.g.
-``tree hugger'').
-
-Other web annotation systems such as ShiftSpace.org, Stickis.com, SharedCopy.com, and Diigo.com allow people to add their own annotations to existing web pages and view annotations written by other people.
-Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relevant documents.
-More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.
-We are not aware of any such system that links web pages to a graph of factual claims.
-
-Web clipping tools such as Google Notebook, Scrapbook~\cite{scrapbook}, and Zotero.org allow one to gather and organize interesting from web pages.
-Many web clipping tools are also web annotation systems.
-These tools are designed for gathering and sharing interesting information, rather than for identifying the claims being made, or allowing users to navigate to related claims being made on other sites.
-
-In Vannevar Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them.
-As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''.
-Several more recent systems have allowed user to add links to existing pages.
-ENQUIRE~\cite{weavingtheweb} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it.
-Everything2.com links each page to the most popular pages that users viewed at the same time.
-Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making and allowing users to browse this graph, rather than just allowing users to specify links between pages.
 
@@
 We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link.
-Think Link uses icons from the free FamFamFam Silk~\cite{silkicons} collection.
+Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.
 
+\todo{Sort out bad references}
 \bibliography{refs}

### 2009-03-20 papers/uist_thinklink/thinklink.tex
Fixed position of top bar. Added ability to search wikipedia topics

@@
 Think Link builds on work in several different areas.
-The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987}; the idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by Wiki-Trust~\cite{Adler2008}; the model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}; and the idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
+The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}; the idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by Wiki-Trust~\cite{Adler2008}; the model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}; and the idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
 
@@
 Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}.
-IBIS tools such as gIBIS~\cite{Conklin1987}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1996}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas.
+IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1996}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas.
 While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue.
-Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.
+Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.
 
@@
 
-Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklink1987}, allowing a claim to support, oppose, or be related to another claim.
-Cohere~\cite{Shum2008} extends this by allowing one to new link types marked with pro,con,or neutral polarity Toulmin~\cite{toulmin1958} proposes a more complex graph structure, implemented that expresses warrants, data, qualifiers, and reservations.
+Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklink1987a}, allowing a claim to support, oppose, or be related to another claim.
+Cohere~\cite{Shum2008} extends this by allowing one to new link types marked with pro,con,or neutral polarity Toulmin~\cite{toulmin1958} proposes a more complex graph structure, that expresses warrants, data, qualifiers, and reservations.
 Verheij~\cite{Verheij1999} uses the Toulmin model to create an argumentation tool for lawyers.
+More complicated models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence, where it is necessary to be more precise about the structure of an argument.
 
@@
 Several tools layer an alternative navigation graph over information on the web.
-TextRunner~\cite{Etzioni2008} looks for instances of subject-verb-object triples on web pages and connects these together as a graph in which objects are linked by statements made about them on different web pages.
-
+TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages.
+ScentHighlights~\cite{Chi2005a} highlights snippets of text on a web page that are related to topics that the user has said that they are intersted in.
 Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
@@
 Wikify~\cite{Mihalcea2007}.
-
-One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed.
-This is a goal that is shared with several other projects.
-Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allow users to navigate from such a passage to all other documents where that passage is quoted.
-Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus.
-ScentHighlights~\cite{Chi2005} identifies sections of text that you might find interesting and highlights them for you.
-ScentTrails~\cite{Olston2003} identifies links to documents that you might find interesting and makes them bigger.
-Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.
-
-Much work has been done on the idea of using a graph to represent an argument~\cite{argumentation,argmas}.
-Popular argument models include the Toulmin Model~\cite{toulmin}, the Carneades Model~\cite{carneades}, and the IBIS model~\cite{ibis}.
-Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model, with the result that they provide a more accurate model of the logical argument, at the cost of requiring more skill to assemble.
-One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numerical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.
 

### 2009-03-20 client_js/tl_snippet.js

@@ -141,7 +141,7 @@ function tl_snippet_dialog(margin) {
 		node = para;
 		
 		var pagetext = "";
-		while(pagetext.length < 1000){
+		while(node && pagetext.length < 1000){
 			if(node.tagName == para.tagName){
 				pagetext += node.textContent + " ";
 			}

### 2009-03-20 java/com/intel/thinklink/MainServlet.java

@@ -21,18 +21,19 @@ public class MainServlet extends HttpServlet {
 		doGet(req,res);
 	}
 	
-	protected void matchForId(PrintWriter out, HttpServletRequest req, int id){
+	protected void matchForId(PrintWriter out, HttpServletRequest req, int id,String text){
 		try{
 			DataBase base = ConnectionPool.get();
 			try{
-				Dyn info = base.getInfo(id);
-				String text;
-				if(info.get("type").equals("snippet")){
-					Dyn snippet = base.getSnippet(id);
-					String sniptext = snippet.get("text");
-					text = sniptext + " " + sniptext + " " + sniptext + " " + sniptext+ " " + sniptext + " " + snippet.get("page_text");			
-				}else{
-					text = info.get("text");
+				if(text == null){
+					Dyn info = base.getInfo(id);
+					if(info.get("type").equals("snippet")){
+						Dyn snippet = base.getSnippet(id);
+						String sniptext = snippet.get("text");
+						text = sniptext + " " + sniptext + " " + sniptext + " " + sniptext+ " " + sniptext + " " + snippet.get("page_text");			
+					}else{
+						text = info.get("text");
+					}
 				}
 				
 				Vector<WikiMatch> matches = WikiMatcher.getMatches(text); 
@@ -80,9 +81,15 @@ public class MainServlet extends HttpServlet {
 		
 		String text = req.getParameter("text");
 		String id = req.getParameter("id");
+		String callback = req.getParameter("callback");
 		
+		int idnum = 0;
 		if(id != null){
-			matchForId(out,req,Integer.parseInt(id));
+			idnum = Integer.parseInt(id);
+		}
+		
+		if(callback != null){
+			matchForId(out,req,idnum,text);
 			out.close();
 			return;
 		}

### 2009-03-20 webapps/node/javascript/leftrightui.js

@@ -182,6 +182,18 @@ function makeNavButtons(panelnum){
 	return navbuttons;
 }
 
+function filterByType(list,type){
+	var out = [];
+	if(!list) return [];
+	for(var i = 0; i<list.length;i++){
+		var item = list[i];
+		if(item.type == type){
+			out.push(item);
+		}
+	}
+	return out;
+}
+
 function makeInfo(obj,panelnum){
 	var info = $("<div class='info'/>");
 	var body = $("<div class='panelbody'>").appendTo(info);
@@ -226,8 +238,10 @@ function makeInfo(obj,panelnum){
 			body.append(makeSubGroup("related topics",obj.from.about,panelnum));
 			break;
 		case "topic":
-			body.append(makeSubGroup("claims about this topic",obj.to.about,panelnum));
-			body.append(makeSubGroup("snippets about this topic",obj.to.snipabout,panelnum));
+			var claims = filterByType(obj.to.about,"claim");
+			var snippets = filterByType(obj.to.about,"snippet");
+			body.append(makeSubGroup("claims about this topic",claims,panelnum));
+			body.append(makeSubGroup("snippets about this topic",snippets,panelnum));
 			body.append(makeSubGroup("related topics",relates,panelnum));
 			break;
 		case "claim":
@@ -303,16 +317,25 @@ function makeAdder(title,type,verb,reverse,panel,obj,panelnum){
 			adder.parent().find(".adder-selected").attr("class","adder");
 			adder.attr("class","adder-selected");
 			var textbox = $("<input class='addtxt' type='text'>").appendTo(panel);
-			var gobut = $("<input class='addbutton' type='button' value='add'>").appendTo(panel);
+			var gobut = $("<input class='addbutton' type='button' value='add'>")
+				.click(function(){
+					callback({text:textbox.val(),id:"none"});
+				})
+				.appendTo(panel);
 
 			textbox.keyup(function(){
 				var text = textbox.val();
 				setTimeout(function(){
 					var nowtext = textbox.val();
 					if(text == nowtext){
-						updateSuggestions(panel,
-							urlbase+"node/search.js?type="+type+"&callback=?&query="+encodeURIComponent(text),
-							panelnum,"suggested "+type+"s",obj,callback);
+						if(type=="topic"){
+							updateTopicSuggestions(panel,text,
[…]

### 2009-03-21 papers/uist_thinklink/thinklink.tex
Added transparency to the UI. Fixed some bugs. Wrote more paper stuff

@@
 \newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
+\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
 
@@
 
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/v2_popup.png}
+	\caption{Click on a claim to investigate evidence for and against it}
+	\label{claimview}
+	\end{center}
+\end{figure}
+
 In this paper we present Think Link, a tool helps users discover when information they read conflicts with information on other web sites, and shows users the best sources that provide alternative points of view.
@@
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/claim_popup_crop2.png}
-	\caption{Click on a claim to investigate evidence for and against it}
-	\label{claimview}
-	\end{center}
-\end{figure}
+\todo{Talk about automatically including all arguments from snopes}.
 
@@
 \section{Related Work}
+\todo{Don't cite things that aren't relevant}
 
@@
 
-Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklink1987a}, allowing a claim to support, oppose, or be related to another claim.
+Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklin1987a}, allowing a claim to support, oppose, or be related to another claim.
 Cohere~\cite{Shum2008} extends this by allowing one to new link types marked with pro,con,or neutral polarity Toulmin~\cite{toulmin1958} proposes a more complex graph structure, that expresses warrants, data, qualifiers, and reservations.
@@
 The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.
+
+% \subsection{Open Hypermedia}
+% 
+% 
+% \todo{Talk about other hypertext systems - mention arguments integrated into documents an old idea and talk about open hypermedias}
 
@@
 FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.
+Think Link's database automatically imports all contentious claims identified by Snopes.
 
@@
 
-\subsection{Tagging, Clipping, and Annotating}
+\subsection{Annotating, Tagging, and Clipping}
+
+Think Link is an example of an Open Hypermedia system~\cite{Bouvin2000}.
+Like other Open Hypermedia systems, Think Link allows users to lay an additional link structure over an existing hypertext document.
+Think Link differs from prior open hypermedia systems in its focus on revealing contentious arguments.
+While other systems such as HyperDISCO~\cite{Wiil1996} could be used to link a snippet to a contentious claim, they do not provide user interface support to make this easy.
+
+\todo{Say how different from other Open Hypermedia link annotation systems}
 
@@
 
-Some tagging tools also do clipping.
+Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001}, CritLink~\cite{Yee2002},
+
+Some tagging and annotation tools also do clipping.
 Clipping tools such as Internet Scrapbook~\cite{Sugiura19998}, Hunter Gatherer~\cite{2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends.
@@
 
-Several tools allow users to mark up content that is considered to controversial.
+Several tools allow users to annotate content that is considered to controversial.
 Videolyzer~\cite{Diakopoulos2008} allows users to annotate and comment on political videos with accompanying textual transcriptions.
@@
 Comments can include references to external sources that back up the argument being made.
-
 SpinSpotter\footnote{http://spinspotter.com} allows a user to highlight snippets of text that contain spin or bias and either describe why the text is biased, or rewrite the text in an unbiased way.
@@
 Importance of Lurkers~\cite{Takahashi2003}
-Wikify~\cite{Mihalcea2007}.
+Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.
 
@@
 
-Think Link is a tool that overlays a web of factual claims on the existing web (Figure~\ref{summarygraph}).
-As a user browses the web, Think Link highlights snippets of text that have been identified as making factual claims.
-If a user clicks on a highlighted snippet, Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}).
-Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.
+Think Link is designed to be used in two different ways.
+Sceptical readers browse the web and wish to be alerted when information they read conflicts with information found on other web sites.
+Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of sceptical readers to claims that they disagree with.
+The same user may act as a sceptical reader sometimes and an activist at other times.
 
-Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}).
-This graph is managed like a wiki, allowing any user to add new claims or snippets.
-As a user browses the web, they can identify snippets that make claims that are interesting or controversial and link them into the global claim graph.
+\subsection{Browsing the Disputed Web}
 
-Think Link is implemented as a Firefox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.
+If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
+If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is.
+If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evedience for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).
 
-\subsection{Exploring factual claims on a page}
+Since the purpose of a highlight is to alert the user to claims that they had not realised were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious.
+A user can click the ``don't highlight this claim again'' button to tell Think Link that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.
 
-When a user browses a web page, we want to make them aware of claims being made on the page that they might find interesting, or that other sources disagree with.
-Think Link draws attention to the factual claims that other users have identified on a web page by highlighting them (Figure~\ref{highlight}).
-Snippets are highlighted in red if they are contentious (other sources disagree with the claim).
-The highlight colors are chosen to be pale enough to not impede reading, dark enough to be noticeable\footnote{Unless the background is close to a highlight color.
-Think Link does not yet adapt to different page background colors}, and different enough to be distinguishable by colorblind people.
-A user can see what claim a snippet is making by hovering their mouse over the snippet (Figure~\ref{highlight}).
+\todo{ignore button}
+\todo{talk about the margin?}
+
+\subsection{Exploring the Argument Graph}
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/sidebar_diagram.png}
-	\caption{The margin summarizes the key claims on the page}
-	\label{margin}
+	\includegraphics[width=8.5cm]{../screenshots/v2_panels.png}
+	\caption{The claim graph consists of a series of linked panels}
+	\label{panels}
 	\end{center}
@@
 
-If a user thinks a claim is interesting and wants to know what other sources say about it then they can open up a ``claim browser'' window (Figures~\ref{claimview} and \ref{claimbrowse_diagram}) by clicking on the highlighted snippet.
-The claim browser allows the user to easily view claims that support or oppose the selected claim, and find snippets of text on the web that make these claims (Figure~\ref{claimview}).
-For example, if a user browsed a web page that claimed ``Global Warming does not exist'', then the snippet that made this claim would be highlighted in red, indicating that there are web pages elsewhere that make opposing claims.
-If the user were to click on the highlighted snippet then an ``investigate claim'' window would appear (Figure~\ref{claimview}).
-This window would show the user that the claim ``Global Warming does not exist'' is opposed by the claim ``There is strong evidence for global warming''.
-If the user navigated to this new claim then they could quickly see the best claims that support the existence of global warming, and would be able to see summaries of the best sources that supported these claims.
+Once a user has identified a claim that they are interested in, they can use Think Link's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.
 
-%\begin{floatingfigure}{2cm}
-%\includegraphics[width=2cm]{../screenshots/marginpull_out.png}
-%\end{floatingfigure}
+In our user studies, we found that users wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim.
+We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left.
+If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right.
+To emphasise the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
 
-If the current page contains snippets then a tab appears in the top left corner of the window.
+We found that it was important to allow the claim browser interface to be used in two different ways.
+When a user is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.
+
+To preserve visual consistency, Think Link uses the same claim browser interface for the small popup interface as for the full-window interface.
+When used as a popup browser, the interface shows only one panel.
+Clicking on an item in the panel scrolls the display to the right to reveal a new panel in a manner similar to Apple's iPhone.
+If the user clicks the ``back'' button, the interface will quickly scroll left back to the previous panel.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/v2_vote.png}
+	\caption{Voting buttons let users say which evidence is important}
+	\label{voting}
+	\end{center}
+\end{figure}
+
+%\todo{Key issue with hypertext was not talking about things that highlighted arguments?}
+
+Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model.
+There are four types of node: snippets, claims, topics, and users.
+A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to, and a user is a person who users Think Link.
+Nodes are connected together by typed, directed, links.
+There are three link types: supports, opposes, and relates-to.
+A claim can support,oppose, or relate-to another claim, a claim can relate-to a topic, and a topic can relate-to another topic.
+This is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, and we allow a claim to simply relate-to another claim, rather than having to either support or oppose it.
+
+Think Link uses topics to group together related claims.
+A topic be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''.
+Alternatively, it can be a thing that claims are about, for example ``Carbon Dioxide''.
+Think Link uses the list of page titles on Wikipedia as a seed-set for its topics.
+
+The panel for a claim lists evidence that will help a user decide whether the claim is true.
+Evidence is categorised as either supporting, opposing, or being related-to the claim.
+The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument.
+Evidence can either be a snippet that talks about that claim, or another claim whose truth would support the truth of this claim.
+
+The order in which evidence is displayed is determined by user voting.
+A user can vote for or against a particular piece of evidence by clicking on the voting button next to that item~(Figure~\ref{voting}).
+When a user looks at a list of evidence they will see first the things they voted for and then the other evidence ordered based on the number of votes it received from other users.
+
+One danger in a voting system is that a large group of people will drown out the opinions of their opponents by voting down their opinions.
+Think Link uses several strategies to try to avoid this happening.
+Firstly, positive votes count for more than negative votes.
+Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent.
+Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side.
+Of course, these techniques only work to a limited extent, and so we expect that editorial moderation may be needed for highly controversial topics, as it is in Wikipedia.
+
+\todo{Talk about searches}
+\todo{Cite work on collaborative filtering}
+
+% If the current page contains snippets then a tab appears in the top left corner of the window.
 The tab contains a light bulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim.
@@
 
-\subsection{The Mental Model}
+\subsection{Campaigning on the Disputed Web}
 
@@
 	\begin{center}
-	\includegraphics[width=7cm]{../screenshots/bookmark_icons2.png}
-	\caption{Icons used for Claims, Snippets, and Topics}
-	\label{bookmark_icons}
+	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
+	\caption{Use topic suggestion to quickly file evidence snippets}
+	\label{sniptopic}
 	\end{center}
@@
 
-Think Link users interact with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}):
+\subsection{Organizing the Argument Graph}
 
-\begin{itemize}
-\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false.
-For example ``Global warming is man made''.
-A claim may support or oppose other claims.
-Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
-\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim.
-Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
-\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about.
-For example ``Global Warming'', or ``Computer Science''.
-A claim can be about one or more topics, and a topic can have one or more more general topics.
-Topics are used to organize and disambiguate claims.
-For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''.
-Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
-A topic can itself by disambiguated by having a super-topic.
-\end{itemize}
-
-\subsection{Browsing factual claims}
-\label{browseclaim}\label{claimbrowser}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
-	\caption{The claim browser visualizes the claim graph}
-	\label{claimbrowse_diagram}
-	\end{center}
-\end{figure}
-
-Claims and topics form a directed graph structure. A claim can have any number of claims that support or oppose it, and any number of claims that it supports or opposes.
-A topic can have any number of more specific topics (e.g.
-``US Election 2008'' is more specific than ``US Elections'') and any number of more general topics.
-A topic can also have any number of claims about that topic.
-
-When designing an interface to this structure, we were faced with two opposing constraints.
-We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree.
-Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place.
-Tree-based outliners such as OmniOutliner~\cite{omnioutliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
-
-After several design iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner.
-Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it.
-Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.
-
-The placement of objects above and below is intended to emphasize the conventional hierarchical structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
-A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/claimbrowse_zoom.png}
-	\caption{Close up of a list of supporting claims}
-	\label{claimbrowse_zoom}
-	\end{center}
-\end{figure}
-
-Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states.
-When a new item is selected, it grows in size and moves to the center.
-Other items that were already on the screen move from their current locations to their new locations.
-Other objects appear and disappear by smoothly sliding into or out of view.
-
-Users see a claim browser in three different places.
-The {\it organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}).
-The {\it popup browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}).
-The {\it claim selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).
+\todo{Talk about organizing stuff}
 
@@
 When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.
+
+\subsection{Implementation}
+
+Think Link consists of a browser extension a shared public database of contentious claims, and a web-based argument interface that allows one to explore and manipulate the claim graph.
+These three components are largely independent of each other and talk to each other using an open API that can also be used by other tools.
+Indeed the settings panel for the browser extension allows it to be pointed to alternative data stores or graphical interfaces.
+
+As a user browses the web, the browser extension consults the database to identify snippets that other users have previously marked as making disputed claims.
+Any such snippets are highlighted in red to show the user that there is an alternative viewpoint that they might want to investigate.
+If a user clicks on a highlighted snippet then the browser extension opens the web based argument interface, showing the user the evidence that users have collected on both sides of the issue.
+
+\todo{Describe how one goes about marking disputed claims}.
+
+If a user has added the Think Link extension to their browser then it will highlight snippets that make disputed claims (Figure~\ref{highlight}). If
+
+an open database of contentious claims, and an interactive claim browser that allows one to explore the various snippe
+
+If a user has added the Think Link extension to their browser then it will highlight
+
+Think Link is a browser plugin that is designed to help users tell when the information that they read on the web is inaccurate or presents only one side of a contentious issue.
+As the user browses the web, Think Link
+
+% 
+% 
+% \subsection{The Mental Model}
+% 
+% \begin{figure}[tb]
+% 	\begin{center}
+% 	\includegraphics[width=7cm]{../screenshots/bookmark_icons2.png}
+% 	\caption{Icons used for Claims, Snippets, and Topics}
+% 	\label{bookmark_icons}
+% 	\end{center}
+% \end{figure}
+% 
+% Think Link users interact with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}): 	
+% 
+% \begin{itemize}
+% \item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false.
+For example ``Global warming is man made''.
+A claim may support or oppose other claims.
+Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
+% \item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim.
+Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
+% \item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about.
+For example ``Global Warming'', or ``Computer Science''.
+A claim can be about one or more topics, and a topic can have one or more more general topics.
+Topics are used to organize and disambiguate claims.
+For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''.
+Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
+A topic can itself by disambiguated by having a super-topic.
+% \end{itemize}
+% 
+% 
+% \subsection{Browsing factual claims}
+% \label{browseclaim}\label{claimbrowser}
+% 
+% \begin{figure}[tb]
+% 	\begin{center}
+% 	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
+% 	\caption{The claim browser visualizes the claim graph}
+% 	\label{claimbrowse_diagram}
+% 	\end{center}
+% \end{figure}
+% 
+% 
+% Claims and topics form a directed graph structure. A claim can have any number of claims that support or oppose it, and any number of claims that it supports or opposes.
+% A topic can have any number of more specific topics (e.g.
+``US Election 2008'' is more specific than ``US Elections'') and any number of more general topics.
+A topic can also have any number of claims about that topic.
+% 
+% When designing an interface to this structure, we were faced with two opposing constraints.
+We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree.
+Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place.
+Tree-based outliners such as OmniOutliner~\cite{omnioutliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
+% 
+% After several design iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner.
+Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it.
+Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.
+% 
+% The placement of objects above and below is intended to emphasize the conventional hierarchical structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
+A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
+% 
+% \begin{figure}[tb]
+% 	\begin{center}
+% 	\includegraphics[width=6cm]{../screenshots/claimbrowse_zoom.png}
+% 	\caption{Close up of a list of supporting claims}
+% 	\label{claimbrowse_zoom}
+% 	\end{center}
+% \end{figure}
+% 
+% Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states.
+When a new item is selected, it grows in size and moves to the center.
+Other items that were already on the screen move from their current locations to their new locations.
+Other objects appear and disappear by smoothly sliding into or out of view.
+% 
+% Users see a claim browser in three different places.
+The {\it organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}).
+The {\it popup browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}).
+The {\it claim selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).
 

### 2009-03-21 client_js/tl_point.js

@@ -43,13 +43,24 @@ function tl_point_browser() {
 	this.init = function() {
 	}
 		
+	this.addFader = function(viewframe){
+		var fader = document.createElement("div");
+		fader.className = "tl_fader";
+		fader.addEventListener("click",function(ev){
+			document.body.removeChild(fader);
+			document.body.removeChild(viewframe);
+		},true);
+		document.body.appendChild(fader);
+		return fader;
+	}	
+		
 	this.viewFrame = function(snippet) {
 		var url;
 		if(snippet.claimid){
-			title = "Claim Info";
+			//title = "Claim Info";
 			url = thinklink_pointbase+snippet.claimid+"?snippet="+snippet.id;
 		}else{
-			title = "Snippet Info";
+			//title = "Snippet Info";
 			url = thinklink_pointbase+snippet.id+"/setclaim";
 		}
 		
@@ -65,6 +76,8 @@ function tl_point_browser() {
 		win.style.zIndex = "214783647";
 		document.body.appendChild(win);
 		
+		var fader = this.addFader(win);
+				
 		win.style.overflow = "hidden";
 		win.style.position = "fixed";
 		win.style.top = "50px";
@@ -87,37 +100,55 @@ function tl_point_browser() {
 		buttonBox.style.right = "4px";
 		titleBar.appendChild(buttonBox);
 		
-		var titleBox = document.createElement("nobr");
-		titleBox.textContent = title;
-		titleBar.appendChild(titleBox);
+		//var titleBox = document.createElement("nobr");
+		//titleBox.textContent = title;
+		//titleBar.appendChild(titleBox);
+
+
+		var ignoreButton = document.createElement("input");
+		ignoreButton.className = "tl_openbutton";
+		ignoreButton.setAttribute("type","button");
+		ignoreButton.setAttribute("value","Don't highlight this again");
+		buttonBox.appendChild(ignoreButton);
+		ignoreButton.addEventListener("click",function(){
+			that.hideMe();
+			tl_doAJAX("tl_ignore","scripthack/ignoreclaim.js"+
+				"?claim="+snippet.claimid,function(){});					
+		},true);
 		
 		var openButton = document.createElement("input");
 		openButton.className = "tl_openbutton";
 		openButton.setAttribute("type","button");
-		openButton.setAttribute("value","Open Organizer");
+		openButton.setAttribute("value","Open Full Interface");
 		buttonBox.appendChild(openButton);
 		openButton.addEventListener("click",function(){
[…]

### 2009-03-21 webapps/node/javascript/leftrightui.js

@@ -4,10 +4,12 @@ var panelbox = null;
 var topbar = null;
 
 var widthpad = null;
+var global_miniui = true;
 
 function makeUI(id,withtop){
 	if(withtop){
 		topbar = makeTopBar();
+		global_miniui = false;
 	}
 	if(!id){
 		id = "recent.js";
@@ -15,8 +17,19 @@ function makeUI(id,withtop){
 	$(document.body).append(topbar);
 	panelbox = $("<tr class='panelbox'/>");
 	$(document.body).append($("<table class='toptable'>").append(panelbox));
-	widthpad = $("<div class='widthpad'>pad</div>").appendTo(document.body);	
+	widthpad = $("<div class='widthpad'/>").appendTo(document.body);	
 	getPanel(0,id);
+	if(global_miniui){
+		$(".toptable").css("margin-top",0);
+	}else{
+		$(window).resize(doLayout);
+		doLayout();
+	}
+}
+
+function doLayout(){
+	if(global_miniui) return;
+	$(".panelbody").height(window.innerHeight - 90 + "px");
 }
 
 function makeTopBar(){
@@ -77,6 +90,7 @@ function getPanel(panelnum,nodeid,name){
 	}
 	panel = makePanel(panelnum,nodeid,name);
 	panelbox.append(panel);
+	doLayout();
 }
 
 function removeArrows(panelnum){
@@ -87,25 +101,21 @@ function removeArrows(panelnum){
 
 function makeArrow(panelnum,item){
 	removeArrows(panelnum);
-	var pos = getPos(item.get(0));
+	var pos = GetElementAbsolutePos(item.get(0));
 	var arrow = $("<td class='arrow'>")
 		.attr("id","arrow-"+panelnum)
-		.css("padding-top",pos.top + item.height()/2 - 60);
+		.css("padding-top",pos.y + item.height()/2 - 60);
 	arrow.append($("<img/>").attr("src",iconUrl("big_right_arrow")));
 	return arrow;	
 }
 
-function moveArrow(){
-	var node;
-	if(selection){
-		node = selection;
-	}else{
-		node = $("#panel-0");
+function updateArrowPos(panelnum){
+	var item = selection[panelnum];
+	var arrow = $("#arrow-"+panelnum);
+	if(item && arrow){
+		var pos = GetElementAbsolutePos(item.get(0));
+		arrow.css("padding-top",pos.y + item.height()/2 - 60);				
 	}
[…]

### 2009-03-21 papers/uist_thinklink/thinklink.tex
More paper, screenshot, and bug fix work

@@
 \todo{Cite work on collaborative filtering}
+\todo{Mention the sidebar?}
 
@@
 
+If an activist user has installed the Think Link browser extension then they can mark up snippets that they believe make disputed claims, causing them to be highlighted when viewed by other readers.
+A user can mark a snippet as disputed by selecting the text, and clicking ``This is disputed'' in the context menu.
+
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/v2_snipmark.png}
+	\caption{Use the context menu to mark a new snippet}
+	\label{createprocess}
+	\end{center}
+\end{figure*}
+
+In order for the snippet to be useful for other readers, one needs to state what claim it is making.
+Since a user will often want to collect many snippets that make the same point, Think Link allows a user to associate snippets with claims in bulk, rather than having to specify a snippet every time they create a snippet.
+
+When a user creates a snippet, it is initially highlighted in blue, to show that it has not yet been associated with a claim.
+Such unattached snippets are only visible to the user who created them.
+A user can chose to associate a snippet with a claim immediately by clicking on it and selecting from a list of suggested snippets.
+Alternatively, they can use the claim browser to assign snippets to claims in bulk (Figure~\ref{sniptopic}).
+
+% Put all user study stuff at the end
+
+In order for the snippet to be useful for other readers, one needs to state what claim it is making.
+Early versions of Think Link required a user to state the disputed claim that a snippet was making at the point at which they marked it; however our studies revealed that this made the process of marking snippets too arduous and deterred users from marking snippets.
+Recent versions of TWe thus instead created an interface that allows a user to mark up snippets without saying what claim they are making and then assign snippets to claims ``in bulk'' (Figure~\ref{sniptopic}.
+
 \begin{figure}[tb]
@@
 	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
-	\caption{Use topic suggestion to quickly file evidence snippets}
+	\caption{The claim browser shows a list of unfiled snippets}
 	\label{sniptopic}
 	\end{center}
+\end{figure}
+
+When a user creates a snippet, it is intially highlighted in blue, to show that it has not yet been associated with a snippet and will not be visible to other users.
+If the user clicks on the highlighted snippet then
+
+If an activist user is looking for snippets that make a particular claim that they disagree with then they may collect many snippets that are making the same claim. Rather than requiring
+
+It is important to make this process as simple and easy as possible.
+
+ Rather than requiring a user to specify the claim a snippet is making when the snippet is created, Think Link allows users to mark snippets without saying what it is they claim and then associate snippets with claims ``in bulk''.
+
+It is important to make the process of creating snippassociating snippets with claims as easy as possible. If
+
+ In early versions of Think Link we required a user to state the claim a snippet was making when they marked it; however our user studies revealed that this made the process of creating snippets take too long and put users off creating them.
+
+In early versions of Think Link we required a user to state the claim a snippet was making at the point at which they created the snippet; however our user studies revealed that
+
+Think Link allows an activist user to highlight snippets that they believe make contentious claims so that other readers will be exposed to the evidence on the other side.
+If a user finds a snippet of text that they believe is making a disputed claim then they can select the text, and select ``This is disputed'' from the
+
+\begin{figure}[tb]
+	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram_full.png}
+	\caption{Selecting the claim made by a new snippet}
+	\label{snipsavecrop}
 \end{figure}
@@
 
-\begin{figure*}[tb]
-	\begin{center}
-	\includegraphics[width=16cm]{../screenshots/newsnip_all.png}
-	\caption{Process for creating a new snippet}
-	\label{createprocess}
-	\end{center}
-\end{figure*}
-
 %\begin{figure}[tb]
@@
 %\end{figure}
-
-\begin{figure}[tb]
-	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram_full.png}
-	\caption{Selecting the claim made by a new snippet}
-	\label{snipsavecrop}
-\end{figure}
 

### 2009-03-21 webapps/node/javascript/leftrightui.js

@@ -377,8 +377,8 @@ function makeAdder(title,type,verb,reverse,panel,obj,panelnum){
 					panelnum,"suggested topics",obj,callback);
 			}else{ // crappy suggestions for the moment
 				updateSuggestions(panel,
-					"http://localhost:8180/thinklink/node/search.js?type=claim&query="+encodeURIComponent(obj.text)+"&callback=?",
-					panelnum,"suggested claims",obj,callback);
+					"http://localhost:8180/thinklink/node/search.js?type="+type+"&query="+encodeURIComponent(obj.text)+"&callback=?",
+					panelnum,"suggested "+type+"s",obj,callback);
 			}
 		});
 	
@@ -464,7 +464,12 @@ function makeSuggestion(obj,panelnum,callback){
 			callback(obj.text);
 		});
 
-	var text = $("<span/>").css('font-size','13px').text(obj.text);
+	var text;
+	if(obj.type == "snippet"){
+		text = $("<span class='snippet-text'/>").text("\"..."+obj.text.substring(0,160)+"...\"");	
+	}else{
+		text = $("<span/>").css('font-size','13px').text(obj.text);
+	}
 	item.append(makeHBox([add,text],"linkbox"));
 	
 	return item;

### 2009-03-22 papers/uist_thinklink/thinklink.tex
More paper work + associated bug fixes

--- 2009-03-21 papers/uist_thinklink/thinklink.tex
@@
 
-\keywords{CSCW, sensemaking, web, browsers, collaboration, mind mapping}
-
 \classification{H5.2 [Information interfaces and presentation]:
@@
 
-\keywords{Sense-making, Annotation, Argumentation, Web}
+\keywords{CSCW, Sensemaking, Annotation, Argumentation, Web}
 
@@
 
+In this paper we present Think Link, a tool helps users discover when information they read conflicts with information on other web sites, and shows users the best sources that provide alternative points of view.
+When Think Link is used as a browser plugin it will highlight text that makes a disputed claim.
+If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by other users of Think Link (Figure~\ref{claimview}).
+The argument graph contains links to snippets of text on other web sites that express conflicting or supporting points of view.
+
 \begin{figure}[tb]
 	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/v2_popup.png}
+	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
+	\caption{Think Link highlights snippets that make disputed claims}
+	\label{highlight}
+	\end{center}
+\end{figure}
+
+Think Link relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.
+If a user is viewing a web page, they can identify disputed claims and useful evidence.
+Think Link will guide a user in finding existing claims that a snippet may be making and in connecting existing claims.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=5cm]{../screenshots/v2_popup_dim.png}
 	\caption{Click on a claim to investigate evidence for and against it}
@@
 
-In this paper we present Think Link, a tool helps users discover when information they read conflicts with information on other web sites, and shows users the best sources that provide alternative points of view.
-When Think Link is used as a browser plugin it will highlight text that makes a disputed claim.
-If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by other users of Think Link (Figure~\ref{claimview}).
-The argument graph contains links to snippets of text on other web sites that express conflicting or supporting points of view.
-
-Think Link relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.
-If a user is viewing a web page, they can identify disputed claims and useful evidence.
-Think Link will guide a user in finding existing claims that a snippet may be making and in connecting existing claims.
+\todo{Claim panel should have 'more' buttons}
 
@@
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
-	\caption{Hovering over a highlighted snippet shows a summary}
-	\label{highlight}
-	\end{center}
-\end{figure}
-
 Think Link is designed to be used in two different ways.
@@
 To emphasise the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/v2_panel.png}
+	\caption{A claim panel presents information for and against a claim}
+	\label{panel}
+	\end{center}
+\end{figure}
 
@@
 
+If a user has installed the Think Link browser extension then they can create a snippet from text on a web page by selecting the text and selecting either ``This is disputed'' or ``This is interesting'' from the context menu.
+A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted of the fact that a claim that that snippet is making or implying is disputed.
+A user selects ``This is interesting'' if they believe that the snippet contains useful information that would be useful to readers investigating a disputed claim.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/v2_snipmark.png}
+	\caption{Use the context menu to mark a new snippet}
+	\label{createprocess}
+	\end{center}
+\end{figure}
+
+Think Link does not require that a user associate a snippet with a snippet at the point at which they create it.
+Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets.
+One anticipated usage scenario for Think Link is an activist user who users a search engine to find a large number of snippets that make a clam that the user disagrees with.
+In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.
+
+Think Link provides three ways for a user to associate a claim with a snippet:
+
+\begin{description}
+\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Think Link will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}).
+A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates to'' link types.
+If Think Link does not suggest the right snippets then Think Link can guide the suggestions by entering keywords into the text box above the suggestion list.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/v2_sugsnippet.png}
+	\caption{Claim first: Pick unfiled snippets to attach to a claim}
+	\label{snipclaim}
+	\end{center}
+\end{figure}
+
+\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Think Link will show a list of all the snippets that they have marked but not yet associated with a claim or a snippet (Figure~\ref{sniptopic}).
+If the user selects an unfiled snippet then Think Link will suggest claims or topics that the user might want to associate with that snippet.
+As with the snippet suggested, a user can guide the suggestions by entering keywords.
+If the correct claim is not suggested then the user can create a new claim by typing it into the text box and clicking the ``add'' button.
+
 \begin{figure}[tb]
@@
 	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
-	\caption{Use topic suggestion to quickly file evidence snippets}
+	\caption{Snippet first: Pick a claim or topic for each unfiled snippet}
 	\label{sniptopic}
@@
 
-\subsection{Organizing the Argument Graph}
+\item[Immediate:] A user can select a claim for a snippet that they have just marked.
+When a user marks a snippet, Think Link will initially highlight it in blue to show the user that the snippet is not currently associated with a claim or topic and will not be shown to other users.
+If the user clicks on the highlighted snippet, then Think Link will bring up the same suggestion panel used in the ``snippet first'' method.
+\end{description}
 
-\todo{Talk about organizing stuff}
+When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim.
+It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to offer support for a particular claim.
+In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for.
+In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.
 
-\subsection{Creating new Snippets}
-\label{newsnippet}
+Think Link uses the Wikify!
+algorithm~\cite{Mihalcea} to suggest topics for snippets or claims.
+The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page.
+Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles.
+The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that a heavily linked to.
 
-\begin{figure*}[tb]
-	\begin{center}
-	\includegraphics[width=16cm]{../screenshots/newsnip_all.png}
-	\caption{Process for creating a new snippet}
-	\label{createprocess}
-	\end{center}
-\end{figure*}
+\todo{Mention about topic previewing}
 
-%\begin{figure}[tb]
-%	\includegraphics[width=8.5cm]{../screenshots/snipsave_full.png}
-%	\caption{The claim selection window allows one to identify the claim a snippet is making}
-%	\label{snipsavefull}
-%\end{figure}
+As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected.
+If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected.
+Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together.
 
-\begin{figure}[tb]
-	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram_full.png}
-	\caption{Selecting the claim made by a new snippet}
-	\label{snipsavecrop}
-\end{figure}
+\todo{Allow two claims to be marked as being identical}.
 
-There are several reasons a user may wish to add a snippet to Think Link.
-They may find the snippet useful and may want to refer to it again in the future; they may disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments; they may think the claim argues a point well and want to be able to use it to make an argument, or they may agree with the claim and want to provide easy access to evidence elsewhere that backs it up.
+Think Link uses the same suggestion system to allow users to connect claims to snippets, and to connect claims to other related claims.
 
-To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser tool bar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}).
-This is a similar approach to that taken clipping tools such as Google Notebook.
-
-Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making.
-To do this, Think Link presents the user with a ``claim selector'' window.
-This window contains a small version of the claim browser that the user can use to select the claim that the snippet is making.
-
-Since much of Think Link's utility comes from linking snippets together, it is important to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics.
-We designed the claim selection window to make it easier to pick out an existing claim than to create a new one.
-Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim.
-To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to.
-For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim.
-This is an intentionally different model to that used by ad-hoc tag-based systems such as Del.icio.us and Flickr.com.
-This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected.
-In practice, it is inevitable that duplicates claims and topics will sometimes be created.
-When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.
+\todo{BUG: don't have 'add' button for snippets}
 
@@
 
-\todo{Describe how one goes about marking disputed claims}.
-
-If a user has added the Think Link extension to their browser then it will highlight snippets that make disputed claims (Figure~\ref{highlight}). If
-
-an open database of contentious claims, and an interactive claim browser that allows one to explore the various snippe
-
-If a user has added the Think Link extension to their browser then it will highlight
-
-Think Link is a browser plugin that is designed to help users tell when the information that they read on the web is inaccurate or presents only one side of a contentious issue.
-As the user browses the web, Think Link
-
-% 
-% 
-% \subsection{The Mental Model}
-% 
-% \begin{figure}[tb]
-% 	\begin{center}
-% 	\includegraphics[width=7cm]{../screenshots/bookmark_icons2.png}
-% 	\caption{Icons used for Claims, Snippets, and Topics}
-% 	\label{bookmark_icons}
-% 	\end{center}
-% \end{figure}
-% 
-% Think Link users interact with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}): 	
-% 
-% \begin{itemize}
-% \item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false.
-For example ``Global warming is man made''.
-A claim may support or oppose other claims.
-Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
-% \item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim.
-Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
-% \item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about.
-For example ``Global Warming'', or ``Computer Science''.
-A claim can be about one or more topics, and a topic can have one or more more general topics.
-Topics are used to organize and disambiguate claims.
-For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''.
-Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
-A topic can itself by disambiguated by having a super-topic.
-% \end{itemize}
-% 
-% 
-% \subsection{Browsing factual claims}
-% \label{browseclaim}\label{claimbrowser}
-% 
-% \begin{figure}[tb]
-% 	\begin{center}
-% 	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
-% 	\caption{The claim browser visualizes the claim graph}
-% 	\label{claimbrowse_diagram}
-% 	\end{center}
-% \end{figure}
-% 
-% 
-% Claims and topics form a directed graph structure. A claim can have any number of claims that support or oppose it, and any number of claims that it supports or opposes.
-% A topic can have any number of more specific topics (e.g.
-``US Election 2008'' is more specific than ``US Elections'') and any number of more general topics.
-A topic can also have any number of claims about that topic.
-% 
-% When designing an interface to this structure, we were faced with two opposing constraints.
-We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree.
-Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place.
-Tree-based outliners such as OmniOutliner~\cite{omnioutliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.
-% 
-% After several design iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner.
-Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it.
-Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.
-% 
-% The placement of objects above and below is intended to emphasize the conventional hierarchical structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards.
-A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.
-% 
-% \begin{figure}[tb]
-% 	\begin{center}
-% 	\includegraphics[width=6cm]{../screenshots/claimbrowse_zoom.png}
-% 	\caption{Close up of a list of supporting claims}
-% 	\label{claimbrowse_zoom}
-% 	\end{center}
-% \end{figure}
-% 
-% Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states.
-When a new item is selected, it grows in size and moves to the center.
-Other items that were already on the screen move from their current locations to their new locations.
-Other objects appear and disappear by smoothly sliding into or out of view.
-% 
-% Users see a claim browser in three different places.
-The {\it organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}).
-The {\it popup browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}).
-The {\it claim selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).
-
-\subsection{Organizing the Claim Graph}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/claimbrowse.png}
-	\caption{The Claim Organizer contains two claim browsers}
-	\label{fig:claimbrowser}
-	\end{center}
-\end{figure}
-
-Like Wikipedia~\cite{wikipedia}, Think Link allows any user to improve the information in the claim graph.
-The claim graph is shared between all users and editable by anyone.
-Any user can add new snippets, create new claims, create new topics, or establish new relationships between these objects.
-One can think of Think Link as being rather like a wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.
-
-Think Link uses collaborative filtering~\cite{collective} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim.
-If a user finds a snippet or claim interesting then they can vote in favor of it by clicking on its icon, causing it to light up (Figure~\ref{bookmark_icons}).
-When Think Link lists claims or snippets, it will show first those that the user marked as interesting, and order the rest according to the number of other users who marked them as interesting.
-
-It is important to avoid political fights, where two competing sides delete claims, snippets, or connections that they disagree with.
-Similarly, it is important to avoid vandalism, where people abuse people with competing beliefs by adding abuse claims or snippets.
-While we do not have a perfect solution to this problem, our current approach is to treat deletion as a special case of collaborative filtering.
-If a user believes a claim, topic, snippet, or connection is junk then they can request that it be deleted by clicking on the ``delete'' button.
-This will hide the object for the user who request deletion and reduce the score of the object for other users.
-If enough people vote to delete the object then its score will eventually be low enough that it is not displayed to users unless they request to see junk objects.
-
-In a wiki, users edit and delete information produced by others, and history is used to revert abusive changes.
-Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects.
-The hope is that over time ratings should converge to a steady state and edit wars should be avoided.
-It would not be practical for a wiki to take this approach as wiki data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.
-
-Think Link uses the familiar drag and drop interface for establishing new connections.
-To establish a connection between two claims, one need simply drag one claim onto the other.
-The claim organizer window has two claim browsers, allowing a user to points from one browser onto points on the other (Figure~\ref{fig:claimbrowser}).
-
-\subsection{Why People Annotate}
-
-Tools like Think Link rely on user contributions in order to be useful.
-If no users are identifying factual claims on pages then other people who browse such pages will not see any claims identified.
-Similarly, if no other users are connecting claims together, then users will not see any supporting or opposing claims when they click on a highlighted snippet.
-
-Moreover, in order to become popular, a tool like Think Link needs to be useful even when very few people are using it.
-If a tool is only useful when it has a large community using it then it is unlikely that early adopters will stick with it enough for it to ever acquire a large community.
-
-Our user study participants identified several reasons why they would want to mark up factual claims in documents they found.
-The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found.
-One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments.
-The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.
-
-\subsection{Implementation}
-
-Think Link is implemented as three largely independent components:
-
-\begin{itemize}
-\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains the claim graph and provides an API that allows this data to be queried and modified
-\item {\bf A web UI}, written using Javascript that implements the claim browser
-\item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page.
-This script displays the web UI in an iframe to pick or investigate a claim.
-\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides tool bar and context-menu shortcuts.
-\end{itemize}
-
-These components are largely independent.
-One could use the page enhancement script on a web page without using the Firefox extension, by either manually including it on the page (e.g.
-to enhance your own blog) or by adding it using a proxy.
-Since the server API is public, one could write alternative tools that mark up web pages in different ways, or use the claim graph for different purposes.
-
-The source code to Think Link is publicly available under the Apache license.
+\todo{finish this section}
 

### 2009-03-23 papers/uist_thinklink/thinklink.tex
Now have a full draft

@@
 
-\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
-\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
-\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
+% \newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
+% \newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
+% \newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
+% \newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}
+
+\newcommand{\want}[1]{}
+\newcommand{\todo}[1]{}
+\newcommand{\idea}[1]{}
+\newcommand{\node}[1]{}
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
+	\includegraphics[width=5cm]{../screenshots/highlight_crop.png}
 	\caption{Think Link highlights snippets that make disputed claims}
@@
 Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}.
-IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1996}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas.
+IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas.
 While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue.
@@
 policy maker vs industrialist vs environmentalist).
-
-In attempt to unify the different argumentation tools being developed, several interchange formats have been proposed~\cite{Rahwan2007a,McGinnis2007} to allow different web argumentation tools to share descriptions of contentious issues.
 
@@
 Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags.
-Notable tagging systems include del.icio.us\footnote{http:\\del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.
+Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.
 
@@
 Some tagging and annotation tools also do clipping.
-Clipping tools such as Internet Scrapbook~\cite{Sugiura19998}, Hunter Gatherer~\cite{2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends.
+Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends.
 In many cases, a tagging or clipping system will also allow users who are looking at a tagged or clipped object to see the tags that other users have associated with it, or highlight the parts of a document that have been clipped.
@@
 
-\subsection{To discuss in the body}
-
-Paraphrases~\cite{Chklovski2005}. Suggested formal paraphrases~\cite{Blythe2004}.
-Importance of Lurkers~\cite{Takahashi2003}
-Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.
+% \subsection{To discuss in the body}
+% 
+% Paraphrases~\cite{Chklovski2005}. Suggested formal paraphrases~\cite{Blythe2004}.
+% Importance of Lurkers~\cite{Takahashi2003}
+% Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.
 
@@
 Think Link uses the Wikify!
-algorithm~\cite{Mihalcea} to suggest topics for snippets or claims.
+algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims.
 The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page.
@@
 
-Think Link consists of a browser extension a shared public database of contentious claims, and a web-based argument interface that allows one to explore and manipulate the claim graph.
-These three components are largely independent of each other and talk to each other using an open API that can also be used by other tools.
-Indeed the settings panel for the browser extension allows it to be pointed to alternative data stores or graphical interfaces.
+Think Link consists of a browser extension, a page annotation script, a shared public database of contentious claims, and a web-based argument interface that allows one to explore and manipulate the claim graph.
+These four components are largely independent of each other and talk to each other using an open API that can also be used by other tools.
+Indeed the settings panel for the browser extension allows a user to tell it to bind to alternative versions of the other modules.
 
-As a user browses the web, the browser extension consults the database to identify snippets that other users have previously marked as making disputed claims.
-Any such snippets are highlighted in red to show the user that there is an alternative viewpoint that they might want to investigate.
-If a user clicks on a highlighted snippet then the browser extension opens the web based argument interface, showing the user the evidence that users have collected on both sides of the issue.
+The page annotation script is a javascript file that can be included into any HTML page.
+When it is run on a page it sends the page URL to the server, asking it to send back information about any contentious snippets on that page.
+If any such snippets are found, the page modification script highlights them in red.
+If the user clicks on a highlighted snippet then it shows an iframe containing a visualisation from whatever visualization server it has been configured to use.
 
-\todo{finish this section}
+The only purpose of the browser extension is to insert the page modification script onto every page that the user loads.
+The browser extension is not the only way that one can access Think Link highlights.
+One can get the same effect by browsing through a proxy (like WBI~\cite{Barrett1997}), or if the owner of a web site included the page annotation script themselves.
+
+Think Link's annotation system has some privacy issues.
+Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page.
+Privacy issues are reduced by the fact that the requests contain no cookies or other identifying information, and can be cached by a third-party proxy if desired; however issues still remain.
+In future work hope to reduce these privacy issues.
+One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.
+
+The protocol used by the Think Link server is an open REST API that other tools are free to use.
+We are also considering supporting one or more of the several argumentation interchange formats that have been proposed ~\cite{Rahwan2007a,McGinnis2007}.
 
@@
 
-We performed two qualitative ``think aloud'' user studies to guide the development of Think Link.
+We performed two qualitative ``think aloud'' user studies.
+The aim of these studies was to inform the development of Think Link.
+The studies were not intended to validate the design of Think Link as being correct.
+Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different points.
+To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for.
 
-The aim of the first study was to see how users normally browse the web and how they might go about using Think Link to identify snippets in the pages they browse.
-The aim of the second study was to evaluate changes made to the interface as a result of the first study and see how people react to browsing pages that have interesting claims highlighted.
+The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph.
+The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page.
+We present the results of the two studies together.
 
@@
 
+\todo{This was a bad recruiting strategy. We should have recruited people that fitted one of our two personas and then set them tasks that fitted our vision for that persona.}
+
 Study sessions took approximately 45 minutes.
-Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link plugin.
-We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they found interesting and connect those claims to the existing claim graph.
+Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension.
+We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph.
 For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.
@@
 We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
-The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw.
-The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with.
-Participants were shown an interface that is largely identical to that described earlier in this paper.
+The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case).
+The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).
+
+Participants were shown the prototype interface shown in Figure~\ref{secondbrowser}.
+This is similar to the interface described earlier in this paper, but uses drag and drop to make connections, rather than a suggestion system.
 
@@
 
-\subsubsection{Usability}
-
-Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version.
-None of these problems re-occurred during the second study.
-We discuss some of these changes in the sections below.
-
 Most participants in the first study, and all participants in the second study were able to use the tool competently.
@@
 Participants said they found the tool ``very intuitive''.
-
-\subsubsection{Creating a Snippet}
-
-Users would often encounter a snippet that could be interpreted as making several interesting claims, and were unsure about what to do in such circumstances.
-Some users would deal with this by writing a compound claim like ``Global Warming will cause X and Y'' while other users would create several snippets for the same text, making different claims.
-Users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.
-
-One special case of this problem was that several users wanted to mark up a table as a snippet.
-A table can usually be considered to be making several interesting claims and users were often confused about what they should say the table claimed.
-Our current guidance is that one should mark up a table as making the most interesting claims that that table makes --- those that support or oppose claims made elsewhere.
-In other cases, a user wanted to mark up an image as a snippet.
-While Think Link does not currently support this, it might make sense to allow this if an interesting claim can be inferred from the image.
-
-Some users expressed an interest in marking up a snippet as a primary source rather than a claim.
-For example they might find the text of an important speech or an Olympic results table.
-Several expressed a desire to have a new class of object that was neither a topic nor a claim, but instead just ``interesting information relevant to this topic''.
-
-Many users would consistently mark the first paragraph of an article as a snippet.
-This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.
 
@@
 	\includegraphics[width=8.5cm]{../screenshots/oldsnipcreate_diagram.png}
-	\caption{Initial Prototype Snippet Creation Dialog}
+	\caption{First Prototype Snippet Creation Dialog}
 	\label{oldsnippetbox}
@@
 
-In the initial interface we used a simplified snippet creation window (Figure~\ref{oldsnippetbox}) that was intended to make the process of snippet creation very lightweight.
-This window contained two text boxes.
-The first of these boxes was for the topic (e.g.
-``Global Warming'') and the second of the boxes was for the claim (e.g.
-``Global Warming is Man Made'').
-Both of these boxes used an auto-complete drop-down list to suggest appropriate existing topics or snippets as the user typed,
-biasing towards topics that were recent or hot.
-The auto-complete list would show either when the user started typing, or when the user clicked the drop down button.
-Selecting a claim would auto-populate the topic.
-Selecting a topic would constrain the claims that were suggested to be within that topic.
+\begin{figure}[t]
+\begin{center}
+	\includegraphics[width=5cm]{../screenshots/newsnip_browseopen.png}
+	\caption{Second Prototype Snippet Creation Dialog}
+	\label{secondsnippetbox}
+\end{center}
+\end{figure}
 
-We found that participants using this initial interface felt disorientated by the fact that the interface for creating snippets was different to the interface used for visualizing them.
-Participants would often confuse claims and topics, either entering a claim in the topic box, or a topic in the claim box.
-Participants would also frequently create new points and topics when appropriate points and topics already existed in the claim graph, even when the suggestion list was drawing their attention to a topic or claim that would have been appropriate.
+The prototype interfaces required that a user enter a claim for a snippet at the point at which they created the snippet.
+When the user marked a snippet, Think Link would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype).
+There turned out to be several problems with requiring that a user select a claim at the point at which they marked a snippet:
 
-For the second study, we used the snippet creation interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph.
-We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics.
-We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.
+Users would often encounter a snippet that could be interpreted as making several interesting claims.
+Users got confused by the need to pick only one claim.
+Some users dealt with this by writing a compound claim such as ``Global warming will cause X and Y'', while other users would mark several overlapping snippets making different claims.
+In the final interface one can associate a snippet with several claims.
+
+Some users wanted to associate a snippet with a topic but without associating it with a specific claim.
+For example, they might find the text of an important speech, or the results of a sporting event.
+While it is possible that they might want to use this as evidence for a claim in the future, they didn't want to have to decide what the claim was immediately.
+In the final interface one can associate a snippet with a topic rather than a claim.
+
+Some users seemed to be deterred from marking interesting snippets by the mental effort required to choose an appropriate claim.
+In several cases, we saw a user pause to decide whether an interesting snippet was worth marking up.
+Similarly, some users seemed to find it difficult to decide what the right claim to use for a snippet was, since they had not yet decided how they wanted to structure their argument, or even if this was a topic they wanted to argue about.
+The final interface does not require a user to associate a snippet with a claim at the time they create the snippet.
+Instead a user can mark snippets with minimal effort and then later search through their snippets to find evidence for particular claims.
 
@@
 For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information?
+In the final interface, users can choose how specific to make their claims after they have gathered a large number of snippets and know what information is repeated between sources.
 
-Several users also expressed an interest in being able to use the text of the snippet they selected as the text of its claim, particularly for short snippets.
-We intentionally made this a little difficult to do in an attempt to encourage users to find existing claims that are appropriate, however this may have been a mistake as it also increases the amount of effort required to create a snippet.
+Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they they could make the dialog go away.
+Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet.
+The final interface avoids this problem by allowing a used to delay the association of a claim for a snippet until they know what useful claim they want to use that snippet as evidence for.
+
+\todo{Need to do some kind of evaluation to show that the new interface solves these problems}
+
+\subsubsection{Choosing what to mark as a snipet}
+
+Many users would consistently mark the first paragraph of an article as a snippet.
+This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.
+
+Several users wanted to mark up a table or an image as a snippet.
+This is valid behaviour -- a table or image is often useful evidence for a claim; however it is not currently supported by Think Link.
+In future versions of Think Link we intend to support this behaviour.
 
@@
 For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''.
-Our current advice in such circumstances is to use topics to group claims that are related.
-For example these claims could all be in a topic called ``America and the Kyoto Protocol''.
-Participants seemed comfortable with the idea of relating claims in this way when we pointed it out to them, but most participants needed to be told that this was a strategy they could use.
+In the first prototypes, a user needed to chose between ``supports/opposes'' when connecting two claims together (follwing gIBIS~\cite{Conklin1987a}).
+In the final interface we introduced a ``related-to'' link type to allow users to connect claims that they thought should be related but which didn't confirm to a simple pro/con relationship.
 
@@
 	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
-	\caption{Initial Prototype Claim Browser}
+	\caption{First Prototype Claim Browser}
 	\label{oldbrowser}
@@
 
-\section{Limitations and Future Work}
+\begin{figure}[tb]
+\begin{center}
+	\includegraphics[width=5cm]{../screenshots/claimbrowse.png}
+	\caption{Second Prototype Claim Browser}
+	\label{secondbrowser}
+\end{center}
+\end{figure}
 
-There are a number of issues that a widely released tool would need to address.
-Firstly, our current implementation has privacy issues.
-Every time one navigates to a web page, the plugin contacts our server and gives it the current URL so that the server can check if there are snippets on that page.
-These requests are anonymous, cacheable, and not logged, but it is still likely that some people would object to this information being given to an external server.
+The first two versions of Think Link used a drag-and-drop interface to allow a user to create links between claims.
+In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree.
+In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphore, providing two identical browser windows that a user could drag and drop claims between.
+In both cases, we found that users would often not intially realise they could use drag and drop to arganize claims, even when we added a prominant information message at the top of the display (Figure~\ref{secondbrowser}).
+We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections.
+In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.
 
-At present, all claims have to be marked up by users who must not only identify the correct section of text to highlight, but also use a browsing interface to find the interesting claim that is being made.
-It would be interesting to see if natural language processing techniques could be used to either simplify the process of marking snippets, or even to detect snippets that make known claims without human intervention.
+\section{Future Work}
+
+At present Think Link relies on users to mark up snippets and connect them to claims.
+In the future we plan to explore using natural language and machine learning techniques to assist in this process.
+Our plan is to allow a user to request that Think Link present them with potential web snippets that make a claim that they disagree with, and then quickly select which of these should be highlighted as being contentious.
 
@@
 
-We have introduced the concept of browsing the web of factual claims using Think Link.
+We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on either side of the issue.
 Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors.
-It allows users to identify contentious claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.
+It allows users to identify disputed claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.
 
-On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using an ``append only, collaborative filtering'' model to allow users to collaborate together to structure claims into an argument graph.
+On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.
 
@@
 
-We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link.
-Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.
+Acknowledgements ommitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.
 

### 2009-03-23 papers/uist_thinklink/thinklink.tex
Spell check

@@
 \usepackage{color}
-% \usepackage[pdftex]{hyperref}
-% \hypersetup{%
-% pdftitle={Browsing the Web of Factual Claims},
-% pdfauthor={Beth Trushkowsky and Rob Ennals},
-% pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
-% bookmarksnumbered,
-% pdfstartview={FitH},
-% colorlinks,
-% citecolor=black,
-% filecolor=black,
-% linkcolor=black,
-% urlcolor=black,
-% breaklinks=true,
-% }
 
@@
 \parbox[t]{9cm}{\centering
-	     {\em Author Name removed for blind review}\\
+	     {\em Author names removed for blind review}\\
 }
-\parbox[t]{9cm}{\centering
-	     {\em Author Name removed for blind review}}
 }
@@
 As the user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites.
-If a user clicks on such a disputed claim then Think Link will show tem an argument graph showing the best evidence for and against the claim being true, as determined by other users of Think Link.
+If a user clicks on such a disputed claim then Think Link will show them an argument graph showing the best evidence for and against the claim being true, as determined by other users of Think Link.
 
@@
 If a user is to form a rounded opinion about a topic then they will need to either stick to sources that they trust or spend time looking for evidence on other web sites that supports or opposes what they read.
-Even if a user tries hard to research every topic they read, they can still get caught out by beliefs that they had not realised were disputed.
+Even if a user tries hard to research every topic they read, they can still get caught out by beliefs that they had not realized were disputed.
 
@@
 
-Think Link is designed to cator to two distinct groups of people.
+Think Link is designed to cater to two distinct groups of people.
 Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them.
@@
 
-The design of Think Link was guided by two user studies, in which we observed the behaviour of users who fitted the roles of Activist or Sceptical Reader.
+The design of Think Link was guided by two user studies, in which we observed the behavior of users who fitted the roles of Activist or Sceptical Reader.
 
-\todo{Talk about automatically including all arguments from snopes}.
+\todo{Talk about automatically including all arguments from Snopes}.
 
@@
 While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue.
-Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.
+Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2006} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.
 
@@
 
-When chosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use.
+When choosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use.
 For Think Link, we have tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model.
@@
 If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is.
-If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evedience for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).
+If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).
 
-Since the purpose of a highlight is to alert the user to claims that they had not realised were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious.
+Since the purpose of a highlight is to alert the user to claims that they had not realized were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious.
 A user can click the ``don't highlight this claim again'' button to tell Think Link that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.
@@
 If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right.
-To emphasise the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
+To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
 
@@
 The panel for a claim lists evidence that will help a user decide whether the claim is true.
-Evidence is categorised as either supporting, opposing, or being related-to the claim.
+Evidence is categorized as either supporting, opposing, or being related-to the claim.
 The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument.
@@
 If any such snippets are found, the page modification script highlights them in red.
-If the user clicks on a highlighted snippet then it shows an iframe containing a visualisation from whatever visualization server it has been configured to use.
+If the user clicks on a highlighted snippet then it shows an iframe containing a visualization from whatever visualization server it has been configured to use.
 
@@
 
-\subsubsection{Choosing what to mark as a snipet}
+\subsubsection{Choosing what to mark as a snippet}
 
@@
 Several users wanted to mark up a table or an image as a snippet.
-This is valid behaviour -- a table or image is often useful evidence for a claim; however it is not currently supported by Think Link.
-In future versions of Think Link we intend to support this behaviour.
+This is valid behavior -- a table or image is often useful evidence for a claim; however it is not currently supported by Think Link.
+In future versions of Think Link we intend to support this behavior.
 
@@
 For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''.
-In the first prototypes, a user needed to chose between ``supports/opposes'' when connecting two claims together (follwing gIBIS~\cite{Conklin1987a}).
+In the first prototypes, a user needed to chose between ``supports/opposes'' when connecting two claims together (following gIBIS~\cite{Conklin1987a}).
 In the final interface we introduced a ``related-to'' link type to allow users to connect claims that they thought should be related but which didn't confirm to a simple pro/con relationship.
@@
 In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree.
-In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphore, providing two identical browser windows that a user could drag and drop claims between.
-In both cases, we found that users would often not intially realise they could use drag and drop to arganize claims, even when we added a prominant information message at the top of the display (Figure~\ref{secondbrowser}).
+In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between.
+In both cases, we found that users would often not intially realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}).
 We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections.
@@
 
-Acknowledgements ommitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.
+Acknowledgements omitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.
 

### 2009-03-24 papers/uist_thinklink/thinklink.tex
Tidied up stuff on argumentation and improved the intro and abstract

@@
 \abstract
-We present Think Link, a browser extension that aims to let users see when the information they are reading presents only one side of a disputed issue.
-As the user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites.
-If a user clicks on such a disputed claim then Think Link will show them an argument graph showing the best evidence for and against the claim being true, as determined by other users of Think Link.
+Think Link is a tool that helps a user know when information they read on a web page is disputed on presents only one side of a contentious issue.
+As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites.
+If a user clicks on a highlighted snippet then Think Link will show them an argument graph showing the best evidence for and against the claim being true.
+
+All information in Think Link is provided by users.
+Think Link is designed to cator to two usage scenarios.
+Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with.
+Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.
 
@@
 
-The web provides users with a huge number of pages that they can read, but extracting accurate and balanced information from these pages can be difficult.
-Not everything on the web is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and many web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
-If a user is to form a rounded opinion about a topic then they will need to either stick to sources that they trust or spend time looking for evidence on other web sites that supports or opposes what they read.
-Even if a user tries hard to research every topic they read, they can still get caught out by beliefs that they had not realized were disputed.
+The web contains a huge amount of information, but but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
+If a user is to gain a broad understanding ofa topic then they will need to either stick to sources that they trust or spend time looking for information on other web sites that conflicts with what they have read.
+Even if a user tries hard to research every topic they read, they can still get caught out by claims that they had not realized were disputed.
 
-In this paper we present Think Link, a tool helps users discover when information they read conflicts with information on other web sites, and shows users the best sources that provide alternative points of view.
+In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources that provide different points of view.
 When Think Link is used as a browser plugin it will highlight text that makes a disputed claim.
-If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by other users of Think Link (Figure~\ref{claimview}).
-The argument graph contains links to snippets of text on other web sites that express conflicting or supporting points of view.
+If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by the voting of other Think Link users (Figure~\ref{claimview}).
 
@@
 
-Think Link relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.
-If a user is viewing a web page, they can identify disputed claims and useful evidence.
-Think Link will guide a user in finding existing claims that a snippet may be making and in connecting existing claims.
+Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
+Think Link is designed to cater to two distinct groups of people.
+Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them.
+Sceptical readers install Think Link as a browser plugin so that they can see when things they read are disputed and find other links that present other points of view.
+A reader may be an activist for one issue and a sceptical reader for others.
 
@@
 
-Think Link is designed to cater to two distinct groups of people.
-Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them.
-Sceptical readers install Think Link as a browser plugin so that they can see when things they read and disputed and find other links that present other points of view.
-A reader may of course be an activist for one issue and a sceptical reader for others.
+The design of Think Link was guided by two user studies, in which we observed the behavior of users as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.
 
-The design of Think Link was guided by two user studies, in which we observed the behavior of users who fitted the roles of Activist or Sceptical Reader.
-
-\todo{Talk about automatically including all arguments from Snopes}.
+\todo{Talk about automatically including all arguments from Snopes}
+\todo{I think we need to do some kind of evaluation of the new interface, even if it is just showing it to some people, or having people in the lab try it.}
+\todo{Need figures saying how efficient it is for an activist user to mark up a topic}
 
@@
 Think Link builds on work in several different areas.
-The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}; the idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by Wiki-Trust~\cite{Adler2008}; the model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}; and the idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
+The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.
+The idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
+The model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}.
+The idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
 
-What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of leading users towards information that conflicts with that which they read.
+What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of showing users when the information they read conflicts with information from other sources.
 
-\subsection{Argumentation}
+\subsection{Argumentation and Design Rationale}
 
 Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}.
-IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas.
+IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model arguments around an issue as a graph of connected ideas.
 While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue.
@@
 
-Cohere is perhaps the tool most similar to Think Link.
+Prior IBIS tools have been intended for conflict modelling and resolution: users build up a complex graph modelling an issue and then use this graph to decide what to do.
+By contrast Think Link uses an IBIS graph for conflict discovery and evidence identification.
+In a tool like gIBIS a user is encouraged to break down their argument into as much detail as possible and encouraged to use the graph itself to reach a decision.
+By contrast, in Think Link a user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form their opinion primarily by reading the articles that have been linked as evidence.
+In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit the expected usage for other IBIS tools.
+
+Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use.
+We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
+
+Cohere~\cite{Shum2008} is perhaps the IBIS tool most similar to Think Link.
 Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from pages that one browses.
@@
 By contrast, in Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument.
+More generally,
 
-ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly document with logical triples (subject, verb, object) describing interesting claims that are being made in the document.
-This semantic information can be used to connect claims in different documents and see when a logical claim in one document contradicts another.
-Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.
+More generally, a key way Think Link differs from Cohere is that it separates the creation of claims from their association with snippets.
+A user can mark a snippet without yet being sure what claims it should be linked to, or can mark a claim without knowing what snippets other users will associate with it.
 
-Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklin1987a}, allowing a claim to support, oppose, or be related to another claim.
-Cohere~\cite{Shum2008} extends this by allowing one to new link types marked with pro,con,or neutral polarity Toulmin~\cite{toulmin1958} proposes a more complex graph structure, that expresses warrants, data, qualifiers, and reservations.
-Verheij~\cite{Verheij1999} uses the Toulmin model to create an argumentation tool for lawyers.
-More complicated models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence, where it is necessary to be more precise about the structure of an argument.
+Think Link uses a simple IBIS-style graph structure in which claims support, oppose, or relate-to other claims.
+Several alternative graph structures have been proposed for describing arguments and design rationale.
+WinWin~\cite{Boehm2006} models the different stakeholders and their different motives.
+The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions.
+QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions.
+More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.
+
+When choosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use.
+For Think Link, we tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model.
+The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.
 
@@
 policy maker vs industrialist vs environmentalist).
-
-Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use.
-We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
-We do not expect users to use Think Link to create a detailed model of an argument and use this to reach consensus.
-Instead, our aim is that a user should use Think Link to discover when things they read are disputed, and easily find evidence for the other side.
-\todo{Say more about this}.
-
-When choosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use.
-For Think Link, we have tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model.
-The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.
-
-% \subsection{Open Hypermedia}
-% 
-% 
-% \todo{Talk about other hypertext systems - mention arguments integrated into documents an old idea and talk about open hypermedias}
-
-% TRELLIS
-% 
-%  gIBIS~\cite{Conklin1987} and other IBIS~\cite{Rittel1973} such as ZEN
-% 
-% Cohere~\cite{Shum2008} is probably the tool most similar
-% 
-% 
-% 
-% Cohere~\cite{Shum2008}.
-Compendium~\cite{Selvin2001}.
-Cope it~\cite{Karacapilidis2001}.
-AIF~\cite{McGinnis2007} and ArgDF~\cite{Rahwan2007}.
-IBIS~\cite{Rittel1973}.
-gIBIS~\cite{Conklin1987}.
-IBIS problems~\cite{Isenmann1997}.
-ClaimSpotter~\cite{Sereno2005,Sereno2004}.
-ClaiMaker~\cite{Uren2003}.
-Video Annotation~\cite{Diakopoulos2008}.
-Collabatorium~\cite{Klein2007}, for Global Warming~\cite{Malone2007}.
-Lawyer argument model~\cite{Verheij1999}.
-Toulmin model~\cite{Toulmin1958}.
-Zeno~\cite{Gordon1997}.
-Discoursium~\cite{Yetim2007}.
-% Entity Workspace~\cite{Billman2007}. 
-% Mess Maps and Resolution Mapping~\cite{Horn2007}.
-% TRELLIS~\cite{Chklovski2005}.  
-% People should define own link types~\cite{Wang1998}.
-% 
-% Hypertext systems such as Notecards~\cite{Halasz1988}.
 
@@
 Several authors have investigated ways to make Wikipedia\footnote{http://wikipedia.org} more trustworthy.
-WikiTrust~\cite{Adler2008} highlights passages on wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors.
+WikiTrust~\cite{Adler2008a} highlights passages on wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors.
 Wiki Dashboard~\cite{Kittur2008} presents the reader of a Wikipedia article with a visualization that shows them how it has been edited in the past and lets them see graphically how contentious the topic is.
@@
 
-\subsection{Annotating, Tagging, and Clipping}
+\subsection{Annotating, Tagging, Clipping, and Open Hypermedia}
 
@@
 
-Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001}, CritLink~\cite{Yee2002},
+Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004} allow users to highlight sections of text on a page.
+Annotation systems often also do clipping.
+Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends.
+In some cases, other users who see a web page an see text highlighted where other users have clipped it.
 
-Some tagging and annotation tools also do clipping.
-Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends.
-In many cases, a tagging or clipping system will also allow users who are looking at a tagged or clipped object to see the tags that other users have associated with it, or highlight the parts of a document that have been clipped.
+ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly document with logical triples (subject, verb, object) describing interesting claims that are being made in the document.
+This semantic information can be used to connect claims in different documents and see when a logical claim in one document contradicts another.
+Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.
 
-Several tools allow users to annotate content that is considered to controversial.
 Videolyzer~\cite{Diakopoulos2008} allows users to annotate and comment on political videos with accompanying textual transcriptions.
@@
 Comments can include references to external sources that back up the argument being made.
+
 SpinSpotter\footnote{http://spinspotter.com} allows a user to highlight snippets of text that contain spin or bias and either describe why the text is biased, or rewrite the text in an unbiased way.
@@
 
-% Tagging~\cite{Marlow2006}. Tagomizer~\cite{Park2007}. Reasons for choices of tags~\cite{Sen2006}. Tagging Roles~\cite{Muller2008}. 
-% 
-% SpinSpotter\footnote{http://spinspotter.com}. ClipMarks\footnote{http://clipmarks.com}, Diigo~\footnote{http://diigo.com}, Stickis\footnote{http://stickis.com}.
-% 
-% How to Personalize the Web~\cite{Barrett1997}.
-
-% \subsection{Clipping}
-% 
-% ScratchPad~\cite{Gotz2007}. Internet Scrapbook~\cite{Sugiura1998}. Reverse Linking~\cite{Yesilada2007}. Hunter Gatherer~\cite{2002}. Dontcheva~\cite{Dontcheva2007a}.
-
 % \subsection{Semantic Web}
@@
 % Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.
-
-%\subsection{Automated Reasoning}
-%
-%Case-Based reasoning
-%Sensemaking
-
-%\subsection{Argumentation Graphs}
-%Argumentation graphs express positions and arguments in a formal graph model as nodes and edges, respectively, and are typically used to make a decision or draw a conclusion about some issue.
-One example implementation is the {\it Zeno} argumentation framework~\cite{zeno}, designed for collaborative use in mediation systems to debate the quality of alternative solutions for a problem.
-In their object model of argumentation elements, based on Rittel's IBIS model~\cite{ibis}, example nodes include pro/con arguments, positions, preferences, comments, and decisions.
-Importantly, arguments are connected via {\it consequent} and {\it antecedent} edges, which are used to inform {\it choices}.
-The decision-making power of the argumentation graph follows from the traversal of argument relationships to enhance the depth and breadth of understanding about an issue.
-Our application similarly links claims as {\it supporting} and {\it opposing} other claims to allow users to develop a cohesive understanding of arguments.
-%
-%Traditional argumentation graphs are designed to solve a specific, isolated issue.
-Our application supports an ever-expanding set of topics, and arguments can form links between multiple topics.
-Users can consult the web of ideas directly to form an opinion about a particular issue, but they can also browse for new issues to explore.
-Opinions or decisions in our model don't have to be static: as the topic is expanded with more supporting and opposing evidence, users may alter previous viewpoints.
-Another advantage of our model is that the ability to explore claims' source-document evidence is built right into the navigation.
-Looking at an argument shows both its related argument as well as its supporting {\it snippets}, allowing the user to explore the evidence for himself.
 
@@
 
-\todo{Allow two claims to be marked as being identical}.
+\todo{Allow two claims to be marked as being identical.}
 

### 2009-03-27 papers/uist_thinklink/thinklink_changes_beth.tex
Starting to implement Mayur-suggested changes. Distinguishing more clearly between topic and claim. Adding icons to headers.

--- 2009-03-24 papers/uist_thinklink/thinklink.tex
@@
 % --- Copyright notice ---
-\conferenceinfo{UIST'09}{October 4-7, 2008, Victoria, BC, Canada}
+\conferenceinfo{UIST'09}{October 4-7, 2009, Victoria, BC, Canada}  % beth: conf info year
 \CopyrightYear{2009}
@@
 \abstract
-Think Link is a tool that helps a user know when information they read on a web page is disputed on presents only one side of a contentious issue.
+Think Link is a tool that helps a user know when information they read on a web page is disputed or presents only one side of a contentious issue. % beth: typo
 As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. 
-If a user clicks on a highlighted snippet then Think Link will show them an argument graph showing the best evidence for and against the claim being true.
+If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against that snippet's claim. % beth: word changes
 
-All information in Think Link is provided by users.
-Think Link is designed to cator to two usage scenarios.
-Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with.
-Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.
+Users provide all Think Link's information: they highlight new snippets, and create and relate claims % beth: reworded, added details 
+Think Link is designed to cater to two primary usage scenarios. % beth: typo, insert 'primary' 
+Activists who care strongly about a particular issue can combine Think Link with a search engine to find and mark where web sites make statements that they disagree with.  % beth: word changes
+Skeptical readers can install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints. % beth: word changes
 
@@
 
-The web contains a huge amount of information, but but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
-If a user is to gain a broad understanding ofa topic then they will need to either stick to sources that they trust or spend time looking for information on other web sites that conflicts with what they have read.
-Even if a user tries hard to research every topic they read, they can still get caught out by claims that they had not realized were disputed.
+A huge amount of information is available on the web, but some websites have inaccurate information~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004}, and some present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
+% beth: reworded
+If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust have full information, or spend time searching for information on other web sites that conflicts with what they have read.
+% beth: reworded
+Even if a user researches every topic they read, they may not look for contradictory evidence for claims they had not realized were disputed. % beth: reworded, but still awkward
 
-In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources that provide different points of view.
-When Think Link is used as a browser plugin it will highlight text that makes a disputed claim.
-If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by the voting of other Think Link users (Figure~\ref{claimview}).
+In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources with different points of view.
+% beth: reworded
+When Think Link is used as a browser plugin, it will highlight snippets of text that make disputed claims.  % beth: added 'snippets'
+If a user clicks on such a highlighted snippet, Think Link presents an argument graph that shows the best evidence for and against the snippet's claim.  % beth: shortened, reworded
+The best evidence is judged by votes from other Think Link users (Figure~\ref{claimview}).  % beth: new sentence, reworded
 
@@
 Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
-Think Link is designed to cater to two distinct groups of people.
-Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them.
-Sceptical readers install Think Link as a browser plugin so that they can see when things they read are disputed and find other links that present other points of view.
-A reader may be an activist for one issue and a sceptical reader for others.
+Think Link is designed to cater to two primary usage scenarios. % beth: insert 'primary' 
+Activists who care strongly about a particular issue can combine Think Link with a search engine to find and mark where web sites make statements that they disagree with.  % beth: word changes
+Skeptical readers can install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints. % beth: word changes
+A reader may be an activist for one issue and a skeptical reader for others.
 
@@
 
-The design of Think Link was guided by two user studies, in which we observed the behavior of users as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.
+The design of Think Link was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for the Activist and Skeptical Reader.
+% beth: typos, reworded
 
@@
 Think Link builds on work in several different areas. 
-The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.
-The idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
-The model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}.
-The idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
+The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.  % beth: typo
+The idea of highlighting potentially untrustworthy information was previously applied to Wikipedia by WikiTrust~\cite{Adler2008a}.   % beth: reworded
+Tagging systems~\cite{Marlow2006} influenced Think Link's model of using a community to collect and filter information from a range of sources. % beth: reworded
+Gathering a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.  % beth: reworded
 
-What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of showing users when the information they read conflicts with information from other sources.
+Think Link is interesting because it combines ideas from these different domains to create a collaborative infrastructure for connecting conflicting information on the web.
+% beth: big rewording, not sure if you like it...
 
@@
 
-Prior IBIS tools have been intended for conflict modelling and resolution: users build up a complex graph modelling an issue and then use this graph to decide what to do.
-By contrast Think Link uses an IBIS graph for conflict discovery and evidence identification.
-In a tool like gIBIS a user is encouraged to break down their argument into as much detail as possible and encouraged to use the graph itself to reach a decision.
-By contrast, in Think Link a user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form their opinion primarily by reading the articles that have been linked as evidence.
-In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit the expected usage for other IBIS tools.
+Prior IBIS tools have been intended for conflict modeling and resolution: users build a complex graph modeling an issue and then use this graph to make a decision.  % beth: typos, word changes
+By contrast, Think Link uses an IBIS graph for conflict discovery and evidence identification.  % beth: comma
+In a tool like gIBIS, a user is encouraged to break down their argument into as much detail as possible and to use the graph itself to reach a decision.  % beth: comma, removed word
+By contrast, in Think Link a user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim; the user is expected to form their opinion primarily by reading the articles that have been linked as evidence.
+% beth: , and->semicolon
+In Think Link it is acceptable for a claim to be not linked to any other claims or topics, but be associated with many snippets --- this would not fit the expected usage for other IBIS tools.
+% beth: reworded
 
-Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use.
-We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
+Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use.  % beth: what issues?? say a few!
+We believe that while the problems they observe are important when an IBIS tool is being used for conflict modeling and resolution, they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
+% beth: comma
 
-Cohere~\cite{Shum2008} is perhaps the IBIS tool most similar to Think Link.
-Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from pages that one browses.
-While Cohere and Think Link both connect an argument graph to the web, they do so in very different ways.
-In Cohere, a user attaches a web snippet to their idea in order to use it as evidence.
-By contrast, in Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument.
-More generally,
+Cohere~\cite{Shum2008} is the IBIS tool most similar to Think Link.  % beth: removed word
+Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from web pages.
+% beth: rmeoved words
+While Cohere and Think Link both connect an argument graph to the web, they do so in very different ways. In Cohere, a user attaches a web snippet to their idea in order to use it as evidence. 
+In Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument.
+% beth: hmmm...
+think link really does both use cases
 
-More generally, a key way Think Link differs from Cohere is that it separates the creation of claims from their association with snippets.
+More generally, Think Link's key difference from Cohere is that it separates the creation of claims from their association with snippets.  % beth: reworded
 A user can mark a snippet without yet being sure what claims it should be linked to, or can mark a claim without knowing what snippets other users will associate with it.
@@
 
-When choosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use.
-For Think Link, we tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model.
-The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.
+When choosing an argumentation structure, there is an inherent trade-off between accurately modeling the structure of an argument and making the tool easy to use.  % beth: typo
+For Think Link, we tried to minimize the model complexity, and thus adopted a simple pro/con/netural linking model.  % beth: reworded
+The goal is to show a user what sources they should look at when forming an argument for or against a claim, rather than to present the detailed logical structure of an argument.
+% beth: big rewording
 
@@
 If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. 
-Snopes is a database of urban legends that the site owners have investigated to determine whether they are true or not.
+Snopes is a database of urban legends that the site owners have investigated to determine whether they are true.  % beth: removed words
+Think Link's database automatically imports all contentious claims identified by Snopes. % beth: moved sentence up
 FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.
-Think Link's database automatically imports all contentious claims identified by Snopes.
 
@@
 Several authors have investigated ways to make Wikipedia\footnote{http://wikipedia.org} more trustworthy.
-WikiTrust~\cite{Adler2008a} highlights passages on wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors.
+WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors.
 Wiki Dashboard~\cite{Kittur2008} presents the reader of a Wikipedia article with a visualization that shows them how it has been edited in the past and lets them see graphically how contentious the topic is.
@@
 TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages.
-ScentHighlights~\cite{Chi2005a} highlights snippets of text on a web page that are related to topics that the user has said that they are intersted in.
+ScentHighlights~\cite{Chi2005a} highlights snippets of text on a web page that are related to topics that the user has said that they are interested in.  % beth: typo
 Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
@@
 Think Link is designed to be used in two different ways. 
-Sceptical readers browse the web and wish to be alerted when information they read conflicts with information found on other web sites.
-Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of sceptical readers to claims that they disagree with.
-The same user may act as a sceptical reader sometimes and an activist at other times.
+Skeptical readers browse the web and wish to be alerted when information they read conflicts with information found on other web sites.  % beth: typo
+Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of skeptical readers to claims that they disagree with.  % beth: typo
+The same user may act as a skeptical reader sometimes and an activist at other times.  % beth: typo
 
@@
 
-If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
+If a skeptical reader has installed the Think Link browser extension, Think Link will draw the user's attention to text snippets that make or imply disputed claims with red highlighting (Figure~\ref{highlight}).
+% beth: rewording
 If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is.
-If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).
+Clicking on a highlighted snippet will display a visualization showing the best evidence for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).
+% beth: reworded
 
@@
 If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right.
-To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
+To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item. % beth: typo
 
@@
 We found that it was important to allow the claim browser interface to be used in two different ways. 
-When a user is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.
+When a user is browsing a web page and sees a disputed claim, they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail, it is preferable to use a full-window interface, as the small popup interface is too small to easily view large amounts of information.
+% beth: reworded
 
@@
 There are four types of node: snippets, claims, topics, and users.
-A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to, and a user is a person who users Think Link.
-Nodes are connected together by typed, directed, links.
+A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to; a user is a person who uses Think Link.
+% beth: typos
+Nodes are connected by typed, directed links.  % beth: word changes
 There are three link types: supports, opposes, and relates-to. 
-A claim can support,oppose, or relate-to another claim, a claim can relate-to a topic, and a topic can relate-to another topic.
+A claim can support, oppose, or relate-to another claim.
+A claim can also relate-to a topic, and a topic can relate-to another topic.  % beth: new sentence
 This is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, and we allow a claim to simply relate-to another claim, rather than having to either support or oppose it.
@@
 Think Link uses topics to group together related claims. 
-A topic be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''.
-Alternatively, it can be a thing that claims are about, for example ``Carbon Dioxide''.
+A topic may be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''. % beth: typo
+Alternatively, it can be what claims are about, for example ``Carbon Dioxide''.  % beth: changed wording
 Think Link uses the list of page titles on Wikipedia as a seed-set for its topics.
@@
 Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets.
-One anticipated usage scenario for Think Link is an activist user who users a search engine to find a large number of snippets that make a clam that the user disagrees with.
+One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that the user disagrees with.  % beth: typos
 In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.
@@
 In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.
+% beth: not clear what happens if they never file them...
 
@@
 algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims.
-The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page.
+The Wikify algorithm imagines that a piece of text was on a Wikipedia page and predicts which pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page.
+% beth: typos
 Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. 
-The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that a heavily linked to.
+The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to. % beth: typo
 
@@
 Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together.
+% beth: maybe more here?
 
@@
 
-Think Link's annotation system has some privacy issues.
-Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page.
-Privacy issues are reduced by the fact that the requests contain no cookies or other identifying information, and can be cached by a third-party proxy if desired; however issues still remain.
-In future work hope to reduce these privacy issues.
+Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. 
+Privacy issues are reduced by the fact that the requests contain no cookies or other identifying information, and can be cached by a third-party proxy if desired.  % beth: removed words
+In future work we hope to reduce these privacy issues.  % beth: typo
 One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.
@@
 To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for.
+% beth: maybe talk about plans for the larger study?
+(would that add or take away from this?)
 
@@
 
-For the first study we recruited 12 paid participants.
+For the first study we recruited twelve paid participants.  % beth: 12->twelve
 Five were female, seven were male.
@@
 
-Study sessions took approximately 45 minutes.
+Study sessions took approximately forty-five minutes.  % beth: number
 Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension.
@@
 
-For the second study, we recruited 6 paid participants.
+For the second study, we recruited six paid participants.  % beth: number
 Four were female and two were male.
@@
 We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
-The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case).
+The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``skeptical reader'' use case).
 The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).
@@
 
-\subsubsection{High-Level Impressions}
+\subsubsection{High-Level Impressions}  % beth: not sure this section is necessary, or maybe spin it more to be like "yes, people actually said they'd use this""...
+demonstrating practicality and usefullness
 
 Response was generally positive, with many participants being very keen to use the tool soon. 
-One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed.
+One participant said ``I can see myself getting addicted to this'', and several participants asked us to notify them when it is properly deployed.  % beth: typo
 Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
@@
 
-Most participants in the first study, and all participants in the second study were able to use the tool competently.
+Most participants in the first study, and all participants in the second study, were able to use the tool competently.  % beth: comma
 Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
@@
 When the user marked a snippet, Think Link would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype).
-There turned out to be several problems with requiring that a user select a claim at the point at which they marked a snippet:
+There turned out to be several problems with requiring that a user select a claim at the point at which they marked a snippet:  % beth: the folloing list should be indented or bulleted or something
 
@@
 Several users got confused by claims that referred to similar events at different points in time. 
-For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written.
-This is a particular problem when talking about breaking news events, where what claims are true can change fast.
-If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the time at which a claim was asserted to be true.
+For example, one participant in the first study marked two claims as opposing each other when each was true at the time that it was written.  % beth: typo
+This is a particular problem when talking about breaking news events, where which claims are true can change fast.  % beth: word change
+If Think Link is to be effective for describing such events then it will need to have better support for identifying the time at which a claim was asserted to be true.
+% beth: removed words, maybe say we'll work on this in future?
+maybe have timeline?
 
@@
 In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree.
-In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between.
-In both cases, we found that users would often not intially realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}).
+The second interface (Figure~\ref{secondbrowser}) followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between.  % beth: typo
+In both cases, we found that users would often not realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}).
+% beth: removed word
 We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections.
@@
 Since our graph and user base are currently small, we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.
+% beth: but we will once we launch and do big user study yada yada yada
 
@@
 
-We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on either side of the issue.
-Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors.
-It allows users to identify disputed claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.
+We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on all sides of the issue.
+% beth: word change
+Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by web page authors.  % beth: clarified
+Users can identify snippets making on web pages that make disputed claims, connect those snippets to the appropriate arguments, and create relationships to claims on other websites.
+% beth: big rewording
 
-On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.
+Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then uses a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.
+% beth: reworded
 

### 2009-03-28 papers/uist_thinklink/thinklink.tex
Folded in Tye suggestions

@@
 \abstract
-Think Link is a tool that helps a user know when information they read on a web page is disputed on presents only one side of a contentious issue.
+Think Link is a tool that helps a user know when information they read on a web page is disputed.
 As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites.
@@
 All information in Think Link is provided by users.
-Think Link is designed to cator to two usage scenarios.
-Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with.
-Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.
+Think Link is designed to support two usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.
 
@@
 
-\keywords{CSCW, Sensemaking, Annotation, Argumentation, Web}
+\keywords{Sensemaking, Annotation, Argumentation, Web, CSCW}
 
@@
 
-The web contains a huge amount of information, but but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
-If a user is to gain a broad understanding ofa topic then they will need to either stick to sources that they trust or spend time looking for information on other web sites that conflicts with what they have read.
+The web contains a huge amount of information, but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
+If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust to provide accurate and balanced information or spend time looking for information on other web sites that conflicts with what they have read.
 Even if a user tries hard to research every topic they read, they can still get caught out by claims that they had not realized were disputed.
+\todo{word this better}\todo{update all screenshots}
 
 In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources that provide different points of view.
-When Think Link is used as a browser plugin it will highlight text that makes a disputed claim.
-If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by the voting of other Think Link users (Figure~\ref{claimview}).
+When Think Link is used as a browser plugin it will highlight text that makes a disputed claim (Figure~\ref{highlight}).
+When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim, as voted for by other Think Link users (Figure~\ref{claimview}).
 
@@
 Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
-Think Link is designed to cater to two distinct groups of people.
-Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them.
-Sceptical readers install Think Link as a browser plugin so that they can see when things they read are disputed and find other links that present other points of view.
-A reader may be an activist for one issue and a sceptical reader for others.
+Think Link is designed to cater to two groups of people:
+
+\begin{description}
+\item[Activists] care strongly about particular issues.
+They use Think Link to find and mark instances of claims that this disagree with so that other readers will see that these claims are disputed and be exposed to the opposing point of view.
+
+\item[Sceptical Readers] want to know when information they read is disputed.
+They install Think Link as a browser plugin so that it will highlight disputed claims and show them the best evidence supporting opposing points of view.
+\end{description}
 
@@
 
-Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}.
-IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model arguments around an issue as a graph of connected ideas.
-While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue.
-Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2006} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.
+Think Link's argument graph is inspired by Issue Based Information System (IBIS)~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model arguments as a graph of connected ideas.
+While the graph structure varies between tools, most tools allow one to mark a claim as supporting or opposing another claim, and allow one to mark an claim as relating to an issue.
 
-Prior IBIS tools have been intended for conflict modelling and resolution: users build up a complex graph modelling an issue and then use this graph to decide what to do.
-By contrast Think Link uses an IBIS graph for conflict discovery and evidence identification.
-In a tool like gIBIS a user is encouraged to break down their argument into as much detail as possible and encouraged to use the graph itself to reach a decision.
-By contrast, in Think Link a user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form their opinion primarily by reading the articles that have been linked as evidence.
-In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit the expected usage for other IBIS tools.
+Although Think Link's argument graph is very similar to that used by IBIS tools, it uses it for a different purpose.
+In Think Link the focus is on the snippets, and the purpose of the argument graph is to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular point of view.
+A user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form an opinion primarily by looking at the snippets that make that claim, rather than by looking at the argument graph itself.
+This differs from the normal way in which previous IBIS tools have been used.
+In a tool such as gIBIS~\cite{Conklin1987a} the focus is on the argument graph.
+A user is encouraged to break their argument down into as many separate ideas as possible and a user is expected to use the graph itself to reach a conclusion.
+In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many topics --- this would not fit with the expected usage model for other IBIS tools.
 
-Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use.
+Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with using IBIS tools to help people resolve disputes and make decisions.
+Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their dispute, and that users found it difficult to properly encode a complex issue as an argument graph.
 We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
 
-Cohere~\cite{Shum2008} is perhaps the IBIS tool most similar to Think Link.
-Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from pages that one browses.
-While Cohere and Think Link both connect an argument graph to the web, they do so in very different ways.
-In Cohere, a user attaches a web snippet to their idea in order to use it as evidence.
-By contrast, in Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument.
-More generally,
+Cohere~\cite{Shum2008} allows a user to associate a web page with a claim in an argument graph and provides a Firefox plugin to help users do this; however Cohere and Think Link have very different models.
+In Cohere, when one creates a new claim one can specify one or more URLs to be used as supporting evidence.
+Cohere is not intended to be used as a tool to identify disputed snippets, and does not expect users to attach large numbers of web snippets to existing claims.
 
-More generally, a key way Think Link differs from Cohere is that it separates the creation of claims from their association with snippets.
-A user can mark a snippet without yet being sure what claims it should be linked to, or can mark a claim without knowing what snippets other users will associate with it.
-
-Think Link uses a simple IBIS-style graph structure in which claims support, oppose, or relate-to other claims.
+Think Link uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims.
 Several alternative graph structures have been proposed for describing arguments and design rationale.
@@
 More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.
-
-When choosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use.
-For Think Link, we tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model.
-The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.
 
@@
 Think Link's database automatically imports all contentious claims identified by Snopes.
+FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.
 
@@
 In some cases, other users who see a web page an see text highlighted where other users have clipped it.
+These tools do not attempt to identify when snippets make disputed claims or to connect them to opposing sides of an argument.
 
-ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly document with logical triples (subject, verb, object) describing interesting claims that are being made in the document.
-This semantic information can be used to connect claims in different documents and see when a logical claim in one document contradicts another.
+ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical triples (subject, verb, object) describing interesting claims that are being made in the document.
+This semantic information can be used to connect claims in different documents.
 Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.
-
-Videolyzer~\cite{Diakopoulos2008} allows users to annotate and comment on political videos with accompanying textual transcriptions.
-A user can mark up a section of video for bias, accuracy, or rhetorical technique.
-Comments can include references to external sources that back up the argument being made.
+Unlike Think Link, these tools are looking for logical relations between entities rather than instances of already-known claims.
 
@@
 SpinSpotter annotates a snippet with an annotation specific to that particular snippet of text, while Think Link treats a snippet as being an instance of a shared contentious claim, and links all snippets identified as making that claim to a shared graph node linking to other information about that claim.
+
+Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos with accompanying textual transcriptions.
+A user can mark up a section of video for bias, accuracy, or rhetorical technique.
+Comments can include references to external sources that back up the argument being made.
+Like SpinSpotter, Videolyzer attaches annotations to a specific video section and does not attempty to gather multiple video sections that make a common contentious claim.
+
+\todo{Ask Nicholas if he would like to read the paper}
 
@@
 If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is.
-If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).
+If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim, where best is determined by the number of users who voted for that evidence (Figure~\ref{claimview}).
 
@@
 
-Once a user has identified a claim that they are interested in, they can use Think Link's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.
+Once a sceptical reader has identified a claim that they are interested in, they can use Think Link's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.
 
-In our user studies, we found that users wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim.
+In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim.
 We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left.
-If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right.
+If a panel describes a disputed claim (Figure~\ref{panel}), then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right.
 To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
+
+The panel for a claim (Figure~\ref{panel}) lists evidence that will help a user decide whether the claim is true.
+Evidence is categorized as either supporting, opposing, or being related-to the claim.
+The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument.
+Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.
 
@@
 We found that it was important to allow the claim browser interface to be used in two different ways.
-When a user is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.
+When a sceptical reader is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.
 
@@
 Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model.
-There are four types of node: snippets, claims, topics, and users.
+There are three types of node: snippets, claims, and topics.
 A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to, and a user is a person who users Think Link.
@@
 There are three link types: supports, opposes, and relates-to.
-A claim can support,oppose, or relate-to another claim, a claim can relate-to a topic, and a topic can relate-to another topic.
-This is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, and we allow a claim to simply relate-to another claim, rather than having to either support or oppose it.
+A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.
 
@@
 Alternatively, it can be a thing that claims are about, for example ``Carbon Dioxide''.
-Think Link uses the list of page titles on Wikipedia as a seed-set for its topics.
+Think Link uses the list of page titles on Wikipedia as a seed-set for its topics and users can also add new topics from within the claim browser.
 
-The panel for a claim lists evidence that will help a user decide whether the claim is true.
-Evidence is categorized as either supporting, opposing, or being related-to the claim.
-The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument.
-Evidence can either be a snippet that talks about that claim, or another claim whose truth would support the truth of this claim.
+Think Link's graph model is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, we collapse gIBIS's five ways of connecting topics together and four ways of connecting a claim to an topic into a single relates-to relation.
+The result is a graph structure that is significantly simpler.
+While Think Link's graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, it is sufficient for the conflict discovery and snippet organization task that Think Link's graph is intended for, and we have found that the smaller set of link and node types reduces the mential effort required to create an argument graph.
 
@@
 Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side.
-Of course, these techniques only work to a limited extent, and so we expect that editorial moderation may be needed for highly controversial topics, as it is in Wikipedia.
+In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong.
 
@@
 A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted of the fact that a claim that that snippet is making or implying is disputed.
-A user selects ``This is interesting'' if they believe that the snippet contains useful information that would be useful to readers investigating a disputed claim.
+A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be for readers investigating a disputed claim.
 
@@
 
-Think Link does not require that a user associate a snippet with a snippet at the point at which they create it.
+Think Link does not require that a user associate a snippet with a claim at the point at which they create it.
 Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets.
-One anticipated usage scenario for Think Link is an activist user who users a search engine to find a large number of snippets that make a clam that the user disagrees with.
+One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a clam that they disagrees with.
 In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.
@@
 \item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Think Link will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}).
-A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates to'' link types.
+A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates-to'' link types.
 If Think Link does not suggest the right snippets then Think Link can guide the suggestions by entering keywords into the text box above the suggestion list.
@@
 
-\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Think Link will show a list of all the snippets that they have marked but not yet associated with a claim or a snippet (Figure~\ref{sniptopic}).
+\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Think Link will show a list of all the snippets that they have marked but not yet associated with a claim or a topic (Figure~\ref{sniptopic}).
 If the user selects an unfiled snippet then Think Link will suggest claims or topics that the user might want to associate with that snippet.
-As with the snippet suggested, a user can guide the suggestions by entering keywords.
+As with the claim-first method, a user can guide the suggestions by entering keywords.
 If the correct claim is not suggested then the user can create a new claim by typing it into the text box and clicking the ``add'' button.
@@
 When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim.
-It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to offer support for a particular claim.
+It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to use it as evidence for a particular claim.
 In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for.
@@
 
-Think Link uses the Wikify!
-algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims.
-The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page.
+As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected.
+If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected.
+Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to connect them with a single click.
+Think Link uses the same suggestion system to allow users to connect claims to snippets, and to connect claims to other related claims.
+
+Think Link uses the Wikify algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims.
+The Wikify algorithm imagines that a piece of text was on a Wikipedia page and predicts what pages that text would most likely link to based on the probability that any particular n-gram links to any particular page.
 Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles.
-The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that a heavily linked to.
+The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to.
+
+Even with these suggestion and bulk connection features, gathering snippets that make a disputed claim or provide useful evidence requires a non-trivial amount of work.
+Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks; currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog.
+Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to be notified every time a new page appears about the issue they are interested in.
+Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashkov2006}, and so one can achive useful coverage by only marking up the relatively small number of very popular pages (for example articles on major news sites).
 
@@
 
-As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected.
-If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected.
-Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together.
-
 \todo{Allow two claims to be marked as being identical.}
-
-Think Link uses the same suggestion system to allow users to connect claims to snippets, and to connect claims to other related claims.
 
@@
 The studies were not intended to validate the design of Think Link as being correct.
-Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different points.
+Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different claims.
 To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for.
@@
 The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page.
+At the end of each study, we asked each partipicant whether there were times in the past where they would have wanted to use Think Link.
 We present the results of the two studies together.
+
+\todo{Say something about final informal evaluation}
+%After the second study, we made minor changes to our user interface (described below) and performed an informal user study with people in our organization to
 
@@
 
-For the first study we recruited 12 paid participants.
-Five were female, seven were male.
-Their ages ranged from high school age to retired.
-Our intention was to recruit users who were not experts, but who regularly used the Internet to find information.
-We recruited participants using a posting to the Craigslist.org classified advert site.
-In our advert, we expressed an interest in people who use the Internet to gather knowledge, rather than just for tasks such as email or shopping.
-We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.
+For the first study we recruited 12 paid participants, 5 female, 7 male, aged 18 to 52.
+Nine participants regularly posted to a blog and the other three regularly posted comments to blogs or mailing lists.
+Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas.
+In our advert, we asked people to tell us what kind of information they looked at on the web, and how they shared information with others.
+We selected participants who looked at information that was likely to be disputed (e.g.
+political commentry) and said they regularly shared information with friends.
+We avoided applications from people who were more interested in less disputed topics like social networking or sport.
+
+\todo{Get the correct number of bloggers}
 
@@
 Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension.
-We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph.
+We first demonstrated Think Link's interface, and then asked them to browse web sites they normally use
+
+the web sites they normally normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph.
 For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.
@@
 
-For the second study, we recruited 6 paid participants.
-Four were female and two were male.
-Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the college semester meant that five of the participants were students.
-Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.
+For the second study, we recruited 6 paid participants, 4 female, 2 male.
+Four participants had a blog.
+Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the local university semester meant that five of the participants were college students.
 
-In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it.
-We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
+In the second study we were more confident about the usability of our tool and so we decided to tell the participants nothing about how to use it.
+We gave each user a brief description of the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
 The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case).
@@
 
-Participants were shown the prototype interface shown in Figure~\ref{secondbrowser}.
-This is similar to the interface described earlier in this paper, but uses drag and drop to make connections, rather than a suggestion system.
+Participants were shown the prototype interface shown in Figures~\ref{secondbrowser} and \ref{secondsnippetbox}.
+This was similar to the interface described earlier in this paper, except that it used drag and drop to make connections rather than a suggestion system, it did not offer a ``relates-to'' link between claims, and it required a user to choose a claim at the point at which they create a snippet.
 
@@
 
-Participants liked the ability to see when other pages disagreed with the claim they were looking at.
+Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader).
 One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
+A smaller number said they would want to marking up claims they disagreed with (activist).
+One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.
 
@@
 Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
-Participants said they found the tool ``very intuitive''.
+One participants said they found the tool ``very intuitive''.
 
@@
 While it is possible that they might want to use this as evidence for a claim in the future, they didn't want to have to decide what the claim was immediately.
-In the final interface one can associate a snippet with a topic rather than a claim.
+In the final interface one can choose to associate a snippet with a topic.
 
@@
 For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information?
-In the final interface, users can choose how specific to make their claims after they have gathered a large number of snippets and know what information is repeated between sources.
+In the final interface, users are expected to only create a claim when they have several snippets that make the same claim.
+This makes it easier to know how broad the claim should be as they know how much information is shared by claims.
 
@@
 Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet.
-The final interface avoids this problem by allowing a used to delay the association of a claim for a snippet until they know what useful claim they want to use that snippet as evidence for.
+The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and have a particular disputed claim in mind.
 
@@
 
-Some users incorrectly marked one claim as supporting another when in fact they should have both been marked as supporting a third claim that needed to be created.
-For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing environmental problems''.
-Users realized that the claims were related, but did not immediately recognize that they needed to create new claims in order to structure the relationship correctly.
-It is possible that creating correct logical claim structures may just be too difficult for some people, or it may be that users would get used to the idea with more practice.
-We hope that if Think Link was deployed more widely many of the intermediate claims that were needed would already have been created and this problem would thus be reduced.
+Some users marked one claim as supporting another when it would have been more logically correct to make them both as supporting a third claim that needed to be created.
+For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing problems''.
+Users realized that the claims were related, but were not sure how best to connect them.
+It is possible that creating logically correct claim structures may be too difficult for some people (see Isenmann and Reuter~\cite{Isenmann1997}).
+We believe that this problem can be addressed to some extend though voting by other users who recognize that a claim does not provide useful evidence.
 
@@
 For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''.
-Similarly, many users expressed a desire to mark claims as being ``related'' without supporting or opposing each other.
-For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''.
-In the first prototypes, a user needed to chose between ``supports/opposes'' when connecting two claims together (following gIBIS~\cite{Conklin1987a}).
-In the final interface we introduced a ``related-to'' link type to allow users to connect claims that they thought should be related but which didn't confirm to a simple pro/con relationship.
+Similarly, many users expressed a desire to mark claims as being related without supporting or opposing each other.
+For example ``America did not sign the Kyoto Protocol'' {\it  relates-to} ``America was right to not sign the Kyoto Protocol''.
+In the final interface we introduced a ``relates-to'' link type to allow users to connect claims that they thought should be related but which didn't confirm to a simple pro/con relationship.
 

### 2009-03-28 webapps/node/javascript/leftrightui.js

@@ -529,7 +529,7 @@ function makeSuggester(type,verbs,reverse,panel,obj,panelnum){
 			}
 		});
 	
-	if(obj.type == "snippet" && !obj.to.supports && !obj.to.opposes && type == "claim"){
+	if(obj.type == "snippet" && !obj.from.supports && !obj.from.opposes && type == "claim"){
 		adder.click();
 		
 	}
@@ -833,12 +833,12 @@ function makeLink(obj,panelnum,parentobj,novote){
 	if(!novote){
 		var votebox = $("<nobr class='votebox'/>").appendTo(text);
 		
-		var up = $("<img class='vote' title='Promote'/>").attr("src",iconUrl(getVoteUpIcon(obj,false)))
+		var up = $("<img class='vote' title='Vote up'/>").attr("src",iconUrl(getVoteUpIcon(obj,false)))
 			.mouseover(function(){up.attr("src",iconUrl(getVoteUpIcon(obj,true)))})
 			.mouseout(function(){up.attr("src",iconUrl(getVoteUpIcon(obj,false)))})
 			.appendTo(votebox);
 
-		var down = $("<img class='vote' title='Remove'/>").attr("src",iconUrl(getVoteDownIcon(obj,false)))
+		var down = $("<img class='vote' title='Vote down'/>").attr("src",iconUrl(getVoteDownIcon(obj,false)))
 			.mouseover(function(){down.attr("src",iconUrl(getVoteDownIcon(obj,true)))})
 			.mouseout(function(){down.attr("src",iconUrl(getVoteDownIcon(obj,false)))})
 			.appendTo(votebox);		

### 2009-03-28 papers/uist_thinklink/thinklink.tex
Made changes suggested by Beth

@@
 % --- Copyright notice ---
-\conferenceinfo{UIST'09}{October 4-7, 2008, Victoria, BC, Canada}
+\conferenceinfo{UIST'09}{October 4-7, 2009, Victoria, BC, Canada}
 \CopyrightYear{2009}
@@
 As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites.
-If a user clicks on a highlighted snippet then Think Link will show them an argument graph showing the best evidence for and against the claim being true.
+If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against the claim the snippet is making.
 
-All information in Think Link is provided by users.
-Think Link is designed to support two usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.
+Users provide all Think Link's information: they create new claims, mark new snippets, connect claims and snippets together.
+Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.
 
@@
 
-The web contains a huge amount of information, but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
+\todo{update screenshots}
+
+The web contains a huge amount of information, but some web sites contain innaccurate information~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
 If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust to provide accurate and balanced information or spend time looking for information on other web sites that conflicts with what they have read.
-Even if a user tries hard to research every topic they read, they can still get caught out by claims that they had not realized were disputed.
+Even if a user tries to be careful they can still be caught out by claims that they had not realized were disputed.
 \todo{word this better}\todo{update all screenshots}
 
-In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources that provide different points of view.
-When Think Link is used as a browser plugin it will highlight text that makes a disputed claim (Figure~\ref{highlight}).
-When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim, as voted for by other Think Link users (Figure~\ref{claimview}).
+In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view.
+When Think Link is used as a browser plugin it will highlight snippets of text that makes disputed claims (Figure~\ref{highlight}).
+When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).
 
@@
 Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
-Think Link is designed to cater to two groups of people:
+Think Link is designed to cater to two primary usage scenarios:
 
@@
 
-The design of Think Link was guided by two user studies, in which we observed the behavior of users as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.
+The design of Think Link was guided by two user studies in which we observed users' behaviour as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.
 
@@
 Think Link builds on work in several different areas.
-The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.
-The idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
-The model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}.
-The idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
+The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.
+The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
+Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information.
+Clipping tools such as Internet Scrapbook~\cite{Sugiura1998} allow users to mark snippets on web sites.
 
 What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of showing users when the information they read conflicts with information from other sources.
+\todo{rewrite this?}
 
@@
 
-Think Link's argument graph is inspired by Issue Based Information System (IBIS)~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model arguments as a graph of connected ideas.
-While the graph structure varies between tools, most tools allow one to mark a claim as supporting or opposing another claim, and allow one to mark an claim as relating to an issue.
+Think Link's argument graph is inspired by Issue Based Information System (IBIS)~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
+IBIS tools model debate as a graph of connected issues, positions, and arguments.
+While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.
 
@@
 In Think Link the focus is on the snippets, and the purpose of the argument graph is to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular point of view.
-A user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form an opinion primarily by looking at the snippets that make that claim, rather than by looking at the argument graph itself.
+A user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim.
+A Think Link user is expected to form an opinion primarily by looking at the snippets listed as evidence, rather than by looking at the argument graph itself.
 This differs from the normal way in which previous IBIS tools have been used.
-In a tool such as gIBIS~\cite{Conklin1987a} the focus is on the argument graph.
-A user is encouraged to break their argument down into as many separate ideas as possible and a user is expected to use the graph itself to reach a conclusion.
-In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many topics --- this would not fit with the expected usage model for other IBIS tools.
+In a tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph.
+A user is encouraged to break their argument down into as many separate ideas as possible and users are expected to use the graph itself to reach a conclusion.
+In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit with the expected usage model for other IBIS tools.
 
 Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with using IBIS tools to help people resolve disputes and make decisions.
-Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their dispute, and that users found it difficult to properly encode a complex issue as an argument graph.
-We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
+Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
+We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
 
-Cohere~\cite{Shum2008} allows a user to associate a web page with a claim in an argument graph and provides a Firefox plugin to help users do this; however Cohere and Think Link have very different models.
-In Cohere, when one creates a new claim one can specify one or more URLs to be used as supporting evidence.
-Cohere is not intended to be used as a tool to identify disputed snippets, and does not expect users to attach large numbers of web snippets to existing claims.
+Cohere~\cite{Shum2008} allows a user to specify one or more URLs as evidence when creating a new claim and provides a Firefox plugin to help a user create a claim based on the page they are browsing; Cohere works with URLs rather than snippets and does not allow one to associate a new URL with an existing claim written by someone else.
+Cohere is not designed to be used to identify snippets on web pages that make disputed claims.
 
@@
 If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}.
-Snopes is a database of urban legends that the site owners have investigated to determine whether they are true or not.
+Snopes is a database of urban legends that the site owners investigated to determine whether they are true.
+Think Link's database automatically imports all contentious claims identified by Snopes.
 FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.
-Think Link's database automatically imports all contentious claims identified by Snopes.
-FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.
+
+%FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.
 
@@
 TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages.
-ScentHighlights~\cite{Chi2005a} highlights snippets of text on a web page that are related to topics that the user has said that they are intersted in.
+ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in.
 Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
@@
 Think Link is designed to be used in two different ways.
-Sceptical readers browse the web and wish to be alerted when information they read conflicts with information found on other web sites.
+Sceptical wish to be alerted when information they read on the web conflicts with information on other web sites.
 Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of sceptical readers to claims that they disagree with.
@@
 
-If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
-If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is.
-If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim, where best is determined by the number of users who voted for that evidence (Figure~\ref{claimview}).
+If a sceptical reader has installed the Think Link browser extension, Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
+If a user hovers their mouse over a highlighted snippet then Think Link displays a tooltip giving the disputed claim.
+Clicking on a highlighted snippet reveals a visualization showing the best evidence for and against the claim, as determined by the user community (Figure~\ref{claimview}).
 
@@
 If a panel describes a disputed claim (Figure~\ref{panel}), then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right.
-To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
+To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
 
@@
 We found that it was important to allow the claim browser interface to be used in two different ways.
-When a sceptical reader is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.
+When a sceptical reader is browsing a web page and sees a disputed claim, they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail, it is preferable to use a full-window interface, as the small popup interface is too small to easily view large amounts of information.
 
@@
 There are three types of node: snippets, claims, and topics.
-A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to, and a user is a person who users Think Link.
+A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; and a topic is an issue or concept that a claim might relate to..
 Nodes are connected together by typed, directed, links.
@@
 Think Link uses topics to group together related claims.
-A topic be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''.
-Alternatively, it can be a thing that claims are about, for example ``Carbon Dioxide''.
+A topic may be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''.
+Alternatively, it can be something claims are about, for example ``Carbon Dioxide''.
 Think Link uses the list of page titles on Wikipedia as a seed-set for its topics and users can also add new topics from within the claim browser.
 
-Think Link's graph model is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, we collapse gIBIS's five ways of connecting topics together and four ways of connecting a claim to an topic into a single relates-to relation.
-The result is a graph structure that is significantly simpler.
-While Think Link's graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, it is sufficient for the conflict discovery and snippet organization task that Think Link's graph is intended for, and we have found that the smaller set of link and node types reduces the mential effort required to create an argument graph.
+Think Link's graph model is a simpler than that used by gIBIS~\cite{Conklin1987}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation.
+While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, it is sufficient for the conflict discovery and snippet organization task that Think Link's graph is intended for, and we have found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.
 
@@
 Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets.
-One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a clam that they disagrees with.
-In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.
+One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagrees with. 
+In this case, the user can save time by first collecting all their snippets, and then attaching all their snippets to their disputed claim in bulk.
 
@@
 
+Think Link uses the same suggestion system to suggest connections between claims.
+It is important to make sure that the argument graph stays well connected as it grows.
+If users create duplicate claims or don't connect their claims to existing claims then then graph becomes less useful.
+Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to enable a suggested connection with a single click.
+
 When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim.
@@
 In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.
-
-As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected.
-If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected.
-Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to connect them with a single click.
-Think Link uses the same suggestion system to allow users to connect claims to snippets, and to connect claims to other related claims.
 
@@
 
-Think Link's annotation system has some privacy issues.
-Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page.
-Privacy issues are reduced by the fact that the requests contain no cookies or other identifying information, and can be cached by a third-party proxy if desired; however issues still remain.
-In future work hope to reduce these privacy issues.
-One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.
+Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. 
+Think Link reduces privacy issues by not sending cookies or other identifying information, and Think Link's requests can be cached by a third-party proxy if desired. 
+In future work we hope to reduce these privacy issues. One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.
 
@@
 
+These studies identified some usability problems which we responded to with changes to the user interface which we describe below.
+We conducted a lightweight evaluation of our final interface and it seemed our revisions successfully addressed the usability concerns.
+
+\todo{Test with at least 4 people}
 \todo{Say something about final informal evaluation}
@@
 
-For the first study we recruited 12 paid participants, 5 female, 7 male, aged 18 to 52.
-Nine participants regularly posted to a blog and the other three regularly posted comments to blogs or mailing lists.
+For the first study we recruited twelve paid participants, five female, seven male, aged 18 to 52.
+Nine participants regularly posted to a blog.
+We recruited participants by posting an advert on craigslist\footnote{http://craigslist.org}.
 Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas.
@@
 
-Study sessions took approximately 45 minutes.
+Study sessions took approximately fourty five minutes.
 Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension.
@@
 
-For the second study, we recruited 6 paid participants, 4 female, 2 male.
+For the second study, we recruited six paid participants, four female, two male.
 Four participants had a blog.
@@
 
-\subsubsection{High-Level Impressions}
-
-Response was generally positive, with many participants being very keen to use the tool soon.
+% \subsubsection{High-Level Impressions}
+% 
+% Response was generally positive, with many participants being very keen to use the tool soon.
 One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed.
 Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
-
-Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader).
+% 
+% Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader).
 One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
-A smaller number said they would want to marking up claims they disagreed with (activist).
+A smaller number said they would want to mark up claims they disagreed with (activist).
 One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.
-
-Most participants in the first study, and all participants in the second study were able to use the tool competently.
+% 
+% Most participants in the first study, and all participants in the second study were able to use the tool competently.
 Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
@@
 For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written.
-This is a particular problem when talking about breaking news events, where what claims are true can change fast.
-If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the time at which a claim was asserted to be true.
+This is a particular problem when talking about breaking news events, where the facts can change fast.
+If Think Link is to be effective for describing such events then it will need to have better support associating times with claims and snippets.
 
@@
 
-The first two versions of Think Link used a drag-and-drop interface to allow a user to create links between claims.
-In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree.
-In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between.
-In both cases, we found that users would often not intially realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}).
-We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections.
+The prototype versions of Think Link used a drag-and-drop interface to allow a user to create links between claims.
+In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find others claims and then drag them into appropriate positions in the argument graph.
+The second interface (Figure~\ref{secondbrowser}) followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between.
+In both cases, we found that users would often not realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}).
+We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and the rendering of a claim did not have any visual clue to suggest that they could use drag and drop to create connections.
 In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.
@@
 
-We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on either side of the issue.
-Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors.
-It allows users to identify disputed claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.
+We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on all sides of the issue.
+Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by web page authors.
+Users can identify snippets that make disputed pages, connect those snippets to the appropriate claims, and connect claims that relate to each other.
 
-On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.
+Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then uses a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.
 

### 2009-03-29 papers/uist_thinklink/thinklink.tex
Spellcheck. Fixed arrow bug in UI

@@
 Users provide all Think Link's information: they create new claims, mark new snippets, connect claims and snippets together.
-Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.
+Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.
 
@@
 
-The design of Think Link was guided by two user studies in which we observed users' behaviour as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.
+The design of Think Link was guided by two user studies in which we observed users' behaviour as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.
 
@@
 The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.
-The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
+The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
 Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information.
@@
 Comments can include references to external sources that back up the argument being made.
-Like SpinSpotter, Videolyzer attaches annotations to a specific video section and does not attempty to gather multiple video sections that make a common contentious claim.
+Like SpinSpotter, Videolyzer attaches annotations to a specific video section and does not attempt to gather multiple video sections that make a common contentious claim.
 
@@
 The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page.
-At the end of each study, we asked each partipicant whether there were times in the past where they would have wanted to use Think Link.
+At the end of each study, we asked each participant whether there were times in the past where they would have wanted to use Think Link.
 We present the results of the two studies together.
@@
 We selected participants who looked at information that was likely to be disputed (e.g.
-political commentry) and said they regularly shared information with friends.
+political commentary) and said they regularly shared information with friends.
 We avoided applications from people who were more interested in less disputed topics like social networking or sport.
@@
 
-Study sessions took approximately fourty five minutes.
+Study sessions took approximately forty five minutes.
 Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension.

### 2009-03-29 webapps/node/javascript/leftrightui.js

@@ -207,7 +207,7 @@ function makeNavButtons(panelnum){
 		.appendTo(navbuttons);
 	var right = $("<img class='navright'/>").attr("src",iconUrl("resultset_next"))
 		.click(function(){
-			scrollToPanel(panelnum+1);
+			scrollToPanel(panelnum);
 		})
 		.appendTo(navbuttons);
 
@@ -384,7 +384,7 @@ function makeInfo(obj,panelnum){
 	info.append(makeNavButtons(panelnum));	
 
 	if(panelnum != 0){
-		var closebutton = $("<img class='closebutton'/>").attr("src",iconUrl("cancel")).appendTo(info);
+		var closebutton = $("<img class='closebutton'/>").attr("src",iconUrl("cancel_grey")).appendTo(info);
 		closebutton.click(function(){
 			removeArrows(panelnum-1);
 			scrollToPanel(panelnum-1);
@@ -666,6 +666,8 @@ function makeSubGroup(subtitle,links,panelnum,parentobj,showall){
 			}
 		} 
 		
+	}else{
+		group.attr("class","nogroup");
 	}
 
 

### 2009-03-30 papers/uist_thinklink/thinklink.tex
Did another pass over the paper. Now have a half-page spare for filling with more figures.

--- 2009-03-28 papers/uist_thinklink/thinklink.tex
@@
 \abstract
-Think Link is a tool that helps a user know when information they read on a web page is disputed.
-As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites.
+Think Link is a tool that helps users know when information they read on a the web is disputed.
+As a user browses the web, Think Link highlights snippets of text that make claims that users have identified as being disputed.
 If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against the claim the snippet is making.
 
-Users provide all Think Link's information: they create new claims, mark new snippets, connect claims and snippets together.
+Users provide all of Think Link's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
 Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.
@@
 
-The web contains a huge amount of information, but some web sites contain innaccurate information~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}.
-If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust to provide accurate and balanced information or spend time looking for information on other web sites that conflicts with what they have read.
-Even if a user tries to be careful they can still be caught out by claims that they had not realized were disputed.
+The web contains a huge amount of information, but some of this information is incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}.
+If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
+Even if a user tries to be careful, they can still be caught out by claims that they had not realized were disputed.
 \todo{word this better}\todo{update all screenshots}
@@
 In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view.
-When Think Link is used as a browser plugin it will highlight snippets of text that makes disputed claims (Figure~\ref{highlight}).
+If a user has installed the Think Link browser extension hen it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}).
 When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).
@@
 
-Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
+Think Link relies on users to identify disputed claims, to find instances of these claims on web pages, and to vote for the sources that provide the best support or opposition for a claim. 
 Think Link is designed to cater to two primary usage scenarios:
@@
 \item[Activists] care strongly about particular issues.
-They use Think Link to find and mark instances of claims that this disagree with so that other readers will see that these claims are disputed and be exposed to the opposing point of view.
+They use Think Link to mark snippets that make claims that they disagree with.
+They are motivated by a desire to make other readers see that these claims are disputed and learn about the opposing point of view.
 
-\item[Sceptical Readers] want to know when information they read is disputed.
-They install Think Link as a browser plugin so that it will highlight disputed claims and show them the best evidence supporting opposing points of view.
+\item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled.
+They install Think Link as a browser plugin so that it will highlight disputed claims and show them opposing points of view.
 \end{description}
+
+The same user may be an Activist for some issues and a Sceptical Reader for others.
 
@@
 	\includegraphics[width=5cm]{../screenshots/v2_popup_dim.png}
-	\caption{Click on a claim to investigate evidence for and against it}
+	\caption{Click on a snippet to investigate evidence for the claim it makes}
 	\label{claimview}
@@
 
-Think Link builds on work in several different areas.
-The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.
+Think Link builds on prior work in several different areas.
+The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.
 The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
 Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information.
-Clipping tools such as Internet Scrapbook~\cite{Sugiura1998} allow users to mark snippets on web sites.
+Think Link's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
 
-What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of showing users when the information they read conflicts with information from other sources.
-\todo{rewrite this?}
+What makes Think Link interesting is the way that it applies ideas from these different domains to the task of helping users deal with misinformation and bias on the web.
 
@@
 
-Think Link's argument graph is inspired by Issue Based Information System (IBIS)~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
-IBIS tools model debate as a graph of connected issues, positions, and arguments.
+Think Link's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
+IBIS tools model debate as a graph of issues, positions, and arguments.
 While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.
 
-Although Think Link's argument graph is very similar to that used by IBIS tools, it uses it for a different purpose.
-In Think Link the focus is on the snippets, and the purpose of the argument graph is to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular point of view.
-A user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim.
-A Think Link user is expected to form an opinion primarily by looking at the snippets listed as evidence, rather than by looking at the argument graph itself.
-This differs from the normal way in which previous IBIS tools have been used.
-In a tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph.
-A user is encouraged to break their argument down into as many separate ideas as possible and users are expected to use the graph itself to reach a conclusion.
-In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit with the expected usage model for other IBIS tools.
+Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox plugin to help a user create a claim about a web page they are reading.
+Unlike Think Link, Cohere is not designed to be used to alert users about disputed snippets.
+Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.
 
-Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with using IBIS tools to help people resolve disputes and make decisions.
+Although Think Link's argument graph is similar to that used by IBIS tools, it uses it for a different purpose.
+In Think Link the focus is on snippets, and the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim.
+A user is expected to create a new claim only when they want to group together several snippets that make that claim.
+A Think Link user is expected to form an opinion primarily by looking at the snippets and the pages they are part of, rather than by looking at the argument graph itself.
+By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph.
+A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion.
+In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.
+
+Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions.
 Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
-We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.
-
-Cohere~\cite{Shum2008} allows a user to specify one or more URLs as evidence when creating a new claim and provides a Firefox plugin to help a user create a claim based on the page they are browsing; Cohere works with URLs rather than snippets and does not allow one to associate a new URL with an existing claim written by someone else.
-Cohere is not designed to be used to identify snippets on web pages that make disputed claims.
+We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Think Link that is designed for identifying snippets that represent conflicting points of view.
 
@@
 
-Think Link's argument visualization is influenced by the left-to-right layout of Cohere~\cite{Shum2008}.
-Compendium~\cite{Selvin2001} contains a number of other visualizations of argument graphs.
-Mess Maps~\cite{Horn2007} present an alternative view in which an argument is divided into different sectors, each of which presents the argument from a different frame of discourse (e.g.
-policy maker vs industrialist vs environmentalist).
-
 \subsection{Checking Accuracy and Bias on the Web}
@@
 Think Link's database automatically imports all contentious claims identified by Snopes.
-FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.
+FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. We use Fact Check as a useful source of disputed claims.
 
-%FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.
+% FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.
+
+\todo{Make sure we stay in sync}
 
 NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias.
-NewsCube presents a user with articles on the same topic that have different biases.
-MediaCloud applies various statistical analyses to news sources so that a reader can see when different news sources associate different words with the same topic.
+NewsCube finds articles on the same topic that have different biases.
+MediaCloud shows which different words different news sources associate with the same topic.
 
-Several authors have investigated ways to make Wikipedia\footnote{http://wikipedia.org} more trustworthy.
-WikiTrust~\cite{Adler2008a} highlights passages on wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors.
-Wiki Dashboard~\cite{Kittur2008} presents the reader of a Wikipedia article with a visualization that shows them how it has been edited in the past and lets them see graphically how contentious the topic is.
-Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds Wikipedia edits that have been made by people with an interest in spreading misinformation (e.g.
-people from a company editing pages about that company).
+Several authors have created tools that help users know when to trust information on Wikipedia\footnote{http://wikipedia.org}.
+WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors.
+Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is.
+Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
 
@@
 
-Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004} allow users to highlight sections of text on a page.
-Annotation systems often also do clipping.
+Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001}, ScreenCrayons~\cite{Olsen2004}, and ReframeIt\footnote{http://reframeit.com} allow users to highlight sections of text on a page.
 Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends.
-In some cases, other users who see a web page an see text highlighted where other users have clipped it.
+Some tools highlight snippets that have been clipped by other users.
 These tools do not attempt to identify when snippets make disputed claims or to connect them to opposing sides of an argument.
 
-ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical triples (subject, verb, object) describing interesting claims that are being made in the document.
-This semantic information can be used to connect claims in different documents.
+SpinSpotter\footnote{http://spinspotter.com} allows a user to mark snippets that contain spin or bias.
+A user can comment on why a snippet is biased and rewrite the snippet in a neutral way.
+While SpinSpotter and Think Link both draw attention to biased or inaccurate snippets, they do different things with the snippets.
+SpinSpotter lets users annotate a snippet with comments specific to that particular snippet, while Think Link treats a snippet as being an instance of a shared claim, and links all snippets identified as making that claim to a shared node in the argument graph that is linked to other points of view.
+
+Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos.
+A user can attach a comment to a section of video and tag it for bias, accuracy, or rhetorical technique.
+Comments can include references to external sources that back up the argument being made.
+Like SpinSpotter, Videolyzer does not attempty to gather multiple video sections that make a common contentious claim.
+
+ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical subject-verb-object triples describing important claims made in the document.
 Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.
-Unlike Think Link, these tools are looking for logical relations between entities rather than instances of already-known claims.
-
-SpinSpotter\footnote{http://spinspotter.com} allows a user to highlight snippets of text that contain spin or bias and either describe why the text is biased, or rewrite the text in an unbiased way.
-While SpinSpotter and Think Link share a goal of drawing user attention to biased or inaccurate information, they do so in a different way.
-SpinSpotter annotates a snippet with an annotation specific to that particular snippet of text, while Think Link treats a snippet as being an instance of a shared contentious claim, and links all snippets identified as making that claim to a shared graph node linking to other information about that claim.
-
-Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos with accompanying textual transcriptions.
-A user can mark up a section of video for bias, accuracy, or rhetorical technique.
-Comments can include references to external sources that back up the argument being made.
-Like SpinSpotter, Videolyzer attaches annotations to a specific video section and does not attempty to gather multiple video sections that make a common contentious claim.
+Like Think Link, these tools allow a user to mark the claims being made in a document, however these tools are more formal and are designed to extract knowledge rather than informally mark disputed snippets.
 
@@
 Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
-This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.
 
@@
 
-Think Link is designed to be used in two different ways.
-Sceptical wish to be alerted when information they read on the web conflicts with information on other web sites.
-Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of sceptical readers to claims that they disagree with.
-The same user may act as a sceptical reader sometimes and an activist at other times.
+For Sceptical Readers, Think Link highlights disputed snippets and links them to snippets on other web sites that present alternative points of view.
+For Activists, Think Link makes it easy for users to mark snippets about issues they care about and connect them into an argument graph.
 
@@
 
-If a sceptical reader has installed the Think Link browser extension, Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
+If a sceptical reader has installed the Think Link browser extension, Think Link will draw attention to snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
 If a user hovers their mouse over a highlighted snippet then Think Link displays a tooltip giving the disputed claim.
@@
 
+Normally Think Link will only highlight snippets that make disputed claims that the user has not asked to ignore, and snippets marked by the user themselves.
+If the user wants to see all snippets on a page then they can do so by opening the Think Link sidebar.
+
 \todo{ignore button}
 \todo{talk about the margin?}
+\todo{Talk about snippet and topic previewing}
 
@@
 In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim.
-We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left.
-If a panel describes a disputed claim (Figure~\ref{panel}), then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right.
+We thus created an interface that consists of an expanding horizontal array of panels where each panel provides information about the item that is selected in the panel to its left.
+If a user clicks on a link in a panel then a new panel opens to the right giving more information about the linked node.
 To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
@@
 Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.
+The panel for a snippet shows the snippet text in the context of the web page it is part of.
+This, combined with the cascading panel interface allows a user to quickly read the evidence for and against a claim without having to leave the claim browser interface.
+
+\todo{Remove ``related`` fom the topics list - confuses with related claims}
+\todo{Show the other panels?}
 
@@
 When used as a popup browser, the interface shows only one panel.
-Clicking on an item in the panel scrolls the display to the right to reveal a new panel in a manner similar to Apple's iPhone.
+Clicking on an item in the panel scrolls the display to the right to reveal a new panel.
 If the user clicks the ``back'' button, the interface will quickly scroll left back to the previous panel.
@@
 There are three types of node: snippets, claims, and topics.
-A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; and a topic is an issue or concept that a claim might relate to..
+A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about.
 Nodes are connected together by typed, directed, links.
@@
 
-Think Link uses topics to group together related claims.
-A topic may be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''.
-Alternatively, it can be something claims are about, for example ``Carbon Dioxide''.
-Think Link uses the list of page titles on Wikipedia as a seed-set for its topics and users can also add new topics from within the claim browser.
+Think Link uses the list of page titles on Wikipedia as a seed-set for its topics.
+This allows Think Link to use the Wikify~\cite{Mihalcea2007} algorithm to automatically suggest topics for snippets and provides us with a comprehensive ready-made set of topics with well-maintained descriptions and synonyms.
 
-Think Link's graph model is a simpler than that used by gIBIS~\cite{Conklin1987}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation.
-While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, it is sufficient for the conflict discovery and snippet organization task that Think Link's graph is intended for, and we have found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.
+Think Link's graph model is a simpler than that used by gIBIS~\cite{Conklin1987}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation.
+While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link's is designed for, and we have found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.
 
 The order in which evidence is displayed is determined by user voting.
-A user can vote for or against a particular piece of evidence by clicking on the voting button next to that item~(Figure~\ref{voting}).
-When a user looks at a list of evidence they will see first the things they voted for and then the other evidence ordered based on the number of votes it received from other users.
+A user can vote for or against a particular piece of evidence by clicking on the voting buttons next to that item~(Figure~\ref{voting}).
+When a user votes for something it will be moved to the top of their list, and also make that item earlier for other users.
 
-One danger in a voting system is that a large group of people will drown out the opinions of their opponents by voting down their opinions.
+One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions.
 Think Link uses several strategies to try to avoid this happening.
@@
 
-If a user has installed the Think Link browser extension then they can create a snippet from text on a web page by selecting the text and selecting either ``This is disputed'' or ``This is interesting'' from the context menu.
-A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted of the fact that a claim that that snippet is making or implying is disputed.
-A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be for readers investigating a disputed claim.
+If an Activist has installed the Think Link browser extension then they can create a snippet by selecting text on a web page and selecting either ``This is disputed'' or ``This is interesting'' from the context menu (Figure~\ref{createprocess}).
+A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted that the snippet is making a claim that is disputed.
+A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be useful for readers investigating a disputed claim.
 
@@
 
-Think Link does not require that a user associate a snippet with a claim at the point at which they create it.
-Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets.
-One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagrees with. 
-In this case, the user can save time by first collecting all their snippets, and then attaching all their snippets to their disputed claim in bulk.
+Think Link does not require a user to specify the disputed claim a snippet is making at the point at which they mark it.
+Instead, Think Link encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
+One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
+In this case, the user can save time by first collecting all their snippets, and then attaching all their snippets to their disputed claim together.
 
@@
 
+\todo{Updated screenshot with ``enter new claim or search keywords'' present}
+
 \begin{figure}[tb]
@@
 \item[Immediate:] A user can select a claim for a snippet that they have just marked.
-When a user marks a snippet, Think Link will initially highlight it in blue to show the user that the snippet is not currently associated with a claim or topic and will not be shown to other users.
+When a user marks a snippet, Think Link will initially highlight it in blue to show that the snippet is not currently associated with a claim or topic and will not be shown to other users.
 If the user clicks on the highlighted snippet, then Think Link will bring up the same suggestion panel used in the ``snippet first'' method.
@@
 If users create duplicate claims or don't connect their claims to existing claims then then graph becomes less useful.
-Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to enable a suggested connection with a single click.
+Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.
 
-When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim.
-It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to use it as evidence for a particular claim.
-In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for.
-In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.
+When gathering ``interesting'' snippets, a user may not yet know what argument they might want to use the snippet to support, or even whether they want to use it at all.
+In such cases the user can either leave the snippet unfiled until they thing of something to use it for, or attach it to a topic in the hope that another user might find it useful.
 
@@
 The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to.
+Connecting claims and snippets to topics makes it easier to find other claims and snippets that might be related.
 
-Even with these suggestion and bulk connection features, gathering snippets that make a disputed claim or provide useful evidence requires a non-trivial amount of work.
+\todo{Talk about previewing a topic by showing wikipedia page}
+
+Even though Think Link tries to make creating and linking snippets as easy as possible, it still requires a non-trivial amount of work.
 Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks; currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog.
-Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to be notified every time a new page appears about the issue they are interested in.
-Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashkov2006}, and so one can achive useful coverage by only marking up the relatively small number of very popular pages (for example articles on major news sites).
+Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to learn when a new page appears about an issue they are interested in.
+Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashkov2006}, and so one can achieve useful coverage by only marking up the relatively small number of very popular pages (for example major news sites).
 
@@
 
-Think Link consists of a browser extension, a page annotation script, a shared public database of contentious claims, and a web-based argument interface that allows one to explore and manipulate the claim graph.
+Think Link consists of a browser extension, a page annotation script, a shared database server, and a web-based claim browser interface.
 These four components are largely independent of each other and talk to each other using an open API that can also be used by other tools.
-Indeed the settings panel for the browser extension allows a user to tell it to bind to alternative versions of the other modules.
 
 The page annotation script is a javascript file that can be included into any HTML page.
-When it is run on a page it sends the page URL to the server, asking it to send back information about any contentious snippets on that page.
-If any such snippets are found, the page modification script highlights them in red.
-If the user clicks on a highlighted snippet then it shows an iframe containing a visualization from whatever visualization server it has been configured to use.
+When it is run on a page it sends the page URL to the server, asking it to send back any snippets on that page.
+There are of course privacy issues here since this could allow user browsing to be tracked.
+We reduce this problem a little by not sending cookies or other identifying information, and making the protocol cacheable.
+In future we hope to device a way to reduce concerns further.
+One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and then requiring a user to explicitly enable Think Link for particular sites for Think Link will request disputed snippets.
 
-The only purpose of the browser extension is to insert the page modification script onto every page that the user loads.
-The browser extension is not the only way that one can access Think Link highlights.
-One can get the same effect by browsing through a proxy (like WBI~\cite{Barrett1997}), or if the owner of a web site included the page annotation script themselves.
+The browser extension inserts the page annotation script onto every page the browser loads. One can get the same affect by browsing through a proxy or if the page included directly by the page author.
 
-Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. 
-Think Link reduces privacy issues by not sending cookies or other identifying information, and Think Link's requests can be cached by a third-party proxy if desired. 
-In future work we hope to reduce these privacy issues. One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.
-
-The protocol used by the Think Link server is an open REST API that other tools are free to use.
-We are also considering supporting one or more of the several argumentation interchange formats that have been proposed ~\cite{Rahwan2007a,McGinnis2007}.
+%The protocol used by the Think Link server is an open REST API that other tools are free to use.
+In the future, the server may support one or more of the argumentation interchange formats that have been proposed~\cite{Rahwan2007a,McGinnis2007}.
 
@@
 The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page.
-At the end of each study, we asked each partipicant whether there were times in the past where they would have wanted to use Think Link.
 We present the results of the two studies together.
@@
 For the first study we recruited twelve paid participants, five female, seven male, aged 18 to 52.
-Nine participants regularly posted to a blog.
-We recruited participants by posting an advert on craigslist\footnote{http://craigslist.org}.
+Nine participants maintained a blog.
+We recruited participants by posting an advert on Craigslist\footnote{http://craigslist.org}.
 Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas.
-In our advert, we asked people to tell us what kind of information they looked at on the web, and how they shared information with others.
+In our advert, we asked people to tell us what kind of information they looked at on the web and how they shared information with others.
 We selected participants who looked at information that was likely to be disputed (e.g.
-political commentry) and said they regularly shared information with friends.
-We avoided applications from people who were more interested in less disputed topics like social networking or sport.
-
-\todo{Get the correct number of bloggers}
+political commentry) and who said they regularly shared information with friends.
 
@@
 Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension.
-We first demonstrated Think Link's interface, and then asked them to browse web sites they normally use
-
-the web sites they normally normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph.
+We first demonstrated Think Link's interface, and then asked them to find information as they would normally and use Think Link to mark snippets that made claims that they thought were interesting or disputed.
 For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.
@@
 
-In the second study we were more confident about the usability of our tool and so we decided to tell the participants nothing about how to use it.
+In the second study we were more confident about usability and so told the participants nothing about how to use it.
 We gave each user a brief description of the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
-The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case).
+The first task was to look at a selection of web pages that already had highlighted snippets and to explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case).
 The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).
@@
 % \subsubsection{High-Level Impressions}
+
+%\todo{Do we want this section}
 % 
@@
 When the user marked a snippet, Think Link would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype).
-There turned out to be several problems with requiring that a user select a claim at the point at which they marked a snippet:
+There turned out to be several problems with this approach:
 
-Users would often encounter a snippet that could be interpreted as making several interesting claims.
-Users got confused by the need to pick only one claim.
-Some users dealt with this by writing a compound claim such as ``Global warming will cause X and Y'', while other users would mark several overlapping snippets making different claims.
+Users would often encounter a snippet that could be interpreted as making several interesting claims and were confused by the need to pick only one claim.
+Some users dealt with this by writing a compound claim such as ``Global warming will cause X and Y'', while other users marked several overlapping snippets making different claims.
 In the final interface one can associate a snippet with several claims.
@@
 For example, they might find the text of an important speech, or the results of a sporting event.
-While it is possible that they might want to use this as evidence for a claim in the future, they didn't want to have to decide what the claim was immediately.
+While they might want to use this as evidence for a claim in the future, they didn't yet know what that claim might be.
 In the final interface one can choose to associate a snippet with a topic.
@@
 Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one.
-For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information?
-In the final interface, users are expected to only create a claim when they have several snippets that make the same claim.
-This makes it easier to know how broad the claim should be as they know how much information is shared by claims.
+For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information?
+In the final interface, users are expected to only create a claim when they have several snippets that support or oppose the same claim.
+This makes it easier to know how broad the claim should be as the user knows how much information is shared by claims.
 
@@
 Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet.
-The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and have a particular disputed claim in mind.
+The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and they have a particular disputed claim in mind.
 
@@
 
-Many users would consistently mark the first paragraph of an article as a snippet.
+Users would frequently mark the first paragraph of an article as a snippet.
 This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.
@@
 
-Many participants expressed a desire to organize claims into connected arguments during their session.
+Several participants expressed a desire to connect related claims during their session.
 
-Some users marked one claim as supporting another when it would have been more logically correct to make them both as supporting a third claim that needed to be created.
+Some users marked one claim as supporting another when it would have been more logically correct to mark them both as supporting a third claim that needed to be created.
 For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing problems''.
@@
 It is possible that creating logically correct claim structures may be too difficult for some people (see Isenmann and Reuter~\cite{Isenmann1997}).
-We believe that this problem can be addressed to some extend though voting by other users who recognize that a claim does not provide useful evidence.
+We believe that this problem can be addressed to some extent though voting by other users who recognize that a claim does not provide useful evidence.
 
@@
 
-Several users expressed an interest in being able to mark a claim as controversial without having to create an opposing claim.
+Several users expressed an interest in being able to mark a claim as disputed without having to find opposing evidence.
 One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
@@
 We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and the rendering of a claim did not have any visual clue to suggest that they could use drag and drop to create connections.
-In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.
+In the final interface we resolved this issue by moving to a ``click to link'' interface and having the connection actions (``add claim'' etc) prominently visible.
 
-\section{Future Work}
+\section{Conclusions and Future Work}
+
+We have introduced the idea of highlighting disputed claims and connecting them to sources that give alternative points of view.
+We have created an interface that makes it easy for users to explore evidence that supports or opposes a claim, and makes it easy for users to gather and connect new snippets.
 
@@
 In the future we plan to explore using natural language and machine learning techniques to assist in this process.
-Our plan is to allow a user to request that Think Link present them with potential web snippets that make a claim that they disagree with, and then quickly select which of these should be highlighted as being contentious.
+Our plan is to allow a user to request that Think Link search the web to find potential snippets that make a claim that they disagree with, and then quickly select which of these are indeed making the claim.
 
@@
 
-We think it could be useful to use Think Link as a tool to suggest reading material.
-Just as tools like Digg suggest pages that you might like, Think Link could potentially suggest pages that contain claims that the user had not read and would be likely to find interesting.
-
-\section{Conclusions}
-
-We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on all sides of the issue.
-Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by web page authors.
-Users can identify snippets that make disputed pages, connect those snippets to the appropriate claims, and connect claims that relate to each other.
-
-Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then uses a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.
-
-We hope that Think Link will make it easier for people to be informed about the world and be exposed to factual claims that they might not otherwise be exposed to.
+We hope that Think Link will make it easier for people to be informed about the world and be exposed to alternative points of view that they might not otherwise be exposed to.
 

### 2009-03-30 papers/uist_thinklink/thinklink.tex

@@
 
-\title{Exposing Disputed Statements on the Web}
+\title{Exposing and Exploring Disputed Statements on the Web}
 
@@
 \abstract
-Think Link is a tool that helps users know when information they read on a the web is disputed.
-As a user browses the web, Think Link highlights snippets of text that make claims that users have identified as being disputed.
-If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against the claim the snippet is making.
+Think Link is a tool that helps users know when information they read on the web is disputed. 
+As a user browses the web, Think Link highlights snippets of text that make claims that users have identified as contentious. 
+If a user clicks on a highlighted snippet, Think Link displays an argument graph showing the best evidence for and against the claim the snippet is making.
 
 Users provide all of Think Link's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
-Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.
+Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.
 
@@
 In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. 
-If a user has installed the Think Link browser extension hen it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}).
-When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).
+If a user has installed the Think Link browser extension then it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). 
+When a user clicks on a highlighted snippet, Think Link presents an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).
 
@@
 \item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled.
-They install Think Link as a browser plugin so that it will highlight disputed claims and show them opposing points of view.
+They install Think Link as a browser extension so that it will highlight disputed claims and show them opposing points of view.
 \end{description}
@@
 	\begin{center}
-	\includegraphics[width=5cm]{../screenshots/v2_popup_dim.png}
+	\includegraphics[width=8cm]{../screenshots/v2_popup_dim.png}
 	\caption{Click on a snippet to investigate evidence for the claim it makes}
@@
 
-The design of Think Link was guided by two user studies in which we observed users' behaviour as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.
+Think Link's design was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.
 
@@
 
-Think Link builds on prior work in several different areas.
-The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}.
-The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
+Think Link builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. 
+The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
 Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information.
@@
 
-Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox plugin to help a user create a claim about a web page they are reading.
+Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox extension to help a user create a claim about a web page they are reading.
 Unlike Think Link, Cohere is not designed to be used to alert users about disputed snippets.
@@
 
-Although Think Link's argument graph is similar to that used by IBIS tools, it uses it for a different purpose.
-In Think Link the focus is on snippets, and the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim.
+Although Think Link's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
+In Think Link the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim.
 A user is expected to create a new claim only when they want to group together several snippets that make that claim. 
-A Think Link user is expected to form an opinion primarily by looking at the snippets and the pages they are part of, rather than by looking at the argument graph itself.
+A Think Link user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself.
 By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph.
@@
 Think Link's database automatically imports all contentious claims identified by Snopes.
-FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. We use Fact Check as a useful source of disputed claims.
+FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. 
+%We use Fact Check as a useful source of disputed claims.
 
@@
 Comments can include references to external sources that back up the argument being made.
-Like SpinSpotter, Videolyzer does not attempty to gather multiple video sections that make a common contentious claim.
+Like SpinSpotter, Videolyzer does not attempt to gather multiple video sections that make a common contentious claim.
 
@@
 
-The panel for a claim (Figure~\ref{panel}) lists evidence that will help a user decide whether the claim is true.
+The panel for a claim (Figure~\ref{panel}) lists evidence that will help inform the users opinion about the claim and alternative points of view.
 Evidence is categorized as either supporting, opposing, or being related-to the claim.
@@
 
-\todo{Remove ``related`` fom the topics list - confuses with related claims}
+\todo{Remove ``related`` from the topics list - confuses with related claims}
 \todo{Show the other panels?}
@@
 
-Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model.
-There are three types of node: snippets, claims, and topics.
+Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of nodes: snippets, claims, and topics. 
 A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about.
 Nodes are connected together by typed, directed, links.
-There are three link types: supports, opposes, and relates-to.
-A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.
+There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.
 
@@
 
-Think Link's graph model is a simpler than that used by gIBIS~\cite{Conklin1987}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation.
-While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link's is designed for, and we have found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.
+Think Link's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation.
+While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link is designed for.
+We have also found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.
 
@@
 A user can vote for or against a particular piece of evidence by clicking on the voting buttons next to that item~(Figure~\ref{voting}).
-When a user votes for something it will be moved to the top of their list, and also make that item earlier for other users.
+When a user votes for something it will be moved to the top of their list, and also make that item appear earlier for other users.
 
@@
 In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong.
+\todo{Talk about whether we know if this works}
 
@@
 
+The only difference between selecting ``this is disputed'' and ``this is interesting'' is that Think Link remembers which you used when you marked a snippet.
+A snippet is only highlighted in red for other users if it is connected to a disputed claim.
+The main reason for having two different options is to show users what kinds of information Think Link expects them to mark as snippets.
+\todo{Say something smart about the difference}
+
 \begin{figure}[tb]
@@
 
-Think Link does not require a user to specify the disputed claim a snippet is making at the point at which they mark it.
+Think Link does not require a user to specify the claim a snippet is making at the point at which they mark it.
 Instead, Think Link encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
 One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
-In this case, the user can save time by first collecting all their snippets, and then attaching all their snippets to their disputed claim together.
+In this case, the user can save time by first collecting all their snippets, and then attaching all the snippets to their disputed claim at the same time.
 
@@
 It is important to make sure that the argument graph stays well connected as it grows.
-If users create duplicate claims or don't connect their claims to existing claims then then graph becomes less useful.
+If users create duplicate claims or don't connect their claims to existing claims then the graph becomes less useful.
 Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.
@@
 Even though Think Link tries to make creating and linking snippets as easy as possible, it still requires a non-trivial amount of work.
-Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks; currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog.
+Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks: currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog.
 Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to learn when a new page appears about an issue they are interested in.
-Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashkov2006}, and so one can achieve useful coverage by only marking up the relatively small number of very popular pages (for example major news sites).
+Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashakov2006}, and so one can achieve useful coverage by only marking up the relatively small number of very popular pages (for example major news sites).
 
@@
 There are of course privacy issues here since this could allow user browsing to be tracked.
-We reduce this problem a little by not sending cookies or other identifying information, and making the protocol cacheable.
-In future we hope to device a way to reduce concerns further.
-One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and then requiring a user to explicitly enable Think Link for particular sites for Think Link will request disputed snippets.
+We lessen this problem by not sending cookies or other identifying information, and making the protocol cacheable.
+In the future we hope to devise a way to reduce concerns further. 
+One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and require a user to explicitly ask for Think Link to highlight snippets on a particular site.
 
@@
 We selected participants who looked at information that was likely to be disputed (e.g.
-political commentry) and who said they regularly shared information with friends.
+political commentary) and who said they regularly shared information with friends.
 
@@
 
-% \subsubsection{High-Level Impressions}
+\subsubsection{High-Level Impressions}
 
-%\todo{Do we want this section}
-% 
-% Response was generally positive, with many participants being very keen to use the tool soon.
+Response was generally positive, with many participants being very keen to use the tool soon.
 One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed.
 Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
-% 
-% Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader).
+
+Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader).
 One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
@@
 One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.
-% 
-% Most participants in the first study, and all participants in the second study were able to use the tool competently.
+
+Most participants in the first study, and all participants in the second study were able to use the tool competently.
 Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
-One participants said they found the tool ``very intuitive''.
+Participants said they found the tool ``very intuitive'' and ``really cool''.
 
@@
 
-Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they they could make the dialog go away.
+Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they could make the dialog go away. 
 Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet.
-The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and they have a particular disputed claim in mind.
+The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and have a particular disputed claim in mind.
 
@@
 The prototype versions of Think Link used a drag-and-drop interface to allow a user to create links between claims.
-In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find others claims and then drag them into appropriate positions in the argument graph.
+In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find others' claims and then drag them into appropriate positions in the argument graph.
 The second interface (Figure~\ref{secondbrowser}) followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between.

### 2009-03-31 papers/uist_thinklink/thinklink.tex
Paper changes from Tye. Fixed UI glitches revealed when running on windows

@@
 	\begin{center}
-	\includegraphics[width=5cm]{../screenshots/highlight_crop.png}
+	\includegraphics[width=6cm]{../screenshots/v2_highlight_shadow.png}
 	\caption{Think Link highlights snippets that make disputed claims}
 	\label{highlight}
+	\end{center}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{../screenshots/v2_popup_dim2.png}
+	\caption{Click on a snippet to investigate evidence for the claim it makes}
+	\label{claimview}
 	\end{center}
@@
 The same user may be an Activist for some issues and a Sceptical Reader for others.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/v2_popup_dim.png}
-	\caption{Click on a snippet to investigate evidence for the claim it makes}
-	\label{claimview}
-	\end{center}
-\end{figure}
 
@@
 FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.
+The advantage of Think Link is that it tells you when information on web sites is disputed automatically, without requiring you to suspect that information might be disputed and look for it on another site.
+
 %We use Fact Check as a useful source of disputed claims.
@@
 MediaCloud shows which different words different news sources associate with the same topic.
+Unlike Think Link, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.
 
@@
 Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
+Unlike these Wikipedia-based systems, Think Link does not use edit history to determine when text is untrustworthy; rather it relies on a community of activist users.
 
@@
 Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.
+While Think Link also allows users to organize information from other sources, it does not use tags.
 
@@
 
-Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos.
+Videolyzer~\cite{Diakopoulos2008}\footnote{http://www.videolyzer.com} allows users to annotate and comment on political videos.
 A user can attach a comment to a section of video and tag it for bias, accuracy, or rhetorical technique.
@@
 Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
+Think Link also creates new links between information, but it's links are created by users, rather than being mined automatically.
 
@@
 
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=18cm]{../screenshots/v2_panels2.png}
+	\caption{The claim graph consists of an expanding sequence of linked panels}
+	\label{panels}
+	\end{center}
+\end{figure*}
+
 Since the purpose of a highlight is to alert the user to claims that they had not realized were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious.
@@
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8.5cm]{../screenshots/v2_panels.png}
-	\caption{The claim graph consists of a series of linked panels}
-	\label{panels}
-	\end{center}
-\end{figure}
-
 Once a sceptical reader has identified a claim that they are interested in, they can use Think Link's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.
@@
 In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim.
-We thus created an interface that consists of an expanding horizontal array of panels where each panel provides information about the item that is selected in the panel to its left.
+We thus created an interface that consists of an expanding horizontal array of panels where each panel provides information about the item that is selected in the panel to its left (Figure~\ref{panels}).
 If a user clicks on a link in a panel then a new panel opens to the right giving more information about the linked node.
@@
 
-The panel for a claim (Figure~\ref{panel}) lists evidence that will help inform the users opinion about the claim and alternative points of view.
+The panel for a claim (third panel in Figure~\ref{panels}) lists evidence that will help inform the users opinion about the claim and alternative points of view.
 Evidence is categorized as either supporting, opposing, or being related-to the claim.
@@
 Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.
-The panel for a snippet shows the snippet text in the context of the web page it is part of.
+The panel for a snippet (last panel in Figure~\ref{panels}) shows the snippet text in the context of the web page it is part of.
 This, combined with the cascading panel interface allows a user to quickly read the evidence for and against a claim without having to leave the claim browser interface.
@@
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/v2_panel.png}
-	\caption{A claim panel presents information for and against a claim}
-	\label{panel}
-	\end{center}
-\end{figure}
+% \begin{figure}[tb]
+% 	\begin{center}
+% 	\includegraphics[width=6cm]{../screenshots/v2_panel.png}
+% 	\caption{A claim panel presents information for and against a claim}
+% 	\label{panel}
+% 	\end{center}
+% \end{figure}
 
@@
 If the user clicks the ``back'' button, the interface will quickly scroll left back to the previous panel.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/v2_vote.png}
-	\caption{Voting buttons let users say which evidence is important}
-	\label{voting}
-	\end{center}
-\end{figure}
 
@@
 
-Think Link's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation.
+Think Link's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to link type.
 While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link is designed for.
@@
 
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{../screenshots/v2_vote.png}
+	\caption{Voting buttons let users say which evidence is important}
+	\label{voting}
+	\end{center}
+\end{figure}
+
 One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions.
-Think Link uses several strategies to try to avoid this happening.
+Think Link uses two strategies to try to reduce this problem.
 Firstly, positive votes count for more than negative votes.
 Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent.
-Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side.
-In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong.
+Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side -- though of course they may vote up bad arguments for the opposing point of view.
+We anticipate that we will eventually need to introduce a moderation system similar to that used in Wikipedia, allowing trusted users to override popular opinion when things go wrong.
 \todo{Talk about whether we know if this works}
@@
 	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
+	\includegraphics[width=8.5cm]{../screenshots/v2_sniptopic.png}
 	\caption{Snippet first: Pick a claim or topic for each unfiled snippet}
@@
 Participants were shown the prototype interface shown in Figures~\ref{secondbrowser} and \ref{secondsnippetbox}.
-This was similar to the interface described earlier in this paper, except that it used drag and drop to make connections rather than a suggestion system, it did not offer a ``relates-to'' link between claims, and it required a user to choose a claim at the point at which they create a snippet.
+This was similar to the interface described earlier in this paper, except that it used drag and drop to make connections rather than a suggestion system, it did not offer a ``relates-to'' link between claims, it required a user to choose a claim at the point at which they create a snippet, and the claim browser only showed one panel at a time.
 
@@
 One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
-A smaller number said they would want to mark up claims they disagreed with (activist).
+A smaller number said they would be likely to mark up claims they disagreed with (activist).
 One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.
@@
 Several users got confused by claims that referred to similar events at different points in time. 
-For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written.
+For example, one participant in the first study marked two claims as opposing each other when each was true at the time that it was written.
 This is a particular problem when talking about breaking news events, where the facts can change fast.
@@
 One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
-In the future we are planning to implement a social voting system to allow users to say what claims they believe are false and see what claims their friends agreed or disagreed with.
+In the future we are planning to allow users to say what claims they personally believe are true or false and see what claims their friends agreed or disagreed with.
 
 \begin{figure}[tb]
-	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
+	\includegraphics[width=8cm]{../screenshots/oldpoint_diagram.png}
 	\caption{First Prototype Claim Browser}
@@
 \begin{center}
-	\includegraphics[width=5cm]{../screenshots/claimbrowse.png}
+	\includegraphics[width=5.5cm]{../screenshots/claimbrowse.png}
 	\caption{Second Prototype Claim Browser}
@@
 
-Acknowledgements omitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.
+Acknowledgements omitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.
 

### 2009-03-31 client_js/tl_margin.js

@@ -379,7 +379,7 @@ function tl_margin()
 					that.setHighlightClass(snippet,true);
 					var div = document.createElement("div");
 					if (snippet.claimid && snippet.opposed){
-						div.innerHTML = "<span class='tl_claim_warn'>contentious claim: "+
+						div.innerHTML = "<span class='tl_claim_warn'>disputed claim: "+
 								"</span><span class='tl_claim_text'>"+
 								snippet.claimtext+"</span><span class='tl_claim_click'>"+
 								"(click snippet for more info)</span>";

### 2009-05-20 papers/uist_thinklink/uist_rebuttal.txt
Signup by email. Trying out facebook connect. More panels on front page. Save Turk results.

The users were primarily concerned with two issues: (i) a perceived lack of novelty (primarily reviewer 1), (ii) worries about bootstrapping

= Novelty =

While web annotation systems are old hat, as reviewer 1 stated: "[Think Link] appears to be the first work to make use of Open Hypermedia for identifying disputed statements on the web"

You could of course use an existing, less structured, annotation system to mark disputed information: either insert a comment saying that you disagree with something, or insert a link to conflicting information.

The key contribution of Think Link is that, by imposing additional structure on annotations, it provides a better experience for finding and marking disputed information. In particular:

* Since Think Link knows when snippets are making the same claim, a user can ask to not be notified about a particular claim again - seeing many annotations about the same claims would be annoying.

* Since Think Link links to an argumentation graph rather than an arbitrary web page, a link will always give a user whatever the community believes to be the best evidence for or against a claim, rather than what a particular user liked.

* Think Link reduces "noise" by not allowing users to add arbitrary text to a page, only allowing a user to link to a structured claim node, and using voting to determine what claims and snippets are actually worth showing to users.

* Think Link makes it easy for a user to mark many snippets that make the same same claim "in bulk" and suggests claims and topics.

= Bootstrapping =

Bootstrapping is an important challenge for a tool such as Think Link and something we could discuss in more depth.

Our set of claims has been bootstrapped by important lists of disputed claims from several existing web sites. Currently we have Snopes and a couple of debate-focussed websites. We also have a task on Amazon Mechanical Turk to tell us more disputed claims.

Our set of snippets has been bootstrapped by using a task on Amazon Mechanical Turk. Turk users are presented with a list of candidate snippets for a claim and asked to tell us which snippets are indeed making the claim. The candidate snippets come from a Yahoo BOSS search. We have found that users will mark up 10 snippets for only 2 cents - allowing us to build data sat very quickly provided

Our connections between claims are currently entered entirely manually, but in future we plan to bootstrap that using mechanical turk too.

Reviewer 5 was concerned that, since a web page saying global warming did not exist was less popular, it would be less likely to be marked than one that said it did exist. In fact the converse is true. Since there are more activists who believe that global warming exists, more people will use search engines to find and highlight pages that say global warming does not exist, and thus such pages are more likely to be highlighted.

### 2009-05-20 papers/uist_thinklink/uist_rebuttal_v2.txt
Signup by email. Trying out facebook connect. More panels on front page. Save Turk results.

Reviewers were primarily concerned with two issues: (i) a perceived lack of noverty WRT previous annotation systems and (ii) bootstrapping. We believe that we could easily address both issues with revisions to the paper.

= Novelty =

As reviewer 1 stated: "[Think Link] appears to be the first work to make use of Open Hypermedia for identifying disputed statements on the web".

One could of course use a general-purpose annotation system to do this: if you disagree with something then highlight it, add a comment, or link to opposing evidence.

However this approach raises several issues: Pages could get crowded with noisy "this sucks" comments, users could get frustrated by being told about things they already knew were disputed, and links would not necessarily go to the most useful evidence.

Think Link tries to address these issues by enforcing more structure. A user cannot add an arbitrary comment to a page - instead they must link a snippet to a community-curated claim. A user cannot link a snippet directly to opposing evidence - instead they can add evidence to a claim and hope that the community votes their evidence up.

This structured approach has several user-visible advantages:

* If a user knows something is disputed then they can ask Think Link to not highlight any snippet that makes this claim again.

* Think Link presents the best evidence as voted for by the community, rather than the favorite link chosen by a single user. Similarly, crowdsourcing is used to filter out low quality claims and snippets

* The argumentation graph allows users to see how a claim fits into a larger argument

* Think Link makes it easy for an activist user to rapidly mark many snippets that make the same claim that they disagree with. A common usage model is to Google a sentence, tab-open all pages that look relevant, quickly highlight a relevant snippet in each page, and then bulk-assign all such snippets to the same disputed claim.

= Bootstrapping =

A final version would talk more about bootstrapping.

Our claims are seeded from lists of disputed claims on several websites, including Snopes and several smaller debate web sites. We use Mechanical Turk to produce a seed-set of snippets (4 cents per 10 snippets).

= Misc =

Reviewer 5 was concerned that, since a web page saying global warming did not exist was less popular, it would be less likely to be marked than one that said it did exist. In fact the converse is true. Since there are more activists who believe that global warming exists, more people will use search engines to find and highlight pages that say global warming does not exist, and thus such pages are more likely to be highlighted.

We intend to include a link to several videos in the paper.

Yes, the figures should be bigger.

Think Link does not use IBIS. Our argument graph is simpler than IBIS, but we compare to it since readers may be familiar with it.

### 2009-05-20 scala/src/com/intel/thinkscala/Datastore.scala

@@ -61,13 +61,46 @@ class Datastore {
   def stmt(s : String) = new SqlStatement(con,s)
   def mkinsert(table : String, fields : String*) = SqlStatement.mkInsert(con,table,fields)
 
-  val get_user = stmt("SELECT id,password,name FROM v2_user WHERE email = ?")
+  val get_user = stmt("SELECT id,password,name FROM v2_user WHERE email = ? AND nonce = 0")
   def getUser(email : String, password : String) : User = 
     get_user.queryMaybe(email) match {
       case Some(row) if row("password") == password => 
         new User(row.str("name"),row.int("id"))
       case _ => User.nouser
     }  
+  
+  val create_user = stmt("INSERT INTO v2_user (email,name,password,nonce) VALUES (?,?,?,?)")
+  def createUser(email : String,name : String,password : String) : (Int,Int) = {
+    import java.util.Random
+    val nonce : Int = new Random nextInt
+    val userid = create_user.insert(email,name,password,nonce)
+    return (userid,nonce)      
+  }                      
+  
+  val email_registered = stmt("SELECT id FROM v2_user WHERE email = ?")
+  def emailRegistered(email : String) = 
+	  email_registered.queryMaybe(email) match {
+	    case Some(_) => true
+	    case _ => false
+	  }
+
+  val name_registered = stmt("SELECT id FROM v2_user WHERE name = ?")
+  def nameRegistered(name : String) = 
+	  name_registered.queryMaybe(name) match {
+	    case Some(_) => true
+	    case _ => false
+	  }
+
+  
+  val check_confirm_user = stmt("SELECT * FROM v2_user WHERE id = ? AND nonce = ?")
+  val confirm_user = stmt("UPDATE v2_user SET nonce = 0 WHERE id = ?")
+  def confirmUser(userid : Int, nonce : Int) = {
+    check_confirm_user.queryMaybe(userid,nonce) match {
+      case Some(_) => confirm_user.update(userid); true
+      case _ => false                                                                                                
+    }
+  }
+                         
   
   val get_user_info = stmt("SELECT * FROM v2_user WHERE id = ?")
   def getUserInfo(id : Int) = get_user_info.queryOne(id)
@@ -87,6 +120,14 @@ class Datastore {
   val log_recent = stmt("REPLACE DELAYED INTO v2_history (user_id,node_id,date) VALUES (?,?,CURRENT_TIMESTAMP)")
   def logRecent(userid : Int, nodeid : Int) = log_recent.update(userid,nodeid)
  
[…]

### 2009-05-20 scala/src/com/intel/thinkscala/Facebook.scala

@@ -1,0 +1,9 @@
+package com.intel.thinkscala
+
+
+
+object Facebook {
+	val key = "9a300c9b0d241b501002440468ad4c40"
+	
+  
+}

### 2009-05-20 scala/src/com/intel/thinkscala/MainServlet.scala

@@ -2,15 +2,22 @@ package com.intel.thinkscala
 import javax.servlet.http._
 import java.io._
 import com.intel.thinkscala.Util._
+import com.intel.thinkscala.util._
 import com.intel.thinkscala.view._
 import scala.xml._
 import com.intel.thinkscala.view.Template
+
+object FixedUrls {
+  val base = "http://factextract.cs.berkeley.edu/thinklink"
+  def confirmUser(id : Int, nonce : Int) = base + "/confirm?userid="+id+"&nonce="+nonce 
+}
 
 object Urls {
   val base = "/thinklink"
   val home = base
   val login = base+"/login"
   val logout = base+"/logout"
+  val signup = base+"/signup"
   val search = base+"/search"
   def profile(id : Any) = base + "/user/"+id
   def claim(id : Any) = base + "/claim/"+id
@@ -63,6 +70,23 @@ class MainServlet extends HttpServlet {
       }else{
         c.outputHtml("Login Failed - Please Try Again",Page.login("Login Failed"))
       }
+    }),
+    UrlHandler("/signup", c => {
+      val email = c.arg("email")
+      val name = c.arg("name")      
+      if(c.store.emailRegistered(email)){
+        c.outputHtml("An account already exists with this email address",Page.emailregistered)
+      }else if(c.store.nameRegistered(name)){
+    	c.outputHtml("An account already exists with this email address",Page.nameregistered)
+      }else{
+          val (userid,nonce) = c.store.createUser(email,name,c.arg("password"))
+	      try{
+	    	  SendMail.sendSignup(email,name,userid,nonce)
+	    	  c.outputHtml("Confirmation Email Sent",Page.sentconfirm)
+	      }catch{
+	        case _ => c.outputHtml("Could Not Send Mail",Page.badmail)
+	      }
+       }
     }),
     UrlHandler("/claim/new", c => {
       val name = c.arg("name")
@@ -161,6 +185,18 @@ class MainServlet extends HttpServlet {
     }),   
     UrlHandler("/login",c => {
       c.outputHtml("Login",(<div>{Page.login("Login")}</div>))
+    }),
+    UrlHandler("/signup",c => {
+      c.outputHtml("Sign up with Think Link",Page.signup)      
+    }),
+    UrlHandler("/confirm",c => {
+      val nonce = c.argInt("nonce")
+      val userid = c.argInt("userid")
+      if(c.store.confirmUser(userid,nonce)){
[…]

### 2009-05-20 scala/src/com/intel/thinkscala/UrlHandler.scala

@@ -47,6 +47,8 @@ class ReqContext(val store : Datastore, m : Match, req : HttpServletRequest, res
   
   def modifiedUrl(key : String, value : Any) = mkUrl("/thinklink"+path,params.update(key,value))  
   
+  def modifiedUrl(changes : (String,Any)*) = mkUrl("/thinklink"+path,params ++ changes)
+  
   def output(obj : Any) {
     res.setContentType("text/html; charset=UTF-8") // TODO: set this correctly
     val writer = res.getWriter

### 2009-05-20 scala/src/com/intel/thinkscala/Util.scala

@@ -174,10 +174,10 @@ object Util {
     return lines
   }
   
-  def parseCsvFile(filename : String) : ArrayBuffer[Map[String,String]] = {
+  def parseCsvFile(filename : String) : ArrayBuffer[HashMap[String,String]] = {
     val rows = parseCsvRows(filename)
     val header = rows(0)
-    val result = new ArrayBuffer[Map[String,String]]();
+    val result = new ArrayBuffer[HashMap[String,String]]();
     for(i <- 1 until rows.length){
       val item = new HashMap[String,String]
       for(j <- 0 until rows(i).length){

### 2009-05-20 scala/src/com/intel/thinkscala/turk/MakeTurkCSV.scala

@@ -6,6 +6,8 @@ import scala.collection.mutable.HashMap
 import java.io.FileWriter
 
 object MakeTurkCSV {
+  val filename = "v4_hoaxes"
+  
   val store = Pool.get
 
   // questions per task
@@ -15,7 +17,7 @@ object MakeTurkCSV {
 //    (n => List("front","snip","back") map (v => v+n)))
   
   val cols = List("claim") ++ ((1 to PERTASK) flatMap 
-    (n => List("snip") map (v => v+n)))
+    (n => List("snip","url","title","searchtext") map (v => v+n)))
 
                                     //  def splitContext(context : String, snip : String) : (String,String) = {
 //    val startpos = context indexOf snip
@@ -43,6 +45,10 @@ object MakeTurkCSV {
 //      thisreq("front"+nthitem) = front
 //      thisreq("back"+nthitem) = back
       thisreq("snip"+nthitem) = r.str("abstract")        
+      thisreq("url"+nthitem) = r.str("url")
+      thisreq("title"+nthitem) = r.str("title")
+      thisreq("searchtext"+nthitem) = r.str("searchtext")
+      thisreq("position"+nthitem) = r.int("position").toString
       nthitem+=1
     })
     return turkdata
@@ -51,11 +57,12 @@ object MakeTurkCSV {
   def mkFileName(claim : String) = "/home/rob/git/thinklink/turk/input/"+claim+".csv"
   
   def main(args : Array[String]){
+    val outfile = new FileWriter(mkFileName(filename))
     val requests = GenerateTurkData.requests
     requests.foreach(req => {
       val turkdata = makeWorkUnits(req.claim)
-      val outfile = new FileWriter(mkFileName("newbatch_"+req.claim))
       outfile.write(printCSV(turkdata,cols))
     })
+    outfile.close()
   }
 }

### 2009-05-20 scala/src/com/intel/thinkscala/util/SendMail.scala

@@ -1,0 +1,36 @@
+package com.intel.thinkscala.util
+import java.io._
+import java.net._
+import javax.mail._
+import javax.mail.internet._
+
+object SendMail {
+	def sendMail(to : String, subject : String, text : String){
+	  val props = System.getProperties
+      props.put("mail.smtp.host","localhost")
+	  val session = Session.getDefaultInstance(props,null)
+	  val msg = new MimeMessage(session)
+	  msg.setFrom(new InternetAddress("thinklink@factextract.cs.berkeley.edu"))
+	  msg.setRecipients(Message.RecipientType.TO, to)
+	  msg.setSubject(subject)
+	  msg.setText(text)
+	  Transport.send(msg)
+	}
+
+	def main(args : Array[String]){
+	  sendMail("rob.ennals@gmail.com","Testing Java Mail","Hello Hello Hello")
+	}
+ 
+	def sendSignup(email : String,name : String,id : Int,nonce : Int){
+	  var body = 
+      "Hi "+name+",\n\n"+
+      "Thank you for signing up for an account with Think Link.\n"+
+      "To confirm your account, please click this link:\n"+
+      FixedUrls.confirmUser(id,nonce) +
+      "\n\n"+
+      "Thank you for signing up with Think Link\n"
+     
+	  sendMail(email,"Please confirm your Think Link account",body)
+	}
+	
+}

### 2009-05-20 scala/src/com/intel/thinkscala/view/Page.scala

@@ -10,7 +10,7 @@ object Page {
     <div class="content">
       <h1 class="logo">Think Link</h1>
       <div class="tagline">Are you being duped?</div>
-      <a class="install" href="http://confront.intel-research.net/thinklink.xpi">Install The Think Link Firefox Extension</a> 
+      <a class="install" href="https://addons.mozilla.org/en-US/firefox/addon/11712">Install The Think Link Firefox Extension</a> 
       <div class="message">{Messages.pitch}</div>
 
       <form id="bigsearch" action="search" method="GET">        
@@ -19,8 +19,12 @@ object Page {
       </form>
       <div id="claimlist">
         {Widgets.tabs(
-          "Hot Claims" -> (() => c.store.getFrequentClaims flatMap Render.claim),
-          "Hot Topics" -> (() => c.store.getBigTopics flatMap Render.topic)
+          "Hot Claims" -> (() => 
+            	Widgets.pagedList(c.store.getFrequentClaims(_).toSeq flatMap Render.claim)),
+          "Hot Topics" -> (() => 
+                Widgets.pagedList(c.store.getBigTopics(_).toSeq flatMap Render.topic)),
+          "Recently Marked Pages" -> (() => 
+                  Widgets.pagedList(c.store.recentMarkedPages(_).toSeq flatMap Render.markedPage))
         )}
       </div>
   </div>
@@ -141,15 +145,102 @@ object Page {
   def login(title : String) =
     <div class="content">
     	<h1>{title}</h1>
-	    <form id="login" action="login" method="POST">
+	    <form class='form' id="login" action="login" method="POST">
 		    <div class="message">
-		      Enter the email address and password that you used to register with Think Link
+		      Enter the email address and password that you used to register with Think Link.
 		    </div>		
+		    <div class='message'>
+              If you don't have a Think Link account then <a href={Urls.signup}>sign up</a>
+            </div>
 	        <p><label for="email">email</label><input type="text" id="email" name="email"/></p>
 	        <p><label for="password">password</label><input type="password" id="password" name="password"/></p>
-	        <input type="submit" value="Login"/>
+	        <input class='submit' type="submit" value="Login"/>
 	    </form>
     </div>
+    
+    // TODO: sign up with facebook connect
+  def signup = 
+    <div class='content'>
+    	<h1>Sign up for a Think Link Account</h1>
+           <p>Reasons to sign up for a Think Link account:
+             <ul>
+               <li>Add new claims to Think Link</li>
[…]

### 2009-05-20 scala/src/com/intel/thinkscala/view/Render.scala

@@ -45,6 +45,7 @@ object Render {
 	         <a class="user" href={Urls.profile(c.user.userid)}>{c.user.name}</a>
 	         <a class="logout" href={Urls.logout}>logout</a>
 	     else
+             <a class="signup" href={Urls.signup}>sign up</a>
 	         <a class="login" href={Urls.login}>login</a>           
 	    }
 	    <form class="searchbox" action={Urls.search} method="GET">
@@ -107,6 +108,13 @@ object Render {
   
   def topicref(row : SqlRow) = 
     <a href={Urls.topic(row.int("id"))}>{row("text")}</a>
+    
+  def markedPage(row : SqlRow) = 
+    <div class='claim'>
+       <a class='title' href={row.str("url")}>{row("title")}</a>
+       <a class='url' href={row.str("url")}>{Util.trimString(row.str("url"),80)}</a>
+       <div class='says'>says that <a class='claimlink' href={Urls.claim(row("claimid"))}>{row("claimtext")}</a></div>
+    </div>
 }      
 
 
@@ -122,7 +130,7 @@ object Images {
 object Messages {
   val pitch = <p>
     Discover when information you read on the web is disputed.
-    Install the <a href="/thinklink/extension">Firefox browser extension</a> to have Think Link
+    Install the <a href="https://addons.mozilla.org/en-US/firefox/addon/11712">Firefox browser extension</a> to have Think Link
     highlight disputed claims on pages you read.  
     </p>
 }

### 2009-05-21 papers/uist_thinklink/uist_rebuttal_v2.txt
Various bug fixes, following on from marketting meeting

@@
-Reviewers were primarily concerned with two issues: (i) a perceived lack of noverty WRT previous annotation systems and (ii) bootstrapping.
+Reviewers were primarily concerned with two issues: (i) a perceived lack of novelty WRT previous annotation systems and (ii) bootstrapping.
 We believe that we could easily address both issues with revisions to the paper.
@@
 
-* Think Link presents the best evidence as voted for by the community, rather than the favorite link chosen by a single user.
-Similarly, crowdsourcing is used to filter out low quality claims and snippets
+* Think Link presents the best evidence as voted for by the community, rather than the favourite link chosen by a single user.
+Similarly, crowd-sourcing is used to filter out low quality claims and snippets
 

### 2009-05-21 firefox_plugin/chrome/content/marker.js

@@ -15,6 +15,8 @@ function get_api_path(){
 	return apipath;
 }
 
+var global_marked = false;
+
 function mark_snippets(doc){
 	tl_log("mark snippets");
 	var targeturl = doc.location.href;
@@ -23,6 +25,7 @@ function mark_snippets(doc){
 	tl_log(url);
 	ajaxRequest(url,function(snippets){
 		tl_log("received "+snippets.length+" snippets");
+		global_marked = false;
 		for(var i = 0; i < snippets.length; i++){
 			var snip = snippets[i];
 			tl_log(snip.text);
@@ -34,7 +37,12 @@ function mark_snippets(doc){
 			}
 		}
 		if(snippets.length > 0){
-			showMessage("This page contains disputed claims (highlighted in pink)",doc);
+			if(global_marked == true){
+				showMessage("This page contains disputed claims (highlighted in pink)",doc);
+			}else{
+				// TODO: cope better when can't find disputed claim
+				showMessage("This url was tagged with disputed claims, but we can't find them on the page anymore",doc);
+			}
 		}
 	})
 }
@@ -82,6 +90,7 @@ function mark_snippet(text,claimid,claimtext,node){
 		node.parentNode.addEventListener("click",function(){
 			viewClaim(claimid);
 		},true);
+		global_marked = true;
 	}else{
 		for(var i = 0; i < node.childNodes.length; i++){
 			var child = node.childNodes[i];
@@ -126,7 +135,7 @@ function addFader(viewframe){
 
 function viewClaim(id) {
 	var apipath = get_api_path();
-	viewFrame(apipath+"/node/"+id);
+	viewFrame(apipath+"/mini/claim/"+id);
 }
 
 function viewFrame(url) {
@@ -149,7 +158,7 @@ function viewFrame(url) {
 	win.style.position = "fixed";
 	win.style.top = "50px";
 	win.style.left = "200px";
-	win.style.width = "435px";
+	win.style.width = "458px";
 	
 	var titleBar = doc.createElement("div");
 	win.appendChild(titleBar);
@@ -166,16 +175,16 @@ function viewFrame(url) {
 	buttonBox.style.right = "4px";
 	titleBar.appendChild(buttonBox);
 	
-	var ignoreButton = doc.createElement("input");
-	ignoreButton.className = "tl_openbutton";
-	ignoreButton.setAttribute("type","button");
-	ignoreButton.setAttribute("value","Don't highlight again");
[…]

### 2009-05-21 firefox_plugin/chrome/content/thinklink.js

@@ -107,6 +107,15 @@ var thinklink_winlistener = {
 };
 
 
+function thinklink_setCookie(url,name,value){
+	var ios = Components.classes["@mozilla.org/network/io-service;1"].getService(Components.interfaces.nsIIOService);   
+	var uri = ios.newURI(url, null, null);
+	var cookies = Components.classes["@mozilla.org/cookieService;1"].getService(Components.interfaces.nsICookieService);
+
+	cookies.setCookieString(uri, null, name+"="+value+";",null)
+}
+
+
 function thinklink_setCookieWithPaths(cookieSvc,cookieUri,name,value,path){
   cookieSvc.setCookieString(cookieUri, null, name+"="+value+"; path=/node", null);
   cookieSvc.setCookieString(cookieUri, null, name+"="+value+"; path=/scripthack", null);
@@ -166,9 +175,28 @@ function autoLogin(){
 	}
 }
 
+
 window.addEventListener("load", function(){
+	thinklink_setCookie("http://factextract.cs.berkeley.edu/","extension","true");
+	thinklink_setCookie("http://localhost:8180/","extension","true");
 	window.addEventListener("DOMContentLoaded",function(ev){
 		thinklink_getLogin();
 		mark_snippets(ev.target);
 	},false);
 },false);
+
+//window.addEventListener("load", function(){
+	//var appcontent = document.getElementById("appcontent")
+	//var tabcontent = document.getElementById("content")
+	//if(!appcontent && tabcontent){
+		//appcontent = tabcontent.parentNode;	
+	//}
+
+	//thinklink_setCookie("http://factextract.cs.berkeley.edu/","extension","true");
+	//thinklink_setCookie("http://localhost:8180/","extension","true");
+	//appcontent.addEventListener("DOMContentLoaded",function(ev){
+		//thinklink_getLogin();
+		//var doc = ev.target.defaultView.content.document;
+		//mark_snippets(doc);
+	//},false);
+//},false);

### 2009-05-21 scala/src/com/intel/thinkscala/Datastore.scala

@@ -42,7 +42,7 @@ class User(val name : String, val userid : Int){
 }
 
 object User {
-  val autoimport = new User("autoimport",0)
+  val autoimport = new User("autoimport",2)
   val nouser = new User("no user",0)
   val turk = new User("turk",2)
 }
@@ -72,7 +72,7 @@ class Datastore {
   val create_user = stmt("INSERT INTO v2_user (email,name,password,nonce) VALUES (?,?,?,?)")
   def createUser(email : String,name : String,password : String) : (Int,Int) = {
     import java.util.Random
-    val nonce : Int = new Random nextInt
+    val nonce : Int = Math.abs(new Random nextInt)
     val userid = create_user.insert(email,name,password,nonce)
     return (userid,nonce)      
   }                      
@@ -92,11 +92,11 @@ class Datastore {
 	  }
 
   
-  val check_confirm_user = stmt("SELECT * FROM v2_user WHERE id = ? AND nonce = ?")
-  val confirm_user = stmt("UPDATE v2_user SET nonce = 0 WHERE id = ?")
-  def confirmUser(userid : Int, nonce : Int) = {
-    check_confirm_user.queryMaybe(userid,nonce) match {
-      case Some(_) => confirm_user.update(userid); true
+  val check_confirm_user = stmt("SELECT * FROM v2_user WHERE nonce = ?")
+  val confirm_user = stmt("UPDATE v2_user SET nonce = 0 WHERE nonce = ?")
+  def confirmUser(nonce : Int) = {
+    check_confirm_user.queryMaybe(nonce) match {
+      case Some(_) => confirm_user.update(nonce); true
       case _ => false                                                                                                
     }
   }
@@ -132,6 +132,7 @@ class Datastore {
                                    "FROM v2_searchresult, v2_searchurl, v2_node "+
                                    "WHERE v2_searchurl.id = url_id "+
                                    "AND v2_node.id = v2_searchresult.claim_id "+
+                                   "AND v2_searchresult.state = 'true' "+
                                    "ORDER BY searchdate DESC LIMIT 20 OFFSET ?")
   def recentMarkedPages(page : Int) = recent_marked_pages.queryRows(page * 20)
   

### 2009-05-21 scala/src/com/intel/thinkscala/turk/CheckTurkData.scala

@@ -11,7 +11,7 @@ class User(val id : String, val total : Int, val agree : Int, val disagree : Int
 
 
 object CheckTurkData { 
-  val filename = "/home/rob/git/thinklink/turk/output/carbon_dioxide_warming.csv"
+  val filename = "/home/rob/git/thinklink/turk/output/hoaxes.csv"
 
   def main(args : Array[String]){
     val rows = Util.parseCsvFile(filename)

### 2009-05-21 scala/src/com/intel/thinkscala/turk/StoreTurkResults.scala

@@ -7,7 +7,7 @@ import scala.util.Sorting
 import Util._
 
 object StoreTurkResults { 
-  val filename = "/home/rob/git/thinklink/turk/output/carbon_dioxide_warming_expanded.csv"
+  val filename = "/home/rob/git/thinklink/turk/output/hoaxes.csv"
   
   val store = Pool.get
   

### 2009-05-21 scala/src/com/intel/thinkscala/view/Mini.scala

@@ -2,6 +2,49 @@ package com.intel.thinkscala.view
 import com.intel.thinkscala._
 
 object Mini {
+  def claim(row : SqlRow)(implicit c : ReqContext) =
+    <div class="minicontent">
+      <h1>Disputed Claim:</h1>
+      <div><a class='minititle' target="_blank" href={Urls.claim(row("id"))}>{row("text")}
+      <img src={Urls.img("application_go")}/>
+      </a></div>
+      
+      {Widgets.tabs(
+          "Opposing Evidence" -> (() =>
+	  	      <div class='evidence' id="opposed">
+		        <h2>Opposing Evidence</h2>
+	            {c.store.evidence(row.int("id"),"opposes") flatMap Render.snippet}
+	            <a class='add' target="_blank" href={Urls.addevidence(row.int("id"),"opposes")}>add opposing evidence</a>
+		      </div>
+            ),
+          "Supporting Evidence" -> (() =>
+	   	      <div class='evidence' id="supports">
+		        <h2>Supporting Evidence</h2>
+	            {c.store.evidence(row.int("id"),"supports") flatMap Render.snippet}
+	            <a class='add' target="_blank" href={Urls.addevidence(row.int("id"),"supports")}>add supporting evidence</a>
+		      </div>
+            )
+//          "Related Claims" -> (() => 
+//		      <div id="related-claims">
+//		        <h2>Related Claims</h2>
+//		            {c.store.linkedEitherAnyNodes(row.int("id"),"claim",0,4) flatMap Render.claim}
+//		      </div>            
+//            ),
+//          "Topics" -> (() => 
+//              <div id="minitopics">
+//		        <h2>Topics</h2>
+//		        {c.store.linkedToNodes(row.int("id"),"about","topic",0,10) flatMap Render.topicref}
+//		      </div>
+//            ),
+//          "Instance" -> (() =>
+//             <div id="instances">
+//               <span>seen <span class="count">{row("instance_count")}</span> times on the web
+//               	<a target="_blank" href={Urls.findsnippets(row("id"))}>find more</a></span>
+//             </div>
+             )
+         }
+  </div>
+  
   def newsnippet(text : String, url : String, title : String, disputed : Boolean, query : String)(implicit c : ReqContext) =
     <div class="minicontent">
       {if(disputed)
@@ -47,7 +90,7 @@ object Mini {
      
    def createNewClaim(implicit c : ReqContext) = 
      <div>
[…]

### 2009-05-21 scala/src/com/intel/thinkscala/view/Page.scala

@@ -10,7 +10,6 @@ object Page {
     <div class="content">
       <h1 class="logo">Think Link</h1>
       <div class="tagline">Are you being duped?</div>
-      <a class="install" href={Urls.extension}>Install The Think Link Firefox Extension</a> 
       <div class="message">{Messages.pitch}</div>
 
       <form id="bigsearch" action="search" method="GET">        
@@ -73,9 +72,7 @@ object Page {
       </div>
       <div class="description">{row("description")}</div>
       {userref(row.int("user_id"),row.str("username"),"found by ")}
-      <span class="agree"><span class="count">{row("agree_count")}</span> agree</span>
-      <span class="disagree"><span class="count">{row("disagree_count")}</span> disagree</span>    
-      <div id="evidence">
+      <div class="evidence">
    	      <div id="opposed">
 	        <h2>Opposing Evidence</h2>
             {c.store.evidence(row.int("id"),"opposes") flatMap Render.snippet}
@@ -164,7 +161,7 @@ object Page {
     <div class="error">
     </div>
     
-  def login(title : String) =
+  def login(title : String, path : String) =
     <div class="content">
     	<h1>{title}</h1>
 		<div class="message">
@@ -174,6 +171,7 @@ object Page {
           If you don't have a Think Link account then <a href={Urls.signup}>sign up</a>
         </div>
 	    <form class='form' id="login" action="login" method="POST">	   
+            <input class='hidden' type='hidden' name='url' value={path}/>
 	        <label for="email">email</label>
 	        {Widgets.greyInput(null,"email","Enter the email address you signed up with")}
 	        <p><label for="password">password</label>
@@ -235,7 +233,7 @@ object Page {
        <div class='message'>
          Your account has been successfully confirmed. 
        </div>
-       <div class='message'><a href={Urls.login}>login</a> with your new account.</div>
+       <div class='message'><a href={Urls.login(Urls.base)}>login</a> with your new account.</div>
     </div>
     
   // TODO: support retreiving or changing existing password

### 2009-05-26 papers/uist_thinklink/uist_rebuttal_v3.txt
Markers update after adding stuff. Stipped out dead code. Moved UTF8 into server config. Fixed Turk bug. Adding stuff from plugin now works

There are two key ways we would improve a final draft of this paper: (i) Make it clearer why extra structure makes Think Link work better than a general annotation system for this task and (ii) explain our approach to bootstrapping in more detail.

We will also be happy to address the other helpful suggestions, such as making the figures larger.

= Why additional structure is important =

As reviewer 1 stated: "[Think Link] appears to be the first work to make use of Open Hypermedia for identifying disputed statements on the web".

One could of course use a general-purpose annotation system for this purpose. You could highlight disputed statements, write comments saying things were disputed, and provide links to things you thought were useful evidence.

Think Link is a more specialized tool. Rather than allowing a user to highlight, comment, or link in arbitrary ways, Think Link only permits a user to link a snippet to a claim, link a claim to evidence, link a claim to a related claim, or vote on the quality of links provided by other users.

We believe that this more structure approach provides a significantly improved user experince. In particular:

* Since Think Link knows what claim each snippet is making, Think Link can avoid highlighting disputed claims that the user already knows about.

* When a user clicks on a highlighted claim, they see the best evidence for and against that claim, as determined by the votes of the entire community - rather than the favourite link of use user.

* The argumentation links allow a user to see how a claim fits into a larger argument.

* Voting allows Think Link to filter out lower quality claims/links/snippets and focus on ones the community judged to be more important.

* Think Link makes it easily for an activist user to rapidly mark many snippets that make the same claim that they disagree with. A common usage model is to Google a disputed claim, tab-open all pages that look relevant, quickly highlight a relevant snippet in each page, and then bulk-assign all such snippets to the same disputed claim.

= Bootstrapping =

Bootstrapping is very important for a tool like Think Link. If it does not have a good chance of highlighting pages that the user look it, users will get bored of it.

We have been building a large database of disputed claims by crawling lists of disputed claims from other websites such as Snopes and several political debate web sites. We then use Amazon Mechanical Turk to mark large numbers of snippets for known claims - paying 4 cents per 10 snippets.

Some topics are already very well covered. E.g. we think it would be very difficult for a user to find a page that argued global warming does not exist and that is not highlighted by Think Link.

### 2009-05-26 scala/src/com/intel/thinkscala/Util.scala

@@ -19,9 +19,9 @@ object Util {
   
  def encode(claim : String) = URLEncoder.encode(claim,"UTF-8")
  def decode(claim : String) = URLDecoder.decode(claim,"UTF-8")
- 
+  
  def mkUrl(path : String, args : Map[String,Any]) = 
-    path + (args map {case (key,value) => key + "=" + encode(value.toString)}).mkString("?","&","")  
+    path + (args map {case (key,value) => key + "=" + encode(com.intel.thinklink.Util.toUTF8(value.toString))}).mkString("?","&","")  
 
  
  def readToString(reader : BufferedReader) : String = {

### 2009-05-26 scala/src/com/intel/thinkscala/turk/MakeTurkCSV.scala

@@ -6,7 +6,7 @@ import scala.collection.mutable.HashMap
 import java.io.FileWriter
 
 object MakeTurkCSV {
-  val filename = "v4_hoaxes"
+  val filename = "v4_tye_first"
   
   val store = Pool.get
 

### 2009-05-26 scala/src/com/intel/thinkscala/view/Mini.scala

@@ -47,18 +47,31 @@ object Mini {
   
   def newsnippet(text : String, url : String, title : String, disputed : Boolean, query : String)(implicit c : ReqContext) =
     <div class="minicontent">
-      {if(disputed)
+      <form id='newsnippet' action={MiniUrls.newsnippet} method="POST">        
+     {if(disputed)
         <h1>What claim is this snippet making?</h1>
       else
-        <h1>What claim is this evidence for?</h1>
-      }
-        {Widgets.tabs(
-          "Suggested Claims" -> (() => searchForClaims(query)),
-          "Recent Claims" -> (() => 
-            	<div id='claimlist'>{c.store.getRecentClaims(c.userid) flatMap claimButton}</div>),
-          "Create New Claim" -> (() =>
-                createNewClaim)
-        )}
+        (<div><h1>What claim is this evidence for?</h1>
+        This evidence <select name="rel">
+            <option selected={if(c.arg("rel")=="opposes") "selected" else null}>opposes</option>
+            <option selected={if(c.arg("rel")=="supports") "selected" else null}>supports</option>
+       </select> the claim:</div>)     
+     }  
+        <input type='hidden' name='text' value={c.arg("text")}/>
+        <input type='hidden' name='title' value={c.arg("title")}/>
+        <input type='hidden' name='url' value={c.arg("url")}/>
+        <input type='hidden' name='isdisputed' value={c.arg("isdisputed")}/>
+        <input type='hidden' name='claimid' id='claimid' value="0"/>
+        <input type='hidden' name='name'/>
+        <input type='hidden' name='descr'/>
+      </form>
+	    {Widgets.tabs(
+	      "Search Claims" -> (() => searchForClaims(query)),
+	      "Recent Claims" -> (() => 
+	        	<div id='claimlist'>{c.store.getRecentClaims(c.userid) flatMap claimButton}</div>),
+	      "Create New Claim" -> (() =>
+	            createNewClaim)
+	    )}
    </div>
 
    def searchForClaims(query : String)(implicit c : ReqContext) =
@@ -67,7 +80,7 @@ object Mini {
         <input type='hidden' name='text' value={c.arg("text")}/>
         <input type='hidden' name='title' value={c.arg("title")}/>
         <input type='hidden' name='url' value={c.arg("url")}/>
-        <input type='hidden' name='disputed' value={c.arg("disputed")}/>
+        <input type='hidden' name='isdisputed' value={c.arg("isdisputed")}/>
[…]

### 2009-05-26 scala/src/com/intel/thinkscala/view/Widgets.scala

@@ -23,7 +23,7 @@ object Widgets {
 		      case (name,_) => <a href={c.modifiedUrl("tab" -> name, "page" -> 0)}>{name}</a>
 		    }}
 		  </div>
-		  <div class="body">
+		  <div class="tabbody">
 		    {options flatMap {
 		      case (name,func) if name == selected => func()
 		      case _ => NodeSeq.Empty 

### 2009-05-26 webapps/node/javascript/standard.js

@@ -57,3 +57,23 @@ function setSnipStatus(snip,vote){
 		}
 	)
 }
+
+function submitForm(formid,fieldname,fieldval){
+	var form = document.forms[formid];
+	form[fieldname].value = fieldval;
+	form.submit();		
+}
+
+function submitNewClaim(){
+	var claimform = document.forms.newclaimform;
+	var snipform = document.forms.newsnippet;
+	snipform.name.value = claimform.name.value;
+	snipform.descr.value = claimform.descr.value;
+	snipform.submit();
+}
+
+function closePopupWindow(){
+    var ev = document.createEvent("Events");
+    ev.initEvent("thinklink-close-popup", true, false);
+    document.body.dispatchEvent(evt);	
+}

### 2009-05-28 papers/uist_thinklink/uist_rebuttal_v4.txt
Added cookie stripping. Improved paging. Sped up some database queries

The reviewers were primarily concerned with two issues: 
(i) How is Think Link better than using a general-purpose annotation system to mark disputed claims?
(ii) how can we bootstrap our set of disputed snippets to a big enough size to attract users?

We believe that we can address both issues, as we discuss below.
We will also be happy to address the other helpful suggestions, such as making the figures larger.

= Why additional structure is important =

As reviewer 1 stated: "[Think Link] appears to be the first work to make use of Open Hypermedia for identifying disputed statements on the web".

As several reviewers noted, one could use a general-purpose annotation system for this purpose. You could highlight disputed statements, write comments saying things were disputed, or provide links to things you thought were useful evidence.

Think Link is a more specialized tool. Rather than allowing a user to highlight, comment, or link in arbitrary ways, Think Link only permits a user to link a snippet to a claim, link a claim to evidence, link a claim to a related claim, and vote on the quality of links provided by other users.

We believe that this more structured approach provides an improved user experience. In particular:

* Since Think Link knows what canonical claim each snippet is making, it can avoid highlighting disputed claims that the user already knows about and has requested not be marked again.

* When a user clicks on a highlighted claim, they see the best evidence for and against that claim, as determined by the votes of the entire community - rather than the favourite link of one user.

* The argumentation links allow a user to see how a claim fits into a larger argument.

* Voting allows Think Link to filter out lower quality claims/links/snippets and focus on ones the community judged to be more interesting.

* Think Link makes it easier for an activist user to rapidly mark many snippets that make the same claim. A common usage model is to Google a claim you disagree with, tab-open all pages that look relevant, quickly mark a relevant snippet in each page, and then bulk-assign all marked snippets to the same disputed claim.

= Bootstrapping =

If a user installed Think Link but didn't see anything highlighted then they it is likely they would get bored and stop using it. It is thus important to bootstrap with an initial data set that has reasonable coverage.

This has been problem for previous annotation systems in which the database contained personal annotations specific to particular pages. Fortunately we have found Think Link's restricted domain makes building a data set easier:

Several existing web sites maintain lists of disputed claims. So far we have imported all claims from Snopes and merged in lists taken from several debate websites.

We have found we can pay Mechanical Turk workers 4 cents to mark 10 snippets (using a tool) and 20 cents to create a new disputed claim with snippets and evidence.

### 2009-05-28 firefox_plugin/chrome/content/marker.js

@@ -37,11 +37,12 @@ function mark_snippets(doc){
 			}
 		}
 		if(snippets.length > 0){
-			if(global_marked.length == 0){
+			if(global_marked.length > 0){
 				showMessage("This page contains disputed claims (highlighted in pink)",doc);
 			}else{
 				// TODO: cope better when can't find disputed claim
-				showMessage("This url was tagged with disputed claims, but we can't find them on the page anymore",doc);
+				claimMessage(snippets[0].claimtext,snippets[0].claimid);
+//				showMessage("This url was tagged with disputed claims, but we can't find them on the page anymore",doc);
 			}
 		}
 		doc.thinklink_marked = global_marked;
@@ -65,6 +66,31 @@ function findBrowser(doc){
 		}
 	}
 }
+
+function claimMessage(claimtext,id,doc){
+	var notificationBox = gBrowser.getNotificationBox(findBrowser(doc));
+	var notification =
+		notificationBox.getNotificationWithValue("thinklink-disputed");
+	var buttons = [{
+		label: "More Info",
+		callback: function(){viewClaim(id);},
+		accessKey: "I",
+		popup: null
+		}];
+	//{
+		//label: "ping",
+		//accessKey: "K",
+		//popup: "blockedPopupOptions",
+		//callback: null
+	 //}];
+	 
+	var message = "disputed claim: "+claimtext;
+
+	const priority = notificationBox.PRIORITY_INFO_MEDIUM;
+	notificationBox.appendNotification(message, "thinklink-disputed",
+	"chrome://thinklink/skin/lightbulb_red.png", priority, buttons);	
+}
+
 
 function showMessage(message,doc){
 	var notificationBox = gBrowser.getNotificationBox(findBrowser(doc));

### 2009-05-28 scala/src/com/intel/thinkscala/MainServlet.scala

@@ -30,6 +30,7 @@ object Urls {
   def createClaim(query : String) = base+"/claim/new?query="+encode(query)
   def searchclaims(query : String) = "/claim/search?query="+encode(query)
   def addevidence(id : Any, rel : String) = claim(id)+"/addevidence?rel="+encode(rel)
+  def addlinks(id : Any, typ: String) = claim(id)+"/addlinks?typ="+encode(typ)
 }
 
 object MiniUrls {
@@ -243,7 +244,7 @@ class MainServlet extends HttpServlet {
     UrlHandler("""/claim/(\d*)""",c => {
       val claim = c.store.getInfo(c.urlInt(1),c.maybe_userid)
       val title = claim("text") + " - Think Link Claim"
-      c.outputHtml(title,Page.claim(c,claim))
+      c.outputHtml(title,Page.claim(claim)(c))
     }),
     UrlHandler("""/topic/(\d*)""",c => {
       val row = c.store.getInfo(c.urlInt(1),c.maybe_userid)
@@ -253,7 +254,7 @@ class MainServlet extends HttpServlet {
     UrlHandler("""/user/(\d*)""",c => {
       val row = c.store.getUserInfo(c.urlInt(1))
       val title = row("name") + " - Think Link User"
-      c.outputHtml(title,Page.user(c,row))
+      c.outputHtml(title,Page.user(row)(c))
     }),   
     UrlHandler("/login",c => {
       c.outputHtml("Login",(<div>{Page.login("Login",Urls.base)}</div>))

### 2009-05-28 scala/src/com/intel/thinkscala/turk/CheckTurkData.scala

@@ -11,7 +11,7 @@ class User(val id : String, val total : Int, val agree : Int, val disagree : Int
 
 
 object CheckTurkData { 
-  val filename = "/home/rob/git/thinklink/turk/output/hoaxes.csv"
+  val filename = "/home/rob/git/thinklink/turk/output/tye_first.csv"
 
   def main(args : Array[String]){
     val rows = Util.parseCsvFile(filename)

### 2009-05-28 scala/src/com/intel/thinkscala/view/Page.scala

@@ -62,31 +62,37 @@ object Page {
         </form>
     </div>
     
-  def claim(c : ReqContext, row : SqlRow) =
+  def claim(row : SqlRow)(implicit c : ReqContext) =
     <div id="claim">
       <div class="topclaim">
-	      <h1>{row("text")}</h1>
-	      <span class="instances">seen <span class="count">{row("instance_count")}</span> times on the web
+	      <h1>Claim: {row("text")}</h1>
+	      <span class="instances"><a href={Urls.findsnippets(row("id"))}>seen <span class="count">{row("instance_count")}</span> times on the web</a>
 	        <a href={Urls.findsnippets(row("id"))}>find more</a>
 	      </span>   
       </div>
       <div class="description">{row("description")}</div>
       {userref(row.int("user_id"),row.str("username"),"found by ")}
-      <div class="evidence">
-   	      <div id="opposed">
-	        <h2>Opposing Evidence</h2>
-            {c.store.evidence(row.int("id"),"opposes") flatMap Render.snippet}
-            <a class='add' href={Urls.addevidence(row.int("id"),"opposes")}>add opposing evidence</a>
-	      </div>
-	      <div id="supports">
-	        <h2>Supporting Evidence</h2>
-            {c.store.evidence(row.int("id"),"supports") flatMap Render.snippet}
-            <a class='add' href={Urls.addevidence(row.int("id"),"supports")}>add supporting evidence</a>
-	      </div>
-      </div>
-      <div id="related-claims">
-        <h2>Related Claims</h2>
-            {c.store.linkedEitherAnyNodes(row.int("id"),"claim",0,4) flatMap Render.claim}
+       <div id="claimlist">
+        {Widgets.tabs(
+          "Opposing Evidence" -> (() => 
+ 	  	      <div class='evidence' id="opposed">
+		        <h2>Opposing Evidence</h2>
+            	{Widgets.pagedList(c.store.evidence(row.int("id"),"opposes",_).toSeq flatMap Render.snippet)}
+                <a class='add' href={Urls.addevidence(row.int("id"),"opposes")}>add opposing evidence</a>
+              </div>),
+          "Supporting Evidence" -> (() => 
+  	  	      <div class='evidence' id="supports">
+		        <h2>Supporting Evidence</h2>
+               	{Widgets.pagedList(c.store.evidence(row.int("id"),"supports",_).toSeq flatMap Render.snippet)}
[…]

### 2009-10-10 papers/www_disputefinder/disputefinder.tex
Started writing paper

--- 2009-03-31 papers/uist_thinklink/thinklink.tex
@@
 %\documentclass{article}
-\documentclass{chi2009}
+\documentclass{www2010-submission}
 \usepackage{times}
@@
 
-% --- Copyright notice ---
-\conferenceinfo{UIST'09}{October 4-7, 2009, Victoria, BC, Canada}
-\CopyrightYear{2009}
-\crdata{x-xxxxx-xxx-x/xx/xxxx}
-
-% Uncomment the following line to hide the copyright notice
-\toappear{}
-% ------------------------
+\toappear
 
@@
 
-\title{Exposing and Exploring Disputed Statements on the Web}
+\title{Highlighting Disputed Information on the Web}
 
@@
 
+\numberofauthors{5}
+
 \author{
-\parbox[t]{9cm}{\centering
-	     {\em Author names removed for blind review}\\
+\alignauthor Rob Ennals\\
+       \affaddr{Intel Labs Berkeley}\\
+       \affaddr{2150 Shattuck Ave}\\
+       \affaddr{Berkeley, CA, USA}\\
+       \email{robert.ennals@intel.com}
+\alignauthor Beth Trushkowsky\\
+       \affaddr{Computer Science Division}\\
+       \affaddr{University of California at Berkeley}\\
+       \affaddr{Berkeley, CA, USA}\\
+       \email{trush@berkeley.edu}
+\alignauthor John Mark Agosta\\
+       \affaddr{Intel Labs Santa Clara}\\
+       \affaddr{2200 Mission College Blvd}\\
+       \affaddr{Santa Clara, CA, USA}\\
+       \email{john.m.agosta@intel.com}
 }
-}
+
+\additionalauthors{+ Whoever else wants to join in}
 
@@
 
-%RULE: Don't cite media reports unless I have to
+%RULE: Don't cite media reports unless I have to - some reviewers don't like it
 
 \abstract
-Think Link is a tool that helps users know when information they read on the web is disputed. 
-As a user browses the web, Think Link highlights snippets of text that make claims that users have identified as contentious. 
-If a user clicks on a highlighted snippet, Think Link displays an argument graph showing the best evidence for and against the claim the snippet is making.
+Dispute Finder is a tool that helps users know when information they read on the web is disputed. 
+As a user browses the web, Dispute Finder highlights snippets of text that make claims that users have identified as contentious. 
+If a user clicks on a highlighted snippet, Dispute Finder displays an argument graph showing the best evidence for and against the claim the snippet is making.
 
-Users provide all of Think Link's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
-Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.
+Users provide all of Dispute Finder's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
+Dispute Finder is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Dispute Finder with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Dispute Finder as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.
 
-\classification{H5.2 [Information interfaces and presentation]:
-User Interfaces. - Graphical user interfaces.}
+\category{H.4.m}{Information Systems}{Miscellaneous}
+\category{H.4.2}{Information Systems}{Decision Support}
+\category{H.5.2}{User Interfaces}{Graphical User Interfaces}
 
@@
 
-In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. 
-If a user has installed the Think Link browser extension then it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). 
-When a user clicks on a highlighted snippet, Think Link presents an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).
+In this paper we present Dispute Finder, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. 
+If a user has installed the Dispute Finder browser extension then it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). 
+When a user clicks on a highlighted snippet, Dispute Finder presents an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).
 
@@
 	\includegraphics[width=6cm]{../screenshots/v2_highlight_shadow.png}
-	\caption{Think Link highlights snippets that make disputed claims}
+	\caption{Dispute Finder highlights snippets that make disputed claims}
 	\label{highlight}
@@
 
-Think Link relies on users to identify disputed claims, to find instances of these claims on web pages, and to vote for the sources that provide the best support or opposition for a claim. 
-Think Link is designed to cater to two primary usage scenarios:
+Dispute Finder relies on users to identify disputed claims, to find instances of these claims on web pages, and to vote for the sources that provide the best support or opposition for a claim. 
+Dispute Finder is designed to cater to two primary usage scenarios:
 
@@
 \item[Activists] care strongly about particular issues.
-They use Think Link to mark snippets that make claims that they disagree with.
+They use Dispute Finder to mark snippets that make claims that they disagree with.
 They are motivated by a desire to make other readers see that these claims are disputed and learn about the opposing point of view.
@@
 \item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled.
-They install Think Link as a browser extension so that it will highlight disputed claims and show them opposing points of view.
+They install Dispute Finder as a browser extension so that it will highlight disputed claims and show them opposing points of view.
 \end{description}
@@
 
-Think Link's design was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.
+Dispute Finder's design was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.
 
@@
 % 	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
-% 	\caption{Think link connects claims to each other and to web snippets}
+% 	\caption{Dispute Finder connects claims to each other and to web snippets}
 % 	\label{summarygraph}
@@
 
-Think Link builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. 
+Dispute Finder builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. 
 The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
-Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information.
-Think Link's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
+Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information.
+Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
 
-What makes Think Link interesting is the way that it applies ideas from these different domains to the task of helping users deal with misinformation and bias on the web.
+What makes Dispute Finder interesting is the way that it applies ideas from these different domains to the task of helping users deal with misinformation and bias on the web.
 
@@
 
-Think Link's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
+Dispute Finder's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
 IBIS tools model debate as a graph of issues, positions, and arguments.
@@
 Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox extension to help a user create a claim about a web page they are reading.
-Unlike Think Link, Cohere is not designed to be used to alert users about disputed snippets.
+Unlike Dispute Finder, Cohere is not designed to be used to alert users about disputed snippets.
 Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.
 
-Although Think Link's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
-In Think Link the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim.
+Although Dispute Finder's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
+In Dispute Finder the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim.
 A user is expected to create a new claim only when they want to group together several snippets that make that claim. 
-A Think Link user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself.
+A Dispute Finder user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself.
 By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph.
 A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion.
-In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.
+In Dispute Finder it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.
 
@@
 Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
-We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Think Link that is designed for identifying snippets that represent conflicting points of view.
+We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Dispute Finder that is designed for identifying snippets that represent conflicting points of view.
 
-Think Link uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims.
+Dispute Finder uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims.
 Several alternative graph structures have been proposed for describing arguments and design rationale.
@@
 Snopes is a database of urban legends that the site owners investigated to determine whether they are true.
-Think Link's database automatically imports all contentious claims identified by Snopes.
+Dispute Finder's database automatically imports all contentious claims identified by Snopes.
 FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.
-The advantage of Think Link is that it tells you when information on web sites is disputed automatically, without requiring you to suspect that information might be disputed and look for it on another site.
+The advantage of Dispute Finder is that it tells you when information on web sites is disputed automatically, without requiring you to suspect that information might be disputed and look for it on another site.
 
@@
 
-% FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.
+% FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Dispute Finder as they appear.
 
@@
 MediaCloud shows which different words different news sources associate with the same topic.
-Unlike Think Link, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.
+Unlike Dispute Finder, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.
 
@@
 Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
-Unlike these Wikipedia-based systems, Think Link does not use edit history to determine when text is untrustworthy; rather it relies on a community of activist users.
+Unlike these Wikipedia-based systems, Dispute Finder does not use edit history to determine when text is untrustworthy; rather it relies on a community of activist users.
 
@@
 
-Think Link is an example of an Open Hypermedia system~\cite{Bouvin2000}.
-Like other Open Hypermedia systems, Think Link allows users to lay an additional link structure over an existing hypertext document.
-Think Link differs from prior open hypermedia systems in its focus on revealing contentious arguments.
+Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000}.
+Like other Open Hypermedia systems, Dispute Finder allows users to lay an additional link structure over an existing hypertext document.
+Dispute Finder differs from prior open hypermedia systems in its focus on revealing contentious arguments.
 While other systems such as HyperDISCO~\cite{Wiil1996} could be used to link a snippet to a contentious claim, they do not provide user interface support to make this easy.
@@
 Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.
-While Think Link also allows users to organize information from other sources, it does not use tags.
+While Dispute Finder also allows users to organize information from other sources, it does not use tags.
 
@@
 A user can comment on why a snippet is biased and rewrite the snippet in a neutral way.
-While SpinSpotter and Think Link both draw attention to biased or inaccurate snippets, they do different things with the snippets.
-SpinSpotter lets users annotate a snippet with comments specific to that particular snippet, while Think Link treats a snippet as being an instance of a shared claim, and links all snippets identified as making that claim to a shared node in the argument graph that is linked to other points of view.
+While SpinSpotter and Dispute Finder both draw attention to biased or inaccurate snippets, they do different things with the snippets.
+SpinSpotter lets users annotate a snippet with comments specific to that particular snippet, while Dispute Finder treats a snippet as being an instance of a shared claim, and links all snippets identified as making that claim to a shared node in the argument graph that is linked to other points of view.
 
@@
 Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.
-Like Think Link, these tools allow a user to mark the claims being made in a document, however these tools are more formal and are designed to extract knowledge rather than informally mark disputed snippets.
+Like Dispute Finder, these tools allow a user to mark the claims being made in a document, however these tools are more formal and are designed to extract knowledge rather than informally mark disputed snippets.
 
@@
 Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
-Think Link also creates new links between information, but it's links are created by users, rather than being mined automatically.
+Dispute Finder also creates new links between information, but it's links are created by users, rather than being mined automatically.
 
@@
 
-\section{The Think Link System}
+\section{The Dispute Finder System}
 
-For Sceptical Readers, Think Link highlights disputed snippets and links them to snippets on other web sites that present alternative points of view.
-For Activists, Think Link makes it easy for users to mark snippets about issues they care about and connect them into an argument graph.
+For Sceptical Readers, Dispute Finder highlights disputed snippets and links them to snippets on other web sites that present alternative points of view.
+For Activists, Dispute Finder makes it easy for users to mark snippets about issues they care about and connect them into an argument graph.
 
@@
 
-If a sceptical reader has installed the Think Link browser extension, Think Link will draw attention to snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
-If a user hovers their mouse over a highlighted snippet then Think Link displays a tooltip giving the disputed claim.
+If a sceptical reader has installed the Dispute Finder browser extension, Dispute Finder will draw attention to snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
+If a user hovers their mouse over a highlighted snippet then Dispute Finder displays a tooltip giving the disputed claim.
 Clicking on a highlighted snippet reveals a visualization showing the best evidence for and against the claim, as determined by the user community (Figure~\ref{claimview}).
@@
 Since the purpose of a highlight is to alert the user to claims that they had not realized were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious.
-A user can click the ``don't highlight this claim again'' button to tell Think Link that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.
+A user can click the ``don't highlight this claim again'' button to tell Dispute Finder that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.
 
-Normally Think Link will only highlight snippets that make disputed claims that the user has not asked to ignore, and snippets marked by the user themselves.
-If the user wants to see all snippets on a page then they can do so by opening the Think Link sidebar.
+Normally Dispute Finder will only highlight snippets that make disputed claims that the user has not asked to ignore, and snippets marked by the user themselves.
+If the user wants to see all snippets on a page then they can do so by opening the Dispute Finder sidebar.
 
@@
 
-Once a sceptical reader has identified a claim that they are interested in, they can use Think Link's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.
+Once a sceptical reader has identified a claim that they are interested in, they can use Dispute Finder's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.
 
@@
 
-To preserve visual consistency, Think Link uses the same claim browser interface for the small popup interface as for the full-window interface.
+To preserve visual consistency, Dispute Finder uses the same claim browser interface for the small popup interface as for the full-window interface.
 When used as a popup browser, the interface shows only one panel.
@@
 
-Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of nodes: snippets, claims, and topics. 
+Dispute Finder's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of nodes: snippets, claims, and topics. 
 A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about.
@@
 
-Think Link uses the list of page titles on Wikipedia as a seed-set for its topics.
-This allows Think Link to use the Wikify~\cite{Mihalcea2007} algorithm to automatically suggest topics for snippets and provides us with a comprehensive ready-made set of topics with well-maintained descriptions and synonyms.
+Dispute Finder uses the list of page titles on Wikipedia as a seed-set for its topics.
+This allows Dispute Finder to use the Wikify~\cite{Mihalcea2007} algorithm to automatically suggest topics for snippets and provides us with a comprehensive ready-made set of topics with well-maintained descriptions and synonyms.
 
-Think Link's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to link type.
-While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link is designed for.
+Dispute Finder's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to link type.
+While Dispute Finder's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Dispute Finder is designed for.
 We have also found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.
@@
 One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions.
-Think Link uses two strategies to try to reduce this problem.
+Dispute Finder uses two strategies to try to reduce this problem.
 Firstly, positive votes count for more than negative votes.
@@
 
-If an Activist has installed the Think Link browser extension then they can create a snippet by selecting text on a web page and selecting either ``This is disputed'' or ``This is interesting'' from the context menu (Figure~\ref{createprocess}).
+If an Activist has installed the Dispute Finder browser extension then they can create a snippet by selecting text on a web page and selecting either ``This is disputed'' or ``This is interesting'' from the context menu (Figure~\ref{createprocess}).
 A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted that the snippet is making a claim that is disputed.
@@
 
-The only difference between selecting ``this is disputed'' and ``this is interesting'' is that Think Link remembers which you used when you marked a snippet.
+The only difference between selecting ``this is disputed'' and ``this is interesting'' is that Dispute Finder remembers which you used when you marked a snippet.
 A snippet is only highlighted in red for other users if it is connected to a disputed claim.
-The main reason for having two different options is to show users what kinds of information Think Link expects them to mark as snippets.
+The main reason for having two different options is to show users what kinds of information Dispute Finder expects them to mark as snippets.
 \todo{Say something smart about the difference}
@@
 
-Think Link does not require a user to specify the claim a snippet is making at the point at which they mark it.
-Instead, Think Link encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
-One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
+Dispute Finder does not require a user to specify the claim a snippet is making at the point at which they mark it.
+Instead, Dispute Finder encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
+One anticipated usage scenario for Dispute Finder is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
 In this case, the user can save time by first collecting all their snippets, and then attaching all the snippets to their disputed claim at the same time.
 
-Think Link provides three ways for a user to associate a claim with a snippet:
+Dispute Finder provides three ways for a user to associate a claim with a snippet:
 
 \begin{description}
-\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Think Link will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}).
+\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Dispute Finder will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}).
 A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates-to'' link types.
-If Think Link does not suggest the right snippets then Think Link can guide the suggestions by entering keywords into the text box above the suggestion list.
+If Dispute Finder does not suggest the right snippets then Dispute Finder can guide the suggestions by entering keywords into the text box above the suggestion list.
 
@@
 
-\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Think Link will show a list of all the snippets that they have marked but not yet associated with a claim or a topic (Figure~\ref{sniptopic}).
-If the user selects an unfiled snippet then Think Link will suggest claims or topics that the user might want to associate with that snippet.
+\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Dispute Finder will show a list of all the snippets that they have marked but not yet associated with a claim or a topic (Figure~\ref{sniptopic}).
+If the user selects an unfiled snippet then Dispute Finder will suggest claims or topics that the user might want to associate with that snippet.
 As with the claim-first method, a user can guide the suggestions by entering keywords.
@@
 \item[Immediate:] A user can select a claim for a snippet that they have just marked.
-When a user marks a snippet, Think Link will initially highlight it in blue to show that the snippet is not currently associated with a claim or topic and will not be shown to other users.
-If the user clicks on the highlighted snippet, then Think Link will bring up the same suggestion panel used in the ``snippet first'' method.
+When a user marks a snippet, Dispute Finder will initially highlight it in blue to show that the snippet is not currently associated with a claim or topic and will not be shown to other users.
+If the user clicks on the highlighted snippet, then Dispute Finder will bring up the same suggestion panel used in the ``snippet first'' method.
 \end{description}
 
-Think Link uses the same suggestion system to suggest connections between claims.
+Dispute Finder uses the same suggestion system to suggest connections between claims.
 It is important to make sure that the argument graph stays well connected as it grows.
 If users create duplicate claims or don't connect their claims to existing claims then the graph becomes less useful.
-Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.
+Dispute Finder tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.
 
@@
 
-Think Link uses the Wikify algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims.
+Dispute Finder uses the Wikify algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims.
 The Wikify algorithm imagines that a piece of text was on a Wikipedia page and predicts what pages that text would most likely link to based on the probability that any particular n-gram links to any particular page.
-Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles.
+Recall that the set of Dispute Finder topics is seeded with the set of Wikipedia page titles.
 The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to.
@@
 
-Even though Think Link tries to make creating and linking snippets as easy as possible, it still requires a non-trivial amount of work.
+Even though Dispute Finder tries to make creating and linking snippets as easy as possible, it still requires a non-trivial amount of work.
 Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks: currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog.
@@
 
-Think Link consists of a browser extension, a page annotation script, a shared database server, and a web-based claim browser interface.
+Dispute Finder consists of a browser extension, a page annotation script, a shared database server, and a web-based claim browser interface.
 These four components are largely independent of each other and talk to each other using an open API that can also be used by other tools.
@@
 In the future we hope to devise a way to reduce concerns further. 
-One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and require a user to explicitly ask for Think Link to highlight snippets on a particular site.
+One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and require a user to explicitly ask for Dispute Finder to highlight snippets on a particular site.
 
@@
 
-%The protocol used by the Think Link server is an open REST API that other tools are free to use.
+%The protocol used by the Dispute Finder server is an open REST API that other tools are free to use.
 In the future, the server may support one or more of the argumentation interchange formats that have been proposed~\cite{Rahwan2007a,McGinnis2007}.
@@
 We performed two qualitative ``think aloud'' user studies.
-The aim of these studies was to inform the development of Think Link.
-The studies were not intended to validate the design of Think Link as being correct.
-Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different claims.
-To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for.
+The aim of these studies was to inform the development of Dispute Finder.
+The studies were not intended to validate the design of Dispute Finder as being correct.
+Dispute Finder is designed to be used by a large number of users gathering a vast amount of evidence for many different claims.
+To confidently state that our design was successful we would need to be able to test Dispute Finder on a much greater scale than we currently have resources for.
 
-The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph.
+The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Dispute Finder argument graph.
 The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page.
@@
 Study sessions took approximately forty five minutes.
-Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension.
-We first demonstrated Think Link's interface, and then asked them to find information as they would normally and use Think Link to mark snippets that made claims that they thought were interesting or disputed.
+Participants were seated at a single-screen workstation with the Firefox browser augmented with the Dispute Finder extension.
+We first demonstrated Dispute Finder's interface, and then asked them to find information as they would normally and use Dispute Finder to mark snippets that made claims that they thought were interesting or disputed.
 For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.
@@
 
-Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader).
+Most participants said that they would want to use Dispute Finder to tell them when information they read was disputed (sceptical reader).
 One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
@@
 Most participants in the first study, and all participants in the second study were able to use the tool competently.
-Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
+Participants in the second study were able to use Dispute Finder competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
 Participants said they found the tool ``very intuitive'' and ``really cool''.
@@
 The prototype interfaces required that a user enter a claim for a snippet at the point at which they created the snippet.
-When the user marked a snippet, Think Link would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype).
+When the user marked a snippet, Dispute Finder would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype).
 There turned out to be several problems with this approach:
@@
 Several users wanted to mark up a table or an image as a snippet.
-This is valid behavior -- a table or image is often useful evidence for a claim; however it is not currently supported by Think Link.
-In future versions of Think Link we intend to support this behavior.
+This is valid behavior -- a table or image is often useful evidence for a claim; however it is not currently supported by Dispute Finder.
+In future versions of Dispute Finder we intend to support this behavior.
 
@@
 This is a particular problem when talking about breaking news events, where the facts can change fast.
-If Think Link is to be effective for describing such events then it will need to have better support associating times with claims and snippets.
+If Dispute Finder is to be effective for describing such events then it will need to have better support associating times with claims and snippets.
 
@@
 
-The prototype versions of Think Link used a drag-and-drop interface to allow a user to create links between claims.
+The prototype versions of Dispute Finder used a drag-and-drop interface to allow a user to create links between claims.
 In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find others' claims and then drag them into appropriate positions in the argument graph.
@@
 
-At present Think Link relies on users to mark up snippets and connect them to claims.
+At present Dispute Finder relies on users to mark up snippets and connect them to claims.
 In the future we plan to explore using natural language and machine learning techniques to assist in this process.
-Our plan is to allow a user to request that Think Link search the web to find potential snippets that make a claim that they disagree with, and then quickly select which of these are indeed making the claim.
+Our plan is to allow a user to request that Dispute Finder search the web to find potential snippets that make a claim that they disagree with, and then quickly select which of these are indeed making the claim.
 
-Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics.
-Since our graph and user base are currently small, we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.
+Dispute Finder is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics.
+Since our graph and user base are currently small, we have not yet evaluated how Dispute Finder works when data sets are huge, many users are concurrently editing data, and some users are malicious.
 
-We hope that Think Link will make it easier for people to be informed about the world and be exposed to alternative points of view that they might not otherwise be exposed to.
+We hope that Dispute Finder will make it easier for people to be informed about the world and be exposed to alternative points of view that they might not otherwise be exposed to.
 
@@
 
-Acknowledgements omitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.
+Acknowledgements omitted for blind submission. Dispute Finder uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.
 

### 2009-10-10 papers/www_disputefinder/www2010-sample.tex
Started writing paper

% This is "www2010-sample.tex" copied from "www2005-sample.tex" V1.2 January 26 2004
% This file should be compiled with V1.4 of "www2010-submission.class"
%
% This example file demonstrates the use of the 'www2010-submission.cls'
% V1.4 LaTeX2e document class file. It is for those submitting
% articles to the WWW'04 Conference WHO DO NOT WISH TO 
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'www2010-submission.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V1.4) produces:
%       1) NO Permission Statement
%       2) WWW'04-specific conference (location) information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Julie Goetz (goetz@acm.org) or Adrienne Griscti (griscti@acm.org)
%
% Technical questions only to
% Gerald Murray (murray@acm.org)
% ===============================================================
%
% For tracking purposes - this is V1.2 - January 26 2004
\documentclass{www2010-submission}

\begin{document}
%
\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Produces the WWW2010-specific release, location and
copyright information). For use with
www2010-submission.cls V1.4. Supported by ACM.}}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the "boxing"
% and alignment of the authors under the title, and to add
% a section for authors number 4 through n.
%
% Up to the first three authors are aligned under the title;
% use the \alignauthor commands below to handle those names
% and affiliations. Add names, affiliations, addresses for
% additional authors as the argument to \additionalauthors;
% these will be set for you without further effort on your
% part as the last section in the body of your article BEFORE
% References or any Appendices.

\numberofauthors{5}
%
% Put no more than the first THREE authors in the \author command

% NOTE: All authors should be on the first page. For instructions
% for more than 3 authors, see:
% http://www.acm.org/sigs/pubs/proceed/sigfaq.htm#a18

\author{
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
%% e-mail address with \email.
\alignauthor Ben Trovato\titlenote{Dr.~Trovato also works at...}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
\alignauthor G.K.M. Tobin\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\\
       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
}
\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}

\maketitle
\begin{abstract}
This paper provides a sample of a LaTeX document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.
The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.
To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

% A category with only the three required fields
\category{H.4.m}{Information Systems}{Miscellaneous}
\category{D.2}{Software}{Software Engineering}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures,
performance measures]

\terms{Delphi theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (2.54cm [1"] top and
bottom and 1.9cm [.75"] left and right; specified column width
(8.45cm [3.33"]) and gutter size (.083cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings \cite{clark:pct} or
books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed or supported.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
%\epsfig{file=fly.eps}
\caption{A sample black and white graphic (.eps format).}
\end{figure}

\begin{figure}
\centering
%\epsfig{file=fly.eps, height=1in, width=1in}
\caption{A sample black and white graphic (.eps format)
that has been resized with the \texttt{epsfig} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
\begin{figure*}
\centering
%\epsfig{file=flies.eps}
\caption{A sample black and white graphic (.eps format)
that needs to span two columns of text.}
\end{figure*}
and don't forget to end the environment with
{figure*}, not {figure}!

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\begin{figure}
\centering
%\psfig{file=rosette.ps, height=1in, width=1in,}
\caption{A sample black and white graphic (.ps format) that has
been resized with the \texttt{psfig} command.}
\end{figure}

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the \texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
%
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The www2010-submission.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
\balancecolumns % GM July 2000
% That's all folks!
\end{document}

### 2009-10-10 papers/www_disputefinder/www_disputefinder.tex
Started writing paper

\documentclass{www2010-submission}
\usepackage{graphics}
\usepackage{color}

\newcommand{\idea}[1]{\\\noindent{\color{blue} #1}\\}

\begin{document}
\title{Highlighting Disputed Claims on The Web}

\numberofauthors{5}

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{trush@berkeley.edu}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

\maketitle

\begin{abstract}
\idea{Dispute Finder highlights Disputed claims on the web}
\idea{Disputed means that a site you might trust gives a different point of view}
\idea{Use NLP techniques to highlight many pages that make the same claim}
\idea{Mine claims from existing sites, and from user submissions}
\idea{User testing discovers interesting issues, which directed the design}
\end{abstract}

\section{Introduction}

\idea{Web allows anyone to publish whatever they want. Sometimes this is good, but sometimes bad.}
\idea{Traditional newspapers are dying, or laying off fact checking staff. Can we provide an alterative.}

\idea{Two personas: Activist and Skeptical Reader}

\idea{Dispute Finder is available to the public.}
\idea{As yet, around 12k people have installed it and tried it out, but of those, only around 2k remain active daily users and around 1k actively contribute. Number of users rises and falls with media attention. }

\section{Related Work}

\subsection{Checking Accuracy and Bias on the Web}

\idea{Snops, Fact Check, Politifact, etc}

\idea{NewsCube, MediaCloud, etc}

\subsection{Web Annotation and Clipping Systems}

\idea{Hunter Gatherer}

\idea{VideoLyzer}

\end{document}

### 2009-10-13 papers/www_disputefinder/disputefinder.tex
Minor paper changes - abstract and intro

@@
 
-\additionalauthors{+ Whoever else wants to join in}
+\additionalauthors{Whoever else wants to help out with the paper. Let me know.}
 
@@
 \abstract
-Dispute Finder is a tool that helps users know when information they read on the web is disputed. 
-As a user browses the web, Dispute Finder highlights snippets of text that make claims that users have identified as contentious. 
-If a user clicks on a highlighted snippet, Dispute Finder displays an argument graph showing the best evidence for and against the claim the snippet is making.
 
-Users provide all of Dispute Finder's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
-Dispute Finder is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Dispute Finder with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Dispute Finder as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.
+We describe Dispute Finder, a browser extension that helps a user know when information they read online is disputed -- where by 'disputed' we mean that a source that they might trust expresses a different point of view.
+As a user browses the web, Dispute Finder examines the text on pages that the user is browsing and highlights any phrases that appear to be supporting claims from its database of known disputed claims.
+If a user clicks on a highlighted phrase, Dispute Finder will show the user a summary of arguments from other sources that support other points of view.
+
+Disputed Claims can be submitted by users, or may be found automatically by crawling web sites that already maintain lists of disputed claims.
+Dispute Finder identifies instances of disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of a subset of our claim database.
+
+Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is good enough to be compelling for most users.
+We do however believe that Dispute Finder attacks an interesting problem that, if addressed well, could significantly improve the utility of the web.
 
@@
 \todo{update screenshots}
+
+A great thing about the web is that it allows anyone to publish whatever they want without having to go through a higher authority that must approve everything that is written.
+However a consequence of this is that much of the information that one encounters on the web has not been certified by an authority that a user trusts, and so it becomes much harder for a user to decide whether they should trust the information they are reading.
+
+\idea{Of course, old media wasn't entirely trustworthy either}
+
+However the old way of doing things had certain advantages.
+
+One frustrating consequence of this is that
+
+ that much of the information on the web comes from sources that users do not know whether they can trust.
+
+When the available media is filtered through a small number of publishers,
 

### 2009-10-16 papers/www_disputefinder/disputefinder.tex
Updates to WWW paper. Added all claims API. Added ACM TechNews and CSM to Press list

@@
 
-% \newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
-% \newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
-% \newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
-% \newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}
+\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
+\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
+\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
+\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}
 
-\newcommand{\want}[1]{}
-\newcommand{\todo}[1]{}
-\newcommand{\idea}[1]{}
-\newcommand{\node}[1]{}
+%\newcommand{\want}[1]{}
+%\newcommand{\todo}[1]{}
+%\newcommand{\idea}[1]{}
+%\newcommand{\node}[1]{}
 
@@
 
-\additionalauthors{Whoever else wants to help out with the paper. Let me know.}
+\additionalauthors{Additional authors: Tad Hirsch (Intel Research PaPR, email: {\texttt{tad.hirsch@intel.com}}) and Tye Rattenbury (Intel Research PaPR), email: {\texttt{tye.rattenbury@intel.com}})}
 
@@
 
-A great thing about the web is that it allows anyone to publish whatever they want without having to go through a higher authority that must approve everything that is written.
-However a consequence of this is that much of the information that one encounters on the web has not been certified by an authority that a user trusts, and so it becomes much harder for a user to decide whether they should trust the information they are reading.
-
-\idea{Of course, old media wasn't entirely trustworthy either}
-
-However the old way of doing things had certain advantages.
-
-One frustrating consequence of this is that
-
- that much of the information on the web comes from sources that users do not know whether they can trust.
-
-When the available media is filtered through a small number of publishers,
-
-The web contains a huge amount of information, but some of this information is incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}.
+The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}.
 If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
@@
 
-In this paper we present Dispute Finder, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. 
-If a user has installed the Dispute Finder browser extension then it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). 
-When a user clicks on a highlighted snippet, Dispute Finder presents an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).
+In this paper we describe Dispute Finder, a service that informs a user when information they read online is disputed by a source that they might trust.
+Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in.
+
+If a user has installed the Dispute Finder browser extension then it will highlight snippets of text on the web that make claims that Dispute Finder believes are disputed (Figure~\ref{highlight}). 
+When a user clicks on a highlighted snippet, Dispute Finder will present a list of articles that present alternative points of view, each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).
+
+Dispute Finder consists of a database, an API, and a firefox browser extension.
+The database contains information about the disputed claims that are known to be made on web sites, and hints about how to tell when a web page is making such a claim.
+The API allows an external client to determine whether particular content is making a disputed cliam.
+The firefox extension uses the API to determine whether the web pages a user browses make disputed claims.
+The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.
 
@@
 
-Dispute Finder relies on users to identify disputed claims, to find instances of these claims on web pages, and to vote for the sources that provide the best support or opposition for a claim. 
-Dispute Finder is designed to cater to two primary usage scenarios:
+There are a number of design decisions that must be made when building a system such as this, which we will address in the remainder of the paper. In particular:
 
 \begin{description}
-\item[Activists] care strongly about particular issues.
-They use Dispute Finder to mark snippets that make claims that they disagree with.
-They are motivated by a desire to make other readers see that these claims are disputed and learn about the opposing point of view.
+\item[What claims are disputed?] In order to highlight claims as being disputed, we need to know what claims these are.
+To be useful, the set of known disputed claims needs to be both large (so people see some benefit) and accurate (so that people don't get annoyed by things that aren't actually disputed.
+We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims.
+There are also other interesting alternative approaches that may be worth exploring.
 
-\item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled.
-They install Dispute Finder as a browser extension so that it will highlight disputed claims and show them opposing points of view.
+\item[What disputed claims should we tell the user about?] In some sense almost everything is disputed by someone.
+If we highlighted everything that was disputed by anyone then the tool would be too noisy to be useful.
+The challenge is to determine when the other point of view is something the user might take seriously.
+We do not yet have a large enough database of disputed claims for this to be a serious problem, but we believe that there may be interesting solutions.
+
+\item[How do we tell that a snippet is making a disputed claim?] If a user is reading a web page that might contain disputed claims, then how do we determine which sentences are making disputed claims?
+We have experimented with several different approaches, each of which has different advantages and disadvantages.
+One can ask users to mark snippets individually.
+One can build a search tool that allows a user to find and mark similar snippets in bulk.
+One can provide an interface that allows a user to train a machine learning classifier to recognize snippets.
+One can use a textual entailment algorithm to recognize phrases that seem to have a similar meaning to the claim.
+
+\item[How do we add highlights to the pages a user browses?] If a user is reading web pages, how should we augment that experience with information about disputed claims?
+Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension~\cite{nolike-extension?}.
+Using a proxy~\cite{proxy?} has similar adoption problems to a browser extension, and is likely to break some web sites.
+Providing an API allows external sites such as news readers and search engines to provide information about disputed claims, but limits coverage to those sites that support the API.
+The best approach may be a combination.
+
+\item[What information should we show someone about a disputed claim?] If someone clicked on a disputed claim on a web page, what information should we show them that will help them decide whether to talk the alternative points of view seriously.
+Alternatives include an argumentation graph, user comments, a wiki page,
+We experimented with providing an argumentation graph, user comments, aut
 \end{description}
 
+In order for Dispute Finder to be useful, it needs to provide a service that users will actually appreciate.
+It is thus important that we understand how users feel about disputed information.
+Dispute Finder is designed to cater to two personas.
+Each persona was created from interviews we conducted with people who we believe fit into these categories:
+
+\todo{Use interviews to get some actual observations here. These are just fillers.}
+
+\begin{description}
+
+\item[Skeptical Readers] want to know when information they read is disputed.
+They are primarily motivated by a desire to avoid being misled.
+Although there are some sources that they strongly trust, they also regularly read web sites that they do not trust, and they are worried about being misled.
+In the abscence of Dispute Finder, they often try to verify information they read online by searching several web sites on the same topic, or checking something they have read on a known trusted site.
+
+\item[Activists] care strongly about particular issues and are prepared to spend some time helping other users know that something they read is disputed.
+They are the same kinds of people who join protest groups, argue about topics online, post stories to news aggregators, or edit wikipedia.
+They are motivated by a desire to gain status by being publically seen to have led others to discover that important issues are disputed.
+They are also motivated by a desire to entertain themselves by seeing what disputed claims are being made and where online they are being made.
+
+\end{description}
+
+\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
+\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
+\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}
+
 The same user may be an Activist for some issues and a Sceptical Reader for others.
+Dispute Finder is not useful for everyone.
+In our interviews, we encountered several people who either didn't rely on the internet as an important source of information, or only obtained important information from sources that they trust.
+If a user never reads information they care about from web sites that they don't entirely trust, then Dispute Finder will not be useful to them.
 
-\todo{Claim panel should have 'more' buttons}
-
-Dispute Finder's design was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.
-
-\todo{Talk about automatically including all arguments from Snopes}
-\todo{I think we need to do some kind of evaluation of the new interface, even if it is just showing it to some people, or having people in the lab try it.}
-\todo{Need figures saying how efficient it is for an activist user to mark up a topic}
-
-% \begin{figure}[tb]
-% 	\begin{center}
-% 	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
-% 	\caption{Dispute Finder connects claims to each other and to web snippets}
-% 	\label{summarygraph}
-% 	\end{center}
-% \end{figure}
+\todo{Should we explicitly list what we think are our key contributions?}
 
 \section{Related Work}
-\todo{Don't cite things that aren't relevant}
 
-Dispute Finder builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. 
+Dispute Finder builds on prior work in several different areas.
 The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
@@
 Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
+Many people have developed textual entailment algorithms~\cite{entail?} that determine when one sentence implies the trust of another, or contradiction detection algorithms that determine when one sentence contradicts another.
 
-What makes Dispute Finder interesting is the way that it applies ideas from these different domains to the task of helping users deal with misinformation and bias on the web.
+\todo{Add more references from the NewsCube paper}
 
-\subsection{Argumentation and Design Rationale}
+\subsection{Fact Checking Sites}
 
-Dispute Finder's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
-IBIS tools model debate as a graph of issues, positions, and arguments.
-While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.
+If a user suspects that something they read online may be false then they can look it up on one of many fact checking sites such as Snopes.com, FactCheck.org, or Politifact.com.
+If one is aware that an issue is controversial and wants to understand the different sides, then one can use sites like Wikipedia.org, Debate.org, and ProCon.org.
+These sites do an excellent job at presenting accurate and balanced information about controversial topics.
 
-Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox extension to help a user create a claim about a web page they are reading.
-Unlike Dispute Finder, Cohere is not designed to be used to alert users about disputed snippets.
-Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.
+Dispute Finder is designed to deal with the cases where the user is not aware that the information they are reading is disputed and so does not realise that they should check it on one of these services, or does not know which of these services might have more information.
+Dispute Finder is designed to work together with fact checking sites like Snopes and Politifact.
+Indeed Dispute Finder automatically imports disputed claims made on Snopes or Politifact into its claim database, and will use articles from Snopes and Politifact as evidence about disputed claims.
 
-Although Dispute Finder's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
-In Dispute Finder the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim.
-A user is expected to create a new claim only when they want to group together several snippets that make that claim. 
-A Dispute Finder user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself.
-By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph.
-A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion.
-In Dispute Finder it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.
+\subsection{Analysing News}
 
-Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions.
-Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
-We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Dispute Finder that is designed for identifying snippets that represent conflicting points of view.
+News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
+The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader persective of the issue.
+Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the slant of the entire article.
+A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.
 
-Dispute Finder uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims.
-Several alternative graph structures have been proposed for describing arguments and design rationale.
-WinWin~\cite{Boehm2006} models the different stakeholders and their different motives.
-The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions.
-QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions.
-More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.
+Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias.
+Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking.
+Newstrust allows users to rate news articles for quality and objectivity.
 
-\subsection{Checking Accuracy and Bias on the Web}
+\subsection{Highlighting Disputed Information}
 
-If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}.
-Snopes is a database of urban legends that the site owners investigated to determine whether they are true.
-Dispute Finder's database automatically imports all contentious claims identified by Snopes.
-FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.
-The advantage of Dispute Finder is that it tells you when information on web sites is disputed automatically, without requiring you to suspect that information might be disputed and look for it on another site.
+Several previous tools have used highlighting to alert an author about information that they should perhaps be suspicious of.
+WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author.
 
-%We use Fact Check as a useful source of disputed claims.
+Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, so that they can put forward their own point of view.
+Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
+There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}.
 
-% FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Dispute Finder as they appear.
+These annotation tools all allow a user to annotate a page with their thoughts on the same topic.
+In Dispute Finder, we do not allow a user to directly express their own opinions about a topic.
+Instead, the only way they can disagree with something that is said is to link it to an article from a trusted source that argues for a different point of view.
+We believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
 
-\todo{Make sure we stay in sync}
+Another key difference between these annotation tools and Dispute Finder is that these annotation tools all allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
+If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
+By contrast, if a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that it appears.
 
-NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias.
-NewsCube finds articles on the same topic that have different biases.
-MediaCloud shows which different words different news sources associate with the same topic.
-Unlike Dispute Finder, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.
+\todo{Cite google quotation stuff and Ed Chi movable quotations stuff}
 
-Several authors have created tools that help users know when to trust information on Wikipedia\footnote{http://wikipedia.org}.
-WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors.
-Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is.
-Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
-Unlike these Wikipedia-based systems, Dispute Finder does not use edit history to determine when text is untrustworthy; rather it relies on a community of activist users.
+\subsection{Finding Repeated Information on the Web}
 
-% 
-% 
-% NewsCube~\cite{Park2009}.
-% Wikipedia fixes Vandalism~\cite{Viegas2004}.
-% Trustworthiness~\cite{Gil2006}.
-% WikiTrust~\cite{Adler2008}. Wiki Dashboard~\cite{Kittur2008}.
-% Wiki Scanner\footnote{http://wikiscanner.virgil.gr}.
-% SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.
+A key component of Dispute Finder is that in needs to identify phrases on the web that make a know disputed claim.
+The techniques that Dispute Finder uses have been influenced by related work that does similar things.
+
+\cite{Kim2009} Efficient Overlap and Content Reuse Detection.
+
+\cite{schillit?}
+
+Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
+Dispute Finder also creates new links between information, but it's links are created by users, rather than being mined automatically.
+
+\cite{Something by Ed CHi about this}
+
+\todo{Talk about textual entailment}
+
+\todo{Talk about MemeTracker}
+
+\subsection{Textual Entailment}
 
@@
 ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in.
-Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
-Dispute Finder also creates new links between information, but it's links are created by users, rather than being mined automatically.
 
@@
 % Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.
+
+\subsection{Argumentation and Design Rationale}
+
+Dispute Finder's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
+IBIS tools model debate as a graph of issues, positions, and arguments.
+While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.
+
+Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox extension to help a user create a claim about a web page they are reading.
+Unlike Dispute Finder, Cohere is not designed to be used to alert users about disputed snippets.
+Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.
+
+Although Dispute Finder's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
+In Dispute Finder the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim.
+A user is expected to create a new claim only when they want to group together several snippets that make that claim. 
+A Dispute Finder user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself.
+By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph.
+A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion.
+In Dispute Finder it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.
+
+Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions.
+Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
+We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Dispute Finder that is designed for identifying snippets that represent conflicting points of view.
+
+Dispute Finder uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims.
+Several alternative graph structures have been proposed for describing arguments and design rationale.
+WinWin~\cite{Boehm2006} models the different stakeholders and their different motives.
+The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions.
+QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions.
+More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.
 

### 2009-10-16 scala/src/com/intel/thinkscala/MainServlet.scala

@@ -465,6 +465,10 @@ class MainServlet extends HttpServlet {
     },c => {
       c.output(c.store.allSnippets(c.urlInt(1)))
     }),
+    UrlHandler("/claim/all", c => {
+    },c => {
+      c.output(c.store.allClaims)
+    }),
     UrlHandler("/claim/hot",c => {
       c.outputHtml("Hot Claims - Dispute Finder",Page.hotClaims(c))      
 //      c.outputHtml(Docs.applyXml("fragments","hot",HashMap("hot" -> c.hotClaims)))

### 2009-10-16 scala/src/com/intel/thinkscala/data/Nodes.scala

@@ -81,4 +81,7 @@ trait Nodes extends BaseData {
 	def unIgnoreClaim(claimid : Int, userid : Int) = unignore_claim.update(claimid,userid)
 
 	def hotClaims = claims(0) where ("disagree_count > 0") orderdesc ("id") rows
+	
+	val all_claims = stmt("SELECT id,text FROM v2_node WHERE type=?")
+	def allClaims = all_claims.queryRows("claim")
 }

### 2009-10-17 papers/www_disputefinder/disputefinder.tex
Fleshing out the related work - which helps inform what to write in the rest of the paper

@@
 \usepackage{color}
+%
+%\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
+%\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
+%\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
+%\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}
 
-\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
-\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
-\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
-\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}
-
-%\newcommand{\want}[1]{}
-%\newcommand{\todo}[1]{}
-%\newcommand{\idea}[1]{}
-%\newcommand{\node}[1]{}
+\newcommand{\want}[1]{}
+\newcommand{\todo}[1]{}
+\newcommand{\idea}[1]{}
+\newcommand{\node}[1]{}
 
@@
 \author{
-\alignauthor Rob Ennals\\
-       \affaddr{Intel Labs Berkeley}\\
-       \affaddr{2150 Shattuck Ave}\\
-       \affaddr{Berkeley, CA, USA}\\
-       \email{robert.ennals@intel.com}
-\alignauthor Beth Trushkowsky\\
-       \affaddr{Computer Science Division}\\
-       \affaddr{University of California at Berkeley}\\
-       \affaddr{Berkeley, CA, USA}\\
-       \email{trush@berkeley.edu}
-\alignauthor John Mark Agosta\\
-       \affaddr{Intel Labs Santa Clara}\\
-       \affaddr{2200 Mission College Blvd}\\
-       \affaddr{Santa Clara, CA, USA}\\
-       \email{john.m.agosta@intel.com}
+	Author list to be determined
 }
 
-\additionalauthors{Additional authors: Tad Hirsch (Intel Research PaPR, email: {\texttt{tad.hirsch@intel.com}}) and Tye Rattenbury (Intel Research PaPR), email: {\texttt{tye.rattenbury@intel.com}})}
+%\author{
+%\alignauthor Rob Ennals\\
+%       \affaddr{Intel Labs Berkeley}\\
+%       \affaddr{2150 Shattuck Ave}\\
+%       \affaddr{Berkeley, CA, USA}\\
+%       \email{robert.ennals@intel.com}
+%\alignauthor Beth Trushkowsky\\
+%       \affaddr{Computer Science Division}\\
+%       \affaddr{University of California at Berkeley}\\
+%       \affaddr{Berkeley, CA, USA}\\
+%       \email{trush@berkeley.edu}
+%\alignauthor John Mark Agosta\\
+%       \affaddr{Intel Labs Santa Clara}\\
+%       \affaddr{2200 Mission College Blvd}\\
+%       \affaddr{Santa Clara, CA, USA}\\
+%       \email{john.m.agosta@intel.com}
+%}
+%
+%\additionalauthors{Additional authors: Tad Hirsch (Intel Research PaPR, email: {\texttt{tad.hirsch@intel.com}}) and Tye Rattenbury (Intel Research PaPR), email: {\texttt{tye.rattenbury@intel.com}})}
 
@@
 One can use a textual entailment algorithm to recognize phrases that seem to have a similar meaning to the claim.
+We found advantages and disadvantages of all these approaches.
 
@@
 \item[What information should we show someone about a disputed claim?] If someone clicked on a disputed claim on a web page, what information should we show them that will help them decide whether to talk the alternative points of view seriously.
-Alternatives include an argumentation graph, user comments, a wiki page,
-We experimented with providing an argumentation graph, user comments, aut
+We experimented with using an argumentation graph, a summary of snippets from sources that support the two sides, automatically-found articles, and user-curated articles.
 \end{description}
@@
 
-\subsection{Highlighting Disputed Information}
+\subsection{Web Annotation Tools}
 
-Several previous tools have used highlighting to alert an author about information that they should perhaps be suspicious of.
-WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author.
-
-Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, so that they can put forward their own point of view.
-Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
+Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
 There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}.
@@
 These annotation tools all allow a user to annotate a page with their thoughts on the same topic.
-In Dispute Finder, we do not allow a user to directly express their own opinions about a topic.
+Dispute Finder does not allow a user to directly express their own opinions about a topic.
 Instead, the only way they can disagree with something that is said is to link it to an article from a trusted source that argues for a different point of view.
@@
 
-\todo{Cite google quotation stuff and Ed Chi movable quotations stuff}
+More generally, Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000,Wiil1996}.
+Like other Open Hypermedia systems, Dispute Finder lays an additional link structure over an existing hypertext document.
+In the case of Dispute Finder, the links are from disputed claims to information about those claims.
+
+Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}.
+Tagging tools allow users to collectively catagorize information by associating it with a user-created set of tags.
+In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
+
+\subsection{Sensemaking Tools}
+
+Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users.
+TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph.
+ClaimSpotter~\cite{Sereno2005,Serono2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
+Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.
+
+Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as "is an example of", "supports", or "challenges".
+An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is part of a known idea.
+
+All these tools are intended to be used to identify the source of information that is being used to reach a conclusion.
+These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.
+While Dispute Finder does allow a user to mark up a trustworthy article as being the source of information, the focus is on making it easy for a user to mark up large numbers of documets that make claims that are disputed.
+
+\subsection{Argumentation Tools}
+
+One of the design options we explored for Dispute Finder is to explain a disputed claim by showing a user a user-editable argument graph, explaining the various aspects of the issue, and linking to the various sources.
+This graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
+These tools model debate as a graph of issues, positions, and arguments.
+
+Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions.
+Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
+We encountered similar problems with using an IBIS graph to describe claims, which is why the current version of Dispute Finder presents a user with a list of articles, rather than an argument graph.
+
+Several alternative graph structures have been proposed for describing arguments and design rationale.
+WinWin~\cite{Boehm2006} models the different stakeholders and their different motives.
+The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions.
+QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions.
+
+\subsection{Recognizing Textual Entailment}
+
+The textual entailment problem is one of the standard problems in natural language processing.
+In the 3-way variant of the PASCAL Recognizing Textual Entailment (RTE) Challenge\footnote{http://pascallin.ecs.soton.ac.uk/Challenges/RTE/}, an algorithm is given two sentences T and H and asked to return one of three results: T {\it entails} H, T {\it contradicts} H, or the truth of H cannot be determined from T.
+
+Dispute Finder uses the standard Local Lexical Matching (LLM) algorithm, which is commonly used as a non-trivial baseline to which other algorithms are compared~\cite{Braz2005}.
+LLM simply reduces a sentence to a bag of lemmatized words, removes stopwords, checks for negations, and then looks at what the overlap is.
+LLM is far from being state of the art and many more sophisticated algorithms exist.
+One popular approach is to treat a sentence as being a logical formula and then attempt a logical proof, taking into account knowledge about the world~\cite{Bayer2005,Bos2005}.
+Snow et al~\cite{Snow2006} parse a phrase into a syntax tree, and then use syntax heuristics to determine entailment.
+
+While Dispute Finder would probably improve its accuracy if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a users web browser for every page they look at without causing a noticeable slowdown.
+
+\todo{Do human-guided approach that works well? Talk more about human guided task.}
+
+\subsection{Finding Disputed Information on the Web}
+
+An important part of Dispute Finder is identifying what claims are disputed. Several other authors looked at disputed information on the web.
+
+Kittur et al~\cite{Kittur2007} developed an algorithm that can determine whether a wikipedia page is about a disputed topic.
+Kittur and Chi~\cite{Kittur2009} broke down the disputed pages by catagory and found that People, Society, and Religion were the categories with the most disputed pages.
+
+Information extration tools such as TextRunner~\cite{Etzioni2008}
+
+TextRunner~\cite{Etzioni2008}
+
+\todo{cite lots of Etzioni stuff}
+
+\todo{Online Dispute Resolution}
+
+\todo{Cite Kittur et al}
 
 \subsection{Finding Repeated Information on the Web}
+
+\todo{Cite google quotation stuff and Ed Chi movable quotations stuff}
 
@@
 
-\subsection{Textual Entailment}
+\subsection{Measuring Trust}
 
-\subsection{Annotating, Tagging, Clipping, and Open Hypermedia}
+Several authors have analysed trust on Wikipedia.
+WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author.
+Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is.
+Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
+All these tools determine trustworthiness by examining the edit history of a page.
 
-Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000}.
-Like other Open Hypermedia systems, Dispute Finder allows users to lay an additional link structure over an existing hypertext document.
-Dispute Finder differs from prior open hypermedia systems in its focus on revealing contentious arguments.
-While other systems such as HyperDISCO~\cite{Wiil1996} could be used to link a snippet to a contentious claim, they do not provide user interface support to make this easy.
-
-\todo{Say how different from other Open Hypermedia link annotation systems}
-
-Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags.
-Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.
-While Dispute Finder also allows users to organize information from other sources, it does not use tags.
-
-Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001}, ScreenCrayons~\cite{Olsen2004}, and ReframeIt\footnote{http://reframeit.com} allow users to highlight sections of text on a page.
-Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends.
-Some tools highlight snippets that have been clipped by other users.
-These tools do not attempt to identify when snippets make disputed claims or to connect them to opposing sides of an argument.
-
-SpinSpotter\footnote{http://spinspotter.com} allows a user to mark snippets that contain spin or bias.
-A user can comment on why a snippet is biased and rewrite the snippet in a neutral way.
-While SpinSpotter and Dispute Finder both draw attention to biased or inaccurate snippets, they do different things with the snippets.
-SpinSpotter lets users annotate a snippet with comments specific to that particular snippet, while Dispute Finder treats a snippet as being an instance of a shared claim, and links all snippets identified as making that claim to a shared node in the argument graph that is linked to other points of view.
-
-Videolyzer~\cite{Diakopoulos2008}\footnote{http://www.videolyzer.com} allows users to annotate and comment on political videos.
-A user can attach a comment to a section of video and tag it for bias, accuracy, or rhetorical technique.
-Comments can include references to external sources that back up the argument being made.
-Like SpinSpotter, Videolyzer does not attempt to gather multiple video sections that make a common contentious claim.
-
-ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical subject-verb-object triples describing important claims made in the document.
-Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.
-Like Dispute Finder, these tools allow a user to mark the claims being made in a document, however these tools are more formal and are designed to extract knowledge rather than informally mark disputed snippets.
-
-\todo{Ask Nicholas if he would like to read the paper}
+BJ Fogg et al~\cite{Fogg2000, Fogg2003} have looked at the metrics that users use to determine when they should trust a source online.
+They found that the most important factor was whether a web site had a professional-looking design.
+Gill and Arts~\cite{Gil2006} identified on a different set of factors, including topic (a medical site may not be trusted on car repair), popularity and authority.
 
@@
 % Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.
-
-\subsection{Argumentation and Design Rationale}
-
-Dispute Finder's argument graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
-IBIS tools model debate as a graph of issues, positions, and arguments.
-While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.
-
-Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox extension to help a user create a claim about a web page they are reading.
-Unlike Dispute Finder, Cohere is not designed to be used to alert users about disputed snippets.
-Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.
-
-Although Dispute Finder's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
-In Dispute Finder the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim.
-A user is expected to create a new claim only when they want to group together several snippets that make that claim. 
-A Dispute Finder user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself.
-By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph.
-A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion.
-In Dispute Finder it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.
-
-Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions.
-Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
-We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Dispute Finder that is designed for identifying snippets that represent conflicting points of view.
-
-Dispute Finder uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims.
-Several alternative graph structures have been proposed for describing arguments and design rationale.
-WinWin~\cite{Boehm2006} models the different stakeholders and their different motives.
-The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions.
-QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions.
-More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.
 

### 2009-10-17 papers/www_disputefinder/unused.tex
Added unused.tex

Unlike most prior forms

One of the really transformative properties of the web is that it allows anyone to publish whatever they want without having to go through a higher authority that must approve everything that is written. Older mediums such as print, radio, and television, have inherent costs of publication, which led us to limit the amount that was published, and have all publication gated through a small set of publishers, distributers, and channels~\cite{shirky?}. With it's much lower publication costs, the internet has removed the need for

constraints of the medium, most information people obtain through

A consequence of this is that users are exposed to much more information that has not been vetted by an organization with a known reputation or agenda. Due to the constraints of the media, all information transmitted through print, radio, or television has had to be approved in some way by one of a small set of publishers,

With print media,

The downside of this is that, unlike print media, in which most information one encounters has been approved by a publisher with a known reputation, much of the information on the web is provided by sources that users know little about. When a user reads information on a web page, they often have little idea of the trustworthiness, competence, or biases of the author.

The downside of this is that, unlike print media, in which most information one encounters has been filtered through a publisher with a known reputation, much of the information on the web has been written by user

A consequence of this is that much of the information that one encounters on the web has not been certified by an authority that a user trusts, and so it becomes much harder for a user to decide whether they should trust the information they are reading.

\idea{Of course, old media wasn't entirely trustworthy either}

However the old way of doing things had certain advantages.

One frustrating consequence of this is that

 that much of the information on the web comes from sources that users do not know whether they can trust.

When the available media is filtered through a small number of publishers,

We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of Disputed claims. An alternative approach would be to automatically detect conflicts between statements on the web, or detect sentences that look like they are criticisi

Like Dispute Finder, several other services highlight content that users should be suspicious of.

WikiTrust~\cite{Adler2008a} highlights pass

Several authors have built tools that help people know when they should trust information on Wikipedia. Wikipedia\footnote{http://wikipedia.org}. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.

\todo{Make sure we stay in sync}

\todo{Talk about Skewz and Newstrust?}

\todo{Talk about WikiNews}

NewsTrust: users rank articles they read based on fairness, accuracy, context, and sourcing. But it's a lot of work. Shows a story in a frame with a toolbar above it. Not practical to apply to all news. People just read too much.

\todo{Cite previous work in topic detection and tracking on news stories?}

\todo{We should talk to NewsTrust and Skewz}

Skewz - shows you conservative and liberal stories - but why read the conservative one?
Feeds in stories and users drag them to their political bisas.

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube finds articles on the same topic that have different biases. MediaCloud shows which different words different news sources associate with the same topic. Unlike Dispute Finder, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.

Several authors have created tools that help users know when to trust information on 
% 
% 
% NewsCube~\cite{Park2009}.
% Wikipedia fixes Vandalism~\cite{Viegas2004}.
% Trustworthiness~\cite{Gil2006}.
% WikiTrust~\cite{Adler2008}. Wiki Dashboard~\cite{Kittur2008}.
% Wiki Scanner\footnote{http://wikiscanner.virgil.gr}.
% SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.

### 2009-10-19 papers/www_disputefinder/disputefinder.tex
Changing the body to match the structure from the intro

@@
 
-There are a number of design decisions that must be made when building a system such as this, which we will address in the remainder of the paper. In particular:
+There are several design decisions that must be made when building a system such as this, which we will address in the remainder of the paper. In particular:
 
@@
 
-For Sceptical Readers, Dispute Finder highlights disputed snippets and links them to snippets on other web sites that present alternative points of view.
-For Activists, Dispute Finder makes it easy for users to mark snippets about issues they care about and connect them into an argument graph.
+Users interact with Dispute Finder in two ways.
+Skeptical readers browse the web using the Dispute Finder Firefox extension and discover when pages they read make disputed claims.
+Activists tell Dispute Finder about disputed claims that they care about, and add evidence to support their point of view.
 
-\subsection{Browsing the Disputed Web}
+\subsection{Highlighting Disputed Claims}
 
-If a sceptical reader has installed the Dispute Finder browser extension, Dispute Finder will draw attention to snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}).
-If a user hovers their mouse over a highlighted snippet then Dispute Finder displays a tooltip giving the disputed claim.
-Clicking on a highlighted snippet reveals a visualization showing the best evidence for and against the claim, as determined by the user community (Figure~\ref{claimview}).
+Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust.
+We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.
 
-\begin{figure*}[tb]
-	\begin{center}
-	\includegraphics[width=18cm]{../screenshots/v2_panels2.png}
-	\caption{The claim graph consists of an expanding sequence of linked panels}
-	\label{panels}
-	\end{center}
-\end{figure*}
+Dispute Finder uses two mechanisms to inform a user when information on the page they are reading is disputed.
+It highlights any snippets that make the disputed claims in red, and it displays a message bar.
 
-Since the purpose of a highlight is to alert the user to claims that they had not realized were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious.
-A user can click the ``don't highlight this claim again'' button to tell Dispute Finder that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.
+The message bar alerts the user that they should look out for highlighted snippets on the current page. 
+Highlighted snippets can be difficult to see if the page is using a background color that is similar to our highlight color\footnote{We tried to choose a color that is rarely used as a background} or if the user is color blind.
+The message also provides a ``go to next snippet'' button that allows the user to step though the highlighted snippets one at a time.
 
-Normally Dispute Finder will only highlight snippets that make disputed claims that the user has not asked to ignore, and snippets marked by the user themselves.
-If the user wants to see all snippets on a page then they can do so by opening the Dispute Finder sidebar.
+The highlights show a user {\it why} Dispute Finder thinks that a page is making a disputed claim.
+In some cases Dispute Finder may have mistakenly thought an article was saying something it wasn't, or the disputed claim may be in text the user isn't interested in, such as a comment.
+If Dispute Finder has incorrectly marked a snippet as making a disputed claim then the user is encouraged to tell Dispute Finder this by clicking on the snippet and then cliking on the ``report incorrect highlighing'' button in the popup interface.
 
-\todo{ignore button}
-\todo{talk about the margin?}
-\todo{Talk about snippet and topic previewing}
+A user can discover what disputed claim Dispute Finder thinks a snippet is making by hovering their mouse over it, and can bring up more information about a claim by clicking on the snippet (Figure\ref{claimview}).
 
-\subsection{Exploring the Argument Graph}
+There is little point repeatedly telling a user that the same claim is disputed.
+In our current version, a user can ask Dispute Finder to not highlight a claim again by clicking on the ``ignore this claim]'' button in the popup interface.
+An alternative is to automatically stop highlighting a disputed claim, once the user has brought up the popup interface for it once.
+We have not yet conclusively decided which method works better.
+Requiring a user to manually opt out of a claim requires more work from the user, but also causes less user-confusion as users do not normally expect viewing something to be a destructive operation.
 
-Once a sceptical reader has identified a claim that they are interested in, they can use Dispute Finder's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.
+The Dispute Finder Firefox extension is not the only way that a user can find disputed claims.
+A web site can also opt to use the Dispute Finder API to detect disputed claims on the content that they present to users.
+This API could be particularly useful to tools like search engines and RSS feed readers that a user may use to access a large proportion of the information they consume.
+The firefox extension itself uses the same API.
+The advantage of using the Firefox extension is that it can look for disputed claims on any web site.
+The disadvantage is that it can only be used by users who use a compatible browser and are prepared to install an extension (well known to be a significant barrier to adoption\cite{extension-bad?}
 
-In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim.
-We thus created an interface that consists of an expanding horizontal array of panels where each panel provides information about the item that is selected in the panel to its left (Figure~\ref{panels}).
-If a user clicks on a link in a panel then a new panel opens to the right giving more information about the linked node.
-To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.
+\todo{Document API online}
+\todo{Change the highlight color to yellow? Auto-adjust highlight color based on background color?}
+\todo{Should we automatically adjust the highlight color, based on the background color of the page}
 
-The panel for a claim (third panel in Figure~\ref{panels}) lists evidence that will help inform the users opinion about the claim and alternative points of view.
-Evidence is categorized as either supporting, opposing, or being related-to the claim.
-The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument.
-Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.
-The panel for a snippet (last panel in Figure~\ref{panels}) shows the snippet text in the context of the web page it is part of.
-This, combined with the cascading panel interface allows a user to quickly read the evidence for and against a claim without having to leave the claim browser interface.
+\subsection{Explaining Disputed Claims}
 
-\todo{Remove ``related`` from the topics list - confuses with related claims}
-\todo{Show the other panels?}
+\subsection{Building a Database of Disputed Claims}
 
-% \begin{figure}[tb]
-% 	\begin{center}
-% 	\includegraphics[width=6cm]{../screenshots/v2_panel.png}
-% 	\caption{A claim panel presents information for and against a claim}
-% 	\label{panel}
-% 	\end{center}
-% \end{figure}
-
-We found that it was important to allow the claim browser interface to be used in two different ways.
-When a sceptical reader is browsing a web page and sees a disputed claim, they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail, it is preferable to use a full-window interface, as the small popup interface is too small to easily view large amounts of information.
-
-To preserve visual consistency, Dispute Finder uses the same claim browser interface for the small popup interface as for the full-window interface.
-When used as a popup browser, the interface shows only one panel.
-Clicking on an item in the panel scrolls the display to the right to reveal a new panel.
-If the user clicks the ``back'' button, the interface will quickly scroll left back to the previous panel.
-
-%\todo{Key issue with hypertext was not talking about things that highlighted arguments?}
-
-Dispute Finder's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of nodes: snippets, claims, and topics. 
-A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about.
-Nodes are connected together by typed, directed, links.
-There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.
-
-Dispute Finder uses the list of page titles on Wikipedia as a seed-set for its topics.
-This allows Dispute Finder to use the Wikify~\cite{Mihalcea2007} algorithm to automatically suggest topics for snippets and provides us with a comprehensive ready-made set of topics with well-maintained descriptions and synonyms.
-
-Dispute Finder's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to link type.
-While Dispute Finder's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Dispute Finder is designed for.
-We have also found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.
-
-The order in which evidence is displayed is determined by user voting.
-A user can vote for or against a particular piece of evidence by clicking on the voting buttons next to that item~(Figure~\ref{voting}).
-When a user votes for something it will be moved to the top of their list, and also make that item appear earlier for other users.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/v2_vote.png}
-	\caption{Voting buttons let users say which evidence is important}
-	\label{voting}
-	\end{center}
-\end{figure}
-
-One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions.
-Dispute Finder uses two strategies to try to reduce this problem.
-Firstly, positive votes count for more than negative votes.
-Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent.
-Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side -- though of course they may vote up bad arguments for the opposing point of view.
-We anticipate that we will eventually need to introduce a moderation system similar to that used in Wikipedia, allowing trusted users to override popular opinion when things go wrong.
-\todo{Talk about whether we know if this works}
-
-\todo{Talk about searches}
-\todo{Cite work on collaborative filtering}
-\todo{Mention the sidebar?}
-
-% If the current page contains snippets then a tab appears in the top left corner of the window.
-The tab contains a light bulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim.
-This allows a user to quickly tell if a page contains something of interest without having to scroll through the whole page.
-Clicking on the tab opens the margin.
-The margin provides a summary of all the interesting claims that users have identified on the current page and is designed to mimic the traditional margin notes that readers often write on physical documents~\cite{marginalia}.
-To emphasize the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.
-
-\subsection{Campaigning on the Disputed Web}
-
-If an Activist has installed the Dispute Finder browser extension then they can create a snippet by selecting text on a web page and selecting either ``This is disputed'' or ``This is interesting'' from the context menu (Figure~\ref{createprocess}).
-A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted that the snippet is making a claim that is disputed.
-A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be useful for readers investigating a disputed claim.
-
-The only difference between selecting ``this is disputed'' and ``this is interesting'' is that Dispute Finder remembers which you used when you marked a snippet.
-A snippet is only highlighted in red for other users if it is connected to a disputed claim.
-The main reason for having two different options is to show users what kinds of information Dispute Finder expects them to mark as snippets.
-\todo{Say something smart about the difference}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/v2_snipmark.png}
-	\caption{Use the context menu to mark a new snippet}
-	\label{createprocess}
-	\end{center}
-\end{figure}
-
-Dispute Finder does not require a user to specify the claim a snippet is making at the point at which they mark it.
-Instead, Dispute Finder encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
-One anticipated usage scenario for Dispute Finder is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
-In this case, the user can save time by first collecting all their snippets, and then attaching all the snippets to their disputed claim at the same time.
-
-Dispute Finder provides three ways for a user to associate a claim with a snippet:
-
-\begin{description}
-\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Dispute Finder will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}).
-A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates-to'' link types.
-If Dispute Finder does not suggest the right snippets then Dispute Finder can guide the suggestions by entering keywords into the text box above the suggestion list.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/v2_sugsnippet.png}
-	\caption{Claim first: Pick unfiled snippets to attach to a claim}
-	\label{snipclaim}
-	\end{center}
-\end{figure}
-
-\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Dispute Finder will show a list of all the snippets that they have marked but not yet associated with a claim or a topic (Figure~\ref{sniptopic}).
-If the user selects an unfiled snippet then Dispute Finder will suggest claims or topics that the user might want to associate with that snippet.
-As with the claim-first method, a user can guide the suggestions by entering keywords.
-If the correct claim is not suggested then the user can create a new claim by typing it into the text box and clicking the ``add'' button.
-
-\todo{Updated screenshot with ``enter new claim or search keywords'' present}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8.5cm]{../screenshots/v2_sniptopic.png}
-	\caption{Snippet first: Pick a claim or topic for each unfiled snippet}
-	\label{sniptopic}
-	\end{center}
-\end{figure}
-
-\item[Immediate:] A user can select a claim for a snippet that they have just marked.
-When a user marks a snippet, Dispute Finder will initially highlight it in blue to show that the snippet is not currently associated with a claim or topic and will not be shown to other users.
-If the user clicks on the highlighted snippet, then Dispute Finder will bring up the same suggestion panel used in the ``snippet first'' method.
-\end{description}
-
-Dispute Finder uses the same suggestion system to suggest connections between claims.
-It is important to make sure that the argument graph stays well connected as it grows.
-If users create duplicate claims or don't connect their claims to existing claims then the graph becomes less useful.
-Dispute Finder tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.
-
-When gathering ``interesting'' snippets, a user may not yet know what argument they might want to use the snippet to support, or even whether they want to use it at all.
-In such cases the user can either leave the snippet unfiled until they thing of something to use it for, or attach it to a topic in the hope that another user might find it useful.
-
-Dispute Finder uses the Wikify algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims.
-The Wikify algorithm imagines that a piece of text was on a Wikipedia page and predicts what pages that text would most likely link to based on the probability that any particular n-gram links to any particular page.
-Recall that the set of Dispute Finder topics is seeded with the set of Wikipedia page titles.
-The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to.
-Connecting claims and snippets to topics makes it easier to find other claims and snippets that might be related.
-
-\todo{Talk about previewing a topic by showing wikipedia page}
-
-Even though Dispute Finder tries to make creating and linking snippets as easy as possible, it still requires a non-trivial amount of work.
-Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks: currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog.
-Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to learn when a new page appears about an issue they are interested in.
-Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashakov2006}, and so one can achieve useful coverage by only marking up the relatively small number of very popular pages (for example major news sites).
-
-\todo{Mention about topic previewing}
-
-\todo{Allow two claims to be marked as being identical.}
-
-\todo{BUG: don't have 'add' button for snippets}
-
-\subsection{Implementation}
-
-Dispute Finder consists of a browser extension, a page annotation script, a shared database server, and a web-based claim browser interface.
-These four components are largely independent of each other and talk to each other using an open API that can also be used by other tools.
-
-The page annotation script is a javascript file that can be included into any HTML page.
-When it is run on a page it sends the page URL to the server, asking it to send back any snippets on that page.
-There are of course privacy issues here since this could allow user browsing to be tracked.
-We lessen this problem by not sending cookies or other identifying information, and making the protocol cacheable.
-In the future we hope to devise a way to reduce concerns further. 
-One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and require a user to explicitly ask for Dispute Finder to highlight snippets on a particular site.
-
-The browser extension inserts the page annotation script onto every page the browser loads. One can get the same affect by browsing through a proxy or if the page included directly by the page author.
-
-%The protocol used by the Dispute Finder server is an open REST API that other tools are free to use.
-In the future, the server may support one or more of the argumentation interchange formats that have been proposed~\cite{Rahwan2007a,McGinnis2007}.
+\subsection{Finding Snippets that Make Disputed Claims}
 

### 2009-10-19 papers/www_disputefinder/disputefinder.tex
Fleshing out the body of the paper

@@
 
+The design decisions made in Dispute Finder have been motivated by our interactions with potential users. We conducted a small survey, a series of interviews, and several rounds of user studies.
+
 \todo{Should we explicitly list what we think are our key contributions?}
@@
 
+\subsection{Persuasive Technology}
+
 % \subsection{Semantic Web}
@@
 
-The Dispute Finder Firefox extension is not the only way that a user can find disputed claims.
 A web site can also opt to use the Dispute Finder API to detect disputed claims on the content that they present to users.
@@
 \todo{Should we automatically adjust the highlight color, based on the background color of the page}
+\todo{Discuss previous work on highlighting here, rather than in related work?}
 
@@
 
-\subsection{Building a Database of Disputed Claims}
+Once a user has been informed that the page they are reading is making a disputed claim, they will typically be interested in learning more about that claim, so they can judge whether there are alternative points of view that they should take seriously.
+
+The simplest option would be to merely inform the user that the page is making a disputed claim, but provide no further information about that claim.The user could then use a tool such as a search engine to investigate the claim further.
+
+There are several reasons why it is useful to associate a claim with information justifying alternative points of view:
+
+\begin{itemize}
+\item To allow a user to quickly determine whether alternative points of view are sufficiently credible that they should take them seriously
+\item To allow users who are moderating the database to determine when no arguments exist for other points of view, and thus the claim should not be in the database
+\item To allow Dispute Finder's algorithms to determine whether the claim is disputed by someone that that particular user would take seriously.
+Although we have not yet implemented such features, we believe they will be important.
+\end{itemize}
+
+We prototyped and tested two different ways of showing a user alternative points of view to the disputed claim they are looking at:
+
+\begin{description}
+\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them an IBIS-style\cite{gibis} argumentation graph that explains the structure of the argument against the claim.
+Each claim is linked to claims that represent alternative points of view, and claims that support that point of view.
+Each claim also has a list of sources that argue in favor of that claim (Figure\ref{arg-graph?})
+
+\item[Source lists:] Dispute Finder shows the user two lists of sources, one of which contains sources arguing in favor of the claim, and the other of which contains sources arguing against the claim (Figure~\ref{article-list})
+\end{description}
+
+The argumentation graph is potentially much more powerful.
+When a user is presented with a simple list of sources, several of them may be making the same core points and it may not be obvious that one of the sources is making a point that the user had not come across before.
+The argumentation graph also allows the user to browse around the network of different claims being made about an area, which can be interesting in itself.
+
+On important disadvantage of using an argumentation graph is that someone has to build it.
+In our prototype, the argumentation graph was built entirely by users.
+We found that our users had difficulty creating well structured argumentation graphs that were useful for other users, a result that is consistent with previous studies~\cite{ibis-bad?}.
+It is possible that an alternative (simpler?) graph structure or interface that made it easier to build such graphs might make them work better.
+Argumentation graphs might also work better if they could be built automatically by mining the web.
+
+Another point in favor of using a simple list of sources is that we found that users are far more concerned with ``who'' disputes a claim, than what their argument is.
+For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with.
+The argumentation graph focusses on presenting the user with the structure of the argument against the claim, but our studies suggest that the user is likely to find this much less interesting than the authority behind the arguments against the claim.
+
+In the present version of Dispute Finder, a source can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable.
+Good sources include newspapers, universities, respected organizations, and Wikipedia itself.
+Users can vote on whether they think a particular source is useful, and this voting determines the order in which sources are listed.
+A user can also request that a source be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable sources.
+Users with moderator privileges review requests for deletion and delete claims and sources that do not meet requirements.
+
+\todo{study result: verify}
+There are significant weaknesses in this approach.
+In our studies, we found that users disagree about what they would consider a reliable source.
+Users consider a source to be reliable if it espouses opinions that they themselves agree with, and is accepted as being a reliable source within their social group.
+There may be little point showing liberal sources to a conservative, or vice-versa.
+Similarly, a global voting system can be gamed by people who want to hide good arguments against a claim that they support by voting up bad ones.
+Another problem is that, by resorting to moderators to decide which sources and claims are high enough quality to be included, we open ourselves up to charges of bias.
+
+In the future it may be better to learn what sources a particular user is likely to believe are reliable, and then adjust both what sources Dispute Finder shows to the user, and what claims are highlighted, based on this.
+
+There is a difficult trade-off here.
+If we only show users sources that we believe they are likely to trust, then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
+On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment, and stifling the voices of those who are less widely respected by the establishment, but may be right.
+If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously.
+We do not yet claim to know a good solution for this problem.
+
+\subsection{What is Disputed?}
+
+One of the key challenges for Dispute Finder is determining what claims are Disputed.
+Dispute Finder takes the approach of maintaining a database of known disputed claims, which it then looks for on web pages.
+
+What we are after is not a list of everything that has every been disputed by anyone, but a list of claims that are frequently believed and are opposed by reliable sources.
+In some sense almost everything is disputed by someone on the web.
+There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless.
+Similarly, there is little point spending effort rebutting claims that nobody believes.
+For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true.
+
+Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them.
+For example Snopes.com maintains a list of urban legends and politifact.com maintains a list of false claims about politics.
+We automatically import all claims that these sites debunk into our database and treat the sites themselves as reliable sources about the claims they debunk.
+In the future we intend to also import claims from other such sites.
+
+We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{web-add?}.
+The web interface is modeled after common issue-reporting software such as UserVoice\footnote{url?}.
+It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim.
+When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing source.
 
 \subsection{Finding Snippets that Make Disputed Claims}
+
+\todo{Do a load more people in a final user-study round. Try to get it up to 8.}
 

### 2009-10-20 papers/www_disputefinder/disputefinder.tex
Fleshed out the body more

@@
 
+\todo{Cite Pew Research study saying people like to read news that supports their own point of view, but many others like neutral sources. http://people-press.org/report/?pageid=1353}
+
 \subsection{What is Disputed?}
@@
 
-We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{web-add?}.
+We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{web-add?}).
 The web interface is modeled after common issue-reporting software such as UserVoice\footnote{url?}.
@@
 
-\subsection{Finding Snippets that Make Disputed Claims}
+\todo{Actually import the Politifact data}
 
+\subsection{Finding Snippets}
+
+Given a web page that the user is browsing, and a database of claims that we believe are disputed, how can we determine what snippets on the page are making claims that are in our database?
+We implemented and tested four approaches:
+
+\begin{description}
+\item[Explicit page marking:] If the page a user is reading contains a snippet that makes a disputed claim, the user can mark that snippet by selecting it, right clicking, and selecting "mark as disputed" from a popup menu.
+
+\item[Bulk page marking:] The user enters a paraphrase of the claim into a web UI.
+The server searches the web for snippets that resemble this phrase using Yahoo BOSS~\cite{boss?} and shows the user the snippets it found.
+The user clicks on all of the snippets that they would like to mark.
+
+\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier.
+We used a simple baysian classifier with n-grams as its features.
+As the user gives examples of snippets that do or do not entail the original claim, the classifier learns what n-grams should or should not be in a snippet.
+Once the classifier is sufficiently trained, the server applies it to the rest of the results from Yahoo BOSS to automatically mark web pages.
+We have only partially implemented this approach.
+
+\todo{Has anyone done something like this before.}
+\todo{We only partially implemented this approach}
+
+\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database.
+A user can enter additional paraphrases of a claim to help the entailment algorithm.
+This is the implementation used by the currently released version of Dispute Finder.
+\end{description}
+
+Explicit page marking has the highest accuracy, but the poorest coverage.
+Since a user is looking at the page in its entirity, they can read the snippet in context and make a good judgement about whether the snippet is indeed making the claim.
+However the manual effort required per page makes it difficult for this approach to scale.
+It can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page.
+This is the same problem that has hindered the adoption of web page annotation tools.
+
+Bulk page marking trades off some accuracy for better coverage.
+When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them.
+Since they are reading the snippet out of context, they are more likely to mark a phrase incorrectly.
+
+Server side classification trades off more accuracy for more coverage. The classifier can mark more pages than a user could ever mark manually, but is inevitably less accurate than a human.
+
+Client side entailment gets even more coverage.
+Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined.
+This is particularly important for news pages, which are frequently read only a few minutes after they have been written.
+Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.
+
+The client side entailment method uses the standard Local Lexical Matching algorithm that is a common baseline in NLP.
+It divides the page into sentences, strips out stopwords, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
+If the claim contains a negation word (e.g.
+not, never, can't) then so must the matching sentence.
+
+\todo{Discuss how and why this is simpler than the server-side classification method}
+\todo{Explain how we avoid downloading the entire database}
+
+The client side entailment method uses a simpler algorithm than the server-side classifier.
+
+\todo{Should we have a version where the interface merely suggests n-grams that should be used by the classifier}
+\todo{Can we present all these systems without giving detailed stats about how they compare?}
+\todo{Add support for a user to enter 'anti-phrases' when a snippet is wrongly highlighted}
+\todo{Add support for a user to enter a paraphrase that will match the snippet they are looking at}
 \todo{Do a load more people in a final user-study round. Try to get it up to 8.}
+\todo{Explain how our algorithm relates to existing NLP work - due to unusual domain}
 

### 2009-10-22 papers/www_disputefinder/disputefinder.tex
Did the user study section - now no longer just the UIST text

@@
 
-\section{User Studies}
+\section{Studying the Users}
 
-We performed two qualitative ``think aloud'' user studies.
-The aim of these studies was to inform the development of Dispute Finder.
+The Design of Dispute Finder has been influenced by several different kinds of input from potential users.
+We performed a series of "think aloud" user studies to evaluate the user interface, we circulated a survey among members of a local debate club, and we performed a series of interviews with people selected from those who completed the survey.
+
+\subsection{Survey}
+
+\subsection{Interviews}
+
+\subsection{Think-Aloud User Studies}
+
+We performed three qualitative "think aloud" user studies.
+The aim of these studies was to inform the iterative design of the Dispute Finder tool.
 The studies were not intended to validate the design of Dispute Finder as being correct.
-Dispute Finder is designed to be used by a large number of users gathering a vast amount of evidence for many different claims.
-To confidently state that our design was successful we would need to be able to test Dispute Finder on a much greater scale than we currently have resources for.
+The only way we will be able to truly validate Dispute Finder is by having it be adopted by a large community of active users - something it is not yet mature enough for.
 
-The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Dispute Finder argument graph.
-The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page.
-We present the results of the two studies together.
+\subsubsection{Procedure}
 
-These studies identified some usability problems which we responded to with changes to the user interface which we describe below.
-We conducted a lightweight evaluation of our final interface and it seemed our revisions successfully addressed the usability concerns.
+For the first two studies, we recruited participants using Craigslist.
+We posted a message asking people to tell us how they used the web to form and promote their opinions, and used this to select people who we thought might fit our "skeptical reader" and "activist" personas.
+After these studies, we decided that the kind of person who looks for jobs of craigslist is unlikely to be a good fit for our personas, and so for the final study we instead used people we knew personally and thought fit our personas well.
+All study groups were small.
+The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had ??
+participants (??
+male, ??
+male).
 
-\todo{Test with at least 4 people}
-\todo{Say something about final informal evaluation}
-%After the second study, we made minor changes to our user interface (described below) and performed an informal user study with people in our organization to
+Each batch of users was shown a different iteration of the Dispute Finder design.
+The first two batches used versions in which users marked snippets explicitly, and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view.
+The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim.
+We present the findings of the three user studies together.
+Where a comment refers to particular version we make this clear.
 
-\subsection{Procedure for the First Study}
+Study sessions took approximately fourty five minutes.
+Participants were seated at a workstatation with the Firefox browser augemented with the Dispute Finder extension.
+They were asked to view pages that had highlighted claims on them, and to attempt to add new disputed claims to our database.
 
-For the first study we recruited twelve paid participants, five female, seven male, aged 18 to 52.
-Nine participants maintained a blog.
-We recruited participants by posting an advert on Craigslist\footnote{http://craigslist.org}.
-Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas.
-In our advert, we asked people to tell us what kind of information they looked at on the web and how they shared information with others.
-We selected participants who looked at information that was likely to be disputed (e.g.
-political commentary) and who said they regularly shared information with friends.
+\todo{Need to finish the third wave of user studies}
 
-\todo{This was a bad recruiting strategy. We should have recruited people that fitted one of our two personas and then set them tasks that fitted our vision for that persona.}
-
-Study sessions took approximately forty five minutes.
-Participants were seated at a single-screen workstation with the Firefox browser augmented with the Dispute Finder extension.
-We first demonstrated Dispute Finder's interface, and then asked them to find information as they would normally and use Dispute Finder to mark snippets that made claims that they thought were interesting or disputed.
-For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.
-
-In this initial study, users were exposed to the prototype interface shown in Figures~\ref{oldsnippetbox} and \ref{oldbrowser}, rather than the final interface described earlier in this paper.
-We discuss some of the key differences in the findings section.
-
-\subsection{Procedure for the Second Study}
-
-For the second study, we recruited six paid participants, four female, two male.
-Four participants had a blog.
-Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the local university semester meant that five of the participants were college students.
-
-In the second study we were more confident about usability and so told the participants nothing about how to use it.
-We gave each user a brief description of the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it.
-The first task was to look at a selection of web pages that already had highlighted snippets and to explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case).
-The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).
-
-Participants were shown the prototype interface shown in Figures~\ref{secondbrowser} and \ref{secondsnippetbox}.
-This was similar to the interface described earlier in this paper, except that it used drag and drop to make connections rather than a suggestion system, it did not offer a ``relates-to'' link between claims, it required a user to choose a claim at the point at which they create a snippet, and the claim browser only showed one panel at a time.
-
-\subsection{Findings}
-
-In this section we present the findings from our two user studies. Findings from the two studies are presented together and clustered by topic.
-
-\subsubsection{High-Level Impressions}
+\subsubsection{Findings}
 
 Response was generally positive, with many participants being very keen to use the tool soon.
-One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed.
+Several participants asked as to notify them when it is properly deployed.
 Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
 
-Most participants said that they would want to use Dispute Finder to tell them when information they read was disputed (sceptical reader).
+Most participants said that they would want to use Dispute Finder to tell them when information they read was disputed (skeptical reader).
 One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
-A smaller number said they would be likely to mark up claims they disagreed with (activist).
-One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.
+A smaller number said they would be likely to enter claims they disagreed with (activist).
+One participant who was a political blogger was very excited about the mark things he thought were lies.
 
-Most participants in the first study, and all participants in the second study were able to use the tool competently.
-Participants in the second study were able to use Dispute Finder competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant.
-Participants said they found the tool ``very intuitive'' and ``really cool''.
+Most users were able to use Dispute Finder compentently as a skeptical reader (browsing information about disputed claims) but found it harder to act compentently as an activist (adding new disputed claims).
 
-\subsubsection{Choosing a Claim for a Snippet}
+When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed.
+Not all users realised that one could click on a disputed claim to bring up more information.
 
-\begin{figure}[t]
-	\includegraphics[width=8.5cm]{../screenshots/oldsnipcreate_diagram.png}
-	\caption{First Prototype Snippet Creation Dialog}
-	\label{oldsnippetbox}
-\end{figure}
+%In the first study, a user could mark a snippet by 
+%
+%In the interface used in the first two studies, a user could mark a snippet by selecting it, right clicking on it, and clicking "mark as disputed".
+They were then prompted to either select an existing claim or create a new one.
 
-\begin{figure}[t]
-\begin{center}
-	\includegraphics[width=5cm]{../screenshots/newsnip_browseopen.png}
-	\caption{Second Prototype Snippet Creation Dialog}
-	\label{secondsnippetbox}
-\end{center}
-\end{figure}
+When asked to mark snippets on a particular page that make disputed claims, users often did not appreciate that they should either re-use existing claims or create claims that would be applicable to snippets on many other pages.
+Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to "enter the text again".
+Similarly, users got confused when a snippet made two different disputed claims.
+The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as "Global warming will cause X and Y".
 
-The prototype interfaces required that a user enter a claim for a snippet at the point at which they created the snippet.
-When the user marked a snippet, Dispute Finder would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype).
-There turned out to be several problems with this approach:
+Conversely, when adding a claim to the Dispute Finder web site, users would often enter claims that are not disputed anywhere on the web, or enter paraphrases that do not resemble the wording used on any web site.
+The challenge of how to help users come up with claims that occur on many web sites is one that we have not yet solved.
 
-Users would often encounter a snippet that could be interpreted as making several interesting claims and were confused by the need to pick only one claim.
-Some users dealt with this by writing a compound claim such as ``Global warming will cause X and Y'', while other users marked several overlapping snippets making different claims.
-In the final interface one can associate a snippet with several claims.
+Several users expressed confusion about how specific a claim they created should be.
+For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information?
+In order to make a good judgement, one needs to know the range of similar claims that are being made by other web sites, and what claims one has good evidence against.
+If one makes the claim too specific then one will be able to find less web pages that make it, but if one makes the claim too general then it might be harder to find solid evidence against it.
 
-Some users wanted to associate a snippet with a topic but without associating it with a specific claim.
-For example, they might find the text of an important speech, or the results of a sporting event.
-While they might want to use this as evidence for a claim in the future, they didn't yet know what that claim might be.
-In the final interface one can choose to associate a snippet with a topic.
+When adding sources that support or oppose a claim, a user would frequently mark the first paragraph of the article rather than seeking out the sentence that best summarized the argument that the article was using against the claim.
+In some cases the first paragraph is indeed the right text to select, since the first paragraph is typically a summary of the core argument made by the articles.
+Several users wanted to mark up a table or image as the summary of an article, which is not currently supported.
 
-Some users seemed to be deterred from marking interesting snippets by the mental effort required to choose an appropriate claim.
-In several cases, we saw a user pause to decide whether an interesting snippet was worth marking up.
-Similarly, some users seemed to find it difficult to decide what the right claim to use for a snippet was, since they had not yet decided how they wanted to structure their argument, or even if this was a topic they wanted to argue about.
-The final interface does not require a user to associate a snippet with a claim at the time they create the snippet.
-Instead a user can mark snippets with minimal effort and then later search through their snippets to find evidence for particular claims.
+In the first two studies, the popup interface for a claim showed an argumentation graph.
+This graph connected the graphs in our database using "supports" or "opposes" links, and allowed each claim to also be associated with supporting articles.
 
-Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one.
-For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information?
-In the final interface, users are expected to only create a claim when they have several snippets that support or oppose the same claim.
-This makes it easier to know how broad the claim should be as the user knows how much information is shared by claims.
+When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected.
+One user said "I can see myself getting addicted to this", and another said "it's very intuitivet".
 
-Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they could make the dialog go away. 
-Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet.
-The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and have a particular disputed claim in mind.
-
-\todo{Need to do some kind of evaluation to show that the new interface solves these problems}
-
-\subsubsection{Choosing what to mark as a snippet}
-
-Users would frequently mark the first paragraph of an article as a snippet.
-This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.
-
-Several users wanted to mark up a table or an image as a snippet.
-This is valid behavior -- a table or image is often useful evidence for a claim; however it is not currently supported by Dispute Finder.
-In future versions of Dispute Finder we intend to support this behavior.
-
-\subsubsection{Connecting Claims}
-
-Several participants expressed a desire to connect related claims during their session.
-
-Some users marked one claim as supporting another when it would have been more logically correct to mark them both as supporting a third claim that needed to be created.
-For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing problems''.
-Users realized that the claims were related, but were not sure how best to connect them.
-It is possible that creating logically correct claim structures may be too difficult for some people (see Isenmann and Reuter~\cite{Isenmann1997}).
-We believe that this problem can be addressed to some extent though voting by other users who recognize that a claim does not provide useful evidence.
-
+Users seemed to have difficulty creating such graph structures however.
+Some users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim.
+For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems".
+Users correctly realised that the claims were related, but were not sure how best to connect them.
 Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship.
 For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''.
-Similarly, many users expressed a desire to mark claims as being related without supporting or opposing each other.
-For example ``America did not sign the Kyoto Protocol'' {\it  relates-to} ``America was right to not sign the Kyoto Protocol''.
-In the final interface we introduced a ``relates-to'' link type to allow users to connect claims that they thought should be related but which didn't confirm to a simple pro/con relationship.
+It is possible that creating logically correct claim structures may be too difficult for some people (see Isenmann and Reuter~\cite{Isenmann1997}).
 
@@
 
-Several users expressed an interest in being able to mark a claim as disputed without having to find opposing evidence.
+Several users expressed an interest in being able to add a disputed claim without having to find opposing evidence.
 One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
-In the future we are planning to allow users to say what claims they personally believe are true or false and see what claims their friends agreed or disagreed with.
 
-\begin{figure}[tb]
-	\includegraphics[width=8cm]{../screenshots/oldpoint_diagram.png}
-	\caption{First Prototype Claim Browser}
-	\label{oldbrowser}
-\end{figure}
+Several users created claims that had ambiguous meanings.
+One user entered a disputed claim about "Wood", meaning the guitarist "Ronnie Wood" of the Rolling Stones.
+Similar problems occured with claims that were specific to a particular country, or a particular point in time.
 
-\begin{figure}[tb]
-\begin{center}
-	\includegraphics[width=5.5cm]{../screenshots/claimbrowse.png}
-	\caption{Second Prototype Claim Browser}
-	\label{secondbrowser}
-\end{center}
-\end{figure}
+\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"oppsose" graph.}.
 
-The prototype versions of Dispute Finder used a drag-and-drop interface to allow a user to create links between claims.
-In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find others' claims and then drag them into appropriate positions in the argument graph.
-The second interface (Figure~\ref{secondbrowser}) followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between.
-In both cases, we found that users would often not realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}).
-We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and the rendering of a claim did not have any visual clue to suggest that they could use drag and drop to create connections.
-In the final interface we resolved this issue by moving to a ``click to link'' interface and having the connection actions (``add claim'' etc) prominently visible.
+\todo{Come up with terminology for marking an evidence snippet, and agree on evidence vs source vs article}
+\todo{Talk about how the early versions conflated evidence and snippets - and whether it makes sense to distinguish between them}
+\todo{Screenshot of the claim graph interface}
 

### 2009-10-23 papers/www_disputefinder/disputefinder.tex
Minor changes to the abstract, intro, and conclusions

@@
 
-We describe Dispute Finder, a browser extension that helps a user know when information they read online is disputed -- where by 'disputed' we mean that a source that they might trust expresses a different point of view.
-As a user browses the web, Dispute Finder examines the text on pages that the user is browsing and highlights any phrases that appear to be supporting claims from its database of known disputed claims.
-If a user clicks on a highlighted phrase, Dispute Finder will show the user a summary of arguments from other sources that support other points of view.
+We describe Dispute Finder, a browser extension that alerts a user when information they read online is disputed by a source that they might trust.
+Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that appear to entail claims in its database of known disputed claims.
+If a user clicks on a highlighted phrase then Dispute Finder will show the user a summary of articles that support other points of view.
 
-Disputed Claims can be submitted by users, or may be found automatically by crawling web sites that already maintain lists of disputed claims.
+Dispute Finder builds it's database of disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed.
 Dispute Finder identifies instances of disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of a subset of our claim database.
@@
 
-We have introduced the idea of highlighting disputed claims and connecting them to sources that give alternative points of view.
-We have created an interface that makes it easy for users to explore evidence that supports or opposes a claim, and makes it easy for users to gather and connect new snippets.
+We have introduced the idea of creating an Open Hypermedia system that automatically highlight snippets on the web that are disputed by sources you might trust.
+We have explored several different design options, tested multiple variants on users, and reported insights from this testing.
 
-At present Dispute Finder relies on users to mark up snippets and connect them to claims.
-In the future we plan to explore using natural language and machine learning techniques to assist in this process.
-Our plan is to allow a user to request that Dispute Finder search the web to find potential snippets that make a claim that they disagree with, and then quickly select which of these are indeed making the claim.
+An experimental preview version of Dispute Finder is available at the following URL:
+\url{http://disputefinder.org}
 
-Dispute Finder is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics.
-Since our graph and user base are currently small, we have not yet evaluated how Dispute Finder works when data sets are huge, many users are concurrently editing data, and some users are malicious.
-
-We hope that Dispute Finder will make it easier for people to be informed about the world and be exposed to alternative points of view that they might not otherwise be exposed to.
+Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users.
+We do however believe that Dispute Finder attacks an interseting problem that, if solved well, could significantly improve the utility of the web.
 
@@
 
-Acknowledgements omitted for blind submission. Dispute Finder uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.
+\todo{Do we want to have acknowledgements}
+% We would like to Thank Barbara Rosario for help with textual entailment, and 
+% Acknowledgements omitted for blind submission. Dispute Finder uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.
 

### 2009-10-24 papers/www_disputefinder/disputefinder.tex
Related work improved. Also some changes to the intro. Still need to do another pass over the system section.

@@
 \todo{update screenshots}
+\todo{should this be spun as about news, or information in general}
+\todo{need to talk more about what we know about people}
+
+% The last few years have seen the rapid decline of printed newspapers and rapid rise of the web as a source of news~\cite{pew-news?}.
 
@@
 If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
-Even if a user tries to be careful, they can still be caught out by claims that they had not realized were disputed.
-\todo{word this better}\todo{update all screenshots}
-
-In this paper we describe Dispute Finder, a service that informs a user when information they read online is disputed by a source that they might trust.
-Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in.
-
-If a user has installed the Dispute Finder browser extension then it will highlight snippets of text on the web that make claims that Dispute Finder believes are disputed (Figure~\ref{highlight}). 
-When a user clicks on a highlighted snippet, Dispute Finder will present a list of articles that present alternative points of view, each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).
-
-Dispute Finder consists of a database, an API, and a firefox browser extension.
-The database contains information about the disputed claims that are known to be made on web sites, and hints about how to tell when a web page is making such a claim.
-The API allows an external client to determine whether particular content is making a disputed cliam.
-The firefox extension uses the API to determine whether the web pages a user browses make disputed claims.
-The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{../screenshots/v2_highlight_shadow.png}
-	\caption{Dispute Finder highlights snippets that make disputed claims}
+	\includegraphics[width=8cm]{pictures/highlight_abortion.png}
+	\caption{A highlighted snippet that makes a disputed claim}
 	\label{highlight}
@@
 	\begin{center}
-	\includegraphics[width=8cm]{../screenshots/v2_popup_dim2.png}
-	\caption{Click on a snippet to investigate evidence for the claim it makes}
+	\includegraphics[width=6cm]{pictures/popup_abortion.png}
+	\caption{Popup interface with articles for and against a claim}
 	\label{claimview}
@@
 \end{figure}
+\todo{Popup interface should contain a "don't mark this" button}
 
-There are several design decisions that must be made when building a system such as this, which we will address in the remainder of the paper. In particular:
+\todo{More screenshots/graphs/visual information}
+
+In the realm of News, Pew~\cite{pew-news} report that, while internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible.
+Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.
+
+\todo{word this better}\todo{update all screenshots}
+
+In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust.
+Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in, understand why other people hold different points of view, and avoid being mislead by misinformation.
+
+A user can install Disute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser.
+When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}).
+If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward different points of view,  each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).
+
+Dispute Finder consists of a database, an API, and a Firefox browser extension.
+The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to recognise them when they appear on a web page.
+The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims.
+The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims.
+The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.
+
+\todo{Figure that does a smaller highlight}
+
+There are several design decisions that must be made when building a system such as this. In particular:
 
 \begin{description}
-\item[What claims are disputed?] In order to highlight claims as being disputed, we need to know what claims these are.
-To be useful, the set of known disputed claims needs to be both large (so people see some benefit) and accurate (so that people don't get annoyed by things that aren't actually disputed.
+\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users aren't distracted by things that they would not consider to be disputed).
 We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims.
-There are also other interesting alternative approaches that may be worth exploring.
+More generally, the challenge is not to determine if a claim is disputed by {\it anyone} but to determine whether there is an alternative point of view that this particular user would take seriously.
 
-\item[What disputed claims should we tell the user about?] In some sense almost everything is disputed by someone.
-If we highlighted everything that was disputed by anyone then the tool would be too noisy to be useful.
-The challenge is to determine when the other point of view is something the user might take seriously.
-We do not yet have a large enough database of disputed claims for this to be a serious problem, but we believe that there may be interesting solutions.
-
-\item[How do we tell that a snippet is making a disputed claim?] If a user is reading a web page that might contain disputed claims, then how do we determine which sentences are making disputed claims?
+\item[How do we find disputed snippets?] Given a particular web page, how do we determine which phrases on that page are making known disputed claims?
 We have experimented with several different approaches, each of which has different advantages and disadvantages.
@@
 One can provide an interface that allows a user to train a machine learning classifier to recognize snippets.
-One can use a textual entailment algorithm to recognize phrases that seem to have a similar meaning to the claim.
-We found advantages and disadvantages of all these approaches.
+One can run a textual entailment algorithm on the client that looks for phrases that look similar to a known claim.
 
-\item[How do we add highlights to the pages a user browses?] If a user is reading web pages, how should we augment that experience with information about disputed claims?
+\item[How do we highlight snippets?] How do we tell what web page a user is reading, and augment their interface to alert them about disputed claims?
 Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension~\cite{nolike-extension?}.
 Using a proxy~\cite{proxy?} has similar adoption problems to a browser extension, and is likely to break some web sites.
-Providing an API allows external sites such as news readers and search engines to provide information about disputed claims, but limits coverage to those sites that support the API.
-The best approach may be a combination.
+If external sites such as news readers and search engines use our API then they can provide information about disputed claims to users without them having to install anything, but this limits coverage to content accessed through sites that use the API.
 
-\item[What information should we show someone about a disputed claim?] If someone clicked on a disputed claim on a web page, what information should we show them that will help them decide whether to talk the alternative points of view seriously.
-We experimented with using an argumentation graph, a summary of snippets from sources that support the two sides, automatically-found articles, and user-curated articles.
+\item[How should we explain a disputed claim?] If someone requests more information about a disputed claim by clicking on a highlighted snippet, what information should we show them that will help them decide whether to consider alternative points of view?
+We tried an argumentation graph and lists of articles that support or oppose the claim.
 \end{description}
 
-In order for Dispute Finder to be useful, it needs to provide a service that users will actually appreciate.
-It is thus important that we understand how users feel about disputed information.
+If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use.
 Dispute Finder is designed to cater to two personas.
-Each persona was created from interviews we conducted with people who we believe fit into these categories:
+Each persona was created from interviews we conducted with people who we believe fit into these categories.
 
+{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust.
+Their are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic.
+A user may behave like a skeptical reader for some topics and not others.
+For example a user may be skeptical when reading about topics that affect them (e.g.
+health, things important to their job, or things they are expected to be knowledgable about), but disengaged when reading about topics that don't affect them (e.g.
+entertainment) or topics for
 \todo{Use interviews to get some actual observations here. These are just fillers.}
 
-\begin{description}
+{\it Activists} care strongly about particular issues and are prepared to spend some time helping others know that something that they disagree with is disputed.
+They are the same kinds of people who join protest groups, write blogs, email news stories, or argue about topics online.
+They are motivated by a desire to influence others and to gain status by being seen to do so.
+A user is likely to be an activist on some issues, but not for others.
+An activist will often also be a skeptical reader.
 
-\item[Skeptical Readers] want to know when information they read is disputed.
-They are primarily motivated by a desire to avoid being misled.
-Although there are some sources that they strongly trust, they also regularly read web sites that they do not trust, and they are worried about being misled.
-In the abscence of Dispute Finder, they often try to verify information they read online by searching several web sites on the same topic, or checking something they have read on a known trusted site.
+Many users fall into neither of these two personas.
+If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then Dispute Finder is unlikely to be useful for them.
 
-\item[Activists] care strongly about particular issues and are prepared to spend some time helping other users know that something they read is disputed.
-They are the same kinds of people who join protest groups, argue about topics online, post stories to news aggregators, or edit wikipedia.
-They are motivated by a desire to gain status by being publically seen to have led others to discover that important issues are disputed.
-They are also motivated by a desire to entertain themselves by seeing what disputed claims are being made and where online they are being made.
-
-\end{description}
+We used several different methods to gain input from users.
+We performed three rounds of users studies, circulated a survey within a target group, and conducted a series of interviews.
+We discuss the conclusions of these studies throught the paper, and in a section at the end.
+These studies were intended to inform the design of Dispute Finder, rather than to validate it.
+The only way to conclusively demonstrate that Dispute Finder is useful would be for it to be adopted by many active users -- something that the current implementation is not mature enough to support.
 
@@
 
-The same user may be an Activist for some issues and a Sceptical Reader for others.
-Dispute Finder is not useful for everyone.
-In our interviews, we encountered several people who either didn't rely on the internet as an important source of information, or only obtained important information from sources that they trust.
-If a user never reads information they care about from web sites that they don't entirely trust, then Dispute Finder will not be useful to them.
-
-The design decisions made in Dispute Finder have been motivated by our interactions with potential users. We conducted a small survey, a series of interviews, and several rounds of user studies.
-
 \todo{Should we explicitly list what we think are our key contributions?}
@@
 
-Dispute Finder builds on prior work in several different areas.
+Dispute Finder builds on prior work in many different areas.
 The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
@@
 If one is aware that an issue is controversial and wants to understand the different sides, then one can use sites like Wikipedia.org, Debate.org, and ProCon.org.
-These sites do an excellent job at presenting accurate and balanced information about controversial topics.
+These sites do an excellent job presenting accurate and balanced information about controversial topics.
 
-Dispute Finder is designed to deal with the cases where the user is not aware that the information they are reading is disputed and so does not realise that they should check it on one of these services, or does not know which of these services might have more information.
-Dispute Finder is designed to work together with fact checking sites like Snopes and Politifact.
-Indeed Dispute Finder automatically imports disputed claims made on Snopes or Politifact into its claim database, and will use articles from Snopes and Politifact as evidence about disputed claims.
+Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realise that they should check it on one of these services.
+Dispute Finder is designed to work together with fact checking sites.
+Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.
 
@@
 
+While Dispute Finder is not intended to be applied only to news content, News is a particularly interesting source of disputed information, and one that others have looked at before.
+
 News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
 The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader persective of the issue.
-Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the slant of the entire article.
+Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overal slant of the article.
 A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.
@@
 
-Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
-There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}.
+Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content.
+Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
+There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features.
 
-These annotation tools all allow a user to annotate a page with their thoughts on the same topic.
-Dispute Finder does not allow a user to directly express their own opinions about a topic.
-Instead, the only way they can disagree with something that is said is to link it to an article from a trusted source that argues for a different point of view.
-We believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
+Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic.
+Instead, the only way they can add promote an opinion is to link to an article from a trusted source that argues for that opinion.
+Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
 
-Another key difference between these annotation tools and Dispute Finder is that these annotation tools all allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
+Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
 If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
-By contrast, if a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that it appears.
+If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears.
+The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.
 
@@
 
-\subsection{Sensemaking Tools}
+\subsection{Sensemaking and Argumentation Tools}
 
@@
 TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph.
-ClaimSpotter~\cite{Sereno2005,Serono2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
+ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
 Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.
@@
 Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as "is an example of", "supports", or "challenges".
-An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is part of a known idea.
+An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.
 
-All these tools are intended to be used to identify the source of information that is being used to reach a conclusion.
+The intention behind these tools is that a user uses them to identify the source of information that is being used to motivate a conclusion.
 These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.
-While Dispute Finder does allow a user to mark up a trustworthy article as being the source of information, the focus is on making it easy for a user to mark up large numbers of documets that make claims that are disputed.
 
-\subsection{Argumentation Tools}
-
-One of the design options we explored for Dispute Finder is to explain a disputed claim by showing a user a user-editable argument graph, explaining the various aspects of the issue, and linking to the various sources.
-This graph is inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
-These tools model debate as a graph of issues, positions, and arguments.
+We experimented with several different ways of explaining a disputed claim to a user.
+One of the approaches we implemented was a user-editable argumentation graph that connected each claim to other claims that support and oppose it, in addition to articles that argue in favor of that claim.
+This graph was inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
 
@@
 Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
-We encountered similar problems with using an IBIS graph to describe claims, which is why the current version of Dispute Finder presents a user with a list of articles, rather than an argument graph.
-
-Several alternative graph structures have been proposed for describing arguments and design rationale.
-WinWin~\cite{Boehm2006} models the different stakeholders and their different motives.
-The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions.
-QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions.
+We encountered similar problems with using an argumentation graph in Dispute Finder, which is why the current version of Dispute Finder presents a user with a list of articles rather than an argument graph.
 
@@
 
+\todo{Trim this down??}
+
 The textual entailment problem is one of the standard problems in natural language processing.
-In the 3-way variant of the PASCAL Recognizing Textual Entailment (RTE) Challenge\footnote{http://pascallin.ecs.soton.ac.uk/Challenges/RTE/}, an algorithm is given two sentences T and H and asked to return one of three results: T {\it entails} H, T {\it contradicts} H, or the truth of H cannot be determined from T.
+In the 3-way variant of the PASCAL Recognizing Textual Entailment (RTE) Challenge\footnote{http://pascallin.ecs.soton.ac.uk/Challenges/RTE/}, an algorithm is given two sentences T and H and asked to return one of three answers: T {\it entails} H, T {\it contradicts} H, or the truth of H cannot be determined from T.
 
-Dispute Finder uses the standard Local Lexical Matching (LLM) algorithm, which is commonly used as a non-trivial baseline to which other algorithms are compared~\cite{Braz2005}.
-LLM simply reduces a sentence to a bag of lemmatized words, removes stopwords, checks for negations, and then looks at what the overlap is.
+Several of the core challenges in Dispute Finder are forms of the textual entailment problem.
+Finding disputed claims is a special case of finding two sentences on the web, such that one {\it contradicts} the other.
+Finding a snippet that makes a disputed claim is a special case of finding a snippet that {\it entails} a disputed claim.
+
+One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it condradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical.
+Dispute Finder thus instead uses separate approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims.
+Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.
+
+Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims.
+The algorithm we use is a simple varient of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}.
+LLM simply reduces a sentence to a bag of lemmatized words, removes stopwords, checks for negations, and then looks at what the overlap is between the words in the two phrases.
+Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.
+
+\todo{Implement word weighting and word similarity?}
+
+%Following the taxonomy used by Jijkoun and Rijke~\cite{Jijkoun2006} our algorithm is M-sim-imp, that is, we assign entailment scores based soley on word overl
+%
+%The algorithm we use is a simple Local Lexical Matching (LLM) algorithm.
+
 LLM is far from being state of the art and many more sophisticated algorithms exist.
-One popular approach is to treat a sentence as being a logical formula and then attempt a logical proof, taking into account knowledge about the world~\cite{Bayer2005,Bos2005}.
-Snow et al~\cite{Snow2006} parse a phrase into a syntax tree, and then use syntax heuristics to determine entailment.
+Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
 
-While Dispute Finder would probably improve its accuracy if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a users web browser for every page they look at without causing a noticeable slowdown.
+While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
+Naturally, as processor speeds improve, it will become practical to use increasingly sophisticated algorithms.
 
+\todo{Talk about Glickman et all 2005 and MT system of Bayer et al 2005}
+\todo{Cite Web Based probabalistic textual entailment}
+\todo{Cite MITRE's submission to the EU PASCAL RTE Challenge}
+
+\todo{Talk a lot about how people do textual entailment now}
 \todo{Do human-guided approach that works well? Talk more about human guided task.}
+
+\subsection{Finding Repeated Information on the Web}
+
+\todo{is this important}
+
+When Dispute Finder highlights many snippets that make a single disputed claim, this is a special case of the more general task of finding repeated information on the web.
+Kolak and Schillit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
+MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news soures and blogs.
+
+\todo{Cite plagarism detection}
+\todo{Talk about how our algorithm looks for key terms used in disputed claims}
+\todo{Talk about how our first pass NLP algo is rather like }
 
@@
 
+\subsection{Extracting Information from the Web}
+
 Information extration tools such as TextRunner~\cite{Etzioni2008} 
+Read The Web
 
@@
 
+\cite{SnowBall}
+\cite{Read The Web}
+\cite{Information Extraction from Wikipedia}
+\cite{KnowItAll}
+\cite{TextRunner}
+
 \todo{Online Dispute Resolution}
@@
 \todo{Cite Kittur et al}
-
-\subsection{Finding Repeated Information on the Web}
-
-\todo{Cite google quotation stuff and Ed Chi movable quotations stuff}
-
-A key component of Dispute Finder is that in needs to identify phrases on the web that make a know disputed claim.
-The techniques that Dispute Finder uses have been influenced by related work that does similar things.
-
-\cite{Kim2009} Efficient Overlap and Content Reuse Detection.
-
-\cite{schillit?}
-
-Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.
-Dispute Finder also creates new links between information, but it's links are created by users, rather than being mined automatically.
-
-\cite{Something by Ed CHi about this}
-
-\todo{Talk about textual entailment}
-
-\todo{Talk about MemeTracker}
 
@@
 
-\subsection{Highlighting Disputed Claims}
+\subsection{Highlighting Snippets}
 
@@
 We prototyped and tested two different ways of showing a user alternative points of view to the disputed claim they are looking at:
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/popup_graph_crop.png}
+	\caption{Argumentation graph interface for a disputed claim}
+	\label{popup_graph}
+	\end{center}
+\end{figure}
 
@@
 
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/add_claim.png}
+	\caption{Interface for adding a new disputed claim}
+	\label{add_claim}
+	\end{center}
+\end{figure}
+
 Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them.
@@
 We implemented and tested four approaches:
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/mark_disputed.png}
+	\caption{Explicit page marking}
+	\label{mark_disputed}
+	\end{center}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=7cm]{pictures/training.png}
+	\caption{Bulk page marking}
+	\label{training}
+	\end{center}
+\end{figure}
 
@@
 
+The biggest problem that Dispute Finder has right now is that it is rare that Dispute Finder will highlight a snippet that makes a claim that the user did not already know was disputed.
+This is for two reasons: our database of disputed claims is currently too small (around two thousand claims at the time of writing), and our textual entailment algorithm is not sufficiently sophisticated to stand a good chance of highlighting snippets when they make those claims.
+
+The biggest problem that Dispute Finder has right now is that its coverage is not very high.
+Both our database of disputed claims, and the number of snippets that we highlight that make each disputed claim
+
+In its current state, it is unlikely that a user will see a snippet highlighted that makes a claim that they did
+
 \todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"oppsose" graph.}.

### 2009-10-25 papers/www_disputefinder/disputefinder.tex
Improved system description

@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/popup_abortion.png}
+	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
 	\caption{Popup interface with articles for and against a claim}
@@
 \item[How do we highlight snippets?] How do we tell what web page a user is reading, and augment their interface to alert them about disputed claims?
-Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension~\cite{nolike-extension?}.
-Using a proxy~\cite{proxy?} has similar adoption problems to a browser extension, and is likely to break some web sites.
+Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension.
+Using a proxy~\cite{Barrett1997} has similar adoption problems to a browser extension, and is likely to break some web sites.
 If external sites such as news readers and search engines use our API then they can provide information about disputed claims to users without them having to install anything, but this limits coverage to content accessed through sites that use the API.
@@
 Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
+Tools such as AuContraire~\cite{Ritter2008} focus specifically on detecting contradictions.
+Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.
 
 While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
-Naturally, as processor speeds improve, it will become practical to use increasingly sophisticated algorithms.
+We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.
 
@@
 
-\subsection{Finding Disputed Information on the Web}
-
-An important part of Dispute Finder is identifying what claims are disputed. Several other authors looked at disputed information on the web.
-
-Kittur et al~\cite{Kittur2007} developed an algorithm that can determine whether a wikipedia page is about a disputed topic.
+%
+%\subsection{Finding Disputed Information on the Web}
+%
+%An important part of Dispute Finder is identifying what claims are disputed. Several other authors looked at disputed information on the web.
+%
+%Kittur et al~\cite{Kittur2007} developed an algorithm that can determine whether a wikipedia page is about a disputed topic.
 Kittur and Chi~\cite{Kittur2009} broke down the disputed pages by catagory and found that People, Society, and Religion were the categories with the most disputed pages.
-
-\subsection{Extracting Information from the Web}
-
-Information extration tools such as TextRunner~\cite{Etzioni2008} 
-Read The Web
-
-TextRunner~\cite{Etzioni2008}
-
-\todo{cite lots of Etzioni stuff}
-
-\cite{SnowBall}
-\cite{Read The Web}
-\cite{Information Extraction from Wikipedia}
-\cite{KnowItAll}
-\cite{TextRunner}
-
-\todo{Online Dispute Resolution}
-
-\todo{Cite Kittur et al}
+%
+%\subsection{Extracting Information from the Web}
+%
+%Information extration tools such as TextRunner~\cite{Etzioni2008} 
+%Read The Web
+%
+%TextRunner~\cite{Etzioni2008} 
+%
+%\todo{cite lots of Etzioni stuff}
+%
+%\cite{SnowBall}
+%\cite{Read The Web}
+%\cite{Information Extraction from Wikipedia}
+%\cite{KnowItAll}
+%\cite{TextRunner}
+%
+%\todo{Online Dispute Resolution}
+%
+%\todo{Cite Kittur et al}
 
@@
 
-\subsection{Persuasive Technology}
+%\subsection{Persuasive Technology}
 
@@
 Users interact with Dispute Finder in two ways.
-Skeptical readers browse the web using the Dispute Finder Firefox extension and discover when pages they read make disputed claims.
-Activists tell Dispute Finder about disputed claims that they care about, and add evidence to support their point of view.
+{\it Skeptical Readers} browse the web using the Dispute Finder Firefox extension and discover when pages they read make disputed claims.
+{\it Activists} tell Dispute Finder about disputed claims that they care about, add evidence to support their point of view, and help teach Dispute Finder to recognize particular claims on the web.
 
@@
 
-Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust.
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{pictures/highlight_bar.png}
+	\caption{Highlight and Notification Bar}
+	\label{highlight_bar}
+	\end{center}
+\end{figure}
+
+%Dispute Finder is designed to alert a user when information they read on a web page makes a claim that is disputed by a source they might trust. 
+%
+%
+%Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust.
 We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.
 
-Dispute Finder uses two mechanisms to inform a user when information on the page they are reading is disputed.
-It highlights any snippets that make the disputed claims in red, and it displays a message bar.
+The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed.
+It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).
 
-The message bar alerts the user that they should look out for highlighted snippets on the current page. 
-Highlighted snippets can be difficult to see if the page is using a background color that is similar to our highlight color\footnote{We tried to choose a color that is rarely used as a background} or if the user is color blind.
-The message also provides a ``go to next snippet'' button that allows the user to step though the highlighted snippets one at a time.
+The notification bar alerts the user that they should look out for highlighted snippets.
+Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors} or if the user is color blind.
+The notification bar also allows a user to step through the highlighted snippets on the page.
 
-The highlights show a user {\it why} Dispute Finder thinks that a page is making a disputed claim.
-In some cases Dispute Finder may have mistakenly thought an article was saying something it wasn't, or the disputed claim may be in text the user isn't interested in, such as a comment.
-If Dispute Finder has incorrectly marked a snippet as making a disputed claim then the user is encouraged to tell Dispute Finder this by clicking on the snippet and then cliking on the ``report incorrect highlighing'' button in the popup interface.
+The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims.
+This allows a user to ignore disputed claims that are made by text that the user isn't interested in - such as user comments.
+The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making.
+In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the "report incorrect highlighting" button from the popup interface.
 
-A user can discover what disputed claim Dispute Finder thinks a snippet is making by hovering their mouse over it, and can bring up more information about a claim by clicking on the snippet (Figure\ref{claimview}).
+Once a user is aware that a claim is disputed, there is little point telling them about the same disputed claim again in the future.
+We have not yet concluded whether it is better for Dispute Finder to automatically stop highlighting a claim once a user has viewed the claim, or whether it is better for a user to explicitly ask Dispute Finder to stop highlighting a claim.
+In our current implementation, a user can tell Dispute Finder to not highlight a claim again by setting the ``don't highlight this claim for me again'' checkbox in the popup interface (Figure~\ref{claimview}).
+Requiring a user to manually opt out of a claim requires more work from the user, but hiding already viewed claims can be confusing, since users do not normally expect viewing something to be a destructive operation.
+A compromise position is to highlight claims that have been seen before in a fainter color; similar to the way links are typically colored on web pages.
 
-There is little point repeatedly telling a user that the same claim is disputed.
-In our current version, a user can ask Dispute Finder to not highlight a claim again by clicking on the ``ignore this claim]'' button in the popup interface.
-An alternative is to automatically stop highlighting a disputed claim, once the user has brought up the popup interface for it once.
-We have not yet conclusively decided which method works better.
-Requiring a user to manually opt out of a claim requires more work from the user, but also causes less user-confusion as users do not normally expect viewing something to be a destructive operation.
+\todo{Try using a fainter color}
 
-A web site can also opt to use the Dispute Finder API to detect disputed claims on the content that they present to users.
-This API could be particularly useful to tools like search engines and RSS feed readers that a user may use to access a large proportion of the information they consume.
-The firefox extension itself uses the same API.
-The advantage of using the Firefox extension is that it can look for disputed claims on any web site.
-The disadvantage is that it can only be used by users who use a compatible browser and are prepared to install an extension (well known to be a significant barrier to adoption\cite{extension-bad?}
+\todo{Text is wrong in the screenshot}
+
+Dispute Finder also provides an API that can be used by other sites to determine whether their content makes disputed claims.
+For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.
 
@@
 
-Once a user has been informed that the page they are reading is making a disputed claim, they will typically be interested in learning more about that claim, so they can judge whether there are alternative points of view that they should take seriously.
+If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view.
+We could have ommitted this feature and still had a useful system.
+Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim.
+There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:
 
-The simplest option would be to merely inform the user that the page is making a disputed claim, but provide no further information about that claim.The user could then use a tool such as a search engine to investigate the claim further.
+\begin{description}
+\item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
+\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view - otherwise Dispute Finder would be annoying.
+By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
+\item[Filtering:] Although we have not implement this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
+\end{description}
 
-There are several reasons why it is useful to associate a claim with information justifying alternative points of view:
-
-\begin{itemize}
-\item To allow a user to quickly determine whether alternative points of view are sufficiently credible that they should take them seriously
-\item To allow users who are moderating the database to determine when no arguments exist for other points of view, and thus the claim should not be in the database
-\item To allow Dispute Finder's algorithms to determine whether the claim is disputed by someone that that particular user would take seriously.
-Although we have not yet implemented such features, we believe they will be important.
-\end{itemize}
+Naturally, sources such as Wikipedia, Politifact, and Snopes are often used as sources of evidence for and against a claim --- indeed we currently import articles from Politifact and Snopes automatically.
 
@@
 \begin{description}
-\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them an IBIS-style\cite{gibis} argumentation graph that explains the structure of the argument against the claim.
+\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph~\cite{Conklin1987a}.
 Each claim is linked to claims that represent alternative points of view, and claims that support that point of view.
-Each claim also has a list of sources that argue in favor of that claim (Figure\ref{arg-graph?})
+Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})
 
-\item[Source lists:] Dispute Finder shows the user two lists of sources, one of which contains sources arguing in favor of the claim, and the other of which contains sources arguing against the claim (Figure~\ref{article-list})
+\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{claimview}).
+For each article, the interface shows a summary sentence that captures the core argument used by the article.
+A user can add any web page as a supporting article by browsing to the page, selecting "use as evidence" from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
 \end{description}
 
-The argumentation graph is potentially much more powerful.
-When a user is presented with a simple list of sources, several of them may be making the same core points and it may not be obvious that one of the sources is making a point that the user had not come across before.
-The argumentation graph also allows the user to browse around the network of different claims being made about an area, which can be interesting in itself.
+The argumentation graph makes it easier to see {\it why} a claim is disputed, while the article lists make it easier to see {\it who} supports or opposes the claim.
 
-On important disadvantage of using an argumentation graph is that someone has to build it.
-In our prototype, the argumentation graph was built entirely by users.
-We found that our users had difficulty creating well structured argumentation graphs that were useful for other users, a result that is consistent with previous studies~\cite{ibis-bad?}.
-It is possible that an alternative (simpler?) graph structure or interface that made it easier to build such graphs might make them work better.
-Argumentation graphs might also work better if they could be built automatically by mining the web.
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/mark_evidence.png}
+	\caption{Adding an article, with a summary sentence selected}
+	\label{add_article}
+	\end{center}
+\end{figure}
 
-Another point in favor of using a simple list of sources is that we found that users are far more concerned with ``who'' disputes a claim, than what their argument is.
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
+	\caption{Choose how to connect an article with a claim}
+	\label{article_choose}
+	\end{center}
+\end{figure}
+
+\todo{Call them supporting pages? Naming is a mess right now.}
+
+When using the article list approach, several different articles may be expressing essentially the same point of view and it may not be obvious that one of the articles is making a point that the user had not come across before.
+The argumentation graph allows the user to easily see what the range of different opinions is, and quickly see if there is an argument that they have not encountered before.
+
+A significant weakness of the argumentation graph approach is that a good argumentation graph takes significantly more effort to build than a simple list of articles.
+In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users.
+There were two problems here: firstly, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; secondly, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}.
+This result is consistent with previous studies~\cite{Isenmann1997}.
+
+Another point in favor of using a simple list of sources is that most of the users we talked to seemed to be more interested in {\it who} disputed a claim, rather than what their argument was.
 For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with.
-The argumentation graph focusses on presenting the user with the structure of the argument against the claim, but our studies suggest that the user is likely to find this much less interesting than the authority behind the arguments against the claim.
+Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they prefered to read whichever article seemed to be most credible, rather than browsing an argumentation graph.
 
-In the present version of Dispute Finder, a source can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable.
-Good sources include newspapers, universities, respected organizations, and Wikipedia itself.
-Users can vote on whether they think a particular source is useful, and this voting determines the order in which sources are listed.
-A user can also request that a source be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable sources.
-Users with moderator privileges review requests for deletion and delete claims and sources that do not meet requirements.
+It is possible that the best solution would be a visualisation that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and {\it why} the various sources held those opinions.
+
+\subsection{Trustworthy Sources}
+
+In the current version of Dispute Finder, an article can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable.
+Good sources of articles include newspapers, universities, respected organizations, and Wikipedia itself.
+Users can vote on whether they think a particular article is useful, and this voting determines the order in which articles are listed.
+A user can also request that an article be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable articles.
+Users with moderator privileges review requests for deletion and delete claims and articles that do not meet requirements.
 
@@
 There are significant weaknesses in this approach.
-In our studies, we found that users disagree about what they would consider a reliable source.
-Users consider a source to be reliable if it espouses opinions that they themselves agree with, and is accepted as being a reliable source within their social group.
+Pew have shown~\cite{pew-news} that different people trust different sources.
 There may be little point showing liberal sources to a conservative, or vice-versa.
-Similarly, a global voting system can be gamed by people who want to hide good arguments against a claim that they support by voting up bad ones.
-Another problem is that, by resorting to moderators to decide which sources and claims are high enough quality to be included, we open ourselves up to charges of bias.
+Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments.
+Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.
 
-In the future it may be better to learn what sources a particular user is likely to believe are reliable, and then adjust both what sources Dispute Finder shows to the user, and what claims are highlighted, based on this.
+It may thus be better to learn what sources a particular user is likely to believe are reliable, and then adjust both what sources Dispute Finder shows to the user, and what claims are highlighted, based on this.
 
 There is a difficult trade-off here.
-If we only show users sources that we believe they are likely to trust, then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
-On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment, and stifling the voices of those who are less widely respected by the establishment, but may be right.
+If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own worldview then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
+On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right.
 If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously.
-We do not yet claim to know a good solution for this problem.
+We do not yet claim to know a good solution for this problem, but we believe it is an interesting area for further research.
 
@@
 
-\section{Studying the Users}
+\section{Learning from Users}
 
@@
 Several users got confused by claims that referred to similar events at different points in time.
-For example, one participant in the first study marked two claims as opposing each other when each was true at the time that it was written.
-This is a particular problem when talking about breaking news events, where the facts can change fast.
-If Dispute Finder is to be effective for describing such events then it will need to have better support associating times with claims and snippets.
+For example, one participant in the first study marked one claim as opposing another claim when they were referring to similar incidents that occurred at different times.
+
+When using the article-list interface, several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative.
+For example a user would mark an article that opposed global warming as opposing the claim "global warming is bad" because the article opposed global warming.
 
@@
 This is for two reasons: our database of disputed claims is currently too small (around two thousand claims at the time of writing), and our textual entailment algorithm is not sufficiently sophisticated to stand a good chance of highlighting snippets when they make those claims.
-
-The biggest problem that Dispute Finder has right now is that its coverage is not very high.
-Both our database of disputed claims, and the number of snippets that we highlight that make each disputed claim
-
-In its current state, it is unlikely that a user will see a snippet highlighted that makes a claim that they did
 

### 2009-10-26 papers/www_disputefinder/disputefinder.tex
More improvements to the system section

@@
 
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{pictures/snippet_claim_article_fancy2.png}
+	\caption{Snippets entail claims, which are entailed or contradicted by articles}
+	\label{snippet_claim_article}
+	\end{center}
+\end{figure}
+
 Dispute Finder consists of a database, an API, and a Firefox browser extension.
-The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to recognise them when they appear on a web page.
+The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_clim_article}).
 The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims.
@@
 \subsection{Recognizing Textual Entailment}
+\label{related:entailment}
 
@@
 One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it condradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical.
-Dispute Finder thus instead uses separate approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims.
+Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims.
 Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.
@@
 
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
+	\caption{Article List interface for a disputed claim}
+	\label{article_list}
+	\end{center}
+\end{figure}
+
 \begin{description}
@@
 
-\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{claimview}).
+\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}).
 For each article, the interface shows a summary sentence that captures the core argument used by the article.
@@
 
-One of the key challenges for Dispute Finder is determining what claims are Disputed.
-Dispute Finder takes the approach of maintaining a database of known disputed claims, which it then looks for on web pages.
+One of the biggest challenges in Dispute Finder, is how to build a list of disputed claims that should be highlighted for users.
+As discussed in Section~\ref{related:entailment}, rather than directly inferring whether a snippet is disputed by a trusted article on the web, Dispute Finder instead builds a database of known disputed claims and tries to determine whether a snippet on a web page entails the truth of one of these claims.
 
-What we are after is not a list of everything that has every been disputed by anyone, but a list of claims that are frequently believed and are opposed by reliable sources.
+\todo{We are repeating information between here and the related work section on Recognizing Textual Entailment}
+
+We do not want the database of disputed claims to contain everything that has every been disputed by anyone.
 In some sense almost everything is disputed by someone on the web.
@@
 For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true.
+What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/add_claim.png}
-	\caption{Interface for adding a new disputed claim}
+	\includegraphics[width=8cm]{pictures/add_claim_list.png}
+	\caption{Interface for adding a new disputed claim manually}
 	\label{add_claim}
@@
 Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them.
-For example Snopes.com maintains a list of urban legends and politifact.com maintains a list of false claims about politics.
-We automatically import all claims that these sites debunk into our database and treat the sites themselves as reliable sources about the claims they debunk.
-In the future we intend to also import claims from other such sites.
+For example Snopes.com maintains a list of urban legends and Politifact.com maintains a list of false claims about politics.
+We automatically import all claims that either of these sites debunk into our database and treat the sites themselves as reliable sources about the claims they debunk.
+In the future we intend to also import claims from other such sites, and allow users to choose which feeds of disputed claims should be used to highlight snippets on pages they browse.
 
-We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{web-add?}).
-The web interface is modeled after common issue-reporting software such as UserVoice\footnote{url?}.
+We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{add_claim}).
+The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org.
 It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim.
-When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing source.
+When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.
+
+The automatic import feeds allow Dispute Finder to bootstrap a large database of disputed claims without needing a large active user community and the crowdsourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.
+
+\todo{Say how many disputed claims}
+
+\todo{talk about duplicates}
 

### 2009-10-26 papers/www_disputefinder/disputefinder.tex
Finished my pass over the system section

@@
 
-\title{Highlighting Disputed Information on the Web}
+\title{Highlighting Disputed Claims on the Web}
 
@@
 
-A user can install Disute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser.
+A user can install Dispute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser.
 When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}).
@@
 \begin{description}
-\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users aren't distracted by things that they would not consider to be disputed).
+\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users are not distracted by things that they would not consider to be disputed).
 We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims.
@@
 
-Given a web page that the user is browsing, and a database of claims that we believe are disputed, how can we determine what snippets on the page are making claims that are in our database?
-We implemented and tested four approaches:
+Given a web page, Dispute Finder needs to indentify which snippets are making known disputed claims. We implemented and tested four different approaches:
 
@@
 	\begin{center}
-	\includegraphics[width=7cm]{pictures/training.png}
-	\caption{Bulk page marking}
+	\includegraphics[width=7cm]{pictures/training2.png}
+	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons}
 	\label{training}
@@
 
+\begin{figure}[t]
+	\begin{center}
+	\includegraphics[width=7cm]{pictures/nlp_client_server2.png}
+	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server}
+	\label{nlp_client_server}
+	\end{center}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=7cm]{pictures/paraphrases.png}
+	\caption{Users can enter paraphrases of a claim to help the entailment algorithm}
+	\label{paraphrases}
+	\end{center}
+\end{figure}
+
 \begin{description}
-\item[Explicit page marking:] If the page a user is reading contains a snippet that makes a disputed claim, the user can mark that snippet by selecting it, right clicking, and selecting "mark as disputed" from a popup menu.
+\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting "mark as disputed" from a context menu (Figure~\ref{mark_disputed}).
 
-\item[Bulk page marking:] The user enters a paraphrase of the claim into a web UI.
-The server searches the web for snippets that resemble this phrase using Yahoo BOSS~\cite{boss?} and shows the user the snippets it found.
-The user clicks on all of the snippets that they would like to mark.
+\item[Bulk page marking:] The user uses a search interface to rapidly gather a large number of snippets that contain similar phrases, and then marks them in bulk.
+The server uses Yahoo BOSS\footnote{http://developer.yahoo.com/search/boss} to search the web for snippets that resemble a paraphrase entered by the user.
+The user then selects all the snippets that they would like to mark (Figure~\ref{training}).
 
 \item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier.
-We used a simple baysian classifier with n-grams as its features.
-As the user gives examples of snippets that do or do not entail the original claim, the classifier learns what n-grams should or should not be in a snippet.
-Once the classifier is sufficiently trained, the server applies it to the rest of the results from Yahoo BOSS to automatically mark web pages.
-We have only partially implemented this approach.
+We used a simple baysian classifier with n-grams as features.
+This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.
+Once the classifier has been trained, the server uses it to automatically choose which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).
+
+%We have only partially implemented this approach.
+\todo{Should we say that we didn't completely finish this version?}
 
@@
 
-\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database.
+\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}).
 A user can enter additional paraphrases of a claim to help the entailment algorithm.
-This is the implementation used by the currently released version of Dispute Finder.
+This is the implementation used by the currently released version of Dispute Finder (Figure~\ref{paraphrases}).
 \end{description}
@@
 However the manual effort required per page makes it difficult for this approach to scale.
-It can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page.
-This is the same problem that has hindered the adoption of web page annotation tools.
+We also foundf that it can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page.
+This same problem that has hindered the adoption of numerous web page annotation tools.
 
@@
 
-Server side classification trades off more accuracy for more coverage. The classifier can mark more pages than a user could ever mark manually, but is inevitably less accurate than a human.
+Server side classification trades off more accuracy for more coverage.
+The classifier can mark more pages than a user could ever mark manually, and can keep marking new pages as they appear, but it is inevitably less accurate than a human.
 
@@
 
-The client side entailment method uses the standard Local Lexical Matching algorithm that is a common baseline in NLP.
+A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing.
+The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be pratical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy.
+By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.
+
+The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP.
 It divides the page into sentences, strips out stopwords, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
@@
 not, never, can't) then so must the matching sentence.
+To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scaccing the page for "hot terms" such as "Global Warming" that are known to appear in disputed claims.
+The hot terms are selected such that every claim contains at least one hot term.
+If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.
+
+\todo{Mention that we could add the +ve and -ve n-grams to the client code? Actually do this?}
 
@@
 \todo{Explain how we avoid downloading the entire database}
-
-The client side entailment method uses a simpler algorithm than the server-side classifier.
 
@@
 Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users.
-We do however believe that Dispute Finder attacks an interseting problem that, if solved well, could significantly improve the utility of the web.
+We do however believe that Dispute Finder attacks an interesting problem that, if solved well, could significantly improve the utility of the web.
+
+At the time of writing 11,682 people have installed and tried out Dispute Finder, 2,297 are active daily users, 140 have added new claims to our database, 149 have added articles, and our database contains 2,146 disputed claims.
+
+\todo{Add count of disputed claims}
 

### 2009-10-27 papers/www_disputefinder/disputefinder.tex
More paper tweaks

@@
 
-%\author{
-%\alignauthor Rob Ennals\\
-%       \affaddr{Intel Labs Berkeley}\\
-%       \affaddr{2150 Shattuck Ave}\\
-%       \affaddr{Berkeley, CA, USA}\\
-%       \email{robert.ennals@intel.com}
-%\alignauthor Beth Trushkowsky\\
-%       \affaddr{Computer Science Division}\\
-%       \affaddr{University of California at Berkeley}\\
-%       \affaddr{Berkeley, CA, USA}\\
-%       \email{trush@berkeley.edu}
-%\alignauthor John Mark Agosta\\
-%       \affaddr{Intel Labs Santa Clara}\\
-%       \affaddr{2200 Mission College Blvd}\\
-%       \affaddr{Santa Clara, CA, USA}\\
-%       \email{john.m.agosta@intel.com}
-%}
-%
-%\additionalauthors{Additional authors: Tad Hirsch (Intel Research PaPR, email: {\texttt{tad.hirsch@intel.com}}) and Tye Rattenbury (Intel Research PaPR), email: {\texttt{tye.rattenbury@intel.com}})}
+\author{
+\alignauthor Rob Ennals\\
+       \affaddr{Intel Labs Berkeley}\\
+       \affaddr{2150 Shattuck Ave}\\
+       \affaddr{Berkeley, CA, USA}\\
+       \email{robert.ennals@intel.com}
+\alignauthor Beth Trushkowsky\\
+       \affaddr{Computer Science Division}\\
+       \affaddr{University of California at Berkeley}\\
+       \affaddr{Berkeley, CA, USA}\\
+       \email{trush@berkeley.edu}
+\alignauthor John Mark Agosta\\
+       \affaddr{Intel Labs Santa Clara}\\
+       \affaddr{2200 Mission College Blvd}\\
+       \affaddr{Santa Clara, CA, USA}\\
+       \email{john.m.agosta@intel.com}
+}
+
+%\sloppy
+
+\additionalauthors{Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}
 
@@
 
-\subsection{Interviews}
+We circulated a survey amongst members of a local debate club - a set of people who we believe is a good match for our Skeptical Reader and Activist personas.
+They survey asked respondants to tell us how often they typically engaged in various behaviours on the web.
+Although the survey was too small to be statistically useful, the results gave some useful information that we believe is worth reporting.
+
+Most people 65\% said that some of the information they read is not trustworthy, but they know which sites they can trust.
+Nobody said that they trusted the most of the information they read.
+17\% trust very little of the information they read, and 9\% feel confused about what they can trust.
+
+Everyone had used another source to double-check information they had read online.
+74\% "often" search the web to find web pages that confirm a claim they have read.
+64\% "often" check a website they trust.
+55\% "sometimes" ask a friend and 55\% "sometimes" check a book.
+
+When deciding whether to trust a web site, the most important factor was whether the site was run by an organization they trusted (61\% often, 30\% sometimes), followed by whether the site was linked from another site they trusted (18\%,50\%), and whether the site was well written (18\%,50\%).
+
+% \subsection{Interviews}
+
+\todo{Do we have enough interview content to integrate it? Probably not yet...}
+\todo{Is the survey interesting enough to quote here? Only 23 people, and not exciting. Just quote inline with findings.}
 
@@
 All study groups were small.
-The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had ??
-participants (??
-male, ??
-male).
+The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had six participants participants (all male).
 

### 2009-10-27 papers/www_disputefinder/disputefinder.tex
Playing with the user study section

@@
 \item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}).
-A user can enter additional paraphrases of a claim to help the entailment algorithm.
-This is the implementation used by the currently released version of Dispute Finder (Figure~\ref{paraphrases}).
+A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}).
+This is the implementation used by the currently released version of Dispute Finder.
 \end{description}
@@
 
-The Design of Dispute Finder has been influenced by several different kinds of input from potential users.
+%The Design of Dispute Finder has been influenced by several different kinds of input from potential users.
 We performed a series of "think aloud" user studies to evaluate the user interface, we circulated a survey among members of a local debate club, and we performed a series of interviews with people selected from those who completed the survey.
-
-\subsection{Survey}
-
-We circulated a survey amongst members of a local debate club - a set of people who we believe is a good match for our Skeptical Reader and Activist personas.
+%
+%\subsection{Survey}
+%
+%We circulated a survey amongst members of a local debate club - a set of people who we believe is a good match for our Skeptical Reader and Activist personas.
 They survey asked respondants to tell us how often they typically engaged in various behaviours on the web.
 Although the survey was too small to be statistically useful, the results gave some useful information that we believe is worth reporting.
-
-Most people 65\% said that some of the information they read is not trustworthy, but they know which sites they can trust.
+%
+%Most people 65\% said that some of the information they read is not trustworthy, but they know which sites they can trust.
 Nobody said that they trusted the most of the information they read.
 17\% trust very little of the information they read, and 9\% feel confused about what they can trust.
-
-Everyone had used another source to double-check information they had read online.
+%
+%Everyone had used another source to double-check information they had read online.
 74\% "often" search the web to find web pages that confirm a claim they have read.
@@
 55\% "sometimes" ask a friend and 55\% "sometimes" check a book.
-
-When deciding whether to trust a web site, the most important factor was whether the site was run by an organization they trusted (61\% often, 30\% sometimes), followed by whether the site was linked from another site they trusted (18\%,50\%), and whether the site was well written (18\%,50\%).
-
-% \subsection{Interviews}
-
-\todo{Do we have enough interview content to integrate it? Probably not yet...}
-\todo{Is the survey interesting enough to quote here? Only 23 people, and not exciting. Just quote inline with findings.}
-
-\subsection{Think-Aloud User Studies}
+%
+%When deciding whether to trust a web site, the most important factor was whether the site was run by an organization they trusted (61\% often, 30\% sometimes), followed by whether the site was linked from another site they trusted (18\%,50\%), and whether the site was well written (18\%,50\%).
+%
+%% \subsection{Interviews}
+%
+%\todo{Do we have enough interview content to integrate it? Probably not yet...}
+%\todo{Is the survey interesting enough to quote here? Only 23 people, and not exciting. Just quote inline with findings.}
 
@@
 
-\subsubsection{Procedure}
+\subsection{Procedure}
 
@@
 
+We also conducted interviews with most of our user study participants, and six additional people, asking them how they use the web to form and promote their opinions.
+
 \todo{Need to finish the third wave of user studies}
@@
 Most users were able to use Dispute Finder compentently as a skeptical reader (browsing information about disputed claims) but found it harder to act compentently as an activist (adding new disputed claims).
+Several participants wanted to see Dispute Finder work for them as a skeptical reader before dedicating time to adding and curating new claims ("I want to see it work before I add stuff").
 
@@
 Not all users realised that one could click on a disputed claim to bring up more information.
+Several users complained about Dispute Finder highlighing snippets that weren't making the claim Dispute Finder indicated.
 
@@
 
-When asked to mark snippets on a particular page that make disputed claims, users often did not appreciate that they should either re-use existing claims or create claims that would be applicable to snippets on many other pages.
+When marking a snippet on a particular page, users often did not appreciate that a claim should apply to more than one snippet.
 Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to "enter the text again".
-Similarly, users got confused when a snippet made two different disputed claims.
+Similarly, several users got confused when a snippet made two different disputed claims.
 The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as "Global warming will cause X and Y".
 
-Conversely, when adding a claim to the Dispute Finder web site, users would often enter claims that are not disputed anywhere on the web, or enter paraphrases that do not resemble the wording used on any web site.
+Conversely, when adding a claim to the Dispute Finder web site, users would often enter claims that are not disputed anywhere on the web or enter paraphrases that do not resemble the wording used on any web site.
 The challenge of how to help users come up with claims that occur on many web sites is one that we have not yet solved.
@@
 For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information?
-In order to make a good judgement, one needs to know the range of similar claims that are being made by other web sites, and what claims one has good evidence against.
+In order to make a good judgement, one needs to know the range of similar claims that are being made by other web sites, and what claims there is good evidence against.
 If one makes the claim too specific then one will be able to find less web pages that make it, but if one makes the claim too general then it might be harder to find solid evidence against it.
@@
 This graph connected the graphs in our database using "supports" or "opposes" links, and allowed each claim to also be associated with supporting articles.
-
 When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected.
@@
 Users seemed to have difficulty creating such graph structures however.
-Some users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim.
+Several users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim.
 For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems".
@@
 For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''.
-It is possible that creating logically correct claim structures may be too difficult for some people (see Isenmann and Reuter~\cite{Isenmann1997}).
+These findings are consistent with those of Isenmann and Reuter~\cite{Isenmann1997}.
 
@@
 One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
+Users did however recognize that they would want to see opposing evidence as a reader.
 
@@
 
-The biggest problem that Dispute Finder has right now is that it is rare that Dispute Finder will highlight a snippet that makes a claim that the user did not already know was disputed.
-This is for two reasons: our database of disputed claims is currently too small (around two thousand claims at the time of writing), and our textual entailment algorithm is not sufficiently sophisticated to stand a good chance of highlighting snippets when they make those claims.
+Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them or that they were expected to be knowledgeable about, but were less interested about applying it to pages about other topics, that they were less interested in.
+For topics that didn't affect them users felt that misinformation was "not important enough to bother with", or that they could "afford to be misinformed".
 
-\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"oppsose" graph.}.
+Most users were frustrated by the relatively poor accuracy and recall that Dispute Finder has at present.
+Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder didn't highlight anything.
+Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated.
+If Dispute Finder is to be adopted widely then we will need to significantly improve precission and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.
+
+\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"oppsose" graph.}
 
@@
 
-An experimental preview version of Dispute Finder is available at the following URL:
+An experimental preview version of Dispute Finder is available at 
 \url{http://disputefinder.org}
@@
 
-\section{Acknowledgments}
+%\section{Acknowledgments}
 

### 2009-10-27 papers/www_disputefinder/disputefinder.tex
Spell check

@@
 
-In the realm of News, Pew~\cite{pew-news} report that, while internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible.
+In the realm of News, Pew~\cite{pew-news} report that, while Internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible.
 Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.
@@
 Dispute Finder consists of a database, an API, and a Firefox browser extension.
-The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_clim_article}).
+The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}).
 The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims.
@@
 \item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users are not distracted by things that they would not consider to be disputed).
-We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims.
+We currently use a combination of crowd-sourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims.
 More generally, the challenge is not to determine if a claim is disputed by {\it anyone} but to determine whether there is an alternative point of view that this particular user would take seriously.
@@
 For example a user may be skeptical when reading about topics that affect them (e.g.
-health, things important to their job, or things they are expected to be knowledgable about), but disengaged when reading about topics that don't affect them (e.g.
+health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that don't affect them (e.g.
 entertainment) or topics for
@@
 We performed three rounds of users studies, circulated a survey within a target group, and conducted a series of interviews.
-We discuss the conclusions of these studies throught the paper, and in a section at the end.
+We discuss the conclusions of these studies throughout the paper, and in a section at the end.
 These studies were intended to inform the design of Dispute Finder, rather than to validate it.
@@
 
-Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realise that they should check it on one of these services.
+Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services.
 Dispute Finder is designed to work together with fact checking sites.
@@
 
-\subsection{Analysing News}
+\subsection{Analyzing News}
 
@@
 News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
-The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader persective of the issue.
-Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overal slant of the article.
+The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue.
+Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overall slant of the article.
 A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.
@@
 Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}.
-Tagging tools allow users to collectively catagorize information by associating it with a user-created set of tags.
+Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags.
 In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
@@
 
-One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it condradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical.
+One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it contradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical.
 Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims.
@@
 Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims.
-The algorithm we use is a simple varient of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}.
-LLM simply reduces a sentence to a bag of lemmatized words, removes stopwords, checks for negations, and then looks at what the overlap is between the words in the two phrases.
+The algorithm we use is a simple variant of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}.
+LLM simply reduces a sentence to a bag of lemmatized words, removes stop-words, checks for negations, and then looks at what the overlap is between the words in the two phrases.
 Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.
@@
 When Dispute Finder highlights many snippets that make a single disputed claim, this is a special case of the more general task of finding repeated information on the web.
-Kolak and Schillit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
-MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news soures and blogs.
+Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
+MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news sources and blogs.
 
@@
 
-Several authors have analysed trust on Wikipedia.
+Several authors have analyzed trust on Wikipedia.
 WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author.
@@
 If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view.
-We could have ommitted this feature and still had a useful system.
+We could have omitted this feature and still had a useful system.
 Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim.
@@
 For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with.
-Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they prefered to read whichever article seemed to be most credible, rather than browsing an argumentation graph.
+Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they preferred to read whichever article seemed to be most credible, rather than browsing an argumentation graph.
 
-It is possible that the best solution would be a visualisation that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and {\it why} the various sources held those opinions.
+It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and {\it why} the various sources held those opinions.
 
@@
 There is a difficult trade-off here.
-If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own worldview then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
+If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own world-view then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
 On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right.
@@
 
-The automatic import feeds allow Dispute Finder to bootstrap a large database of disputed claims without needing a large active user community and the crowdsourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.
+The automatic import feeds allow Dispute Finder to bootstrap a large database of disputed claims without needing a large active user community and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.
 
@@
 
-Given a web page, Dispute Finder needs to indentify which snippets are making known disputed claims. We implemented and tested four different approaches:
+Given a web page, Dispute Finder needs to identify which snippets are making known disputed claims. We implemented and tested four different approaches:
 
@@
 Explicit page marking has the highest accuracy, but the poorest coverage.
-Since a user is looking at the page in its entirity, they can read the snippet in context and make a good judgement about whether the snippet is indeed making the claim.
+Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim.
 However the manual effort required per page makes it difficult for this approach to scale.
-We also foundf that it can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page.
+We also found that it can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page.
 This same problem that has hindered the adoption of numerous web page annotation tools.
@@
 A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing.
-The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be pratical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy.
+The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be practical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy.
 By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.
@@
 The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP.
-It divides the page into sentences, strips out stopwords, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
+It divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
 If the claim contains a negation word (e.g.
 not, never, can't) then so must the matching sentence.
-To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scaccing the page for "hot terms" such as "Global Warming" that are known to appear in disputed claims.
+To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for "hot terms" such as "Global Warming" that are known to appear in disputed claims.
 The hot terms are selected such that every claim contains at least one hot term.
@@
 For the first two studies, we recruited participants using Craigslist.
-We posted a message asking people to tell us how they used the web to form and promote their opinions, and used this to select people who we thought might fit our "skeptical reader" and "activist" personas.
-After these studies, we decided that the kind of person who looks for jobs of craigslist is unlikely to be a good fit for our personas, and so for the final study we instead used people we knew personally and thought fit our personas well.
+We posted a message asking people to tell us how they used the web to form and promote their opinions, and used their responses to select people who we thought might fit our "skeptical reader" and "activist" personas.
+After these studies, we decided that the kind of person who looks for jobs of Craigslist is typically not a good fit for our personas, and so for the final study we instead used people we knew personally and thought fit our personas well.
 All study groups were small.
@@
 Each batch of users was shown a different iteration of the Dispute Finder design.
-The first two batches used versions in which users marked snippets explicitly, and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view.
+The first two batches used versions in which users marked snippets explicitly and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view.
 The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim.
@@
 
-Study sessions took approximately fourty five minutes.
-Participants were seated at a workstatation with the Firefox browser augemented with the Dispute Finder extension.
+Study sessions took approximately forty five minutes.
+Participants were seated at a workstation with the Firefox browser augmented with the Dispute Finder extension.
 They were asked to view pages that had highlighted claims on them, and to attempt to add new disputed claims to our database.
@@
 
-\subsubsection{Findings}
+\subsection{Findings}
 
@@
 
-Most users were able to use Dispute Finder compentently as a skeptical reader (browsing information about disputed claims) but found it harder to act compentently as an activist (adding new disputed claims).
+Most users were able to use Dispute Finder competently as a skeptical reader (browsing information about disputed claims) but found it harder to act competently as an activist (adding new disputed claims).
 Several participants wanted to see Dispute Finder work for them as a skeptical reader before dedicating time to adding and curating new claims ("I want to see it work before I add stuff").
@@
 When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed.
-Not all users realised that one could click on a disputed claim to bring up more information.
-Several users complained about Dispute Finder highlighing snippets that weren't making the claim Dispute Finder indicated.
+Not all users realized that one could click on a disputed claim to bring up more information.
+Several users complained about Dispute Finder highlighting snippets that weren't making the claim Dispute Finder indicated.
 
@@
 For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information?
-In order to make a good judgement, one needs to know the range of similar claims that are being made by other web sites, and what claims there is good evidence against.
+In order to make a good judgment, one needs to know the range of similar claims that are being made by other web sites, and what claims there is good evidence against.
 If one makes the claim too specific then one will be able to find less web pages that make it, but if one makes the claim too general then it might be harder to find solid evidence against it.
@@
 When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected.
-One user said "I can see myself getting addicted to this", and another said "it's very intuitivet".
+One user said "I can see myself getting addicted to this", and another said "it's very intuitive".
 
@@
 For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems".
-Users correctly realised that the claims were related, but were not sure how best to connect them.
+Users correctly realized that the claims were related, but were not sure how best to connect them.
 Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship.
@@
 One user entered a disputed claim about "Wood", meaning the guitarist "Ronnie Wood" of the Rolling Stones.
-Similar problems occured with claims that were specific to a particular country, or a particular point in time.
+Similar problems occurred with claims that were specific to a particular country, or a particular point in time.
 
@@
 Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated.
-If Dispute Finder is to be adopted widely then we will need to significantly improve precission and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.
+If Dispute Finder is to be adopted widely then we will need to significantly improve precision and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.
 
-\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"oppsose" graph.}
+\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"opposes" graph.}
 

### 2009-10-28 papers/www_disputefinder/disputefinder.tex
Addressed comments from Tye and fixed bad quotes

@@
 
-Dispute Finder builds it's database of disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed.
+Dispute Finder builds its database of disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed.
 Dispute Finder identifies instances of disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of a subset of our claim database.
@@
 	\includegraphics[width=8cm]{pictures/highlight_abortion.png}
-	\caption{A highlighted snippet that makes a disputed claim}
+	\caption{Dispute Finder highlights text snippets that make disputed claims.}
 	\label{highlight}
@@
 	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
-	\caption{Popup interface with articles for and against a claim}
+	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
 	\label{claimview}
@@
 \end{figure}
-\todo{Popup interface should contain a "don't mark this" button}
+\todo{Popup interface should contain a ``don't mark this'' button}
 
@@
 
-In the realm of News, Pew~\cite{pew-news} report that, while Internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible.
+In the realm of News, Pew~\cite{pew-news} reports that, while Internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible.
 Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.
@@
 In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust.
-Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in, understand why other people hold different points of view, and avoid being mislead by misinformation.
+Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in by exposing them to different points of view.
 
@@
 	\begin{center}
-	\includegraphics[width=8cm]{pictures/snippet_claim_article_fancy2.png}
-	\caption{Snippets entail claims, which are entailed or contradicted by articles}
+	\includegraphics[width=8cm]{pictures/snippet_claim_article_fancy3.png}
+	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
 	\label{snippet_claim_article}
@@
 {\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust.
-Their are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic.
+They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic.
 A user may behave like a skeptical reader for some topics and not others.
@@
 health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that don't affect them (e.g.
-entertainment) or topics for
+entertainment).
+
+\todo{Move our personals to a ``people'' section}
+
 \todo{Use interviews to get some actual observations here. These are just fillers.}
@@
 Many users fall into neither of these two personas.
-If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then Dispute Finder is unlikely to be useful for them.
+If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then they are unlikely to be interested in Dispute Finder.
 
@@
 Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic.
-Instead, the only way they can add promote an opinion is to link to an article from a trusted source that argues for that opinion.
+Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion.
 Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
@@
 
-Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as "is an example of", "supports", or "challenges".
+Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''.
 An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.
@@
 
+\todo{Talk about what dispute finder does, and how it differs - maybe by moving this into the main system section}
 \todo{Cite plagarism detection}
@@
 
+\todo{Talk about how this information was used in the design of Dispute Finder.}
+
 \subsection{Augmented Web Navigation}
@@
 	\includegraphics[width=8cm]{pictures/highlight_bar.png}
-	\caption{Highlight and Notification Bar}
+	\caption{Dispute Finder highlights text snippets that make disputed claims, and displays a notification bar to inform the user that they should look out for highlighted snippets.}
 	\label{highlight_bar}
@@
 The notification bar alerts the user that they should look out for highlighted snippets.
-Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors} or if the user is color blind.
+Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind.
 The notification bar also allows a user to step through the highlighted snippets on the page.
@@
 The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making.
-In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the "report incorrect highlighting" button from the popup interface.
+In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/popup_graph_crop.png}
-	\caption{Argumentation graph interface for a disputed claim}
-	\label{popup_graph}
-	\end{center}
-\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
 	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
@@
 For each article, the interface shows a summary sentence that captures the core argument used by the article.
-A user can add any web page as a supporting article by browsing to the page, selecting "use as evidence" from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
+A user can add any web page as a supporting article by browsing to the page, selectinguse as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
 \end{description}
@@
 	\includegraphics[width=6cm]{pictures/mark_evidence.png}
-	\caption{Adding an article, with a summary sentence selected}
+	\caption{To add an article, select some summary text, and click ``use as evidence'' from the context menu.}
 	\label{add_article}
@@
 	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
-	\caption{Choose how to connect an article with a claim}
+	\caption{Choose how to connect an article with a claim.}
 	\label{article_choose}
@@
 
-It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and {\it why} the various sources held those opinions.
+It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and what arguments were being put forward.
 
@@
 
-We do not want the database of disputed claims to contain everything that has every been disputed by anyone.
+We do not want the database of disputed claims to contain everything that has ever been disputed by anyone.
 In some sense almost everything is disputed by someone on the web.
@@
 	\includegraphics[width=8cm]{pictures/add_claim_list.png}
-	\caption{Interface for adding a new disputed claim manually}
+	\caption{A user can use this interface to add a new disputed claim manually.}
 	\label{add_claim}
@@
 For example Snopes.com maintains a list of urban legends and Politifact.com maintains a list of false claims about politics.
-We automatically import all claims that either of these sites debunk into our database and treat the sites themselves as reliable sources about the claims they debunk.
+We automatically import all claims that from these sites into our database.
 In the future we intend to also import claims from other such sites, and allow users to choose which feeds of disputed claims should be used to highlight snippets on pages they browse.
 
-We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{add_claim}).
+We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}).
 The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org.
@@
 	\includegraphics[width=6cm]{pictures/mark_disputed.png}
-	\caption{Explicit page marking}
+	\caption{Explicit page marking: select the text that makes a disputed claim and click ``this is disputed'' from the context menu.}
 	\label{mark_disputed}
@@
 	\includegraphics[width=7cm]{pictures/training2.png}
-	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons}
+	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
 	\label{training}
@@
 	\includegraphics[width=7cm]{pictures/nlp_client_server2.png}
-	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server}
+	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
 	\label{nlp_client_server}
@@
 	\includegraphics[width=7cm]{pictures/paraphrases.png}
-	\caption{Users can enter paraphrases of a claim to help the entailment algorithm}
+	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
 	\label{paraphrases}
@@
 \begin{description}
-\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting "mark as disputed" from a context menu (Figure~\ref{mark_disputed}).
+\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting ``mark as disputed'' from a context menu (Figure~\ref{mark_disputed}).
 
@@
 
-\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}).
+\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browses, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}).
 A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}).
@@
 not, never, can't) then so must the matching sentence.
-To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for "hot terms" such as "Global Warming" that are known to appear in disputed claims.
+To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims.
 The hot terms are selected such that every claim contains at least one hot term.
@@
 
-%The Design of Dispute Finder has been influenced by several different kinds of input from potential users.
-We performed a series of "think aloud" user studies to evaluate the user interface, we circulated a survey among members of a local debate club, and we performed a series of interviews with people selected from those who completed the survey.
-%
-%\subsection{Survey}
-%
-%We circulated a survey amongst members of a local debate club - a set of people who we believe is a good match for our Skeptical Reader and Activist personas.
-They survey asked respondants to tell us how often they typically engaged in various behaviours on the web.
-Although the survey was too small to be statistically useful, the results gave some useful information that we believe is worth reporting.
-%
-%Most people 65\% said that some of the information they read is not trustworthy, but they know which sites they can trust.
-Nobody said that they trusted the most of the information they read.
-17\% trust very little of the information they read, and 9\% feel confused about what they can trust.
-%
-%Everyone had used another source to double-check information they had read online.
-74\% "often" search the web to find web pages that confirm a claim they have read.
-64\% "often" check a website they trust.
-55\% "sometimes" ask a friend and 55\% "sometimes" check a book.
-%
-%When deciding whether to trust a web site, the most important factor was whether the site was run by an organization they trusted (61\% often, 30\% sometimes), followed by whether the site was linked from another site they trusted (18\%,50\%), and whether the site was well written (18\%,50\%).
-%
-%% \subsection{Interviews}
-%
-%\todo{Do we have enough interview content to integrate it? Probably not yet...}
-%\todo{Is the survey interesting enough to quote here? Only 23 people, and not exciting. Just quote inline with findings.}
-
-We performed three qualitative "think aloud" user studies.
+We performed three qualitative ``think aloud'' user studies.
 The aim of these studies was to inform the iterative design of the Dispute Finder tool.
 The studies were not intended to validate the design of Dispute Finder as being correct.
-The only way we will be able to truly validate Dispute Finder is by having it be adopted by a large community of active users - something it is not yet mature enough for.
 
@@
 For the first two studies, we recruited participants using Craigslist.
-We posted a message asking people to tell us how they used the web to form and promote their opinions, and used their responses to select people who we thought might fit our "skeptical reader" and "activist" personas.
-After these studies, we decided that the kind of person who looks for jobs of Craigslist is typically not a good fit for our personas, and so for the final study we instead used people we knew personally and thought fit our personas well.
-All study groups were small.
+We posted a message asking people to tell us how they used the web to form and promote their opinions, and used their responses to select people who we thought might fit our ``skeptical reader'' and ``activist'' personas.
+For the final study, we instead used people from our lab who we thought would be a good fit for our personas.
 The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had six participants participants (all male).
@@
 Each batch of users was shown a different iteration of the Dispute Finder design.
-The first two batches used versions in which users marked snippets explicitly and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view.
+The first two batches used versions in which users marked snippets explicitly and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view (Figure~\ref{popup_graph}).
 The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim.
@@
 Where a comment refers to particular version we make this clear.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/popup_graph_crop.png}
+	\caption{Argumentation graph interface for a disputed claim}
+	\label{popup_graph}
+	\end{center}
+\end{figure}
 
@@
 
-We also conducted interviews with most of our user study participants, and six additional people, asking them how they use the web to form and promote their opinions.
+We also conducted interviews with most of our user study participants, and five additional people, asking them how they use the web to form and promote their opinions.
 
@@
 
-Response was generally positive, with many participants being very keen to use the tool soon.
-Several participants asked as to notify them when it is properly deployed.
-Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
+Responses were generally positive. Most of the participants expressed an interest in using the tool ``when it is more mature'' with some keen to use it in its current state.
+
+\todo{Tye: say how many were keen to use the tool.}
 
@@
 A smaller number said they would be likely to enter claims they disagreed with (activist).
-One participant who was a political blogger was very excited about the mark things he thought were lies.
+One participant who was a political blogger was eager to mark things he thought were lies.
 
@@
 %
-%In the interface used in the first two studies, a user could mark a snippet by selecting it, right clicking on it, and clicking "mark as disputed".
+%In the interface used in the first two studies, a user could mark a snippet by selecting it, right clicking on it, and clicking ``mark as disputed''.
 They were then prompted to either select an existing claim or create a new one.
@@
 When marking a snippet on a particular page, users often did not appreciate that a claim should apply to more than one snippet.
-Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to "enter the text again".
+Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to ``enter the text again''.
 Similarly, several users got confused when a snippet made two different disputed claims.
-The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as "Global warming will cause X and Y".
+The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as ``Global warming will cause X and Y''.
 
@@
 In the first two studies, the popup interface for a claim showed an argumentation graph.
-This graph connected the graphs in our database using "supports" or "opposes" links, and allowed each claim to also be associated with supporting articles.
+This graph connected the graphs in our database using ``supports'' or ``opposes'' links, and allowed each claim to also be associated with supporting articles.
 When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected.
-One user said "I can see myself getting addicted to this", and another said "it's very intuitive".
+One user said ``I can see myself getting addicted to this'', and another said ``it's very intuitive''.
 
@@
 Several users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim.
-For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems".
+For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing problems''.
 Users correctly realized that the claims were related, but were not sure how best to connect them.
@@
 
-When using the article-list interface, several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative.
-For example a user would mark an article that opposed global warming as opposing the claim "global warming is bad" because the article opposed global warming.
+When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative.
+For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.
 
@@
 Several users created claims that had ambiguous meanings.
-One user entered a disputed claim about "Wood", meaning the guitarist "Ronnie Wood" of the Rolling Stones.
+One user entered a disputed claim about ``Wood'', meaning the guitarist ``Ronnie Wood'' of the Rolling Stones.
 Similar problems occurred with claims that were specific to a particular country, or a particular point in time.
@@
 Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them or that they were expected to be knowledgeable about, but were less interested about applying it to pages about other topics, that they were less interested in.
-For topics that didn't affect them users felt that misinformation was "not important enough to bother with", or that they could "afford to be misinformed".
+For topics that didn't affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''.
 
@@
 
-\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"opposes" graph.}
+\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple ``supports"/``opposes'' graph.}
 
@@
 
-An experimental preview version of Dispute Finder is available at 
-\url{http://disputefinder.org}
-
-Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users.
+As we discuss in this paper, our system requires multiple components to work in concert.
+Performing the tasks associated with these components well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users.
 We do however believe that Dispute Finder attacks an interesting problem that, if solved well, could significantly improve the utility of the web.
@@
 At the time of writing 11,682 people have installed and tried out Dispute Finder, 2,297 are active daily users, 140 have added new claims to our database, 149 have added articles, and our database contains 2,146 disputed claims.
+
+An experimental preview version of Dispute Finder is available at 
+\url{http://disputefinder.org}
 

### 2009-10-29 papers/www_disputefinder/disputefinder.tex
Reorganized content to merge related work into the main paper flow - but haven't yet edited anything

@@
        \affaddr{Berkeley, CA, USA}\\
-       \email{trush@berkeley.edu}
+       \email{trush@cs.berkeley.edu}
 \alignauthor John Mark Agosta\\
@@
 Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that appear to entail claims in its database of known disputed claims.
-If a user clicks on a highlighted phrase then Dispute Finder will show the user a summary of articles that support other points of view.
+If a user clicks on a highlighted phrase then Dispute Finder shows them a summary of articles that support other points of view.
 
@@
 
-Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is good enough to be compelling for most users.
-We do however believe that Dispute Finder attacks an interesting problem that, if addressed well, could significantly improve the utility of the web.
+In this paper, we explain the design of Dispute Finder, and the trade-offs between the various design decisions that we explored.
 
@@
 
-\section{INTRODUCTION}
+\section{Introduction}
 
@@
 
-\section{Related Work}
-
-Dispute Finder builds on prior work in many different areas.
+%\section{Related Work}
+%
+%Dispute Finder builds on prior work in many different areas.
 The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
@@
 Many people have developed textual entailment algorithms~\cite{entail?} that determine when one sentence implies the trust of another, or contradiction detection algorithms that determine when one sentence contradicts another.
-
-\todo{Add more references from the NewsCube paper}
-
-\subsection{Fact Checking Sites}
-
-If a user suspects that something they read online may be false then they can look it up on one of many fact checking sites such as Snopes.com, FactCheck.org, or Politifact.com.
-If one is aware that an issue is controversial and wants to understand the different sides, then one can use sites like Wikipedia.org, Debate.org, and ProCon.org.
-These sites do an excellent job presenting accurate and balanced information about controversial topics.
-
-Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services.
-Dispute Finder is designed to work together with fact checking sites.
-Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.
-
-\subsection{Analyzing News}
-
-While Dispute Finder is not intended to be applied only to news content, News is a particularly interesting source of disputed information, and one that others have looked at before.
-
-News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
-The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue.
-Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overall slant of the article.
-A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.
-
-Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias.
-Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking.
-Newstrust allows users to rate news articles for quality and objectivity.
-
-\subsection{Web Annotation Tools}
-
-Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content.
-Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
-There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features.
-
-Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic.
-Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion.
-Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
-
-Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
-If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
-If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears.
-The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.
-
-More generally, Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000,Wiil1996}.
-Like other Open Hypermedia systems, Dispute Finder lays an additional link structure over an existing hypertext document.
-In the case of Dispute Finder, the links are from disputed claims to information about those claims.
-
-Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}.
-Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags.
-In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
-
-\subsection{Sensemaking and Argumentation Tools}
-
-Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users.
-TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph.
-ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
-Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.
-
-Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''.
-An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.
-
-The intention behind these tools is that a user uses them to identify the source of information that is being used to motivate a conclusion.
-These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.
-
-We experimented with several different ways of explaining a disputed claim to a user.
-One of the approaches we implemented was a user-editable argumentation graph that connected each claim to other claims that support and oppose it, in addition to articles that argue in favor of that claim.
-This graph was inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
-
-Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions.
-Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
-We encountered similar problems with using an argumentation graph in Dispute Finder, which is why the current version of Dispute Finder presents a user with a list of articles rather than an argument graph.
-
-\subsection{Recognizing Textual Entailment}
-\label{related:entailment}
-
-\todo{Trim this down??}
-
-The textual entailment problem is one of the standard problems in natural language processing.
-In the 3-way variant of the PASCAL Recognizing Textual Entailment (RTE) Challenge\footnote{http://pascallin.ecs.soton.ac.uk/Challenges/RTE/}, an algorithm is given two sentences T and H and asked to return one of three answers: T {\it entails} H, T {\it contradicts} H, or the truth of H cannot be determined from T.
-
-Several of the core challenges in Dispute Finder are forms of the textual entailment problem.
-Finding disputed claims is a special case of finding two sentences on the web, such that one {\it contradicts} the other.
-Finding a snippet that makes a disputed claim is a special case of finding a snippet that {\it entails} a disputed claim.
-
-One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it contradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical.
-Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims.
-Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.
-
-Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims.
-The algorithm we use is a simple variant of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}.
-LLM simply reduces a sentence to a bag of lemmatized words, removes stop-words, checks for negations, and then looks at what the overlap is between the words in the two phrases.
-Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.
-
-\todo{Implement word weighting and word similarity?}
-
-%Following the taxonomy used by Jijkoun and Rijke~\cite{Jijkoun2006} our algorithm is M-sim-imp, that is, we assign entailment scores based soley on word overl
 %
-%The algorithm we use is a simple Local Lexical Matching (LLM) algorithm.
-
-LLM is far from being state of the art and many more sophisticated algorithms exist.
-Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
-Tools such as AuContraire~\cite{Ritter2008} focus specifically on detecting contradictions.
-Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.
-
-While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
-We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.
-
-\todo{Talk about Glickman et all 2005 and MT system of Bayer et al 2005}
-\todo{Cite Web Based probabalistic textual entailment}
-\todo{Cite MITRE's submission to the EU PASCAL RTE Challenge}
-
-\todo{Talk a lot about how people do textual entailment now}
-\todo{Do human-guided approach that works well? Talk more about human guided task.}
-
-\subsection{Finding Repeated Information on the Web}
-
-\todo{is this important}
-
-When Dispute Finder highlights many snippets that make a single disputed claim, this is a special case of the more general task of finding repeated information on the web.
-Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
-MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news sources and blogs.
-
-\todo{Talk about what dispute finder does, and how it differs - maybe by moving this into the main system section}
-\todo{Cite plagarism detection}
-\todo{Talk about how our algorithm looks for key terms used in disputed claims}
-\todo{Talk about how our first pass NLP algo is rather like }
+%\todo{Add more references from the NewsCube paper}
 
@@
 
-\subsection{Measuring Trust}
-
-Several authors have analyzed trust on Wikipedia.
-WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author.
-Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is.
-Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
-All these tools determine trustworthiness by examining the edit history of a page.
-
-BJ Fogg et al~\cite{Fogg2000, Fogg2003} have looked at the metrics that users use to determine when they should trust a source online.
-They found that the most important factor was whether a web site had a professional-looking design.
-Gill and Arts~\cite{Gil2006} identified on a different set of factors, including topic (a medical site may not be trusted on car repair), popularity and authority.
-
-\todo{Talk about how this information was used in the design of Dispute Finder.}
-
 \subsection{Augmented Web Navigation}
@@
 
-\section{The Dispute Finder System}
+\section{Trusting Online Content}
 
-Users interact with Dispute Finder in two ways.
-{\it Skeptical Readers} browse the web using the Dispute Finder Firefox extension and discover when pages they read make disputed claims.
-{\it Activists} tell Dispute Finder about disputed claims that they care about, add evidence to support their point of view, and help teach Dispute Finder to recognize particular claims on the web.
+\subsection{Measuring Trust}
 
-\subsection{Highlighting Snippets}
+Several authors have analyzed trust on Wikipedia.
+WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author.
+Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is.
+Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
+All these tools determine trustworthiness by examining the edit history of a page.
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{pictures/highlight_bar.png}
-	\caption{Dispute Finder highlights text snippets that make disputed claims, and displays a notification bar to inform the user that they should look out for highlighted snippets.}
-	\label{highlight_bar}
-	\end{center}
-\end{figure}
+BJ Fogg et al~\cite{Fogg2000, Fogg2003} have looked at the metrics that users use to determine when they should trust a source online.
+They found that the most important factor was whether a web site had a professional-looking design.
+Gill and Arts~\cite{Gil2006} identified on a different set of factors, including topic (a medical site may not be trusted on car repair), popularity and authority.
 
-%Dispute Finder is designed to alert a user when information they read on a web page makes a claim that is disputed by a source they might trust. 
-%
-%
-%Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust.
-We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.
+\todo{Talk about how this information was used in the design of Dispute Finder.}
 
-The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed.
-It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).
+\subsection{Fact Checking Sites}
 
-The notification bar alerts the user that they should look out for highlighted snippets.
-Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind.
-The notification bar also allows a user to step through the highlighted snippets on the page.
+If a user suspects that something they read online may be false then they can look it up on one of many fact checking sites such as Snopes.com, FactCheck.org, or Politifact.com.
+If one is aware that an issue is controversial and wants to understand the different sides, then one can use sites like Wikipedia.org, Debate.org, and ProCon.org.
+These sites do an excellent job presenting accurate and balanced information about controversial topics.
 
-The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims.
-This allows a user to ignore disputed claims that are made by text that the user isn't interested in - such as user comments.
-The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making.
-In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.
+Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services.
+Dispute Finder is designed to work together with fact checking sites.
+Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.
 
-Once a user is aware that a claim is disputed, there is little point telling them about the same disputed claim again in the future.
-We have not yet concluded whether it is better for Dispute Finder to automatically stop highlighting a claim once a user has viewed the claim, or whether it is better for a user to explicitly ask Dispute Finder to stop highlighting a claim.
-In our current implementation, a user can tell Dispute Finder to not highlight a claim again by setting the ``don't highlight this claim for me again'' checkbox in the popup interface (Figure~\ref{claimview}).
-Requiring a user to manually opt out of a claim requires more work from the user, but hiding already viewed claims can be confusing, since users do not normally expect viewing something to be a destructive operation.
-A compromise position is to highlight claims that have been seen before in a fainter color; similar to the way links are typically colored on web pages.
+\subsection{Analyzing News}
 
-\todo{Try using a fainter color}
+While Dispute Finder is not intended to be applied only to news content, News is a particularly interesting source of disputed information, and one that others have looked at before.
 
-\todo{Text is wrong in the screenshot}
+News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
+The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue.
+Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overall slant of the article.
+A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.
 
-Dispute Finder also provides an API that can be used by other sites to determine whether their content makes disputed claims.
-For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.
+Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias.
+Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking.
+Newstrust allows users to rate news articles for quality and objectivity.
 
-\todo{Document API online}
-\todo{Change the highlight color to yellow? Auto-adjust highlight color based on background color?}
-\todo{Should we automatically adjust the highlight color, based on the background color of the page}
-\todo{Discuss previous work on highlighting here, rather than in related work?}
-
-\subsection{Explaining Disputed Claims}
-
-If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view.
-We could have omitted this feature and still had a useful system.
-Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim.
-There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:
-
-\begin{description}
-\item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
-\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view - otherwise Dispute Finder would be annoying.
-By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
-\item[Filtering:] Although we have not implement this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
-\end{description}
-
-Naturally, sources such as Wikipedia, Politifact, and Snopes are often used as sources of evidence for and against a claim --- indeed we currently import articles from Politifact and Snopes automatically.
-
-We prototyped and tested two different ways of showing a user alternative points of view to the disputed claim they are looking at:
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
-	\caption{Article List interface for a disputed claim}
-	\label{article_list}
-	\end{center}
-\end{figure}
-
-\begin{description}
-\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph~\cite{Conklin1987a}.
-Each claim is linked to claims that represent alternative points of view, and claims that support that point of view.
-Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})
-
-\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}).
-For each article, the interface shows a summary sentence that captures the core argument used by the article.
-A user can add any web page as a supporting article by browsing to the page, selectinguse as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
-\end{description}
-
-The argumentation graph makes it easier to see {\it why} a claim is disputed, while the article lists make it easier to see {\it who} supports or opposes the claim.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{pictures/mark_evidence.png}
-	\caption{To add an article, select some summary text, and click ``use as evidence'' from the context menu.}
-	\label{add_article}
-	\end{center}
-\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
-	\caption{Choose how to connect an article with a claim.}
-	\label{article_choose}
-	\end{center}
-\end{figure}
-
-\todo{Call them supporting pages? Naming is a mess right now.}
-
-When using the article list approach, several different articles may be expressing essentially the same point of view and it may not be obvious that one of the articles is making a point that the user had not come across before.
-The argumentation graph allows the user to easily see what the range of different opinions is, and quickly see if there is an argument that they have not encountered before.
-
-A significant weakness of the argumentation graph approach is that a good argumentation graph takes significantly more effort to build than a simple list of articles.
-In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users.
-There were two problems here: firstly, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; secondly, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}.
-This result is consistent with previous studies~\cite{Isenmann1997}.
-
-Another point in favor of using a simple list of sources is that most of the users we talked to seemed to be more interested in {\it who} disputed a claim, rather than what their argument was.
-For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with.
-Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they preferred to read whichever article seemed to be most credible, rather than browsing an argumentation graph.
-
-It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and what arguments were being put forward.
-
-\subsection{Trustworthy Sources}
-
-In the current version of Dispute Finder, an article can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable.
-Good sources of articles include newspapers, universities, respected organizations, and Wikipedia itself.
-Users can vote on whether they think a particular article is useful, and this voting determines the order in which articles are listed.
-A user can also request that an article be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable articles.
-Users with moderator privileges review requests for deletion and delete claims and articles that do not meet requirements.
-
-\todo{study result: verify}
-There are significant weaknesses in this approach.
-Pew have shown~\cite{pew-news} that different people trust different sources.
-There may be little point showing liberal sources to a conservative, or vice-versa.
-Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments.
-Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.
-
-It may thus be better to learn what sources a particular user is likely to believe are reliable, and then adjust both what sources Dispute Finder shows to the user, and what claims are highlighted, based on this.
-
-There is a difficult trade-off here.
-If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own world-view then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
-On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right.
-If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously.
-We do not yet claim to know a good solution for this problem, but we believe it is an interesting area for further research.
-
-\todo{Cite Pew Research study saying people like to read news that supports their own point of view, but many others like neutral sources. http://people-press.org/report/?pageid=1353}
-
-\subsection{What is Disputed?}
+\section{What is Disputed?}
 
@@
 
-\subsection{Finding Snippets}
+\section{Finding Snippets}
 
@@
 \todo{Explain how our algorithm relates to existing NLP work - due to unusual domain}
+
+\subsection{Sensemaking and Argumentation Tools}
+
+\todo{Talk about this work in the introduction?}
+
+Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users.
+TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph.
+ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
+Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.
+
+Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''.
+An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.
+
+The intention behind these tools is that a user uses them to identify the source of information that is being used to motivate a conclusion.
+These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.
+
+\subsection{Recognizing Textual Entailment}
+\label{related:entailment}
+
+\todo{Trim this down??}
+
+The textual entailment problem is one of the standard problems in natural language processing.
+In the 3-way variant of the PASCAL Recognizing Textual Entailment (RTE) Challenge\footnote{http://pascallin.ecs.soton.ac.uk/Challenges/RTE/}, an algorithm is given two sentences T and H and asked to return one of three answers: T {\it entails} H, T {\it contradicts} H, or the truth of H cannot be determined from T.
+
+Several of the core challenges in Dispute Finder are forms of the textual entailment problem.
+Finding disputed claims is a special case of finding two sentences on the web, such that one {\it contradicts} the other.
+Finding a snippet that makes a disputed claim is a special case of finding a snippet that {\it entails} a disputed claim.
+
+One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it contradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical.
+Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims.
+Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.
+
+Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims.
+The algorithm we use is a simple variant of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}.
+LLM simply reduces a sentence to a bag of lemmatized words, removes stop-words, checks for negations, and then looks at what the overlap is between the words in the two phrases.
+Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.
+
+\todo{Implement word weighting and word similarity?}
+
+%Following the taxonomy used by Jijkoun and Rijke~\cite{Jijkoun2006} our algorithm is M-sim-imp, that is, we assign entailment scores based soley on word overl
+%
+%The algorithm we use is a simple Local Lexical Matching (LLM) algorithm.
+
+LLM is far from being state of the art and many more sophisticated algorithms exist.
+Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
+Tools such as AuContraire~\cite{Ritter2008} focus specifically on detecting contradictions.
+Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.
+
+While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
+We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.
+
+\todo{Talk about Glickman et all 2005 and MT system of Bayer et al 2005}
+\todo{Cite Web Based probabalistic textual entailment}
+\todo{Cite MITRE's submission to the EU PASCAL RTE Challenge}
+
+\todo{Talk a lot about how people do textual entailment now}
+\todo{Do human-guided approach that works well? Talk more about human guided task.}
+
+\subsection{Finding Repeated Information on the Web}
+
+\todo{is this important}
+
+When Dispute Finder highlights many snippets that make a single disputed claim, this is a special case of the more general task of finding repeated information on the web.
+Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
+MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news sources and blogs.
+
+\todo{Talk about what dispute finder does, and how it differs - maybe by moving this into the main system section}
+\todo{Cite plagarism detection}
+\todo{Talk about how our algorithm looks for key terms used in disputed claims}
+\todo{Talk about how our first pass NLP algo is rather like }
+
+\section{Explaining Disputed Claims}
+
+If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view.
+We could have omitted this feature and still had a useful system.
+Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim.
+There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:
+
+\begin{description}
+\item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
+\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view - otherwise Dispute Finder would be annoying.
+By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
+\item[Filtering:] Although we have not implement this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
+\end{description}
+
+Naturally, sources such as Wikipedia, Politifact, and Snopes are often used as sources of evidence for and against a claim --- indeed we currently import articles from Politifact and Snopes automatically.
+
+We prototyped and tested two different ways of showing a user alternative points of view to the disputed claim they are looking at:
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
+	\caption{Article List interface for a disputed claim}
+	\label{article_list}
+	\end{center}
+\end{figure}
+
+\begin{description}
+\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph~\cite{Conklin1987a}.
+Each claim is linked to claims that represent alternative points of view, and claims that support that point of view.
+Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})
+
+\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}).
+For each article, the interface shows a summary sentence that captures the core argument used by the article.
+A user can add any web page as a supporting article by browsing to the page, selectinguse as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
+\end{description}
+
+The argumentation graph makes it easier to see {\it why} a claim is disputed, while the article lists make it easier to see {\it who} supports or opposes the claim.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/mark_evidence.png}
+	\caption{To add an article, select some summary text, and click ``use as evidence'' from the context menu.}
+	\label{add_article}
+	\end{center}
+\end{figure}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
+	\caption{Choose how to connect an article with a claim.}
+	\label{article_choose}
+	\end{center}
+\end{figure}
+
+\todo{Call them supporting pages? Naming is a mess right now.}
+
+When using the article list approach, several different articles may be expressing essentially the same point of view and it may not be obvious that one of the articles is making a point that the user had not come across before.
+The argumentation graph allows the user to easily see what the range of different opinions is, and quickly see if there is an argument that they have not encountered before.
+
+A significant weakness of the argumentation graph approach is that a good argumentation graph takes significantly more effort to build than a simple list of articles.
+In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users.
+There were two problems here: firstly, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; secondly, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}.
+This result is consistent with previous studies~\cite{Isenmann1997}.
+
+Another point in favor of using a simple list of sources is that most of the users we talked to seemed to be more interested in {\it who} disputed a claim, rather than what their argument was.
+For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with.
+Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they preferred to read whichever article seemed to be most credible, rather than browsing an argumentation graph.
+
+It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and what arguments were being put forward.
+
+\subsection{Argumentation Graphs}
+
+We experimented with several different ways of explaining a disputed claim to a user.
+One of the approaches we implemented was a user-editable argumentation graph that connected each claim to other claims that support and oppose it, in addition to articles that argue in favor of that claim.
+This graph was inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
+
+Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions.
+Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
+We encountered similar problems with using an argumentation graph in Dispute Finder, which is why the current version of Dispute Finder presents a user with a list of articles rather than an argument graph.
+
+\section{Trustworthy Sources}
+
+In the current version of Dispute Finder, an article can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable.
+Good sources of articles include newspapers, universities, respected organizations, and Wikipedia itself.
+Users can vote on whether they think a particular article is useful, and this voting determines the order in which articles are listed.
+A user can also request that an article be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable articles.
+Users with moderator privileges review requests for deletion and delete claims and articles that do not meet requirements.
+
+\todo{study result: verify}
+There are significant weaknesses in this approach.
+Pew have shown~\cite{pew-news} that different people trust different sources.
+There may be little point showing liberal sources to a conservative, or vice-versa.
+Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments.
+Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.
+
+It may thus be better to learn what sources a particular user is likely to believe are reliable, and then adjust both what sources Dispute Finder shows to the user, and what claims are highlighted, based on this.
+
+There is a difficult trade-off here.
+If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own world-view then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
+On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right.
+If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously.
+We do not yet claim to know a good solution for this problem, but we believe it is an interesting area for further research.
+
+\todo{Cite Pew Research study saying people like to read news that supports their own point of view, but many others like neutral sources. http://people-press.org/report/?pageid=1353}
+
+\section{Highlighting Snippets}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{pictures/highlight_bar.png}
+	\caption{Dispute Finder highlights text snippets that make disputed claims, and displays a notification bar to inform the user that they should look out for highlighted snippets.}
+	\label{highlight_bar}
+	\end{center}
+\end{figure}
+
+%Dispute Finder is designed to alert a user when information they read on a web page makes a claim that is disputed by a source they might trust. 
+%
+%
+%Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust.
+We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.
+
+The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed.
+It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).
+
+The notification bar alerts the user that they should look out for highlighted snippets.
+Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind.
+The notification bar also allows a user to step through the highlighted snippets on the page.
+
+The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims.
+This allows a user to ignore disputed claims that are made by text that the user isn't interested in - such as user comments.
+The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making.
+In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.
+
+Once a user is aware that a claim is disputed, there is little point telling them about the same disputed claim again in the future.
+We have not yet concluded whether it is better for Dispute Finder to automatically stop highlighting a claim once a user has viewed the claim, or whether it is better for a user to explicitly ask Dispute Finder to stop highlighting a claim.
+In our current implementation, a user can tell Dispute Finder to not highlight a claim again by setting the ``don't highlight this claim for me again'' checkbox in the popup interface (Figure~\ref{claimview}).
+Requiring a user to manually opt out of a claim requires more work from the user, but hiding already viewed claims can be confusing, since users do not normally expect viewing something to be a destructive operation.
+A compromise position is to highlight claims that have been seen before in a fainter color; similar to the way links are typically colored on web pages.
+
+\todo{Try using a fainter color}
+
+\todo{Text is wrong in the screenshot}
+
+Dispute Finder also provides an API that can be used by other sites to determine whether their content makes disputed claims.
+For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.
+
+\todo{Document API online}
+\todo{Change the highlight color to yellow? Auto-adjust highlight color based on background color?}
+\todo{Should we automatically adjust the highlight color, based on the background color of the page}
+\todo{Discuss previous work on highlighting here, rather than in related work?}
+
+\subsection{Web Annotation Tools}
+
+Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content.
+Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
+There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features.
+
+Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic.
+Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion.
+Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
+
+Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
+If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
+If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears.
+The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.
+
+More generally, Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000,Wiil1996}.
+Like other Open Hypermedia systems, Dispute Finder lays an additional link structure over an existing hypertext document.
+In the case of Dispute Finder, the links are from disputed claims to information about those claims.
+
+Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}.
+Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags.
+In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
 

### 2009-10-29 papers/www_disputefinder/disputefinder.tex
Applied Beth changes and puled most of the related work content into the body of the paper

@@
 If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
+Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.
 
@@
 
-In the realm of News, Pew~\cite{pew-news} reports that, while Internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible.
-Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.
-
 \todo{word this better}\todo{update all screenshots}
@@
 
+Dispute Finder consists of a database, an API, and a Firefox browser extension.
+The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}).
+The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claim.
+The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims.
+The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.
+
+In this paper, we describe the design of Dispute Finder, the trade-offs we encountered between different design choices, and our experiences testing Dispute Finder with users.
+
 \begin{figure}[tb]
@@
 
-Dispute Finder consists of a database, an API, and a Firefox browser extension.
-The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}).
-The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims.
-The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims.
-The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.
+Dispute Finder has been influenced by previous work in many different fields, including sensemaking, web annotation, natural language processing, and information extraction.
+We discuss this work throughout the paper.
 
-\todo{Figure that does a smaller highlight}
+\subsection{Challenges}
 
-There are several design decisions that must be made when building a system such as this. In particular:
+During the design and implementation of Dispute Finder, we had to come up with solutions for several challenges:
 
 \begin{description}
-\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users are not distracted by things that they would not consider to be disputed).
-We currently use a combination of crowd-sourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims.
-More generally, the challenge is not to determine if a claim is disputed by {\it anyone} but to determine whether there is an alternative point of view that this particular user would take seriously.
+\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large and credible.
+If the database is too small then users will rarely see snippets highlighted.
+If a snippet is highlighted but there is no credible evidence for other points of view, then users will find Dispute Finder annoying.
+We currently crowd-source claims from users, and mine disputed claims from web sites such as Snopes and Politifact that already maintain lists of disputed claims.
 
-\item[How do we find disputed snippets?] Given a particular web page, how do we determine which phrases on that page are making known disputed claims?
-We have experimented with several different approaches, each of which has different advantages and disadvantages.
-One can ask users to mark snippets individually.
-One can build a search tool that allows a user to find and mark similar snippets in bulk.
-One can provide an interface that allows a user to train a machine learning classifier to recognize snippets.
-One can run a textual entailment algorithm on the client that looks for phrases that look similar to a known claim.
+\item[How do we find disputed snippets?] Given a particular web page, how do we determine which phrases on that page are making known disputed claims and should be highlighted?
+There is a tradeoff between precision and recall.
+If we highlight a snippet that is not making a disputed claim then the user will be annoyed, but if we do not highlight a snippet that is making a disputed claim then Dispute Finding missed an opportunity to be useful.
+We currently run a textual entailment algorithm inside the browser extension that looks for phrases that look similar to a known disputed claim.
 
-\item[How do we highlight snippets?] How do we tell what web page a user is reading, and augment their interface to alert them about disputed claims?
-Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension.
-Using a proxy~\cite{Barrett1997} has similar adoption problems to a browser extension, and is likely to break some web sites.
-If external sites such as news readers and search engines use our API then they can provide information about disputed claims to users without them having to install anything, but this limits coverage to content accessed through sites that use the API.
+\item[How do we highlight snippets?] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed.
+Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt.
+We currently use a browser extension that checks for disputed claims on every page the user browses, and offer an API that other web sites can use to mark disputed claims on content that they serve.
 
-\item[How should we explain a disputed claim?] If someone requests more information about a disputed claim by clicking on a highlighted snippet, what information should we show them that will help them decide whether to consider alternative points of view?
-We tried an argumentation graph and lists of articles that support or oppose the claim.
+\item[How should we explain a disputed claim?] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim.
+We currently use a simple list of articles arguing for and against the claim.
+
+\item[What do people want?] To be useful for users, Dispute Finder needs to serve a real need that users have.
+We used interviews, user studies, and a small survey to try to learn what users want and what users are likely to use.
 \end{description}
 
+In the rest of this paper, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.
+
+\subsection{Personas}
+
 If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use.
-Dispute Finder is designed to cater to two personas.
+We designed Dispute Finder is designed to cater to two personas.
 Each persona was created from interviews we conducted with people who we believe fit into these categories.
@@
 
-We used several different methods to gain input from users.
-We performed three rounds of users studies, circulated a survey within a target group, and conducted a series of interviews.
-We discuss the conclusions of these studies throughout the paper, and in a section at the end.
-These studies were intended to inform the design of Dispute Finder, rather than to validate it.
-The only way to conclusively demonstrate that Dispute Finder is useful would be for it to be adopted by many active users -- something that the current implementation is not mature enough to support.
+\section{Related Work}
 
-\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
-\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
-\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}
+Many other tools highlight disputed information on web pages.
+ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content.
+Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
+There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features, and most of which could be used to annotate disputed content.
 
-\todo{Should we explicitly list what we think are our key contributions?}
+Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic.
+Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion.
+Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
 
-%\section{Related Work}
-%
-%Dispute Finder builds on prior work in many different areas.
-The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
-Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information.
-Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
-Many people have developed textual entailment algorithms~\cite{entail?} that determine when one sentence implies the trust of another, or contradiction detection algorithms that determine when one sentence contradicts another.
-%
-%\todo{Add more references from the NewsCube paper}
+Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
+If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
+If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears.
+The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.
 
-%
-%\subsection{Finding Disputed Information on the Web}
-%
-%An important part of Dispute Finder is identifying what claims are disputed. Several other authors looked at disputed information on the web.
-%
-%Kittur et al~\cite{Kittur2007} developed an algorithm that can determine whether a wikipedia page is about a disputed topic.
-Kittur and Chi~\cite{Kittur2009} broke down the disputed pages by catagory and found that People, Society, and Religion were the categories with the most disputed pages.
-%
-%\subsection{Extracting Information from the Web}
-%
-%Information extration tools such as TextRunner~\cite{Etzioni2008} 
-%Read The Web
-%
-%TextRunner~\cite{Etzioni2008} 
-%
-%\todo{cite lots of Etzioni stuff}
-%
-%\cite{SnowBall}
-%\cite{Read The Web}
-%\cite{Information Extraction from Wikipedia}
-%\cite{KnowItAll}
-%\cite{TextRunner}
-%
-%\todo{Online Dispute Resolution}
-%
-%\todo{Cite Kittur et al}
+Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users.
+TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph.
+ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
+Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.
+Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''.
+An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.
 
-\subsection{Augmented Web Navigation}
+The intention behind these tools is that a user uses them to identify the source of information that is being used to motivate a conclusion.
+These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.
 
-Several tools layer an alternative navigation graph over information on the web.
-TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages.
-ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in.
+There are also several tools that find pages that put forward different points of view, rather than identifying disputed claims within a page.
+News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
+The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue.
+Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias.
+Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking.
+Newstrust allows users to rate news articles for quality and objectivity.
 
-%\subsection{Persuasive Technology}
+On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
 
-% \subsection{Semantic Web}
-% 
-% Nobody is going to mark up their own web page as being wrong.
+More generally, Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000,Wiil1996}.
+Like other Open Hypermedia systems, Dispute Finder lays an additional link structure over an existing hypertext document.
+In the case of Dispute Finder, the links are from disputed claims to information about those claims.
 
-% \subsection{To discuss in the body}
-% 
-% Paraphrases~\cite{Chklovski2005}. Suggested formal paraphrases~\cite{Blythe2004}.
-% Importance of Lurkers~\cite{Takahashi2003}
-% Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.
+Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}.
+Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags.
+In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
 
@@
 
-\subsection{Measuring Trust}
+If a web user trusted all the content that they read, or were unconcerned that information they read might be wrong, then it is unlikely that they they would be much demand for a service such as Dispute Finder.
+Fortunately, there is ample evidence that at least some people are skeptical about the information they read and would like to know about alternative points of view that are supported by sources that they trust.
 
-Several authors have analyzed trust on Wikipedia.
-WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author.
-Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is.
-Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
-All these tools determine trustworthiness by examining the edit history of a page.
+According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust.
+Their 2008 survey found that 33\% of registered democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says.
+Pew also found that online sources are viewed with more skepticism than their print, broadcast, and cable counterparts.
 
-BJ Fogg et al~\cite{Fogg2000, Fogg2003} have looked at the metrics that users use to determine when they should trust a source online.
-They found that the most important factor was whether a web site had a professional-looking design.
-Gill and Arts~\cite{Gil2006} identified on a different set of factors, including topic (a medical site may not be trusted on car repair), popularity and authority.
+This result was backed up by our interviews.
+Several participants told us that they regularly get information from sources that they don't entirely trust.
+A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search.
 
-\todo{Talk about how this information was used in the design of Dispute Finder.}
+There is also evidence that a significant group of people are interested in checking information they read on the web.
+Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web.
+Snopes.com contains information about urban myths such as ``eskimos have many words for snow''.
+Factcheck.org and Politifact.com investigate claims about US politics.
+According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand.
+Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts.
+In our survey, 64\% of respondents said that they often check information they read on a trusted site and 74\% of respondents said that they often check information they read by searching for other web pages with information about that topic.
 
-\subsection{Fact Checking Sites}
-
-If a user suspects that something they read online may be false then they can look it up on one of many fact checking sites such as Snopes.com, FactCheck.org, or Politifact.com.
-If one is aware that an issue is controversial and wants to understand the different sides, then one can use sites like Wikipedia.org, Debate.org, and ProCon.org.
-These sites do an excellent job presenting accurate and balanced information about controversial topics.
+Fact checking web sites and search engines work great when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed.
+The primary aim of Dispute Finder is to let you know when something you are reading is disputed.
 
@@
 
-\subsection{Analyzing News}
-
-While Dispute Finder is not intended to be applied only to news content, News is a particularly interesting source of disputed information, and one that others have looked at before.
-
-News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
-The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue.
-Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overall slant of the article.
-A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.
-
-Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias.
-Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking.
-Newstrust allows users to rate news articles for quality and objectivity.
+\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
+\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
+\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}
+\todo{Should we explicitly list what we think are our key contributions?}
 
 \section{What is Disputed?}
+\label{sec:disputed}
 
-One of the biggest challenges in Dispute Finder, is how to build a list of disputed claims that should be highlighted for users.
-As discussed in Section~\ref{related:entailment}, rather than directly inferring whether a snippet is disputed by a trusted article on the web, Dispute Finder instead builds a database of known disputed claims and tries to determine whether a snippet on a web page entails the truth of one of these claims.
+Dispute Finder maintains a shared database of known disputed claims.
+The browser extension highlights a text snippet if it believes that the snippet entails one of the claims in this database (Figure~\ref{snippet_claim_article}).
+Claims can either be added directly by users (Figure~\ref{add_claim}) or mined from web sites such as Snopes and Politifact that already maintain well curated databases of disputed claims,
 
-\todo{We are repeating information between here and the related work section on Recognizing Textual Entailment}
-
-We do not want the database of disputed claims to contain everything that has ever been disputed by anyone.
+This database should not contain contain everything that has ever been disputed by anyone.
 In some sense almost everything is disputed by someone on the web.
@@
 
-Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them.
-For example Snopes.com maintains a list of urban legends and Politifact.com maintains a list of false claims about politics.
-We automatically import all claims that from these sites into our database.
-In the future we intend to also import claims from other such sites, and allow users to choose which feeds of disputed claims should be used to highlight snippets on pages they browse.
+Currently most of our claims are automatically mined Snopes and Politifact.
+Both of these sites maintain well curated databases of disputed claims, together with information about them.
+Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American Policitians.
+In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g.
+medical claims) and to provide an API to allow any site to provide a well-structured feed that we can use.
+At the time of writing, Dispute Finder has imported 1,457 claims from Snopes and 595 claims from Politifact.
 
@@
 
+An alternative approach would be to use Contradiction Detection~\cite{Ritter} to find frequently repeated statements that appear to contradict statements from trusted sources.
+Unfortunately at the time of writing, Contradiction Detection does not seem to be robust enough for us to use it for this purpose.
+
+In future work, we hope to automatically find disputed claims on the web by looking for phrases like ``falsely claimed that X'' --- a similar techniques to that used by Hearst to find hyponyms~\cite{Hearst1992}.
+
 \todo{Say how many disputed claims}
-
 \todo{talk about duplicates}
-
 \todo{Actually import the Politifact data}
@@
 
-Given a web page, Dispute Finder needs to identify which snippets are making known disputed claims. We implemented and tested four different approaches:
+Given a web page, Dispute Finder needs to identify which snippets are making known disputed claims.
+Our current implementation runs a simple textual entailment algorithm inside the browser to look for sentences that entail known disputed claims.
+
+We implemented and tested four different approaches:
 
@@
 However the manual effort required per page makes it difficult for this approach to scale.
-We also found that it can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page.
+We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page.
 This same problem that has hindered the adoption of numerous web page annotation tools.
@@
 
-Client side entailment gets even more coverage.
+Client side entailment gets the most coverage.
 Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined.
@@
 
-The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP.
-It divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
+The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}.
+Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
 If the claim contains a negation word (e.g.
@@
 If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.
+
+LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist.
+Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
+Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions.
+Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.
+
+While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
+We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.
 
@@
 
-\subsection{Sensemaking and Argumentation Tools}
+Other authors have used similar algorithms to find repeated information on the web.
+Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
+MemeTracker~\cite{Backstrom2009} looks for phrases shared by multiple news stories, accounting for minor variations, and uses this to track the way that news flows between traditional news sources and blogs.
 
-\todo{Talk about this work in the introduction?}
+The authors of MemeTracker observed that many ideas often flow around the web in the form of ``memes'' that are repeated on many web sites with relatively little variation.
+MemeTracker uses this to track the way an idea propagates across the web using a relatively simple algorithm.
+We have found that the precision and recall of our client-side textual entailment algorithm varies hugely depending on how meme-like a claim is.
+Some claims (particularly those derived from quotes) are widely repeated almost-verbatim, and can be detected relatively easily.
+However many other claims are rarely stated explicitly in a single sentence or with the same choice of words, making them much harder to detect with a simple algorithm.
 
-Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users.
-TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph.
-ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
-Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.
-
-Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''.
-An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.
-
-The intention behind these tools is that a user uses them to identify the source of information that is being used to motivate a conclusion.
-These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.
-
-\subsection{Recognizing Textual Entailment}
-\label{related:entailment}
-
-\todo{Trim this down??}
-
-The textual entailment problem is one of the standard problems in natural language processing.
-In the 3-way variant of the PASCAL Recognizing Textual Entailment (RTE) Challenge\footnote{http://pascallin.ecs.soton.ac.uk/Challenges/RTE/}, an algorithm is given two sentences T and H and asked to return one of three answers: T {\it entails} H, T {\it contradicts} H, or the truth of H cannot be determined from T.
-
-Several of the core challenges in Dispute Finder are forms of the textual entailment problem.
-Finding disputed claims is a special case of finding two sentences on the web, such that one {\it contradicts} the other.
-Finding a snippet that makes a disputed claim is a special case of finding a snippet that {\it entails} a disputed claim.
-
-One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it contradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical.
-Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims.
-Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.
-
-Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims.
-The algorithm we use is a simple variant of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}.
-LLM simply reduces a sentence to a bag of lemmatized words, removes stop-words, checks for negations, and then looks at what the overlap is between the words in the two phrases.
-Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.
-
-\todo{Implement word weighting and word similarity?}
-
-%Following the taxonomy used by Jijkoun and Rijke~\cite{Jijkoun2006} our algorithm is M-sim-imp, that is, we assign entailment scores based soley on word overl
-%
-%The algorithm we use is a simple Local Lexical Matching (LLM) algorithm.
-
-LLM is far from being state of the art and many more sophisticated algorithms exist.
-Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
-Tools such as AuContraire~\cite{Ritter2008} focus specifically on detecting contradictions.
-Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.
-
-While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
-We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.
-
-\todo{Talk about Glickman et all 2005 and MT system of Bayer et al 2005}
-\todo{Cite Web Based probabalistic textual entailment}
-\todo{Cite MITRE's submission to the EU PASCAL RTE Challenge}
-
-\todo{Talk a lot about how people do textual entailment now}
-\todo{Do human-guided approach that works well? Talk more about human guided task.}
-
-\subsection{Finding Repeated Information on the Web}
-
-\todo{is this important}
-
-When Dispute Finder highlights many snippets that make a single disputed claim, this is a special case of the more general task of finding repeated information on the web.
-Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
-MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news sources and blogs.
+\todo{Give an example of a good meme}
 
@@
 \section{Explaining Disputed Claims}
+
+When a user clicks on a highlighted snippet, Dispute Finder displays a popup interface with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read.
+In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}).
+We also implemented and tested an interface that contained a user-editable argumentation graph, however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.
 
@@
 \begin{description}
-\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph~\cite{Conklin1987a}.
+\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
 Each claim is linked to claims that represent alternative points of view, and claims that support that point of view.
@@
 
-\subsection{Argumentation Graphs}
-
-We experimented with several different ways of explaining a disputed claim to a user.
-One of the approaches we implemented was a user-editable argumentation graph that connected each claim to other claims that support and oppose it, in addition to articles that argue in favor of that claim.
-This graph was inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
-
-Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions.
-Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph.
-We encountered similar problems with using an argumentation graph in Dispute Finder, which is why the current version of Dispute Finder presents a user with a list of articles rather than an argument graph.
-
 \section{Trustworthy Sources}
@@
 
-\todo{study result: verify}
-There are significant weaknesses in this approach.
-Pew have shown~\cite{pew-news} that different people trust different sources.
-There may be little point showing liberal sources to a conservative, or vice-versa.
+Unfortunately, as Pew report~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust tend to be those that share the person's own point of view.
+It seems that ``without a point of view'' is a similar concept to ``without an accent''.
+As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa.
 Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments.
@@
 \todo{Cite Pew Research study saying people like to read news that supports their own point of view, but many others like neutral sources. http://people-press.org/report/?pageid=1353}
+
+Other researchers have looked at ways to determine what sources a user will trust. 
+BJ Fogg et al~\cite{Fogg2003} found that the most important factor was whether a web site had a professional-looking design.
+Gill and Arts~\cite{Gil2006} identified on a different set of factors, including topic (a medical site may not be trusted for advice on car repair), popularity (does everyone else use this) and authority.
 
@@
 
-Dispute Finder also provides an API that can be used by other sites to determine whether their content makes disputed claims.
+Dispute Finder also provides an API that allows other sites to determine whether their content makes disputed claims.
 For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.
@@
 \todo{Discuss previous work on highlighting here, rather than in related work?}
-
-\subsection{Web Annotation Tools}
-
-Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content.
-Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
-There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features.
-
-Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic.
-Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion.
-Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
-
-Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
-If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
-If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears.
-The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.
-
-More generally, Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000,Wiil1996}.
-Like other Open Hypermedia systems, Dispute Finder lays an additional link structure over an existing hypertext document.
-In the case of Dispute Finder, the links are from disputed claims to information about those claims.
-
-Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}.
-Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags.
-In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
 

### 2009-10-29 papers/www_disputefinder/disputefinder.tex
Folded in JM's changes

@@
 The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}.
-If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
+If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
 Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.
@@
 
-Dispute Finder consists of a database, an API, and a Firefox browser extension.
+Dispute Finder consists of a server-side database, an API, and a Firefox browser extension.
 The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}).
@@
 \item[What is disputed?] To be useful, the set of known disputed claims needs to be both large and credible.
-If the database is too small then users will rarely see snippets highlighted.
+If the database's coverage is too small then users will rarely see snippets highlighted.
 If a snippet is highlighted but there is no credible evidence for other points of view, then users will find Dispute Finder annoying.
@@
 According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust.
-Their 2008 survey found that 33\% of registered democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says.
+Their 2008 survey found that 33\% of registered Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says.
 Pew also found that online sources are viewed with more skepticism than their print, broadcast, and cable counterparts.
@@
 
-Fact checking web sites and search engines work great when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed.
+Fact checking web sites and search engines work well when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed.
 The primary aim of Dispute Finder is to let you know when something you are reading is disputed.
@@
 Similarly, there is little point spending effort rebutting claims that nobody believes.
-For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true.
+For example there is reliable evidence opposing the claim that the moon is made of cheese, but few people believe this claim is true.
 What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.
@@
 
-Currently most of our claims are automatically mined Snopes and Politifact.
+Currently most of our claims are automatically mined from Snopes and Politifact.
 Both of these sites maintain well curated databases of disputed claims, together with information about them.
@@
 
-We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}).
+We also provide users means to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}).
 The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org.
@@
 
-The automatic import feeds allow Dispute Finder to bootstrap a large database of disputed claims without needing a large active user community and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.
+The automatic import bootstraps Dispute Finder with a large database of disputed claims without needing a large active user community, and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.
 
@@
 
-Given a web page, Dispute Finder needs to identify which snippets are making known disputed claims.
+To highlight disputed snippets on a web page, Dispute Finder needs to identify which snippets are making known disputed claims.
 Our current implementation runs a simple textual entailment algorithm inside the browser to look for sentences that entail known disputed claims.
@@
 \item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier.
-We used a simple baysian classifier with n-grams as features.
+We used a simple Baysian classifier with n-grams as features.
 This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.
-Once the classifier has been trained, the server uses it to automatically choose which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).
+Once the classifier has been trained, the server uses it to refine which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).
 
@@
 
-Explicit page marking has the highest accuracy, but the poorest coverage.
+Explicit page marking has the highest precision, but the poorest coverage.
 Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim.
@@
 
-Bulk page marking trades off some accuracy for better coverage.
+Bulk page marking trades off some precesion for better coverage.
 When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them.
@@
 
-Server side classification trades off more accuracy for more coverage.
+Server side classification trades off more precision for more coverage.
 The classifier can mark more pages than a user could ever mark manually, and can keep marking new pages as they appear, but it is inevitably less accurate than a human.
@@
 Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined.
-This is particularly important for news pages, which are frequently read only a few minutes after they have been written.
+This is particularly important for news pages, which are frequently read only a few minutes after they are posted.
 Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.
@@
 
-The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}.
+Detecting entailment between texts is a semantic analyss problem.
+Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}.
 Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
@@
 LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist.
-Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
+Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
 Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions.
@@
 The authors of MemeTracker observed that many ideas often flow around the web in the form of ``memes'' that are repeated on many web sites with relatively little variation.
+To the extent that this is true, it simplifies identifying snippets that repeat the idea.
 MemeTracker uses this to track the way an idea propagates across the web using a relatively simple algorithm.
@@
 
-When a user clicks on a highlighted snippet, Dispute Finder displays a popup interface with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read.
+When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read.
 In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}).
@@
 
-If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view.
-We could have omitted this feature and still had a useful system.
+We could have omitted this claim-information feature and still had a useful system.
 Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim.
@@
 
-Unfortunately, as Pew report~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust tend to be those that share the person's own point of view.
+Unfortunately, as Pew Research discovered~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view.
 It seems that ``without a point of view'' is a similar concept to ``without an accent''.
+Similarly, Manjou~\cite{Manjou2008} found that people tend to measure the reliablity of a source based on how well it fits with what they already believe to be true.
 As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa.

### 2009-10-30 papers/www_disputefinder/disputefinder.tex
Changes suggested by Tad

@@
 
-The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}.
+In recent years, we have seen the emergence of a new class of applications that help users recognize and make sense of online dispute.
+In this paper, we describe Dispute Finder, an application that alerts a user when information they read online is disputed by a source that they might trust.
+
+%The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}.
 If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
@@
 	\begin{center}
-	\includegraphics[width=8cm]{pictures/highlight_abortion.png}
+	\includegraphics[width=8.5cm]{pictures/highlight_abortion.png}
 	\caption{Dispute Finder highlights text snippets that make disputed claims.}
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
+	\includegraphics[width=7cm]{pictures/popup_abortion_shadow.png}
 	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
@@
 
-In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust.
+%In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust.
 Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in by exposing them to different points of view.
@@
 
-Dispute Finder consists of a server-side database, an API, and a Firefox browser extension.
-The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}).
-The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claim.
-The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims.
-The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.
+Dispute Finder consists of a server-side database and a Firefox browser extension.
+The database contains a set of known disputed claims that appear on the web.
+For each claim, the database contains references to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).
+The browser extension maintains its own local copy of the database, and runs a textual entailment algorithm on every sentence the user views to determine whether it is likely to be making a known disputed claim.
 
-In this paper, we describe the design of Dispute Finder, the trade-offs we encountered between different design choices, and our experiences testing Dispute Finder with users.
+\todo{Should we mention the API? Cut from this version as tangential}
+
+In this paper, we describe the design of Dispute Finder, the constituent problems that must be solved to make a tool like Dispute Finder work well, the trade-offs we encountered between different design choices, and our experiences testing Dispute Finder with users.
 
@@
 	\begin{center}
-	\includegraphics[width=8cm]{pictures/snippet_claim_article_fancy3.png}
+	\includegraphics[width=8.5cm]{pictures/snippet_claim_article_fancy3.png}
 	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
@@
 
-Dispute Finder has been influenced by previous work in many different fields, including sensemaking, web annotation, natural language processing, and information extraction.
-We discuss this work throughout the paper.
-
-\subsection{Challenges}
-
-During the design and implementation of Dispute Finder, we had to come up with solutions for several challenges:
-
-\begin{description}
-\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large and credible.
-If the database's coverage is too small then users will rarely see snippets highlighted.
-If a snippet is highlighted but there is no credible evidence for other points of view, then users will find Dispute Finder annoying.
-We currently crowd-source claims from users, and mine disputed claims from web sites such as Snopes and Politifact that already maintain lists of disputed claims.
-
-\item[How do we find disputed snippets?] Given a particular web page, how do we determine which phrases on that page are making known disputed claims and should be highlighted?
-There is a tradeoff between precision and recall.
-If we highlight a snippet that is not making a disputed claim then the user will be annoyed, but if we do not highlight a snippet that is making a disputed claim then Dispute Finding missed an opportunity to be useful.
-We currently run a textual entailment algorithm inside the browser extension that looks for phrases that look similar to a known disputed claim.
-
-\item[How do we highlight snippets?] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed.
-Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt.
-We currently use a browser extension that checks for disputed claims on every page the user browses, and offer an API that other web sites can use to mark disputed claims on content that they serve.
-
-\item[How should we explain a disputed claim?] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim.
-We currently use a simple list of articles arguing for and against the claim.
-
-\item[What do people want?] To be useful for users, Dispute Finder needs to serve a real need that users have.
-We used interviews, user studies, and a small survey to try to learn what users want and what users are likely to use.
-\end{description}
-
-In the rest of this paper, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.
-
 \subsection{Personas}
@@
 If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use.
-We designed Dispute Finder is designed to cater to two personas.
-Each persona was created from interviews we conducted with people who we believe fit into these categories.
+We used interviews to construct two personas, which model the two ways that we expect a user to use Dispute Finder.
 
@@
 For example a user may be skeptical when reading about topics that affect them (e.g.
-health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that don't affect them (e.g.
+health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that do not affect them (e.g.
 entertainment).
-
-\todo{Move our personals to a ``people'' section}
-
-\todo{Use interviews to get some actual observations here. These are just fillers.}
 
@@
 
-\section{Related Work}
+\section{Background and Related Work}
+
+There is ample evidence that at least some people are skeptical about the information they read and would like to know about alternative points of view that are supported by sources that they trust.
+This has lead to a growing set of tools that aim to help users deal with disputed and biased information.
+
+According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust.
+Their 2008 survey found that 33\% of Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says.
+Similarly, 51\% of Democrats regularly watch CNN, and yet only 35\% believe all or most of what CNN says.
+While these figures covered TV, rather than the web, Pew report that 48\% of web users people regularly follow search links to unfamiliar sources, and that users view online sources such as blogs with more skepticism that their print, broadcast, and cable counterparts.
+
+These findings were backed up by our interviews.
+Several participants told us that they regularly get information from sources that they do not entirely trust.
+A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search.
+For example they might read Michael Moore because he is entertaining, or read articles mailed to them by friends.
+
+\todo{Talk about people reading from a wide range of sources.}
+
+There is also evidence that a significant group of people are interested in checking information they read on the web.
+Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web.
+Snopes.com contains information about urban myths such as ``eskimos have many words for snow''.
+Factcheck.org and Politifact.com investigate claims about US politics.
+According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand.
+Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts and so the real number of users who regularly check facts online is likely to be much higher.
+
+To check our assumptions, we circulated a survey among members of a local debate club, who we anticipated would be a good match for our Skeptical Reader and Activist personals.
+Of the 23 people who responded, 91\% said that they sometimes or often check information they read on a trusted site (64\% often, 27\% sometimes) and 91\% said that they sometimes of often check information by searching for other web pages about the same topic (74\% often, 17\% sometimes).
+
+\todo{Talk about our survey}
+
+Fact checking web sites and search engines work well when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed.
+The primary aim of Dispute Finder is to let you know when something you are reading is disputed.
+
+Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services.
+Dispute Finder is designed to work together with fact checking sites.
+Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.
 
@@
 
-Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
+Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
 If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
@@
 On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
+These tools have a similar aim to Dispute Finder, but are limited to Wikipedia.
 
@@
 
-Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}.
+Dispute Finder also has some similarity to tagging tools~\cite{Marlow2006,Golder2006}.
 Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags.
 In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
-
-\section{Trusting Online Content}
-
-If a web user trusted all the content that they read, or were unconcerned that information they read might be wrong, then it is unlikely that they they would be much demand for a service such as Dispute Finder.
-Fortunately, there is ample evidence that at least some people are skeptical about the information they read and would like to know about alternative points of view that are supported by sources that they trust.
-
-According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust.
-Their 2008 survey found that 33\% of registered Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says.
-Pew also found that online sources are viewed with more skepticism than their print, broadcast, and cable counterparts.
-
-This result was backed up by our interviews.
-Several participants told us that they regularly get information from sources that they don't entirely trust.
-A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search.
-
-There is also evidence that a significant group of people are interested in checking information they read on the web.
-Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web.
-Snopes.com contains information about urban myths such as ``eskimos have many words for snow''.
-Factcheck.org and Politifact.com investigate claims about US politics.
-According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand.
-Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts.
-In our survey, 64\% of respondents said that they often check information they read on a trusted site and 74\% of respondents said that they often check information they read by searching for other web pages with information about that topic.
-
-Fact checking web sites and search engines work well when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed.
-The primary aim of Dispute Finder is to let you know when something you are reading is disputed.
-
-Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services.
-Dispute Finder is designed to work together with fact checking sites.
-Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.
 
@@
 
-\section{What is Disputed?}
+\section{Design}
+
+Creating a tool to manage disputed information requires designers to address a number of challenges, including:
+
+\begin{description}
+\item[Developing a corpus of disputed claims:] To be useful, the set of known disputed claims needs to be both large and credible.
+If the database's coverage is too small then users will rarely see snippets highlighted.
+If the database is not credible then users will often see snippets highlighted for which there is no credible evidence for other points of view.
+
+\item[Detecting these disputed claims on the web:] Given a particular web page, how do we determine which phrases on that page are making known disputed claims and should be highlighted?
+There is a trade-off between precision and recall.
+We do not want to highlight a snippet that is not making a disputed claim, but we do want to maximize the likelihood that we highlight a snippet that is making a disputed claim.
+
+\item[Highlighting disputed claims for users:] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed.
+Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt.
+We also want to avoid distracting the user unnecessarily, while also making sure that they do notice disputed claims that they would care about.
+
+\item[Providing tools that help users interpret disputed claims:] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim.
+We want to help a user understand both {\it who} holds other points of view and {\it why} other people hold different points of view.
+
+\item[Determining Trustworthy Sources:] What sources should we consider ``trustworthy'' in the sense that they opinions are worth presenting to the user, and we should inform the user when a trustworthy source disagrees with what they are reading.
+There is a trade-off between showing a user sources that they will trust, and showing them sources that will expose them to a new point of view.
+
+\end{description}
+
+These challenges are not unique to dispute finder. They apply to any tool that informs a user about disputed information and helps users interpret this disputed information.
+
+In the rest of this section, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.
+
+\subsection{Developing a Corpus}
 \label{sec:disputed}
@@
 Both of these sites maintain well curated databases of disputed claims, together with information about them.
-Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American Policitians.
+Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American politicians.
 In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g.
@@
 
-\section{Finding Snippets}
+\subsection{Detecting Disputed Claims}
 
@@
 	\begin{center}
-	\includegraphics[width=7cm]{pictures/nlp_client_server2.png}
+	\includegraphics[width=8cm]{pictures/nlp_client_server2.png}
 	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
@@
 	\begin{center}
-	\includegraphics[width=7cm]{pictures/paraphrases.png}
+	\includegraphics[width=8cm]{pictures/paraphrases.png}
 	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
@@
 \item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier.
-We used a simple Baysian classifier with n-grams as features.
+We used a simple Bayesian classifier with n-grams as features.
 This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.
@@
 
-Bulk page marking trades off some precesion for better coverage.
+Bulk page marking trades off some precision for better coverage.
 When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them.
@@
 
-Detecting entailment between texts is a semantic analyss problem.
+Detecting entailment between texts is a semantic analysis problem.
 Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}.
@@
 LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist.
-Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
+Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Bayesian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
 Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions.
@@
 
-\section{Explaining Disputed Claims}
+\subsection{Highlighting Disputed Claims}
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8cm]{pictures/highlight_bar.png}
+	\caption{Dispute Finder highlights text snippets that make disputed claims, and displays a notification bar to inform the user that they should look out for highlighted snippets.}
+	\label{highlight_bar}
+	\end{center}
+\end{figure}
+
+%Dispute Finder is designed to alert a user when information they read on a web page makes a claim that is disputed by a source they might trust. 
+%
+%
+%Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust.
+We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.
+
+The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed.
+It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).
+
+The notification bar alerts the user that they should look out for highlighted snippets.
+Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind.
+The notification bar also allows a user to step through the highlighted snippets on the page.
+
+The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims.
+This allows a user to ignore disputed claims that are made by text that the user is not interested in - such as user comments.
+The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it is not making.
+In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.
+
+Once a user is aware that a claim is disputed, there is little point telling them about the same disputed claim again in the future.
+We have not yet concluded whether it is better for Dispute Finder to automatically stop highlighting a claim once a user has viewed the claim, or whether it is better for a user to explicitly ask Dispute Finder to stop highlighting a claim.
+In our current implementation, a user can tell Dispute Finder to not highlight a claim again by setting the ``don't highlight this claim for me again'' checkbox in the popup interface (Figure~\ref{claimview}).
+Requiring a user to manually opt out of a claim requires more work from the user, but hiding already viewed claims can be confusing, since users do not normally expect viewing something to be a destructive operation.
+A compromise position is to highlight claims that have been seen before in a fainter color; similar to the way links are typically colored on web pages.
+
+\todo{Try using a fainter color}
+
+\todo{Text is wrong in the screenshot}
+
+Dispute Finder also provides an API that allows other sites to determine whether their content makes disputed claims.
+For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.
+
+\todo{Document API online}
+\todo{Change the highlight color to yellow? Auto-adjust highlight color based on background color?}
+\todo{Should we automatically adjust the highlight color, based on the background color of the page}
+\todo{Discuss previous work on highlighting here, rather than in related work?}
+
+\subsection{Helping Users Interpret Claims}
 
@@
 For each article, the interface shows a summary sentence that captures the core argument used by the article.
-A user can add any web page as a supporting article by browsing to the page, selectinguse as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
+A user can add any web page as a supporting article by browsing to the page, selecting ``use as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
 \end{description}
@@
 
-\section{Trustworthy Sources}
+\subsection{Determining Trustworthy Sources}
 
@@
 It seems that ``without a point of view'' is a similar concept to ``without an accent''.
-Similarly, Manjou~\cite{Manjou2008} found that people tend to measure the reliablity of a source based on how well it fits with what they already believe to be true.
+Similarly, Manjou~\cite{Manjou2008} found that people tend to measure the reliability of a source based on how well it fits with what they already believe to be true.
 As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa.
@@
 
-\section{Highlighting Snippets}
+\section{Evaluation}
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{pictures/highlight_bar.png}
-	\caption{Dispute Finder highlights text snippets that make disputed claims, and displays a notification bar to inform the user that they should look out for highlighted snippets.}
-	\label{highlight_bar}
-	\end{center}
-\end{figure}
-
-%Dispute Finder is designed to alert a user when information they read on a web page makes a claim that is disputed by a source they might trust. 
-%
-%
-%Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust.
-We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.
-
-The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed.
-It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).
-
-The notification bar alerts the user that they should look out for highlighted snippets.
-Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind.
-The notification bar also allows a user to step through the highlighted snippets on the page.
-
-The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims.
-This allows a user to ignore disputed claims that are made by text that the user isn't interested in - such as user comments.
-The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making.
-In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.
-
-Once a user is aware that a claim is disputed, there is little point telling them about the same disputed claim again in the future.
-We have not yet concluded whether it is better for Dispute Finder to automatically stop highlighting a claim once a user has viewed the claim, or whether it is better for a user to explicitly ask Dispute Finder to stop highlighting a claim.
-In our current implementation, a user can tell Dispute Finder to not highlight a claim again by setting the ``don't highlight this claim for me again'' checkbox in the popup interface (Figure~\ref{claimview}).
-Requiring a user to manually opt out of a claim requires more work from the user, but hiding already viewed claims can be confusing, since users do not normally expect viewing something to be a destructive operation.
-A compromise position is to highlight claims that have been seen before in a fainter color; similar to the way links are typically colored on web pages.
-
-\todo{Try using a fainter color}
-
-\todo{Text is wrong in the screenshot}
-
-Dispute Finder also provides an API that allows other sites to determine whether their content makes disputed claims.
-For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.
-
-\todo{Document API online}
-\todo{Change the highlight color to yellow? Auto-adjust highlight color based on background color?}
-\todo{Should we automatically adjust the highlight color, based on the background color of the page}
-\todo{Discuss previous work on highlighting here, rather than in related work?}
-
-\section{Learning from Users}
-
+We gathered information from users using user-studies, a survey, and a set of interviews.
 We performed three qualitative ``think aloud'' user studies.
@@
 The studies were not intended to validate the design of Dispute Finder as being correct.
+We also interviewed most of our user study participants, and five additional people.
+
+We found that most people were interested in having a tool like Dispute Finder, and were able to use Dispute Finder effectively as a Skeptical Reader.
+However we found that users were frustrated by the relatively low fraction of disputed claims that Dispute Finder currently highlights, and had some difficulty adding new claims themselves.
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/popup_graph_crop.png}
+	\includegraphics[width=8cm]{pictures/popup_graph_crop.png}
 	\caption{Argumentation graph interface for a disputed claim}
@@
 Not all users realized that one could click on a disputed claim to bring up more information.
-Several users complained about Dispute Finder highlighting snippets that weren't making the claim Dispute Finder indicated.
+Several users complained about Dispute Finder highlighting snippets that were not making the claim Dispute Finder indicated.
+
+Most users were frustrated by the relatively poor precision and recall that Dispute Finder has at present.
+Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder did not highlight anything.
+Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated.
+If Dispute Finder is to be adopted widely then we will need to significantly improve precision and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.
+
+Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them (e.g.
+health) or that they were expected to be knowledgeable about (e.g.
+something relating to their work), but were less interested in applying it to pages about topics that they were less interested in.
+For topics that did not affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''.
+Users read about some topics (e.g.
+celebrity gossip) ``for entertainment'' or ``to relax'' and so they were less interested in making sure they properly understood those topics.
 
@@
 They were then prompted to either select an existing claim or create a new one.
+
+\subsubsection{Claims}
 
@@
 
+Several users got confused by claims that referred to similar events at different points in time.
+For example, one participant in the first study marked one claim as opposing another claim when they were referring to similar incidents that occurred at different times.
+
+Several users created claims that had ambiguous meanings.
+One user entered a disputed claim about ``Wood'', meaning the guitarist ``Ronnie Wood'' of the Rolling Stones.
+Similar problems occurred with claims that were specific to a particular country, or a particular point in time.
+
+\subsubsection{The Article List}
+
 When adding sources that support or oppose a claim, a user would frequently mark the first paragraph of the article rather than seeking out the sentence that best summarized the argument that the article was using against the claim.
@@
 Several users wanted to mark up a table or image as the summary of an article, which is not currently supported.
+
+When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative.
+For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.
+
+Several users expressed an interest in being able to add a disputed claim without having to find opposing evidence.
+One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
+Users did however recognize that they would want to see opposing evidence as a reader.
+
+\subsubsection{The Argumentation Graph}
 
@@
 These findings are consistent with those of Isenmann and Reuter~\cite{Isenmann1997}.
-
-Several users got confused by claims that referred to similar events at different points in time.
-For example, one participant in the first study marked one claim as opposing another claim when they were referring to similar incidents that occurred at different times.
-
-When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative.
-For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.
-
-Several users expressed an interest in being able to add a disputed claim without having to find opposing evidence.
-One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
-Users did however recognize that they would want to see opposing evidence as a reader.
-
-Several users created claims that had ambiguous meanings.
-One user entered a disputed claim about ``Wood'', meaning the guitarist ``Ronnie Wood'' of the Rolling Stones.
-Similar problems occurred with claims that were specific to a particular country, or a particular point in time.
-
-Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them or that they were expected to be knowledgeable about, but were less interested about applying it to pages about other topics, that they were less interested in.
-For topics that didn't affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''.
-
-Most users were frustrated by the relatively poor accuracy and recall that Dispute Finder has at present.
-Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder didn't highlight anything.
-Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated.
-If Dispute Finder is to be adopted widely then we will need to significantly improve precision and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.
 

### 2009-10-30 papers/www_disputefinder/disputefinder.tex
Folded in changes suggested by Wes

@@
 The database contains a set of known disputed claims that appear on the web.
+A disputed claim is a statement about the world that some people disagree with.
+For example ``global warming is a hoax'', ``gun control will reduce crime'', ``eskimos have many words for snow'', or ``margarine is healthier than butter''.
+A claim can be stated in many ways.
+For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are paraphrases of the same claim.
 For each claim, the database contains references to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).
-The browser extension maintains its own local copy of the database, and runs a textual entailment algorithm on every sentence the user views to determine whether it is likely to be making a known disputed claim.
+
+The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to {\it entail} a claim.
+A snippet is a continuous region of text on a web page.
+A snippet is defined to entail a claim if a normal user reading that snippet would reasonably conclude that the author of the page believed the claim was true.
+For example ``the english have as many words for rain as the eskimos have for snow'' {\it entails} ``eskimos have many words for snow'', even though this claim is never stated explicitly.
 
@@
 
-These findings were backed up by our interviews.
+These findings were backed up by our interviews (Section~\ref{sec:interviews}).
 Several participants told us that they regularly get information from sources that they do not entirely trust.
@@
 
-Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic.
-Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion.
-Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
+Rather than allowing a user to directly express their own opinions about a topic, Dispute Finder instead requires a user who wants to promote a particular opinion to do so by linking to an article from a trusted source that argues for that opinion.
+Our interviews (Section~\ref{sec:interviews}) lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
 
-Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
+Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a particular page} while Dispute Finder attempts to allow a user to annotate a {\it general claim, everywhere it appears on the web, however it is worded}.
 If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
@@
 
-The intention behind these tools is that a user uses them to identify the source of information that is being used to motivate a conclusion.
-These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.
+These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim, or to automatically inform a user when other sources disagree with what they are reading.
 
@@
 
-\subsection{Detecting Disputed Claims}
+\subsection{Detecting Known Disputed Claims}
 
-To highlight disputed snippets on a web page, Dispute Finder needs to identify which snippets are making known disputed claims.
-Our current implementation runs a simple textual entailment algorithm inside the browser to look for sentences that entail known disputed claims.
+To highlight disputed snippets on a web page, Dispute Finder needs to be able to determine when a snippet entails the truth of a known disputed claim.
+This is complicated by the fact that a claim can be phrased many different ways, and a snippet does not need to explicitly state a claim in order to entail its truth.
+For example ``I prefer margarine to butter because it is healthier'' entails ``margarine is healthier than butter''.
+Our implementation maintains a local copy of our claim database inside the browser extension and runs a simple textual entailment algorithm inside the browser to look for sentences that appear to entail known disputed claims.
 
-We implemented and tested four different approaches:
+There is a trade-off between precision and recall.
+We want to maximize the likelihood that Dispute Finder will highlight a snippet if it is making a known disputed claim, while minimizing the likelihood that it will highlight a snippet that is not making a known disputed claim.
+
+We implemented and tested four different approaches that represent different points along this trade-off:
 
@@
 A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}).
-This is the implementation used by the currently released version of Dispute Finder.
+This is the implementation used by the released version of Dispute Finder.
 \end{description}
@@
 By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.
+
+\subsubsection{Textual Entailment}
 
@@
 \section{Evaluation}
+\label{sec:interviews}
 

### 2009-10-31 papers/www_disputefinder/disputefinder.tex
Did a polishing pass over the paper

@@
 We describe Dispute Finder, a browser extension that alerts a user when information they read online is disputed by a source that they might trust.
-Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that appear to entail claims in its database of known disputed claims.
-If a user clicks on a highlighted phrase then Dispute Finder shows them a summary of articles that support other points of view.
+Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that resemble known disputed claims.
+If a user clicks on a highlighted phrase then Dispute Finder shows them a list of articles that support other points of view.
 
-Dispute Finder builds its database of disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed.
-Dispute Finder identifies instances of disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of a subset of our claim database.
+Dispute Finder builds a database of known disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed.
+Dispute Finder identifies snippets that make known disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of the claim database.
 
@@
 
-In recent years, we have seen the emergence of a new class of applications that help users recognize and make sense of online dispute.
-In this paper, we describe Dispute Finder, an application that alerts a user when information they read online is disputed by a source that they might trust.
-
-%The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}.
+The web contains a huge amount of information, but some of this information is factually incorrect and some sites present only one side of a contentious issue~\cite{Herman2002}.
 If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
 Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.
+
+In recent years, we have seen the emergence of a new class of tools that help users recognize and make sense of disputed information on the web.
+In this paper, we describe Dispute Finder, a tool that alerts a user when a web page they are reading appears to be making a claim that is disputed by a source that they might trust.
 
@@
 When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}).
-If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward different points of view,  each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).
+If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward alternative points of view,  each of which is from a source we believe the user might trust (Figure~\ref{claimview}).
 
 Dispute Finder consists of a server-side database and a Firefox browser extension.
-The database contains a set of known disputed claims that appear on the web.
+The database contains a set of known disputed claims that frequently appear on the web.
 A disputed claim is a statement about the world that some people disagree with.
-For example ``global warming is a hoax'', ``gun control will reduce crime'', ``eskimos have many words for snow'', or ``margarine is healthier than butter''.
+For example ``global warming is a hoax'', ``gun control will reduce crime'', ``Eskimos have many words for snow'', or ``margarine is healthier than butter''.
 A claim can be stated in many ways.
-For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are paraphrases of the same claim.
-For each claim, the database contains references to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).
+For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are {\it paraphrases} of the same claim.
+For each claim, the database contains links to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).
 
@@
 A snippet is a continuous region of text on a web page.
-A snippet is defined to entail a claim if a normal user reading that snippet would reasonably conclude that the author of the page believed the claim was true.
-For example ``the english have as many words for rain as the eskimos have for snow'' {\it entails} ``eskimos have many words for snow'', even though this claim is never stated explicitly.
+A snippet is considered to {\it entail} a claim if a typical user reading that snippet would reasonably conclude that the author of the page believed the claim was true.
+For example ``the English have as many words for rain as the Eskimos have for snow'' {\it entails} ``Eskimos have many words for snow'', even though this claim is never stated explicitly.
 
@@
 
-If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use.
-We used interviews to construct two personas, which model the two ways that we expect a user to use Dispute Finder.
+If users are going to adopt Dispute Finder, it is important that it solves a real need.
+We used interviews to construct two personas which model the two ways that we expect a user to use Dispute Finder.
 
@@
 They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic.
-A user may behave like a skeptical reader for some topics and not others.
+A user will typically behave like a skeptical reader for some topics and not others.
 For example a user may be skeptical when reading about topics that affect them (e.g.
@@
 
-{\it Activists} care strongly about particular issues and are prepared to spend some time helping others know that something that they disagree with is disputed.
+{\it Activists} care strongly about particular issues and are prepared to spend some time informing others that something that they disagree with is disputed.
 They are the same kinds of people who join protest groups, write blogs, email news stories, or argue about topics online.
 They are motivated by a desire to influence others and to gain status by being seen to do so.
-A user is likely to be an activist on some issues, but not for others.
+A user is likely to be an activist on some issues, but not on others.
 An activist will often also be a skeptical reader.
@@
 Many users fall into neither of these two personas.
-If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then they are unlikely to be interested in Dispute Finder.
+If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then they are unlikely to be interested in a tool like Dispute Finder.
 
@@
 Similarly, 51\% of Democrats regularly watch CNN, and yet only 35\% believe all or most of what CNN says.
-While these figures covered TV, rather than the web, Pew report that 48\% of web users people regularly follow search links to unfamiliar sources, and that users view online sources such as blogs with more skepticism that their print, broadcast, and cable counterparts.
+While these figures are for TV News, rather than the web, Pew report that 48\% of web users people regularly follow search links to unfamiliar sources, and that users view online sources such as blogs with more skepticism that their print, broadcast, and cable counterparts.
 
@@
 A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search.
-For example they might read Michael Moore because he is entertaining, or read articles mailed to them by friends.
+For example they might read Michael Moore because he is entertaining, while having low opinions of his credibility, or they might read articles mailed to them by friends.
 
@@
 There is also evidence that a significant group of people are interested in checking information they read on the web.
-Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web.
-Snopes.com contains information about urban myths such as ``eskimos have many words for snow''.
-Factcheck.org and Politifact.com investigate claims about US politics.
-According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand.
-Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts and so the real number of users who regularly check facts online is likely to be much higher.
+Several popular web sites are designed primarily to help users check information they read elsewhere.
+For example Snopes.com contains information about urban myths such as ``eskimos have many words for snow'' and Factcheck.org and Politifact.com investigate claims made by American political figures.
+According to Quantcast.com, Snopes has around five million unique visitors per month.
 
-To check our assumptions, we circulated a survey among members of a local debate club, who we anticipated would be a good match for our Skeptical Reader and Activist personals.
-Of the 23 people who responded, 91\% said that they sometimes or often check information they read on a trusted site (64\% often, 27\% sometimes) and 91\% said that they sometimes of often check information by searching for other web pages about the same topic (74\% often, 17\% sometimes).
+To check these assumptions, we circulated a survey among members of a local debate club, who we anticipated would be a good match for our Skeptical Reader and Activist personals.
+Of the 23 people who responded, 91\% said that they sometimes or often check information they read on a trusted site (64\% often, 27\% sometimes) and 91\% said that they sometimes or often check information by searching for other web pages about the same topic (74\% often, 17\% sometimes).
 
@@
 
-Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services.
-Dispute Finder is designed to work together with fact checking sites.
-Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.
-
 Many other tools highlight disputed information on web pages.
@@
 
-Rather than allowing a user to directly express their own opinions about a topic, Dispute Finder instead requires a user who wants to promote a particular opinion to do so by linking to an article from a trusted source that argues for that opinion.
-Our interviews (Section~\ref{sec:interviews}) lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
+There are two key differences between Dispute Finder and these annotation tools: First, rather than allowing a user to express their own opinions about a topic, Dispute Finder instead requires a user who wants to promote a particular opinion to do so by linking to an article from a trusted source that argues for that opinion.
+Our interviews (Section~\ref{sec:interviews}) lead us to believe that most users would rather know that a trusted source disagrees with what is being written than that an unknown user disagrees.
 
-Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a particular page} while Dispute Finder attempts to allow a user to annotate a {\it general claim, everywhere it appears on the web, however it is worded}.
+The second key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a particular page} while Dispute Finder attempts to allow a user to annotate a {\it general claim, everywhere it appears on the web, however it is worded}.
 If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
 If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears.
-The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.
+The closest annotation system to Dispute Finder in this respect is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.
 
 Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users.
-TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph.
+TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that they extracted from them, and connecting these facts into a decision graph.
 ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
-Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.
+Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts extracted from it.
 Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''.
@@
 
-There are also several tools that find pages that put forward different points of view, rather than identifying disputed claims within a page.
+There are also several tools that find pages write about the same topic with different slants, rather than looking at the specific claims a page makes.
 News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
@@
 
-\item[Highlighting disputed claims for users:] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed.
-Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt.
-We also want to avoid distracting the user unnecessarily, while also making sure that they do notice disputed claims that they would care about.
+\item[Highlighting disputed claims for users:] If we are to alert a user when they read disputed information, we need to be able to tell what text they are reading, and we need a way to inform them that this information is disputed.
+Ideally, this method should apply to as much of the information the user reads as possible, and be easy for a user to adopt.
+We also want to avoid distracting the user unnecessarily, while also making sure that they notice disputed claims that they would care about.
 
-\item[Providing tools that help users interpret disputed claims:] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim.
+\item[Providing tools that help users interpret disputed claims:] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim and what other sources they should read.
 We want to help a user understand both {\it who} holds other points of view and {\it why} other people hold different points of view.
 
-\item[Determining Trustworthy Sources:] What sources should we consider ``trustworthy'' in the sense that they opinions are worth presenting to the user, and we should inform the user when a trustworthy source disagrees with what they are reading.
+\item[Determining Trustworthy Sources:] What sources should we consider ``trustworthy'' in the sense that their opinions are worth presenting to the user, and things that they disagree with should be highlighted as disputed.
 There is a trade-off between showing a user sources that they will trust, and showing them sources that will expose them to a new point of view.
-
 \end{description}
 
-These challenges are not unique to dispute finder. They apply to any tool that informs a user about disputed information and helps users interpret this disputed information.
+These challenges are not unique to dispute finder; indeed they apply to any tool that informs a user about disputed information and helps users interpret this disputed information.
 
-In the rest of this section, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.
+In the rest of this section, we discuss the various alternative solutions that we explored for each of these problems, and our experiences with the approaches that we implemented and tested.
 
@@
 
-Dispute Finder maintains a shared database of known disputed claims.
+Dispute Finder maintains a shared server-side database of known disputed claims.
 The browser extension highlights a text snippet if it believes that the snippet entails one of the claims in this database (Figure~\ref{snippet_claim_article}).
@@
 In some sense almost everything is disputed by someone on the web.
-There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless.
+There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would be so distracting as to be worthless.
 Similarly, there is little point spending effort rebutting claims that nobody believes.
@@
 
-We also provide users means to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}).
+One weakness of the automatic import approach is that the claims found on these sites are often phrased differently to the way they commonly appear on the web.
+For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''.
+In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be widely recogonsized.
+
+Dispute Finder also provides users means to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}).
 The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org.
@@
 When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.
+At the time of writing, users have added 557 claims, and 140 users have added at least one claim.
 
-The automatic import bootstraps Dispute Finder with a large database of disputed claims without needing a large active user community, and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.
+%The automatic import bootstraps Dispute Finder with a useful database of disputed claims without needing a large active user community, and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.
 
@@
 
-In future work, we hope to automatically find disputed claims on the web by looking for phrases like ``falsely claimed that X'' --- a similar techniques to that used by Hearst to find hyponyms~\cite{Hearst1992}.
+In future work, we hope to automatically find disputed claims on the web by looking for phrases like ``falsely claimed that X'' --- a similar techniques to that used by Hearst to find hyponyms~\cite{Hearst1992}, and then use context to help determine which phrases are likely to be making the same claim.
 
@@
 
-To highlight disputed snippets on a web page, Dispute Finder needs to be able to determine when a snippet entails the truth of a known disputed claim.
-This is complicated by the fact that a claim can be phrased many different ways, and a snippet does not need to explicitly state a claim in order to entail its truth.
+Dispute Finder highlights a snippet if it thinks it entails the truth of a known disputed claim.
+This is complicated by the fact that a claim can be phrased in many different ways, and a snippet does not need to explicitly state a claim in order to entail its truth.
 For example ``I prefer margarine to butter because it is healthier'' entails ``margarine is healthier than butter''.
@@
 We want to maximize the likelihood that Dispute Finder will highlight a snippet if it is making a known disputed claim, while minimizing the likelihood that it will highlight a snippet that is not making a known disputed claim.
-
 We implemented and tested four different approaches that represent different points along this trade-off:
@@
 	\includegraphics[width=6cm]{pictures/mark_disputed.png}
-	\caption{Explicit page marking: select the text that makes a disputed claim and click ``this is disputed'' from the context menu.}
+	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
 	\label{mark_disputed}
@@
 
+\label{sec:explicit_mark}
 \begin{description}
@@
 
-\item[Bulk page marking:] The user uses a search interface to rapidly gather a large number of snippets that contain similar phrases, and then marks them in bulk.
+\item[Bulk page marking:] The user uses a search interface to rapidly gather many snippets that contain similar phrases, and then selects those that they would like to mark (Figure~\ref{training}).
 The server uses Yahoo BOSS\footnote{http://developer.yahoo.com/search/boss} to search the web for snippets that resemble a paraphrase entered by the user.
-The user then selects all the snippets that they would like to mark (Figure~\ref{training}).
 
@@
 We used a simple Bayesian classifier with n-grams as features.
-This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.
-Once the classifier has been trained, the server uses it to refine which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).
+The classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.
+Once the classifier has been trained, the server uses it to refine which other results from Yahoo BOSS should be marked (Figure~\ref{training}).
 
@@
 We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page.
-This same problem that has hindered the adoption of numerous web page annotation tools.
+This same problem has hindered the adoption of numerous web page annotation tools.
 
@@
 This is particularly important for news pages, which are frequently read only a few minutes after they are posted.
-Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.
+Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and intranet sites.
 
@@
 By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.
+As our database grows bigger, it will of course become more challenging to maintain a local copy in the browser extension.
 
@@
 LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist.
-Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Bayesian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
+Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2001,Dinu2009,Bhagat2009}, and using Bayesian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
 Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions.
@@
 Other authors have used similar algorithms to find repeated information on the web.
-Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
+Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, and duplicate-detection is often used to clean up web searches~\cite{Theobald2008}.
 MemeTracker~\cite{Backstrom2009} looks for phrases shared by multiple news stories, accounting for minor variations, and uses this to track the way that news flows between traditional news sources and blogs.
@@
 The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed.
-It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).
+It highlights any disputed snippets in red, and it displays a notification bar (Figure~\ref{highlight_bar}).
 
 The notification bar alerts the user that they should look out for highlighted snippets.
-Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind.
+Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} particularly if the user is color blind.
 The notification bar also allows a user to step through the highlighted snippets on the page.
 
-The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims.
-This allows a user to ignore disputed claims that are made by text that the user is not interested in - such as user comments.
+The highlights show a user {\it which snippets} Dispute Finder believes are making disputed claims.
+A user can see whether the highlights are in the text that they are reading and ignore disputed snippets in text that they are not interested in - such as user comments.
 The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it is not making.
@@
 In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}).
-We also implemented and tested an interface that contained a user-editable argumentation graph, however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.
+We also implemented and tested an interface that contained a user-editable argumentation graph; however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.
 
@@
 \item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
-\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view - otherwise Dispute Finder would be annoying.
+\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view.
 By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
-\item[Filtering:] Although we have not implement this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
+\item[Filtering:] Although we have not implemented this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
 \end{description}
-
-Naturally, sources such as Wikipedia, Politifact, and Snopes are often used as sources of evidence for and against a claim --- indeed we currently import articles from Politifact and Snopes automatically.
 
@@
 \begin{description}
-\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
+\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph.
+This graph is inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
 Each claim is linked to claims that represent alternative points of view, and claims that support that point of view.
@@
 
-When using the article list approach, several different articles may be expressing essentially the same point of view and it may not be obvious that one of the articles is making a point that the user had not come across before.
+When using the article list approach, several different articles may be making essentially the same argument and it may not be obvious that one of the articles is making a point that the user had not come across before.
 The argumentation graph allows the user to easily see what the range of different opinions is, and quickly see if there is an argument that they have not encountered before.
@@
 In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users.
-There were two problems here: firstly, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; secondly, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}.
+There were two problems here: first, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; second, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}.
 This result is consistent with previous studies~\cite{Isenmann1997}.
@@
 
-In the current version of Dispute Finder, an article can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable.
+When showing articles to a user, it is important that these be from sources that the user would be likely to trust.
+In the current version of Dispute Finder, a user can add any web page as a source, but users are requested to restrict themselves to pages that meet the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable.
 Good sources of articles include newspapers, universities, respected organizations, and Wikipedia itself.
-Users can vote on whether they think a particular article is useful, and this voting determines the order in which articles are listed.
-A user can also request that an article be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable articles.
-Users with moderator privileges review requests for deletion and delete claims and articles that do not meet requirements.
+A user can vote on whether they think a particular article is useful, and this voting determines the order in which articles are listed.
+A user can also request that an article be deleted they believe the source does not meet credibility requirements, or if it is not relevant to the claim.
+These requests are forwarded to moderator users who have the power to delete links to articles.
 
-Unfortunately, as Pew Research discovered~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view.
+Unfortunately, as Pew Research discovered~\cite{PewResearch2008} when looking at TV news, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view.
 It seems that ``without a point of view'' is a similar concept to ``without an accent''.
-Similarly, Manjou~\cite{Manjou2008} found that people tend to measure the reliability of a source based on how well it fits with what they already believe to be true.
+Similarly, Manjou~\cite{Manjou2008} reports that people tend to measure the credibility of a source based on how well it fits with what they already believe to be true.
 As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa.
@@
 If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own world-view then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
-On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right.
-If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously.
+On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment but may still be right.
+If we pay no attention to what sources the user trusts, or what sources are generally regarded as credible, then we may waste time trying to persuade users using sources that they would not take seriously.
 We do not yet claim to know a good solution for this problem, but we believe it is an interesting area for further research.
@@
 \label{sec:interviews}
+\label{user-studies}
 
-We gathered information from users using user-studies, a survey, and a set of interviews.
-We performed three qualitative ``think aloud'' user studies.
+We gathered information from users using user-studies and a set of interviews.
+We performed three qualitative ``think aloud'' user studies and interviewed most of our user study participants, along with six additional people.
 The aim of these studies was to inform the iterative design of the Dispute Finder tool.
 The studies were not intended to validate the design of Dispute Finder as being correct.
-We also interviewed most of our user study participants, and five additional people.
 
@@
 For the first two studies, we recruited participants using Craigslist.
-We posted a message asking people to tell us how they used the web to form and promote their opinions, and used their responses to select people who we thought might fit our ``skeptical reader'' and ``activist'' personas.
+We posted a message asking people to tell us how they used the web to form and promote their opinions and used their responses to select people who we thought might fit our ``skeptical reader'' and ``activist'' personas.
 For the final study, we instead used people from our lab who we thought would be a good fit for our personas.
@@
 Each batch of users was shown a different iteration of the Dispute Finder design.
-The first two batches used versions in which users marked snippets explicitly and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view (Figure~\ref{popup_graph}).
-The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim.
+The first two batches used versions in which users marked snippets explicitly and in which the popup window explaining a claim showed an argumentation graph describing the structure of the different alternative points of view (Figure~\ref{popup_graph}).
+The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of articles that support or oppose the claim.
 We present the findings of the three user studies together.
@@
 Most users were able to use Dispute Finder competently as a skeptical reader (browsing information about disputed claims) but found it harder to act competently as an activist (adding new disputed claims).
-Several participants wanted to see Dispute Finder work for them as a skeptical reader before dedicating time to adding and curating new claims ("I want to see it work before I add stuff").
+Several participants wanted to see Dispute Finder work for them as a skeptical reader before dedicating time to adding and curating new claims (``I want to see it work before I add stuff'').
 
-When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed.
-Not all users realized that one could click on a disputed claim to bring up more information.
+When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought Dispute Finder was saying the sentences were wrong, rather than merely disputed.
+Not all users realized that one could click on a highlighted snippet to bring up more information.
 Several users complained about Dispute Finder highlighting snippets that were not making the claim Dispute Finder indicated.
@@
 For topics that did not affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''.
-Users read about some topics (e.g.
+Users said they read about some topics (e.g.
 celebrity gossip) ``for entertainment'' or ``to relax'' and so they were less interested in making sure they properly understood those topics.
@@
 
-When marking a snippet on a particular page, users often did not appreciate that a claim should apply to more than one snippet.
+When using explicit page marking (Section~\ref{sec:explicit_mark}) to mark a snippet on a particular page, many users often did not appreciate that a claim should apply to more than one snippet.
 Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to ``enter the text again''.
@@
 When adding sources that support or oppose a claim, a user would frequently mark the first paragraph of the article rather than seeking out the sentence that best summarized the argument that the article was using against the claim.
-In some cases the first paragraph is indeed the right text to select, since the first paragraph is typically a summary of the core argument made by the articles.
+In some cases the first paragraph is indeed the right text to select, since the first paragraph is typically a summary of the core argument made by the articles; however there was often a better choice available.
 Several users wanted to mark up a table or image as the summary of an article, which is not currently supported.
 
-When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative.
+When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was phrased negatively.
 For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.
@@
 
-In the first two studies, the popup interface for a claim showed an argumentation graph.
-This graph connected the graphs in our database using ``supports'' or ``opposes'' links, and allowed each claim to also be associated with supporting articles.
+In the first two studies, the popup interface for a claim showed an argumentation graph (Figure~\ref{popup_graph}).
+This graph connected the claims in our database using ``supports'' or ``opposes'' links, and allowed each claim to also be associated with supporting articles.
 When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected.
@@
 
-We have introduced the idea of creating an Open Hypermedia system that automatically highlight snippets on the web that are disputed by sources you might trust.
-We have explored several different design options, tested multiple variants on users, and reported insights from this testing.
+We have introduced the idea of Dispute Finder, an Open Hypermedia tool that informs a user when a web page they are reading is making a claim that is disputed by a source they might trust.
+We have discussed the key challenges that one must address in order to make a system like this work, proposed several solutions to these challenges, and discussed our experiences with those solutions that we have implemented and tested with users.
 
@@
 
-At the time of writing 11,682 people have installed and tried out Dispute Finder, 2,297 are active daily users, 140 have added new claims to our database, 149 have added articles, and our database contains 2,146 disputed claims.
+At the time of writing 11,729 people have installed and tried out Dispute Finder, 2,297 are active daily users, 140 have added new claims to our database, 149 have added articles, and our database contains 2,609 disputed claims.
 

### 2010-01-15 papers/www_disputefinder/unused.tex

@@
+%\section{Related Work}
+%
+%Dispute Finder builds on prior work in many different areas.
+The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}.
+Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information.
+Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.
+Many people have developed textual entailment algorithms~\cite{entail?} that determine when one sentence implies the trust of another, or contradiction detection algorithms that determine when one sentence contradicts another.
+%
+%\todo{Add more references from the NewsCube paper}
+
+%
+%\subsection{Finding Disputed Information on the Web}
+%
+%An important part of Dispute Finder is identifying what claims are disputed. Several other authors looked at disputed information on the web.
+%
+%Kittur et al~\cite{Kittur2007} developed an algorithm that can determine whether a wikipedia page is about a disputed topic.
+Kittur and Chi~\cite{Kittur2009} broke down the disputed pages by catagory and found that People, Society, and Religion were the categories with the most disputed pages.
+%
+%\subsection{Extracting Information from the Web}
+%
+%Information extration tools such as TextRunner~\cite{Etzioni2008} 
+%Read The Web
+%
+%TextRunner~\cite{Etzioni2008} 
+%
+%\todo{cite lots of Etzioni stuff}
+%
+%\cite{SnowBall}
+%\cite{Read The Web}
+%\cite{Information Extraction from Wikipedia}
+%\cite{KnowItAll}
+%\cite{TextRunner}
+%
+%\todo{Online Dispute Resolution}
+%
+%\todo{Cite Kittur et al}
+
+\subsection{Augmented Web Navigation}
+
+%\subsection{Persuasive Technology}
+
+% \subsection{Semantic Web}
+% 
+% Nobody is going to mark up their own web page as being wrong.
+
+% \subsection{To discuss in the body}
+% 
+% Paraphrases~\cite{Chklovski2005}. Suggested formal paraphrases~\cite{Blythe2004}.
+% Importance of Lurkers~\cite{Takahashi2003}
+% Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.
+
 Unlike most prior forms
@@
 % SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.
+
+\subsection{Textual Entailment}
+\label{related:entailment}
+
+The textual entailment problem is a common problems in natural language processing.
+In the 3-way variant of the PASCAL Recognizing Textual Entailment (RTE) Challenge\footnote{http://pascallin.ecs.soton.ac.uk/Challenges/RTE/}, an algorithm is given two sentences T and H and asked to return one of three answers: T {\it entails} H, T {\it contradicts} H, or the truth of H cannot be determined from T.
+
+Our client side textual entailment algorith approach.
+
+Several of the core challenges in Dispute Finder are forms of the textual entailment problem.
+Finding disputed claims is a special case of finding a sentence on the web that is {\it contradicted} by a sentence on a trusted page.
+Finding a snippet that makes a disputed claim is a special case of finding a snippet that {\it entails} a disputed claim.
+
+One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it contradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical.
+Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims.
+Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.
+
+Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims.
+The algorithm we use is a simple variant of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}.
+LLM simply reduces a sentence to a bag of lemmatized words, removes stop-words, checks for negations, and then looks at what the overlap is between the words in the two phrases.
+Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.
+
+\todo{Implement word weighting and word similarity?}
+
+%Following the taxonomy used by Jijkoun and Rijke~\cite{Jijkoun2006} our algorithm is M-sim-imp, that is, we assign entailment scores based soley on word overl
+%
+%The algorithm we use is a simple Local Lexical Matching (LLM) algorithm.
+
+\todo{Talk about Glickman et all 2005 and MT system of Bayer et al 2005}
+\todo{Cite Web Based probabalistic textual entailment}
+\todo{Cite MITRE's submission to the EU PASCAL RTE Challenge}
+
+\todo{Talk a lot about how people do textual entailment now}
+\todo{Do human-guided approach that works well? Talk more about human guided task.}

### 2010-01-26 papers/wicow_claimfinder/claimfinder.tex
Started work on WICOW paper. Added files that should have been committed earlier. Cleaned up .gitignore.

--- 2009-10-30 papers/www_disputefinder/disputefinder.tex
@@
 
+% Mark up a point that we want to flesh out into more text
+\newcommand{\x}[1]{{\color{blue} #1}\\}
+
 \begin{document}
@@
 
-\title{Highlighting Disputed Claims on the Web}
+\title{What is disputed on the web?}
 
@@
 \author{
-	Author list to be determined
-}
-
-\author{
+\alignauthor Dan Byler\\
+       \affaddr{School of Information}\\
+       \affaddr{University of California at Berkeley}\\
+       \affaddr{Berkeley, CA, USA}\\
+       \email{dan@ischool.berkeley.edu}
 \alignauthor Rob Ennals\\
@@
        \email{robert.ennals@intel.com}
-\alignauthor Beth Trushkowsky\\
-       \affaddr{Computer Science Division}\\
-       \affaddr{University of California at Berkeley}\\
-       \affaddr{Berkeley, CA, USA}\\
-       \email{trush@cs.berkeley.edu}
 \alignauthor John Mark Agosta\\
@@
 
-\additionalauthors{Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}
+\additionalauthors{Barbara Rosario, Intel Labs Santa Clara, \\\texttt{[barbara.rosario@intel.com]}; Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\\\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}
 
@@
 \abstract
+[Final author list is to be determined]
 
-We describe Dispute Finder, a browser extension that alerts a user when information they read online is disputed by a source that they might trust.
-Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that appear to entail claims in its database of known disputed claims.
-If a user clicks on a highlighted phrase then Dispute Finder shows them a summary of articles that support other points of view.
-
-Dispute Finder builds its database of disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed.
-Dispute Finder identifies instances of disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of a subset of our claim database.
-
-In this paper, we explain the design of Dispute Finder, and the trade-offs between the various design decisions that we explored.
-
-\category{H.4.m}{Information Systems}{Miscellaneous}
-\category{H.4.2}{Information Systems}{Decision Support}
-\category{H.5.2}{User Interfaces}{Graphical User Interfaces}
+%\subsection{Categories and Subject Descriptors}
+%\todo{Categories, terms, and keywords need updating}
+\category{H.3.1}{INFORMATION STORAGE AND RETRIEVAL}{Content Analysis and Indexing}
+\category{I.2.7}{ARTIFICIAL INTELLIGENCE}{Natural Language Processing}
 
@@
 
-\todo{update screenshots}
-\todo{should this be spun as about news, or information in general}
-\todo{need to talk more about what we know about people}
-
-% The last few years have seen the rapid decline of printed newspapers and rapid rise of the web as a source of news~\cite{pew-news?}.
-
-In recent years, we have seen the emergence of a new class of applications that help users recognize and make sense of online dispute.
-In this paper, we describe Dispute Finder, an application that alerts a user when information they read online is disputed by a source that they might trust.
-
-%The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}.
-If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
-Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8.5cm]{pictures/highlight_abortion.png}
-	\caption{Dispute Finder highlights text snippets that make disputed claims.}
-	\label{highlight}
-	\end{center}
-\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=7cm]{pictures/popup_abortion_shadow.png}
-	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
-	\label{claimview}
-	\end{center}
-\end{figure}
-\todo{Popup interface should contain a ``don't mark this'' button}
-
-\todo{More screenshots/graphs/visual information}
-
-\todo{word this better}\todo{update all screenshots}
-
-%In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust.
-Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in by exposing them to different points of view.
-
-A user can install Dispute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser.
-When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}).
-If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward different points of view,  each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).
-
-Dispute Finder consists of a server-side database and a Firefox browser extension.
-The database contains a set of known disputed claims that appear on the web.
-For each claim, the database contains references to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).
-The browser extension maintains its own local copy of the database, and runs a textual entailment algorithm on every sentence the user views to determine whether it is likely to be making a known disputed claim.
-
-\todo{Should we mention the API? Cut from this version as tangential}
-
-In this paper, we describe the design of Dispute Finder, the constituent problems that must be solved to make a tool like Dispute Finder work well, the trade-offs we encountered between different design choices, and our experiences testing Dispute Finder with users.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8.5cm]{pictures/snippet_claim_article_fancy3.png}
-	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
-	\label{snippet_claim_article}
-	\end{center}
-\end{figure}
-
-\subsection{Personas}
-
-If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use.
-We used interviews to construct two personas, which model the two ways that we expect a user to use Dispute Finder.
-
-{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust.
-They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic.
-A user may behave like a skeptical reader for some topics and not others.
-For example a user may be skeptical when reading about topics that affect them (e.g.
-health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that do not affect them (e.g.
-entertainment).
-
-{\it Activists} care strongly about particular issues and are prepared to spend some time helping others know that something that they disagree with is disputed.
-They are the same kinds of people who join protest groups, write blogs, email news stories, or argue about topics online.
-They are motivated by a desire to influence others and to gain status by being seen to do so.
-A user is likely to be an activist on some issues, but not for others.
-An activist will often also be a skeptical reader.
-
-Many users fall into neither of these two personas.
-If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then they are unlikely to be interested in Dispute Finder.
+\x{Information credibility is important.}
+\x{People are increasingly relying on the web for information.}
+\x{People read a wider range of sources that before, many of which they do not know whether to trust.}
 
@@
 
-There is ample evidence that at least some people are skeptical about the information they read and would like to know about alternative points of view that are supported by sources that they trust.
-This has lead to a growing set of tools that aim to help users deal with disputed and biased information.
+\subsection{What is credible?}
 
-According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust.
-Their 2008 survey found that 33\% of Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says.
-Similarly, 51\% of Democrats regularly watch CNN, and yet only 35\% believe all or most of what CNN says.
-While these figures covered TV, rather than the web, Pew report that 48\% of web users people regularly follow search links to unfamiliar sources, and that users view online sources such as blogs with more skepticism that their print, broadcast, and cable counterparts.
+\subsection{The distributional hypothesis}
 
-These findings were backed up by our interviews.
-Several participants told us that they regularly get information from sources that they do not entirely trust.
-A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search.
-For example they might read Michael Moore because he is entertaining, or read articles mailed to them by friends.
+\subsection{Contradiction Detection}
 
-\todo{Talk about people reading from a wide range of sources.}
+\subsection{Sentiment Analysis}
 
-There is also evidence that a significant group of people are interested in checking information they read on the web.
-Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web.
-Snopes.com contains information about urban myths such as ``eskimos have many words for snow''.
-Factcheck.org and Politifact.com investigate claims about US politics.
-According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand.
-Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts and so the real number of users who regularly check facts online is likely to be much higher.
+\subsection{Crowdsourcing disputed claims}
 
-To check our assumptions, we circulated a survey among members of a local debate club, who we anticipated would be a good match for our Skeptical Reader and Activist personals.
-Of the 23 people who responded, 91\% said that they sometimes or often check information they read on a trusted site (64\% often, 27\% sometimes) and 91\% said that they sometimes of often check information by searching for other web pages about the same topic (74\% often, 17\% sometimes).
+\x{Dispute Finder. Wikipedia. WikiTrust}
 
-\todo{Talk about our survey}
+\subsection{Curated Databases of Disputed Claims}
 
-Fact checking web sites and search engines work well when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed.
-The primary aim of Dispute Finder is to let you know when something you are reading is disputed.
+\x{Dispute Finder.}
 
-Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services.
-Dispute Finder is designed to work together with fact checking sites.
-Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.
+\section{Finding Disputed Claims}
 
-Many other tools highlight disputed information on web pages.
-ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content.
-Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips.
-There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features, and most of which could be used to annotate disputed content.
+\subsection{Disputed Templates}
 
-Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic.
-Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion.
-Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.
+\x{Include a table with templates we use and templates we generated}
 
-Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web.
-If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page.
-If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears.
-The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.
+\subsection{Selecting Good Statements}
 
-Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users.
-TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph.
-ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document.
-Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.
-Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''.
-An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.
+\subsection{Generating New Templates}
 
-The intention behind these tools is that a user uses them to identify the source of information that is being used to motivate a conclusion.
-These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.
+\x{Following the distributional hypothesis.}
+\x{Search for known disputed claims and find most frequent words that surround them.}
 
-There are also several tools that find pages that put forward different points of view, rather than identifying disputed claims within a page.
-News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
-The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue.
-Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias.
-Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking.
-Newstrust allows users to rate news articles for quality and objectivity.
+\section{Using Disputed Claims}
 
-On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
-These tools have a similar aim to Dispute Finder, but are limited to Wikipedia.
+\x{We are building lots of applications that will use this data set.}
+\x{Dispute Finder highlights disputed claims on the web.}
+\x{Tell people when audio they hear is disputed.}
+\x{Tell people when a source you trust disagrees with others.}
+\x{Tell me when a source I read in the past is now disputed.}
+\x{Tell me how contentious a topic is.}
+\x{Let me explore what is disputed about a particular topic.}
+\x{Tell me when something new is disputed about a topic I care about.}
+\x{Examine the zeitgeist of disputes.}
+\x{Tell me about things that are disputed by the kind of sites I trust.}
+\x{We also want to make this data set available to others.}
 
-More generally, Dispute Finder is an example of an Open Hypermedia system~\cite{Bouvin2000,Wiil1996}.
-Like other Open Hypermedia systems, Dispute Finder lays an additional link structure over an existing hypertext document.
-In the case of Dispute Finder, the links are from disputed claims to information about those claims.
+\section{Analysing the Data}
 
-Dispute Finder also has some similarity to tagging tools~\cite{Marlow2006,Golder2006}.
-Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags.
-In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
+\subsection{Data Quality}
 
-\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
-\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
-\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}
-\todo{Should we explicitly list what we think are our key contributions?}
+\x{Look at a random sample of the data and say how clean it is.}
+\x{Evaluate the quality of the claims that we extracted.}
+\x{Evaluate the quality of the clusters that we created.}
+\x{Evaluate the quality of the different individual templates - which ones have the highest quality claims.}
 
-\section{Design}
+\subsection{Trends over time}
 
-Creating a tool to manage disputed information requires designers to address a number of challenges, including:
+\x{Look at what noun phrases were most disputed at particular years.}
+\x{Look at what noun phrases were most disputed on particular days.}
 
-\begin{description}
-\item[Developing a corpus of disputed claims:] To be useful, the set of known disputed claims needs to be both large and credible.
-If the database's coverage is too small then users will rarely see snippets highlighted.
-If the database is not credible then users will often see snippets highlighted for which there is no credible evidence for other points of view.
+\section{Conclusions}
 
-\item[Detecting these disputed claims on the web:] Given a particular web page, how do we determine which phrases on that page are making known disputed claims and should be highlighted?
-There is a trade-off between precision and recall.
-We do not want to highlight a snippet that is not making a disputed claim, but we do want to maximize the likelihood that we highlight a snippet that is making a disputed claim.
-
-\item[Highlighting disputed claims for users:] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed.
-Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt.
-We also want to avoid distracting the user unnecessarily, while also making sure that they do notice disputed claims that they would care about.
-
-\item[Providing tools that help users interpret disputed claims:] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim.
-We want to help a user understand both {\it who} holds other points of view and {\it why} other people hold different points of view.
-
-\item[Determining Trustworthy Sources:] What sources should we consider ``trustworthy'' in the sense that they opinions are worth presenting to the user, and we should inform the user when a trustworthy source disagrees with what they are reading.
-There is a trade-off between showing a user sources that they will trust, and showing them sources that will expose them to a new point of view.
-
-\end{description}
-
-These challenges are not unique to dispute finder. They apply to any tool that informs a user about disputed information and helps users interpret this disputed information.
-
-In the rest of this section, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.
-
-\subsection{Developing a Corpus}
-\label{sec:disputed}
-
-Dispute Finder maintains a shared database of known disputed claims.
-The browser extension highlights a text snippet if it believes that the snippet entails one of the claims in this database (Figure~\ref{snippet_claim_article}).
-Claims can either be added directly by users (Figure~\ref{add_claim}) or mined from web sites such as Snopes and Politifact that already maintain well curated databases of disputed claims,
-
-This database should not contain contain everything that has ever been disputed by anyone.
-In some sense almost everything is disputed by someone on the web.
-There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless.
-Similarly, there is little point spending effort rebutting claims that nobody believes.
-For example there is reliable evidence opposing the claim that the moon is made of cheese, but few people believe this claim is true.
-What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{pictures/add_claim_list.png}
-	\caption{A user can use this interface to add a new disputed claim manually.}
-	\label{add_claim}
-	\end{center}
-\end{figure}
-
-Currently most of our claims are automatically mined from Snopes and Politifact.
-Both of these sites maintain well curated databases of disputed claims, together with information about them.
-Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American politicians.
-In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g.
-medical claims) and to provide an API to allow any site to provide a well-structured feed that we can use.
-At the time of writing, Dispute Finder has imported 1,457 claims from Snopes and 595 claims from Politifact.
-
-We also provide users means to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}).
-The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org.
-It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim.
-When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.
-
-The automatic import bootstraps Dispute Finder with a large database of disputed claims without needing a large active user community, and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.
-
-An alternative approach would be to use Contradiction Detection~\cite{Ritter} to find frequently repeated statements that appear to contradict statements from trusted sources.
-Unfortunately at the time of writing, Contradiction Detection does not seem to be robust enough for us to use it for this purpose.
-
-In future work, we hope to automatically find disputed claims on the web by looking for phrases like ``falsely claimed that X'' --- a similar techniques to that used by Hearst to find hyponyms~\cite{Hearst1992}.
-
-\todo{Say how many disputed claims}
-\todo{talk about duplicates}
-\todo{Actually import the Politifact data}
-
-\subsection{Detecting Disputed Claims}
-
-To highlight disputed snippets on a web page, Dispute Finder needs to identify which snippets are making known disputed claims.
-Our current implementation runs a simple textual entailment algorithm inside the browser to look for sentences that entail known disputed claims.
-
-We implemented and tested four different approaches:
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{pictures/mark_disputed.png}
-	\caption{Explicit page marking: select the text that makes a disputed claim and click ``this is disputed'' from the context menu.}
-	\label{mark_disputed}
-	\end{center}
-\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=7cm]{pictures/training2.png}
-	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
-	\label{training}
-	\end{center}
-\end{figure}
-
-\begin{figure}[t]
-	\begin{center}
-	\includegraphics[width=8cm]{pictures/nlp_client_server2.png}
-	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
-	\label{nlp_client_server}
-	\end{center}
-\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{pictures/paraphrases.png}
-	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
-	\label{paraphrases}
-	\end{center}
-\end{figure}
-
-\begin{description}
-\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting ``mark as disputed'' from a context menu (Figure~\ref{mark_disputed}).
-
-\item[Bulk page marking:] The user uses a search interface to rapidly gather a large number of snippets that contain similar phrases, and then marks them in bulk.
-The server uses Yahoo BOSS\footnote{http://developer.yahoo.com/search/boss} to search the web for snippets that resemble a paraphrase entered by the user.
-The user then selects all the snippets that they would like to mark (Figure~\ref{training}).
-
-\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier.
-We used a simple Bayesian classifier with n-grams as features.
-This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.
-Once the classifier has been trained, the server uses it to refine which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).
-
-%We have only partially implemented this approach.
-\todo{Should we say that we didn't completely finish this version?}
-
-\todo{Has anyone done something like this before.}
-\todo{We only partially implemented this approach}
-
-\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browses, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}).
-A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}).
-This is the implementation used by the currently released version of Dispute Finder.
-\end{description}
-
-Explicit page marking has the highest precision, but the poorest coverage.
-Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim.
-However the manual effort required per page makes it difficult for this approach to scale.
-We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page.
-This same problem that has hindered the adoption of numerous web page annotation tools.
-
-Bulk page marking trades off some precision for better coverage.
-When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them.
-Since they are reading the snippet out of context, they are more likely to mark a phrase incorrectly.
-
-Server side classification trades off more precision for more coverage.
-The classifier can mark more pages than a user could ever mark manually, and can keep marking new pages as they appear, but it is inevitably less accurate than a human.
-
-Client side entailment gets the most coverage.
-Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined.
-This is particularly important for news pages, which are frequently read only a few minutes after they are posted.
-Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.
-
-A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing.
-The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be practical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy.
-By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.
-
-Detecting entailment between texts is a semantic analysis problem.
-Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}.
-Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
-If the claim contains a negation word (e.g.
-not, never, can't) then so must the matching sentence.
-To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims.
-The hot terms are selected such that every claim contains at least one hot term.
-If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.
-
-LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist.
-Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Bayesian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.
-Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions.
-Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.
-
-While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
-We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.
-
-\todo{Mention that we could add the +ve and -ve n-grams to the client code? Actually do this?}
-
-\todo{Discuss how and why this is simpler than the server-side classification method}
-\todo{Explain how we avoid downloading the entire database}
-
-\todo{Should we have a version where the interface merely suggests n-grams that should be used by the classifier}
-\todo{Can we present all these systems without giving detailed stats about how they compare?}
-\todo{Add support for a user to enter 'anti-phrases' when a snippet is wrongly highlighted}
-\todo{Add support for a user to enter a paraphrase that will match the snippet they are looking at}
-\todo{Do a load more people in a final user-study round. Try to get it up to 8.}
-\todo{Explain how our algorithm relates to existing NLP work - due to unusual domain}
-
-Other authors have used similar algorithms to find repeated information on the web.
-Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}.
-MemeTracker~\cite{Backstrom2009} looks for phrases shared by multiple news stories, accounting for minor variations, and uses this to track the way that news flows between traditional news sources and blogs.
-
-The authors of MemeTracker observed that many ideas often flow around the web in the form of ``memes'' that are repeated on many web sites with relatively little variation.
-To the extent that this is true, it simplifies identifying snippets that repeat the idea.
-MemeTracker uses this to track the way an idea propagates across the web using a relatively simple algorithm.
-We have found that the precision and recall of our client-side textual entailment algorithm varies hugely depending on how meme-like a claim is.
-Some claims (particularly those derived from quotes) are widely repeated almost-verbatim, and can be detected relatively easily.
-However many other claims are rarely stated explicitly in a single sentence or with the same choice of words, making them much harder to detect with a simple algorithm.
-
-\todo{Give an example of a good meme}
-
-\todo{Talk about what dispute finder does, and how it differs - maybe by moving this into the main system section}
-\todo{Cite plagarism detection}
-\todo{Talk about how our algorithm looks for key terms used in disputed claims}
-\todo{Talk about how our first pass NLP algo is rather like }
-
-\subsection{Highlighting Disputed Claims}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{pictures/highlight_bar.png}
-	\caption{Dispute Finder highlights text snippets that make disputed claims, and displays a notification bar to inform the user that they should look out for highlighted snippets.}
-	\label{highlight_bar}
-	\end{center}
-\end{figure}
-
-%Dispute Finder is designed to alert a user when information they read on a web page makes a claim that is disputed by a source they might trust. 
-%
-%
-%Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust.
-We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.
-
-The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed.
-It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).
-
-The notification bar alerts the user that they should look out for highlighted snippets.
-Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind.
-The notification bar also allows a user to step through the highlighted snippets on the page.
-
-The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims.
-This allows a user to ignore disputed claims that are made by text that the user is not interested in - such as user comments.
-The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it is not making.
-In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.
-
-Once a user is aware that a claim is disputed, there is little point telling them about the same disputed claim again in the future.
-We have not yet concluded whether it is better for Dispute Finder to automatically stop highlighting a claim once a user has viewed the claim, or whether it is better for a user to explicitly ask Dispute Finder to stop highlighting a claim.
-In our current implementation, a user can tell Dispute Finder to not highlight a claim again by setting the ``don't highlight this claim for me again'' checkbox in the popup interface (Figure~\ref{claimview}).
-Requiring a user to manually opt out of a claim requires more work from the user, but hiding already viewed claims can be confusing, since users do not normally expect viewing something to be a destructive operation.
-A compromise position is to highlight claims that have been seen before in a fainter color; similar to the way links are typically colored on web pages.
-
-\todo{Try using a fainter color}
-
-\todo{Text is wrong in the screenshot}
-
-Dispute Finder also provides an API that allows other sites to determine whether their content makes disputed claims.
-For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.
-
-\todo{Document API online}
-\todo{Change the highlight color to yellow? Auto-adjust highlight color based on background color?}
-\todo{Should we automatically adjust the highlight color, based on the background color of the page}
-\todo{Discuss previous work on highlighting here, rather than in related work?}
-
-\subsection{Helping Users Interpret Claims}
-
-When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read.
-In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}).
-We also implemented and tested an interface that contained a user-editable argumentation graph, however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.
-
-We could have omitted this claim-information feature and still had a useful system.
-Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim.
-There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:
-
-\begin{description}
-\item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
-\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view - otherwise Dispute Finder would be annoying.
-By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
-\item[Filtering:] Although we have not implement this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
-\end{description}
-
-Naturally, sources such as Wikipedia, Politifact, and Snopes are often used as sources of evidence for and against a claim --- indeed we currently import articles from Politifact and Snopes automatically.
-
-We prototyped and tested two different ways of showing a user alternative points of view to the disputed claim they are looking at:
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
-	\caption{Article List interface for a disputed claim}
-	\label{article_list}
-	\end{center}
-\end{figure}
-
-\begin{description}
-\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
-Each claim is linked to claims that represent alternative points of view, and claims that support that point of view.
-Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})
-
-\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}).
-For each article, the interface shows a summary sentence that captures the core argument used by the article.
-A user can add any web page as a supporting article by browsing to the page, selecting ``use as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
-\end{description}
-
-The argumentation graph makes it easier to see {\it why} a claim is disputed, while the article lists make it easier to see {\it who} supports or opposes the claim.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{pictures/mark_evidence.png}
-	\caption{To add an article, select some summary text, and click ``use as evidence'' from the context menu.}
-	\label{add_article}
-	\end{center}
-\end{figure}
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
-	\caption{Choose how to connect an article with a claim.}
-	\label{article_choose}
-	\end{center}
-\end{figure}
-
-\todo{Call them supporting pages? Naming is a mess right now.}
-
-When using the article list approach, several different articles may be expressing essentially the same point of view and it may not be obvious that one of the articles is making a point that the user had not come across before.
-The argumentation graph allows the user to easily see what the range of different opinions is, and quickly see if there is an argument that they have not encountered before.
-
-A significant weakness of the argumentation graph approach is that a good argumentation graph takes significantly more effort to build than a simple list of articles.
-In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users.
-There were two problems here: firstly, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; secondly, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}.
-This result is consistent with previous studies~\cite{Isenmann1997}.
-
-Another point in favor of using a simple list of sources is that most of the users we talked to seemed to be more interested in {\it who} disputed a claim, rather than what their argument was.
-For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with.
-Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they preferred to read whichever article seemed to be most credible, rather than browsing an argumentation graph.
-
-It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and what arguments were being put forward.
-
-\subsection{Determining Trustworthy Sources}
-
-In the current version of Dispute Finder, an article can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable.
-Good sources of articles include newspapers, universities, respected organizations, and Wikipedia itself.
-Users can vote on whether they think a particular article is useful, and this voting determines the order in which articles are listed.
-A user can also request that an article be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable articles.
-Users with moderator privileges review requests for deletion and delete claims and articles that do not meet requirements.
-
-Unfortunately, as Pew Research discovered~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view.
-It seems that ``without a point of view'' is a similar concept to ``without an accent''.
-Similarly, Manjou~\cite{Manjou2008} found that people tend to measure the reliability of a source based on how well it fits with what they already believe to be true.
-As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa.
-Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments.
-Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.
-
-It may thus be better to learn what sources a particular user is likely to believe are reliable, and then adjust both what sources Dispute Finder shows to the user, and what claims are highlighted, based on this.
-
-There is a difficult trade-off here.
-If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own world-view then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against.
-On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right.
-If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously.
-We do not yet claim to know a good solution for this problem, but we believe it is an interesting area for further research.
-
-\todo{Cite Pew Research study saying people like to read news that supports their own point of view, but many others like neutral sources. http://people-press.org/report/?pageid=1353}
-
-Other researchers have looked at ways to determine what sources a user will trust. 
-BJ Fogg et al~\cite{Fogg2003} found that the most important factor was whether a web site had a professional-looking design.
-Gill and Arts~\cite{Gil2006} identified on a different set of factors, including topic (a medical site may not be trusted for advice on car repair), popularity (does everyone else use this) and authority.
-
-\section{Evaluation}
-
-We gathered information from users using user-studies, a survey, and a set of interviews.
-We performed three qualitative ``think aloud'' user studies.
-The aim of these studies was to inform the iterative design of the Dispute Finder tool.
-The studies were not intended to validate the design of Dispute Finder as being correct.
-We also interviewed most of our user study participants, and five additional people.
-
-We found that most people were interested in having a tool like Dispute Finder, and were able to use Dispute Finder effectively as a Skeptical Reader.
-However we found that users were frustrated by the relatively low fraction of disputed claims that Dispute Finder currently highlights, and had some difficulty adding new claims themselves.
-
-\subsection{Procedure}
-
-For the first two studies, we recruited participants using Craigslist.
-We posted a message asking people to tell us how they used the web to form and promote their opinions, and used their responses to select people who we thought might fit our ``skeptical reader'' and ``activist'' personas.
-For the final study, we instead used people from our lab who we thought would be a good fit for our personas.
-The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had six participants participants (all male).
-
-Each batch of users was shown a different iteration of the Dispute Finder design.
-The first two batches used versions in which users marked snippets explicitly and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view (Figure~\ref{popup_graph}).
-The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim.
-We present the findings of the three user studies together.
-Where a comment refers to particular version we make this clear.
-
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8cm]{pictures/popup_graph_crop.png}
-	\caption{Argumentation graph interface for a disputed claim}
-	\label{popup_graph}
-	\end{center}
-\end{figure}
-
-Study sessions took approximately forty five minutes.
-Participants were seated at a workstation with the Firefox browser augmented with the Dispute Finder extension.
-They were asked to view pages that had highlighted claims on them, and to attempt to add new disputed claims to our database.
-
-We also conducted interviews with most of our user study participants, and five additional people, asking them how they use the web to form and promote their opinions.
-
-\todo{Need to finish the third wave of user studies}
-
-\subsection{Findings}
-
-Responses were generally positive. Most of the participants expressed an interest in using the tool ``when it is more mature'' with some keen to use it in its current state.
-
-\todo{Tye: say how many were keen to use the tool.}
-
-Most participants said that they would want to use Dispute Finder to tell them when information they read was disputed (skeptical reader).
-One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.
-A smaller number said they would be likely to enter claims they disagreed with (activist).
-One participant who was a political blogger was eager to mark things he thought were lies.
-
-Most users were able to use Dispute Finder competently as a skeptical reader (browsing information about disputed claims) but found it harder to act competently as an activist (adding new disputed claims).
-Several participants wanted to see Dispute Finder work for them as a skeptical reader before dedicating time to adding and curating new claims ("I want to see it work before I add stuff").
-
-When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed.
-Not all users realized that one could click on a disputed claim to bring up more information.
-Several users complained about Dispute Finder highlighting snippets that were not making the claim Dispute Finder indicated.
-
-Most users were frustrated by the relatively poor precision and recall that Dispute Finder has at present.
-Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder did not highlight anything.
-Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated.
-If Dispute Finder is to be adopted widely then we will need to significantly improve precision and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.
-
-Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them (e.g.
-health) or that they were expected to be knowledgeable about (e.g.
-something relating to their work), but were less interested in applying it to pages about topics that they were less interested in.
-For topics that did not affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''.
-Users read about some topics (e.g.
-celebrity gossip) ``for entertainment'' or ``to relax'' and so they were less interested in making sure they properly understood those topics.
-
-%In the first study, a user could mark a snippet by 
-%
-%In the interface used in the first two studies, a user could mark a snippet by selecting it, right clicking on it, and clicking ``mark as disputed''.
-They were then prompted to either select an existing claim or create a new one.
-
-\subsubsection{Claims}
-
-When marking a snippet on a particular page, users often did not appreciate that a claim should apply to more than one snippet.
-Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to ``enter the text again''.
-Similarly, several users got confused when a snippet made two different disputed claims.
-The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as ``Global warming will cause X and Y''.
-
-Conversely, when adding a claim to the Dispute Finder web site, users would often enter claims that are not disputed anywhere on the web or enter paraphrases that do not resemble the wording used on any web site.
-The challenge of how to help users come up with claims that occur on many web sites is one that we have not yet solved.
-
-Several users expressed confusion about how specific a claim they created should be.
-For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information?
-In order to make a good judgment, one needs to know the range of similar claims that are being made by other web sites, and what claims there is good evidence against.
-If one makes the claim too specific then one will be able to find less web pages that make it, but if one makes the claim too general then it might be harder to find solid evidence against it.
-
-Several users got confused by claims that referred to similar events at different points in time.
-For example, one participant in the first study marked one claim as opposing another claim when they were referring to similar incidents that occurred at different times.
-
-Several users created claims that had ambiguous meanings.
-One user entered a disputed claim about ``Wood'', meaning the guitarist ``Ronnie Wood'' of the Rolling Stones.
-Similar problems occurred with claims that were specific to a particular country, or a particular point in time.
-
-\subsubsection{The Article List}
-
-When adding sources that support or oppose a claim, a user would frequently mark the first paragraph of the article rather than seeking out the sentence that best summarized the argument that the article was using against the claim.
-In some cases the first paragraph is indeed the right text to select, since the first paragraph is typically a summary of the core argument made by the articles.
-Several users wanted to mark up a table or image as the summary of an article, which is not currently supported.
-
-When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative.
-For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.
-
-Several users expressed an interest in being able to add a disputed claim without having to find opposing evidence.
-One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.
-Users did however recognize that they would want to see opposing evidence as a reader.
-
-\subsubsection{The Argumentation Graph}
-
-In the first two studies, the popup interface for a claim showed an argumentation graph.
-This graph connected the graphs in our database using ``supports'' or ``opposes'' links, and allowed each claim to also be associated with supporting articles.
-When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected.
-One user said ``I can see myself getting addicted to this'', and another said ``it's very intuitive''.
-
-Users seemed to have difficulty creating such graph structures however.
-Several users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim.
-For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing problems''.
-Users correctly realized that the claims were related, but were not sure how best to connect them.
-Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship.
-For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''.
-These findings are consistent with those of Isenmann and Reuter~\cite{Isenmann1997}.
-
-\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple ``supports"/``opposes'' graph.}
-
-\todo{Come up with terminology for marking an evidence snippet, and agree on evidence vs source vs article}
-\todo{Talk about how the early versions conflated evidence and snippets - and whether it makes sense to distinguish between them}
-\todo{Screenshot of the claim graph interface}
-
-\section{Conclusions and Future Work}
-
-We have introduced the idea of creating an Open Hypermedia system that automatically highlight snippets on the web that are disputed by sources you might trust.
-We have explored several different design options, tested multiple variants on users, and reported insights from this testing.
-
-As we discuss in this paper, our system requires multiple components to work in concert.
-Performing the tasks associated with these components well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users.
-We do however believe that Dispute Finder attacks an interesting problem that, if solved well, could significantly improve the utility of the web.
-
-At the time of writing 11,682 people have installed and tried out Dispute Finder, 2,297 are active daily users, 140 have added new claims to our database, 149 have added articles, and our database contains 2,146 disputed claims.
-
-An experimental preview version of Dispute Finder is available at 
-\url{http://disputefinder.org}
-
-\todo{Add count of disputed claims}
+\x{We can use the web as a corpus to determine what people think is disputed.}
 
@@
 
-\todo{Sort out bad references}
 \bibliography{refs}

### 2010-01-26 papers/wicow_claimfinder/claimfinder.tex
Python noun extraction. Added a table of claim phrases to the paper

@@
 
+Not everything on the Web is accurate or unbiased. One way to determine that information on the web should not be trusted is if a trustworthy source elsewhere on the web is explicitly disagreeing
+
+We describe a method for the automatic acquisition of a database of
+
+We describe a method for automatically aquiring a collection of claims that
+
 %\subsection{Categories and Subject Descriptors}
@@
 
+\begin{figure}[tb]
+  \begin{tabular}{|ll|}
+    \hline
+    {\bf Google Count} & {\bf Template}\\ 
+    \hline
+    \multicolumn{2}{|c|}{\it Something that could be challenged}\\
+    163,000,000 & believe that \\
+    206,000,000 & think that \\
+    49,500,000 & idea that \\
+    33,600,000 & claim that \\
+    \hline
+    \multicolumn{2}{|c|}{\it Something others believe}\\
+    120,000,000 & the belief that \\
+    49,000,000 & who believe that \\
+    50,500,000 & who think that \\
+    10,100,000 & believing that \\
+    9,430,000 & claiming that \\
+    \hline
+    \multicolumn{2}{|c|}{\it Something false}\\
+    9,960,000 & into believing that \\
+    15,600,000 & the misconception that \\
+    13,000,000 & the delusion that \\
+    12,400,000 & the myth that \\
+    7,190,000 & the mistaken belief that \\
+    4,950,000 & the fallacy that \\
+    3,720,000 & the lie that \\
+    3,600,000 & the false belief that \\
+    2,140,000 & the deception that \\
+    1,760,000 & the misunderstanding that \\
+    148,000 & false claim that \\
+    1,090,000 & false claim is that \\
+    1,630,000 & mistakenly believe that \\
+    3,700,000 & mistaken belief that \\
+    530,000 & the absurd idea that \\
+    1,290,000 & the hoax that \\
+    3,440,000 & the deceit that \\
+    681,000 & falsely claimed that \\
+    103,000 & falsely claiming that \\
+    373,000 & erroneously believe that \\
+    140,000 & erroneous belief that \\
+    334,000 & the fabrication that \\
+    72,600 & falsely claim that \\
+    152,000 & bogus claim that \\
+    65,300 & urban myth that \\
+    654,000 & urban legend that \\
+    224,000 & the fantasy that \\
+    171,000 & incorrectly claim that \\
+    249,000 & incorrectly claimed that \\
+    232,000 & incorrectly believe that \\
+    98,900 & stupidly believe that \\
+    429,000 & falsely believe that \\
+    376,000 & wrongly believe that \\
+    189,000 & falsely suggests that \\
+    280,000 & falsely claims that \\
+    59,500 & falsely stated that \\
+    698,000 & absurdity of the claim that \\
+    136,000 & no longer believe that \\
+    659,000 & no longer think that \\
+    \hline
+  \end{tabular}
+
+\end{figure}
+
+\x{Some prefixes suggest that some disagree, without saying that they do. E.g. ``people who believe that''}
+
 \x{Include a table with templates we use and templates we generated}
@@
 \subsection{Selecting Good Statements}
+
+\x{Remove anything containing stuff like 'if'}
+\x{Disallow possesives like its/his etc unless a noun has come first}
+\x{Strip HTML tags}
 
@@
 
+\x{Named entity recognition}
+
 \x{Look at what noun phrases were most disputed at particular years.}

### 2010-01-26 papers/wicow_claimfinder/relatedwork.tex
Split related work out into a separate file to make it easier to edit independently

\subsection{What is credible?}

\subsection{The distributional hypothesis}

\subsection{Contradiction Detection}

\subsection{Sentiment Analysis}

\subsection{Crowdsourcing disputed claims}

\x{Dispute Finder. Wikipedia. WikiTrust}

\subsection{Curated Databases of Disputed Claims}

\x{Dispute Finder.}

### 2010-01-27 papers/wicow_claimfinder/relatedwork.tex

@@
 
-\subsection{The distributional hypothesis}
+%\subsection{The distributional hypothesis}
 
-\subsection{Contradiction Detection}
+\subsection{Natural Language Processing for Claim Mining}
 
-\subsection{Sentiment Analysis}
+The automatic analysis of text falls into the field of natural language processing (NLP) and the problems and methods described here draw from a variety of sub-areas within the NLP literature.
+The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate candidate claims  is inspired by \cite{hearst92} and is an instance of template inference (aka pattern matching) that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and \cite{etzioni05} for information extraction).
+{\bf XX DESCRIBE SIMILARITIES AND DIFFENRENCES}.
+In Section~\ref{sec:XXX} we describe a clustering approach for {\bf XX}.
+Clustering in text processing is used for a variety  of tasks; clustering at the {\em word} level is used for smoothing for statistical language models, at the {\em document} level is most commonly used for finding and organizing documents around  general “themes”—such as for the Google News).
+Clustering is used when labeled data is not available; most methods can be classified as hard vs.
+soft clustering, flat vs.
+hierarchical clustering and they vary depending on the similarity measure and merging method used.
+In this paper {\bf XX}.
+This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, textual entailment and contradiction detection.
+Sentiment analysis aims to determine the attitude (usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}.
+Textual entailment is the task of deciding, given two text fragments, whether the meaning of one text can be inferred from the other text (add references).
+Disputed claims can be seen as contradictions, contradictions occur when information found in two different texts is incompatible\cite{harabagiu}.
+Here {\bf XX}.
+
+%\subsection{Contradiction Detection}
+
+%\subsection{Sentiment Analysis}
 

### 2010-01-27 papers/wicow_claimfinder/relatedwork.tex

@@
 
-The automatic analysis of text falls into the field of natural language processing (NLP) and the problems and methods described here draw from a variety of sub-areas within the NLP literature.
-The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate candidate claims  is inspired by \cite{hearst92} and is an instance of template inference (aka pattern matching) that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and \cite{etzioni05} for information extraction).
-{\bf XX DESCRIBE SIMILARITIES AND DIFFENRENCES}.
+The automatic analysis of text falls into the field of natural language processing (NLP) 
+and the problems and methods described here draw from a variety of sub-areas within the NLP literature. 
+The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate 
+candidate claims  is inspired by \cite{hearst92} and is an instance of template inference (aka pattern matching) 
+that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and 
+\cite{etzioni05} for information extraction). {\bf XX DESCRIBE SIMILARITIES AND DIFFENRENCES}.
+
 In Section~\ref{sec:XXX} we describe a clustering approach for {\bf XX}. 
-Clustering in text processing is used for a variety  of tasks; clustering at the {\em word} level is used for smoothing for statistical language models, at the {\em document} level is most commonly used for finding and organizing documents around  general “themes”—such as for the Google News).
+Clustering in text processing is used for a variety  of tasks; clustering at the {\em word} level 
+is used for smoothing for statistical language models, at the {\em document} level is most commonly 
+used for finding and organizing documents around  general “themes”—such as for the Google News). 
 Clustering is used when labeled data is not available; most methods can be classified as hard vs. 
-soft clustering, flat vs.
-hierarchical clustering and they vary depending on the similarity measure and merging method used.
-In this paper {\bf XX}.
-This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, textual entailment and contradiction detection.
-Sentiment analysis aims to determine the attitude (usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}.
-Textual entailment is the task of deciding, given two text fragments, whether the meaning of one text can be inferred from the other text (add references).
-Disputed claims can be seen as contradictions, contradictions occur when information found in two different texts is incompatible\cite{harabagiu}.
-Here {\bf XX}.
+soft clustering, flat vs. hierarchical clustering and they vary depending on the similarity measure 
+and merging method used. In this paper {\bf XX}.
+
+This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, 
+textual entailment and contradiction detection. Sentiment analysis aims to determine the attitude 
+(usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}. 
+Textual entailment is the task of deciding, given two text fragments, whether the meaning of one 
+text can be inferred from the other text (add references). Disputed claims can be seen as 
+contradictions, contradictions occur when information found in two different texts is 
+incompatible\cite{harabagiu}. Here {\bf XX}.
 

### 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
Split related work out into a separate file to make it easier to edit independently
Author list not determined

--- 2010-01-26 papers/wicow_claimfinder/claimfinder.tex
@@
-%\documentclass{article}
-\documentclass{www2010-submission}
+\documentclass{acm_proc_article-sp}
 \usepackage{times}
-%\usepackage{uist}
 \usepackage{url}
@@
 \usepackage{color}
-%
-%\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
-%\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
-%\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
-%\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}
-
 \newcommand{\want}[1]{}
-\newcommand{\todo}[1]{}
 \newcommand{\idea}[1]{}
@@
 \newcommand{\x}[1]{{\color{blue} #1}\\}
+
+% Mark up some work that we need to do in order for this paper to be telling the truth
+\newcommand{\todo}[1]{{\color{red} #1}\\}
+
+\newcommand{\maybe}[1]{}
 
@@
 \author{
-\alignauthor Dan Byler\\
-       \affaddr{School of Information}\\
-       \affaddr{University of California at Berkeley}\\
-       \affaddr{Berkeley, CA, USA}\\
-       \email{dan@ischool.berkeley.edu}
 \alignauthor Rob Ennals\\
@@
        \email{robert.ennals@intel.com}
+\alignauthor Dan Byler\\
+       \affaddr{School of Information}\\
+       \affaddr{University of California at Berkeley}\\
+       \affaddr{Berkeley, CA, USA}\\
+       \email{trush@cs.berkeley.edu}
 \alignauthor John Mark Agosta\\
@@
        \email{john.m.agosta@intel.com}
+\and
+\alignauthor Barbara Rosario\\
+       \affaddr{Intel Labs Santa Clara}\\
+       \affaddr{2200 Mission College Blvd}\\
+       \affaddr{Santa Clara, CA, USA}\\
+       \email{john.m.agosta@intel.com}
+\alignauthor Tye Rattenbury\\
+       \affaddr{Intel Principles and Practices}\\
+       \affaddr{2200 Mission College Blvd}\\
+       \affaddr{Santa Clara, CA, USA}\\
+       \email{tye.l.rattenbury@intel.com}
 }
@@
 %\sloppy
-
-\additionalauthors{Barbara Rosario, Intel Labs Santa Clara, \\\texttt{[barbara.rosario@intel.com]}; Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\\\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}
 
@@
 \abstract
-[Final author list is to be determined]
+
+We describe a method for the automatic acquisition of a corpus of disputed claims from the web.
+We consider a claim to be disputed if a document on the web suggests that this claim is wrong and that other people on the web are suggesting that it is true.
+
+Our tool extracts disputed claims by searching the web for templates such as ``falsely claimed that X'' or ``the myth that X'', and then analysing the parsed sentence structure to identify claims that seem to have the correct form.
+Given a set of known disputed claims, we can infer further templates by searching for other contexts in which known disputed claims appear.
+
+We believe that our corpus of disputed claims could be useful for a wide range of applications related to information credibility on the web.
 
@@
 
+The web contains a vast number of documents written by a vast number of people.
+In many cases, these people disagree with each other, and the documents they write contain conflicting information.
+If a user is to extract reliable information from a the web, then it is useful for them to be able to determine when different documents disagree about a topic.
+
+In this paper we describe a method for automatically aquiring a corpus of disputed claims from the web.
+By {\it disputed claim} we mean a statement about the world that some sources believe are true, and other sources believe is false.
+Our intention is that this corpus of disputed claims will be used as input to tools that help users know what information they encounter in their lives is potentially unreliable.
+
+We identify disputed claims by searching the web for patterns that indicate that a particular phrase is a disputed claim.
+One such pattern is ``the misconception that $S$'', an instance of which would be ``the minconception that {\it the moon is made of cheese}''.
+If we find a document that contains this text then that suggests that the author of the document believes both that the statement ``{\it the moon is made of cheese}'' is false, and that there are other authors who claim that ``{\it the moon is made of cheese}'' is true.
+
+We have found many other patterns that have this property, some of which we list in Figure~\ref{templates}.
+Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{hearst-hyponyms} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.
+
+\todo{TODO: we need to use template mining to get a more complete list of the templates that are good.}
+
+Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear.
+This is an instance of the distributional hypothesis~\cite{distributional-hypothesis}, that theorises that if a pattern occurs with similar phrases filling it's slots (it is distributionally similar) then it has a similar meaning.
+
+We believe that this corpus will be useful for many purposes.
+We are using it as part of our Dispute Finder~\cite{www-disputefinder} project, to automatically highlight phrases on web pages that are disputed by other sources.
+We are also exploring other applications of this corpus, including visualization tools that let users see what is disputed about topics they are interested in, or what has been disputed at particular times.
+
+We are making our corpus publically available so that other researchers who believe it would be useful for them can download it.
+We plan to continue to update our corpus as new pages are added to the web, and to develop tool that allow people to query it in useful ways.
+
+We believe that our corpus is the first large-scale corpus of disputed claims.
+
+\todo{Need to put our data online somewhere so that others can download it.}
+
+In this paper, we describe in more detail the way that we built this corpus, we explain ways that we think this corpus could be used, and we describe some features that we found in our data.
+
+\x{Include graph showing process by which we import claims.}
+
+\section{Background and Related Work}
+
 \x{Information credibility is important.}
@@
 
-\section{Background and Related Work}
+Information credibility on the web is becoming increasingly important.
+In the past people typically obtained information from a relatively small set of sources such as books, TV channels, and radio stations.
+Each of these sources had a known reputation, and had publishing barriers and quality control to make sure that all information they provided met the standards expected from that source.
+The web is very different.
+A user has access to a vast number of different sources, but a user will know the reputation of only a small subset of these.
+Moreover, the internet has little in the way of publishing barriers or quality control.
+If users are going to extract trustworthy information from the web then they need to either restrict themselves to a small set of sources that they trust, or use some kind of mechanism to determine the credibility of the information that they read.
 
-\subsection{What is credible?}
+\x{Cite Pew study on this? Cite other people talking about misinformation}.
 
-\subsection{The distributional hypothesis}
+Given a document that contains information that may or may not be trustworthy, there are several ways that a reader can determine whether they should trust the information.
+They can check the reputation of the source; they can check whether it looks like a reliable document; or they can check whether the information in the document is consistent with information available from other sources.
 
-\subsection{Contradiction Detection}
+To check the reputation of a source, a user can use a web site such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources.
+Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy.
+Alternatively, a user can simply use a search engine such as Google to look for information about the source.
+These tools can be very useful; however trustworthy sources sometimes publish unreliable information.
+For example a source may have been misled by an unreliable source they were using themselves.
+Moreover, a user may have a document from a source that is not known to be reliable, and still wish to know if the information itself is trustworthy.
 
-\subsection{Sentiment Analysis}
+Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content.
+For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by looking at the edit history.
+Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether there are videos.
+Fogg et al~\cite{Fogg} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing.
+Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.
 
-\subsection{Crowdsourcing disputed claims}
+In our research, we are following the third approach.
+We aim to inform users when information that they encounter is disputed by another source.
+We have built an extension to the Firefox web browser called Dispute Finder~\cite{www-disputefinder} that informs users when a web page that they are reading makes a claim that it knows to be disputed.
+For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
+In the currently released version of Dispute Finder, it builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims; however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
 
-\x{Dispute Finder. Wikipedia. WikiTrust}
+Our primary motivation for automatically acquiring a large corpus of disputed claims is to use this corpus to enable tools like Dispute Finder to automatically inform users when they encounter information that this corpus says is disputed.
 
-\subsection{Curated Databases of Disputed Claims}
+\todo{Want some kind of numerical estimate of how many disputed claims we have. Maybe measure this by pair of unique nouns and verbs. Noun + verb or noun + noun = disputed claim?}
 
-\x{Dispute Finder.}
+\maybe{Want to apply wikify to get nouns, and then use Chi-style catagory rules to find out what catagories are disputed on the web?}
+
+\input{relatedwork.tex}
 
@@
 
+We distinguish between a {\it contradiction} and a {\it dispute}.
+A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true.
+For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
+A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong.
+For example the text ``only idiots think that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''.
+A {\it contradiction} is logical, while a {\it dispute} is social.
+It is possible to have a contradiction without a dispute and a dispute without a contradiction.
+While the concepts are different, they are obviously closely related.
+Usually if someone disputes a claim it is because they believe an alternative claim that contradicts it.
+
+We distinguish between a claim that is {\it contradicted} and a claim that is {\it disputed}. 
+A claim in a document is {\it contradicted} if there is another document somewhere else that makes a contradictory claim. A claim is {\it disputed} if another document explicitly says
+
+A claim is {\it disputed} if another document
+
+For example if one document says ``The moon is made of cheese'' and another document says ``The moon is made of rock'' then then the first statement is contradicted by the first.
+
+We consider a claim to be disputed if at least one source suggests that the claim is true, and at least one source suggests that the claim is not true.
+
+One way to find disputed claims is to compare statements on different web pages and look for contradictions.
+AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a {\it functional} verb maps the same subject to multiple different objects and the difference cannot be resolved using a semantic knowledge.
+
+Harabagiu et al\cite{Harabagiu2006}
+
+\x{A contradiction is not the same as a dispute. A contradiction is where the information is different. A dispute is where the different parties BELIEVE the disagree. }
+
+The RTE-3 Recognizing Textual entailment task
+
+This turned out to be a hard problem;
+
+scanning 117 million web pages yielded only 110 genuine contradictions.
+
+\todo{We might want to try using TextRunner ourselves.}
+
+and then infers a contradiction when
+
+infers which verbs should have like functions, and then reports a contradiction when different statements infer that a verb maps a subject to a different object.
+The authors found that approximately 99\% of the apparent contradictions that they found were not genuine contradictions, and that it would require domain knowledge to understand why.
+
+\x{Need to talk about Harabagiu et al 2006 about contradiction detection through negation.}
+\x{Need to talk about three-way RTE task}.
+
+always map the subject to the same object, and then reports a contradiction when different statements
+
+In theory, one could find disputed claims by comparing statements on different web pages and looking for contradictions.
+
+However the problem of detecting contradictions has been found to be very difficult in practice~\cite{contradiction-hard}. Does ``
+
+\todo{Need to give a good citation of why contradiction detection is hard.}
+
+We consider a claim to be disputed if at least one author both believes that the claim is false and believes that
+
+In theory, the best way to find disputed claims would be to find places where two documents make statements that contradict each other.
+However this problem has been found to be very difficult in practice~\cite{contradiction-hard}.
+
+We obtain such statements $S$ by using the Yahoo BOSS search API to search for strings such as ``the misconception that''.
+We then parse the text that follows using a natural language parser and discard any text that either does not appear to be a valid statement, or that includes referents such as ``it'' or ``he'' that would otherwise need to be resolved based on the context.
+
 \subsection{Disputed Templates}
+
+\x{We use Yahoo BOSS.}
+\x{Yahoo BOSS limits us to 1000 results per query.}
+\x{We use dates to target pages that were published on a particular date.}
+\x{We have not yet done a details analysis of what proportion of pages were actually written on this date}
+\todo{Analyse how well our date targetting works}
+
+\x{We have a database of XXX different text strings, some of which may be the same claim.}
+
+\begin{figure}[tb]
+  \begin{tabular}{|ll|}
+    \hline
+    {\bf Google Count\footnotemark} & {\bf Template}\\ 
+    \hline
+    \multicolumn{2}{|c|}{\it Something that could be challenged}\\
+    163,000,000 & believe that \\
+    206,000,000 & think that \\
+    49,500,000 & idea that \\
+    33,600,000 & claim that \\
+    \hline
+    \multicolumn{2}{|c|}{\it Something others believe}\\
+    120,000,000 & the belief that \\
+    49,000,000 & who believe that \\
+    50,500,000 & who think that \\
+    10,100,000 & believing that \\
+    9,430,000 & claiming that \\
+    \hline
+    \multicolumn{2}{|c|}{\it Something false}\\
+    243,000,000 & it is not the case that \\
+    30,700,000 & it is not true that \\
+    15,600,000 & the misconception that \\
+    13,000,000 & the delusion that \\
+    12,400,000 & the myth that \\
+    9,960,000 & into believing that \\
+    7,190,000 & the mistaken belief that \\
+    4,950,000 & the fallacy that \\
+    3,720,000 & the lie that \\
+    3,700,000 & mistaken belief that \\
+    3,600,000 & the false belief that \\
+    3,440,000 & the deceit that \\
+    2,140,000 & the deception that \\
+    1,760,000 & the misunderstanding that \\
+    1,630,000 & mistakenly believe that \\
+    1,090,000 & false claim is that \\
+    1,290,000 & the hoax that \\
+    698,000 & absurdity of the claim that \\
+    681,000 & falsely claimed that \\
+    659,000 & no longer think that \\
+    654,000 & urban legend that \\
+    530,000 & the absurd idea that \\
+    373,000 & erroneously believe that \\
+    334,000 & the fabrication that \\
+    103,000 & falsely claiming that \\
+    140,000 & erroneous belief that \\
+    72,600 & falsely claim that \\
+    152,000 & bogus claim that \\
+    224,000 & the fantasy that \\
+    171,000 & incorrectly claim that \\
+    249,000 & incorrectly claimed that \\
+    232,000 & incorrectly believe that \\
+    98,900 & stupidly believe that \\
+    429,000 & falsely believe that \\
+    376,000 & wrongly believe that \\
+    189,000 & falsely suggests that \\
+    280,000 & falsely claims that \\
+    148,000 & false claim that \\
+    136,000 & no longer believe that \\
+    65,300 & urban myth that \\
+    59,500 & falsely stated that \\
+    \hline
+  \end{tabular}
+  \label{templates}
+  \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}
+
+\end{figure}
+
+\x{Some prefixes suggest that some disagree, without saying that they do. E.g. ``people who believe that''}
 
@@
 
+\x{Named entity recognition}
+
 \x{Look at what noun phrases were most disputed at particular years.}
 \x{Look at what noun phrases were most disputed on particular days.}
+
+\x{We remove exact-match strings from the same domain - to avoid republishing of same article.}
 
@@
 
-\bibliography{refs}
+% mendelybib is the bibliograph from our shared mendely space and is auto-generated
+% localbib is used for manually adding anything we don't want to add to mendeley, particularly for
+% people who are not mendeley users
+\bibliography{mendeleybib,localbib}
 

### 2010-01-28 papers/wicow_claimfinder/clues.tex

\subsection{Linguistic clues}

Various textual features reveal that an author is presenting a claim 
they don't necessarily agree with, or that there isn't general agreement on. 
For such features we consider especially phrases that introduce a clause. The
phrase qualifies the belief in the claim made by the clause. In linguistic
terms the modality of the phase qualfies the meaning of the clause.

For example...

Understanding the class of phrases that have this property lets us generalize
the expressions that are "templates" for disputed claims.

A modal expression can serve as a linguistic clue to indicate a
disputed claim. The modal clause introduces a subordinate clause,
qualifying its truth value. Modals serve a broad variety of purposes;
we are interested in two modal aspects, specficially, {\bf epistemic}
and {\bf evidential} modality. Epistemic refers generally to the
extent to which the claim is known. Most study has been about {\it
possibility} and {\it necessity} as epistemic qualifiers. In
contrast, our interest is in qualifiers that call the claim into
question, as a presumption, speculation, or a questionable
opinion. This can often, but not always done by attributing the claim
to some other person's belief, either implicitly or explicitly. The
author in so doing raises an issue about the truth, or lack of truth
of the claim.

Evidential modality is used by linguists to describe a feature of the
language that reveals the source of knowledge behind the claim~\cite{Aikenvald.2006}.
In some languages~(\cite{Palmer.2001}, p.64) there are syntactic means 
to indicate, for instance, that the user {\it saw} what they claim. This is
not so with European languages. ``Evidential'' as a linguistic term it is to be
distinguished from the sense of providing evidence about a claim. To
make the difference clear, consider as an example an author tainting a claim by
implying it came about as hearsay, by a phrase such as {\it there are
some who say that}.

There is a current literature about the interplay of evidential and
epistemic modalities, whether they really are
separable. See~\cite{Palmer.2001}, p. 24. The previous example illustrates
this, since, epistemically it attributes a questionable belief to the
phrase it qualifies while at the same time imputes its source. We
don't have to resolve which exactly it is. The range of modalities
suffices to give us a wider range of linguistic tools to reveal
disputed claims.

### 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
Fleshing out the paper. We now have some rough text for every section except the bits on what one can use this data for, and an exploration of the date itself

@@
 \newcommand{\idea}[1]{}
-\newcommand{\node}[1]{}
+\newcommand{\note}[1]{}
 
@@
 In this paper we describe a method for automatically aquiring a corpus of disputed claims from the web.
-By {\it disputed claim} we mean a statement about the world that some sources believe are true, and other sources believe is false.
-Our intention is that this corpus of disputed claims will be used as input to tools that help users know what information they encounter in their lives is potentially unreliable.
+We consider a claim to be {\it disputed} if some people believe both that others are making the claim, and that the claim is not true.
 
-We identify disputed claims by searching the web for patterns that indicate that a particular phrase is a disputed claim.
-One such pattern is ``the misconception that $S$'', an instance of which would be ``the minconception that {\it the moon is made of cheese}''.
-If we find a document that contains this text then that suggests that the author of the document believes both that the statement ``{\it the moon is made of cheese}'' is false, and that there are other authors who claim that ``{\it the moon is made of cheese}'' is true.
+We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$''.
+For example, if a document contains the text ``the minconception that {\it the moon is made of cheese}'', this suggests that the author of the document believes both that the statement ``{\it the moon is made of cheese}'' is false, and that there are other authors who claim that ``{\it the moon is made of cheese}'' is true.
 
-We have found many other patterns that have this property, some of which we list in Figure~\ref{templates}.
+We have found many other patterns that can be used in this way, some of which we list in Figure~\ref{templates}.
 Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{hearst-hyponyms} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.
@@
 
-We believe that our corpus is the first large-scale corpus of disputed claims.
+We believe that ours is the first attempt to automatically aquire a corpus of disputed claims.
 
@@
 
+The problem of detecting disputed claims is closely related to the well studied problem of detecting contradictions.
+A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true.
+For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
+A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong.
+For example the text ``we disagree with the assertion that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''.
+A {\it contradiction} is logical, while a {\it dispute} is social.
+In order for a claim to be disputed, the authors of the documents must be aware that their is a contradiction between their beliefs.
+
+There has been significant work on detecting contradictions.
+Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding.
+de Marneffe et al~\cite{deMarneffe2008} present a taxonoby of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction.
+AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
+Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another.
+The RTE-3 Recognizing Textual Entailment challenge~\cite{rte-3} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.
+
+Detecting contradictions has proven to be a hard problem.
+Much of the difficulty comes from the fact that it typically requires deep semantic knowledge to determine whether two statements that look like they might be contradictory actually are.
+``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush.
+``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England.
+``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.
+
+We detect disputes rather than contradictions.
+Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important.
+The advantage of looking for disputes rather than contradictions is that is is much easier - humans do the hard work of identifying contradictions and deciding whether they are important.
+The disadvantage of looking for disputes is that this method will only identify contradictions that humans have already identified.
+
 \todo{Want some kind of numerical estimate of how many disputed claims we have. Maybe measure this by pair of unique nouns and verbs. Noun + verb or noun + noun = disputed claim?}
@@
 
-We distinguish between a {\it contradiction} and a {\it dispute}.
-A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true.
-For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
-A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong.
-For example the text ``only idiots think that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''.
-A {\it contradiction} is logical, while a {\it dispute} is social.
-It is possible to have a contradiction without a dispute and a dispute without a contradiction.
-While the concepts are different, they are obviously closely related.
-Usually if someone disputes a claim it is because they believe an alternative claim that contradicts it.
+\x{Include a diagram showing the stages of our dispute finding process}
+\maybe{Talk about theories of contrast???}
+\maybe{Look at Kehler 2002 on CONTRAST???}
 
-We distinguish between a claim that is {\it contradicted} and a claim that is {\it disputed}. 
-A claim in a document is {\it contradicted} if there is another document somewhere else that makes a contradictory claim. A claim is {\it disputed} if another document explicitly says
+Figure~\ref{not-yet} shows the process we use to build our corpus of disputed claims. 
+We find disputed claims by searching the web for for patterns like ``the misconception that $S$'' and ``it is not the case that $S$'' (Section~\ref{searchpattern}). 
+For every page that contains the pattern, we grab the raw text from the end of the prefix string, up until the end end of the sentence.
+We then pass each such block of text to a parser that discards any text that does not appear to be a statement (Section~\ref{filterclaim}).
 
-A claim is {\it disputed} if another document
+Given a set of known disputed claims, we then go back and generate new patterns by searching for those claims on the web and looking for contexts in which those claims often appear.
 
-For example if one document says ``The moon is made of cheese'' and another document says ``The moon is made of rock'' then then the first statement is contradicted by the first.
+\subsection{Searching for Patterns}
+\label{searchpattern}
 
-We consider a claim to be disputed if at least one source suggests that the claim is true, and at least one source suggests that the claim is not true.
+We search the web for patterns that indicate that a claim is disputed.
+Figure~\ref{templates} shows a subset of the patterns that we search for.
+For each pattern, we show the number of times that Google estimates that the pattern appears on the web.
 
-One way to find disputed claims is to compare statements on different web pages and look for contradictions.
-AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a {\it functional} verb maps the same subject to multiple different objects and the difference cannot be resolved using a semantic knowledge.
+Rather than building our own search engine, we use the Yahoo BOSS search API~\cite{yahoo-boss} to search for patterns.
+We search Yahoo BOSS for a raw string such as ``the misconception that'' and then download every web page that Yahoo lists in its search results.
 
-Harabagiu et al\cite{Harabagiu2006}
+We form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g.
+'.','?','!',\texttt{</p>},\texttt{</h1>}, etc).
 
-\x{A contradiction is not the same as a dispute. A contradiction is where the information is different. A dispute is where the different parties BELIEVE the disagree. }
+We want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages.
+The Yahoo BOSS API does not offer the ability to request only pages updated in a given date range.
+We thus simulate this behaviour by instead including a literal date string in our queries.
+For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}.
+We instead search for \texttt{``it is not true that'' ``January 4 2010''}.
 
-The RTE-3 Recognizing Textual entailment task
+The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts.
+This approach has false positives and false negatives.
+Some web pages include dates that are not the date the article was posted, and some web pages either don't include the date the article was posted, or write their date in a different format.
+Indeed our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
 
-This turned out to be a hard problem;
+\todo{Produce some kind of measure of how well date searching actually works}
 
-scanning 117 million web pages yielded only 110 genuine contradictions.
+Another advantage of including the date in the search query is it reduces the impact of Yahoo's limit of only 1000 results per query.
+Since we include the date in the query, this translates into a limit of only 1000 results per pattern per day, which gives us access to a much larger set of pages.
 
-\todo{We might want to try using TextRunner ourselves.}
+Since we are using an existing search engine, we are limited to searching for simple text strings.
+This leads us to generate multiple patterns that are almost the same, other than for synonyms.
+E.g.
+``the lie that'' vs ``the deceipt that''.
+We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix.
+For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence.
+While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, it would be inefficient, since many pages would not contain the pattern.
 
-and then infers a contradiction when
+In the longer term we would like to have a more elegant search infrastructure, but for the time being this approach seems to work reasonably well.
 
-infers which verbs should have like functions, and then reports a contradiction when different statements infer that a verb maps a subject to a different object.
-The authors found that approximately 99\% of the apparent contradictions that they found were not genuine contradictions, and that it would require domain knowledge to understand why.
+\subsection{Generating Patterns}
+\label{newtemplate}
 
-\x{Need to talk about Harabagiu et al 2006 about contradiction detection through negation.}
-\x{Need to talk about three-way RTE task}.
+Figure~\ref{templates} shows some of the patterns that we search for.
 
-always map the subject to the same object, and then reports a contradiction when different statements
+As the figure shows, not all patterns have exactly the same meaning. We divide patterns into three fuzzily-grouped categories:
 
-In theory, one could find disputed claims by comparing statements on different web pages and looking for contradictions.
+\begin{itemize}
+ \item {\bf False:} The author believes the claim is wrong
+ \item {\bf Believed by others:} The author believes others think this, and it is likely that the author disagrees.
+Further inspection is required to determine whether the author disagrees with the claim.
+ \item {\bf Could be challenged:} The author feels the need to state that someone believes something, which suggests that this is something that one might not believe.
+For example, if an author says ``I think America is a great place'' this doesn't suggest that the claim is false, but the mere fact that they declared that they thought that suggests that they are aware that the claim could be challenged.
+\end{itemize}
 
-However the problem of detecting contradictions has been found to be very difficult in practice~\cite{contradiction-hard}. Does ``
+We grouped patterns into categories by hand, based on a brief inspection of pages that were using each of the patterns.
 
-\todo{Need to give a good citation of why contradiction detection is hard.}
+Which patterns one should use depends on what one wishes to use the resulting corpus of disputed claims for.
+If one wants to only have claims for which we can present web pages that argue that the claim is false, then only the first set of patterns should be used.
+If however one just wishes to see what things people think are worthy of having opinions expressed about, then the full set is useful.
 
-We consider a claim to be disputed if at least one author both believes that the claim is false and believes that
+We started with an initial set of patterns that we wrote by hand.
+We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim.
+From this set of candidate prefix patterns, we manually selected patterns that we believed would lead us, as a human, to infer that the author thought the claim was disputed, believed by others, or open to challenge.
 
-In theory, the best way to find disputed claims would be to find places where two documents make statements that contradict each other.
-However this problem has been found to be very difficult in practice~\cite{contradiction-hard}.
+\todo{Give some stats about our patterns}
+\todo{Use Yahoo BOSS counts rather than Google}
+\note{It seems silly to use Google's counts for these when we are using Yahoo BOSS. Someone should write a script to re-generate this table using Yahoo BOSS counts.}
 
-We obtain such statements $S$ by using the Yahoo BOSS search API to search for strings such as ``the misconception that''.
-We then parse the text that follows using a natural language parser and discard any text that either does not appear to be a valid statement, or that includes referents such as ``it'' or ``he'' that would otherwise need to be resolved based on the context.
-
-\subsection{Disputed Templates}
-
-\x{We use Yahoo BOSS.}
-\x{Yahoo BOSS limits us to 1000 results per query.}
-\x{We use dates to target pages that were published on a particular date.}
-\x{We have not yet done a details analysis of what proportion of pages were actually written on this date}
 \todo{Analyse how well our date targetting works}
-
-\x{We have a database of XXX different text strings, some of which may be the same claim.}
 
@@
     9,960,000 & into believing that \\
+    8,970,000 & disagree with the claim that \\
     7,190,000 & the mistaken belief that \\
+    6,160,000 & disagree with the assertion that \\
     4,950,000 & the fallacy that \\
@@
     3,440,000 & the deceit that \\
+    2,290,000 & cast doubt on the claim that \\
     2,140,000 & the deception that \\
@@
     659,000 & no longer think that \\
-    654,000 & urban legend that \\
-    530,000 & the absurd idea that \\
-    373,000 & erroneously believe that \\
-    334,000 & the fabrication that \\
-    103,000 & falsely claiming that \\
-    140,000 & erroneous belief that \\
-    72,600 & falsely claim that \\
-    152,000 & bogus claim that \\
-    224,000 & the fantasy that \\
-    171,000 & incorrectly claim that \\
-    249,000 & incorrectly claimed that \\
-    232,000 & incorrectly believe that \\
-    98,900 & stupidly believe that \\
-    429,000 & falsely believe that \\
-    376,000 & wrongly believe that \\
-    189,000 & falsely suggests that \\
-    280,000 & falsely claims that \\
-    148,000 & false claim that \\
-    136,000 & no longer believe that \\
-    65,300 & urban myth that \\
-    59,500 & falsely stated that \\
+%     654,000 & urban legend that \\
+%     530,000 & the absurd idea that \\
+%     373,000 & erroneously believe that \\
+%     334,000 & the fabrication that \\
+%     103,000 & falsely claiming that \\
+%     140,000 & erroneous belief that \\
+%     72,600 & falsely claim that \\
+%     152,000 & bogus claim that \\
+%     224,000 & the fantasy that \\
+%     171,000 & incorrectly claim that \\
+%     249,000 & incorrectly claimed that \\
+%     232,000 & incorrectly believe that \\
+%     98,900 & stupidly believe that \\
+%     429,000 & falsely believe that \\
+%     376,000 & wrongly believe that \\
+%     189,000 & falsely suggests that \\
+%     280,000 & falsely claims that \\
+%     148,000 & false claim that \\
+%     136,000 & no longer believe that \\
+%     65,300 & urban myth that \\
+%     59,500 & falsely stated that \\
     \hline
@@
 
-\x{Some prefixes suggest that some disagree, without saying that they do. E.g. ``people who believe that''}
+\subsection{Filtering Statements}
+\label{filterclaim}
 
-\x{Include a table with templates we use and templates we generated}
+We pass each such chunk of raw text to a natural language parser (custom grammar, and an NLTK~\cite{nltk} regexp parser).
+We throw away any chunk of text that does not appear to be a statement, or which uses a referent (such as ``it'' or ``he'') that cannot be easily resolved.
+Figure~\ref{filtered} shows examples of phrases that we filter.
 
-\subsection{Selecting Good Statements}
+\begin{figure*}[t]
+\begin{tabular}{|l|l|l|}
+  \hline
+  {\bf extracted text} & {\bf accepted} & {\bf reason} \\
+  \hline
+  {\it the false claim that} won't go away & reject & ``wont go away'' is not a statement \\
+  {\it falsely claimed that} he didn't do it & reject & ``he'' and ``it'' are unbound referents \\ 
+  {\it wrongly believe that} the moon is made of cheese & accept & \\
+  {\it false claim that} Elvis is alive despite all evidence & \\
+  \hline
+\end{tabular}
+\label{filtered}
+\caption{We filter out text that does not look like a statement}
+
+\end{figure*}
+
+\todo{Our parser is currently a bit rubbish. Need to work out how to do this properly.}
+\todo{We need to use the correct terminology here.}
 
@@
 \x{Strip HTML tags}
-
-\subsection{Generating New Templates}
-
-\x{Following the distributional hypothesis.}
-\x{Search for known disputed claims and find most frequent words that surround them.}
 

### 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
Minor edits, mostly typographical in nature

@@
        \affaddr{Berkeley, CA, USA}\\
-       \email{trush@cs.berkeley.edu}
+       \email{daniel.byler@berkeley.edu}
 \alignauthor John Mark Agosta\\
@@
 In many cases, these people disagree with each other, and the documents they write contain conflicting information.
-If a user is to extract reliable information from a the web, then it is useful for them to be able to determine when different documents disagree about a topic.
+For users to extract reliable information from the web, it is useful for them to be able to determine when different documents disagree about a topic.
 
-In this paper we describe a method for automatically aquiring a corpus of disputed claims from the web.
+In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web.
 We consider a claim to be {\it disputed} if some people believe both that others are making the claim, and that the claim is not true.
@@
 Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear.
-This is an instance of the distributional hypothesis~\cite{distributional-hypothesis}, that theorises that if a pattern occurs with similar phrases filling it's slots (it is distributionally similar) then it has a similar meaning.
+This is an instance of the distributional hypothesis~\cite{distributional-hypothesis}, which theorises that if a pattern occurs with similar phrases filling its slots (it is distributionally similar) then it has a similar meaning.
 
 We believe that this corpus will be useful for many purposes.
-We are using it as part of our Dispute Finder~\cite{www-disputefinder} project, to automatically highlight phrases on web pages that are disputed by other sources.
+We are currently using it as part of our Dispute Finder~\cite{www-disputefinder} project to automatically highlight phrases on web pages that are disputed by other sources.
 We are also exploring other applications of this corpus, including visualization tools that let users see what is disputed about topics they are interested in, or what has been disputed at particular times.
 
-We are making our corpus publically available so that other researchers who believe it would be useful for them can download it.
-We plan to continue to update our corpus as new pages are added to the web, and to develop tool that allow people to query it in useful ways.
+We are making our corpus publicly available for other researchers to download.
+We plan to continue to update our corpus as new pages are added to the web, and to develop tools that allow people to query it in useful ways.
 
-We believe that ours is the first attempt to automatically aquire a corpus of disputed claims.
+We believe that ours is the first attempt to automatically acquire a corpus of disputed claims.
 
@@
 In the past people typically obtained information from a relatively small set of sources such as books, TV channels, and radio stations.
-Each of these sources had a known reputation, and had publishing barriers and quality control to make sure that all information they provided met the standards expected from that source.
+Most of these sources had a known reputation, and had publishing barriers and quality control to ensure that the information they provided met the standards expected from that source.
 The web is very different.
@@
 Moreover, the internet has little in the way of publishing barriers or quality control.
-If users are going to extract trustworthy information from the web then they need to either restrict themselves to a small set of sources that they trust, or use some kind of mechanism to determine the credibility of the information that they read.
+If users are to extract trustworthy information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.
 
@@
 
-Given a document that contains information that may or may not be trustworthy, there are several ways that a reader can determine whether they should trust the information.
+Given a document that contains information which may or may not be trustworthy, there are several ways that a reader can determine whether they should trust the information.
 They can check the reputation of the source; they can check whether it looks like a reliable document; or they can check whether the information in the document is consistent with information available from other sources.
@@
 Alternatively, a user can simply use a search engine such as Google to look for information about the source.
-These tools can be very useful; however trustworthy sources sometimes publish unreliable information.
-For example a source may have been misled by an unreliable source they were using themselves.
+While these tools can be very useful, trustworthy sources sometimes publish unreliable information.
+For example, a source may have been misled by an unreliable source they were using themselves.
 Moreover, a user may have a document from a source that is not known to be reliable, and still wish to know if the information itself is trustworthy.
@@
 Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content.
-For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by looking at the edit history.
-Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether there are videos.
+For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by analyzing its edit history.
+Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos.
 Fogg et al~\cite{Fogg} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing.
@@
 For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
-In the currently released version of Dispute Finder, it builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims; however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
+In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims; however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
 
@@
 
-The problem of detecting disputed claims is closely related to the well studied problem of detecting contradictions.
+The problem of detecting disputed claims is closely related to the well-studied problem of detecting contradictions.
 A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true.
@@
 A {\it contradiction} is logical, while a {\it dispute} is social.
-In order for a claim to be disputed, the authors of the documents must be aware that their is a contradiction between their beliefs.
+In order for a claim to be disputed, the authors of the documents must be aware that there is a contradiction between their beliefs.
 
@@
 Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding.
-de Marneffe et al~\cite{deMarneffe2008} present a taxonoby of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction.
+de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction.
 AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
@@
 
-\maybe{Want to apply wikify to get nouns, and then use Chi-style catagory rules to find out what catagories are disputed on the web?}
+\maybe{Want to apply wikify to get nouns, and then use Chi-style category rules to find out what categories are disputed on the web?}
 
@@
 We thus simulate this behaviour by instead including a literal date string in our queries.
-For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}.
-We instead search for \texttt{``it is not true that'' ``January 4 2010''}.
+For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.
 
@@
 E.g.
-``the lie that'' vs ``the deceipt that''.
+``the lie that'' vs ``the deceit that''.
 We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix.
 For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence.
-While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, it would be inefficient, since many pages would not contain the pattern.
+While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, this would be inefficient, since many pages would not contain the pattern.
 

### 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
Added ACM class file. Minor paper tweaks
up to date

--- 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
@@
-\documentclass{acm_proc_article-sp}
+ %\documentclass{article}
+\documentclass{www2010-submission}
 \usepackage{times}
+%\usepackage{uist}
 \usepackage{url}
@@
 \usepackage{color}
+%
+%\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
+%\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
+%\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
+%\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}
+
 \newcommand{\want}[1]{}
+\newcommand{\todo}[1]{}
 \newcommand{\idea}[1]{}
@@
 \newcommand{\x}[1]{{\color{blue} #1}\\}
-
-% Mark up some work that we need to do in order for this paper to be telling the truth
-\newcommand{\todo}[1]{{\color{red} #1}\\}
-
-\newcommand{\maybe}[1]{}
 
@@
 \author{
-\alignauthor Rob Ennals\\
-       \affaddr{Intel Labs Berkeley}\\
-       \affaddr{2150 Shattuck Ave}\\
-       \affaddr{Berkeley, CA, USA}\\
-       \email{robert.ennals@intel.com}
-\alignauthor Dan Byler\\
-       \affaddr{School of Information}\\
-       \affaddr{University of California at Berkeley}\\
-       \affaddr{Berkeley, CA, USA}\\
-       \email{trush@cs.berkeley.edu}
-\alignauthor John Mark Agosta\\
-       \affaddr{Intel Labs Santa Clara}\\
-       \affaddr{2200 Mission College Blvd}\\
-       \affaddr{Santa Clara, CA, USA}\\
-       \email{john.m.agosta@intel.com}
-\and
-\alignauthor Barbara Rosario\\
-       \affaddr{Intel Labs Santa Clara}\\
-       \affaddr{2200 Mission College Blvd}\\
-       \affaddr{Santa Clara, CA, USA}\\
-       \email{john.m.agosta@intel.com}
-\alignauthor Tye Rattenbury\\
-       \affaddr{Intel Principles and Practices}\\
-       \affaddr{2200 Mission College Blvd}\\
-       \affaddr{Santa Clara, CA, USA}\\
-       \email{tye.l.rattenbury@intel.com}
+Author List to be Determined
 }
@@
 %\sloppy
+
+\additionalauthors{Barbara Rosario, Intel Labs Santa Clara, \\\texttt{[barbara.rosario@intel.com]}; Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\\\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}
 
@@
 \abstract
+[Final author list is to be determined]
 
-We describe a method for the automatic acquisition of a corpus of disputed claims from the web.
-We consider a claim to be disputed if a document on the web suggests that this claim is wrong and that other people on the web are suggesting that it is true.
+Not everything on the Web is accurate or unbiased. One way to determine that information on the web should not be trusted is if a trustworthy source elsewhere on the web is explicitly disagreeing
 
-Our tool extracts disputed claims by searching the web for templates such as ``falsely claimed that X'' or ``the myth that X'', and then analysing the parsed sentence structure to identify claims that seem to have the correct form.
-Given a set of known disputed claims, we can infer further templates by searching for other contexts in which known disputed claims appear.
+We describe a method for the automatic acquisition of a database of
 
-We believe that our corpus of disputed claims could be useful for a wide range of applications related to information credibility on the web.
+We describe a method for automatically aquiring a collection of claims that
 
@@
 
-The web contains a vast number of documents written by a vast number of people.
-In many cases, these people disagree with each other, and the documents they write contain conflicting information.
-If a user is to extract reliable information from a the web, then it is useful for them to be able to determine when different documents disagree about a topic.
-
-In this paper we describe a method for automatically aquiring a corpus of disputed claims from the web.
-By {\it disputed claim} we mean a statement about the world that some sources believe are true, and other sources believe is false.
-Our intention is that this corpus of disputed claims will be used as input to tools that help users know what information they encounter in their lives is potentially unreliable.
-
-We identify disputed claims by searching the web for patterns that indicate that a particular phrase is a disputed claim.
-One such pattern is ``the misconception that $S$'', an instance of which would be ``the minconception that {\it the moon is made of cheese}''.
-If we find a document that contains this text then that suggests that the author of the document believes both that the statement ``{\it the moon is made of cheese}'' is false, and that there are other authors who claim that ``{\it the moon is made of cheese}'' is true.
-
-We have found many other patterns that have this property, some of which we list in Figure~\ref{templates}.
-Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{hearst-hyponyms} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.
-
-\todo{TODO: we need to use template mining to get a more complete list of the templates that are good.}
-
-Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear.
-This is an instance of the distributional hypothesis~\cite{distributional-hypothesis}, that theorises that if a pattern occurs with similar phrases filling it's slots (it is distributionally similar) then it has a similar meaning.
-
-We believe that this corpus will be useful for many purposes.
-We are using it as part of our Dispute Finder~\cite{www-disputefinder} project, to automatically highlight phrases on web pages that are disputed by other sources.
-We are also exploring other applications of this corpus, including visualization tools that let users see what is disputed about topics they are interested in, or what has been disputed at particular times.
-
-We are making our corpus publically available so that other researchers who believe it would be useful for them can download it.
-We plan to continue to update our corpus as new pages are added to the web, and to develop tool that allow people to query it in useful ways.
-
-We believe that our corpus is the first large-scale corpus of disputed claims.
-
-\todo{Need to put our data online somewhere so that others can download it.}
-
-In this paper, we describe in more detail the way that we built this corpus, we explain ways that we think this corpus could be used, and we describe some features that we found in our data.
-
-\x{Include graph showing process by which we import claims.}
-
-\section{Background and Related Work}
-
 \x{Information credibility is important.}
@@
 
-Information credibility on the web is becoming increasingly important.
-In the past people typically obtained information from a relatively small set of sources such as books, TV channels, and radio stations.
-Each of these sources had a known reputation, and had publishing barriers and quality control to make sure that all information they provided met the standards expected from that source.
-The web is very different.
-A user has access to a vast number of different sources, but a user will know the reputation of only a small subset of these.
-Moreover, the internet has little in the way of publishing barriers or quality control.
-If users are going to extract trustworthy information from the web then they need to either restrict themselves to a small set of sources that they trust, or use some kind of mechanism to determine the credibility of the information that they read.
+\section{Background and Related Work}
 
-\x{Cite Pew study on this? Cite other people talking about misinformation}.
-
-Given a document that contains information that may or may not be trustworthy, there are several ways that a reader can determine whether they should trust the information.
-They can check the reputation of the source; they can check whether it looks like a reliable document; or they can check whether the information in the document is consistent with information available from other sources.
-
-To check the reputation of a source, a user can use a web site such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources.
-Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy.
-Alternatively, a user can simply use a search engine such as Google to look for information about the source.
-These tools can be very useful; however trustworthy sources sometimes publish unreliable information.
-For example a source may have been misled by an unreliable source they were using themselves.
-Moreover, a user may have a document from a source that is not known to be reliable, and still wish to know if the information itself is trustworthy.
-
-Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content.
-For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by looking at the edit history.
-Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether there are videos.
-Fogg et al~\cite{Fogg} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing.
-Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.
-
-In our research, we are following the third approach.
-We aim to inform users when information that they encounter is disputed by another source.
-We have built an extension to the Firefox web browser called Dispute Finder~\cite{www-disputefinder} that informs users when a web page that they are reading makes a claim that it knows to be disputed.
-For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
-In the currently released version of Dispute Finder, it builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims; however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
-
-Our primary motivation for automatically acquiring a large corpus of disputed claims is to use this corpus to enable tools like Dispute Finder to automatically inform users when they encounter information that this corpus says is disputed.
-
-\todo{Want some kind of numerical estimate of how many disputed claims we have. Maybe measure this by pair of unique nouns and verbs. Noun + verb or noun + noun = disputed claim?}
-
-\maybe{Want to apply wikify to get nouns, and then use Chi-style catagory rules to find out what catagories are disputed on the web?}
-
-\input{relatedwork.tex}
+\input{relatedwork}
 
@@
 
-We distinguish between a {\it contradiction} and a {\it dispute}.
-A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true.
-For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
-A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong.
-For example the text ``only idiots think that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''.
-A {\it contradiction} is logical, while a {\it dispute} is social.
-It is possible to have a contradiction without a dispute and a dispute without a contradiction.
-While the concepts are different, they are obviously closely related.
-Usually if someone disputes a claim it is because they believe an alternative claim that contradicts it.
-
-We distinguish between a claim that is {\it contradicted} and a claim that is {\it disputed}. 
-A claim in a document is {\it contradicted} if there is another document somewhere else that makes a contradictory claim. A claim is {\it disputed} if another document explicitly says
-
-A claim is {\it disputed} if another document
-
-For example if one document says ``The moon is made of cheese'' and another document says ``The moon is made of rock'' then then the first statement is contradicted by the first.
-
-We consider a claim to be disputed if at least one source suggests that the claim is true, and at least one source suggests that the claim is not true.
-
-One way to find disputed claims is to compare statements on different web pages and look for contradictions.
-AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a {\it functional} verb maps the same subject to multiple different objects and the difference cannot be resolved using a semantic knowledge.
-
-Harabagiu et al\cite{Harabagiu2006}
-
-\x{A contradiction is not the same as a dispute. A contradiction is where the information is different. A dispute is where the different parties BELIEVE the disagree. }
-
-The RTE-3 Recognizing Textual entailment task
-
-This turned out to be a hard problem;
-
-scanning 117 million web pages yielded only 110 genuine contradictions.
-
-\todo{We might want to try using TextRunner ourselves.}
-
-and then infers a contradiction when
-
-infers which verbs should have like functions, and then reports a contradiction when different statements infer that a verb maps a subject to a different object.
-The authors found that approximately 99\% of the apparent contradictions that they found were not genuine contradictions, and that it would require domain knowledge to understand why.
-
-\x{Need to talk about Harabagiu et al 2006 about contradiction detection through negation.}
-\x{Need to talk about three-way RTE task}.
-
-always map the subject to the same object, and then reports a contradiction when different statements
-
-In theory, one could find disputed claims by comparing statements on different web pages and looking for contradictions.
-
-However the problem of detecting contradictions has been found to be very difficult in practice~\cite{contradiction-hard}. Does ``
-
-\todo{Need to give a good citation of why contradiction detection is hard.}
-
-We consider a claim to be disputed if at least one author both believes that the claim is false and believes that
-
-In theory, the best way to find disputed claims would be to find places where two documents make statements that contradict each other.
-However this problem has been found to be very difficult in practice~\cite{contradiction-hard}.
-
-We obtain such statements $S$ by using the Yahoo BOSS search API to search for strings such as ``the misconception that''.
-We then parse the text that follows using a natural language parser and discard any text that either does not appear to be a valid statement, or that includes referents such as ``it'' or ``he'' that would otherwise need to be resolved based on the context.
-
 \subsection{Disputed Templates}
-
-\x{We use Yahoo BOSS.}
-\x{Yahoo BOSS limits us to 1000 results per query.}
-\x{We use dates to target pages that were published on a particular date.}
-\x{We have not yet done a details analysis of what proportion of pages were actually written on this date}
-\todo{Analyse how well our date targetting works}
-
-\x{We have a database of XXX different text strings, some of which may be the same claim.}
 
@@
     \hline
-    {\bf Google Count\footnotemark} & {\bf Template}\\ 
+    {\bf Google Count} & {\bf Template}\\ 
     \hline
@@
     \multicolumn{2}{|c|}{\it Something false}\\
-    243,000,000 & it is not the case that \\
-    30,700,000 & it is not true that \\
+    9,960,000 & into believing that \\
     15,600,000 & the misconception that \\
@@
     12,400,000 & the myth that \\
-    9,960,000 & into believing that \\
     7,190,000 & the mistaken belief that \\
@@
     3,720,000 & the lie that \\
-    3,700,000 & mistaken belief that \\
     3,600,000 & the false belief that \\
-    3,440,000 & the deceit that \\
     2,140,000 & the deception that \\
     1,760,000 & the misunderstanding that \\
+    148,000 & false claim that \\
+    1,090,000 & false claim is that \\
     1,630,000 & mistakenly believe that \\
-    1,090,000 & false claim is that \\
+    3,700,000 & mistaken belief that \\
+    530,000 & the absurd idea that \\
     1,290,000 & the hoax that \\
-    698,000 & absurdity of the claim that \\
+    3,440,000 & the deceit that \\
     681,000 & falsely claimed that \\
-    659,000 & no longer think that \\
-    654,000 & urban legend that \\
-    530,000 & the absurd idea that \\
+    103,000 & falsely claiming that \\
     373,000 & erroneously believe that \\
+    140,000 & erroneous belief that \\
     334,000 & the fabrication that \\
-    103,000 & falsely claiming that \\
-    140,000 & erroneous belief that \\
     72,600 & falsely claim that \\
     152,000 & bogus claim that \\
+    65,300 & urban myth that \\
+    654,000 & urban legend that \\
     224,000 & the fantasy that \\
@@
     280,000 & falsely claims that \\
-    148,000 & false claim that \\
+    59,500 & falsely stated that \\
+    698,000 & absurdity of the claim that \\
     136,000 & no longer believe that \\
-    65,300 & urban myth that \\
-    59,500 & falsely stated that \\
+    659,000 & no longer think that \\
     \hline
   \end{tabular}
-  \label{templates}
-  \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}
 
@@
 \x{Include a table with templates we use and templates we generated}
+
+\input{clues}
 
@@
 
-\x{We remove exact-match strings from the same domain - to avoid republishing of same article.}
-
 \section{Conclusions}
@@
 
-% mendelybib is the bibliograph from our shared mendely space and is auto-generated
-% localbib is used for manually adding anything we don't want to add to mendeley, particularly for
-% people who are not mendeley users
-\bibliography{mendeleybib,localbib}
+\bibliography{claimfinder-refs}
 

### 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
Added mendeley bib to git. It's automatically generated so don't edit it, but others need this file in order to properly build the paper. Also reordered some sections and fixed up some references

--- 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
@@
        \email{daniel.byler@berkeley.edu}
+\and
 \alignauthor John Mark Agosta\\
@@
        \email{john.m.agosta@intel.com}
-\and
 \alignauthor Barbara Rosario\\
@@
        \email{john.m.agosta@intel.com}
-\alignauthor Tye Rattenbury\\
-       \affaddr{Intel Principles and Practices}\\
-       \affaddr{2200 Mission College Blvd}\\
-       \affaddr{Santa Clara, CA, USA}\\
-       \email{tye.l.rattenbury@intel.com}
 }
@@
 We have found many other patterns that can be used in this way, some of which we list in Figure~\ref{templates}.
-Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{hearst-hyponyms} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.
+Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{Hearst1992} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.
 
@@
 de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction.
-AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
+AuContraire~\cite{Ritter2008} uses TextRunner~\cite{Banko2007} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
 Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another.
-The RTE-3 Recognizing Textual Entailment challenge~\cite{rte-3} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.
+The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.
 
@@
 In the longer term we would like to have a more elegant search infrastructure, but for the time being this approach seems to work reasonably well.
+
+\subsection{Filtering Statements}
+\label{filterclaim}
+
+Not every chunk of text identified by one of our patterns is a well-formed disputed claim. Consider for example the text chunks in Figure~\ref{filtered}.
+
+We use a simple natural language parser to filter the chunks of text that match our patterns.
+
+We pass each such chunk of raw text to a natural language parser (custom grammar, and an NLTK~\cite{nltk} regexp parser).
+We throw away any chunk of text that does not appear to be a statement, or which uses a referent (such as ``it'' or ``he'') that cannot be easily resolved.
+Figure~\ref{filtered} shows examples of phrases that we filter.
+
+\begin{figure*}[t]
+\begin{tabular}{|l|l|l|}
+  \hline
+  {\bf extracted text} & {\bf accepted} & {\bf reason} \\
+  \hline
+  {\it the false claim that} won't go away & reject & ``wont go away'' is not a statement \\
+  {\it falsely claimed that} he didn't do it & reject & ``he'' and ``it'' are unbound referents \\ 
+  {\it wrongly believe that} the moon is made of cheese & accept & \\
+  {\it false claim that} Elvis is alive despite all evidence & \\
+  \hline
+\end{tabular}
+\label{filtered}
+\caption{We filter out text that does not look like a statement}
+
+\end{figure*}
+
+\todo{Our parser is currently a bit rubbish. Need to work out how to do this properly.}
+\todo{We need to use the correct terminology here.}
+
+\x{Remove anything containing stuff like 'if'}
+\x{Disallow possesives like its/his etc unless a noun has come first}
+\x{Strip HTML tags}
 
@@
 
-\subsection{Filtering Statements}
-\label{filterclaim}
+\subsection{Context}
 
-We pass each such chunk of raw text to a natural language parser (custom grammar, and an NLTK~\cite{nltk} regexp parser).
-We throw away any chunk of text that does not appear to be a statement, or which uses a referent (such as ``it'' or ``he'') that cannot be easily resolved.
-Figure~\ref{filtered} shows examples of phrases that we filter.
-
-\begin{figure*}[t]
-\begin{tabular}{|l|l|l|}
-  \hline
-  {\bf extracted text} & {\bf accepted} & {\bf reason} \\
-  \hline
-  {\it the false claim that} won't go away & reject & ``wont go away'' is not a statement \\
-  {\it falsely claimed that} he didn't do it & reject & ``he'' and ``it'' are unbound referents \\ 
-  {\it wrongly believe that} the moon is made of cheese & accept & \\
-  {\it false claim that} Elvis is alive despite all evidence & \\
-  \hline
-\end{tabular}
-\label{filtered}
-\caption{We filter out text that does not look like a statement}
-
-\end{figure*}
-
-\todo{Our parser is currently a bit rubbish. Need to work out how to do this properly.}
-\todo{We need to use the correct terminology here.}
-
-\x{Remove anything containing stuff like 'if'}
-\x{Disallow possesives like its/his etc unless a noun has come first}
-\x{Strip HTML tags}
+\x{Importance of dates}
+\x{Work meaning depending on surrounding text}
+\x{We do not yet do anything useful with context, but we believe it is important and intend to use it}
 
@@
 \section{Analysing the Data}
+
+\todo{Lots of pretty graphs showing what our data is like.}
 

### 2010-01-28 papers/wicow_claimfinder/relatedwork.tex
No changes. Commiting to allow merge.
Fleshing out the paper. We now have some rough text for every section except the bits on what one can use this data for, and an exploration of the date itself
Added mendeley bib to git. It's automatically generated so don't edit it, but others need this file in order to properly build the paper. Also reordered some sections and fixed up some references

@@
-\subsection{What is credible?}
-
 %\subsection{The distributional hypothesis}
@@
 The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate 
-candidate claims  is inspired by \cite{hearst92} and is an instance of template inference (aka pattern matching) 
+candidate claims  is inspired by \cite{Hearst92} and is an instance of template inference (aka pattern matching) 
 that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and 
@@
 contradictions, contradictions occur when information found in two different texts is 
-incompatible\cite{harabagiu}. Here {\bf XX}.
-
-%\subsection{Contradiction Detection}
-
-%\subsection{Sentiment Analysis}
-
-\subsection{Crowdsourcing disputed claims}
-
-\x{Dispute Finder. Wikipedia. WikiTrust}
-
-\subsection{Curated Databases of Disputed Claims}
-
-\x{Dispute Finder.}
+incompatible\cite{Harabagiu2006}. Here {\bf XX}.

### 2010-01-29 papers/wicow_claimfinder/claimfinder.tex
Improved filter rules. Fleshed out paper text more. Merged related work

@@
 \newcommand{\note}[1]{}
+\newcommand{\x}[1]{}
+\newcommand{\todo}[1]{}
+\newcommand{\maybe}[1]{}
 
 % Mark up a point that we want to flesh out into more text
-\newcommand{\x}[1]{{\color{blue} #1}\\}
+%\newcommand{\x}[1]{{\color{blue} #1}\\}
 
 % Mark up some work that we need to do in order for this paper to be telling the truth
-\newcommand{\todo}[1]{{\color{red} #1}\\}
+%\newcommand{\todo}[1]{{\color{red} #1}\\}
 
-\newcommand{\maybe}[1]{}
+%\newcommand{\maybe}[1]{}
 
@@
 Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear.
-This is an instance of the distributional hypothesis~\cite{distributional-hypothesis}, which theorises that if a pattern occurs with similar phrases filling its slots (it is distributionally similar) then it has a similar meaning.
+This is an instance of the distributional hypothesis~\cite{Harris1954,Systems2000}, which theorises that if a pattern occurs with similar phrases filling its slots (it is distributionally similar) then it has a similar meaning.
 
@@
 
-\x{Cite Pew study on this? Cite other people talking about misinformation}.
+\x{Cite Pew study on this? Cite other people talking about misinformation.}
 
@@
 Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos.
-Fogg et al~\cite{Fogg} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing.
+Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing.
 Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.
@@
 de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction.
-AuContraire~\cite{Ritter2008} uses TextRunner~\cite{Banko2007} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
+AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
 Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another.
@@
 
-\input{relatedwork.tex}
+This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, 
+textual entailment and contradiction detection. Sentiment analysis aims to determine the attitude 
+(usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}. 
+Textual entailment is the task of deciding, given two text fragments, whether the meaning of one 
+text can be inferred from the other text (add references).
+
+% I think I've folded the stuff from this file into the main body now
+%\input{relatedwork.tex}
 
@@
 
+\begin{figure*}[tb]
+\begin{center}
+\begin{tabular}{|l|l|l|l|}
+  \hline
+  & {\bf extracted text} & {\bf valid} & {\bf details} \\
+  \hline
+  1. & the false claim that {\it won't go away} & no & ``wont go away'' is not a statement \\
+  2. & falsely claimed that {\it he didn't do it} & no & ``he'' and ``it'' are unbound referents \\
+  3. & falsely claimed that {\it federal labor laws do not apply} & no & object of the verb is not present\\
+  4. & false claim that {\it Elvis is alive} despite all evidence & yes & but drop everything after ``despite''\\
+  5. & wrongly believe that {\it the moon is made of cheese} & yes & it is a statement about the world \\
+\hline
+\end{tabular}
+\end{center}
+\label{filtered}
+\caption{We filter out text that does not look like a statement}
+
+\end{figure*}
+
 \subsection{Searching for Patterns}
@@
 
-We search the web for patterns that indicate that a claim is disputed.
+We search the web for patterns that indicate that a claim is disputed, such as ``false claim that $X$'' or or ``it is not true that $X$''.
 Figure~\ref{templates} shows a subset of the patterns that we search for.
 For each pattern, we show the number of times that Google estimates that the pattern appears on the web.
+
+This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks.
+Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events.
+TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
 
@@
 
-Not every chunk of text identified by one of our patterns is a well-formed disputed claim. Consider for example the text chunks in Figure~\ref{filtered}.
+Not every chunk of text identified by one of our patterns is a well-formed disputed claim.
+Consider for example the text chunks in Figure~\ref{filtered}.
+A chunk of text might not be a statement (case 1), it might include unbound referents such is ``it'', or ``they'' (case 2), or it might only make sense within the context of a particular document (case 3).
 
-We use a simple natural language parser to filter the chunks of text that match our patterns.
+We use a simple filter that looks for cases 1 and 2, but does not yet deal with case 3.
+We use the part-of-speech tagger from NLTK~\cite{nltk}, and then use a simple regexp parser to apply a series of simple rules.
 
-We pass each such chunk of raw text to a natural language parser (custom grammar, and an NLTK~\cite{nltk} regexp parser).
-We throw away any chunk of text that does not appear to be a statement, or which uses a referent (such as ``it'' or ``he'') that cannot be easily resolved.
-Figure~\ref{filtered} shows examples of phrases that we filter.
+\begin{enumerate}
+\item To ensure that the text represent a real statement (case 1) we accept only text that contains either two noun phrases (e.g.
+``{\it George Bush} is from {\it Texas}''), or a noun phrase and an adjective (e.g.
+``{\it Cocaine} is {\it addictive}'').
+We do not accept text that contains merely a noun and a verb (e.g.
+``{\it Federal laws} do not {\it apply}'') since manual inspection of our data set suggests that in such phrases the verb typically refers to a noun that is defined outside the statement itself.
 
-\begin{figure*}[t]
-\begin{tabular}{|l|l|l|}
-  \hline
-  {\bf extracted text} & {\bf accepted} & {\bf reason} \\
-  \hline
-  {\it the false claim that} won't go away & reject & ``wont go away'' is not a statement \\
-  {\it falsely claimed that} he didn't do it & reject & ``he'' and ``it'' are unbound referents \\ 
-  {\it wrongly believe that} the moon is made of cheese & accept & \\
-  {\it false claim that} Elvis is alive despite all evidence & \\
-  \hline
-\end{tabular}
-\label{filtered}
-\caption{We filter out text that does not look like a statement}
+\item We also discard any statement that contains a personal pronoun such as ``he'', ``she'', ``it'', or ``they'' unless it is proceeded by a noun (addressing case 2).
+We allow a personal pronoun after a noun, since manual inspection suggests that in most cases the personal pronoun refers to the noun, for example ``Bill Clinton said he wants to slow down the economy''.
+While we could in theory resolve other references, this is known to be a hard problem, and we have access to a large enough set of candidate claims that we can afford to throw away claims that are not easy for us to process.
 
-\end{figure*}
+\item In some cases a disputed claim will be followed by information about where the claim was made, or why the claim is wrong.
+For example ``he claimed that the moon was made of cheese {\it on his show}'' or ``he claimed that the moon is made of cheese {\it despite contrary evidence}''.
+We chop off such suffixes by discarding any text that follows a word such as ``despite'', ``however'', ``but'', or ``was''.
+\end{enumerate}
 
-\todo{Our parser is currently a bit rubbish. Need to work out how to do this properly.}
-\todo{We need to use the correct terminology here.}
+These rules were crafted by hand, based on trial and error and manual inspection of a relatively small number of claims.
+In the future we would like to use a more rigorous statistical method to produce more sophisticated rules for selecting high quality disputed claims, guided by a larger hand-annotated data set.
+We are also considering adopting an external framework such as TextRunner~\cite{Etzioni2008,Banko2008}.
 
-\x{Remove anything containing stuff like 'if'}
-\x{Disallow possesives like its/his etc unless a noun has come first}
-\x{Strip HTML tags}
+\todo{Need a rough evaluation of what proportion of claims get thrown away by each rule, and how accurate these rules are.}
 
@@
 
+Rather that searching for an arbitrary collection of known disputed claims, we found that we generated better templates by searching for claims that most documents disagee with (e.g.
+``eskimos have many words for snow'') rather than claims that many people agree with (e.g.
+``there is a God'').
+If many people agree with a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed.
+Even when we search for claims that are highly disputed, our algorithm still finds many patterns that do not indicate dispute.
+We thus rely on a human to pick which prefixes to use.
+
+We also find that we get higher quality results if we limit ourselves to prefixes that end in ``that''.
+For example, if we search for ``that eskimos have many words for snow'' then most prefixes we find do indeed indicate dispute, however if we just search for ``eskimos have many words for snow'' then we get a much lower hit rate.
+
+This approach is an example of the Distributional Hypothesis.
+The distributional hypothesis, as originally framed~\cite{Harris1954,Systems2000}, theorised that words that appear in similar contexts have similar meanings.
+This has more recently been extended to patterns.
+If two patterns appear in a corpus with similar text filling their slots, then it is likely that the patterns have similar meanings.
+DIRT~\cite{Lin2001} discovers inference rules such as (``$X$ is author of $Y$'' $\equv$ ``$X$ wrote $Y$'') by looking for patterns that have a similar distribution of text filling their slots.
+Pasca and Dienes~\cite{Pasca2005} detect paraphrases on the web by searching for text fragments that appear in similar contexts on web pages.
+
 \todo{Give some stats about our patterns}
@@
 \begin{figure}[tb]
+\begin{center}
   \begin{tabular}{|ll|}
@@
   \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}
-
+\end{center}
 \end{figure}

### 2010-01-29 papers/wicow_claimfinder/relatedwork.tex
Improved filter rules. Fleshed out paper text more. Merged related work

@@
 The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate 
-candidate claims  is inspired by \cite{Hearst92} and is an instance of template inference (aka pattern matching) 
+candidate claims  is inspired by \cite{Hearst1992} and is an instance of template inference (aka pattern matching) 
 that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and 

### 2010-01-29 papers/wicow_claimfinder/claimfinder.tex
Replaced Google counts with Yahoo counts

@@
 Figure~\ref{templates} shows a subset of the patterns that we search for.
-For each pattern, we show the number of times that Google estimates that the pattern appears on the web.
+For each pattern, we show the number of times that Yahoo estimates that the pattern appears on the web.
 
@@
 \todo{Give some stats about our patterns}
-\todo{Use Yahoo BOSS counts rather than Google}
-\note{It seems silly to use Google's counts for these when we are using Yahoo BOSS. Someone should write a script to re-generate this table using Yahoo BOSS counts.}
 
@@
     \hline
-    {\bf Google Count\footnotemark} & {\bf Template}\\ 
+    {\bf Yahoo Count\footnotemark} & {\bf Template}\\ 
     \hline
         \multicolumn{2}{|c|}{\it Something that could be challenged}\\
-    163,000,000 & believe that \\
-    206,000,000 & think that \\
-    49,500,000 & idea that \\
-    33,600,000 & claim that \\
+        570,000,000 & think that \\
+        495,000,000 & believe that \\
+        145,000,000 & idea that \\
+        101,000,000 & claim that \\
        \hline
        \multicolumn{2}{|c|}{\it Something others believe}\\
-    120,000,000 & the belief that \\
-    49,000,000 & who believe that \\
-    50,500,000 & who think that \\
-    10,100,000 & believing that \\
-    9,430,000 & claiming that \\
+        40,100,000 & claiming that \\
+        30,600,000 & the belief that \\
+        28,600,000 & believing that \\
+        11,700,000 & who believe that \\
+        8,400,000 & who think that \\
         \hline
         \multicolumn{2}{|c|}{\it Something false}\\
-    243,000,000 & it is not the case that \\
-    30,700,000 & it is not true that \\
-    15,600,000 & the misconception that \\
-    13,000,000 & the delusion that \\
-    12,400,000 & the myth that \\
-    9,960,000 & into believing that \\
-    8,970,000 & disagree with the claim that \\
-    7,190,000 & the mistaken belief that \\
-    6,160,000 & disagree with the assertion that \\
-    4,950,000 & the fallacy that \\
-    3,720,000 & the lie that \\
-    3,700,000 & mistaken belief that \\
-    3,600,000 & the false belief that \\
-    3,440,000 & the deceit that \\
-    2,290,000 & cast doubt on the claim that \\
-    2,140,000 & the deception that \\
-    1,760,000 & the misunderstanding that \\
-    1,630,000 & mistakenly believe that \\
-    1,090,000 & false claim is that \\
-    1,290,000 & the hoax that \\
-    698,000 & absurdity of the claim that \\
-    681,000 & falsely claimed that \\
-    659,000 & no longer think that \\
-%     654,000 & urban legend that \\
-%     530,000 & the absurd idea that \\
-%     373,000 & erroneously believe that \\
-%     334,000 & the fabrication that \\
-%     103,000 & falsely claiming that \\
-%     140,000 & erroneous belief that \\
-%     72,600 & falsely claim that \\
-%     152,000 & bogus claim that \\
-%     224,000 & the fantasy that \\
-%     171,000 & incorrectly claim that \\
-%     249,000 & incorrectly claimed that \\
-%     232,000 & incorrectly believe that \\
-%     98,900 & stupidly believe that \\
-%     429,000 & falsely believe that \\
-%     376,000 & wrongly believe that \\
-%     189,000 & falsely suggests that \\
-%     280,000 & falsely claims that \\
-%     148,000 & false claim that \\
-%     136,000 & no longer believe that \\
-%     65,300 & urban myth that \\
-%     59,500 & falsely stated that \\
+        5,790,000 & the myth that \\
+        3,260,000 & into believing that \\
+        1,690,000 & the lie that \\
+        1,410,000 & it is not true that \\
+        1,220,000 & the delusion that \\
+        1,140,000 & the misconception that \\
+        995,000 & mistaken belief that \\
+        676,000 & the mistaken belief that \\
+        593,000 & mistakenly believe that \\
+        583,000 & the fantasy that \\
+        501,000 & it is not the case that \\
+        459,000 & false claim that \\
+        405,000 & the fallacy that \\
+        351,000 & falsely claimed that \\
+        264,000 & urban legend that \\
+        250,000 & no longer believe that \\
+        216,000 & the false belief that \\
+        215,000 & falsely claiming that \\ 
+        178,000 & falsely believe that \\
+        171,000 & bogus claim that \\
+        163,000 & erroneous belief that \\
+        154,000 & the deception that \\
+        147,000 & the misunderstanding that \\
+        135,000 & urban myth that \\
+    %    131,000 & wrongly believe that \\
+    %    126,000 & falsely claim that \\
+    %    109,000 & erroneously believe that \\
+    %    101,000 & falsely claims that \\
+    %    83,900 & incorrectly believe that \\
+    %    83,200 & no longer think that \\
+    %    82,400 & falsely stated that \\
+    %    79,200 & the absurd idea that \\
+    %    74,100 & the hoax that \\
+    %    41,500 & the deceit that \\
+    %    23,700 & incorrectly claimed that \\
+    %    21,900 & disagree with the claim that \\
+    %    15,900 & falsely suggests that \\
+    %    15,300 & disagree with the assertion that \\
+    %    14,200 & the fabrication that \\
+    %    9,640 & incorrectly claim that \\
+    %    2,110 & cast doubt on the claim that \\
+    %    2,080 & absurdity of the claim that \\
+    %    1,820 & false claim is that \\
+    %    1,750 & stupidly believe that \\
     \hline
@@
   \label{templates}
-  \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}
+  \caption{Some of the templates that we use to search for disputed claims, and Yahoo's rough estimate of how many times each one appears on the web}
 \end{center}

### 2010-01-29 papers/wicow_claimfinder/claimfinder.tex
Improved statement filtering and allowed it to be done in the same pass as noun extraction

@@
 Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{Hearst1992} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.
+{\bf either put here the other related work on this, or just put this reference in the related work section-- especially because there much more important work beyond hearst92, so no need to give it much emphasis in the intro}
 
@@
 '.','?','!',\texttt{</p>},\texttt{</h1>}, etc).
+{\bf it would be quite important to give a sense on the accuracy --precision - of the claims extracted.
+you can calculated this from a subset of returned candidate claims: out of, say, 100, how many were actually claims?}
 
+{\bf is it really important the discussion on the date and search technique? i think it deviates from the main points and is kind of long}
 We want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages.
@@
 
+\x{Talk about how we plan to have a much bigger data set in the future. This is just the start.}
+
 %\section{Acknowledgments}

### 2010-01-30 papers/wicow_claimfinder/claimfinder.tex
Changes by Barbara

--- 2010-01-29 papers/wicow_claimfinder/claimfinder.tex
@@
 \newcommand{\note}[1]{}
-\newcommand{\x}[1]{}
-\newcommand{\todo}[1]{}
+%\newcommand{\x}[1]{}
+%\newcommand{\todo}[1]{}
 \newcommand{\maybe}[1]{}
@@
 % Mark up a point that we want to flesh out into more text
-%\newcommand{\x}[1]{{\color{blue} #1}\\}
+\newcommand{\x}[1]{{\color{blue} #1}\\}
 
 % Mark up some work that we need to do in order for this paper to be telling the truth
-%\newcommand{\todo}[1]{{\color{red} #1}\\}
+\newcommand{\todo}[1]{{\color{red} #1}\\}
 
@@
 For example, if a document contains the text ``the minconception that {\it the moon is made of cheese}'', this suggests that the author of the document believes both that the statement ``{\it the moon is made of cheese}'' is false, and that there are other authors who claim that ``{\it the moon is made of cheese}'' is true.
-
-We have found many other patterns that can be used in this way, some of which we list in Figure~\ref{templates}.
-Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{Hearst1992} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.
+In Figure~\ref{templates} we list some of the patterns we used.
+We then search the web for these patterns, process the text to extract the claims, thus creating a corpus of candidate claims.
 
 \todo{TODO: we need to use template mining to get a more complete list of the templates that are good.}
-
-Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear.
-This is an instance of the distributional hypothesis~\cite{Harris1954,Systems2000}, which theorises that if a pattern occurs with similar phrases filling its slots (it is distributionally similar) then it has a similar meaning.
 
@@
 For every page that contains the pattern, we grab the raw text from the end of the prefix string, up until the end end of the sentence.
-We then pass each such block of text to a parser that discards any text that does not appear to be a statement (Section~\ref{filterclaim}).
-
-Given a set of known disputed claims, we then go back and generate new patterns by searching for those claims on the web and looking for contexts in which those claims often appear.
+We then process each such block of text to filter out any text that does not appear to be a statement (Section~\ref{filterclaim}).
 
@@
 
-\subsection{Searching for Patterns}
-\label{searchpattern}
+\subsection{Patterns for Finding Claims}
+\label{creatingpattern}
 
-We search the web for patterns that indicate that a claim is disputed, such as ``false claim that $X$'' or or ``it is not true that $X$''.
-Figure~\ref{templates} shows a subset of the patterns that we search for.
-For each pattern, we show the number of times that Yahoo estimates that the pattern appears on the web.
+We hand crafted a set of {\bf XX} patterns that indicate that a claim is disputed, such as ``false claim that $X$'' or or ``it is not true that $X$.''
 
@@
 TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
+\x{add more related work here}
+\todo{add more related work here}
 
-Rather than building our own search engine, we use the Yahoo BOSS search API~\cite{yahoo-boss} to search for patterns.
+In this work we simply start with an initial set of patterns that we wrote by hand.
+We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim.
+From this set of candidate prefix patterns, we manually selected additional patterns.
+\x{add more related work on boostraping here}
+\todo{add more related work here}
+
+Rather that searching for an arbitrary collection of known disputed claims, we found that we generated better templates by searching for claims that most documents disagee with (e.g.
+``eskimos have many words for snow'') rather than claims that many people agree with (e.g.
+``there is a God'').
+If many people agree with a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed.
+
+We also find that we get higher quality results if we limit ourselves to prefixes that begin with ``that''.
+For example, if we search for ``that eskimos have many words for snow'' then most prefixes we find do indeed indicate dispute, however if we just search for ``eskimos have many words for snow'' then we get a much lower hit rate.
+
+\x{not sure if to add what follow, posponing the decision for now}
+This approach is an example of the Distributional Hypothesis.
+The distributional hypothesis, as originally framed~\cite{Harris1954,Systems2000}, theorised that words that appear in similar contexts have similar meanings.
+This has more recently been extended to patterns.
+If two patterns appear in a corpus with similar text filling their slots, then it is likely that the patterns have similar meanings.
+DIRT~\cite{Lin2001} discovers inference rules such as (``$X$ is author of $Y$'' $\equv$ ``$X$ wrote $Y$'') by looking for patterns that have a similar distribution of text filling their slots.
+Pasca and Dienes~\cite{Pasca2005} detect paraphrases on the web by searching for text fragments that appear in similar contexts on web pages.
+
+Figure~\ref{templates} shows a subset of the {\bf xx} patterns  that we used. For each pattern, we show the number of times that Yahoo estimates that the pattern appears on the web. 
+\todo{add statistic of patterns and patterna accuracy here}
+\x{add statistic of patterns and patterna accuracy here}
+
+We plan to work on more sophisticated algorithms for finding new patterns automatically in future work.
+
+Not all patterns have exactly the same meaning. We divide patterns into three fuzzily-grouped categories:
+
+\begin{itemize}
+ \item {\bf False:} The author believes the claim is wrong
+ \item {\bf Believed by others:} The author believes others think this, and it is likely that the author disagrees.
+Further inspection is required to determine whether the author disagrees with the claim.
+ \item {\bf Could be challenged:} The author feels the need to state that someone believes something, which suggests that this is something that one might not believe.
+For example, if an author says ``I think America is a great place'' this doesn't suggest that the claim is false, but the mere fact that they declared that they thought that suggests that they are aware that the claim could be challenged.
+\end{itemize}
+
+We grouped patterns into categories by hand, based on a brief inspection of pages that were using each of the patterns.
+
+Which patterns one should use depends on what one wishes to use the resulting corpus of disputed claims for.
+If one wants to only have claims for which we can present web pages that argue that the claim is false, then only the first set of patterns should be used.
+If however one just wishes to see what things people think are worthy of having opinions expressed about, then the full set is useful.
+\todo{Give some stats about our patterns}
+
+\subsection{Searching for Claims}
+\label{searchpattern}
+
+In order to extract a set of claims, we then search the web for the set of patterns described in the previous session.
+Rather than building our own search engine, we use the Yahoo BOSS search API~\cite{yahoo-boss}.
 We search Yahoo BOSS for a raw string such as ``the misconception that'' and then download every web page that Yahoo lists in its search results.
-
-We form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g.
-'.','?','!',\texttt{</p>},\texttt{</h1>}, etc).
-
-We want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages.
-The Yahoo BOSS API does not offer the ability to request only pages updated in a given date range.
-We thus simulate this behaviour by instead including a literal date string in our queries.
-For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.
-
-The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts.
-This approach has false positives and false negatives.
-Some web pages include dates that are not the date the article was posted, and some web pages either don't include the date the article was posted, or write their date in a different format.
-Indeed our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
-
-\todo{Produce some kind of measure of how well date searching actually works}
-
-Another advantage of including the date in the search query is it reduces the impact of Yahoo's limit of only 1000 results per query.
-Since we include the date in the query, this translates into a limit of only 1000 results per pattern per day, which gives us access to a much larger set of pages.
-
 Since we are using an existing search engine, we are limited to searching for simple text strings.
@@
 
+Since we are interested in the time information on the claims and we want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range.
+The Yahoo BOSS API does not offer the ability to do so; we thus simulate this behaviour by instead including a literal date string in our queries.
+For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.
+
+The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts.
+This approach has false positives and false negatives.
+Some web pages include dates that are not the date the article was posted, and some web pages either don't include the date the article was posted, or write their date in a different format.
+Indeed our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
+
+\todo{Produce some kind of measure of how well date searching actually works}
+\todo{Give some stats about search results}
+
 \subsection{Filtering Statements}
 \label{filterclaim}
+
+From the web pages returned from the search, we form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g.
+'.','?','!',\texttt{</p>},\texttt{</h1>}, etc).
+\x{it would be quite important to give a sense on the accuracy --precision - of the claims extracted.
+you can calculated this from a subset of returned candidate claims: out of, say, 100, how many were actually claims?}
 
@@
 We are also considering adopting an external framework such as TextRunner~\cite{Etzioni2008,Banko2008}.
+\todo{add related work here}
 
 \todo{Need a rough evaluation of what proportion of claims get thrown away by each rule, and how accurate these rules are.}
-
-\subsection{Generating Patterns}
-\label{newtemplate}
-
-Figure~\ref{templates} shows some of the patterns that we search for.
-
-As the figure shows, not all patterns have exactly the same meaning. We divide patterns into three fuzzily-grouped categories:
-
-\begin{itemize}
- \item {\bf False:} The author believes the claim is wrong
- \item {\bf Believed by others:} The author believes others think this, and it is likely that the author disagrees.
-Further inspection is required to determine whether the author disagrees with the claim.
- \item {\bf Could be challenged:} The author feels the need to state that someone believes something, which suggests that this is something that one might not believe.
-For example, if an author says ``I think America is a great place'' this doesn't suggest that the claim is false, but the mere fact that they declared that they thought that suggests that they are aware that the claim could be challenged.
-\end{itemize}
-
-We grouped patterns into categories by hand, based on a brief inspection of pages that were using each of the patterns.
-
-Which patterns one should use depends on what one wishes to use the resulting corpus of disputed claims for.
-If one wants to only have claims for which we can present web pages that argue that the claim is false, then only the first set of patterns should be used.
-If however one just wishes to see what things people think are worthy of having opinions expressed about, then the full set is useful.
-
-We started with an initial set of patterns that we wrote by hand.
-We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim.
-From this set of candidate prefix patterns, we manually selected patterns that we believed would lead us, as a human, to infer that the author thought the claim was disputed, believed by others, or open to challenge.
-
-Rather that searching for an arbitrary collection of known disputed claims, we found that we generated better templates by searching for claims that most documents disagee with (e.g.
-``eskimos have many words for snow'') rather than claims that many people agree with (e.g.
-``there is a God'').
-If many people agree with a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed.
-Even when we search for claims that are highly disputed, our algorithm still finds many patterns that do not indicate dispute.
-We thus rely on a human to pick which prefixes to use.
-
-We also find that we get higher quality results if we limit ourselves to prefixes that end in ``that''.
-For example, if we search for ``that eskimos have many words for snow'' then most prefixes we find do indeed indicate dispute, however if we just search for ``eskimos have many words for snow'' then we get a much lower hit rate.
-
-This approach is an example of the Distributional Hypothesis.
-The distributional hypothesis, as originally framed~\cite{Harris1954,Systems2000}, theorised that words that appear in similar contexts have similar meanings.
-This has more recently been extended to patterns.
-If two patterns appear in a corpus with similar text filling their slots, then it is likely that the patterns have similar meanings.
-DIRT~\cite{Lin2001} discovers inference rules such as (``$X$ is author of $Y$'' $\equv$ ``$X$ wrote $Y$'') by looking for patterns that have a similar distribution of text filling their slots.
-Pasca and Dienes~\cite{Pasca2005} detect paraphrases on the web by searching for text fragments that appear in similar contexts on web pages.
-
-\todo{Give some stats about our patterns}
-
-\todo{Analyse how well our date targetting works}
 

### 2010-01-30 papers/wicow_claimfinder/claimfinder.tex
Added draft text for applications, conclusion

@@
 
-\x{We are building lots of applications that will use this data set.}
-\x{Dispute Finder highlights disputed claims on the web.}
-\x{Tell people when audio they hear is disputed.}
-\x{Tell people when a source you trust disagrees with others.}
-\x{Tell me when a source I read in the past is now disputed.}
-\x{Tell me how contentious a topic is.}
-\x{Let me explore what is disputed about a particular topic.}
-\x{Tell me when something new is disputed about a topic I care about.}
-\x{Examine the zeitgeist of disputes.}
-\x{Tell me about things that are disputed by the kind of sites I trust.}
-\x{We also want to make this data set available to others.}
+A corpus of disputed claims could be useful for a variety of applications, including real-time dispute recognition, background dispute analysis agents, and other research tools.
+Real-time dispute recognition agents could be used, for instance, to alert users when a trusted source disagrees with others, or to provide the user with feedback on how contentious a topic is.
+
+Dispute Finder is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages.
+Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications.
+We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation.
+Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.
+
+Dispute analysis agents that run in the background represent another application we see for a corpus of disputed claims.
+Such agents could be trained with information regarding the books, journals, and news articles a user reads.
+It would then be able to alert the user when a previously-read source is now disputed.
+It could also track a set of topics and tell the user when something new is disputed about a topic.
+A background dispute analysis agent would serve as an automated research assistant, alerting me when
+
+A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes.
+In this way the cultural
+
+Recognizing that these are but a few of the ways in which a disputed claim corpus could be used, we will release this data set to the research community as a whole.
+
+\x{"It will be available for unrestricted use under the XXX license. The dataset can be accessed at http://xxx.intel.com/xxx"}
 
@@
 
-\x{We can use the web as a corpus to determine what people think is disputed.}
+Our research has shown that the web can be used as a corpus to determine what claims people identify as being disputed.
+Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the array of views to be found online.
 
-\x{Talk about how we plan to have a much bigger data set in the future. This is just the start.}
+Furthermore, because individuals express opinions freely online, a snapshot of the disputed claims online can provide valuable insights into the cultural zeitgeist of the time.
+
+Challenges of creating a comprehensive corpus of disputed claims are many, from data quality to deeper natural language processing challenges such as recognizing textual entailment.
+We address these in part by taking a high-level statistical view of the data.
+
+The possible applications of a corpus of disputed claims are many and varied.
+These include real-time dispute recognition, autonomous research agents that operate in the background, and sociocultural research.
+
+Using the claim prefix search technique and text processing, we are able to identify
+
+Our data set currently includes approximately 1.2 million records.
+We intend to expand this by several orders of magnitude, an improvement that will address issues of data sparsity and enable more robust data processing.
 

### 2010-01-31 papers/wicow_claimfinder/claimfinder.tex
Changes by Barbara

@@
 
+\x{too much emphasis on {\em how}... rewrite following paragrapgh}
 Our tool extracts disputed claims by searching the web for templates such as ``falsely claimed that X'' or ``the myth that X'', and then analysing the parsed sentence structure to identify claims that seem to have the correct form.
@@
 
-We believe that ours is the first attempt to automatically acquire a corpus of disputed claims.
+We believe that ours is the first attempt to automatically acquire a corpus of disputed claims from the Web.
 
@@
 The advantage of looking for disputes rather than contradictions is that is is much easier - humans do the hard work of identifying contradictions and deciding whether they are important.
+\x{seems like we do this {\em only} because it's simpler...
+so perhaps add something around the fact there it's interesting to see where/how/when people disagree...
+some observation on the social aspects of dispute?}
 The disadvantage of looking for disputes is that this method will only identify contradictions that humans have already identified.
@@
 
-This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, 
-textual entailment and contradiction detection. Sentiment analysis aims to determine the attitude 
-(usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}. 
-Textual entailment is the task of deciding, given two text fragments, whether the meaning of one 
-text can be inferred from the other text (add references).
-
-% I think I've folded the stuff from this file into the main body now
-%\input{relatedwork.tex}
+This work is also  related to the NLP areas of opinion mining and/or sentiment analysis and textual entailment.
+Sentiment analysis aims to determine the attitude (usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}.
+Textual entailment is the task of deciding, given two text fragments, whether the meaning of one  text can be inferred from the other text 
+\x {add references and say why different}
+The methods we use are closely related to related work on information extraction which is the task of identifing and classifing specific semantic entities within documents (i.e.
+names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.
 
 \section{Finding Disputed Claims}
+\label{findingclaims}
 
 \x{Include a diagram showing the stages of our dispute finding process}
+\x{BR: I wouldn't... not very informative, I'd think}
 \maybe{Talk about theories of contrast???}
@@
 
-Figure~\ref{not-yet} shows the process we use to build our corpus of disputed claims. 
-We find disputed claims by searching the web for for patterns like ``the misconception that $S$'' and ``it is not the case that $S$'' (Section~\ref{searchpattern}). 
-For every page that contains the pattern, we grab the raw text from the end of the prefix string, up until the end end of the sentence.
-We then process each such block of text to filter out any text that does not appear to be a statement (Section~\ref{filterclaim}).
+%Figure~\ref{not-yet} shows the process we use to build our corpus of disputed claims.
+
+We implemented a three stage process to build our corpus of disputed claims, each described in the following Sections.
+We first create a set of lexical patterns (i.e.
+``the misconception that'' and ``it is not the case that'').
+We then search the Web for these patterns and finally process the text of the returned Web pages to extract only the parts that describe the disputed claims.
 
@@
 
-We hand crafted a set of {\bf XX} patterns that indicate that a claim is disputed, such as ``false claim that $X$'' or or ``it is not true that $X$.''
+We hand crafted a set of {\bf XX} patterns that we hypothesize may  indicate that a claim is disputed, such as ``false claim that'' or or ``it is not true that.''
 
@@
 TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
+These methods differ on how {\bf finish here}
 \x{add more related work here}
@@
 From this set of candidate prefix patterns, we manually selected additional patterns.
-\x{add more related work on boostraping here}
+
+\x{add more related work on boostraping here, adding differences}
 \todo{add more related work here}
+
+We plan to work on more sophisticated algorithms for finding new patterns automatically in future work.
 
@@
 
-We plan to work on more sophisticated algorithms for finding new patterns automatically in future work.
-
 Not all patterns have exactly the same meaning. We divide patterns into three fuzzily-grouped categories:
@@
 
-\subsection{Searching for Claims}
+\subsection{Searching the Web for Claims}
 \label{searchpattern}
 
-In order to extract a set of claims, we then search the web for the set of patterns described in the previous session.
+We then search the web for the set of patterns described in the previous session.
 Rather than building our own search engine, we use the Yahoo BOSS search API~\cite{yahoo-boss}.
@@
 
-Since we are interested in the time information on the claims and we want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range.
+Since we are interested in the time information of the claims and we want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range.
 The Yahoo BOSS API does not offer the ability to do so; we thus simulate this behaviour by instead including a literal date string in our queries.
@@
 '.','?','!',\texttt{</p>},\texttt{</h1>}, etc).
+
 \x{it would be quite important to give a sense on the accuracy --precision - of the claims extracted.
@@
 \x{We do not yet do anything useful with context, but we believe it is important and intend to use it}
+\x{context can be surrounding text but also features of the web pages -- domain,  "authority," in-links, format; context is also the author: expert? social info on author...}
 
@@
 \x{Evaluate the quality of the different individual templates - which ones have the highest quality claims.}
+\x{say something about {\em duplicate} claims?}
 

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Doing a pass over the paper

@@
 %\newcommand{\x}[1]{}
-%\newcommand{\todo}[1]{}
+\newcommand{\todo}[1]{}
 \newcommand{\maybe}[1]{}
+\newcommand{\resolved}[1]{}
 
@@
 % Mark up some work that we need to do in order for this paper to be telling the truth
-\newcommand{\todo}[1]{{\color{red} #1}\\}
+%\newcommand{\todo}[1]{{\color{red} #1}\\}
 
@@
 
-We describe a method for the automatic acquisition of a corpus of disputed claims from the web.
-We consider a claim to be disputed if a document on the web suggests that this claim is wrong and that other people on the web are suggesting that it is true.
+We present a method for the automatic acquisition of a corpus of disputed claims from the web.
+We consider a claim to be disputed if a page on the web suggests that this claim is wrong and that other people on the web are suggesting that it is true.
 
-\x{too much emphasis on {\em how}... rewrite following paragrapgh}
-Our tool extracts disputed claims by searching the web for templates such as ``falsely claimed that X'' or ``the myth that X'', and then analysing the parsed sentence structure to identify claims that seem to have the correct form.
-Given a set of known disputed claims, we can infer further templates by searching for other contexts in which known disputed claims appear.
+Our tool extracts disputed claims by searching the web for patterns such as ``falsely claimed that $X$'' and then using a statistical classifier to select text that appears to be making a disputed claim.
 
-We believe that our corpus of disputed claims could be useful for a wide range of applications related to information credibility on the web.
+We argue why such a corpus of dispupted claims is useful for a wide range of applications related to information credibility on the web, and we look at what our current corpus reveals about what is being disputed on the web.
+
+\resolved{too much emphasis on {\em how}... rewrite following paragrapgh}
 
@@
 
-The web contains a vast number of documents written by a vast number of people.
-In many cases, these people disagree with each other, and the documents they write contain conflicting information.
-For users to extract reliable information from the web, it is useful for them to be able to determine when different documents disagree about a topic.
+The web contains a vast number of pages written by a vast number of people.
+In many cases, these people disagree with each other, and the pages they write contain conflicting information.
+For users to extract reliable information from the web, it is useful for them to be able to determine when different sources disagree about a topic.
 
 In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web.
-We consider a claim to be {\it disputed} if some people believe both that others are making the claim, and that the claim is not true.
+We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and that there are others that are making the claim.
+We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.
 
-We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$''.
-For example, if a document contains the text ``the minconception that {\it the moon is made of cheese}'', this suggests that the author of the document believes both that the statement ``{\it the moon is made of cheese}'' is false, and that there are other authors who claim that ``{\it the moon is made of cheese}'' is true.
+We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}).
+For example, if a page contains the text ``the minconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim.
 In Figure~\ref{templates} we list some of the patterns we used.
-We then search the web for these patterns, process the text to extract the claims, thus creating a corpus of candidate claims.
-
-\todo{TODO: we need to use template mining to get a more complete list of the templates that are good.}
+In practice, many of the strings that match such a pattern are not well-formed disputed claims.
+We use a statistical classifier to filter out those strings that appear to make a well-formed claim.
 
 We believe that this corpus will be useful for many purposes.
-We are currently using it as part of our Dispute Finder~\cite{www-disputefinder} project to automatically highlight phrases on web pages that are disputed by other sources.
-We are also exploring other applications of this corpus, including visualization tools that let users see what is disputed about topics they are interested in, or what has been disputed at particular times.
+We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources.
+We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, and visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).
 
-We are making our corpus publicly available for other researchers to download.
-We plan to continue to update our corpus as new pages are added to the web, and to develop tools that allow people to query it in useful ways.
+We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}.
+In currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010.
+This amounts to approxmately 1.1 million strings that we believe are making disputed claims.
+We plan to expand our corpus as we crawl more of the web and improve our algorithms.
+
+By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particulary topical at particular times (Section~\ref{analysis}).
 
@@
 
-\todo{Need to put our data online somewhere so that others can download it.}
-
-In this paper, we describe in more detail the way that we built this corpus, we explain ways that we think this corpus could be used, and we describe some features that we found in our data.
-
-\x{Include graph showing process by which we import claims.}
-
 \section{Background and Related Work}
 
-\x{Information credibility is important.}
-\x{People are increasingly relying on the web for information.}
-\x{People read a wider range of sources that before, many of which they do not know whether to trust.}
+The problem of determining information credibility on the web is becoming increasingly important.
+In the past a user would typically obtain information from a relatively small set of sources such as books, TV channels, and radio stations.
+The user would have some idea of the reputation and biases of each of these sources, and publishing barriers and quality control would ensure that these sources only published information that met their standards.
+The web is very different.
+A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them.
+Moreover, the internet has little in the way of publishing barriers or quality control.
+If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.
 
-Information credibility on the web is becoming increasingly important.
-In the past people typically obtained information from a relatively small set of sources such as books, TV channels, and radio stations.
-Most of these sources had a known reputation, and had publishing barriers and quality control to ensure that the information they provided met the standards expected from that source.
-The web is very different.
-A user has access to a vast number of different sources, but a user will know the reputation of only a small subset of these.
-Moreover, the internet has little in the way of publishing barriers or quality control.
-If users are to extract trustworthy information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.
+There are several ways that a user can determine whether to trust information that they find on a web page.
+The user can check the reputation of the person or organization that wrote the web page; they can check whether the web page looks like a they think a reliable web page should look; or they can check whether the information is consistent with information available from other sources.
 
-\x{Cite Pew study on this? Cite other people talking about misinformation.}
-
-Given a document that contains information which may or may not be trustworthy, there are several ways that a reader can determine whether they should trust the information.
-They can check the reputation of the source; they can check whether it looks like a reliable document; or they can check whether the information in the document is consistent with information available from other sources.
-
-To check the reputation of a source, a user can use a web site such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources.
+A user can check the reputation of a source using a service such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources.
 Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy.
 Alternatively, a user can simply use a search engine such as Google to look for information about the source.
-While these tools can be very useful, trustworthy sources sometimes publish unreliable information.
-For example, a source may have been misled by an unreliable source they were using themselves.
-Moreover, a user may have a document from a source that is not known to be reliable, and still wish to know if the information itself is trustworthy.
+While these tools can be very useful, trustworthy sources sometimes publish unreliable information, and untrusted sources sometimes contain useful information.
+For example, a reliable source may have been misled by an unreliable source they were using themselves; or a small unrated blog may publish information that useful, insightful, and accurate.
 
 Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content.
-For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by analyzing its edit history.
+For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{Adler2008b} identifies potentially unreliable sections of an article by analyzing its edit history.
 Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos.
@@
 Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.
+These metrics do a good job at detecting pages that resemble pages that contain unreliable information, but they do not protect against authors who write untrustworthy information in the style of a trustworthy document.
 
@@
 We aim to inform users when information that they encounter is disputed by another source.
-We have built an extension to the Firefox web browser called Dispute Finder~\cite{www-disputefinder} that informs users when a web page that they are reading makes a claim that it knows to be disputed.
+We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed.
 For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
-In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims; however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
+In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
 
 Our primary motivation for automatically acquiring a large corpus of disputed claims is to use this corpus to enable tools like Dispute Finder to automatically inform users when they encounter information that this corpus says is disputed.
+However, as we discuss in Section~\ref{using}, we believe such a corpus could be useful for many other purposes too.
 
@@
 For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
-A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong.
-For example the text ``we disagree with the assertion that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''.
+A contradicted claim is not necessarily a disputed claim.
+In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese.
 A {\it contradiction} is logical, while a {\it dispute} is social.
@@
 Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding.
-de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction.
+de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions.
 AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
@@
 
-Detecting contradictions has proven to be a hard problem.
-Much of the difficulty comes from the fact that it typically requires deep semantic knowledge to determine whether two statements that look like they might be contradictory actually are.
-``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush.
+Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}.
+Much of the difficulty comes from the fact that one typically needs deep semantic knowledge to determine whether two statements that look like they might contradict each other actually do.
+For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush.
 ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England.
@@
 Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important.
-The advantage of looking for disputes rather than contradictions is that is is much easier - humans do the hard work of identifying contradictions and deciding whether they are important.
-\x{seems like we do this {\em only} because it's simpler...
-so perhaps add something around the fact there it's interesting to see where/how/when people disagree...
-some observation on the social aspects of dispute?}
-The disadvantage of looking for disputes is that this method will only identify contradictions that humans have already identified.
+One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important.
+If a page says ``Falsely claimed that George Bush is married to Barbara Bush'' then that suggests that the contradiction with ``George Bush is married to Laura Bush'' is likely to be genuine.
+The corresponding disadvantage is that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.
 
-\todo{Want some kind of numerical estimate of how many disputed claims we have. Maybe measure this by pair of unique nouns and verbs. Noun + verb or noun + noun = disputed claim?}
+Perhaps more importantly, for our purposes disputes are more interesting than contradictions.
+We are interested in the social side of dispute.
+We want to know who disagrees with who, why they disagree, and what they think is important.
 
-\maybe{Want to apply wikify to get nouns, and then use Chi-style category rules to find out what categories are disputed on the web?}
+Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}.
+Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects.
+A focal application has been the automatic summarisation of product reviews, to produce an overview of the product features that are viewed favorably or negatively.
+Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.
 
-This work is also  related to the NLP areas of opinion mining and/or sentiment analysis and textual entailment.
-Sentiment analysis aims to determine the attitude (usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}.
-Textual entailment is the task of deciding, given two text fragments, whether the meaning of one  text can be inferred from the other text 
-\x {add references and say why different}
-The methods we use are closely related to related work on information extraction which is the task of identifing and classifing specific semantic entities within documents (i.e.
-names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.
+\resolved{All merged?
+: The methods we use are closely related to related work on information extraction which is the task of identifing and classifing specific semantic entities within documents (i.e.
+names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.}
 
@@
 
-\x{Include a diagram showing the stages of our dispute finding process}
-\x{BR: I wouldn't... not very informative, I'd think}
-\maybe{Talk about theories of contrast???}
-\maybe{Look at Kehler 2002 on CONTRAST???}
+\begin{figure}[tb]
+\begin{center}
+  \begin{tabular}{|lll|}
+    \hline
+    {\bf Frequency$^*$} & {\bf Template} & {\bf Precision$^\dag$}\\ 
+    \hline
+        \multicolumn{3}{|c|}{\it Something that could be challenged}\\
+        570,000,000 & think that & 28\%\\
+        495,000,000 & believe that & 48\%\\
+        145,000,000 & idea that & 42\% \\
+        101,000,000 & claim that & 46\%\\
+       \hline
+       \multicolumn{3}{|c|}{\it Something others believe}\\
+        40,100,000 & claiming that & 39\% \\
+        30,600,000 & the belief that & \\
+        28,600,000 & believing that & \\
+        11,700,000 & who believe that &\\
+        8,400,000 & who think that &\\
+        \hline
+        \multicolumn{3}{|c|}{\it Something false}\\
+        5,790,000 & the myth that & 62\% \\
+        3,260,000 & into believing that & 52\% \\
+        1,690,000 & the lie that & 52\% \\
+        1,410,000 & it is not true that & 64\% \\
+        1,220,000 & the delusion that  & 54\%\\
+        1,140,000 & the misconception that & 67\%\\
+        995,000 & mistaken belief that &\\
+        676,000 & the mistaken belief that &\\
+        593,000 & mistakenly believe that &\\
+        583,000 & the fantasy that &\\
+        501,000 & it is not the case that &\\
+        459,000 & false claim that &\\
+        405,000 & the fallacy that &\\
+        351,000 & falsely claimed that &\\
+        264,000 & urban legend that &\\
+        250,000 & no longer believe that &\\
+        216,000 & the false belief that &\\
+        215,000 & falsely claiming that &\\ 
+        178,000 & falsely believe that &\\
+        171,000 & bogus claim that &\\
+        163,000 & erroneous belief that &\\
+        154,000 & the deception that &\\
+        147,000 & the misunderstanding that &\\
+        135,000 & urban myth that &\\
+    & & \\
+    \multicolumn{3}{|l|}{$^*$Yahoo's approximate estimate}\\
+    \multicolumn{3}{|l|}{$^\dag$Based on manual inspection of 100 text segments}\\
+    \multicolumn{3}{|l|}{\quad matched by each pattern}\\
+    \hline
+  \end{tabular}
+\end{center}
 
-%Figure~\ref{not-yet} shows the process we use to build our corpus of disputed claims.
+  \label{templates}
+  \caption{Patterns we use to find disputed claims}
+\end{figure}
 
 We implemented a three stage process to build our corpus of disputed claims, each described in the following Sections.
-We first create a set of lexical patterns (i.e.
-``the misconception that'' and ``it is not the case that'').
-We then search the Web for these patterns and finally process the text of the returned Web pages to extract only the parts that describe the disputed claims.
+We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}).
+We then search the Web for these patterns (Section~\ref{searchpattern}).
+Finally, we filter the resulting strings to give only those that resemble unambiguous disputed claims (Section~\ref{filterclaim}).
 
@@
 \subsection{Patterns for Finding Claims}
-\label{creatingpattern}
+\label{patterns}
+
+\x{Cite Snow on auto-finding new patterns. \cite{Snow2005}}
+\x{Cite Ritter on using stats to clean up results. ~\cite{Ritter2009}}
+\x{Cite MemeTracker~\cite{Backstrom2009}}
 
@@
 If two patterns appear in a corpus with similar text filling their slots, then it is likely that the patterns have similar meanings.
-DIRT~\cite{Lin2001} discovers inference rules such as (``$X$ is author of $Y$'' $\equv$ ``$X$ wrote $Y$'') by looking for patterns that have a similar distribution of text filling their slots.
+DIRT~\cite{Lin2001} discovers inference rules such as (``$X$ is author of $Y$'' $\equiv$ ``$X$ wrote $Y$'') by looking for patterns that have a similar distribution of text filling their slots.
 Pasca and Dienes~\cite{Pasca2005} detect paraphrases on the web by searching for text fragments that appear in similar contexts on web pages.
@@
 
-\begin{figure}[tb]
-\begin{center}
-  \begin{tabular}{|ll|}
-    \hline
-    {\bf Yahoo Count\footnotemark} & {\bf Template}\\ 
-    \hline
-        \multicolumn{2}{|c|}{\it Something that could be challenged}\\
-        570,000,000 & think that \\
-        495,000,000 & believe that \\
-        145,000,000 & idea that \\
-        101,000,000 & claim that \\
-       \hline
-       \multicolumn{2}{|c|}{\it Something others believe}\\
-        40,100,000 & claiming that \\
-        30,600,000 & the belief that \\
-        28,600,000 & believing that \\
-        11,700,000 & who believe that \\
-        8,400,000 & who think that \\
-        \hline
-        \multicolumn{2}{|c|}{\it Something false}\\
-        5,790,000 & the myth that \\
-        3,260,000 & into believing that \\
-        1,690,000 & the lie that \\
-        1,410,000 & it is not true that \\
-        1,220,000 & the delusion that \\
-        1,140,000 & the misconception that \\
-        995,000 & mistaken belief that \\
-        676,000 & the mistaken belief that \\
-        593,000 & mistakenly believe that \\
-        583,000 & the fantasy that \\
-        501,000 & it is not the case that \\
-        459,000 & false claim that \\
-        405,000 & the fallacy that \\
-        351,000 & falsely claimed that \\
-        264,000 & urban legend that \\
-        250,000 & no longer believe that \\
-        216,000 & the false belief that \\
-        215,000 & falsely claiming that \\ 
-        178,000 & falsely believe that \\
-        171,000 & bogus claim that \\
-        163,000 & erroneous belief that \\
-        154,000 & the deception that \\
-        147,000 & the misunderstanding that \\
-        135,000 & urban myth that \\
-    %    131,000 & wrongly believe that \\
-    %    126,000 & falsely claim that \\
-    %    109,000 & erroneously believe that \\
-    %    101,000 & falsely claims that \\
-    %    83,900 & incorrectly believe that \\
-    %    83,200 & no longer think that \\
-    %    82,400 & falsely stated that \\
-    %    79,200 & the absurd idea that \\
-    %    74,100 & the hoax that \\
-    %    41,500 & the deceit that \\
-    %    23,700 & incorrectly claimed that \\
-    %    21,900 & disagree with the claim that \\
-    %    15,900 & falsely suggests that \\
-    %    15,300 & disagree with the assertion that \\
-    %    14,200 & the fabrication that \\
-    %    9,640 & incorrectly claim that \\
-    %    2,110 & cast doubt on the claim that \\
-    %    2,080 & absurdity of the claim that \\
-    %    1,820 & false claim is that \\
-    %    1,750 & stupidly believe that \\
-    \hline
-  \end{tabular}
-  \label{templates}
-  \caption{Some of the templates that we use to search for disputed claims, and Yahoo's rough estimate of how many times each one appears on the web}
-\end{center}
-\end{figure}
-
 \subsection{Context}
@@
 \section{Using Disputed Claims}
+\label{using}
 
@@
 \section{Analysing the Data}
+\label{analysis}
+\input{analysis.tex}
 

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Minor edits

@@
 
-We argue why such a corpus of dispupted claims is useful for a wide range of applications related to information credibility on the web, and we look at what our current corpus reveals about what is being disputed on the web.
+We argue why such a corpus of disputed claims is useful for a wide range of applications related to information credibility on the web, and we look at what our current corpus reveals about what is being disputed on the web.
 
@@
 We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}).
-For example, if a page contains the text ``the minconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim.
+For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim.
 In Figure~\ref{templates} we list some of the patterns we used.
@@
 We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources.
-We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, and visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).
+We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).
 
 We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}.
-In currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010.
+It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010.
 This amounts to approxmately 1.1 million strings that we believe are making disputed claims.
@@
 There are several ways that a user can determine whether to trust information that they find on a web page.
-The user can check the reputation of the person or organization that wrote the web page; they can check whether the web page looks like a they think a reliable web page should look; or they can check whether the information is consistent with information available from other sources.
+The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page meets their aesthetic criteria for a reliable web page; or they can check whether the information is consistent with information available from other sources.
 
@@
 
-In our research, we are following the third approach.
+In our research, we are following a third approach.
 We aim to inform users when information that they encounter is disputed by another source.
@@
 Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding.
-de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions.
+De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions.
 AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
@@
 Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}.
-Much of the difficulty comes from the fact that one typically needs deep semantic knowledge to determine whether two statements that look like they might contradict each other actually do.
+Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do.
 For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush.
@@
 
-We implemented a three stage process to build our corpus of disputed claims, each described in the following Sections.
+We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections.
 We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}).
@@
 This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks.
-Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events.
+Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events.
 TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
@@
 
-In this work we simply start with an initial set of patterns that we wrote by hand.
-We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim.
+In this work we start with an initial set of manually crafted search patterns.
+We then identified additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim.
 From this set of candidate prefix patterns, we manually selected additional patterns.
@@
 ``there is a God'').
-If many people agree with a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed.
+If many people agree that a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed.
 
@@
 
-Since we are interested in the time information of the claims and we want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range.
+Since we are interested in the time information of the claims and we want to be able to incrementally update our corpus as new pages appear on the web without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range.
 The Yahoo BOSS API does not offer the ability to do so; we thus simulate this behaviour by instead including a literal date string in our queries.
@@
 This approach has false positives and false negatives.
-Some web pages include dates that are not the date the article was posted, and some web pages either don't include the date the article was posted, or write their date in a different format.
-Indeed our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
+Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format.
+We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
 
@@
 Consider for example the text chunks in Figure~\ref{filtered}.
-A chunk of text might not be a statement (case 1), it might include unbound referents such is ``it'', or ``they'' (case 2), or it might only make sense within the context of a particular document (case 3).
+A chunk of text might not be a statement (case 1), it might include unbound referents such is ``it'' or ``they'' (case 2), or it might only make sense within the context of a particular document (case 3).
 
@@
 Such agents could be trained with information regarding the books, journals, and news articles a user reads.
-It would then be able to alert the user when a previously-read source is now disputed.
+It would then be able to track these subjects and alert the user when a previously-read source is now disputed.
 It could also track a set of topics and tell the user when something new is disputed about a topic.
-A background dispute analysis agent would serve as an automated research assistant, alerting me when
+A background dispute analysis agent would thus serve as an automated research assistant.
 
 A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes.
-In this way the cultural
-
-Recognizing that these are but a few of the ways in which a disputed claim corpus could be used, we will release this data set to the research community as a whole.
-
-\x{"It will be available for unrestricted use under the XXX license. The dataset can be accessed at http://xxx.intel.com/xxx"}
+As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.
 
@@
 Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the array of views to be found online.
-
 Furthermore, because individuals express opinions freely online, a snapshot of the disputed claims online can provide valuable insights into the cultural zeitgeist of the time.

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Updated the text about filtering etc

--- 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
@@
 \newcommand{\note}[1]{}
-%\newcommand{\x}[1]{}
+\newcommand{\x}[1]{}
 \newcommand{\todo}[1]{}
@@
 % Mark up a point that we want to flesh out into more text
-\newcommand{\x}[1]{{\color{blue} #1}\\}
+%\newcommand{\x}[1]{{\color{blue} #1}\\}
 
@@
 \begin{center}
-  \begin{tabular}{|lll|}
+  \begin{tabular}{|llll|}
     \hline
-    {\bf Frequency$^*$} & {\bf Template} & {\bf Precision$^\dag$}\\ 
+    {\bf Frequency$^*$} & {\bf Template} & {\bf P$^\dag$} & {\bf A$^\ddag$}\\ 
     \hline
-        \multicolumn{3}{|c|}{\it Something that could be challenged}\\
-        570,000,000 & think that & 28\%\\
-        495,000,000 & believe that & 48\%\\
-        145,000,000 & idea that & 42\% \\
-        101,000,000 & claim that & 46\%\\
+        \multicolumn{4}{|c|}{\it Plausible to not believe it}\\
+        570,000,000 & think that & 28\%& 69\%\\
+        495,000,000 & believe that & 48\%& 65\%\\
+        145,000,000 & idea that & 42\% & 61\%\\
+        101,000,000 & claim that & 46\%& 72\%\\
        \hline
-       \multicolumn{3}{|c|}{\it Something others believe}\\
-        40,100,000 & claiming that & 39\% \\
-        30,600,000 & the belief that & \\
-        28,600,000 & believing that & \\
-        11,700,000 & who believe that &\\
-        8,400,000 & who think that &\\
+       \multicolumn{4}{|c|}{\it It is notable that others believe it}\\
+        40,100,000 & claiming that & 39\% &\\
+        30,600,000 & the belief that & &\\
+        28,600,000 & believing that & &\\
+        11,700,000 & who believe that &&\\
+        8,400,000 & who think that &&\\
         \hline
-        \multicolumn{3}{|c|}{\it Something false}\\
-        5,790,000 & the myth that & 62\% \\
-        3,260,000 & into believing that & 52\% \\
-        1,690,000 & the lie that & 52\% \\
-        1,410,000 & it is not true that & 64\% \\
-        1,220,000 & the delusion that  & 54\%\\
-        1,140,000 & the misconception that & 67\%\\
-        995,000 & mistaken belief that &\\
-        676,000 & the mistaken belief that &\\
-        593,000 & mistakenly believe that &\\
-        583,000 & the fantasy that &\\
-        501,000 & it is not the case that &\\
-        459,000 & false claim that &\\
-        405,000 & the fallacy that &\\
-        351,000 & falsely claimed that &\\
-        264,000 & urban legend that &\\
-        250,000 & no longer believe that &\\
-        216,000 & the false belief that &\\
-        215,000 & falsely claiming that &\\ 
-        178,000 & falsely believe that &\\
-        171,000 & bogus claim that &\\
-        163,000 & erroneous belief that &\\
-        154,000 & the deception that &\\
-        147,000 & the misunderstanding that &\\
-        135,000 & urban myth that &\\
-    & & \\
-    \multicolumn{3}{|l|}{$^*$Yahoo's approximate estimate}\\
-    \multicolumn{3}{|l|}{$^\dag$Based on manual inspection of 100 text segments}\\
-    \multicolumn{3}{|l|}{\quad matched by each pattern}\\
+        \multicolumn{4}{|c|}{\it Something false}\\
+        5,790,000 & the myth that & 62\% & 73\% \\
+        3,260,000 & into believing that & 52\% &72\% \\
+        1,690,000 & the lie that & 52\% & 76\% \\
+        1,410,000 & it is not true that & 64\% & 78\% \\
+        1,220,000 & the delusion that  & 54\% & 76\% \\
+        1,140,000 & the misconception that & 67\% & 81\% \\
+        676,000 & the mistaken belief that & 51\% & 74\%\\
+        593,000 & mistakenly believe that & &\\
+        583,000 & the fantasy that & &\\
+        501,000 & it is not the case that &&\\
+        459,000 & false claim that &&\\
+        405,000 & the fallacy that &&\\
+        351,000 & falsely claimed that &&\\
+        264,000 & urban legend that &&\\
+        250,000 & no longer believe that &&\\
+        216,000 & the false belief that &&\\
+        215,000 & falsely claiming that &&\\ 
+        178,000 & falsely believe that &&\\
+        171,000 & bogus claim that &&\\
+        163,000 & erroneous belief that & 58\% & 77\%\\
+        154,000 & the deception that &&\\
+        147,000 & the misunderstanding that &&\\
+        135,000 & urban myth that &&\\
+    & & &\\
+    \multicolumn{4}{|l|}{$^*$Yahoo's approximate estimate}\\
+    \multicolumn{4}{|l|}{$^\dag$ P = Pattern precision (Section~\ref{filterclaim})}\\
+    \multicolumn{4}{|l|}{$^\ddag$ A = Filter accuracy (Section~\ref{filterclaim})}\\
     \hline
@@
 
-\x{Cite Snow on auto-finding new patterns. \cite{Snow2005}}
-\x{Cite Ritter on using stats to clean up results. ~\cite{Ritter2009}}
-\x{Cite MemeTracker~\cite{Backstrom2009}}
-
-We hand crafted a set of {\bf XX} patterns that we hypothesize may  indicate that a claim is disputed, such as ``false claim that'' or or ``it is not true that.''
+We hand-crafted a set of {\bf 54} patterns that we hypothesize may indicate that a claim $S$ is disputed, such as ``false claim that $S$'' or or ``it is not true that $S$''.
+Figure~\ref{templates} shows some of the patterns we use.
 
 This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks.
-Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events.
+Hearst~\cite{Hearst1992} searched for patterns like ``$X$ such as $Y$'' to infer hyponyms, Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type, Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer metronyms.
 TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
-These methods differ on how {\bf finish here}
-\x{add more related work here}
-\todo{add more related work here}
 
-In this work we simply start with an initial set of patterns that we wrote by hand.
-We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim.
-From this set of candidate prefix patterns, we manually selected additional patterns.
+Like several previous authors~\cite{Girju2003,Snow2005} we identified new patterns by searching for known disputed claims.
+We searched for claims we knew to be disputed, recorded the text patterns that frequently surrounded them on web pages, and then manually chose those patterns that made sense to us.
 
-\x{add more related work on boostraping here, adding differences}
-\todo{add more related work here}
+\x{Talk about people who do this in a more automatic way?}
 
-We plan to work on more sophisticated algorithms for finding new patterns automatically in future work.
-
-Rather that searching for an arbitrary collection of known disputed claims, we found that we generated better templates by searching for claims that most documents disagee with (e.g.
-``eskimos have many words for snow'') rather than claims that many people agree with (e.g.
-``there is a God'').
-If many people agree with a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed.
-
-We also find that we get higher quality results if we limit ourselves to prefixes that begin with ``that''.
-For example, if we search for ``that eskimos have many words for snow'' then most prefixes we find do indeed indicate dispute, however if we just search for ``eskimos have many words for snow'' then we get a much lower hit rate.
-
-\x{not sure if to add what follow, posponing the decision for now}
-This approach is an example of the Distributional Hypothesis.
+%\x{not sure if to add what follow, posponing the decision for now}
+%This approach is an example of the Distributional Hypothesis.
 The distributional hypothesis, as originally framed~\cite{Harris1954,Systems2000}, theorised that words that appear in similar contexts have similar meanings.
@@
 
-Figure~\ref{templates} shows a subset of the {\bf xx} patterns  that we used. For each pattern, we show the number of times that Yahoo estimates that the pattern appears on the web. 
-\todo{add statistic of patterns and patterna accuracy here}
-\x{add statistic of patterns and patterna accuracy here}
+Figure~\ref{templates} shows a subset of the {\bf 54} patterns that we used. 
+For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern.
+The {\it precision} is an estimate of the proportion of text strings matched by the pattern that are unambiguous disputed claims.
+We discuss precision further in Section~\ref{filterclaim}.
 
-Not all patterns have exactly the same meaning. We divide patterns into three fuzzily-grouped categories:
+Not all patterns have exactly the same meaning. We grouped our patterns into three loose catagories, based on manual inspection of the pages that use them (Figure~\ref{templates}):
 
@@
  \item {\bf False:} The author believes the claim is wrong
- \item {\bf Believed by others:} The author believes others think this, and it is likely that the author disagrees.
+
+ \item {\bf Notable that others believe it:} The author believes that it is notable that others believe it.
+For example ``Fans are claiming that {\it Elvis is alive}''.
 Further inspection is required to determine whether the author disagrees with the claim.
- \item {\bf Could be challenged:} The author feels the need to state that someone believes something, which suggests that this is something that one might not believe.
-For example, if an author says ``I think America is a great place'' this doesn't suggest that the claim is false, but the mere fact that they declared that they thought that suggests that they are aware that the claim could be challenged.
+For example, do they follow it with a word like ``but'' or ``despite''?
+
+ \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it it plausible that someone else might not believe it.
+This is only subtly different from the previous group.
+For example ``Fans think that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''.
+It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims.
+For example ``John thinks Elvis is dead'' implies much more skepticism than ``I think Elvis is dead''.
  \end{itemize}
-
-We grouped patterns into categories by hand, based on a brief inspection of pages that were using each of the patterns.
 
@@
 If however one just wishes to see what things people think are worthy of having opinions expressed about, then the full set is useful.
-\todo{Give some stats about our patterns}
 
@@
 
-We then search the web for the set of patterns described in the previous session.
-Rather than building our own search engine, we use the Yahoo BOSS search API~\cite{yahoo-boss}.
-We search Yahoo BOSS for a raw string such as ``the misconception that'' and then download every web page that Yahoo lists in its search results.
+We use the Yahoo BOSS API~\cite{yahoo-boss} to search for occurrences of our patterns on the web.
+Using Yahoo BOSS allows us to search for patterns on a vast number of web pages, without having to build our own search engine.
+We search Yahoo BOSS for a raw string such as ``the misconception that'', download every page that Yahoo lists in its search results, and then look for text that matches any of our known patterns.
+
 Since we are using an existing search engine, we are limited to searching for simple text strings.
-This leads us to generate multiple patterns that are almost the same, other than for synonyms.
-E.g.
-``the lie that'' vs ``the deceit that''.
+This requires us to generate multiple patterns that are almost the same, other than for synonyms, for example we have both ``the lie that'' vs ``the deceit that''.
 We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix.
 For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence.
-While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, this would be inefficient, since many pages would not contain the pattern.
 
-In the longer term we would like to have a more elegant search infrastructure, but for the time being this approach seems to work reasonably well.
+In the longer term we may work round these issues by building our own search infrastructure, but Yahoo BOSS provides an excellent platform for prototyping an idea and seeing if it works.
 
-Since we are interested in the time information of the claims and we want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range.
-The Yahoo BOSS API does not offer the ability to do so; we thus simulate this behaviour by instead including a literal date string in our queries.
-For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.
+It is useful to be able to update our corpus as new pages appear on the web, without having to repeatedly download the same pages.
+The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range.
+We instead simulate this behaviour by including a literal date string in the queries we pass to Yahoo BOSS.
+For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.
 
@@
 
+Including the date in the search also provides us with a light-weight way to sample what people believed or disputed at particular points in time Section~\ref{timetrends}.
+Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g.
+Elvis was alive in the past, but isn't not).
+
 \todo{Produce some kind of measure of how well date searching actually works}
@@
 
-\subsection{Filtering Statements}
+\subsection{Filtering Claims}
 \label{filterclaim}
+
+Searching the web for our patterns yields a collection of strings.
+From this collection, we want to filter out any strings that are not making a falsifiable claim, and any strings that make a claim that is ambiguous.
+
+Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out.
+a chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might by ambiguous what entities it is referring to (case 3).
+
+The {\it P} column in Figure~\ref{templates} shows the percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims.
+We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambigous.
+
+Whether a claim is unambiguous can be highly subjective.
+For example, in the string ``Obama is the president'' it is possible that ``Obama'' is referring to someone other than ``Barack Obama'' and ``the president'' is referring to a position other than ``President of the United States''.
+When manually judging claims, we considered a claim to be unambiguous if an average person would be pretty sure what the claim meant without knowing its context.
+
+We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim.
+We used a simple Bayesian classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.
+
+The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim.
+
+(Section~\ref{filterclaim}).
+We estimated the precision of each pattern by randomly selectiong 100 strings that match the pattern, and then manually marked strings that we subjectively decided were a well formed and unambiguous statement.
+
+\x{Cite Ritter on using stats to clean up results. ~\cite{Ritter2009}}
 
@@
 
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=16cm]{images/2by5.pdf}
+	\caption{Frequency of each of the top nouns individually}
+	\label{multiplot_nouns}
+	\end{center}
+\end{figure*}
+
 \section{Using Disputed Claims}
@@
 
+\x{Cite MemeTracker~\cite{Backstrom2009}}
+
 \todo{Lots of pretty graphs showing what our data is like.}
@@
 \x{Evaluate the quality of the clusters that we created.}
-\x{Evaluate the quality of the different individual templates - which ones have the highest quality claims.}
+\x{Evaluate the quality of the different individual patterns - which ones have the highest quality claims.}
 \x{say something about {\em duplicate} claims?}

### 2010-02-01 web_claim_finder/classify_good.py

@@ -101,17 +101,42 @@ def get_training_data(phrases):
 				human_marked.append((claim,False))
 	random.shuffle(human_marked)
 	return human_marked
-	
+
 def get_featured_data(phrases):
 	annotated = get_training_data(phrases)
 	featuresets = [(features(claim),g) for (claim,g) in annotated]
+	return featuresets
+	
+def get_featured_data_split(phrases):
+	featuresets = get_featured_data(phrases)
 	length = len(featuresets)
 	splitpoint = int(length * 0.8)
 	train_set,test_set = featuresets[:splitpoint],featuresets[splitpoint:]
 	return (train_set,test_set)
 	
+def real_phrases(phrases):
+	return [phrase for phrase in phrases if os.path.exists("../training/"+phrase.replace(" ","_")+".manual_good")]
+	
+def measure_phrases(phrases):
+	phrases	= real_phrases(phrases)
+	features = {}
+	print " --- accuracy --- "
+	for phrase in phrases:
+		print "features: "+phrase
+		features[phrase] = get_featured_data([phrase])	
+	for phrase in phrases:
+		print "--",phrase,"--"
+		test_set = features[phrase]
+		train_set = []
+		for otherphrase in phrases:
+			if otherphrase != phrase:
+				train_set = train_set + features[otherphrase] 
+		classifier = nltk.NaiveBayesClassifier.train(train_set)		
+		accuracy = nltk.classify.accuracy(classifier,test_set)
+		print phrase,"&",str(int(100*accuracy)) +"\%"	
+	
 def test_classifier(phrases):
-	(train_set,test_set) = get_featured_data()
+	(train_set,test_set) = get_featured_data_split()
 	classifier = nltk.NaiveBayesClassifier.train(train_set)	
 	print "accuracy = "+nltk.classify.accuracy(classifier,test_set)
 	
@@ -120,3 +145,7 @@ def test_classifier_all():
 
 def test_classifier_good():
 	test_classifier(cf.goodphrases)
+
+if __name__ == '__main__':
+	measure_phrases(cf.bad_phrases)
+

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex

@@
 This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks.
+Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events.
+TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
+These methods differ on how {\bf finish here}
+\x{add more related work here}
+\todo{add more related work here}
+
+In this work we start with an initial set of manually crafted search patterns.
+We then identified additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim.
+From this set of candidate prefix patterns, we manually selected additional patterns.
+
+This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks.
 Hearst~\cite{Hearst1992} searched for patterns like ``$X$ such as $Y$'' to infer hyponyms, Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type, Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer metronyms.
@@
 We searched for claims we knew to be disputed, recorded the text patterns that frequently surrounded them on web pages, and then manually chose those patterns that made sense to us.
-
-\x{Talk about people who do this in a more automatic way?}
-
-%\x{not sure if to add what follow, posponing the decision for now}
-%This approach is an example of the Distributional Hypothesis.
-The distributional hypothesis, as originally framed~\cite{Harris1954,Systems2000}, theorised that words that appear in similar contexts have similar meanings.
-This has more recently been extended to patterns.
-If two patterns appear in a corpus with similar text filling their slots, then it is likely that the patterns have similar meanings.
-DIRT~\cite{Lin2001} discovers inference rules such as (``$X$ is author of $Y$'' $\equiv$ ``$X$ wrote $Y$'') by looking for patterns that have a similar distribution of text filling their slots.
-Pasca and Dienes~\cite{Pasca2005} detect paraphrases on the web by searching for text fragments that appear in similar contexts on web pages.
 

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Finished pass over the method section. Now just analysis to go

@@
     \hline
-    {\bf Frequency$^*$} & {\bf Template} & {\bf P$^\dag$} & {\bf A$^\ddag$}\\ 
+    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
+    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
     \hline
-        \multicolumn{4}{|c|}{\it Plausible to not believe it}\\
+        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
+	    & & &\\
+
         570,000,000 & think that & 28\%& 69\%\\
@@
        \hline
-       \multicolumn{4}{|c|}{\it It is notable that others believe it}\\
+       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
+           & & &\\
+
         40,100,000 & claiming that & 39\% &\\
@@
         \hline
-        \multicolumn{4}{|c|}{\it Something false}\\
+        \multicolumn{2}{|l}{\it Something false} & &\\
+	    & & &\\
+
         5,790,000 & the myth that & 62\% & 73\% \\
@@
         676,000 & the mistaken belief that & 51\% & 74\%\\
-        593,000 & mistakenly believe that & &\\
-        583,000 & the fantasy that & &\\
-        501,000 & it is not the case that &&\\
-        459,000 & false claim that &&\\
-        405,000 & the fallacy that &&\\
-        351,000 & falsely claimed that &&\\
-        264,000 & urban legend that &&\\
-        250,000 & no longer believe that &&\\
-        216,000 & the false belief that &&\\
-        215,000 & falsely claiming that &&\\ 
-        178,000 & falsely believe that &&\\
-        171,000 & bogus claim that &&\\
-        163,000 & erroneous belief that & 58\% & 77\%\\
-        154,000 & the deception that &&\\
-        147,000 & the misunderstanding that &&\\
-        135,000 & urban myth that &&\\
+%         593,000 & mistakenly believe that & &\\
+%         583,000 & the fantasy that & &\\
+%         501,000 & it is not the case that &&\\
+%         459,000 & false claim that &&\\
+%         405,000 & the fallacy that &&\\
+%         351,000 & falsely claimed that &&\\
+%         264,000 & urban legend that &&\\
+%         250,000 & no longer believe that &&\\
+%         216,000 & the false belief that &&\\
+%         215,000 & falsely claiming that &&\\ 
+%         178,000 & falsely believe that &&\\
+%         171,000 & bogus claim that &&\\
+%         163,000 & erroneous belief that & 58\% & 77\%\\
+%         154,000 & the deception that &&\\
+%         147,000 & the misunderstanding that &&\\
+%         135,000 & urban myth that &&\\
     & & &\\
     \multicolumn{4}{|l|}{$^*$Yahoo's approximate estimate}\\
-    \multicolumn{4}{|l|}{$^\dag$ P = Pattern precision (Section~\ref{filterclaim})}\\
-    \multicolumn{4}{|l|}{$^\ddag$ A = Filter accuracy (Section~\ref{filterclaim})}\\
     \hline
@@
   \label{templates}
-  \caption{Patterns we use to find disputed claims}
+  \caption{Some of the patterns we use to find disputed claims}
 \end{figure}
@@
 
-Not all patterns have exactly the same meaning. We grouped our patterns into three loose catagories, based on manual inspection of the pages that use them (Figure~\ref{templates}):
+Not all patterns have exactly the same meaning. We grouped our patterns into three loose group, based on manual inspection of the pages that use them (Figure~\ref{templates}):
 
@@
 
-Which patterns one should use depends on what one wishes to use the resulting corpus of disputed claims for.
+Which pattern group one should use depends on what one wishes to use the resulting corpus of disputed claims for.
 If one wants to only have claims for which we can present web pages that argue that the claim is false, then only the first set of patterns should be used.
@@
 The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim.
+In each case, we trained the classifier on the data set for the other patterns in the same group and then tested its performance on the result for that pattern.
 
-(Section~\ref{filterclaim}).
-We estimated the precision of each pattern by randomly selectiong 100 strings that match the pattern, and then manually marked strings that we subjectively decided were a well formed and unambiguous statement.
+We can observe that the patterns in the ``something false'' group perform much better than the patterns in ``plausible to not believe it'' group, but the ``plausible to not believe it'' group has a lot more hits.
 
-\x{Cite Ritter on using stats to clean up results. ~\cite{Ritter2009}}
-
-From the web pages returned from the search, we form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g.
-'.','?','!',\texttt{</p>},\texttt{</h1>}, etc).
-
-\x{it would be quite important to give a sense on the accuracy --precision - of the claims extracted.
-you can calculated this from a subset of returned candidate claims: out of, say, 100, how many were actually claims?}
-
-Not every chunk of text identified by one of our patterns is a well-formed disputed claim.
-Consider for example the text chunks in Figure~\ref{filtered}.
-A chunk of text might not be a statement (case 1), it might include unbound referents such is ``it'' or ``they'' (case 2), or it might only make sense within the context of a particular document (case 3).
-
-We use a simple filter that looks for cases 1 and 2, but does not yet deal with case 3.
-We use the part-of-speech tagger from NLTK~\cite{nltk}, and then use a simple regexp parser to apply a series of simple rules.
-
-\begin{enumerate}
-\item To ensure that the text represent a real statement (case 1) we accept only text that contains either two noun phrases (e.g.
-``{\it George Bush} is from {\it Texas}''), or a noun phrase and an adjective (e.g.
-``{\it Cocaine} is {\it addictive}'').
-We do not accept text that contains merely a noun and a verb (e.g.
-``{\it Federal laws} do not {\it apply}'') since manual inspection of our data set suggests that in such phrases the verb typically refers to a noun that is defined outside the statement itself.
-
-\item We also discard any statement that contains a personal pronoun such as ``he'', ``she'', ``it'', or ``they'' unless it is proceeded by a noun (addressing case 2).
-We allow a personal pronoun after a noun, since manual inspection suggests that in most cases the personal pronoun refers to the noun, for example ``Bill Clinton said he wants to slow down the economy''.
-While we could in theory resolve other references, this is known to be a hard problem, and we have access to a large enough set of candidate claims that we can afford to throw away claims that are not easy for us to process.
-
-\item In some cases a disputed claim will be followed by information about where the claim was made, or why the claim is wrong.
+In some cases a disputed claim will be followed by information about where the claim was made, or why the claim is wrong.
 For example ``he claimed that the moon was made of cheese {\it on his show}'' or ``he claimed that the moon is made of cheese {\it despite contrary evidence}''.
-We chop off such suffixes by discarding any text that follows a word such as ``despite'', ``however'', ``but'', or ``was''.
-\end{enumerate}
-
-These rules were crafted by hand, based on trial and error and manual inspection of a relatively small number of claims.
-In the future we would like to use a more rigorous statistical method to produce more sophisticated rules for selecting high quality disputed claims, guided by a larger hand-annotated data set.
-We are also considering adopting an external framework such as TextRunner~\cite{Etzioni2008,Banko2008}.
-\todo{add related work here}
-
-\todo{Need a rough evaluation of what proportion of claims get thrown away by each rule, and how accurate these rules are.}
+We chop off such suffixes by discarding any text that follows a word such as ``despite'', ``however'', ``but'', or ``was'', provided that word was proceeded by either two noun phrases or a noun phrase and an adjective.
 

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
More changes

@@
 
+\begin{figure}
+ \begin{center}
+  \begin{tabular}{|llll|}
+\hline
+accuracy      & {\bf \#}    &  {\bf \%}  & {\bf   cum} \\
+      \hline
+dead on & 16   &   32\%  &   32\% \\
++/-10 d & 9    &   18\%  &   50\% \\
++/-30 d & 12   &   24\%  &   74\% \\
++/-90 d & 3    &   6\%   &   80\% \\
++/-1 yr & 6    &   12\%  &   92\% \\ 
+>1 yr   & 4    &   8\%   &   100\% \\ 
+\hline
+  \end{tabular}
+ \end{center}
+
+ \label{dateaccuracy}
+ \caption{Accuracy of simple date detection}
+\end{figure}
+
 We use the Yahoo BOSS API~\cite{yahoo-boss} to search for occurrences of our patterns on the web.
@@
 We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
+Despite being very primitive, this method seems to work reasonably well.
+When we manually inspected 50 pages retreived by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).
 
-Including the date in the search also provides us with a light-weight way to sample what people believed or disputed at particular points in time Section~\ref{timetrends}.
+Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends Section~\ref{timetrends}.
 Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g.
@@
 We can observe that the patterns in the ``something false'' group perform much better than the patterns in ``plausible to not believe it'' group, but the ``plausible to not believe it'' group has a lot more hits.
+For the best patterns our classifier has accuracy in the high seventies.
+
+Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambigous.
+This is not surprising.
+We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambigous.
 
@@
 
-\x{Importance of dates}
-\x{Work meaning depending on surrounding text}
-\x{We do not yet do anything useful with context, but we believe it is important and intend to use it}
-\x{context can be surrounding text but also features of the web pages -- domain,  "authority," in-links, format; context is also the author: expert? social info on author...}
+We save the surrounding text, page title, and URL for each of the disputed claims we see made on the web.
+At present we do not do anything with this data, but we anticipate that it could be useful for many purposes.
+For example it may be possible to resolve the meaning of ambiguous words or entities based on the words nearby (with have experimented with an algorithm similar to that used by Wikify~\cite{Mihalcea2007}).
+It is also useful to what person wrote the page, what organization hosted the page, who they link to, what meme-like phrases they make near to the claim, whether the page is written in an ``expert'' style, etc.
 
@@
 
+We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010.
+This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambigous disputable claims.
+Of those 1.1 million text strings, most are repeating claims made elsewhere in the data set.
+
 \x{Cite MemeTracker~\cite{Backstrom2009}}
@@
 \subsection{Trends over time}
+\label{timetrends}
+
+Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years.
+We obtained these figures by using a part-of-speech tagger to identify nouns in claims found on January 10th of every year from 2000 to 2010.
+Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}).
+We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns.
+All graphs are plotted on the same scale.
+The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made.
+
+We manually inspected our claims to determine what was going on that made particular nouns spike at particular times.
+
+\begin{itemize}
+ \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention.
+His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
+ \item {\bf God:} God is always a controversial topic.
+We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawins2006} seems to have sparked extra controversy.
+ \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
+\end{itemize}
 

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
More changes

@@
 We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim.
-We used a simple Bayesian classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.
+We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.
 

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Added text discussing time trends

@@
 	\begin{center}
-	\includegraphics[width=16cm]{images/2by5.pdf}
+	\includegraphics[width=18cm]{images/2by5.pdf}
 	\caption{Frequency of each of the top nouns individually}
@@
 
-\x{Cite MemeTracker~\cite{Backstrom2009}}
-
-\todo{Lots of pretty graphs showing what our data is like.}
-
-\subsection{Data Quality}
-
-\x{Look at a random sample of the data and say how clean it is.}
-\x{Evaluate the quality of the claims that we extracted.}
-\x{Evaluate the quality of the clusters that we created.}
-\x{Evaluate the quality of the different individual patterns - which ones have the highest quality claims.}
-\x{say something about {\em duplicate} claims?}
-
 \subsection{Trends over time}
@@
 The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made.
+It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even the nouns prove to be quite interesting.
 
-We manually inspected our claims to determine what was going on that made particular nouns spike at particular times.
+We manually inspected our claims to determine what was going on that made particular nouns spike at particular times:
 
@@
  \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
+ \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
 \end{itemize}
+
+MemeTracker~\cite{Backstrom2009} produced vaguely similar graphs, showing when particular memes were widely discussed on the web.
+They tracked highly repeated phrases, rather than nouns used in disputed claims.
 

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Added co-occurrence stats, which I will now remove in favor of clusters

@@
 
+\subsection{Co-Occurring Nouns}
+\label{pairs}
+
+\begin{figure}
+ \begin{tabular}{|ll|}
+ \hline
+ {\bf Noun} & {\bf Co-Occurring Nouns} \\
+ \hline
+{\bf obama} & president, election, health, muslim, america, interests,\\
+            & care, peace, year, country, right, states, plan, palicies,\\
+	    & U.S., bill, citizen, prize, democrats, policy, kenya \\
+\hline
+{\bf god}   & jesus, man, word, life, world, son, christ, universe \\  
+\hline
+{\bf iraq}  & war, weapons, destruction, mass, states, afghanistan, \\
+            & saddam, bush, hussein, invasion, forces, uranium \\
+ \hline
+ \end{tabular}
+\label{fig-pairs}
+\caption{The most common co-occurring nouns}
+\end{figure}
+
 \x{Named entity recognition}

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Added cluster data

--- 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
@@
 
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=18cm]{images/2by5.pdf}
+	\caption{Frequency of each of the top nouns individually}
+	\label{multiplot_nouns}
+	\end{center}
+\end{figure*}
+
 Searching the web for our patterns yields a collection of strings.
@@
 It is also useful to what person wrote the page, what organization hosted the page, who they link to, what meme-like phrases they make near to the claim, whether the page is written in an ``expert'' style, etc.
-
-\begin{figure*}[tb]
-	\begin{center}
-	\includegraphics[width=18cm]{images/2by5.pdf}
-	\caption{Frequency of each of the top nouns individually}
-	\label{multiplot_nouns}
-	\end{center}
-\end{figure*}
 
@@
 
+\begin{figure}[tbh]
+ \begin{center}
+  \begin{tabular}{|lll|}
+    \hline
+    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
+    \hline
+   {\bf children} & tiger woods abused & 218\\
+                  & instead encourage daily & 178\\
+    \hline
+   {\bf god} & daily encourage parents & 150 \\
+   \hline
+   {\bf government} & health care & 1267 \\
+                    & united states & 427 \\
+		    & relation environmental matters & 155 \\
+   \hline
+   {\bf iraq} & weapons mass destruction & 373 \\
+              & united states & 247 \\
+	      & saddam hussein & 192 \\
+	      & al qaeda & 149 \\
+   \hline
+   {\bf israel} & middle east & 251 \\
+		& allowed upon population & 128 \\
+                & united states & 107 \\
+		& off map & 106 \\
+   \hline
+   {\bf law}    & lawbreaker rather broken & 133 \\
+		& united states &\\
+   \hline
+    {\bf obama} & working best interests & 568\\
+                & health care & 481\\
+	        & united states & 327 \\
+		& nobel prize & 270 \\
+		& legitimately president & 207 \\
+		& ford hood shooter hasan nidal advised & 190 \\
+		& birth certificate & 180\\
+   \hline
+   {\bf president} & united states & 439 \\
+                   & health care & 203 \\
+		   & george w & 164 \\
+		   & aircraft system jolting bombing & 159 \\
+		   & peace prize & 125 \\
+		   & white house & 125 \\
+   \hline
+      {\bf war} & united states & 340 \\
+   \hline
+
+   {\bf women} & stay home & 183 \\
+               & save vaccine & 85 \\
+   \hline
+  \end{tabular}
+ \end{center}
+ \label{cluster-figure}
+ \caption{Largest word clusters found for nouns}
+\end{figure}
+
+\subsection{Clusters}
+\label{clusters}
+
+For each noun, we analysed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed.
+Rather than clustering claims directly, we instead cluster together words that frequently co-occur.
+We used an agglomerative clustering algorithm, repeatedly merging the two clusters of words that had the most claims in common.
+
 \x{Named entity recognition}

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Added text to accompany cluster data

@@
 
-Dispute Finder is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages.
+Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages.
 Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications.
@@
 
-\x{Named entity recognition}
-
-\x{Look at what noun phrases were most disputed at particular years.}
-\x{Look at what noun phrases were most disputed on particular days.}
-
-\x{We remove exact-match strings from the same domain - to avoid republishing of same article.}
+Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun.
+Most of these will make sense to people who have been following news in the united states.
+For example, we see that disputed claims about Obama often talk about his nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized).
+Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.
 

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Folded in more changes from Barbara

@@
 	    & & &\\
-
-        570,000,000 & think that & 28\%& 69\%\\
         495,000,000 & believe that & 48\%& 65\%\\
-        145,000,000 & idea that & 42\% & 61\%\\
         101,000,000 & claim that & 46\%& 72\%\\
@@
 This is only subtly different from the previous group.
-For example ``Fans think that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''.
+For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''.
 It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims.
@@
 We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim.
+This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification).
+Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}).
 We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.
@@
 The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim.
-In each case, we trained the classifier on the data set for the other patterns in the same group and then tested its performance on the result for that pattern.
+To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g.
+62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus, the pattern precision (e.g.
+52\% for ``believe that'').
 
@@
  \item {\bf God:} God is always a controversial topic.
-We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawins2006} seems to have sparked extra controversy.
+We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006} seems to have sparked extra controversy.
  \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Spellcheck and minor tweaks

@@
 
-\resolved{too much emphasis on {\em how}... rewrite following paragrapgh}
+\resolved{too much emphasis on {\em how}... rewrite following paragraph}
 
@@
 We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources.
-We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).
+We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).
 
@@
 It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010.
-This amounts to approxmately 1.1 million strings that we believe are making disputed claims.
+This amounts to approximately 1.1 million strings that we believe are making disputed claims.
 We plan to expand our corpus as we crawl more of the web and improve our algorithms.
 
-By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particulary topical at particular times (Section~\ref{analysis}).
+By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particularly topical at particular times (Section~\ref{analysis}).
 
@@
 A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them.
-Moreover, the internet has little in the way of publishing barriers or quality control.
+Moreover, the Internet has little in the way of publishing barriers or quality control.
 If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.
@@
 Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects.
-A focal application has been the automatic summarisation of product reviews, to produce an overview of the product features that are viewed favorably or negatively.
+A focal application has been the automatic summarization of product reviews, to produce an overview of the product features that are viewed favorably or negatively.
 Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.
@@
 \resolved{All merged?
-: The methods we use are closely related to related work on information extraction which is the task of identifing and classifing specific semantic entities within documents (i.e.
+: The methods we use are closely related to related work on information extraction which is the task of identifying and classifying specific semantic entities within documents (i.e.
 names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.}
@@
 The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range.
-We instead simulate this behaviour by including a literal date string in the queries we pass to Yahoo BOSS.
+We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS.
 For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.
@@
 Despite being very primitive, this method seems to work reasonably well.
-When we manually inspected 50 pages retreived by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).
+When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).
 
@@
 The {\it P} column in Figure~\ref{templates} shows the percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims.
-We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambigous.
+We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.
 
@@
 
-We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim.
+We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim.
 This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification).
@@
 
-Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambigous.
+Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambiguous.
 This is not surprising.
-We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambigous.
+We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambiguous.
 
@@
 
-\section{Analysing the Data}
+\section{Analyzing the Data}
 \label{analysis}
@@
 We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010.
-This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambigous disputable claims.
+This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims.
 Of those 1.1 million text strings, most are repeating claims made elsewhere in the data set.
@@
 
-MemeTracker~\cite{Backstrom2009} produced vaguely similar graphs, showing when particular memes were widely discussed on the web.
+These graphs resemble those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web.
 They tracked highly repeated phrases, rather than nouns used in disputed claims.
@@
 
-For each noun, we analysed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed.
+For each noun, we analyzed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed.
 Rather than clustering claims directly, we instead cluster together words that frequently co-occur.
@@
 Most of these will make sense to people who have been following news in the united states.
-For example, we see that disputed claims about Obama often talk about his nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized).
+For example, we see that disputed claims about Obama often talk about his Nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized).
 Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Folded in John Mark's changes

@@
        \affaddr{Santa Clara, CA, USA}\\
-       \email{john.m.agosta@intel.com}
+       \email{barbara.rosario@intel.com}
 }
@@
 We argue why such a corpus of disputed claims is useful for a wide range of applications related to information credibility on the web, and we look at what our current corpus reveals about what is being disputed on the web.
-
-\resolved{too much emphasis on {\em how}... rewrite following paragraph}
 
@@
 In many cases, these people disagree with each other, and the pages they write contain conflicting information.
-For users to extract reliable information from the web, it is useful for them to be able to determine when different sources disagree about a topic.
+For users to extract reliable information from the web, it is important that they be able to determine the credibility of the information that they read.
+One way to determine whether information is credible is to check whether it is disputed by other sources.
 
 In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web.
-We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and that there are others that are making the claim.
+We use the word {\it claim} to mean a statement of opinion or fact contained in the text of a web page.
+We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and also that there are others that are making the claim.
 We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.
 
-We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}).
+We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}).
 For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim.
@@
 In practice, many of the strings that match such a pattern are not well-formed disputed claims.
-We use a statistical classifier to filter out those strings that appear to make a well-formed claim.
+We use a statistical classifier to select only those strings that appear to make a well-formed claim.
 
-We believe that this corpus will be useful for many purposes.
+We believe that this corpus or disputed claims will be useful for many purposes.
 We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources.
@@
 There are several ways that a user can determine whether to trust information that they find on a web page.
-The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page meets their aesthetic criteria for a reliable web page; or they can check whether the information is consistent with information available from other sources.
+The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page looks how they expect a credible source to look; or they can check whether the information is consistent with information available from other sources.
 
@@
 Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy.
-Alternatively, a user can simply use a search engine such as Google to look for information about the source.
+Alternatively, a user can simply use a search engine such as Google to look for information about the source's reputation.
 While these tools can be very useful, trustworthy sources sometimes publish unreliable information, and untrusted sources sometimes contain useful information.
-For example, a reliable source may have been misled by an unreliable source they were using themselves; or a small unrated blog may publish information that useful, insightful, and accurate.
+For example, a reliable source may have been misled by an unreliable source they were using themselves; or a small unrated blog may publish information that is useful, insightful, and accurate.
 
@@
 For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
-A contradicted claim is not necessarily a disputed claim.
+But a contradicted claim is not necessarily a disputed claim.
 In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese.
@@
 Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do.
+Two instances of the same phrase may have the same sense, but a different reference, or two different phrases may refer to the same thing. 
 For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush.
@@
 ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.
+``The company is not going bust'' does not contract ``the company is doing great'' if the statements are about different companies.
 
 We detect disputes rather than contradictions.
-Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important.
+Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important.
 One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important.
-If a page says ``Falsely claimed that George Bush is married to Barbara Bush'' then that suggests that the contradiction with ``George Bush is married to Laura Bush'' is likely to be genuine.
-The corresponding disadvantage is that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.
+If a page says ``Falsely claimed that Obama is a Muslim'' then that suggests that the contradiction with ``Obama is a Muslim'' is likely to be genuine.
+The corresponding disadvantage would be that if one looks for disputes, one would only detect contradictions that humans have found and believe are important.
 
@@
 We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}).
-We then search the Web for these patterns (Section~\ref{searchpattern}).
-Finally, we filter the resulting strings to give only those that resemble unambiguous disputed claims (Section~\ref{filterclaim}).
+We then search the Web for these patterns (Section~\ref{searchpattern}) to collect sentences that contain the pattern, followed by some other string.
+Finally, we filter the resulting strings to give only those that resemble unambiguous falsifiable claims (Section~\ref{filterclaim}).
 
@@
 TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
-These methods differ on how {\bf finish here}
-\x{add more related work here}
-\todo{add more related work here}
 
@@
 
-Figure~\ref{templates} shows a subset of the {\bf 54} patterns that we used. 
-For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern.
-The {\it precision} is an estimate of the proportion of text strings matched by the pattern that are unambiguous disputed claims.
-We discuss precision further in Section~\ref{filterclaim}.
+\input{modals}
 
-Not all patterns have exactly the same meaning. We grouped our patterns into three loose group, based on manual inspection of the pages that use them (Figure~\ref{templates}):
+Not all patterns have exactly the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates}):
 
@@
 
- \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it it plausible that someone else might not believe it.
+ \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it is plausible that someone else might not believe it.
 This is only subtly different from the previous group.
@@
 It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims.
-For example ``John thinks Elvis is dead'' implies much more skepticism than ``I think Elvis is dead''.
+For example ``Some believe that Elvis is dead'' implies much more skepticism than ``I believe Elvis is dead''.
  \end{itemize}
@@
 If however one just wishes to see what things people think are worthy of having opinions expressed about, then the full set is useful.
+
+Figure~\ref{templates} shows a subset of the {\bf 54} patterns that we used. 
+For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern.
+The {\it precision} is an estimate of the proportion of text strings matched by the pattern that are unambiguous disputed claims.
+We discuss precision further in Section~\ref{filterclaim}.
 
@@
 Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out.
-a chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might by ambiguous what entities it is referring to (case 3).
+A chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).
 
-The {\it P} column in Figure~\ref{templates} shows the percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims.
+The {\it P} column in Figure~\ref{templates} shows the precision for different patterns. 
+This is the estimated percentage of the strings that match the pattern that are unambiguous falsifiable claims.
 We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.
@@
 
-We can observe that the patterns in the ``something false'' group perform much better than the patterns in ``plausible to not believe it'' group, but the ``plausible to not believe it'' group has a lot more hits.
-For the best patterns our classifier has accuracy in the high seventies.
+We can observe that the patterns in the ``something false'' group have much higher precision than the ``plausible to not believe it'' group, but have a lot less hits.
+Similarly, we can observe that our classifier performs much better on the ``something false'' patterns, with accuracy getting into the high seventies.
 
@@
 This is not surprising.
-We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambiguous.
+We anticipate that a more sophisticated technique with real world knowledge would be needed in order to accurately determine whether a claim was unambiguous.
 
@@
 
-A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes.
+A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the social dynamics of disputes on the web.
 As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.
@@
 They tracked highly repeated phrases, rather than nouns used in disputed claims.
+Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.
 
@@
 
+In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify other claims on the web that are likely to have a similar meaning.
+
 \section{Conclusions}
@@
 
-%\section{Acknowledgments}
-
-\todo{Do we want to have acknowledgements}
-% We would like to Thank Barbara Rosario for help with textual entailment, and 
-% Acknowledgements omitted for blind submission. Dispute Finder uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.
-
 % mendelybib is the bibliograph from our shared mendely space and is auto-generated

### 2010-02-02 papers/wicow_claimfinder/modals.tex
Folded in John Mark's changes

% modal linguistic patterns
% jma 1 Feb 2010

The linguistic patterns we use are instances of {\it modal phrases} that qualify the meaning of the subordinate clause that follows the word ``that'' in the pattern. Specifically we are interested in
modals that qualify belief.  The phrase offers a syntactic clue that the statement following it
is not to be taken at ``face value.''  An author can use a modal phrase to let the reader know
this.  Modal clues are the basis for some of the preliminary syntactic analysis
we've attempted as a way to generalize claim-finding templates.

Modals serve a broad variety of purposes;
we are interested particularly in  {\bf epistemic} modality. Epistemic phrases qualify the
degree to which the claim is known~\cite{Palmer.2001}. Most linguistic scholarship has focused on {\it
possibility} and {\it necessity} as epistemic qualifiers. In
contrast, our interest is in qualifiers that call the claim into
question, as a presumption, speculation, or a questionable
opinion. This can often, but not always done by attributing the claim
to some other person's belief, either implicitly or explicitly. The
author in so doing raises an issue about the truth, or lack of truth
of the claim.

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Merged Barbara changes to the patterns section

@@
 
-\subsection{Patterns for Finding Claims}
+\subsection{Patterns for Finding Disputes}
 \label{patterns}
 
-We hand-crafted a set of {\bf 54} patterns that we hypothesize may indicate that a claim $S$ is disputed, such as ``false claim that $S$'' or or ``it is not true that $S$''.
+We hand-crafted a set of 54 patterns that we hypothesize may indicate that a claim $S$ is disputed, such as ``false claim that $S$'' or or ``it is not true that $S$''.
 Figure~\ref{templates} shows some of the patterns we use.
 
-This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks.
-Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events.
+This is an instance of pattern matching, a method that has been used extensively for many NLP tasks.
+Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type, Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms.
 TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
+These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed.
+Most often they automatically construct the patterns and often choose them on the basis of
+statistics.
 
-In this work we start with an initial set of manually crafted search patterns.
-We then identified additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim.
-From this set of candidate prefix patterns, we manually selected additional patterns.
+In this work we simply start with an initial set of manually crafted search patterns.
+We then identified additional patterns by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim and manually selected those patterns that made sense to us.
+This technique is inspired by bootstraping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class.
+This process is iterated several times and at each times a score is given to each extraction pattern and to each new lexicon entry and only the most reliable ones are retained.
+In our case, the semantic entity of interest are the claims.
+Currently, we {\em manually} choose the patterns and claims to retain, i.e., as oppose to most relevant work, we don't {\em learn} the patterns and we don't use a measure of "reliability."
 
-This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks.
-Hearst~\cite{Hearst1992} searched for patterns like ``$X$ such as $Y$'' to infer hyponyms, Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type, Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer metronyms.
-TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
-
-Like several previous authors~\cite{Girju2003,Snow2005} we identified new patterns by searching for known disputed claims.
-We searched for claims we knew to be disputed, recorded the text patterns that frequently surrounded them on web pages, and then manually chose those patterns that made sense to us.
+Figure~\ref{templates} shows a subset of the total of 54 patterns that we used. 
+For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern.
+The {\it precision} is an estimate of the proportion of text strings matched by the pattern that are unambiguous disputed claims.
+We discuss precision further in Section~\ref{filterclaim}.
 

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Minor abstract tweaks while doing the initial submission
Discard these changes

--- 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
@@
 \newcommand{\resolved}[1]{}
+
+%%% jma mods  10AM  1 Feb 2010
+
+% remove 
+\newcommand{\jma}[1]{{\color{purple} #1}}
 
@@
        \affaddr{Santa Clara, CA, USA}\\
-       \email{john.m.agosta@intel.com}
+       %\email{john.m.agosta@intel.com} 
+        \jma{\email{barbara.rosario@intel.com}}
 }
@@
 
-\resolved{too much emphasis on {\em how}... rewrite following paragraph}
+\resolved{too much emphasis on {\em how}... rewrite following paragrapgh}
 
@@
 
+%jma we need to motivate dispute finding with credibility here
 The web contains a vast number of pages written by a vast number of people.
@@
 For users to extract reliable information from the web, it is useful for them to be able to determine when different sources disagree about a topic.
+\jma{Web pages commonly include disputes on topics they contain.
+Identifying disputes points out occasions where the credibility of a page could be called into question.}
 
 In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web. 
-We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and that there are others that are making the claim.
+\jma{ A claim is a statement of opinion or fact found in the text of a page.} We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and that there are others that are making the claim.
+%jma  To be precise, it could also be vice versa - to suggest the claim is true and others say its false
 We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.
@@
 We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}).
-For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim.
+For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author %themselves
+\jma{herself} disputes this claim.
 In Figure~\ref{templates} we list some of the patterns we used.
 In practice, many of the strings that match such a pattern are not well-formed disputed claims.
-We use a statistical classifier to filter out those strings that appear to make a well-formed claim.
+We use a statistical classifier to \jma{select only} % filter out
+ those strings that appear to make a well-formed claim.
 
-We believe that this corpus will be useful for many purposes.
+We believe that this corpus 
+\jma{of claims}
+will be useful for many purposes.
 We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources.
-We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).
+We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).
 
@@
 It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010.
-This amounts to approximately 1.1 million strings that we believe are making disputed claims.
+This amounts to approxmately 1.1 million strings that we believe are making disputed claims.
 We plan to expand our corpus as we crawl more of the web and improve our algorithms.
 
-By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particularly topical at particular times (Section~\ref{analysis}).
+By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particulary topical at particular times (Section~\ref{analysis}).
 
@@
 A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them.
-Moreover, the Internet has little in the way of publishing barriers or quality control.
+Moreover, the internet has little in the way of publishing barriers or quality control.
 If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.
@@
 There are several ways that a user can determine whether to trust information that they find on a web page.
-The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page meets their aesthetic criteria for a reliable web page; or they can check whether the information is consistent with information available from other sources.
+The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page meets their aesthetic criteria for a reliable web page;
+% jma: you really mean look at the visual style of the page to infer reliability?
+or they can check whether the information is consistent with information available from other sources.
 
@@
 Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy.
-Alternatively, a user can simply use a search engine such as Google to look for information about the source.
+Alternatively, a user can simply use a search engine such as Google to look for information about the source\jma{'s reputation}.
 While these tools can be very useful, trustworthy sources sometimes publish unreliable information, and untrusted sources sometimes contain useful information.
@@
 For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
-A contradicted claim is not necessarily a disputed claim.
+%A 
+\jma{But a} contradicted claim is not necessarily a disputed claim.
 In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese.
@@
 Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do.
+\jma{Two instances of the same phrase may have the same sense, but a different reference. Or two different phrases may refer to the same thing.}
 For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush.
@@
 
-We detect disputes rather than contradictions.
-Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important.
+We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for %evidence that people
+\jma{linguistic clues that writers} believe that there is a contradiction and that this contradiction is important.
 One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important.
+% jma better to use an example that really is false
 If a page says ``Falsely claimed that George Bush is married to Barbara Bush'' then that suggests that the contradiction with ``George Bush is married to Laura Bush'' is likely to be genuine.
-The corresponding disadvantage is that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.
+The corresponding disadvantage
+\jma{would be that if one looks for disputes, one would} 
+%is that if one looks for disputes, one will 
+only detect contradictions that humans have found and believe are important.
 
@@
 Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects.
-A focal application has been the automatic summarization of product reviews, to produce an overview of the product features that are viewed favorably or negatively.
+A focal application has been the automatic summarisation of product reviews, to produce an overview of the product features that are viewed favorably or negatively.
 Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.
@@
 \resolved{All merged?
-: The methods we use are closely related to related work on information extraction which is the task of identifying and classifying specific semantic entities within documents (i.e.
+: The methods we use are closely related to related work on information extraction which is the task of identifing and classifing specific semantic entities within documents (i.e.
 names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.}
@@
 	    & & &\\
+
+        570,000,000 & think that & 28\%& 69\%\\
         495,000,000 & believe that & 48\%& 65\%\\
+        145,000,000 & idea that & 42\% & 61\%\\
         101,000,000 & claim that & 46\%& 72\%\\
@@
 We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}).
-We then search the Web for these patterns (Section~\ref{searchpattern}).
+We then search the Web for these patterns (Section~\ref{searchpattern})
+\jma{to collect strings containing them followed by a clause that is likely to be a disputed claim}.
+
 Finally, we filter the resulting strings to give only those that resemble unambiguous disputed claims (Section~\ref{filterclaim}).
@@
 
+% \jma{Remove this paragraph?}
 This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks.
@@
 
+\include{modals}
+
+%%% move this paragraph to the end of the section.
+
 Figure~\ref{templates} shows a subset of the {\bf 54} patterns that we used. 
@@
 
-Not all patterns have exactly the same meaning. We grouped our patterns into three loose group, based on manual inspection of the pages that use them (Figure~\ref{templates}):
+Not all patterns have exactly the same meaning. We grouped our patterns into three loose 
+\jma{groups}, based on manual inspection of the pages that use them (Figure~\ref{templates}):
+
+% jma thinks this could be simply described as three epistemic cases: 
+% 1) I don't believe it
+% 2) Someone else believes it (and I don't)
+% 3) Some else doesn't believe it (and I do)
 
@@
 This is only subtly different from the previous group.
-For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''.
+For example ``Fans think that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''.
 It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims.
@@
 \label{searchpattern}
-
-\begin{figure}
- \begin{center}
-  \begin{tabular}{|llll|}
-\hline
-accuracy      & {\bf \#}    &  {\bf \%}  & {\bf   cum} \\
-      \hline
-dead on & 16   &   32\%  &   32\% \\
-+/-10 d & 9    &   18\%  &   50\% \\
-+/-30 d & 12   &   24\%  &   74\% \\
-+/-90 d & 3    &   6\%   &   80\% \\
-+/-1 yr & 6    &   12\%  &   92\% \\ 
->1 yr   & 4    &   8\%   &   100\% \\ 
-\hline
-  \end{tabular}
- \end{center}
-
- \label{dateaccuracy}
- \caption{Accuracy of simple date detection}
-\end{figure}
 
@@
 The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range.
-We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS.
+We instead simulate this behaviour by including a literal date string in the queries we pass to Yahoo BOSS.
 For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.
@@
 We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
-Despite being very primitive, this method seems to work reasonably well.
-When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).
 
-Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends Section~\ref{timetrends}.
+Including the date in the search also provides us with a light-weight way to sample what people believed or disputed at particular points in time Section~\ref{timetrends}.
 Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g.
@@
 
-\begin{figure*}[tb]
-	\begin{center}
-	\includegraphics[width=18cm]{images/2by5.pdf}
-	\caption{Frequency of each of the top nouns individually}
-	\label{multiplot_nouns}
-	\end{center}
-\end{figure*}
-
 Searching the web for our patterns yields a collection of strings.
@@
 
+% jma make this an un-numbered list? 
 Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out. 
-a chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might by ambiguous what entities it is referring to (case 3).
+%a 
+\jma{A} chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might 
+\jma{otherwise be ambiguous about}
+%by ambiguous 
+what entities it is referring to (case 3).
 
-The {\it P} column in Figure~\ref{templates} shows the percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims.
-We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.
+The {\it P} column in Figure~\ref{templates} shows the
+\jma{precision for different patterns as the}
+ percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims.
+We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and \jma{unambiguous}.
 
@@
 
-We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim.
-This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification).
-Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}).
-We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.
+We built a \jma{statistical} classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim.
+We used a simple Bayesian classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.
 
 The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim.
-To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g.
-62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus, the pattern precision (e.g.
-52\% for ``believe that'').
+In each case, we trained the classifier on the data set for the other patterns in the same group and then tested its performance on the result for that pattern.
 
-We can observe that the patterns in the ``something false'' group perform much better than the patterns in ``plausible to not believe it'' group, but the ``plausible to not believe it'' group has a lot more hits.
-For the best patterns our classifier has accuracy in the high seventies.
-
-Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambiguous.
-This is not surprising.
-We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambiguous.
+We can observe that the patterns in the ``something false'' group 
+\jma{ have higher coverage and}
+perform much better than the patterns in ``plausible to not believe it'' group, but the ``plausible to not believe it'' group has a lot more hits.
 
@@
 
-We save the surrounding text, page title, and URL for each of the disputed claims we see made on the web.
-At present we do not do anything with this data, but we anticipate that it could be useful for many purposes.
-For example it may be possible to resolve the meaning of ambiguous words or entities based on the words nearby (with have experimented with an algorithm similar to that used by Wikify~\cite{Mihalcea2007}).
-It is also useful to what person wrote the page, what organization hosted the page, who they link to, what meme-like phrases they make near to the claim, whether the page is written in an ``expert'' style, etc.
+\x{Importance of dates}
+\x{Work meaning depending on surrounding text}
+\x{We do not yet do anything useful with context, but we believe it is important and intend to use it}
+\x{context can be surrounding text but also features of the web pages -- domain,  "authority," in-links, format; context is also the author: expert? social info on author...}
+
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=16cm]{images/2by5.pdf}
+	\caption{Frequency of each of the top nouns individually}
+	\label{multiplot_nouns}
+	\end{center}
+\end{figure*}
 
@@
 
-Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages.
+Dispute Finder is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages.
 Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications.
@@
 
-A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes.
+A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the %zeitgeist
+\jma{social dynamics of of disputes on the web.}
 As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.
 
-\section{Analyzing the Data}
+\section{Analysing the Data}
 \label{analysis}
@@
 
-We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010.
-This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims.
-Of those 1.1 million text strings, most are repeating claims made elsewhere in the data set.
+\x{Cite MemeTracker~\cite{Backstrom2009}}
+
+\todo{Lots of pretty graphs showing what our data is like.}
+
+\subsection{Data Quality}
+
+\x{Look at a random sample of the data and say how clean it is.}
+\x{Evaluate the quality of the claims that we extracted.}
+\x{Evaluate the quality of the clusters that we created.}
+\x{Evaluate the quality of the different individual patterns - which ones have the highest quality claims.}
+\x{say something about {\em duplicate} claims?}
 
 \subsection{Trends over time}
-\label{timetrends}
 
-Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years.
-We obtained these figures by using a part-of-speech tagger to identify nouns in claims found on January 10th of every year from 2000 to 2010.
-Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}).
-We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns.
-All graphs are plotted on the same scale.
-The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made.
-It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even the nouns prove to be quite interesting.
+\x{Named entity recognition}
 
-We manually inspected our claims to determine what was going on that made particular nouns spike at particular times:
+\x{Look at what noun phrases were most disputed at particular years.}
+\x{Look at what noun phrases were most disputed on particular days.}
 
-\begin{itemize}
- \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention.
-His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
- \item {\bf God:} God is always a controversial topic.
-We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006} seems to have sparked extra controversy.
- \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
- \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
-\end{itemize}
-
-These graphs resemble those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web.
-They tracked highly repeated phrases, rather than nouns used in disputed claims.
-
-\begin{figure}[tbh]
- \begin{center}
-  \begin{tabular}{|lll|}
-    \hline
-    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
-    \hline
-   {\bf children} & tiger woods abused & 218\\
-                  & instead encourage daily & 178\\
-    \hline
-   {\bf god} & daily encourage parents & 150 \\
-   \hline
-   {\bf government} & health care & 1267 \\
-                    & united states & 427 \\
-		    & relation environmental matters & 155 \\
-   \hline
-   {\bf iraq} & weapons mass destruction & 373 \\
-              & united states & 247 \\
-	      & saddam hussein & 192 \\
-	      & al qaeda & 149 \\
-   \hline
-   {\bf israel} & middle east & 251 \\
-		& allowed upon population & 128 \\
-                & united states & 107 \\
-		& off map & 106 \\
-   \hline
-   {\bf law}    & lawbreaker rather broken & 133 \\
-		& united states &\\
-   \hline
-    {\bf obama} & working best interests & 568\\
-                & health care & 481\\
-	        & united states & 327 \\
-		& nobel prize & 270 \\
-		& legitimately president & 207 \\
-		& ford hood shooter hasan nidal advised & 190 \\
-		& birth certificate & 180\\
-   \hline
-   {\bf president} & united states & 439 \\
-                   & health care & 203 \\
-		   & george w & 164 \\
-		   & aircraft system jolting bombing & 159 \\
-		   & peace prize & 125 \\
-		   & white house & 125 \\
-   \hline
-      {\bf war} & united states & 340 \\
-   \hline
-
-   {\bf women} & stay home & 183 \\
-               & save vaccine & 85 \\
-   \hline
-  \end{tabular}
- \end{center}
- \label{cluster-figure}
- \caption{Largest word clusters found for nouns}
-\end{figure}
-
-\subsection{Clusters}
-\label{clusters}
-
-For each noun, we analyzed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed.
-Rather than clustering claims directly, we instead cluster together words that frequently co-occur.
-We used an agglomerative clustering algorithm, repeatedly merging the two clusters of words that had the most claims in common.
-
-Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun.
-Most of these will make sense to people who have been following news in the united states.
-For example, we see that disputed claims about Obama often talk about his Nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized).
-Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.
+\x{We remove exact-match strings from the same domain - to avoid republishing of same article.}
 

### 2010-02-02 papers/wicow_claimfinder/modals.tex
Subsection on modal phrases

@@
 we are interested particularly in  {\bf epistemic} modality. Epistemic phrases qualify the
-degree to which the claim is known~\cite{Palmer.2001}. Most linguistic scholarship has focused on {\it
+degree to which the claim is known.~\cite{Palmer.2001} Most linguistic scholarship has focused on {\it
 possibility} and {\it necessity} as epistemic qualifiers. In

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Fold in Barbara's suggested changes and make minor tweaks of my own

--- 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
@@
 We present a method for the automatic acquisition of a corpus of disputed claims from the web.
-We consider a claim to be disputed if a page on the web suggests that this claim is wrong and that other people on the web are suggesting that it is true.
+We consider a claim to be disputed if a page on the web suggests that this claim is wrong and that other people believe it is true.
 
@@
 
-\keywords{Sensemaking, Annotation, Argumentation, Web, CSCW}
+\keywords{dispute, web, credibility}
 
@@
 For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim.
-In Figure~\ref{templates} we list some of the patterns we used.
+In Figure~\ref{templates-fig} we list some of the patterns we used.
 In practice, many of the strings that match such a pattern are not well-formed disputed claims.
@@
     \hline
+        &&&\\
         \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
@@
        \hline
+       &&&\\
        \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
@@
         \hline
+	&&&\\
         \multicolumn{2}{|l}{\it Something false} & &\\
@@
 
-  \label{templates}
   \caption{Some of the patterns we use to find disputed claims}
+  \label{templates-fig}
 \end{figure}
@@
 We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}).
-We then search the Web for these patterns (Section~\ref{searchpattern}) to collect sentences that contain the pattern, followed by some other string.
+We then search the Web for these patterns (Section~\ref{searchpattern}) to collect sentences that contain the pattern.
 Finally, we filter the resulting strings to give only those that resemble unambiguous falsifiable claims (Section~\ref{filterclaim}).
@@
 \end{center}
+\caption{We filter out text that does not look like a statement}
 \label{filtered}
-\caption{We filter out text that does not look like a statement}
 
@@
 We hand-crafted a set of 54 patterns that we hypothesize may indicate that a claim $S$ is disputed, such as ``false claim that $S$'' or or ``it is not true that $S$''.
-Figure~\ref{templates} shows some of the patterns we use.
+Figure~\ref{templates-fig} shows some of the patterns we use.
 
@@
 These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed.
-Most often they automatically construct the patterns and often choose them on the basis of
+Most often they construct the patterns automatically and often choose them on the basis of
 statistics.
@@
 We then identified additional patterns by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim and manually selected those patterns that made sense to us.
-This technique is inspired by bootstraping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class.
+This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class.
 This process is iterated several times and at each times a score is given to each extraction pattern and to each new lexicon entry and only the most reliable ones are retained.
@@
 
-Figure~\ref{templates} shows a subset of the total of 54 patterns that we used. 
+Figure~\ref{templates-fig} shows a subset of the total of 54 patterns that we used. 
 For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern.
@@
 
-Not all patterns have exactly the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates}):
+Not all patterns have exactly the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates-fig}):
 
@@
 
-Figure~\ref{templates} shows a subset of the {\bf 54} patterns that we used. 
-For each pattern, the {\it frequency} is the number of pages that Yahoo estimates contain this pattern.
-The {\it precision} is an estimate of the proportion of text strings matched by the pattern that are unambiguous disputed claims.
-We discuss precision further in Section~\ref{filterclaim}.
-
 \subsection{Searching the Web for Claims}
@@
 \begin{figure}
+\vspace{0.5cm}
  \begin{center}
@@
 \hline
-accuracy      & {\bf \#}    &  {\bf \%}  & {\bf   cum} \\
+{\bf accuracy}      & {\bf count}    &  {\bf percent}  & {\bf cummulative} \\
       \hline
 dead on & 16   &   32\%  &   32\% \\
-+/-10 d & 9    &   18\%  &   50\% \\
-+/-30 d & 12   &   24\%  &   74\% \\
-+/-90 d & 3    &   6\%   &   80\% \\
-+/-1 yr & 6    &   12\%  &   92\% \\ 
->1 yr   & 4    &   8\%   &   100\% \\ 
+within 10 days & 9    &   18\%  &   50\% \\
+within 30 days & 12   &   24\%  &   74\% \\
+within 90 days & 3    &   6\%   &   80\% \\
+within 1 year & 6    &   12\%  &   92\% \\ 
+off by more than 1 year   & 4    &   8\%   &   100\% \\ 
 \hline
@@
 
+ \caption{Accuracy of simple date detection}
  \label{dateaccuracy}
- \caption{Accuracy of simple date detection}
 \end{figure}
@@
 
-Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends Section~\ref{timetrends}.
+Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends (Section~\ref{timetrends}).
 Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g.
@@
 
-The {\it P} column in Figure~\ref{templates} shows the precision for different patterns. 
+The {\it pattern precision} column in Figure~\ref{templates-fig} shows the estimated precision for different patterns. 
 This is the estimated percentage of the strings that match the pattern that are unambiguous falsifiable claims.
@@
 
-The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim.
+The {\it classifier accuracy} column in Figure~\ref{templates-fig} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim.
 To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g.
@@
 
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=18cm]{images/2by5.pdf}
+	\caption{Frequency of each of the top nouns individually}
+	\label{multiplot_nouns}
+	\end{center}
+\end{figure*}
+
 \subsection{Context}
@@
 We save the surrounding text, page title, and URL for each of the disputed claims we see made on the web.
-At present we do not do anything with this data, but we anticipate that it could be useful for many purposes.
-For example it may be possible to resolve the meaning of ambiguous words or entities based on the words nearby (with have experimented with an algorithm similar to that used by Wikify~\cite{Mihalcea2007}).
-It is also useful to what person wrote the page, what organization hosted the page, who they link to, what meme-like phrases they make near to the claim, whether the page is written in an ``expert'' style, etc.
+At present we do not do anything with this data, but we anticipate that it could be useful for many purposes; for example it may be possible to resolve the meaning of ambiguous words or entities based on the words nearby like Wikify~\cite{Mihalcea2007} does.
+Since many web sites have content written by multiple writers with different degrees of credibility, it is also useful to be able to know which writer disputed a particular claim.
+Other useful contextual information includes what organization hosted the page, who they link to, what meme-like phrases they make near to the claim, and whether the page is written in an ``expert'' style.
 
+\vspace{0.25cm}
 \section{Using Disputed Claims}
@@
 
-A corpus of disputed claims could be useful for a variety of applications, including real-time dispute recognition, background dispute analysis agents, and other research tools.
+A corpus of disputed claims could be useful for many purposes, including real-time dispute recognition, background dispute analysis agents, and other research tools.
 Real-time dispute recognition agents could be used, for instance, to alert users when a trusted source disagrees with others, or to provide the user with feedback on how contentious a topic is.
 
-Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages.
-Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications.
+Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that users encounter in their lives.
+The current implementation of Dispute Finder is a web browser extension that highlights text on web pages that appears to make a known disputed claim.
+In future research, we plan to extend Dispute Finder to be able to detect disputed information in television, and in speech that a user hears during conversations.
 We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation.
@@
 
+\vspace{0.25cm}
 \section{Analyzing the Data}
@@
 This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims.
-Of those 1.1 million text strings, most are repeating claims made elsewhere in the data set.
+This does not mean that there are 1.1 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.
 
@@
 Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years.
-We obtained these figures by using a part-of-speech tagger to identify nouns in claims found on January 10th of every year from 2000 to 2010.
+For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''.
+We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims.
+We then analysed the distribution of noun frequencies in claims associated with January 10th of every year from 2000 to 2010.
 Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}).
-We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns.
+We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}).
 All graphs are plotted on the same scale.
@@
 His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
- \item {\bf God:} God is always a controversial topic.
-We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006} seems to have sparked extra controversy.
+ \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
  \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
@@
  \end{center}
+ \caption{Largest word clusters found for nouns}
   \label{cluster-figure}
- \caption{Largest word clusters found for nouns}
+
 \end{figure}
 
-\subsection{Clusters}
+\subsection{What is Disputed about a Noun?}
 \label{clusters}
 
-For each noun, we analyzed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed.
-Rather than clustering claims directly, we instead cluster together words that frequently co-occur.
-We used an agglomerative clustering algorithm, repeatedly merging the two clusters of words that had the most claims in common.
+Once we know what nouns are disputed, it is interesting to know what it is about a noun that is disputed.
+For example, what is it that people are disputing about ``Obama'' or ``Iraq''?
+To address this question, we took the set of claims that contained each popular noun (e.g.
+``Obama'') and looked for sets of words that occurred together much more frequently than would be expected if claims were formed randomly.
+For example in our claims about ``Obama'', we found the word cluster ``health care'' because most claims about Obama that contain the word ``health'' also contain the word ``care'' and vice-versa.
 
 Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun.
-Most of these will make sense to people who have been following news in the united states.
-For example, we see that disputed claims about Obama often talk about his Nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized).
-Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.
+For each cluster, the count is the number of claims about that noun that contain all of the words.
+Most of these will make sense to people who have been following news in the United States.
+For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized).
+Some of the word clusters are not particularly interesting; for example many claims talk about the united states, even when that is not an important part of what is disputed.
 
 In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify other claims on the web that are likely to have a similar meaning.
+This will allow us to better attack some of the problems we outlined in Section~\ref{using}.
 
@@
 Our research has shown that the web can be used as a corpus to determine what claims people identify as being disputed.
-Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the array of views to be found online.
+Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the collection of views that can be be found online.
 Furthermore, because individuals express opinions freely online, a snapshot of the disputed claims online can provide valuable insights into the cultural zeitgeist of the time.
 
-Challenges of creating a comprehensive corpus of disputed claims are many, from data quality to deeper natural language processing challenges such as recognizing textual entailment.
-We address these in part by taking a high-level statistical view of the data.
+Creating a comprehensive corpus of disputed claims presents many challenges: how to create patterns, how to search for patterns, how to avoid malformed sentences, how to resolve or filter out ambiguous claims, how to determine if two claims are paraphrases, and how to determine if text on the web contains a claim that our database says is disputed.
+For each of these tasks, we have implemented enough to get useful results, but there is much scope to do things better.
 
-The possible applications of a corpus of disputed claims are many and varied.
+There are many possible applications for a corpus of disputed claims.
 These include real-time dispute recognition, autonomous research agents that operate in the background, and sociocultural research.
 
-Using the claim prefix search technique and text processing, we are able to identify
-
-Our data set currently includes approximately 1.2 million records.
-We intend to expand this by several orders of magnitude, an improvement that will address issues of data sparsity and enable more robust data processing.
+Our data set currently includes approximately 1.1 million records. We intend to expand this by several orders of magnitude.
 

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
two superficial changes: themselves -> herself capitalize United States

@@
 We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}).
-For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim.
+For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author herself disputes this claim.
 In Figure~\ref{templates-fig} we list some of the patterns we used.
@@
  \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
- \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
+ \item {\bf Israe:} The Gaza conflict of 2007 caused a big spike.  
 \end{itemize}
@@
 For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized).
-Some of the word clusters are not particularly interesting; for example many claims talk about the united states, even when that is not an important part of what is disputed.
+Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.
 

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Final tweaks. Final version?

--- 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
@@
 We present a method for the automatic acquisition of a corpus of disputed claims from the web.
-We consider a claim to be disputed if a page on the web suggests that this claim is wrong and that other people believe it is true.
+We consider a factual claim to be a {\it disputed claim} if a page on the web suggests both that the claim is false and also that other people say it is true.
 
@@
 
-We argue why such a corpus of disputed claims is useful for a wide range of applications related to information credibility on the web, and we look at what our current corpus reveals about what is being disputed on the web.
+We argue that such a corpus of disputed claims is useful for a wide range of applications related to information credibility on the web, and we report what our current corpus reveals about what is being disputed on the web.
 
@@
 We use the word {\it claim} to mean a statement of opinion or fact contained in the text of a web page.
-We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and also that there are others that are making the claim.
+We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and also that there are others who say the claim is true.
 We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.
@@
 For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim.
-In Figure~\ref{templates-fig} we list some of the patterns we used.
+In Figure~\ref{templates-fig} we list some of the patterns we use.
 In practice, many of the strings that match such a pattern are not well-formed disputed claims.
-We use a statistical classifier to select only those strings that appear to make a well-formed claim.
+We use a statistical classifier to select only those strings that appear to make a well-formed unambigous claim.
 
-We believe that this corpus or disputed claims will be useful for many purposes.
+We believe that this corpus of disputed claims will be useful for many purposes.
 We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources.
-We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).
+We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, creating visualization tools that let users know what is disputed about a topic that interests them, and building statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).
+In Section~\ref{analysis} we show how our corpus can be used to reveal trends in dispute on the web.
 
@@
 It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010.
-This amounts to approximately 1.1 million strings that we believe are making disputed claims.
+This amounts to approximately 1.1 million strings that our classifier believes are making disputed claims.
 We plan to expand our corpus as we crawl more of the web and improve our algorithms.
-
-By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particularly topical at particular times (Section~\ref{analysis}).
 
@@
 Moreover, the Internet has little in the way of publishing barriers or quality control.
-If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.
+If a user is to extract reliable information from the web then they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.
 
 There are several ways that a user can determine whether to trust information that they find on a web page.
-The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page looks how they expect a credible source to look; or they can check whether the information is consistent with information available from other sources.
+The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page has features that they would expect a credible source to have; or they can check whether the information is consistent with information available from other sources.
 
@@
 Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos.
-Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing.
-Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.
+Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing; some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.
 These metrics do a good job at detecting pages that resemble pages that contain unreliable information, but they do not protect against authors who write untrustworthy information in the style of a trustworthy document.
@@
 We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed.
-For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
-In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
+For example, if a user is reading a page that says ``Elvis is alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
+In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to the corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
 
@@
 De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions.
-AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction.
+AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine whether this implies that there is a contradiction.
 Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another.
@@
 Two instances of the same phrase may have the same sense, but a different reference, or two different phrases may refer to the same thing. 
-For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush.
-``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England.
-``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.
-``The company is not going bust'' does not contract ``the company is doing great'' if the statements are about different companies.
+For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush; ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England; and ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.
 
@@
 We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}).
-We then search the Web for these patterns (Section~\ref{searchpattern}) to collect sentences that contain the pattern.
+We then search the Web for these patterns (Section~\ref{searchpattern}).
 Finally, we filter the resulting strings to give only those that resemble unambiguous falsifiable claims (Section~\ref{filterclaim}).
@@
   2. & falsely claimed that {\it he didn't do it} & no & ``he'' and ``it'' are unbound referents \\
-  3. & falsely claimed that {\it federal labor laws do not apply} & no & object of the verb is not present\\
+  3. & falsely claimed that {\it federal labor laws do not apply} & no & ambiguous: apply to what?\\
   4. & false claim that {\it Elvis is alive} despite all evidence & yes & but drop everything after ``despite''\\
@@
 This is an instance of pattern matching, a method that has been used extensively for many NLP tasks.
-Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type, Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms.
-TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
+Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms; Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type; Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms; and TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
 These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed.
@@
 In this work we simply start with an initial set of manually crafted search patterns.
-We then identified additional patterns by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim and manually selected those patterns that made sense to us.
+We then identified additional patterns by searching for the text of known disputed claims, observing what text commonly occurred as a prefix of a known disputed claim, and manually selected those patterns that made sense to us.
 This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class.
-This process is iterated several times and at each times a score is given to each extraction pattern and to each new lexicon entry and only the most reliable ones are retained.
-In our case, the semantic entity of interest are the claims.
+In our case, the semantic entities of interest are the disputed claims.
 Currently, we {\em manually} choose the patterns and claims to retain, i.e., as oppose to most relevant work, we don't {\em learn} the patterns and we don't use a measure of "reliability."
@@
 
-Not all patterns have exactly the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates-fig}):
+Not all patterns have the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates-fig}):
 
@@
  \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it is plausible that someone else might not believe it.
-This is only subtly different from the previous group.
+This is subtly different from the previous group.
 For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''.
@@
 \begin{figure}
-\vspace{0.5cm}
  \begin{center}
@@
 \hline
-{\bf accuracy}      & {\bf count}    &  {\bf percent}  & {\bf cummulative} \\
+{\bf accuracy}      & {\bf count}    &  {\bf percent}  & {\bf cumulative} \\
       \hline
@@
 We use the Yahoo BOSS API~\cite{yahoo-boss} to search for occurrences of our patterns on the web.
-Using Yahoo BOSS allows us to search for patterns on a vast number of web pages, without having to build our own search engine.
+Using Yahoo BOSS allows us to search for patterns on a vast number of web pages without having to build our own search engine.
 We search Yahoo BOSS for a raw string such as ``the misconception that'', download every page that Yahoo lists in its search results, and then look for text that matches any of our known patterns.
 
-Since we are using an existing search engine, we are limited to searching for simple text strings.
+Since we are using a general purpose search engine, we are limited to searching for simple text strings.
 This requires us to generate multiple patterns that are almost the same, other than for synonyms, for example we have both ``the lie that'' vs ``the deceit that''.
@@
 
-It is useful to be able to update our corpus as new pages appear on the web, without having to repeatedly download the same pages.
+It is useful to be able to update our corpus as new pages appear on the web without having to repeatedly download the same pages.
 The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range.
@@
 Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format.
-We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
 Despite being very primitive, this method seems to work reasonably well.
 When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).
+We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
 
-Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends (Section~\ref{timetrends}).
+Knowing the rough date when someone believed or disputed something allows us to produce fuzzy time trends (Section~\ref{timetrends}).
 Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g.
-Elvis was alive in the past, but isn't not).
+Elvis was alive in the past, but isn't now).
 
@@
 
-Searching the web for our patterns yields a collection of strings.
+Searching the web for patterns yields a collection of strings.
 From this collection, we want to filter out any strings that are not making a falsifiable claim, and any strings that make a claim that is ambiguous.
 
-Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out.
+Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we want to filter some of them out.
 A chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).
@@
 
-Whether a claim is unambiguous can be highly subjective.
+Whether a claim is unambiguous is ofter subjective.
 For example, in the string ``Obama is the president'' it is possible that ``Obama'' is referring to someone other than ``Barack Obama'' and ``the president'' is referring to a position other than ``President of the United States''.
@@
 Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}).
-We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.
+We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and part-of-speech tag of the first and second words.
 
@@
 To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g.
-62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus, the pattern precision (e.g.
+62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus the pattern precision (e.g.
 52\% for ``believe that'').
 
-We can observe that the patterns in the ``something false'' group have much higher precision than the ``plausible to not believe it'' group, but have a lot less hits.
+We can observe that the patterns in the ``something false'' group have much higher precision than the ``plausible to not believe it'' group, but appear much less frequently on the web.
 Similarly, we can observe that our classifier performs much better on the ``something false'' patterns, with accuracy getting into the high seventies.
@@
 	\includegraphics[width=18cm]{images/2by5.pdf}
-	\caption{Frequency of each of the top nouns individually}
+	\caption{Number of claims containing a particular noun on January 10th of any particular year}
 	\label{multiplot_nouns}
@@
 
-\vspace{0.25cm}
 \section{Using Disputed Claims}
@@
 
-\vspace{0.25cm}
 \section{Analyzing the Data}
@@
 We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims.
-We then analysed the distribution of noun frequencies in claims associated with January 10th of every year from 2000 to 2010.
+We then analyzed the distribution of noun frequencies in claims made on January 10th of every year from 2000 to 2010.
 Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}).
@@
 The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made.
-It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even the nouns prove to be quite interesting.
+It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even these nouns prove to be quite interesting.
 
@@
 
-These graphs resemble those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web.
-They tracked highly repeated phrases, rather than nouns used in disputed claims.
+These graphs are similar to those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web.
+MemeTracker tracked highly repeated phrases, rather than nouns used in disputed claims.
 Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.
@@
 For example in our claims about ``Obama'', we found the word cluster ``health care'' because most claims about Obama that contain the word ``health'' also contain the word ``care'' and vice-versa.
+We used an agglomerative clustering algorithm to group together words that co-occur in the same claims.
 
 Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun.
-For each cluster, the count is the number of claims about that noun that contain all of the words.
+For each cluster, the count is the number of claims about that noun that contain all of the words in the cluster.
 Most of these will make sense to people who have been following news in the United States.
-For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized).
-Some of the word clusters are not particularly interesting; for example many claims talk about the united states, even when that is not an important part of what is disputed.
+For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alledged statement that Israel should be wiped off the map (which the authors had not previously realized was a disputed).
+Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.
 
-In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify other claims on the web that are likely to have a similar meaning.
+In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify text that is making a disputed claim.
 This will allow us to better attack some of the problems we outlined in Section~\ref{using}.
@@
 
-Creating a comprehensive corpus of disputed claims presents many challenges: how to create patterns, how to search for patterns, how to avoid malformed sentences, how to resolve or filter out ambiguous claims, how to determine if two claims are paraphrases, and how to determine if text on the web contains a claim that our database says is disputed.
+Creating a comprehensive corpus of disputed claims presents many challenges: how to create patterns, how to search for patterns, how to avoid malformed sentences, how to resolve or filter out ambiguous claims, how to determine if two claims are paraphrases, and how to learn interesting things from the data set.
 For each of these tasks, we have implemented enough to get useful results, but there is much scope to do things better.
@@
 
-Our data set currently includes approximately 1.1 million records. We intend to expand this by several orders of magnitude.
+Our data set currently includes approximately 1.1 million records. In the future we intend to expand this by several orders of magnitude.
 

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Filled in missing stats

@@
 \begin{center}
+  \vspace{0.5cm}
   \begin{tabular}{|llll|}
@@
 
-        40,100,000 & claiming that & 39\% &\\
-        30,600,000 & the belief that & &\\
-        28,600,000 & believing that & &\\
-        11,700,000 & who believe that &&\\
-        8,400,000 & who think that &&\\
+        40,100,000 & claiming that & 39\% & 65\%\\
+        11,700,000 & who believe that & 69\% & 73\%\\
+        8,400,000 & who think that & 49\% & 66\%\\
         \hline
@@
   \label{templates-fig}
+  \vspace{0.5cm}
 \end{figure}

### 2010-02-09 papers/wicow_claimfinder/claimfinder.tex

@@
    {\bf law}    & lawbreaker rather broken & 133 \\
-		& united states &\\
+		& united states & 116\\
    \hline
@@
 		& legitimately president & 207 \\
-		& ford hood shooter hasan nidal advised & 190 \\
+		& fort hood shooter hasan nidal advised & 190 \\
 		& birth certificate & 180\\

### 2010-02-09 papers/www_disputefinder/disputefinder_final.tex
Improved description of entailment algorithm and added timing figures

--- 2009-10-31 papers/www_disputefinder/disputefinder.tex
@@
 	\begin{center}
-	\includegraphics[width=8.5cm]{pictures/highlight_abortion.png}
+	\includegraphics[width=6cm]{pictures/highlight_vaccine_shadow.png}
 	\caption{Dispute Finder highlights text snippets that make disputed claims.}
@@
 	\begin{center}
-	\includegraphics[width=7cm]{pictures/popup_abortion_shadow.png}
+	\includegraphics[width=7cm]{pictures/popup_vaccine_shadow.png}
 	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
@@
 
-There are also several tools that find pages write about the same topic with different slants, rather than looking at the specific claims a page makes.
+There are also several tools that find pages written about the same topic with different slants, rather than looking at the specific claims a page makes.
 News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story.
@@
 
-These challenges are not unique to dispute finder; indeed they apply to any tool that informs a user about disputed information and helps users interpret this disputed information.
+These challenges are not unique to Dispute Finder; indeed they apply to any tool that informs a user about disputed information and helps users interpret this disputed information.
 
@@
 For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''.
-In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be widely recogonsized.
+In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be reliably detected.
 
@@
 Detecting entailment between texts is a semantic analysis problem.
-Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}.
-Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim.
+Our client side entailment method uses a simple Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006}, similar to those that are often used as a baseline to which other algorithms are often compared~\cite{Braz}.
+Our implementation divides the page into sentences, strips out stop-words, applies a regular expression stemmer, and then looks for sentences that contain all the non stop-words contained in one of the paraphrases of a known claim.
 If the claim contains a negation word (e.g.
 not, never, can't) then so must the matching sentence.
-To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims.
-The hot terms are selected such that every claim contains at least one hot term.
-If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.
+
+To improve performance, rather than running the LLM algorithm for every pair of sentences and paraphrases, we compare each sentence with every paraphrase simultaneously by searching for words in order of their rareness.
+For each paraphrase, we sort the words in order of their rareness in Wikipedia, and then assemble a set that contains the rarerst word in every known paraphrase.
+If a sentence contains one of these rare words, we create a (memoized) set that contains the second-rarest word that appears in each of the paraphrases that contained the first word and then check whether the sentence contains any of these words.
+We repeat this process until we find a claim paraphrase such that all the non stop-words in the paraphrase are contained in the sentence.
+
+The combination of a simple algorithm and a optimized implementation allows us to check for textual entailment between every sentence on every page a user browses and every claim paraphrase in our database with only moderate slowdown.
+On a 2.33Ghz Core2 processor, Dispute Finder is able to check for disputed claims on the New York Times front page in 50 milliseconds, and is able to check the Wikipedia page on Global Warming in 127 milliseconds.
+Moreover, to further hide this latency from users, Dispute Finder checks for disputed claims asynchronously in the background rather than forcing the user to wait.
+Note however that these figures are for a database with only 2,609 disputed claims.
+It remains to be seen how our algorithm will scale to a database with millions of disputed claims.
 
@@
 When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read.
-In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}).
+In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{claimview}).
 We also implemented and tested an interface that contained a user-editable argumentation graph; however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.
@@
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
-	\caption{Article List interface for a disputed claim}
-	\label{article_list}
-	\end{center}
-\end{figure}
-
 \begin{description}
@@
 
-\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}).
+\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{claimview}).
 For each article, the interface shows a summary sentence that captures the core argument used by the article.
@@
 
-\section{Evaluation}
+\section{User Studies}
 \label{sec:interviews}
@@
 
-We also conducted interviews with most of our user study participants, and five additional people, asking them how they use the web to form and promote their opinions.
+We also conducted interviews with most of our user study participants, and six additional people, asking them how they use the web to form and promote their opinions.
 
@@
 
-When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was phrased negatively.
+When using the article list interface (Figure~\ref{claimview}), several users got confused about whether an article supported or opposed a claim that was phrased negatively.
 For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.

### 2010-02-09 papers/www_disputefinder/disputefinder_final.tex
Various changes in response to reviews

@@
 We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page.
-This same problem has hindered the adoption of numerous web page annotation tools.
+This problem has hindered the adoption of many web annotation tools.
 
 Bulk page marking trades off some precision for better coverage.
-When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them.
-Since they are reading the snippet out of context, they are more likely to mark a phrase incorrectly.
+When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them, but since they are reading the snippet out of context they are more likely to mark a phrase incorrectly.
 
@@
 
-Client side entailment gets the most coverage.
+Client side entailment gets the most coverage, but the worst precision.
 Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined.
@@
 Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and intranet sites.
+The flip side is that the classification algorithm needs to be simple enough to run on the client without noticably slowing down the web browser, and the algorithm is limited to only being able to use whatever data can be downloaded to the client.
 
 A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing.
-The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be practical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy.
+The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be practical for the client to store it locally, so any URL-based approach requires that the client asks the server for information about each URL the user browses, reducing user privacy.
 By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.
+
+Our currently deployed database of 2,609 disputed claims takes up around 500 kilobytes and an experimental automatically-generated database of 1.1 million disputed claims takes up 50 megabytes compressed.
+In our current implementation, the client synchronizes with the server by periodically downloading a complete database, but in future versions we intend that the client should only download those claims that have changed since the last update.
 As our database grows bigger, it will of course become more challenging to maintain a local copy in the browser extension.
@@
 \item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph.
-This graph is inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.
+This graph is inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, Cohere~\cite{Shum2008}, and Debategraph.org.
 Each claim is linked to claims that represent alternative points of view, and claims that support that point of view.
@@
 \item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{claimview}).
+This is similar to the lists of articles collected by DiscourseDB.org.
 For each article, the interface shows a summary sentence that captures the core argument used by the article.
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/mark_evidence.png}
+	\includegraphics[width=5cm]{pictures/mark_evidence.png}
 	\caption{To add an article, select some summary text, and click ``use as evidence'' from the context menu.}
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
+	\includegraphics[width=5cm]{pictures/article_choose_claim.png}
 	\caption{Choose how to connect an article with a claim.}

### 2010-02-10 papers/www_disputefinder/disputefinder_final.tex
More tweaks to address reviewer comments

@@
 	\begin{center}
-	\includegraphics[width=7cm]{pictures/popup_vaccine_shadow.png}
+	\includegraphics[width=7.5cm]{pictures/popup_vaccine_shadow.png}
 	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
@@
 
-One weakness of the automatic import approach is that the claims found on these sites are often phrased differently to the way they commonly appear on the web.
+One weakness of the automatic import approach is that the claims on these sites are often phrased differently to the way they commonly appear on the web.
 For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''.
@@
 At the time of writing, users have added 557 claims, and 140 users have added at least one claim.
+
+To reduce abuse, we allow a user to flag junk claims, false paraphrases, or linked articles that are not actually arguing against the disputed claim.
+A user should not flag a claim because they believe it is not disputed, since the level of dispute is a function of the articles that disagree.
+Flagging is currently moderated manually.
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/mark_disputed.png}
+	\includegraphics[width=5cm]{pictures/mark_disputed.png}
 	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
@@
 	\begin{center}
-	\includegraphics[width=7cm]{pictures/training2.png}
+	\includegraphics[width=6cm]{pictures/training2.png}
 	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
@@
 In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users.
-There were two problems here: first, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; second, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}.
+There were two problems here: first, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different points; second, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}.
 This result is consistent with previous studies~\cite{Isenmann1997}.
@@
 	\begin{center}
-	\includegraphics[width=8cm]{pictures/popup_graph_crop.png}
+	\includegraphics[width=7.5cm]{pictures/popup_graph_crop.png}
 	\caption{Argumentation graph interface for a disputed claim}

### 2010-02-10 papers/www_disputefinder/disputefinder_final.tex
Spell check

@@
 Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and intranet sites.
-The flip side is that the classification algorithm needs to be simple enough to run on the client without noticably slowing down the web browser, and the algorithm is limited to only being able to use whatever data can be downloaded to the client.
+The flip side is that the classification algorithm needs to be simple enough to run on the client without noticeably slowing down the web browser, and the algorithm is limited to only being able to use whatever data can be downloaded to the client.
 
@@
 To improve performance, rather than running the LLM algorithm for every pair of sentences and paraphrases, we compare each sentence with every paraphrase simultaneously by searching for words in order of their rareness.
-For each paraphrase, we sort the words in order of their rareness in Wikipedia, and then assemble a set that contains the rarerst word in every known paraphrase.
+For each paraphrase, we sort the words in order of their rareness in Wikipedia, and then assemble a set that contains the rarest word in every known paraphrase.
 If a sentence contains one of these rare words, we create a (memoized) set that contains the second-rarest word that appears in each of the paraphrases that contained the first word and then check whether the sentence contains any of these words.
@@
 The combination of a simple algorithm and a optimized implementation allows us to check for textual entailment between every sentence on every page a user browses and every claim paraphrase in our database with only moderate slowdown.
-On a 2.33Ghz Core2 processor, Dispute Finder is able to check for disputed claims on the New York Times front page in 50 milliseconds, and is able to check the Wikipedia page on Global Warming in 127 milliseconds.
+On a 2.33GHz Core2 processor, Dispute Finder is able to check for disputed claims on the New York Times front page in 50 milliseconds, and is able to check the Wikipedia page on Global Warming in 127 milliseconds.
 Moreover, to further hide this latency from users, Dispute Finder checks for disputed claims asynchronously in the background rather than forcing the user to wait.

### 2010-02-10 papers/www_disputefinder/disputefinder_final.tex
Changes suggested by Beth

@@
 A claim can be stated in many ways.
-For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are {\it paraphrases} of the same claim.
+For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are paraphrases of the same claim.
 For each claim, the database contains links to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).
 
-The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to {\it entail} a claim.
+The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to entail a claim.
 A snippet is a continuous region of text on a web page.
-A snippet is considered to {\it entail} a claim if a typical user reading that snippet would reasonably conclude that the author of the page believed the claim was true.
-For example ``the English have as many words for rain as the Eskimos have for snow'' {\it entails} ``Eskimos have many words for snow'', even though this claim is never stated explicitly.
+A snippet is considered to entail a claim if a typical user reading that snippet would reasonably conclude that the author of the page believed the claim was true.
+For example ``the English have as many words for rain as the Eskimos have for snow'' entails ``Eskimos have many words for snow'', even though this claim is never stated explicitly.
 
@@
 For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''.
-In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be reliably detected.
 
@@
 	\begin{center}
-	\includegraphics[width=5cm]{pictures/mark_disputed.png}
+	\includegraphics[width=6cm]{pictures/mark_disputed.png}
 	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/training2.png}
+	\includegraphics[width=7cm]{pictures/training2.png}
 	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
@@
 	\includegraphics[width=8cm]{pictures/nlp_client_server2.png}
-	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
+	\caption{Client-side entailment: matching happens on the client, using a database downloaded from the server.}
 	\label{nlp_client_server}
@@
 	\begin{center}
-	\includegraphics[width=8cm]{pictures/paraphrases.png}
+	\includegraphics[width=8cm]{pictures/paraphrases2.png}
 	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
@@
 	\begin{center}
-	\includegraphics[width=5cm]{pictures/article_choose_claim.png}
+	\includegraphics[width=5.5cm]{pictures/article_choose_claim.png}
 	\caption{Choose how to connect an article with a claim.}
@@
 Unfortunately, as Pew Research discovered~\cite{PewResearch2008} when looking at TV news, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view.
-It seems that ``without a point of view'' is a similar concept to ``without an accent''.
 Similarly, Manjou~\cite{Manjou2008} reports that people tend to measure the credibility of a source based on how well it fits with what they already believe to be true.
@@
 	\begin{center}
-	\includegraphics[width=7.5cm]{pictures/popup_graph_crop.png}
+	\includegraphics[width=8cm]{pictures/popup_graph_crop.png}
 	\caption{Argumentation graph interface for a disputed claim}
@@
 Several users got confused by claims that referred to similar events at different points in time.
-For example, one participant in the first study marked one claim as opposing another claim when they were referring to similar incidents that occurred at different times.
+For example, one participant in the first study marked one claim as opposing another  when they were referring to similar incidents that occurred at different times.
 

### 2010-02-22 papers/www_disputefinder/disputefinder_final.tex
Minor changes to final version - largely suggested by Beth

@@
 %\documentclass{article}
-\documentclass{www2010-submission}
+\documentclass{www2010-accepted}
 \usepackage{times}
@@
 \usepackage{color}
+%\usepackage{letterpaper}
+
 %
@@
 
+\widowpenalty=1000
+\clubpenalty=1000
+
 \begin{document}
 
-\toappear
+%\special{papersize=8.5in,11in}
+%\setlength{\pdfpageheight}{\paperheight}
+%\setlength{\pdfpagewidth}{\paperwidth}
+
+%\toappear
 
@@
 
-\additionalauthors{Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}
+\additionalauthors{Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\texttt{[tye.l.rattenbury,tad.hirsch]@intel.com}}
 
@@
 	\begin{center}
-	\includegraphics[width=6cm]{pictures/highlight_vaccine_shadow.png}
+	\includegraphics[width=7.5cm]{pictures/highlight_vaccine_shadow.png}
 	\caption{Dispute Finder highlights text snippets that make disputed claims.}
@@
 	\begin{center}
-	\includegraphics[width=7.5cm]{pictures/popup_vaccine_shadow.png}
+	\includegraphics[width=8.5cm]{pictures/popup_vaccine_shadow_big.png}
 	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
@@
 
-\begin{figure}[tb]
-	\begin{center}
-	\includegraphics[width=8.5cm]{pictures/snippet_claim_article_fancy3.png}
-	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
-	\label{snippet_claim_article}
-	\end{center}
-\end{figure}
-
 \subsection{Personas}
@@
 This has lead to a growing set of tools that aim to help users deal with disputed and biased information.
+
+\begin{figure}[tb]
+	\begin{center}
+	\includegraphics[width=8.5cm]{pictures/snippet_claim_article_fancy3.png}
+	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
+	\label{snippet_claim_article}
+	\end{center}
+\end{figure}
 
@@
 
-On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
+On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and WikiScanner.virgil.gr finds cases where a Wikipedia edit has been made by someone with a conflict of interest.
 These tools have a similar aim to Dispute Finder, but are limited to Wikipedia.
@@
 In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.
-
-\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
-\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
-\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}
-\todo{Should we explicitly list what we think are our key contributions?}
 
@@
 	\includegraphics[width=8cm]{pictures/add_claim_list.png}
-	\caption{A user can use this interface to add a new disputed claim manually.}
+	\caption{Interface to add a new disputed claim manually.}
 	\label{add_claim}

### 2010-02-23 papers/www_disputefinder/disputefinder_final.tex
Fixed widow, as requested by printing people

@@
 	\begin{center}
-	\includegraphics[width=8.5cm]{pictures/popup_vaccine_shadow_big.png}
+	\includegraphics[width=8.5cm]{pictures/popup_vaccine_shadow_big2.png}
 	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
@@
 
-While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
+\looseness -1
+While Dispute Finder would likely improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown.
 We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.
@@
 
+\looseness -1
 Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them (e.g.

### 2010-02-24 papers/wicow_claimfinder/claimfinder_final.tex
Starting work on camera-ready version of the WICOW paper
Making changes requested by reviewers and updating for a bigger data set

--- 2010-02-09 papers/wicow_claimfinder/claimfinder.tex
@@
 In practice, many of the strings that match such a pattern are not well-formed disputed claims.
-We use a statistical classifier to select only those strings that appear to make a well-formed unambigous claim.
+We use a statistical classifier to select only those strings that appear to make a well-formed unambiguous claim.
 
@@
 We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}.
-It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010.
-This amounts to approximately 1.1 million strings that our classifier believes are making disputed claims.
+It currently contains claims extracted from pages written on the days between October 1st 2009 and January 31st 2010, and pages written between January 1st and January 31st of every year from 2000 to 2010.
+This amounts to approximately 3.6 million strings that our classifier believes are making disputed claims.
 We plan to expand our corpus as we crawl more of the web and improve our algorithms.
@@
 We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS.
-For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.
+For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 10 2010''}.
 
@@
 
-Whether a claim is unambiguous is ofter subjective.
+Whether a claim is unambiguous is often subjective.
 For example, in the string ``Obama is the president'' it is possible that ``Obama'' is referring to someone other than ``Barack Obama'' and ``the president'' is referring to a position other than ``President of the United States''.
@@
 	\begin{center}
-	\includegraphics[width=18cm]{images/2by5.pdf}
+	\includegraphics[width=18cm]{images/2by5_bigger.pdf}
 	\caption{Number of claims containing a particular noun on January 10th of any particular year}
@@
 We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010.
-This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims.
-This does not mean that there are 1.1 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.
+This gave us a total of 6.1 million text strings, of which 3.6 million were identified by our classifier as being unambiguous disputable claims.
+This does not mean that there are 3.6 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.
 
@@
 We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims.
-We then analyzed the distribution of noun frequencies in claims made on January 10th of every year from 2000 to 2010.
-Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}).
+We then analyzed the distribution of noun frequencies in claims made between January 1st and January 31st of every year from 2000 to 2010.
+Although the date we searched for was in January, the claims we found are often from other points in the year, due to the noisy nature of our date search mechanism (Figure~\ref{dateaccuracy}).
 We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}).
@@
 His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
+We believe that most of the mentions of Obama before 2004 are due to date classification errors.
  \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
  \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
- \item {\bf Israe:} The Gaza conflict of 2007 caused a big spike.  
+ \item {\bf Israel:} Spikes seem to correspond to the 2009 Gaza conflict and the 2006 Lebanon conflict.
 \end{itemize}
@@
 Most of these will make sense to people who have been following news in the United States.
-For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alledged statement that Israel should be wiped off the map (which the authors had not previously realized was a disputed).
+For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alleged statement that Israel should be wiped off the map (which the authors had not previously realized was a disputed).
 Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.
@@
 
-Our data set currently includes approximately 1.1 million records. In the future we intend to expand this by several orders of magnitude.
+Our data set currently includes approximately 3.6 million records. In the future we intend to expand this by several orders of magnitude.
 

### 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
Making more changes to the WICOW paper requested by reviewers

@@
 It currently contains claims extracted from pages written on the days between October 1st 2009 and January 31st 2010, and pages written between January 1st and January 31st of every year from 2000 to 2010.
-This amounts to approximately 3.6 million strings that our classifier believes are making disputed claims.
+This amounts to approximately 4.2 million strings that our classifier believes are making disputed claims.
 We plan to expand our corpus as we crawl more of the web and improve our algorithms.
@@
 Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing; some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.
-These metrics do a good job at detecting pages that resemble pages that contain unreliable information, but they do not protect against authors who write untrustworthy information in the style of a trustworthy document.
+These metrics do a good job of detecting pages that resemble pages that contain unreliable information, but they do not protect against authors who write untrustworthy information in the style of a trustworthy document.
 
 In our research, we are following a third approach.
-We aim to inform users when information that they encounter is disputed by another source.
-We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed.
-For example, if a user is reading a page that says ``Elvis is alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
+We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed by another source.
+For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder knows about another page that argues that this claim is false, then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
 In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to the corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
@@
 Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another.
+Kawahara et al~\cite{Kawahara2008} and Statement Map~\cite{Murakami2009} use contradiction detection to inform a user when a set of documents contain claims that appear to contradict each other.
 The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.
@@
 If a page says ``Falsely claimed that Obama is a Muslim'' then that suggests that the contradiction with ``Obama is a Muslim'' is likely to be genuine.
-The corresponding disadvantage would be that if one looks for disputes, one would only detect contradictions that humans have found and believe are important.
+The corresponding disadvantage would be that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.
 
@@
 Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.
+To put it another way, Dispute Finder can be thought of as a second order of opinion mining in which we are looking for opinions about opinions.
 
@@
 	\begin{center}
-	\includegraphics[width=18cm]{images/2by5_bigger.pdf}
-	\caption{Number of claims containing a particular noun on January 10th of any particular year}
+	\includegraphics[width=18cm]{images/2by5_bigger3_small.pdf}
+	\caption{Number of claims containing a particular noun made during January of any particular year}
 	\label{multiplot_nouns}
@@
 We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010.
-This gave us a total of 6.1 million text strings, of which 3.6 million were identified by our classifier as being unambiguous disputable claims.
-This does not mean that there are 3.6 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.
+This gave us a total of 7 million text strings, of which 4.2 million were identified by our classifier as being unambiguous disputable claims.
+This does not mean that there are 4.2 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.
 
@@
 
-Our data set currently includes approximately 3.6 million records. In the future we intend to expand this by several orders of magnitude.
+Our data set currently includes approximately 4.2 million records. In the future we intend to expand this by several orders of magnitude.
 

### 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
Tweaked related work to talk about contradiction detection before dispute finding

@@
 
-In our research, we are following a third approach.
-We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed by another source.
-For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder knows about another page that argues that this claim is false, then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view.
-In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to the corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.
+A third approach is to inform a user when a document contains information that other sources disagree with.
+Annotation tools such as ReframeIt.com, ShiftSpace.org, and SpinSpotter.com allow a user to manually annotate a web page that they disagree with, overlaying their own opinions on top of existing content.
+Cohere~\cite{Shum2008} allows a user to manually annotate a web page as making a claim that is part of an argumentation graph.
+These tools work well when a user has marked up the page the user is reading, but are limited by the requirement that a human needs to manually mark up each page.
 
-Our primary motivation for automatically acquiring a large corpus of disputed claims is to use this corpus to enable tools like Dispute Finder to automatically inform users when they encounter information that this corpus says is disputed.
-However, as we discuss in Section~\ref{using}, we believe such a corpus could be useful for many other purposes too.
+In previous work, we have build an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs a user when a web page that they are reading makes a claim that it knows to be disputed by another source.
+For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder recognizes this as being an instance of a known disputed claim, then Dispute Finder will highlight the text as being disputed and direct the user to other sources that put forward alternative points of view.
+In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to its corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com).
+This approach scales better than having users manually mark individual pages, but it is still difficult to make this approach scale to the huge number of claims on the web that are disputed.
 
-The problem of detecting disputed claims is closely related to the well-studied problem of detecting contradictions.
-A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true.
-For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
-But a contradicted claim is not necessarily a disputed claim.
-In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese.
-A {\it contradiction} is logical, while a {\it dispute} is social.
-In order for a claim to be disputed, the authors of the documents must be aware that there is a contradiction between their beliefs.
+A more scalable approach is to automatically detect when web pages disagree with each other.
+Tools like Statement Map~\cite{Murakami2009} and WISDOM~\cite{Kawahara2008} use {\it contradiction detection} to inform a user when one document contains a statement that contradicts a statement on another web page.
 
@@
 Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another.
-Kawahara et al~\cite{Kawahara2008} and Statement Map~\cite{Murakami2009} use contradiction detection to inform a user when a set of documents contain claims that appear to contradict each other.
 The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.
@@
 
-We detect disputes rather than contradictions.
+In our work, we attempt to bypass the difficulty of contradiction detection by looking for {\it disputes} rather than {\it contradictions}.
 Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important.
-One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important.
-If a page says ``Falsely claimed that Obama is a Muslim'' then that suggests that the contradiction with ``Obama is a Muslim'' is likely to be genuine.
-The corresponding disadvantage would be that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.
-
-Perhaps more importantly, for our purposes disputes are more interesting than contradictions.
+Looking for disputes rather than contradictions allows humans to do the hard work of identifying contradictions and deciding whether they are important.
+If a page says ``Falsely claimed that Obama is a Muslim'' then that tells us that the author believes that other web pages are claiming that ``Obama is a Muslim'' and that the author believes this claim is false.
+For our purposes, disputes are also more interesting than contradictions.
 We are interested in the social side of dispute.
 We want to know who disagrees with who, why they disagree, and what they think is important.
+
+One disadvantage of looking for disputed claims rather than contradictions is that it limits us to only finding those claims that some human has explicitly said they disagree with.
+For a small corpus this would be a limiting factor; however our hypothesis is that the web is sufficiently large that, at least for areas of general interest, any sufficiently important claim that is false will be explicitly disputed by somebody.
+
+Our primary motivation for automatically acquiring a large corpus of disputed claims is to use this corpus to enable tools like Dispute Finder to automatically inform users when they encounter information that this corpus says is disputed.
+However, as we discuss in Section~\ref{using}, we believe such a corpus could be useful for many other purposes too.
 

### 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
Tidy up pass

@@
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate}
 \usepackage{times}
@@
 
+\def\shortpage{\enlargethispage{-\baselineskip}}
+
 \begin{document}
-
-\toappear
+\conferenceinfo{WICOW'10,} {April 27, 2010,  Raleigh, North Carolina, USA.} 
+\CopyrightYear{2010}
+\crdata{978-1-60558-940-4/10/04}
+\clubpenalty=10000
+\widowpenalty = 10000
 
@@
 
-We present a method for the automatic acquisition of a corpus of disputed claims from the web.
-We consider a factual claim to be a {\it disputed claim} if a page on the web suggests both that the claim is false and also that other people say it is true.
+We present a method for automatically acquiring of a corpus of disputed claims from the web.
+We consider a factual claim to be {\it disputed} if a page on the web suggests both that the claim is false and also that other people say it is true.
 
@@
 \section{Introduction}
+
+\shortpage
 
@@
 
-In previous work, we have build an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs a user when a web page that they are reading makes a claim that it knows to be disputed by another source.
-For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder recognizes this as being an instance of a known disputed claim, then Dispute Finder will highlight the text as being disputed and direct the user to other sources that put forward alternative points of view.
+In previous work, we built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs a user when a web page makes a claim that is in its database of known disputed claims.
+For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder recognizes this as being an instance of a known disputed claim, then Dispute Finder will highlight the text as being disputed and direct the user to web pages that put forward alternative points of view.
 In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to its corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com).
@@
 
-In our work, we attempt to bypass the difficulty of contradiction detection by looking for {\it disputes} rather than {\it contradictions}.
+In our work, we attempt to bypass the difficulty of contradiction detection by looking for {\it disputes} rather than contradictions.
 Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important.
@@
 If a page says ``Falsely claimed that Obama is a Muslim'' then that tells us that the author believes that other web pages are claiming that ``Obama is a Muslim'' and that the author believes this claim is false.
-For our purposes, disputes are also more interesting than contradictions.
-We are interested in the social side of dispute.
-We want to know who disagrees with who, why they disagree, and what they think is important.
+For our purposes, disputes are also more interesting than contradictions; we are interested in the social side of dispute; we want to know who disagrees with who, why they disagree, and what they think is important.
 
@@
 Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects.
-A focal application has been the automatic summarization of product reviews, to produce an overview of the product features that are viewed favorably or negatively.
+A focal application has been automatically summarizing of product reviews to produce an overview of the product features that are viewed favorably or negatively.
 Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.
-To put it another way, Dispute Finder can be thought of as a second order of opinion mining in which we are looking for opinions about opinions.
+To put it another way, dispute mining can be thought of as a second order of opinion mining in which we are looking for opinions about opinions.
 
@@
 This is an instance of pattern matching, a method that has been used extensively for many NLP tasks.
-Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms; Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type; Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms; and TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
+Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms; Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type; Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms; and Text-Runner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
 These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed.
@@
 
-In this work we simply start with an initial set of manually crafted search patterns.
-We then identified additional patterns by searching for the text of known disputed claims, observing what text commonly occurred as a prefix of a known disputed claim, and manually selected those patterns that made sense to us.
-This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class.
+In this work we started with an initial set of manually crafted search patterns.
+We then identified additional patterns by searching for the text of known disputed claims, observing what text commonly occurred as a prefix of a known disputed claim, and manually choosing those patterns that made sense to us.
+This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed items that belong to a semantic class of interest and use these seed items to learn extraction patterns that can be used to find new members of the same semantic class.
 In our case, the semantic entities of interest are the disputed claims.
-Currently, we {\em manually} choose the patterns and claims to retain, i.e., as oppose to most relevant work, we don't {\em learn} the patterns and we don't use a measure of "reliability."
+Currently, we {\em manually} choose the patterns to retain, rather than having the algorithm pick the patterns automatically.
 
@@
 Since we are using a general purpose search engine, we are limited to searching for simple text strings.
-This requires us to generate multiple patterns that are almost the same, other than for synonyms, for example we have both ``the lie that'' vs ``the deceit that''.
+This requires us to generate multiple patterns that use different synonyms of the same word; for example we have both ``the lie that'' and ``the deceit that''.
 We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix.
@@
 
-In the longer term we may work round these issues by building our own search infrastructure, but Yahoo BOSS provides an excellent platform for prototyping an idea and seeing if it works.
+In the longer term we may work round these issues by building our own search infrastructure, but Yahoo BOSS provides an excellent platform for prototyping the idea to see if it works.
 
@@
 Despite being very primitive, this method seems to work reasonably well.
-When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).
+When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% were written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).
 We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).
@@
 
+\begin{figure*}[tb]
+	\begin{center}
+	\includegraphics[width=18.1cm]{images/2by5_bigger3_small.pdf}
+	\caption{Number of claims containing a particular noun made during January of any particular year}
+	\label{multiplot_nouns}
+	\end{center}
+	\vspace{0.6cm}
+\end{figure*}
+
 \subsection{Filtering Claims}
@@
 Searching the web for patterns yields a collection of strings.
-From this collection, we want to filter out any strings that are not making a falsifiable claim, and any strings that make a claim that is ambiguous.
+From this collection we want to filter out any strings that are not making a falsifiable claim and any strings that make a claim that is ambiguous.
 
 Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we want to filter some of them out.
-A chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).
+A chunk of text might not be a statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).
 
@@
 We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim.
-This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification).
-Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}).
+This is a classical text classification task where the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification).
+Naive Bayes classifiers~\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of a document~\cite{mccallum98comparison}).
 We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and part-of-speech tag of the first and second words.
+
+\shortpage
 
@@
 For example ``he claimed that the moon was made of cheese {\it on his show}'' or ``he claimed that the moon is made of cheese {\it despite contrary evidence}''.
-We chop off such suffixes by discarding any text that follows a word such as ``despite'', ``however'', ``but'', or ``was'', provided that word was proceeded by either two noun phrases or a noun phrase and an adjective.
-
-\begin{figure*}[tb]
-	\begin{center}
-	\includegraphics[width=18cm]{images/2by5_bigger3_small.pdf}
-	\caption{Number of claims containing a particular noun made during January of any particular year}
-	\label{multiplot_nouns}
-	\end{center}
-\end{figure*}
+We chop off such suffixes by discarding any text that follows a word such as ``despite'', ``however'', ``but'', or ``was'', provided that word was proceeded by something that looks like a statement.
 
@@
 
-A corpus of disputed claims could be useful for many purposes, including real-time dispute recognition, background dispute analysis agents, and other research tools.
-Real-time dispute recognition agents could be used, for instance, to alert users when a trusted source disagrees with others, or to provide the user with feedback on how contentious a topic is.
+There are many potential uses for a corpus of disputed claims.
 
-Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that users encounter in their lives.
-The current implementation of Dispute Finder is a web browser extension that highlights text on web pages that appears to make a known disputed claim.
-In future research, we plan to extend Dispute Finder to be able to detect disputed information in television, and in speech that a user hears during conversations.
-We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation.
-Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.
+In previous work, we have built Dispute Finder~\cite{Ennals2010}, a web browser extension that informs a user if the page they are browsing appears to make claims that are disputed by other sources.
+In the future, we intend that Dispute Finder will consult our corpus of disputed claims to determine whether claims made on a web page are disputed.
 
-Dispute analysis agents that run in the background represent another application we see for a corpus of disputed claims.
-Such agents could be trained with information regarding the books, journals, and news articles a user reads.
-It would then be able to track these subjects and alert the user when a previously-read source is now disputed.
-It could also track a set of topics and tell the user when something new is disputed about a topic.
-A background dispute analysis agent would thus serve as an automated research assistant.
+In future work, we intend to apply a similar dispute-finding approach to many other sources of information.
+We are working on a tool that listens to conversations and informs a user if they hear or say anything that is disputed by a reliable source.
+We are also interested in enhancing standard tools such as search engines, news aggregators, news readers, and email clients to inform a user if the information they are consuming may be disputed.
 
-A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the social dynamics of disputes on the web.
-As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.
+Since information may only become disputed after you read it, we are also interested in building tools that track all the information a user consumes and alert the user if something they read in the past ceases to be true, is corrected, or becomes disputed.
+Such a tool could also track the topics a user is interested in and inform the user when something new is disputed about the topic.
+
+A third category of applications could be broadly classified as research tools: tools that allow a user to explore what is disputed about a particular topic, or to more broadly examine the social dynamics of disputes on the web.
+As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly useful for sociological and historical research.
 
@@
 
-We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010.
+We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 31st 2010, and for all dates from January 1st to January 31st for every year from 2000 to 2010.
 This gave us a total of 7 million text strings, of which 4.2 million were identified by our classifier as being unambiguous disputable claims.
-This does not mean that there are 4.2 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.
+This does not mean that there are 4.2 million distinct beliefs that are disputed, since many of the claims in our corpus are repeating claims made elsewhere in the corpus.
 
@@
 
-Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years.
+Figure~\ref{multiplot_nouns} shows the frequency with which the ten most common nouns were mentioned in particular years.
 For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''.
 We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims.
-We then analyzed the distribution of noun frequencies in claims made between January 1st and January 31st of every year from 2000 to 2010.
-Although the date we searched for was in January, the claims we found are often from other points in the year, due to the noisy nature of our date search mechanism (Figure~\ref{dateaccuracy}).
+We then analyzed the distribution of noun frequencies in claims made between January 1st and January 31st of each year from 2000 to 2010.
+Although the dates we searched for were in January, the claims we found are often from other points in the year, due to the noisy nature of our date search mechanism (Figure~\ref{dateaccuracy}).
 We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}).
@@
 The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made.
-It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even these nouns prove to be quite interesting.
-
-We manually inspected our claims to determine what was going on that made particular nouns spike at particular times:
-
-\begin{itemize}
- \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention.
-His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
-We believe that most of the mentions of Obama before 2004 are due to date classification errors.
- \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
- \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
- \item {\bf Israel:} Spikes seem to correspond to the 2009 Gaza conflict and the 2006 Lebanon conflict.
-\end{itemize}
-
-These graphs are similar to those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web.
-MemeTracker tracked highly repeated phrases, rather than nouns used in disputed claims.
-Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.
+It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even nouns prove to be quite interesting.
 
@@
     \hline
-   {\bf children} & tiger woods abused & 218\\
-                  & instead encourage daily & 178\\
+   {\bf god} & {\it no significant clusters} & \\
    \hline
-   {\bf god} & daily encourage parents & 150 \\
+   {\bf government} & health care & 2605 \\
+                    & united states & 1710 \\
    \hline
-   {\bf government} & health care & 1267 \\
-                    & united states & 427 \\
-		    & relation environmental matters & 155 \\
+   {\bf iraq} & weapons mass destruction & 3874 \\
+              & united states & 2972 \\
+	      & posed imminent threat & 2547 \\
+	      & saddam hussean & 2088 \\
+	      & damaging manner justify armed forces & 1814 \\
+	      & national security interests & 1673 \\
+	      & use nation & 1503 \\
+	      & al qaeda & 1200 \\
    \hline
-   {\bf iraq} & weapons mass destruction & 373 \\
-              & united states & 247 \\
-	      & saddam hussein & 192 \\
-	      & al qaeda & 149 \\
+   {\bf israel} & united states & 1211 \\
+		& middle east & 556 \\
+		& off map & 543 \\
+                & west bank & 426 \\
+		& second coming & 296 \\
    \hline
-   {\bf israel} & middle east & 251 \\
-		& allowed upon population & 128 \\
-                & united states & 107 \\
-		& off map & 106 \\
+   {\bf jesus}  & {\it no significant clusters} & \\
    \hline
-   {\bf law}    & lawbreaker rather broken & 133 \\
-		& united states & 116\\
+   {\bf money}  & root evil & 503 \\
    \hline
-    {\bf obama} & working best interests & 568\\
-                & health care & 481\\
-	        & united states & 327 \\
-		& nobel prize & 270 \\
-		& legitimately president & 207 \\
-		& fort hood shooter hasan nidal advised & 190 \\
-		& birth certificate & 180\\
+    {\bf obama} & working best interests & 1077\\
+                & health care & 1074\\
+	        & united states & 741 \\
+		& birth certificate & 434 \\
+		& nobel prize & 311 \\
    \hline
-   {\bf president} & united states & 439 \\
-                   & health care & 203 \\
-		   & george w & 164 \\
-		   & aircraft system jolting bombing & 159 \\
-		   & peace prize & 125 \\
-		   & white house & 125 \\
+   {\bf president} & united states & 1695 \\
+		   & white house & 716 \\
+		   & george w & 618 \\
+		   & health care & 491 \\
+		   & saddam hussein & 369 \\
+		   & off map & 363 \\
+		   & mahmoud ahmadinejad & 320 \\
+		   & sarah palin & 277 \\
    \hline
-      {\bf war} & united states & 340 \\
+      {\bf war} & united states & 1323 \\
+		& mass destruction & 484 \\
+		& middle east & 421 \\
    \hline
 
-   {\bf women} & stay home & 183 \\
-               & save vaccine & 85 \\
+   {\bf women} & {\it no significant clusters} & \\
    \hline
@@
 \end{figure}
+
+We manually inspected our claims to determine what was going on in the world that made particular nouns spike at particular times:
+
+\begin{itemize}
+ \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention.
+His level of controversy then rose in 2008, in the run up to the November 2008 US presidential elections and then again after he became president.
+We believe that most of the mentions of Obama before 2004 are due to date classification errors.
+ \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
+ \item {\bf Iraq:} The biggest spike seems to correspond to the initial invasion in 2003.
+ \item {\bf Israel:} Spikes seem to correspond to the 2009 Gaza conflict and the 2006 Lebanon conflict.
+\end{itemize}
+
+These graphs are similar to those produced by MemeTracker~\cite{Backstrom2009}, which graphed the times when particular memes were discussed on the web.
+MemeTracker tracked frequently occurring phrases, rather than nouns used in disputed claims.
+Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.
 
@@
 Most of these will make sense to people who have been following news in the United States.
-For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alleged statement that Israel should be wiped off the map (which the authors had not previously realized was a disputed).
+For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alleged statement that Israel should be wiped off the map (which the authors had not previously realized was disputed).
 Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.
+
+It would be interesting to see how these word clusters compare to word clusters for all sentences on the web about these nouns, including those that are not disputed.
+Unfortunately we do not currently have access to such data.
 

### 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
Spelling fixes

@@
 
-\title{What is disputed on the web?}
+\title{What is Disputed on the Web?}
 
@@
 	      & posed imminent threat & 2547 \\
-	      & saddam hussean & 2088 \\
+	      & saddam hussein & 2088 \\
 	      & damaging manner justify armed forces & 1814 \\

### 2010-03-07 papers/wicow_claimfinder/wicow18e-ennals.tex
Trying to improve claim quality. Improved search engine entailment. Final versions of papers

--- 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
@@
 % people who are not mendeley users
-\bibliography{mendeleybib,localbib}
+
+\begin{thebibliography}{10}
+
+\bibitem{Adler2008b}
+B~Thomas Adler, Krishnendu Chatterjee, Luca~De Alfaro, Marco Faella, Ian Pye,
+  and Vishwanath Raman.
+\newblock {Assigning Trust to Wikipedia Content}.
+\newblock In {\em WikiSym}, 2008.
+
+\bibitem{Banko2008}
+M.~Banko, O.~Etzioni, and T.~Center.
+\newblock {The tradeoffs between open and traditional relation extraction}.
+\newblock In {\em Proceedings of the 46th Annual Meeting of the Association for
+  Computational Linguistics (ACL-08)}, 2008.
+
+\bibitem{Bird2009}
+Steven Bird, Ewan Klein, and Edward Loper.
+\newblock {\em {Natural Language Processing with Python}}.
+\newblock O'Reilly, 2009.
+
+\bibitem{Blumenstock2008}
+Joshua~E Blumenstock.
+\newblock {Size Matters: Word Count as a Measure of Quality on Wikipedia}.
+\newblock {\em Computing}, pages 2007--2008, 2008.
+
+\bibitem{Caraballo2001}
+Sharon Caraballo.
+\newblock {\em {Automatic construction of a hypernym-labeled noun hierarchy
+  from text Sharon A. Caraballo}}.
+\newblock Phd, Brown University, 2001.
+
+\bibitem{Condoravdi2003}
+Cleo Condoravdi, Dick Crouch, Valeria de~Paiva, Reinhard Stolle, and Daniel~G.
+  Bobrow.
+\newblock {Entailment, intensionality and text understanding}.
+\newblock In {\em Proceedings of the HLT-NAACL 2003 workshop on Text meaning
+  -}, pages 38--45, Morristown, NJ, USA, 2003. Association for Computational
+  Linguistics.
+
+\bibitem{Custard2005}
+Myra Custard and Tamara Sumner.
+\newblock {Using Machine Learning to Support Quality Judgements}.
+\newblock {\em D-Lib Magazine}, 11(10), 2005.
+
+\bibitem{Dawkins2006}
+Richard Dawkins.
+\newblock {\em {The God Delusion}}.
+\newblock Houghton Mifflin Harcourt, 2006.
+
+\bibitem{deMarneffe2008}
+M.C. de~Marneffe, A.N. Rafferty, and C.D. Manning.
+\newblock {Finding contradictions in text}.
+\newblock In {\em Proceedings of the 46th Annual Meeting of the Association for
+  Computational Linguistics (ACL-08)}, 2008.
+
+\bibitem{duda}
+R.~O. Duda, P.~E. Hart, and D.~G. Stork.
+\newblock {\em Pattern Classification}.
+\newblock Wiley-Interscience Publication, 2000.
+
+\bibitem{Ennals2010}
+Rob Ennals, Beth Trushkowsky, John~Mark Agosta, Tye Rattenbury, and Tad Hirsch.
+\newblock {Highlighting Disputed Claims on the Web}.
+\newblock In {\em Proceedings of the 19th international conference on World
+  Wide Web - WWW 2010}, 2010.
+
+\bibitem{Etzioni2008}
+Oren Etzioni, Michele Banko, Stephen Soderland, and Daniel~S Weld.
+\newblock {Open information Extraction from the Web}.
+\newblock {\em Communications of the ACM}, 51(12), 2008.
+
+\bibitem{Fogg2003}
+B~J Fogg, Persuasive~Technology Lab, Cordura Hall, Cathy Soohoo, David~R
+  Danielson, Ellen~R Tauber, Sliced~Bread Design, Mountain View, Julianne
+  Stanford, Leslie Marable, and Consumer Webwatch.
+\newblock {How Do Users Evaluate the Credibility of Web Sites? A Study with
+  Over 2,500 Participants}.
+\newblock {\em World Wide Web Internet And Web Information Systems}, pages
+  1--15, 2003.
+
+\bibitem{Giampiccolo2007}
+D.~Giampiccolo, B.~Magnini, I.~Dagan, and B.~Dolan.
+\newblock {The third pascal recognizing textual entailment challenge}.
+\newblock In {\em Proceedings of the ACL-PASCAL Workshop on Textual Entailment
+  and Paraphrasing}, number June, page 1–9, 2007.
+
+\bibitem{Girju2003}
+Roxana Girju, Adriana Badulescu, and Dan Moldovan.
+\newblock {Learning semantic constraints for the automatic discovery of
+  part-whole relations}.
+\newblock In {\em Proceedings of HLT/NAACL}, volume~3, 2003.
+
+\bibitem{Harabagiu2006}
+S.~Harabagiu, A.~Hickl, and F.~Lacatusu.
+\newblock {Negation, contrast and contradiction in text processing}.
+\newblock In {\em Proceedings of the National Conference on Artificial
+  Intelligence}, volume~21, page 755. Menlo Park, CA; Cambridge, MA; London;
+  AAAI Press; MIT Press; 1999, 2006.
+
+\bibitem{Hearst1992}
+Marti~a. Hearst.
+\newblock {Automatic acquisition of hyponyms from large text corpora}.
+\newblock In {\em Computational linguistics}, Morristown, NJ, USA, 1992.
+  Association for Computational Linguistics.
+
+\bibitem{Hu2004}
+Minqing Hu and Bing Liu.
+\newblock {Mining and summarizing customer reviews}.
+\newblock {\em Proceedings of the 2004 ACM SIGKDD international conference on
+  Knowledge discovery and data mining - KDD '04}, page 168, 2004.
+
+\bibitem{jones99bootstrapping}
+Rosie Jones, Andrew McCallum, Kamal Nigam, and Ellen Riloff.
+\newblock Bootstrapping for text learning tasks.
+\newblock In {\em IJCAI-99 Workshop on Text Mining: Foundations, Techniques and
+  Applications}, 1999.
+
+\bibitem{Kawahara2008}
+Daisuke Kawahara, Sadao Kurohashi, and Kentaro Inui.
+\newblock {Grasping Major Statements and Their Contradictions Toward
+  Information Credibility Analysis of Web Contents}.
+\newblock {\em 2008 IEEE/WIC/ACM International Conference on Web Intelligence
+  and Intelligent Agent Technology}, pages 393--397, 2008.
+
+\bibitem{Kittur2009}
+Aniket Kittur, Ed~H Chi, and Bongwon Suh.
+\newblock {What's in Wikipedia? Mapping Topics and Conflict Using Socially
+  Annotated Category Structure}.
+\newblock In {\em CHI}, pages 1509--1512, 2009.
+
+\bibitem{Backstrom2009}
+Jure Lescovec, Lars Backstrom, and Jon Kleinberg.
+\newblock {Meme-tracking and the Dynamics of the News Cycle}.
+\newblock 2009.
+
+\bibitem{mccallum98comparison}
+A.~McCallum and K.~Nigam.
+\newblock A comparison of event models for naive bayes text classification,
+  1998.
+
+\bibitem{Mihalcea2007}
+Rada Mihalcea and Andras Csomai.
+\newblock {Wikify! Linking Documents to Encyclopedic Knowledge}.
+\newblock In {\em CIKM}, pages 233--241, 2007.
+
+\bibitem{Murakami2009}
+Koji Murakami, Eric Nichols, Suguru Matsuyoshi, Asuka Sumida, Shouko Masuda,
+  Kentaro Inui, and Yuji Matsumoto.
+\newblock {Statement Map: Assisting Information Credibility Analysis by
+  Visualizing Arguments}.
+\newblock In {\em Workshop on Information Credibility on the Web (WICOW)},
+  2009.
+
+\bibitem{Nadeau2007}
+D.~Nadeau and S.~Sekine.
+\newblock {A survey of named entity recognition and classification}.
+\newblock {\em Linguisticae Investigationes}, 30(1), 2007.
+
+\bibitem{Palmer.2001}
+Frank~Robert Palmer.
+\newblock {\em Mood and Modality}.
+\newblock Cambridge Univesity Press, 2001.
+
+\bibitem{Pang2004}
+Bo~Pang and Lillian Lee.
+\newblock {A Sentimental Education: Sentiment Analysis Using Subjectivity
+  Summarization Based on Minimum Cuts}.
+\newblock In {\em Proceedings of the Association for Computational
+  Linguistics}, 2004.
+
+\bibitem{Riloff1993}
+E.~Riloff.
+\newblock {Automatically constructing a dictionary for information extraction
+  tasks}.
+\newblock In {\em Proceedings of the National Conference on Artificial
+  Intelligence}, 1993.
+
+\vfill\eject
+
+\bibitem{Ritter}
+Alan Ritter, Doug Downey, Stephen Soderland, and Oren Etzioni.
+\newblock {It's a Contradiction - No, it's Not: A Case Study using Functional
+  Relations}.
+\newblock In {\em Proceedings of the Conference on Empirical Methods in Natural
+  Language Processing}, 2008.
+
+\bibitem{Sahami98abayesian}
+Mehran Sahami, Susan Dumais, David Heckerman, and Eric Horvitz.
+\newblock A bayesian approach to filtering junk e-mail.
+\newblock In {\em Proceedings of the AAAI'98 Workshop on Learning for Text
+  Categorization}, 1998.
+
+\bibitem{Shum2008}
+Simon~Buckingham Shum.
+\newblock {Cohere: Towards Web 2.0 Argumentation}.
+\newblock In {\em Computational Models of Argument (COMMA)}, volume~44, 2008.
+
+\bibitem{Snow2005}
+R.~Snow, D.~Jurafsky, and A.Y. Ng.
+\newblock {Learning syntactic patterns for automatic hypernym discovery}.
+\newblock In {\em Advances in Neural Information Processing Systems},
+  volume~17. Citeseer, 2005.
+
+\bibitem{yahoo-boss}
+Yahoo {BOSS}.
+\newblock \url{http://developer.yahoo.com/search/boss/}.
+
+\end{thebibliography}
 

### 2010-03-07 papers/www_disputefinder/wfp0406_ennals.tex
Trying to improve claim quality. Improved search engine entailment. Final versions of papers

--- 2010-02-23 papers/www_disputefinder/disputefinder_final.tex
@@
 
-\todo{Add count of disputed claims}
+\begin{thebibliography}{10}
 
-%\section{Acknowledgments}
+\bibitem{Adler2008a}
+B~Thomas Adler and Ian Pye.
+\newblock {Measuring Author Contributions to the Wikipedia ∗}.
+\newblock In {\em WikiSym}, 2008.
 
-\todo{Do we want to have acknowledgements}
-% We would like to Thank Barbara Rosario for help with textual entailment, and 
-% Acknowledgements omitted for blind submission. Dispute Finder uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.
+\bibitem{Bayer2001}
+S.~Bayer, J.~Burger, L.~Ferro, J.~Henderson, and A.~Yeh.
+\newblock {MITRE’s Submissions to the EU Pascal RTE Challenge}.
+\newblock In {\em PASCAL Challenge Workshop on Recognizing Textual Entailment}.
+  Citeseer, 2005.
 
-\todo{Sort out bad references}
-\bibliography{refs}
+\bibitem{Bhagat2009}
+R~Bhagat, E~Hovy, and S~Patwardhan.
+\newblock {Acquiring paraphrases from text corpora}.
+\newblock In {\em K-CAP}, 2009.
+
+\bibitem{Bier2006}
+Eric~A Bier, Edward~W Ishak, and Ed~Chi.
+\newblock {Entity Workspace: an evidence file that aids memory, inference, and
+  reading}.
+\newblock In {\em Intelligence and Security Informatics}, 2006.
+
+\bibitem{Bos2005}
+Johan Bos and Katja Markert.
+\newblock {Recognising textual entailment with logical inference}.
+\newblock In {\em Human Language Technology and Empirical Methods in Natural
+  Language Processing - HLT '05}, Morristown, NJ, USA, 2005. Association for
+  Computational Linguistics.
+
+\bibitem{Bouvin2000}
+Niels~Olof Bouvin.
+\newblock {Augmenting the Web through Open Hypermedia}.
+\newblock {\em Phd Thesis, University of Aarhus}, 2000.
+
+\bibitem{Conklin1987a}
+Jeff Conklin and Michael~L Begeman.
+\newblock {gIBIS: A Hypertext Tool for Team Design Deliberation}.
+\newblock In {\em Hypertext}, 1987.
+
+\bibitem{Braz}
+R.~De~Salvo~Braz, R.~Girju, V.~Punyakanok, D.~Roth, and M.~Sammons.
+\newblock {An inference model for semantic entailment in natural language}.
+\newblock In {\em Artifical Intelligence}, volume~20. Springer, 2005.
+
+\bibitem{Diakopoulos2008}
+Nicholas Diakopoulos and Irfan Essa.
+\newblock {An Annotation Model for Making Sense of Information Quality in
+  Online Video}.
+\newblock In {\em Pragmatic Web}, 2008.
+
+\bibitem{Dinu2009}
+Georgiana Dinu and Rui Wang.
+\newblock {Inference Rules and their Application to Recognizing Textual
+  Entailment}.
+\newblock {\em Computational Linguistics}, pages 211--219, 2009.
+
+\bibitem{Etzioni2008}
+Oren Etzioni, Michele Banko, Stephen Soderland, and Daniel~S Weld.
+\newblock {Open information Extraction from the Web}.
+\newblock {\em Communications of the ACM}, 51, 2008.
+
+\bibitem{Fogg2003}
+B~J Fogg, Cathy Soohoo, David~R Danielson, Leslie Marable, Julianne Stanford,
+  and Ellen~R Tauber.
+\newblock {How Do Users Evaluate the Credibility of Web Sites? A Study with
+  Over 2,500 Participants}.
+\newblock In {\em CHI}, 2003.
+
+\bibitem{Gil2002}
+Y.~Gil and V.~Ratnakar.
+\newblock {TRELLIS: An interactive tool for capturing information analysis and
+  decision making}.
+\newblock In {\em Knowledge Engineering and Knowledge Management}. Springer,
+  2002.
+
+\bibitem{Gil2006}
+Yolanda Gil and Donovan Artz.
+\newblock {Towards Content Trust of Web Resources}.
+\newblock In {\em WWW}, pages 565--574, 2006.
+
+\bibitem{Glickman2005}
+O.~Glickman, I.~Dagan, and M.~Koppel.
+\newblock {A probabilistic classification approach for lexical textual
+  entailment}.
+\newblock In {\em Artifical Intelligence}, volume~20. Menlo Park, CA;
+  Cambridge, MA; London; AAAI Press; MIT Press; 1999, 2005.
+
+\bibitem{Golder2006}
+Scott~A Golder and Bernardo~A Huberman.
+\newblock {The Structure of Collaborative Tagging Systems}.
+\newblock {\em Journal of Information Science}, 2006.
+
+\bibitem{Gordon1997}
+Thomas~F Gordon and Nikos Karacapilidis.
+\newblock {The Zeno Argumentation Framework}.
+\newblock In {\em Artificial Intelligence and Law}, 1997.
+
+\bibitem{Hearst1992}
+Marti~a. Hearst.
+\newblock {Automatic acquisition of hyponyms from large text corpora}.
+\newblock In {\em Computational linguistics}, Morristown, NJ, USA, 1992.
+  Association for Computational Linguistics.
+
+\bibitem{Herman2002}
+Edward~S Herman and Noam Chomsky.
+\newblock {\em {Manufacturing Consent: The Political Economy of the Mass
+  Media}}.
+\newblock Pantheon, 2002.
+
+\bibitem{Hong2009}
+L.~Hong and E.H. Chi.
+\newblock {Annotate once, appear anywhere: collective foraging for snippets of
+  interest using paragraph fingerprinting}.
+\newblock In {\em CHI}. ACM New York, NY, USA, 2009.
+
+\bibitem{Isenmann1997}
+Severin Isenmann and Wolf~D Reuter.
+\newblock {IBIS - a Convincing Concept . . . But a Lousy Instrument?}
+\newblock In {\em Designing Interactive Systems (DIS)}, 1997.
+
+\bibitem{Jijkoun2006}
+Valentin Jijkoun and Maarten~De Rijke.
+\newblock {Recognizing Textual Entailment: Is Word Similarity Enough?}
+\newblock In {\em Machine Learning Challenges}, 2006.
+
+\bibitem{Koivunen2001}
+Jose Kahan and Marja-Ritta Koivunen.
+\newblock {Annotea: an open RDF infrastructure for shared Web annotations}.
+\newblock In {\em WWW}, volume~39, 2002.
+
+\bibitem{Kim2009}
+Jong~Wook Kim.
+\newblock {Ef cient Overlap and Content Reuse Detection in Blogs and Online
+  News Articles}.
+\newblock In {\em WWW}, 2009.
+
+\bibitem{Kittur2008}
+Aniket Kittur and Robert~E Kraut.
+\newblock {Harnessing the Wisdom of Crowds in Wikipedia: Quality Through
+  Coordination}.
+\newblock {\em CSCW}, pages 37--46, 2008.
+
+\bibitem{Kolak2008}
+Okan Kolak and Bill~N Schilit.
+\newblock {Generating Links by Mining Quotations}.
+\newblock In {\em Hypertext}, 2008.
+
+\bibitem{Backstrom2009}
+Jure Lescovec, Lars Backstrom, and Jon Kleinberg.
+\newblock {Meme-tracking and the Dynamics of the News Cycle}.
+\newblock In {\em Knowledge Discovery and Data Mining (KDD)}, 2009.
+
+\bibitem{Lin2001}
+Dekang Lin and Patrick Pantel.
+\newblock {DIRT – Discovery of Inference Rules from Text}.
+\newblock In {\em Knowledge Discovery and Data Mining (KDD)}, 2001.
+
+\bibitem{Manjou2008}
+Farhad Manjou.
+\newblock {\em {True Enough: Learning to Live in a Post-Fact Society}}.
+\newblock Wiley, 2008.
+
+\bibitem{Marlow2006}
+Cameron Marlow, Mor Naaman, Danah Boyd, and Marc Davis.
+\newblock {HT06, Tagging Paper, Taxonomy, Flickr, Academic Article, To Read}.
+\newblock In {\em Hypertext}, 2006.
+
+\bibitem{Olsen2004}
+Dan~R Olsen, Trent Taufer, and Jerry~Alan Fails.
+\newblock {ScreenCrayons: Annotating Anything}.
+\newblock In {\em User Interface Software and Technology}, volume~6, 2004.
+
+\bibitem{Park2009}
+Souneil Park, Seungwoo Kang, Sangyoung Chung, and Junehwa Song.
+\newblock {NewsCube: Delivering Multiple Aspects of News to Mitigate Media
+  Bias}.
+\newblock In {\em CHI}. Information Today, 2009.
+
+\bibitem{PewResearch2008}
+Pew Research.
+\newblock {The Pew Research Center Biennial News Consumption Survey}, 2008.
+
+\bibitem{Ritter}
+Alan Ritter, Doug Downey, Stephen Soderland, and Oren Etzioni.
+\newblock {It’s a Contradiction—No, it’s Not: A Case Study using
+  Functional Relations}.
+\newblock In {\em Empirical Methods in Natural Language Processing}, 2008.
+
+\bibitem{Selvin2001}
+Albert Selvin, Simon~Buckingham Shum, Maarten Sierhuis, Jeff Conklin, Beatrix
+  Zimmermann, Charles Palus, Wilfred Drath, and David Horth.
+\newblock {Compendium: Making Meetings into Knowledge Events}.
+\newblock In {\em Knowledge Technologies}, 2001.
+
+\bibitem{Sereno2004}
+Bertrand Sereno, Simon Buckingham, and Enrico Motta.
+\newblock {Semi-Automatic Annotation of Contested Knowledge on the World Wide
+  Web}.
+\newblock {\em WWW}, 2004.
+
+\bibitem{Sereno2005}
+Bertrand Sereno, Buckingham Shum, and Enrico Motta.
+\newblock {ClaimSpotter: an Environment to Support Sensemaking with Knowledge
+  Triples}.
+\newblock In {\em Intelligent User Interfaces (IUI)}, 2005.
+
+\bibitem{Shum2008}
+Simon~Buckingham Shum.
+\newblock {Cohere: Towards Web 2.0 Argumentation}.
+\newblock In {\em Computational Models of Argument (COMMA)}, volume~44, 2008.
+
+\bibitem{Snow2006}
+Rion Snow, Lucy Vanderwende, and Arul Menezes.
+\newblock {Effectively using syntax for recognizing false entailment}.
+\newblock In {\em Human Language Technology}, Morristown, NJ, USA, 2006.
+  Association for Computational Linguistics.
+
+\bibitem{Theobald2008}
+M.~Theobald, J.~Siddharth, and A.~Paepcke.
+\newblock {Spotsigs: robust and efficient near duplicate detection in large web
+  collections}.
+\newblock In {\em SIGIR}. ACM, 2008.
+
+\bibitem{Wiil1996}
+Uffe~Kock Wiil and John~J Leggett.
+\newblock {The HyperDisco Approach to Open Hypermedia Systems}.
+\newblock In {\em Hypertext}, 1996.
+
+\end{thebibliography}
 

### 2010-03-07 papers/www_disputefinder/code/make_entailment_test_data.py

@@ -1,0 +1,105 @@
+
+import urllib2
+import urllib
+import xml.dom.minidom as minidom
+import re
+import nltk
+import stopwords
+import sys
+import random
+
+bossKey = "NpeiOwLV34E5KHWPTxBix1HTRHe4zIj2LfTtyyDKvBdeQHOzlC_RIv4SmAPuBh3E";
+bossSvr = "http://boss.yahooapis.com/ysearch/web/v1";
+
+whitespace = re.compile("\s+")
+sentenceend = re.compile("[\.\!\?] ")
+wordsep = re.compile("[^\w]")
+commentre = re.compile("<!--.*-->")
+scriptre = re.compile("<script[^<]*<\/script>")
+stylere = re.compile("<style[^<]*<\/style>")
+breakre = re.compile("<\/?(div|h.|li|form|br|cite|td|tr|caption)>")
+tagre = re.compile("<\/?[^>]*>")
+
+def bossurl(phrase):
+	return bossSvr + "/"+urllib.quote_plus(phrase)+"?appid="+bossKey+"&format=xml&count=50"
+
+def convert_entities(text):
+	return text.replace("&#8217;","'").replace("&#8220;",'"').replace("&#8221;",'"').replace("&#8230;"," - ").replace("&nbsp;"," ").replace("&amp;","&").replace("&ldquq;",'"').replace("&rdquo;",'"').replace("&acute;","'").replace("&mdash;","-").replace("&quot;","'").replace("&#39;","'").replace("&#039;","'")
+
+
+def getTextFromHTML(html):
+	text = commentre.sub(" ",html.lower())
+	text = scriptre.sub(" ",text)
+	text = stylere.sub(" ",text)
+	text = breakre.sub(". ",text)
+	text = tagre.sub(" ",text)
+	text = whitespace.sub(" ",text)
+	return convert_entities(text)
+	
+def getBossUrlsForClaim(phrase):
+	url = bossurl(phrase)
+	xml = minidom.parse(urllib2.urlopen(url))
+	urlnodes = xml.getElementsByTagName("url")
+	urls = [node.childNodes[0].data for node in urlnodes]
+	return urls
+	
+def getUrlSentences(url):
+	try:
+		file = urllib2.urlopen(url,None,2000)
+		text = getTextFromHTML(file.read())
+		sentences = sentenceend.split(text)
+		return sentences
+	except URLError:
+		return []
+	
+def negated(text):
[…]

### 2010-03-07 papers/www_disputefinder/code/stopwords.py

@@ -1,0 +1,42 @@
+stopwords = set(["a", "about", "above", "above", "across", "after", "afterwards", 
+		"again", "against", "all", "almost", "alone", "along", "already", "also",
+		"although","always","am","among", "amongst", "amoungst", "amount",  "an", 
+		"and", "another", "any","anyhow","anyone","anything","anyway", "anywhere", 
+		"are", "around", "as",  "at", "back","be","became", "because","become",
+		"becomes", "becoming", "been", "before", "beforehand", "behind", "being", 
+		"below", "beside", "besides", "between", "beyond", "bill", "both", "bottom",
+		"but", "by", "call", "can", "cannot", "cant", "co", "con", "could", "couldnt", 
+		"cry", "de", "describe", "detail", "do", "done", "down", "due", "during", 
+		"each", "eg", "either", "else", "elsewhere", "empty", 
+		"enough", "etc", "even", "ever", "every", "everyone", "everything", 
+		"everywhere", "except", "few", "fifteen", "fify", "fill", "find", "fire", 
+		"first", "for", "former", "formerly", "forty", "found",  
+		"from", "front", "full", "further", "get", "give", "go", "had", "has", 
+		"hasnt", "have", "he", "hence", "her", "here", "hereafter", "hereby", 
+		"herein", "hereupon", "hers", "herself", "him", "himself", "his", "how", 
+		"however", "hundred", "ie", "if", "in", "inc", "indeed", "interest", "into", 
+		"is", "it", "its", "itself", "keep", "last", "latter", "latterly", "least", 
+		"less", "ltd", "made", "make", "many", "may", "me", "meanwhile", "might", "mill", 
+		"mine", "more", "moreover", "most", "mostly", "move", "much", "must", 
+		"my", "myself", "name", "namely", "neither", "never", "nevertheless", 
+		"next", "no", "nobody", "none", "noone", "nor", "not", 
+		"now", "nowhere", "of", "off", "often", "on", "once", "one", "only", 
+		"onto", "or", "other", "others", "otherwise", "our", "ours", "ourselves", 
+		"out", "own","part", "per", "perhaps", "please", "put", "rather", 
+		"re", "same", "see", "seem", "seemed", "seeming", "seems", "serious", 
+		"several", "she", "show", "side", "since", "sincere", "should",
+		"so", "some", "somehow", "someone", "something", "sometime", 
+		"sometimes", "somewhere", "still", "such", "system", "take",  
[…]

### 2010-03-07 web_claim_finder/filter_claims_post.py

@@ -1,0 +1,13 @@
+
+import filter_claims as f
+import fileinput
+
+def main():
+	claims = [line.strip() for line in fileinput.input()]
+	good = f.filter_claims(claims)
+	for claim in good:
+		print claim
+			
+	
+if __name__ == '__main__':
+	main()

### 2010-03-07 web_claim_finder/filter_in_file.py

@@ -1,0 +1,36 @@
+"""
+Given a file that contains all known good claims, and a file input
+filter out all the lines that are not in the known good set.
+"""
+
+import filter_claims as f
+
+good_claim_file = "../output/only_good_claims.claims"
+
+def load_good_claims(filename):
+	good = set([])
+	counter = 0
+	for line in file(filename):
+		line = line.strip()
+		line = f.cleanup(line)
+		counter += 1
+		if counter % 5000 == 0:
+			print counter
+		good.add(line)
+	return good
+	
+def filter_good_claims(filename,good):
+	outfile = file(filename.replace(".unique",".nlpgood"),"w")
+	for line in file(filename):
+		line = line.strip()
+		line = f.cleanup(line)
+		if line in good:
+			outfile.write(line+"\n")
+	outfile.close()
+	
+			
+			
+	
+		
+	
+

### 2010-03-07 web_claim_finder/join_claims_for_pattern.py

@@ -1,0 +1,22 @@
+
+import patterns as pats
+
+import os
+
+basewild = "../output/claimfinder/urlphrases_date/*/"
+
+outpath = "../output/claimfinder/phrases_joined/"
+	
+def main():	
+	for pattern in pats.prefix_patterns:
+		print "--",pattern,"--"
+		pathpat = pattern.replace(" ","_")
+		filewild = basewild+pathpat+".claims"
+		joinfile = outpath+pathpat+".claims"
+		uniqfile = outpath+pathpat+".unique"
+		os.system("cat "+filewild+" > "+joinfile)
+		os.system("python remove_duplicates.py <"+joinfile+" >"+uniqfile)
+	
+		
+if __name__ == '__main__':
+	main()

### 2010-03-07 web_claim_finder/patterns.py

@@ -1,0 +1,52 @@
+
+import re
+
+prefix_patterns = [
+			"it is not the case that",
+			"it is not true that",
+			"the misconception that",
+			"the delusion that",	
+			"disagree with the claim that",
+			"disagree with the assertion that",
+			"into believing that",
+			"people who think that",
+			"people who believe that",
+			"the myth that",
+			"the mistaken belief that",
+			"the fallacy that",
+			"the lie that",
+			"the false belief that",
+			"the deception that",
+			"the misunderstanding that",
+			"false claim that",
+			"false claim is that",
+			"mistakenly believe that",
+			"mistaken belief that",
+			"the absurd idea that",
+			"the hoax that",
+			"the deceit that",
+			"falsely claimed that",
+			"falsely claiming that",
+			"erroneously believe that",
+			"erroneous belief that",
+			"the fabrication that",
+			"falsely claim that",
+			"bogus claim that",
+			"urban myth that",
+			"urban legend that",
+			"the fantasy that",
+			"incorrectly claim that",
+			"incorrectly claimed that",
+			"incorrectly believe that",
+			"stupidly believe that",
+			"falsely believe that",
+			"wrongly believe that",
+			"falsely suggests that",
+			"falsely claims that",
+			"falsely stated that",
+			"absurdity of the claim that",
+			"false ad claiming that",
+			"crazies who believe that"
+		]
+
+pattern_regexp = re.compile("("+("|".join(["("+pat+")" for pat in prefix_patterns]))+")")

### 2010-03-07 web_claim_finder/search_templates.py

@@ -1,0 +1,6 @@
+
+head = """
+<head>
+	<title>$title</title>
+</head>
+"""

### 2010-03-07 web_claim_finder/years_csv_bigger_prop.py

@@ -1,0 +1,56 @@
+#!/usr/bin/env python
+# encoding: utf-8
+
+"""
+Generate a graph, showing how different nouns rose and fell in different years.
+"""
+import io
+import csv
+import sys
+import operator as op
+import claimfinder as cf
+import os
+
+base = "../output/claimfinder/urlphrases_date/"
+years = range(2000,2010)
+cols = 10
+writer = csv.writer(sys.stdout,delimiter=",",quotechar='"')
+
+
+
+allfreqs = {}
+yearprops = {}
+
+def add_yearfreqs(year):
+	freqs = {}
+	total = float(os.popen("cat "+base+"*_"+str(year)+".good | wc -l").next()) 
+	for day in range(1,32):
+		freqfile = file(base+"January_"+str(day)+"_"+str(year)+".freqs")
+		for line in freqfile:
+			word,count = line.split("\t")
+			count = int(count)
+			if not word in cf.stopwords:
+				freqs[word] = freqs.get(word,0) + count
+				allfreqs[word] = max(allfreqs.get(word,0),count)
+	props = {}
+	for word in freqs.keys():
+		props[word] = freqs[word] / total
+	yearprops[year] = props
+		
+def get_topwords():
+	topwordfreqs = sorted(allfreqs.iteritems(),key=op.itemgetter(1),reverse=True)
+	topwords = [tuple[0] for tuple in topwordfreqs]
+	return topwords[0:cols]
+	
+def main():
+	for year in years:
+		add_yearfreqs(year)
+	topwords = get_topwords()
+	topwords.reverse()
+	writer.writerow(['word']+topwords)
+	for year in years:
+		cols = [yearprops[year].get(word,0) for word in topwords]	
+		writer.writerow([year]+cols)
+ 
+if __name__ == '__main__':
+	main()

### 2010-03-07 websearch/compute_rarewords.py

@@ -1,0 +1,141 @@
+#!/usr/bin/env python
+# encoding: utf-8
+
+"""
+For each claim, compute the two rarest words (using the wikipedia word list).
+Use this to index into claims efficiently.
+
+Then apply a more complex algorithm to determine whether one of the found phrases actually matches.
+"""
+
+import nltk
+import re
+import cPickle 
+import old_claims as o
+import operator as op
+
+ignorewords = set(["just","merely","purely","only","simple","were",
+		"massive","utter","clearly","the","is","a","the","in",
+		"was","wants","giant","","around","all","really","still"])
+
+wikitotalwords = 18312044.0
+
+def load_wiki():
+	wikifreq = {}
+	for line in file("/home/rob/git/thinklink/wiki_wordfreqs"):
+		(word,freq) = line.split(":")
+		wikifreq[word] = float(freq)
+	return wikifreq
+	
+wordfreqs = load_wiki()
+
+def wordprob(word):
+	return wordfreqs.get(word,2)/wikitotalwords
+
+firstwords = {}
+pairs = {}
+pair_claims = {}
+pair_weights = {}
+triple_claims = {}
+triple_weights = {}
+
+goodword = re.compile("[a-zA-Z]+")
+
+def is_good_word(word): return goodword.match(word)
+
+def claim_words(claim):
+	words = good_tokens(claim)
+	indexedwords = zip(words,range(0,len(words)))
+	scoredwords = [(word,wordfreqs.get(word,2),index) for (word,index) in indexedwords if not word in ignorewords]
+	scoredwords.sort(key=op.itemgetter(1))
+	topwords = scoredwords[:3]
+	topwords.sort(key=op.itemgetter(2))
+	return [word for (word,freq,index) in topwords]	
+
+bad_claims = set([line.strip() for line in file("../web_claim_finder/bad_claims.txt")])
+
+def add_claim(claim):
+	keywords = claim_words(claim)
+	if len(keywords) < 2: return
+	if claim in bad_claims: return
+	(first,second) = keywords[:2]
+	if not first in firstwords: firstwords[first] = set([])
+	firstwords[first].add(second)		
+	pairkey = first+"-"+second
+	if first == second: return
+	if len(keywords) == 2:
+		if not pairkey in pair_claims: pair_claims[pairkey] = []
+		pair_claims[pairkey].append(claim)
[…]

### 2010-03-07 websearch/html_to_text.py

@@ -1,0 +1,30 @@
+#!/usr/bin/env python
+# encoding: utf-8
+
+"""
+Translate an HTML file into simple text, discarding anything that 
+might mess up claim detection.
+"""
+
+import re
+
+script = re.compile("(<script.*?>.*?</script>)",re.I)
+style = re.compile("(<style.*?>.*?</style>)",re.I)
+comment = re.compile("<!--.*?-->")
+head = re.compile("<head.*?>.*?</head>",re.I)
+inline = re.compile("</?(b|em|strong|a|i|img|mark|span).*?>",re.I)
+tag = re.compile("</?.*?>")
+seps = re.compile("[\.\s]*\.[\.\s]*")
+space = re.compile("\s+")
+
+def html_to_text(html):
+	html = html.replace("\n"," ")
+	html = script.sub(". ",html)
+	html = style.sub(". ",html)
+	html = comment.sub(". ",html)
+	html = head.sub(". ",html)
+	html = inline.sub(" ",html)
+	html = tag.sub(". ",html)
+	html = seps.sub(". ",html)
+	html = space.sub(" ",html)
+	return html

### 2010-03-07 websearch/old_claims.py

@@ -1,0 +1,18 @@
+
+"""
+Create a short term claim set from the set of claims we used in the disputefinder toolbar.
+"""
+
+import csv
+import re
+
+def mysql_reader(f):
+	return csv.reader(f,doublequote=False,escapechar='\\',quoting=csv.QUOTE_ALL)
+
+def get_old_claims():
+	basic_claims = [(row[0],row[0]) for row in mysql_reader(file("old_claims.csv"))]
+	paraphrases = [(row[0],row[1]) for row in mysql_reader(file("old_paraphrases.csv"))]
+	return basic_claims + paraphrases
+	
+	
+	

### 2010-06-14 papers/search_disputed/search_disputed.tex
Added a lot of stuff previously missing from the repo. Not all of this is currently used.

\documentclass{acm_proc_article-sp}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}

\begin{document}

\title{Identifying Disputes between Web Pages}

%%
%% Note on formatting authors at different institutions, as shown below:
%% Change width arg (currently 7cm) to parbox commands as needed to
%% accommodate widest lines, taking care not to overflow the 17.8cm line width.
%% Add or delete parboxes for additional authors at different institutions. 
%% If additional authors won't fit in one row, you can add a "\\"  at the
%% end of a parbox's closing "}" to have the next parbox start a new row.
%% Be sure NOT to put any blank lines between parbox commands!
%%

%\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
%\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
%\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
%\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}

\newcommand{\needed}[1]{{\color{red}#1}}
%\newcommand{\needed}[1]{}
\newcommand{\want}[1]{}
\newcommand{\todo}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\node}[1]{}

\numberofauthors{5}

\author{
    Authors ommitted for blind reviewing.
}

\maketitle

\begin{abstract}
We present a method for automatically detecting when a claim appearing on a web page is disputed by another web page. Our method works by searching the web for lingustic patterns such as ``falsely claimed that X'' that suggest that a web page disagrees with some statement, and then examining the text on an input page to see if any of the text on that page is similar to one of the known disputed statements and appears in a similar context.

To determine how our method applies to web pages that users typically browse, we applied our method to \needed{100,000} pages that appear as search results for common web queries, and to \needed{10,000} pages that appear in search results for particular disputed terms. By examining a sample of these results, we found that our algorithm has precision \needed{70\%} and that \needed{10\%} of web searches should be expected to contain a dispute, as judged by our algorithm. 
\end{abstract}

\section{Introduction}

\section{Background and Related Work}

\section{Corpus of Disputed Claims}

\section{Matching Disputed Claims}

Identify wikipedia links on a page that disputes something.

Determine if another page seems to have wikipedia links to the same concepts.

Find a text string that looks similar to something we have on that page because it has the same top keywords.

Then use a classifier that takes into account a number of features. Then refine until we work out what features are important.

Variants: 
\begin{itemize}
 \item Simple bag-of-words with no context
 \item Restrict claims to ones with high linkiness
 \item Restrict claims to ones with high contextual linkiness
 \item Restrict claims to ones with same context
 \item Restrict claims to ones with same context and high contextual linkiness
 \item Only require N keywords to match
 \item Reduce weight of words after comma or ``and''
 \item Bias towards words or wikipedia links near to the suspect sentence.
 \item Bias towards words in the same paragraph, or nearby paragraphs
 \item Take negations into account.
 \item Don't require suspect words to all be in the same sentence.
\end{itemize}

How does accuracy scale with amount of training data. Since we are creating training data manually, it's important to be able to tell when we reach a knee in the curve and don't need to mark any more.

Build a simple web interface to allow people to do training. Interface presents a sequence of examples and invites the user to say whether it is a match or not. If we get it working well, then expose it to users?

Use libsvm for machine learning, following beginers guide, using radial basis function.

Do initial algorithm evaluation on a small claim set where we have the full text of the pages, to give us the opportunity to experiment with different method to see what works.

\section{Evaluating on Search Data}

Evaluate a variety of variants with different features disabled. This reveals how much each feature actually helps in practice.

\section{Discussion}

\section{Conclusions}

\section{To Cite}

Warren Sack on ``Searching the Net for Differences of Opinion'' and ``On the Computation of Point of View''.

Tell Me More project, which provides extra information that was otherwise missing.

Joke Retreival paper.

Learning to Link with Wikipedia.

\end{document}

### 2010-06-14 papers/search_disputed/sigproc-sp.tex
Added a lot of stuff previously missing from the repo. Not all of this is currently used.

--- 2009-10-10 papers/www_disputefinder/www2010-sample.tex
@@
-% This is "www2010-sample.tex" copied from "www2005-sample.tex" V1.2 January 26 2004
-% This file should be compiled with V1.4 of "www2010-submission.class"
+% THIS IS SIGPROC-SP.TEX - VERSION 3.1
+% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
+% APRIL 2009
 %
-% This example file demonstrates the use of the 'www2010-submission.cls'
-% V1.4 LaTeX2e document class file. It is for those submitting
-% articles to the WWW'04 Conference WHO DO NOT WISH TO 
-% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
-% The 'www2010-submission.cls' file will produce a similar-looking,
-% albeit, 'tighter' paper resulting in, invariably, fewer pages.
-%
+% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
+% LaTeX2e document class file for Conference Proceedings submissions.
 % ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V1.4) produces:
-%       1) NO Permission Statement
-%       2) WWW'04-specific conference (location) information
+% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
 %       3) The Copyright Line with ACM data
-%       4) NO page numbers
-%
+%       4) Page numbering
 % ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
+% It is an example which *does* use the .bib file (from which the .bbl file
+% is produced).
 % REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
+% and prior to final submission,
+% you need to 'insert'  your .bbl file into your source .tex file so as to provide
 % ONE 'self-contained' source file.
 %
-% ================= IF YOU HAVE QUESTIONS =======================
-% Questions regarding the SIGS styles, SIGS policies and
-% procedures, Conferences etc. should be sent to
-% Julie Goetz (goetz@acm.org) or Adrienne Griscti (griscti@acm.org)
+% Questions regarding SIGS should be sent to
+% Adrienne Griscti ---> griscti@acm.org
 %
-% Technical questions only to
-% Gerald Murray (murray@acm.org)
-% ===============================================================
+% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
+% Gerald Murray ---> murray@hq.acm.org
 %
-% For tracking purposes - this is V1.2 - January 26 2004
-\documentclass{www2010-submission}
+% For tracking purposes - this is V3.1SP - APRIL 2009
+
+\documentclass{acm_proc_article-sp}
 
 \begin{document}
+
+\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
+Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
+\subtitle{[Extended Abstract]
+\titlenote{A full version of this paper is available as
+\textit{Author's Guide to Preparing ACM SIG Proceedings Using
+\LaTeX$2_\epsilon$\ and BibTeX} at
+\texttt{www.acm.org/eaddress.htm}}}
 %
-\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
-Format\titlenote{(Produces the WWW2010-specific release, location and
-copyright information). For use with
-www2010-submission.cls V1.4. Supported by ACM.}}
-%\subtitle{[Extended Abstract]
-%\titlenote{A full version of this paper is available as
-%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-%\LaTeX$2_\epsilon$\ and BibTeX} at
-%\texttt{www.acm.org/eaddress.htm}}}
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
 %
-% You need the command \numberofauthors to handle the "boxing"
-% and alignment of the authors under the title, and to add
-% a section for authors number 4 through n.
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
 %
-% Up to the first three authors are aligned under the title;
-% use the \alignauthor commands below to handle those names
-% and affiliations. Add names, affiliations, addresses for
-% additional authors as the argument to \additionalauthors;
-% these will be set for you without further effort on your
-% part as the last section in the body of your article BEFORE
-% References or any Appendices.
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+%
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
 
-\numberofauthors{5}
+\numberofauthors{8} %  in this sample file, there are a *total*
+% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+% reasons) and the remaining two appear in the \additionalauthors section.
 %
-% Put no more than the first THREE authors in the \author command
-
-% NOTE: All authors should be on the first page. For instructions
-% for more than 3 authors, see:
-% http://www.acm.org/sigs/pubs/proceed/sigfaq.htm#a18
-
 \author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
 %
@@
 % affiliation/address with \affaddr, and tag the
-%% e-mail address with \email.
-\alignauthor Ben Trovato\titlenote{Dr.~Trovato also works at...}\\
+% e-mail address with \email.
+%
+% 1st. author
+\alignauthor
+Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
        \affaddr{Institute for Clarity in Documentation}\\
@@
        \email{trovato@corporation.com}
-\alignauthor G.K.M. Tobin\\
+% 2nd. author
+\alignauthor
+G.K.M. Tobin\titlenote{The secretary disavows
+any knowledge of this author's actions.}\\
        \affaddr{Institute for Clarity in Documentation}\\
@@
        \email{webmaster@marysville-ohio.com}
-\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\\
-       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
-       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
+% 3rd. author
+\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
+one who did all the really hard work.}\\
+       \affaddr{The Th{\o}rv{\"a}ld Group}\\
+       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
        \affaddr{Hekla, Iceland}\\
        \email{larst@affiliation.org}
+\and  % use '\and' if you need 'another row' of author names
+% 4th. author
+\alignauthor Lawrence P. Leipuner\\
+       \affaddr{Brookhaven Laboratories}\\
+       \affaddr{Brookhaven National Lab}\\
+       \affaddr{P.O. Box 5000}\\
+       \email{lleipuner@researchlabs.org}
+% 5th. author
+\alignauthor Sean Fogarty\\
+       \affaddr{NASA Ames Research Center}\\
+       \affaddr{Moffett Field}\\
+       \affaddr{California 94035}\\
+       \email{fogartys@amesres.org}
+% 6th. author
+\alignauthor Charles Palmer\\
+       \affaddr{Palmer Research Laboratories}\\
+       \affaddr{8600 Datapoint Drive}\\
+       \affaddr{San Antonio, Texas 78229}\\
+       \email{cpalmer@prl.com}
 }
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group,
+% There's nothing stopping you putting the seventh, eighth, etc.
+% author on the opening page (as the 'third row') but we ask,
+% for aesthetic reasons that you place these 'additional authors'
+% in the \additional authors block, viz.
+\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
 email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
@@
 \date{30 July 1999}
+% Just remember to make sure that the TOTAL number of authors
+% is the number that will appear on the first page PLUS the
+% number that will appear in the \additionalauthors section.
 
@@
 \begin{abstract}
-This paper provides a sample of a LaTeX document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings. It is an {\em alternate} style which produces
-a {\em tighter-looking} paper and was designed in response to
-concerns expressed, by authors, over page-budgets.
-It complements the document \textit{Author's (Alternate) Guide to
-Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-This source file has been written with the intention of being
+This paper provides a sample of a \LaTeX\ document which conforms to
+the formatting guidelines for ACM SIG Proceedings.
+It complements the document \textit{Author's Guide to Preparing
+ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
+source file has been written with the intention of being
 compiled under \LaTeX$2_\epsilon$\ and BibTeX.
+
 The developers have tried to include every imaginable sort
@@
 equations, theorems, tables and figures.
+
 To make best use of this sample document, run it through \LaTeX\
 and BibTeX, and compare this source code with the printed
-output produced by the dvi file. A compiled PDF version
-is available on the web page to help you with the
-`look and feel'.
+output produced by the dvi file.
 \end{abstract}
 
-% A category with only the three required fields
-\category{H.4.m}{Information Systems}{Miscellaneous}
-\category{D.2}{Software}{Software Engineering}
+% A category with the (minimum) three required fields
+\category{H.4}{Information Systems Applications}{Miscellaneous}
 %A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures,
-performance measures]
+\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
-\terms{Delphi theory}
+\terms{Theory}
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
 
@@
 \subsection{Citations}
-Citations to articles \cite{bowman:reasoning,
-clark:pct, braams:babel, herlihy:methodology},
-conference proceedings \cite{clark:pct} or
-books \cite{salas:calculus, Lamport:LaTeX} listed
+Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
+conference
+proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
 in the Bibliography section of your
@@
 This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed or supported.
+No other citation format is endorsed.
 
@@
 \centering
-%\epsfig{file=fly.eps}
+\epsfig{file=fly.eps}
 \caption{A sample black and white graphic (.eps format).}
@@
 \centering
-%\epsfig{file=fly.eps, height=1in, width=1in}
+\epsfig{file=fly.eps, height=1in, width=1in}
 \caption{A sample black and white graphic (.eps format)
@@
 \textbf{figure*} to enclose the figure and its caption.
-\begin{figure*}
-\centering
-%\epsfig{file=flies.eps}
-\caption{A sample black and white graphic (.eps format)
-that needs to span two columns of text.}
-\end{figure*}
-and don't forget to end the environment with
-{figure*}, not {figure}!
 
@@
 commands as appropriate for the different file types.
-
-\begin{figure}
-\centering
-%\psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.}
-\end{figure}
 
@@
 This uses the \textbf{theorem} environment, created by
-the \texttt{{\char'134}newtheorem} command:
+the\linebreak\texttt{{\char'134}newtheorem} command:
 \newtheorem{theorem}{Theorem}
@@
 
+\begin{figure}
+\centering
+\psfig{file=rosette.ps, height=1in, width=1in,}
+\caption{A sample black and white graphic (.ps format) that has
+been resized with the \texttt{psfig} command.}
+\end{figure}
+
 Two lists of constructs that use one of these
@@
 \textit{Author's  Guidelines}.
+
+\begin{figure*}
+\centering
+\epsfig{file=flies.eps}
+\caption{A sample black and white graphic (.eps format)
+that needs to span two columns of text.}
+\end{figure*}
+and don't forget to end the environment with
+{figure*}, not {figure}!
 
@@
 the command \texttt{{\char'134}thebibliography}.
-%
 % This next section command marks the start of
@@
 \section{More Help for the Hardy}
-The www2010-submission.cls file itself is chock-full of succinct
+The acm\_proc\_article-sp document class file itself is chock-full of succinct
 and helpful comments.  If you consider yourself a moderately
@@
 it useful but please remember not to change it.
-\balancecolumns % GM July 2000
+\balancecolumns
 % That's all folks!

### 2010-06-14 python/djangotest/polls/admin.py

@@ -1,0 +1,19 @@
+from djangotest.polls.models import Poll, Choice
+from django.contrib import admin
+
+class ChoiceInline(admin.TabularInline):
+	model = Choice
+	extra = 3
+
+class PollAdmin(admin.ModelAdmin):
+	fieldsets = [
+		(None,               {'fields': ['question']}),
+		('Date information', {'fields': ['pub_date']}),
+	]
+	list_display = ['question','pub_date','was_published_today']
+	inlines = [ChoiceInline]
+	list_filter = ['pub_date']
+	search_fields = ['question']
+	date_hierachy = ['pub_date']
+	
+admin.site.register(Poll,PollAdmin)

### 2010-06-14 python/djangotest/polls/models.py

@@ -1,0 +1,25 @@
+from django.db import models
+import datetime
+
+# Create your models here.
+
+class Poll(models.Model):
+	question = models.CharField(max_length=200)
+	pub_date = models.DateTimeField('date published')
+	
+	def __unicode__(self):
+		return self.question
+	
+	def was_published_today(self):
+		return self.pub_date.date() == datetime.date.today()	
+	was_published_today.short_description = "Published today?"
+
+	
+class Choice(models.Model):
+	poll = models.ForeignKey(Poll)
+	choice = models.CharField(max_length=200)
+	votes = models.IntegerField()
+	
+	def __unicode__(self):
+		return self.choice
+	

### 2010-06-14 python/djangotest/polls/views.py

@@ -1,0 +1,34 @@
+from django.http import HttpResponse, HttpResponseRedirect
+from djangotest.polls.models import Choice,Poll
+from django.shortcuts import render_to_response, get_object_or_404
+from django.http import Http404
+from django.template import RequestContext
+from django.core.urlresolvers import reverse
+
+def index(request):
+	latest_poll_list = Poll.objects.all().order_by("-pub_date")[:5]
+	return render_to_response('polls/poll_list.html',{'latest_poll_list':latest_poll_list})
+
+def detail(request,poll_id):
+	p = get_object_or_404(Poll,pk=poll_id)
+	return render_to_response('polls/poll_detail.html',{'poll':p},
+		context_instance=RequestContext(request))
+
+def results(request,poll_id):
+	p = get_object_or_404(Poll,pk=poll_id)
+	return render_to_response('polls/results.html',{'poll':p})
+	
+def vote(request,poll_id):
+	p = get_object_or_404(Poll,pk=poll_id)
+	try:
+		selected_choice = p.choice_set.get(pk=request.POST['choice'])
+	except (KeyError, Choice.DoesNotExist):
+		return render_to_response('polls/poll_detail.html',
+				{'poll':p, 'error_message':"You didn't select a choice."},
+				context_instance=RequestContext(request))
+	else:
+		selected_choice.votes += 1
+		selected_choice.save()
+		return HttpResponseRedirect(reverse('poll_results', args=(p.id,)))
+	
+# Create your views here.

### 2010-06-14 python/djangotest/settings.py

@@ -1,0 +1,83 @@
+# Django settings for disputesearch project.
+
+DEBUG = True
+TEMPLATE_DEBUG = DEBUG
+
+ADMINS = (
+    # ('Your Name', 'your_email@domain.com'),
+)
+
+MANAGERS = ADMINS
+
+DATABASE_ENGINE = 'django.db.backends.sqlite3'           # 'postgresql_psycopg2', 'postgresql', 'mysql', 'sqlite3' or 'oracle'.
+DATABASE_NAME = '/home/rob/databases/djangotest'             # Or path to database file if using sqlite3.
+DATABASE_USER = ''             # Not used with sqlite3.
+DATABASE_PASSWORD = ''         # Not used with sqlite3.
+DATABASE_HOST = ''             # Set to empty string for localhost. Not used with sqlite3.
+DATABASE_PORT = ''             # Set to empty string for default. Not used with sqlite3.
+
+# Local time zone for this installation. Choices can be found here:
+# http://en.wikipedia.org/wiki/List_of_tz_zones_by_name
+# although not all choices may be available on all operating systems.
+# If running in a Windows environment this must be set to the same as your
+# system time zone.
+TIME_ZONE = 'America/Chicago'
+
+# Language code for this installation. All choices can be found here:
+# http://www.i18nguy.com/unicode/language-identifiers.html
+LANGUAGE_CODE = 'en-us'
+
+SITE_ID = 1
+
+# If you set this to False, Django will make some optimizations so as not
+# to load the internationalization machinery.
+USE_I18N = True
+
+# Absolute path to the directory that holds media.
+# Example: "/home/media/media.lawrence.com/"
+MEDIA_ROOT = ''
+
+# URL that handles the media served from MEDIA_ROOT. Make sure to use a
+# trailing slash if there is a path component (optional in other cases).
+# Examples: "http://media.lawrence.com", "http://example.com/media/"
+MEDIA_URL = ''
+
+# URL prefix for admin media -- CSS, JavaScript and images. Make sure to use a
+# trailing slash.
+# Examples: "http://foo.com/media/", "/media/".
+ADMIN_MEDIA_PREFIX = '/media/'
+
+# Make this unique, and don't share it with anybody.
+SECRET_KEY = 'bzbp+u6ktq!lwthyubasc5^3*%pvcbj6y-&ulf=-3xzuc=ay4-'
+
+# List of callables that know how to import templates from various sources.
[…]

### 2010-06-14 python/turk/__init__.py

@@ -1,0 +1,3 @@
+
+""" create jobs on Amazon Mechanical Turk and process the output"""
+

### 2010-06-14 python/turk/turk_process.py

@@ -1,0 +1,152 @@
+"""
+Analyse the answers turkers gave for data produced by "turk_data".
+See if any of the users seem to have misbehaved.
+"""
+
+import csv
+import turk_data as td
+import nlptools as nt
+
+
+def load_data(filename):
+	return [row for row in csv.DictReader(file(filename),delimiter=",",quotechar='"',quoting=csv.QUOTE_ALL,escapechar='\\')]
+
+def print_workers(rows):
+	workers = {}
+	for row in rows:
+		workerid = row["WorkerId"]
+		if row["AssignmentStatus"] == "Rejected": continue
+		workers[workerid] = workers.get(workerid,0) + 1
+	sorted = nt.sorted_freqs(workers)
+	for k,v in sorted:
+		print k,v
+
+def get_answers(rows,worker=None,workerset=None):
+	answers = []
+	for row in rows:
+		workerid = row["WorkerId"]
+		if worker and worker != workerid: continue
+		if workerset and not worker in workerset: continue
+		if row["AssignmentStatus"] == "Rejected": continue
+		if row["AssignmentStatus"] == "Accepted": continue
+		for i in range (1,11):
+			snip = row["Input.snip"+str(i)]
+			answer = row["Answer.Q"+str(i)]
+			answers.append((workerid,snip,answer,row["HITId"]+str(i)))
+	return answers
+	
+def answers_by_hit(answers):
+	byhit = {}
+	for (worker,snip,choice,hit) in answers:
+		byhit[hit] = byhit.get(hit,[]) + [choice]
+	return byhit
+	
+def snip_by_hit(answers):
+	byhit = {}
+	for (worker,snip,choice,hit) in answers:
+		byhit[hit] = snip
+	return byhit	
+	
+def print_answers(answers):
+	for worker,snip,choice,hit in answers:
+		print choice,"--",snip,"\n" 
+
+def is_gold_wrong(answer):
+	worker,snip,choice = answer
+	if snip in td.good_gold and choice != "good": return True
+	if snip in td.bad_gold and choice == "good": return True
+	return False
+	
+def get_gold_wrong(answers): return [answer for answer in answers if is_gold_wrong(answer)]	
+
+approved = set()
+rejected = set()
+
+def approve_workers(workers,rows):
+	for worker in workers:
+		approve_worker(worker,rows)
+
+def approve_worker(workerid,rows):
+	for row in rows:
[…]

### 2010-06-14 website/claimfilter/__init__.py

@@ -1,0 +1,8 @@
+"""
+Use simple machine learning techniques to determine 
+whether a claim is grammatically good, and where a suffix should be 
+chopped off.
+
+This app is used purely to build a classifier that can be used
+elsewhere. It is not used as part of the online system.
+"""

### 2010-06-14 website/claimfilter/models.py

@@ -1,0 +1,8 @@
+from django.db import models
+
+# Create your models here.
+
+class RawClaim(models.Model):
+	rawtext = models.CharField(max_length=1000)
+	correcttrim = models.CharField(max_length=1000)	# "X" if bad, empty if not done yet
+
